### 2018-05-07 docs/google-research-awards-latam/main.tex

\documentclass[11pt]{article}
%\documentclass[dvips,11pt]{article}

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}

% ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
%% macros
\newcommand{\splat}{SPLat}
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}

%% \setlength{\oddsidemargin}{0.25in}
%% \setlength{\textwidth}{6.5in}
%% \setlength{\topmargin}{0in}
%% \setlength{\textheight}{8.5in}

%\renewcommand\Affilfont{\fontsize{9}{10.8}\itshape}
% These force using more of the margins that is the default style

\begin{document}

%\title{Debugging I/O Anomalies in Distributed Configurable Systems}
\title{\LARGE{}Testing for Configuration Errors in Distributed Systems}
\author{}
\date{}

% You can leave out "date" and it will be added automatically for today
% You can change the "\today" date to any text you like

\makeatletter
\def\maketitle{%
  \par{\centering\large\textbf{\@title}\normalsize\par}\vspace{3ex}%
  \par{\@author}%
  \par}
\makeatother

\maketitle

\vspace{-2ex}
\small
\begin{table}[h!]
  \centering%% Centro de Inform\'atica - CIn \\
  \begin{tabular*}{.85\linewidth}{@{\extracolsep{\fill}}ll}
    PI: Marcelo d'Amorim (\url{damorim@cin.ufpe.br}) & Universidade Federal de Pernambuco \\
    Phone: +55 (81) 98800-2010 [mobile]  & Av. Jornalista Anibal Fernandes, S/N \\
    \phantom{x}\hspace{7ex}+55 (81) 2126-8430, ext. 4379 [work] & Cidade Universit\'aria, PE, Brazil, 50.740-560\\
    \multicolumn{2}{l}{\noindent\textbf{Contact}: Wei Jin
      (\url{superbobo@google.com})~~--~~\textbf{Sponsor}: Sai Zhang (\url{saizhang@google.com})}\\
  \end{tabular*}
\end{table}
\normalsize

\vspace{-2ex}
\begin{abstract}
This proposal focuses on the important problem of testing for
configuration errors in distributed systems. The goal is to increase
system's reliability by preventing these errors to escape to
production.
%% The input of our approach is a configurable distributed
%% program and the output is a set of constraints denoting what
%% configurations are likely valid for use.
\end{abstract}

%% Diagnosing those errors
%% can be very challenging.
%% The overall goal is to improve developer's productivity in fixing
%% those errors.  The input to our proposed approach is a set of
%% distributed traces and the output is a likely explanation of failure
%% that developers can relate.

\section{Problem}

\Comment{Configurability enables developers to adapt
system's behavior to different circumstances.  by selecting or
  adjusting options. These systems are \emph{prevalent}. The
  Firefox web browser~\cite{firefox-web}, the Linux
  kernel~\cite{linux-kernel-web}, the GCC compiler
  infrastructure~\cite{gcc-web}, and the deals-recommendation web
  service Groupon~\cite{groupon-web} are some well-known examples of
  configurable systems. }

Configurable systems are those that can be adapted from a set of input
options, reflected in code in the form of variations. Configurable
systems are
prevalent\Comment{~\cite{yin-etal-sosp2011,weiss-etal-ase2017}} and,
unfortunately, configuration-related errors are difficult to
detect~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}
and diagnose~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014}.
Testing and debugging becomes even worse when the system being
configured is a distributed system~\cite{matt-welsh-blog}. Detecting
these errors with testing, before they escape, is therefore important
as it is hard to troubleshoot error manifestations in complex
production
environments~\cite{jin-orso-icse2012}. Configuration-related errors in
distributed systems are unfortunately \emph{not rare}. Some of these
errors have been widely publicized in the media given the volume of
users or data they affected~\cite{azure-error,facebook-error,
  dns-misconfiguration}.

%% Troubleshooting distributed systems is known to be
%% challenging~\cite{BeschastnikhWBE2016}\Comment{ as reconstructing the
%%   global state of the system after failure observations is difficult
%%   or even impossible~\cite{mattern-virtual-time89}}.
%% Distributed systems are prevalent. Examples of distributed
%% applications include the Google Spanner distributed
%% database~\cite{corbett-etal-osdi2012} and IoT
%% deployments~\cite{android-things-one}.

%% Configuration is an orthogonal aspect to distribution but one that
%% makes testing and debugging even more
%% challenging~\cite{matt-welsh-blog}.

\vspace{-1ex}
\begin{center}
\fbox{
  %  \begin{minipage}{18.75cm}
  \begin{minipage}{11.75cm}
    \centering
    \textit{The goal of this project is to improve reliability in
      distributed systems\\ by finding configuration errors during
      testing.}
  \end{minipage}
}
\end{center}
\vspace{-1ex}

%% These errors emerge from the inability of developers to anticipate the
%% impact of local changes in dependent
%% features~\cite{ribeiro-etal-icse2014}.
%% Configuration errors are even
%% more problematic when they manifest in distributed
%% systems.
%% Fighting configuration errors
%% is also
%% challenging~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,kim-etal-fse2013,ribeiro-etal-icse2014,behrang-etal-fse2015}.

%% Preventing developers from
%% making these
%% errors~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,ribeiro-etal-icse2014,behrang-etal-fse2015},
%% testing for these errors~\cite{cohen-etal-icse2003,cohen:issta07,cohen-shmuelur-icse2010,emine-etal-issta2011,medeiros-etal-icse2016}
%% and diagnosing those
%% errors~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014} are
%% challenging activities.
%% At Google, configuration errors are also a
%% problem.
%% Understanding these errors in complex distributed system is an
%% essential time-consuming activitiy~\cite{matt-welsh-blog}.

%\section{Related Work}

\vspace{1ex} \textbf{Related Work.}~Literature on distributed
debugging is vast~\cite{BeschastnikhWBE2016}. Record and replay
solutions, such as Friday~\cite{geels-usenix2007} and
D3S~\cite{d3s-debugging-deployed-distributed-systems}, capture
nondeterministic events during execution to replay them a posteriori.
Tracing solutions~\cite{sambasian-etal-techreport2014}, such as Pivot
Tracing~\cite{mace-etal-usenix2016}, instrument the application to
forward tracing metadata to a distributed database for offline
analysis. In principle, these solutions could be adapted to track
configuration data but they are either heavyweight or intrusive
(\ie{}, they require modification in software).  These issues limit
the applicability of Record and Replay and Tracing in practice. Log
Analysis does not suffer from these limitations as it mines anomalies
from the logs that the system already produces~\cite{xu-etal-slam10}.
However, Log Analysis needs to cope with the potential for missing
relevant data and also to handle massive amounts of data.
%%
Considering the configuration dimension, testing and debugging for
distributed systems has not been studied in
depth~\cite{matt-welsh-blog}, in contrast to what has been observed in
non-distributed
systems~\cite{yin-etal-sosp2011,zhang-ernst-icse2013,zhang-ernst-icse2014,behrang-etal-fse2015,weiss-etal-ase2017}.
Most testing in distributed systems is done manually and after the
fact (\ie{} after failures are observed) to augment regression test
suites~\cite{beschastnikh-etal-icse2014}. Model checking distributed
systems (,which is essentially systematic testing) has been
proposed~\cite{killian-etal-nsdi07,yang-etal-nsdi09} but these
existing approaches do not take configurations into account.

%% \section{Goal}
%% Our general goal is to improve system's reliability\Comment{ in distributed
%%   systems}.  Our specific goal is to find configuration errors in
%% distributed systems.

%% They are hard to diagnose, especially in distributed systems.
%% Furthermore, these errors gain importance when they relate to data
%% from large organizations or a large number of users.
%% Defects that escape to production still need to be handled and,
%% certainly, these are the cases that require more immediate
%% diagnosis.

%% ``In-production'' errors are inevitable; they originate from the
%% inherent inability of ``in-house'' testing to find all possible
%% bugs~\cite{jin-orso-icse2012}.  These errors are pressing given the
%% imminent impact on users.

%% We refer to this problem, prevalent in configuration error diagnosis,
%% as (configuration) error classification.

%% A common problem in
%% this context is to decide whether a failure was manifested because of
%% a misconfiguration, because of invalid inputs\Comment{Undocumented
%%   preconditions in code can delay observation of failures.}, or
%% because of software
%% bugs~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014,sabrina-etal-splc15}.

\section{Approach\Comment{Solution Design (Error Classification from
    Distributed Traces)}}

We propose an approach that uses automated test generation to find
configuration errors in distributed systems.  Our approach exercises
the system observing anomalies in behavior due to configuration
changes. Testing configurable software is a topic on which the group
of the PI has focused in the recent
past~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}.
Our approach is similar in spirit to MoDist~\cite{yang-etal-nsdi09}, a
black-box model checker that runs the system modifying certain aspects
during execution such as processor speed and message sequencing, but
it takes configuration options into account.

\vspace{1ex}\noindent\textbf{Input/Output.}~The input of our technique
is a configurable distributed system and the output is one of more
failing tests and error reports.

%% The input to our
%% problem is a set of distributed traces (\eg{}
%% using Dapper~\cite{dapper-google-tr2010}, Pivot tracing~\cite{mace-etal-usenix2016}), which collectively
%% indicate a failure manifestation.  The output is a high-level report
%% explaining the potential cause of failure.  For example, ``service Y

\vspace{1ex}\noindent\textbf{Requirements.}~The technique should be
simple to use and highly automated. It should produce high-level
reports that enable developers to promptly understand and fix the
problems identified. It should run efficiently.

%%   It should
%% leverage available data\Comment{~--~produced with widely-used
%%   tools~--~} as opposed to relying on additional data that could be
%% produced with new tools.

%% \begin{itemize}
%%    \setlength\itemsep{0.01em}    
%% \end{itemize}

%% As for (1), large distributed systems often provide monitoring
%% solutions to assist with bug triage.  This work will use the
%% distributed traces produced by Dapper~\cite{dapper-google-tr2010}, the
%% distributed tracing infrastructure at Google.

\newcommand{\taskvirtualization}{1}
\newcommand{\taskteststrategies}{2}
%\newcommand{\idinteractions}{3}
\newcommand{\idminimization}{3}

\vspace{1ex}\noindent\textbf{Tasks}.~\taskvirtualization{}) Define
containerization strategy. \taskteststrategies{}) Define test
strategy. \idminimization{}) Minimize test sequences.

%% \idinteractions{}) Identify interactions between configured
%% services.

%% \begin{enumerate}
%%   \setlength\itemsep{0.01em}
%% \item\label{task-virtualization} Define containerization strategy.
%% \item\label{task-test-strategies} Define test strategy.
%% \item\label{id-interactions} Identify interactions between configured services.
%% \item\label{id-minimization} Minimize test sequences.
%% %\item Create benchmark of configuration errors in distributed systems
%% \end{enumerate}

%\vspace{1ex}\noindent\textbf{Approach}.

\vspace{1ex} Considering task~\taskvirtualization{}, it is important
to start a distributed system quickly and to run the system in an
isolated environment. We plan to use Docker images~\cite{docker} to
jump start the individual nodes of a distributed system. Considering
task~\taskteststrategies{}, our approach is to use lighter weight test
methods first and then assess effectiveness and cost of heavier weight
testing strategies.  More specifically, initially, we plan to use
existing test cases~\cite{maddox-2015-acmqueue} and select
configurations to run those tests using black-box techniques, such as
Combinatorial Interaction Testing
(CIT)~\cite{nie-leung-acm-surveys2011}.  It is worth noting that
centralized configuration servers such as
ZooKeeper's~\cite{apache-zookeeper} and Spring Cloud
Config~\cite{spring-cloud-config} are becoming popular to manage
configurations in distributed systems and should facilitate this task.
We also plan to explore gray-box techniques for selecting
configurations~---~we will investigate the effectiveness of mining
network interactions to decide what configurations to test
next. Existing log analysis tools can help on
that~\cite{mace-etal-usenix2016}. For example, our analysis may
discover that a datum in a message triggers a different decision in a
node, as observed from execution logs, and that that datum is related
to a configuration option. We conjecture that selecting configurations
that triggers different interactions increases the ability of testing
to find faults. Finally, automated test generation can create
arbitrarily long test sequences which hinders reproducibility and
fault diagnosis.  Task~\idminimization{} is concerned with the
minimization of fault-revealing tests to facilitate debugging.

%% messages on the network, similarly to
%% MoDist~\cite{yang-etal-nsdi09}\Comment{ and
%%   Basset~\cite{lauterburg-etal-fse2010},}, but also by modifying
%% configurations.

We will build tools that implement and support our approach.  The
output of our approach is a failing test, which could reveal a bug or
a misconfiguration. In case the developer finds out that the failure
corresponds to a bug, the code needs to be fixed.  In case of
misconfigurations, our approach could be used to prevent errors
provided that the developer adds checks to (in)validate certain
configurations from being triggered.  Alternatively, the approach
could be used to diagnose errors as logs reporting error
manifestations could be saved and then used for comparison with
production runs.

%% Our first course of action to
%% diagnosing configuration errors is to search for unexpected
%% \emph{feature interactions}~\cite{pamela-zave-feature-interaction}.  A
%% feature interaction happens, for example, when a service reads from
%% the state that another service writes. The hypothesis is that the
%% failure was caused by an interaction across distributed services
%% manifested through a configuration that has not been extensively
%% tested, resulting in a failure.\Comment{ Consequently, the defect was
%%   enabled in production only at the point in time the error was
%%   manifested.}  As it is challenging to detect those interactions
%% without sacrificing system's performance (\eg{}, adding monitoring probes), we plan to use existing
%% execution logs to estimate them. To fix the problem, a developer needs
%% to either fix a bug in code related to that configuration or prevent
%% the use of that configuration, as it could be illegal.  In case no
%% discrepancy has been found in the patterns of configuration
%% interaction, our approach would look for anomalies in the use of input
%% data involving those configurations. Potential activities associated
%% to this project include:

%% \begin{itemize}
%%   \setlength\itemsep{0.01em}  
%%   \item Identify interaction between configured services.  This task
%%     is responsible to find what services interact
%%     and through which configurations they interact.  Existing log
%%     analysis tools can help assist this
%%     activity~\cite{beschastnikh-etal-icse2014,BeschastnikhWBE2016,shiviz-web}.
%%   \item Investigate techniques to precisely and efficiently identify
%%     anomalies in usage of input data, modulo service interaction and
%%     their configurations.  Potential solutions include the use of
%%     invariant detectors (e.g.,
%%     Daikon~\cite{daikon-2016,BeschastnikhWBE2016}) and anomaly
%%     detectors based on regression and neural network
%%     models~\cite{Alpaydin:2010:IML:1734076}, for instance.
%%   \item Create a benchmark of distributed systems with configuration
%%     errors.\Fix{elaborate...}
%%   \item 
%% \end{itemize}

%% This proposal addresses the problem of debugging large-scale
%% configurable distributed systems.  The hypothesis is that system's
%% configuration errors are often manifested through anomalies in I/O
%% usage.

%\subsection*{Details}

%% For the sake of presentation, we use the term ``test case'' to refer
%% to a scenario of execution that manifests a problem.  A test case can
%% be materialized through an executable test artifact (in-house) or
%% through an execution log (in-production).  Handling in-house and
%% in-production bugs are in the scope of this project.

%% Our debugging approach is summarized as follows: (1) Augment test
%% cases with differential test oracles, (2) Explore configurations from
%% the test, and (3) Look for correlations between configuration options
%% and failures.  We detail below each of these parts.

%% \textbf{Oracles (1).} We assume that an important class of errors in
%% distributed systems are due to
%% misconfigurations~\cite{matt-welsh-blog}.  Furthermore, we conjecture
%% that an important class of these errors manifest I/O anomalies (e.g.,
%% excessive use of memory or time).  We plan to apply differential
%% testing in this context to discover these problems.  More
%% specifically, we want to detect anomalies in the profile of resource
%% usage (memory/network) across multiple executions induced by a
%% selection of configurations over a given test.

%% \textbf{Configuration selection (2).} Testing is an essential part of
%% the debugging process. Test case diversity is generally considered
%% beneficial to identify root causes of
%% failure~\cite{campos-etal-ase2016}.  Diversity of configurations, in
%% particular, plays an important role in the context of this project.
%% We plan to use existing configuration selection
%% techniques~\cite{medeiros-etal-icse2016,kim-etal-fse2013,sabrina-etal-splc15,souto-damorim-jss-2016},
%% including ours, to explore the space of configurations reachable from
%% existing test cases.

%% \textbf{Fault localization and explanation (3).} Statistical-based Fault
%% Localization (SFL) is a lightweight method to identify suspicious
%% components in a computational system from a set of passing and failing
%% executions~\Fix{cite}.  We plan to apply SFL and look for abstractions
%% of error explanation that can be given to users to help identify the
%% culprit.

%% It is important to note that if executable test cases can be
%% obtained diagnosis can be performed at source-level.

%% \subsection*{Debugging in production}

%% In principle, the approach presented above could be used to identify
%% inconsistencies in existing integration tests, by exploring more
%% rigorously reachable configurations from tests.  However, defects that
%% escape to production still need to be handled and, certainly, these
%% are the cases that require more immediate diagnosis.  To this end, one
%% important challenge is to reconstruct, from production logs, the steps
%% that approximately characterize the original error-manifesting
%% execution.  Two alternatives for that will be investigated: (1) to
%% reconstruct executable integration tests that partially reflect the
%% observed behavior in logs.  This assumes that an infrastructure for
%% isolated re-execution of tests exists, which may not be realistic. (2)
%% to elaborate abstract behavior models for resource consumption which
%% \emph{are aware of configuration options used}.  Each approach is
%% challenging.

%% \Fix{...talk about surrogate regression + neural network models...}

%% Ideally, we would like even to generate new execution scenarios
%% from observations...

%% \subsection*{Future}
%% One potentially promising direction to expand this project is to use
%% historical data (both short and long-term) to prune the search space.
%% Lightweight change impact analysis can help finding hot spots for
%% analysis and code stability analysis can help finding cold spots.
%% Other directions for further investigation include plugin validation
%% for user-configurable applications (such as web browsers) and lifting
%% dataflow analysis for configuration awareness, a problem that has been
%% recently investigated but is restricted to simple
%% analysis~\cite{spllift}.  Recent advances of Datalog
%% solvers~\cite{ceri-etal-ieee-tkde-1989} should enable
%% declarative/flexible, yet efficient, specifications.

%% \subsection*{Plan}
%% The first activity in this project is to better understand the context
%% of application (e.g., nature of errors in the software under analysis)
%% as it will certainly drive important decisions in the solution design.
%% Validating our techniques (directly or not) on Google software is
%% ideal.

%% \section{Related Work}
%% \Fix{...general comments...}\Fix{...highlight Wei's BugRedux and Brum's Perfume.}

%% Because of the combinatorial blowup caused by the increasing number of
%% options in a large codebase, exhaustively testing all possible
%% configurations is prohibitive.

\section{Case Studies}

%% https://github.com/ibm-cloud-architecture/refarch-cloudnative-netflix
%% https://github.com/fernandoabcampos/spring-netflix-oss-microservices
%% https://github.com/jbossdemocentral/coolstore-microservice
%% https://github.com/robhinds/microservices
%% https://github.com/spencergibb/oscon2015
%% https://github.com/jduranmaster/MicroServices-Architecture-POC-Engine-SpringBoot-NetflixOSS
%% https://github.com/szokebarnabas/twitterminer

We plan to evaluate our approach in some of the following scenarios:

\begin{itemize}
  \setlength\itemsep{0.01em}
\item \textbf{Software-Defined Networking (SDN).} SDN is a network
  architecture that enables network administrators to programmatically
  control the network behavior through well-defined interfaces such as
  OpenFlow~\cite{open-networking}. Humans can make mistakes in an SDN
  as in any other configurable software.  For example, it is possible
  that ``one of the switches is sending packets to the wrong
  destination network''~\cite{scott-etal-nsdi2015}.
\item \textbf{Internet of Things (IoT).} IoT deployments are highly
  configurable and typically depend on services distributed on the
  network. This is the case for both cloud and non-cloud based IoT
  setups. Considering the scenario of a smart home, for example, the
  number of sensors and the configuration options on each sensor can
  vary (e.g., the max amount of smoke
  acceptable\footnote{~https://diyhacking.com/iot-smoke-alarm-arduino-esp8266-gas-sensor/}
  before signaling an alarm or sending a message to the apartment
  owner).  To note that the PI is involved in a Brazil-US cooperation
  project\footnote{~Funded by RNP, in Brazil, and NSF, in the
    US:~\url{https://www.nsf.gov/pubs/2017/nsf17024/nsf17024.jsp}}
  related to testing IoT infrastructures and this could create
  synergies that will help the project to succeed.

\item \textbf{Microservices.} Microservices is an increasingly-popular
  approach to organize applications (typically, web apps). It promotes
  the breakdown of code in small service units\Comment{ that
    communicate through lightweight protocols}. Consider, for example,
  the scenario where a monolithic application is refactored to use
  microservices. Refactorings can be buggy and the new channels
  created for communication (among microservices) can be vulnerable to
  attacks. 
  %http://mp.binaervarianz.de/pldi2017.pdf
%%  \item \textbf{Collaborative Apps}
\end{itemize}

%% \Comment{We consider using Open Source
%%     Software (OSS) that uses popular frameworks (e.g., Spring
%%     Cloud~\cite{spring-cloud}).}
%% to enable continuous delivery and deployment of
%%   applications.  Microservices promote

We are also eager to evaluate the techniques we develop in scenarios
within Google

\section{Data Policy}

The results produced with this research will be made available to the
public and to the research community.  All tools and data sets
developed will be available online, and the software will be released
under an open source license.

\section{Budget}

The project will support one PhD student for one year.  The total
budget for this period is 25,800 USD.

\begin{itemize}
  \setlength\itemsep{0.05em}  
\item Student salaries: 22,800 (=1,900*12)
\item Conference travel: 3,000
\end{itemize}

%% \begin{thebibliography}{99}
%% \bibitem{gonzalez2012} Jonay I. Gonz\'{a}lez Hern\'{a}ndez, 
%% Pilar Ruiz-Lapuente,	
%% Hugo M. Tabernero,	
%% David Montes,	
%% Ramon Canal,	
%% Javier M\'{e}ndez	
%% and Luigi R. Bedin,
%% {No surviving evolved companions of the progenitor of SN1006},
%% Nature, {\bf 489}, 533-536 (2012).
%% \end{thebibliography}

%\scriptsize
\footnotesize
\bibliographystyle{plain}
\bibliography{tmp}

\end{document}

%%  LocalWords:  d'Amorim Universidade de Pernambuco UFPE Centro CIn
%%  LocalWords:  atica Jornalista Fernandes Cidade Universit Sai GCC
%%  LocalWords:  Zhang Configurability Groupon combinatorial codebase
%%  LocalWords:  tmp misconfigurations SFL dataflow Datalog BugRedux
%%  LocalWords:  Brum's misconfiguration Daikon IoT nondeterministic
%%  LocalWords:  posteriori metadata MoDist postmorten virtualization
%%  LocalWords:  pre USD startup ZooKeeper's Config SDN SDNs OpenFlow
%%  LocalWords:  programmatically Microservices Refactoring OSS Jin
%%  LocalWords:  reproducibility RNP refactored microservices
%%  LocalWords:  Refactorings

### 2018-05-08 docs/google-research-awards-latam/main.tex
organizing template

@@
 
-%\title{Debugging I/O Anomalies in Distributed Configurable Systems}
-\title{\LARGE{}Testing for Configuration Errors in Distributed Systems}
+\title{Finding Bugs in JavaScript Engines with Differential Testing}
 \author{}
@@
   \centering%% Centro de Inform\'atica - CIn \\
-  \begin{tabular*}{.85\linewidth}{@{\extracolsep{\fill}}ll}
-    PI: Marcelo d'Amorim (\url{damorim@cin.ufpe.br}) & Universidade Federal de Pernambuco \\
-    Phone: +55 (81) 98800-2010 [mobile]  & Av. Jornalista Anibal Fernandes, S/N \\
-    \phantom{x}\hspace{7ex}+55 (81) 2126-8430, ext. 4379 [work] & Cidade Universit\'aria, PE, Brazil, 50.740-560\\
-    \multicolumn{2}{l}{\noindent\textbf{Contact}: Wei Jin
-      (\url{superbobo@google.com})~~--~~\textbf{Sponsor}: Sai Zhang (\url{saizhang@google.com})}\\
+  \begin{tabular*}{.85\linewidth}{l}
+
+    Marcelo d'Amorim and Igor Sim\~oes (M.Sc. student)\\
+
+    Postal Address: Av. Jornalista Anibal Fernandes, S/N. Cidade
+    Universit\'aria, PE, Brazil, 50.740-560 \\
+
+    Email addresses: \{damorim, isol2\}@cin.ufpe.br\\
+
+    Phones: +55 (81) 2126-8430,
+    ext. 4379 [work], +55 (81) 98800-2010 [mobile]\\
+
+    Affiliation: Federal University of Pernambuco, Department of
+    Computer Science.\\
+
+    Contacts at Google:~\Fix{...}
+
   \end{tabular*}
@@
 \begin{abstract}
-This proposal focuses on the important problem of testing for
-configuration errors in distributed systems. The goal is to increase
-system's reliability by preventing these errors to escape to
-production.
-%% The input of our approach is a configurable distributed
-%% program and the output is a set of constraints denoting what
-%% configurations are likely valid for use.
+...
 \end{abstract}
-
-%% Diagnosing those errors
-%% can be very challenging.
-%% The overall goal is to improve developer's productivity in fixing
-%% those errors.  The input to our proposed approach is a set of
-%% distributed traces and the output is a likely explanation of failure
-%% that developers can relate.
 
@@
 
-\Comment{Configurability enables developers to adapt
-system's behavior to different circumstances.  by selecting or
-  adjusting options. These systems are \emph{prevalent}. The
-  Firefox web browser~\cite{firefox-web}, the Linux
-  kernel~\cite{linux-kernel-web}, the GCC compiler
-  infrastructure~\cite{gcc-web}, and the deals-recommendation web
-  service Groupon~\cite{groupon-web} are some well-known examples of
-  configurable systems. }
-
-Configurable systems are those that can be adapted from a set of input
-options, reflected in code in the form of variations. Configurable
-systems are
-prevalent\Comment{~\cite{yin-etal-sosp2011,weiss-etal-ase2017}} and,
-unfortunately, configuration-related errors are difficult to
-detect~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}
-and diagnose~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014}.
-Testing and debugging becomes even worse when the system being
-configured is a distributed system~\cite{matt-welsh-blog}. Detecting
-these errors with testing, before they escape, is therefore important
-as it is hard to troubleshoot error manifestations in complex
-production
-environments~\cite{jin-orso-icse2012}. Configuration-related errors in
-distributed systems are unfortunately \emph{not rare}. Some of these
-errors have been widely publicized in the media given the volume of
-users or data they affected~\cite{azure-error,facebook-error,
-  dns-misconfiguration}.
-
-%% Troubleshooting distributed systems is known to be
-%% challenging~\cite{BeschastnikhWBE2016}\Comment{ as reconstructing the
-%%   global state of the system after failure observations is difficult
-%%   or even impossible~\cite{mattern-virtual-time89}}.
-%% Distributed systems are prevalent. Examples of distributed
-%% applications include the Google Spanner distributed
-%% database~\cite{corbett-etal-osdi2012} and IoT
-%% deployments~\cite{android-things-one}.
-
-%% Configuration is an orthogonal aspect to distribution but one that
-%% makes testing and debugging even more
-%% challenging~\cite{matt-welsh-blog}.
+\Fix{...}
 
@@
 \fbox{
-  %  \begin{minipage}{18.75cm}
   \begin{minipage}{11.75cm}
     \centering
-    \textit{The goal of this project is to improve reliability in
-      distributed systems\\ by finding configuration errors during
-      testing.}
+    \textit{...}
   \end{minipage}
@@
 
-%% These errors emerge from the inability of developers to anticipate the
-%% impact of local changes in dependent
-%% features~\cite{ribeiro-etal-icse2014}.
-%% Configuration errors are even
-%% more problematic when they manifest in distributed
-%% systems.
-%% Fighting configuration errors
-%% is also
-%% challenging~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,kim-etal-fse2013,ribeiro-etal-icse2014,behrang-etal-fse2015}.
+\vspace{1ex} \textbf{Related Work.}~\Fix{...}~\cite{maddox-2015-acmqueue}
 
-%% Preventing developers from
-%% making these
-%% errors~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,ribeiro-etal-icse2014,behrang-etal-fse2015},
-%% testing for these errors~\cite{cohen-etal-icse2003,cohen:issta07,cohen-shmuelur-icse2010,emine-etal-issta2011,medeiros-etal-icse2016}
-%% and diagnosing those
-%% errors~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014} are
-%% challenging activities.
-%% At Google, configuration errors are also a
-%% problem.
-%% Understanding these errors in complex distributed system is an
-%% essential time-consuming activitiy~\cite{matt-welsh-blog}.
+\section{Design}
 
-%\section{Related Work}
+...
 
-\vspace{1ex} \textbf{Related Work.}~Literature on distributed
-debugging is vast~\cite{BeschastnikhWBE2016}. Record and replay
-solutions, such as Friday~\cite{geels-usenix2007} and
-D3S~\cite{d3s-debugging-deployed-distributed-systems}, capture
-nondeterministic events during execution to replay them a posteriori.
-Tracing solutions~\cite{sambasian-etal-techreport2014}, such as Pivot
-Tracing~\cite{mace-etal-usenix2016}, instrument the application to
-forward tracing metadata to a distributed database for offline
-analysis. In principle, these solutions could be adapted to track
-configuration data but they are either heavyweight or intrusive
-(\ie{}, they require modification in software).  These issues limit
-the applicability of Record and Replay and Tracing in practice. Log
-Analysis does not suffer from these limitations as it mines anomalies
-from the logs that the system already produces~\cite{xu-etal-slam10}.
-However, Log Analysis needs to cope with the potential for missing
-relevant data and also to handle massive amounts of data.
-%%
-Considering the configuration dimension, testing and debugging for
-distributed systems has not been studied in
-depth~\cite{matt-welsh-blog}, in contrast to what has been observed in
-non-distributed
-systems~\cite{yin-etal-sosp2011,zhang-ernst-icse2013,zhang-ernst-icse2014,behrang-etal-fse2015,weiss-etal-ase2017}.
-Most testing in distributed systems is done manually and after the
-fact (\ie{} after failures are observed) to augment regression test
-suites~\cite{beschastnikh-etal-icse2014}. Model checking distributed
-systems (,which is essentially systematic testing) has been
-proposed~\cite{killian-etal-nsdi07,yang-etal-nsdi09} but these
-existing approaches do not take configurations into account.
+\vspace{1ex}\noindent\textbf{Input/Output.}~...
 
-%% \section{Goal}
-%% Our general goal is to improve system's reliability\Comment{ in distributed
-%%   systems}.  Our specific goal is to find configuration errors in
-%% distributed systems.
+\section{Current Results}
 
-%% They are hard to diagnose, especially in distributed systems.
-%% Furthermore, these errors gain importance when they relate to data
-%% from large organizations or a large number of users.
-%% Defects that escape to production still need to be handled and,
-%% certainly, these are the cases that require more immediate
-%% diagnosis.
-
-%% ``In-production'' errors are inevitable; they originate from the
-%% inherent inability of ``in-house'' testing to find all possible
-%% bugs~\cite{jin-orso-icse2012}.  These errors are pressing given the
-%% imminent impact on users.
-
-%% We refer to this problem, prevalent in configuration error diagnosis,
-%% as (configuration) error classification.
-
-%% A common problem in
-%% this context is to decide whether a failure was manifested because of
-%% a misconfiguration, because of invalid inputs\Comment{Undocumented
-%%   preconditions in code can delay observation of failures.}, or
-%% because of software
-%% bugs~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014,sabrina-etal-splc15}.
-
-\section{Approach\Comment{Solution Design (Error Classification from
-    Distributed Traces)}}
-
-We propose an approach that uses automated test generation to find
-configuration errors in distributed systems.  Our approach exercises
-the system observing anomalies in behavior due to configuration
-changes. Testing configurable software is a topic on which the group
-of the PI has focused in the recent
-past~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}.
-Our approach is similar in spirit to MoDist~\cite{yang-etal-nsdi09}, a
-black-box model checker that runs the system modifying certain aspects
-during execution such as processor speed and message sequencing, but
-it takes configuration options into account.
-
-\vspace{1ex}\noindent\textbf{Input/Output.}~The input of our technique
-is a configurable distributed system and the output is one of more
-failing tests and error reports.
-
-%% The input to our
-%% problem is a set of distributed traces (\eg{}
-%% using Dapper~\cite{dapper-google-tr2010}, Pivot tracing~\cite{mace-etal-usenix2016}), which collectively
-%% indicate a failure manifestation.  The output is a high-level report
-%% explaining the potential cause of failure.  For example, ``service Y
-
-\vspace{1ex}\noindent\textbf{Requirements.}~The technique should be
-simple to use and highly automated. It should produce high-level
-reports that enable developers to promptly understand and fix the
-problems identified. It should run efficiently.
-
-%%   It should
-%% leverage available data\Comment{~--~produced with widely-used
-%%   tools~--~} as opposed to relying on additional data that could be
-%% produced with new tools.
-
-%% \begin{itemize}
-%%    \setlength\itemsep{0.01em}    
-%% \end{itemize}
-
-%% As for (1), large distributed systems often provide monitoring
-%% solutions to assist with bug triage.  This work will use the
-%% distributed traces produced by Dapper~\cite{dapper-google-tr2010}, the
-%% distributed tracing infrastructure at Google.
-
-\newcommand{\taskvirtualization}{1}
-\newcommand{\taskteststrategies}{2}
-%\newcommand{\idinteractions}{3}
-\newcommand{\idminimization}{3}
-
-\vspace{1ex}\noindent\textbf{Tasks}.~\taskvirtualization{}) Define
-containerization strategy. \taskteststrategies{}) Define test
-strategy. \idminimization{}) Minimize test sequences.
-
-%% \idinteractions{}) Identify interactions between configured
-%% services.
-
-%% \begin{enumerate}
-%%   \setlength\itemsep{0.01em}
-%% \item\label{task-virtualization} Define containerization strategy.
-%% \item\label{task-test-strategies} Define test strategy.
-%% \item\label{id-interactions} Identify interactions between configured services.
-%% \item\label{id-minimization} Minimize test sequences.
-%% %\item Create benchmark of configuration errors in distributed systems
-%% \end{enumerate}
-
-%\vspace{1ex}\noindent\textbf{Approach}.
-
-\vspace{1ex} Considering task~\taskvirtualization{}, it is important
-to start a distributed system quickly and to run the system in an
-isolated environment. We plan to use Docker images~\cite{docker} to
-jump start the individual nodes of a distributed system. Considering
-task~\taskteststrategies{}, our approach is to use lighter weight test
-methods first and then assess effectiveness and cost of heavier weight
-testing strategies.  More specifically, initially, we plan to use
-existing test cases~\cite{maddox-2015-acmqueue} and select
-configurations to run those tests using black-box techniques, such as
-Combinatorial Interaction Testing
-(CIT)~\cite{nie-leung-acm-surveys2011}.  It is worth noting that
-centralized configuration servers such as
-ZooKeeper's~\cite{apache-zookeeper} and Spring Cloud
-Config~\cite{spring-cloud-config} are becoming popular to manage
-configurations in distributed systems and should facilitate this task.
-We also plan to explore gray-box techniques for selecting
-configurations~---~we will investigate the effectiveness of mining
-network interactions to decide what configurations to test
-next. Existing log analysis tools can help on
-that~\cite{mace-etal-usenix2016}. For example, our analysis may
-discover that a datum in a message triggers a different decision in a
-node, as observed from execution logs, and that that datum is related
-to a configuration option. We conjecture that selecting configurations
-that triggers different interactions increases the ability of testing
-to find faults. Finally, automated test generation can create
-arbitrarily long test sequences which hinders reproducibility and
-fault diagnosis.  Task~\idminimization{} is concerned with the
-minimization of fault-revealing tests to facilitate debugging.
-
-%% messages on the network, similarly to
-%% MoDist~\cite{yang-etal-nsdi09}\Comment{ and
-%%   Basset~\cite{lauterburg-etal-fse2010},}, but also by modifying
-%% configurations.
-
-We will build tools that implement and support our approach.  The
-output of our approach is a failing test, which could reveal a bug or
-a misconfiguration. In case the developer finds out that the failure
-corresponds to a bug, the code needs to be fixed.  In case of
-misconfigurations, our approach could be used to prevent errors
-provided that the developer adds checks to (in)validate certain
-configurations from being triggered.  Alternatively, the approach
-could be used to diagnose errors as logs reporting error
-manifestations could be saved and then used for comparison with
-production runs.
-
-%% Our first course of action to
-%% diagnosing configuration errors is to search for unexpected
-%% \emph{feature interactions}~\cite{pamela-zave-feature-interaction}.  A
-%% feature interaction happens, for example, when a service reads from
-%% the state that another service writes. The hypothesis is that the
-%% failure was caused by an interaction across distributed services
-%% manifested through a configuration that has not been extensively
-%% tested, resulting in a failure.\Comment{ Consequently, the defect was
-%%   enabled in production only at the point in time the error was
-%%   manifested.}  As it is challenging to detect those interactions
-%% without sacrificing system's performance (\eg{}, adding monitoring probes), we plan to use existing
-%% execution logs to estimate them. To fix the problem, a developer needs
-%% to either fix a bug in code related to that configuration or prevent
-%% the use of that configuration, as it could be illegal.  In case no
-%% discrepancy has been found in the patterns of configuration
-%% interaction, our approach would look for anomalies in the use of input
-%% data involving those configurations. Potential activities associated
-%% to this project include:
-
-%% \begin{itemize}
-%%   \setlength\itemsep{0.01em}  
-%%   \item Identify interaction between configured services.  This task
-%%     is responsible to find what services interact
-%%     and through which configurations they interact.  Existing log
-%%     analysis tools can help assist this
-%%     activity~\cite{beschastnikh-etal-icse2014,BeschastnikhWBE2016,shiviz-web}.
-%%   \item Investigate techniques to precisely and efficiently identify
-%%     anomalies in usage of input data, modulo service interaction and
-%%     their configurations.  Potential solutions include the use of
-%%     invariant detectors (e.g.,
-%%     Daikon~\cite{daikon-2016,BeschastnikhWBE2016}) and anomaly
-%%     detectors based on regression and neural network
-%%     models~\cite{Alpaydin:2010:IML:1734076}, for instance.
-%%   \item Create a benchmark of distributed systems with configuration
-%%     errors.\Fix{elaborate...}
-%%   \item 
-%% \end{itemize}
-
-%% This proposal addresses the problem of debugging large-scale
-%% configurable distributed systems.  The hypothesis is that system's
-%% configuration errors are often manifested through anomalies in I/O
-%% usage.
-
-%\subsection*{Details}
-
-%% For the sake of presentation, we use the term ``test case'' to refer
-%% to a scenario of execution that manifests a problem.  A test case can
-%% be materialized through an executable test artifact (in-house) or
-%% through an execution log (in-production).  Handling in-house and
-%% in-production bugs are in the scope of this project.
-
-%% Our debugging approach is summarized as follows: (1) Augment test
-%% cases with differential test oracles, (2) Explore configurations from
-%% the test, and (3) Look for correlations between configuration options
-%% and failures.  We detail below each of these parts.
-
-%% \textbf{Oracles (1).} We assume that an important class of errors in
-%% distributed systems are due to
-%% misconfigurations~\cite{matt-welsh-blog}.  Furthermore, we conjecture
-%% that an important class of these errors manifest I/O anomalies (e.g.,
-%% excessive use of memory or time).  We plan to apply differential
-%% testing in this context to discover these problems.  More
-%% specifically, we want to detect anomalies in the profile of resource
-%% usage (memory/network) across multiple executions induced by a
-%% selection of configurations over a given test.
-
-%% \textbf{Configuration selection (2).} Testing is an essential part of
-%% the debugging process. Test case diversity is generally considered
-%% beneficial to identify root causes of
-%% failure~\cite{campos-etal-ase2016}.  Diversity of configurations, in
-%% particular, plays an important role in the context of this project.
-%% We plan to use existing configuration selection
-%% techniques~\cite{medeiros-etal-icse2016,kim-etal-fse2013,sabrina-etal-splc15,souto-damorim-jss-2016},
-%% including ours, to explore the space of configurations reachable from
-%% existing test cases.
-
-%% \textbf{Fault localization and explanation (3).} Statistical-based Fault
-%% Localization (SFL) is a lightweight method to identify suspicious
-%% components in a computational system from a set of passing and failing
-%% executions~\Fix{cite}.  We plan to apply SFL and look for abstractions
-%% of error explanation that can be given to users to help identify the
-%% culprit.
-
-%% It is important to note that if executable test cases can be
-%% obtained diagnosis can be performed at source-level.
-
-%% \subsection*{Debugging in production}
-
-%% In principle, the approach presented above could be used to identify
-%% inconsistencies in existing integration tests, by exploring more
-%% rigorously reachable configurations from tests.  However, defects that
-%% escape to production still need to be handled and, certainly, these
-%% are the cases that require more immediate diagnosis.  To this end, one
-%% important challenge is to reconstruct, from production logs, the steps
-%% that approximately characterize the original error-manifesting
-%% execution.  Two alternatives for that will be investigated: (1) to
-%% reconstruct executable integration tests that partially reflect the
-%% observed behavior in logs.  This assumes that an infrastructure for
-%% isolated re-execution of tests exists, which may not be realistic. (2)
-%% to elaborate abstract behavior models for resource consumption which
-%% \emph{are aware of configuration options used}.  Each approach is
-%% challenging.
-
-%% \Fix{...talk about surrogate regression + neural network models...}
-
-%% Ideally, we would like even to generate new execution scenarios
-%% from observations...
-
-%% \subsection*{Future}
-%% One potentially promising direction to expand this project is to use
-%% historical data (both short and long-term) to prune the search space.
-%% Lightweight change impact analysis can help finding hot spots for
-%% analysis and code stability analysis can help finding cold spots.
-%% Other directions for further investigation include plugin validation
-%% for user-configurable applications (such as web browsers) and lifting
-%% dataflow analysis for configuration awareness, a problem that has been
-%% recently investigated but is restricted to simple
-%% analysis~\cite{spllift}.  Recent advances of Datalog
-%% solvers~\cite{ceri-etal-ieee-tkde-1989} should enable
-%% declarative/flexible, yet efficient, specifications.
-
-%% \subsection*{Plan}
-%% The first activity in this project is to better understand the context
-%% of application (e.g., nature of errors in the software under analysis)
-%% as it will certainly drive important decisions in the solution design.
-%% Validating our techniques (directly or not) on Google software is
-%% ideal.
-
-%% \section{Related Work}
-%% \Fix{...general comments...}\Fix{...highlight Wei's BugRedux and Brum's Perfume.}
-
-%% Because of the combinatorial blowup caused by the increasing number of
-%% options in a large codebase, exhaustively testing all possible
-%% configurations is prohibitive.
-
-\section{Case Studies}
-
-%% https://github.com/ibm-cloud-architecture/refarch-cloudnative-netflix
-%% https://github.com/fernandoabcampos/spring-netflix-oss-microservices
-%% https://github.com/jbossdemocentral/coolstore-microservice
-%% https://github.com/robhinds/microservices
-%% https://github.com/spencergibb/oscon2015
-%% https://github.com/jduranmaster/MicroServices-Architecture-POC-Engine-SpringBoot-NetflixOSS
-%% https://github.com/szokebarnabas/twitterminer
-
-We plan to evaluate our approach in some of the following scenarios:
-
-\begin{itemize}
-  \setlength\itemsep{0.01em}
-\item \textbf{Software-Defined Networking (SDN).} SDN is a network
-  architecture that enables network administrators to programmatically
-  control the network behavior through well-defined interfaces such as
-  OpenFlow~\cite{open-networking}. Humans can make mistakes in an SDN
-  as in any other configurable software.  For example, it is possible
-  that ``one of the switches is sending packets to the wrong
-  destination network''~\cite{scott-etal-nsdi2015}.
-\item \textbf{Internet of Things (IoT).} IoT deployments are highly
-  configurable and typically depend on services distributed on the
-  network. This is the case for both cloud and non-cloud based IoT
-  setups. Considering the scenario of a smart home, for example, the
-  number of sensors and the configuration options on each sensor can
-  vary (e.g., the max amount of smoke
-  acceptable\footnote{~https://diyhacking.com/iot-smoke-alarm-arduino-esp8266-gas-sensor/}
-  before signaling an alarm or sending a message to the apartment
-  owner).  To note that the PI is involved in a Brazil-US cooperation
-  project\footnote{~Funded by RNP, in Brazil, and NSF, in the
-    US:~\url{https://www.nsf.gov/pubs/2017/nsf17024/nsf17024.jsp}}
-  related to testing IoT infrastructures and this could create
-  synergies that will help the project to succeed.
-
-\item \textbf{Microservices.} Microservices is an increasingly-popular
-  approach to organize applications (typically, web apps). It promotes
-  the breakdown of code in small service units\Comment{ that
-    communicate through lightweight protocols}. Consider, for example,
-  the scenario where a monolithic application is refactored to use
-  microservices. Refactorings can be buggy and the new channels
-  created for communication (among microservices) can be vulnerable to
-  attacks. 
-  %http://mp.binaervarianz.de/pldi2017.pdf
-%%  \item \textbf{Collaborative Apps}
-\end{itemize}
-
-%% \Comment{We consider using Open Source
-%%     Software (OSS) that uses popular frameworks (e.g., Spring
-%%     Cloud~\cite{spring-cloud}).}
-%% to enable continuous delivery and deployment of
-%%   applications.  Microservices promote
-
-We are also eager to evaluate the techniques we develop in scenarios
-within Google
+\Fix{list/describe/explain some of the bugs we found here}
 
@@
 
-\section{Budget}
-
-The project will support one PhD student for one year.  The total
-budget for this period is 25,800 USD.
-
-\begin{itemize}
-  \setlength\itemsep{0.05em}  
-\item Student salaries: 22,800 (=1,900*12)
-\item Conference travel: 3,000
-\end{itemize}
-
-%% \begin{thebibliography}{99}
-%% \bibitem{gonzalez2012} Jonay I. Gonz\'{a}lez Hern\'{a}ndez, 
-%% Pilar Ruiz-Lapuente,	
-%% Hugo M. Tabernero,	
-%% David Montes,	
-%% Ramon Canal,	
-%% Javier M\'{e}ndez	
-%% and Luigi R. Bedin,
-%% {No surviving evolved companions of the progenitor of SN1006},
-%% Nature, {\bf 489}, 533-536 (2012).
-%% \end{thebibliography}
-
-%\scriptsize
 \footnotesize
@@
 \end{document}
-
-%%  LocalWords:  d'Amorim Universidade de Pernambuco UFPE Centro CIn
-%%  LocalWords:  atica Jornalista Fernandes Cidade Universit Sai GCC
-%%  LocalWords:  Zhang Configurability Groupon combinatorial codebase
-%%  LocalWords:  tmp misconfigurations SFL dataflow Datalog BugRedux
-%%  LocalWords:  Brum's misconfiguration Daikon IoT nondeterministic
-%%  LocalWords:  posteriori metadata MoDist postmorten virtualization
-%%  LocalWords:  pre USD startup ZooKeeper's Config SDN SDNs OpenFlow
-%%  LocalWords:  programmatically Microservices Refactoring OSS Jin
-%%  LocalWords:  reproducibility RNP refactored microservices
-%%  LocalWords:  Refactorings

### 2018-05-08 docs/google-research-awards-latam/main.tex
updated related works (wip)

@@
 
-\vspace{1ex} \textbf{Related Work.}~\Fix{...}~\cite{maddox-2015-acmqueue}
+\vspace{1ex} \textbf{Related Work.}
+~According Maddox \cite{maddox-2015-acmqueue}, is very complex to testing 
+distributed system that have multiple components due lack of configurations, 
+data-flow between nodes and asynchronous behaviour. (wip)
+
+Fuzzing is a very common technique used in software engineering for
+generate code mutations from existing test sample to improve the black-box testing method.
+In Yang et al. \cite{yang-2011-finding}, it was designed the 
+CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
+based on C language to generate invalid entries and found bugs in several C compilers.
+Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
+that exposes the LangFuzz to generate entries based in code fragments 
+(language grammar, sample code, test suite) and the tool Mozilla 
+Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
+that implements a fuzzer based on JavaScript language to improve the 
+testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
+\Fix{...}
 

### 2018-05-09 docs/google-research-awards-latam/main.tex
pass on proposal

--- 2018-05-08 docs/google-research-awards-latam/main.tex
@@
 %% macros
-\newcommand{\splat}{SPLat}
 \newcommand{\ie}{i.e.}
@@
 \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
+\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
 \newcommand{\Comment}[1]{}
@@
 
-\section{Problem}
+\section{Problem Space}
 
-\Fix{...}
+JavaScript is one of the most popular programming languages of
+today~\cite{business-insider,stackify}. Although the languagre is used
+in several application domains, its niche is front-end and back-end
+web development\Comment{, supported several frameworks and runtimes
+  (\eg{}, Express.js and Node.js)}.
 
-\vspace{-1ex}
+Demands for new features occur in JavaScript as in other popular
+programming languages. Recently, the JavaScript specification went
+through a more severe change, called by the name ECMAScript6
+(ES6)~\cite{es6-features}. Compliance with the new standard is
+important for every engine implementation (\eg{}, Google's
+V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
+Chakra\Fix{cite}) because of
+portability~\cite{kangax}.
+
+%\vspace{-1ex}
 \begin{center}
@@
   \begin{minipage}{11.75cm}
-    \centering
-    \textit{...}
+    \centering \textit{The goal of this project is to find bugs in
+      implementations of JavaScript engines by leveraging the diversity
+      across implementations.}
   \end{minipage}
@@
 \end{center}
-\vspace{-1ex}
+%\vspace{-1ex}
 
-\vspace{1ex} \textbf{Related Work.}~\Fix{...}~\cite{maddox-2015-acmqueue}
+Changes in the language specification often demand sensible changes in
+implementations that can result in regressions. Several of these
+regression have been reported, some of which were reported by our team
+(confirmed by engine developers) using a prototype of our solution
+(see Section~\ref{sec:results}).
 
-\section{Design}
+\section{Design Space}
 
-...
+Fuzzing is a popular technique to generate new test inputs from
+existing inputs\Fix{cite} with the typical goal of finding
+crashes. Several fuzzing methods have been proposed in the past,
+varying with respect to how new inputs are generated (\eg{},
+mutation\Fix{cite}, grammar\Fix{cite}, and random\Fix{cite}) and
+whether or not coverage information is taken into account in the
+fuzzing process.\Fix{elaborate...}
+
+\section{Related Work}
+
+\Mar{rule of thumb: explain the
+  contribution/novelty, then results achieved, and then how it relates
+with our proposal.}
+\Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
+of C programs to generate invalid entries\Fix{the goal of a
+  fuzzer is to generate valid inputs/entries. this is strange} and
+find bugs in several C compilers\Fix{it is strange that you don't mention differential
+  testing, which is central in CSmith, and the use of LLVM and GCC as
+  oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
+  follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
+that exposes the LangFuzz to generate entries based in code fragments 
+(language grammar, sample code, test suite) and the tool Mozilla 
+Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
+that implements a fuzzer based on JavaScript language to improve the 
+testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
+\Fix{...}
 
@@
 \section{Current Results}
+\label{sec:results}
 

### 2018-05-09 docs/google-research-awards-latam/main.tex
another pass proposal

@@
 JavaScript is one of the most popular programming languages of
-today~\cite{business-insider,stackify}. Although the languagre is used
-in several application domains, its niche is front-end and back-end
-web development\Comment{, supported several frameworks and runtimes
-  (\eg{}, Express.js and Node.js)}.
+today~\cite{business-insider,stackify}. Its niche is front-end and
+back-end web development\Comment{, supported several frameworks and
+  runtimes (\eg{}, Express.js and Node.js)}, although the languagre
+has been used in other contexts.
 
-Demands for new features occur in JavaScript as in other popular
-programming languages. Recently, the JavaScript specification went
-through a more severe change, called by the name ECMAScript6
-(ES6)~\cite{es6-features}. Compliance with the new standard is
+Recently, the JavaScript specification went through a bigger change
+compared to prior releases\footnote{Called by the name of ECMAScript6
+  (ES6)~\cite{es6-features}}. This is natural as requests for new
+features are common in popular programming languages. Because of
+portability~\cite{kangax}, compliance with the new standard is
 important for every engine implementation (\eg{}, Google's
 V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
-Chakra\Fix{cite}) because of
-portability~\cite{kangax}.
+Chakra\Fix{cite}).
 
@@
     \centering \textit{The goal of this project is to find bugs in
-      implementations of JavaScript engines by leveraging the diversity
+      implementations of JavaScript engines by leveraging diversity
       across implementations.}
@@
 
-Changes in the language specification often demand sensible changes in
-implementations that can result in regressions. Several of these
-regression have been reported, some of which were reported by our team
-(confirmed by engine developers) using a prototype of our solution
-(see Section~\ref{sec:results}).
+As in any piece of software, changes in the specification often demand
+sensible changes in implementations that could lead to regressions. In
+fact, several of these regressions have been reported, some of which
+were reported by our team (confirmed by engine developers; see
+Section~\ref{sec:results}) using a prototype of our solution (see
+Section~\ref{sec:design}).
 
 \section{Design Space}
+\label{sec:design}
 
@@
 varying with respect to how new inputs are generated (\eg{},
-mutation\Fix{cite}, grammar\Fix{cite}, and random\Fix{cite}) and
-whether or not coverage information is taken into account in the
-fuzzing process.\Fix{elaborate...}
+mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
+random-based\Fix{cite}) and whether or not coverage information is
+taken into account in the fuzzing process.\Fix{elaborate...}
+
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
+  \label{fig:workflow}
+  \caption{Workflow of Infrastructure.}
+\end{figure}
 

### 2018-05-10 docs/google-research-awards-latam/main.tex
pass on proposal

@@
 
-JavaScript is one of the most popular programming languages of
+JavaScript (JS) is one of the most popular programming languages of
 today~\cite{business-insider,stackify}. Its niche is front-end and
 back-end web development\Comment{, supported several frameworks and
-  runtimes (\eg{}, Express.js and Node.js)}, although the languagre
-has been used in other contexts.
+  runtimes (\eg{}, Express.js and Node.js)}.
 
-Recently, the JavaScript specification went through a bigger change
-compared to prior releases\footnote{Called by the name of ECMAScript6
-  (ES6)~\cite{es6-features}}. This is natural as requests for new
-features are common in popular programming languages. Because of
-portability~\cite{kangax}, compliance with the new standard is
-important for every engine implementation (\eg{}, Google's
-V8\Fix{cite}, Mozilla's SpiderMonkey\Fix{cite}, and Microsoft's
-Chakra\Fix{cite}).
+Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
+SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
+follow the constant changes in the language
+specification~\cite{kangax}. In fact, recently, the JavaScript
+specification went through a bigger change compared to prior
+releases\footnote{Called by the name of ECMAScript6
+  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
+the specification often demand sensible changes in implementations
+that could lead to errors, including regressions. In fact, bugs in JS
+implementations are often reported by the general public, some of
+which were reported by our team.
+
+%% (confirmed by engine developers; see
+%% Section~\ref{sec:results}) using a prototype of our solution (see
+%% Section~\ref{sec:design}).
+
+The lack of executable specifications that could be used as oracles is
+an important obstacle for test generation--it prevents detection of
+errors which are not explicit, like a crash.  The novelty of our
+approach is the use of multiple engine implementations to assess input
+validity and output correctness. \emph{Differential testing}\Fix{cite}
+has been applied in a variety of contexts\Fix{cite cite}, but it has
+not been used to find functional bugs in JS engines.
 
@@
 
-As in any piece of software, changes in the specification often demand
-sensible changes in implementations that could lead to regressions. In
-fact, several of these regressions have been reported, some of which
-were reported by our team (confirmed by engine developers; see
-Section~\ref{sec:results}) using a prototype of our solution (see
-Section~\ref{sec:design}).
-
 \section{Design Space}
@@
 random-based\Fix{cite}) and whether or not coverage information is
-taken into account in the fuzzing process.\Fix{elaborate...}
+taken into account in the fuzzing process.
 

### 2018-05-11 docs/google-research-awards-latam/main.tex

@@
     Affiliation: Federal University of Pernambuco, Department of
-    Computer Science.\\
+    Computer Science\\
 
-    Contacts at Google:~\Fix{...}
+    Contact at Google:~Martin Barbella (mbarbella@google.com)
 
@@
 follow the constant changes in the language
-specification~\cite{kangax}. In fact, recently, the JavaScript
+specification~\cite{kangax}. Recently, the JavaScript
 specification went through a bigger change compared to prior

### 2018-05-11 docs/google-research-awards-latam/main.tex
another pass on proposal

@@
 \usepackage{tabularx}
+\usepackage{wrapfig}
 
@@
 
-JavaScript (JS) is one of the most popular programming languages of
-today~\cite{business-insider,stackify}. Its niche is front-end and
-back-end web development\Comment{, supported several frameworks and
-  runtimes (\eg{}, Express.js and Node.js)}.
+%% Its niche is front-end and
+%% back-end web development\Comment{, supported several frameworks and
+%%   runtimes (\eg{}, Express.js and Node.js)}.
 
-Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
-SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
-follow the constant changes in the language
-specification~\cite{kangax}. Recently, the JavaScript
-specification went through a bigger change compared to prior
-releases\footnote{Called by the name of ECMAScript6
-  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
-the specification often demand sensible changes in implementations
-that could lead to errors, including regressions. In fact, bugs in JS
-implementations are often reported by the general public, some of
-which were reported by our team.
-
+%% In fact, bugs in JS implementations are often reported by
+%% the general public, some of which were reported by our team.
 %% (confirmed by engine developers; see
@@
 
-The lack of executable specifications that could be used as oracles is
-an important obstacle for test generation--it prevents detection of
-errors which are not explicit, like a crash.  The novelty of our
-approach is the use of multiple engine implementations to assess input
-validity and output correctness. \emph{Differential testing}\Fix{cite}
-has been applied in a variety of contexts\Fix{cite cite}, but it has
-not been used to find functional bugs in JS engines.
+JavaScript (JS) is one of the most popular programming languages of
+today~\cite{business-insider,stackify} largely because of its
+widespread use on the web. As common in software, the JS specification
+changes regularly\footnote{Recently, the specification went through a
+  bigger change compared to prior releases, called by the name of
+  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
+demands~\cite{kangax} and these changes often entail sensible changes
+in engine implementations that could lead to errors, including
+regressions.  Test generation can help reduce the cost of testing, but
+the lack of executable specifications is an important obstacle for
+finding functional errors.
 
@@
 \fbox{
-  \begin{minipage}{11.75cm}
+  \begin{minipage}{13.5cm}
     \centering \textit{The goal of this project is to find bugs in
@@
 
+The novelty of our proposal is the use of multiple engine
+implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
+assess input validity and to check output
+correctness. \emph{Differential testing}\Fix{cite} has been applied in
+a variety of contexts\Fix{cite cite}, but it has not been used to find
+functional bugs in JS engines.
+
 \section{Design Space}
@@
 
+\begin{wrapfigure}[13]{r}[0pt]{0.45\textwidth}
+\vspace{-5ex}
+%\begin{figure}[htbp]
+  \centering
+  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
+  \label{fig:workflow}
+  \caption{Workflow of Infrastructure.}
+%\end{figure}
+\end{wrapfigure}
 Fuzzing is a popular technique to generate new test inputs from
@@
 random-based\Fix{cite}) and whether or not coverage information is
-taken into account in the fuzzing process.
-
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
-  \label{fig:workflow}
-  \caption{Workflow of Infrastructure.}
-\end{figure}
+taken into account in the fuzzing process. Figure~\ref{fig:workflow}
+shows a generic pipeline of a fuzzer. JS files are provided as seeded
+inputs to bootstrap the process. These files can originate from the
+test suites of the engine codebases or from the bug reports in their
+issue trackers. \Fix{elaborate}
 
@@
 
-\vspace{1ex}\noindent\textbf{Input/Output.}~...
-
 \section{Current Results}

### 2018-05-11 docs/google-research-awards-latam/main.tex

@@
 \usepackage{wrapfig}
+\usepackage{microtype}
+\usepackage{hyperref}
 
@@
 \newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
+\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
 \newcommand{\Comment}[1]{}
@@
 a variety of contexts\Fix{cite cite}, but it has not been used to find
-functional bugs in JS engines.
+functional bugs in JS engines \MAB{That's wrong - it has been used at
+  least two times: \cite{patra2016learning} and in jsfunfuzz (with a
+  smaller scope - most likely regressions)}
 
@@
 of C programs to generate invalid entries\Fix{the goal of a
-  fuzzer is to generate valid inputs/entries. this is strange} and
+   fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
+  goal is to generate valid programs without undefined behavior to
+  facilitate differential testing} and
 find bugs in several C compilers\Fix{it is strange that you don't mention differential
@@
 \Fix{...}
+
+\MAB{Unfortunately the low-hanging fruit for this project was already
+  picked \cite{patra2016learning}, so I believe you should focus on
+  taming implementation-specific behavior and/or the testing
+  infrastructure (i.e. how to organize all those fuzzers and make them
+  work together). You might also want to mention the possibility of
+  fuzzing
+  \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
+  directly: LLVM already has (some) support for targeting WebAssembly,
+  which means that we'll be able to run, in the near future, pretty
+  much every language with an LLVM-backed compiler in a browser.}
 

### 2018-05-11 docs/google-research-awards-latam/main.tex
gitignore update

@@
 \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
-\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
-\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
+\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
+\newcommand{\MAB}[1]{\textbf{[[Mateus:~}{\color{darkgreen} #1}\textbf{]]}}
 \newcommand{\Comment}[1]{}
@@
   ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
-demands~\cite{kangax} and these changes often entail sensible changes
-in engine implementations that could lead to errors, including
-regressions.  Test generation can help reduce the cost of testing, but
-the lack of executable specifications is an important obstacle for
-finding functional errors.
+demands of the community and these changes often entail sensible
+changes in engine implementations~\cite{kangax} that could lead to
+errors, including regressions.  Test generation can help reduce the
+cost of testing, but the lack of executable specifications is an
+important obstacle for finding functional errors.
 
@@
 implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
-assess input validity and to check output
-correctness. \emph{Differential testing}\Fix{cite} has been applied in
-a variety of contexts\Fix{cite cite}, but it has not been used to find
-functional bugs in JS engines \MAB{That's wrong - it has been used at
-  least two times: \cite{patra2016learning} and in jsfunfuzz (with a
-  smaller scope - most likely regressions)}
+assess input validity and to check output correctness. Differential
+testing\cite{McKeeman98differentialtesting} has been applied in a
+variety of
+contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
+but it has not been thoroughly explored to find functional bugs in JS
+engines. Patra and Pradel ran a small study, published in 2016 as
+a tech report~\cite{patra2016learning}, where they found
+discrepancies\Fix{confirm if they reported bugs}. The Mozilla
+jsfunfuzz\Fix{elaborate a bit}.\Mar{Mateus, check if this sounds
+  correct/fair to you and try to elaborate the jsfunfuzz part.}
+
+\Fix{finalize}
 
@@
 
-\begin{wrapfigure}[13]{r}[0pt]{0.45\textwidth}
+\begin{wrapfigure}[12]{r}[0pt]{0.45\textwidth}
 \vspace{-5ex}
@@
   \centering
-  \includegraphics[trim=0 350 200 0,clip,width=0.5\textwidth]{google-awards-workflow}
+  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
   \label{fig:workflow}
-  \caption{Workflow of Infrastructure.}
+  \caption{Fuzzing Infrastructure.}
 %\end{figure}
@@
 taken into account in the fuzzing process. Figure~\ref{fig:workflow}
-shows a generic pipeline of a fuzzer. JS files are provided as seeded
-inputs to bootstrap the process. These files can originate from the
-test suites of the engine codebases or from the bug reports in their
-issue trackers. \Fix{elaborate}
+shows a generic pipeline of a fuzzer, instantiated to our problem. In
+our case, JS files are provided as seeded inputs to bootstrap the
+process. These files can originate from the test suites of the engine
+codebases or from the bug reports in their issue trackers. The fuzzing
+infrastrucutre selects randomly one of the inputs to fuzz with a given
+tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing
+iteration produces a new file. For grammar-agnostic fuzzers, like
+Radamsa, the infrastructure needs to detect and discard syntactically
+invalid inputs. Semantically invalid inputs are detected dynamically
+or with linters. Once the input is found to be valid, the
+infrastructure invokes the oracle to check correctness. In case either
+all engines consider the test output consistent (\ie{}, all pass or
+all fail), the infrastructure discards the given input. Otherwise, it
+considers that input as potentially fault-revaling and
+interesting. Currently, we classify those alarms in two groups: HI and
+LO. The HI group includes those warnings that manifest execution
+errors spawned directly by the test (or its close neighborhood)
+whereas the LO group includes the rest of the warnings. We found
+empirically that \Fix{XX\%} of the warnings analyzed in the HI group
+were confirmed (see Section~\ref{sec:results})
 
-\section{Related Work}
-
-\Mar{rule of thumb: explain the
-  contribution/novelty, then results achieved, and then how it relates
-with our proposal.}
-\Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
-of C programs to generate invalid entries\Fix{the goal of a
-   fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
-  goal is to generate valid programs without undefined behavior to
-  facilitate differential testing} and
-find bugs in several C compilers\Fix{it is strange that you don't mention differential
-  testing, which is central in CSmith, and the use of LLVM and GCC as
-  oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
-  follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
-that exposes the LangFuzz to generate entries based in code fragments 
-(language grammar, sample code, test suite) and the tool Mozilla 
-Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
-that implements a fuzzer based on JavaScript language to improve the 
-testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
-\Fix{...}
+%% \section{Related Work}
+%% \Mar{rule of thumb: explain the
+%%   contribution/novelty, then results achieved, and then how it relates
+%% with our proposal.}
+%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
+%% of C programs to generate invalid entries\Fix{the goal of a
+%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
+%%   goal is to generate valid programs without undefined behavior to
+%%   facilitate differential testing} and
+%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
+%%   testing, which is central in CSmith, and the use of LLVM and GCC as
+%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
+%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
+%% that exposes the LangFuzz to generate entries based in code fragments 
+%% (language grammar, sample code, test suite) and the tool Mozilla 
+%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
+%% that implements a fuzzer based on JavaScript language to improve the 
+%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
+%% \Fix{...}
 

### 2018-05-11 docs/google-research-awards-latam/bug_table.tex
pass on results

\begin{table}[]
    \centering
    \caption{Bugs found and reported by \Fix{JSFuzz} team}
    \label{tab:bugs}
    \begin{tabular}{|c|c|c|c|}
    \hline
    Issue    & Engine                                                          & Status                                                                            & \multicolumn{1}{c|}{Url}                                                                                                                      \\ \hline
    Bug \#1  & Chakra                                                          & Fixed                                                                             & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}                                                                                           \\ \hline
    Bug \#2  & Chakra                                                          & Rejected                                                                          & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}                                                                              \\ \hline
    Bug \#3  & JavascriptCore                                                  & New                                                                               & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}                                                                                               \\ \hline
    Bug \#4  & JavascriptCore                                                  & New                                                                               & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}                                                                                               \\ \hline
    Bug \#5  & Chakra                                                          & Confirmed                                                                         & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}                                                                                           \\ \hline
    Bug \#6  & Chakra                                                          & Fixed                                                                             & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}                                                                                           \\ \hline
    Bug \#7  & Chakra                                                          & Confirmed                                                                         & \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}                                                                                           \\ \hline
    Bug \#8  & \begin{tabular}[c]{@{}c@{}}Chakra\\ JavascriptCore\end{tabular} & \begin{tabular}[c]{@{}c@{}}Confirmed (Chakra)\\ New (JavascriptCore)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}\\ \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}\end{tabular} \\ \hline
    Bug \#9  & JavascriptCore                                                  & New                                                                               & \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}                                                                                               \\ \hline
    Bug \#10 & \begin{tabular}[c]{@{}c@{}}Chakra\\ JavascriptCore\end{tabular} & \begin{tabular}[c]{@{}c@{}}Confirmed (Chakra)\\ New (JavascriptCore)\end{tabular} & \begin{tabular}[c]{@{}l@{}}\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}\\ \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}\end{tabular} \\ \hline
    Bug \#11 & JavascriptCore                                                  & New                                                                               & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}                                                                                               \\ \hline
    Bug \#12 & JavascriptCore                                                  & New                                                                               & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}                                                                                               \\ \hline
    Bug \#13 & Chakra                                                          & New                                                                               & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}                                                                      \\ \hline
    \end{tabular}
    \end{table}

### 2018-05-11 docs/google-research-awards-latam/bugs.tex
pass on results

\lstdefinelanguage{JavaScript}{
  keywords={break, case, catch, continue, debugger, default, delete, do, else, finally, for, function, if, in, instanceof, new, return, switch, this, throw, try, typeof, var, void, while, with},
  morecomment=[l]{//},
  morecomment=[s]{/*}{*/},
  morestring=[b]',
  morestring=[b]",
  sensitive=true
}

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{0.4}
        \centering
        \scriptsize
        \lstset{
            language=JavaScript,
            keywords={function, return},
            escapeinside={@}{@},
            numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
            basicstyle=\ttfamily\scriptsize, boxpos=c,
            numberstyle=\tiny,
            linewidth=6cm
        }
\begin{lstlisting} 
var a = {
    valueOf: function () {
-    return ""
+    return "\x00"
    }
}
assert(+a === 0)
\end{lstlisting}
        \normalsize
        \caption{
            \label{fig:bug-chakra}Fuzzed file shows an unexpected behaviour on ChakraCore
        }        
    \end{subfigure}
    \begin{subfigure}[b]{0.4}
\begin{lstlisting}[basicstyle=\ttfamily]
Priority: HIGH
Pattern:
-----JavaScriptCore
Error: Test failed
-----Chakra
-----SpiderMonkey
Error: Test failed
-----v8
Error: Test failed
\end{lstlisting}
\caption{\label{fig:pattern}\Fix{JSFuzz} output log}
\end{subfigure}
\end{figure}

### 2018-05-11 docs/google-research-awards-latam/main.tex
pass on results

--- 2018-05-11 docs/google-research-awards-latam/main.tex
@@
 \usepackage{hyperref}
-
+\usepackage{listings}
+\usepackage{subfigure}
 % ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
@@
 \definecolor{darkblue}{rgb}{0,0,0.5}
+\definecolor{darkaquamarine}{rgb}{0.2,0.4,0.3}
 %% macros
@@
 \newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
+\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
 \newcommand{\Comment}[1]{}
@@
 
-\Fix{list/describe/explain some of the bugs we found here}
+\Igor{
+  Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
+  that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
+  bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
+  At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
+  and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
+  due the engine does not follows the specification and dozens of others warnings already been
+  reported previously.
+
+  The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
+  that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
+  The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
+  \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
+  the unary plus converts the variable to an integer if it is a valid value
+  otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
+  see that we set automatically this testcase as high priority because it is a failure by assertion.
+  The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
+  It was necessary a manual inspection to check if it is a real bug, we observed that 
+  ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
+  the unary plus converts null to 0.
+}
+\Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
+\Igor{Coloco outro caso de bug reportado?}
+
+\input{bugs}
+\input{bug_table}
 

### 2018-05-11 docs/google-research-awards-latam/main.tex

--- 2018-05-11 docs/google-research-awards-latam/main.tex
@@
 \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
-\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
-\newcommand{\MAB}[1]{\textbf{[[Mateus:~}{\color{darkgreen} #1}\textbf{]]}}
+\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
+\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
+\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
 \newcommand{\Comment}[1]{}

### 2018-05-12 docs/google-research-awards-latam/main.tex
uploading draft sent to martin

--- 2018-05-11 docs/google-research-awards-latam/main.tex
@@
 \usepackage{cite}
+\usepackage{multirow}
 \usepackage{lipsum}
@@
 \begin{abstract}
-...
+  \Fix{...}
 \end{abstract}
@@
   bigger change compared to prior releases, called by the name of
-  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
+  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
 demands of the community and these changes often entail sensible
@@
 
-The novelty of our proposal is the use of multiple engine
-implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
-assess input validity and to check output correctness. Differential
-testing\cite{McKeeman98differentialtesting} has been applied in a
-variety of
+Differential testing\cite{McKeeman98differentialtesting} has been
+applied in a variety of
 contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
 but it has not been thoroughly explored to find functional bugs in JS
-engines. Patra and Pradel ran a small study, published in 2016 as
-a tech report~\cite{patra2016learning}, where they found
-discrepancies\Fix{confirm if they reported bugs}. The Mozilla
-jsfunfuzz\Fix{elaborate a bit}.\Mar{Mateus, check if this sounds
-  correct/fair to you and try to elaborate the jsfunfuzz part.}
-
-\Fix{finalize}
+engines. The closest work was done by Patra and
+Pradel~\cite{patra2016learning}, where they evaluated their proposed
+language-agnostic fuzzer to find cross-browser HTML+JS
+discrepancies. This project aims to provide an adaptable
+infrastructure for differential testing of runtime engines, such as
+the JS engine or WebAssembly's. The sensible parts of the
+infrastructure are the checks of input validity (as to reduce
+waste/cost) and output correctness (as to reduce false positives).
 
@@
 Fuzzing is a popular technique to generate new test inputs from
-existing inputs\Fix{cite} with the typical goal of finding
-crashes. Several fuzzing methods have been proposed in the past,
-varying with respect to how new inputs are generated (\eg{},
-mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
-random-based\Fix{cite}) and whether or not coverage information is
-taken into account in the fuzzing process. Figure~\ref{fig:workflow}
-shows a generic pipeline of a fuzzer, instantiated to our problem. In
-our case, JS files are provided as seeded inputs to bootstrap the
-process. These files can originate from the test suites of the engine
-codebases or from the bug reports in their issue trackers. The fuzzing
-infrastrucutre selects randomly one of the inputs to fuzz with a given
-tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing
-iteration produces a new file. For grammar-agnostic fuzzers, like
-Radamsa, the infrastructure needs to detect and discard syntactically
-invalid inputs. Semantically invalid inputs are detected dynamically
-or with linters. Once the input is found to be valid, the
-infrastructure invokes the oracle to check correctness. In case either
-all engines consider the test output consistent (\ie{}, all pass or
-all fail), the infrastructure discards the given input. Otherwise, it
-considers that input as potentially fault-revaling and
-interesting. Currently, we classify those alarms in two groups: HI and
-LO. The HI group includes those warnings that manifest execution
-errors spawned directly by the test (or its close neighborhood)
-whereas the LO group includes the rest of the warnings. We found
-empirically that \Fix{XX\%} of the warnings analyzed in the HI group
-were confirmed (see Section~\ref{sec:results})
+existing inputs~\cite{fuzz-testing-history} with the typical goal of
+finding crashes. Several fuzzing methods have been proposed in the
+past, varying with respect to how new inputs are generated (\eg{},
+coverage-based~\cite{afl,honggfuzz},
+grammar-based~\cite{grammarinator,jsfunfuzz}, and
+random-based~\cite{radamsa}) and whether or not coverage information
+is taken into account in the fuzzing
+process. Figure~\ref{fig:workflow} shows a generic pipeline of a
+fuzzer, instantiated to our problem. In our case, JS files are
+provided as seeded inputs to bootstrap the process. These files can
+originate from the test suites of the engine codebases or from the bug
+reports in their issue trackers. The fuzzing infrastructure selects
+randomly one of the inputs to fuzz with a given tool, say the
+black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
+produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
+infrastructure needs to detect and discard syntactically invalid
+inputs. Semantically invalid inputs are detected dynamically or with
+linters. Once the input is found to be valid, the infrastructure
+invokes the oracle to check correctness. In case either all engines
+consider the test output consistent (\ie{}, all pass or all fail), the
+infrastructure discards the given input. Otherwise, it considers that
+input as potentially fault-revealing and interesting. Currently, we
+classify those alarms in two groups: HI and LO. The HI group includes
+those warnings that manifest execution errors spawned directly by the
+test (or its close neighborhood) whereas the LO group includes the
+rest of the warnings. We found empirically that \Fix{XX\%} of the
+warnings analyzed in the HI group were confirmed (see
+Section~\ref{sec:results})
 
@@
 
-\MAB{Unfortunately the low-hanging fruit for this project was already
-  picked \cite{patra2016learning}, so I believe you should focus on
-  taming implementation-specific behavior and/or the testing
-  infrastructure (i.e. how to organize all those fuzzers and make them
-  work together). You might also want to mention the possibility of
-  fuzzing
-  \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
-  directly: LLVM already has (some) support for targeting WebAssembly,
-  which means that we'll be able to run, in the near future, pretty
-  much every language with an LLVM-backed compiler in a browser.}
-
 \section{Current Results}
@@
 
-\Fix{list/describe/explain some of the bugs we found here}
+\newcommand{\checkm}{Y}
+\newcommand{\crossmark}{N}
+
+\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
+  \vspace{-6ex}
+  \scriptsize
+  \centering
+  \caption{List of bug reports issued by our team from April 12 to May
+    10, 2018.}
+  \label{tab:bugs}
+  \begin{tabular}{cccccc}
+    \toprule
+    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
+    \midrule    
+    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
+    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
+    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
+    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
+    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
+    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
+    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
+    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
+    \\
+    \midrule
+    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
+                        & \checkm &                       &
+    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
+    \midrule    
+    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
+    \midrule    
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
+                        &                        &        &
+    JavascriptCore & New &
+    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
+    \\
+    \midrule    
+    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
+    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
+    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
+   \bottomrule     
+  \end{tabular}
+\end{wraptable}
+
+Although there are many features yet to implement in our
+infrastructure, the basic workflow described in
+Section~\ref{sec:design} is already functional. Table~\ref{tab:bugs}
+shows the list of bugs we reported on issue trackers of different
+engines in the period of a month. So far, six of the bugs we reported
+were confirmed, two of which were fixed. One bug report we
+submitted was rejected on the basis that the offending JS file
+manifested an expected incompatibility across engine
+implementations.
+
+Note from the table that, with the exception of one case, all bug
+reports still waiting for confirmation are associated with the
+JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
+showed that the triage process is very slow for that engine. As of
+now, we did not find any bug on SpiderMonkey and V8. Finally, it is
+worth noting that seven of the 13 JS files that manifested
+discrepancies were produced with fuzzing (column ``Fuzz''). This
+emphasizes the importance of continuously collecting test suites from
+multiple sources; today, we use test suites from six different open
+source engines, including a total of \Fix{38.9K} test files.
+
+%% \Igor{
+%%   Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
+%%   that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
+%%   bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
+%%   At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
+%%   and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
+%%   due the engine does not follows the specification and dozens of others warnings already been
+%%   reported previously.
+
+%%   The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
+%%   that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
+%%   The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
+%%   \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
+%%   the unary plus converts the variable to an integer if it is a valid value
+%%   otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
+%%   see that we set automatically this testcase as high priority because it is a failure by assertion.
+%%   The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
+%%   It was necessary a manual inspection to check if it is a real bug, we observed that 
+%%   ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
+%%   the unary plus converts null to 0.
+%% }
+%% \Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
+%% \Igor{Coloco outro caso de bug reportado?}
+
+%\input{bugs}
+%\input{bug_table}
+
+\section{Future Steps}
+
+The list below shows future tasks for this project.
+
+\begin{itemize}
+\item Integrate different fuzzers, including AFL~\cite{afl},
+  HonggFuzz~\cite{honggfuzz}, jsfunfuzz~\cite{jsfunfuzz}, and
+  Grammarinator~\cite{grammarinator}.
+
+\item Find balance between generational strategies (, which often
+  produce valid but simple inputs) and mutational strategies (, which
+  often produce complex but invalid inputs) for fuzzing.
+
+\item Explore different strategies to reduce the number of false
+  positives. For example, mining issue trackers for similar bug
+  reports.
+
+\item Use our infrastructure to find bugs on
+  WebAssembly~\cite{webassembly}, a new binary format already
+  supported by major browsers. 
+\end{itemize}
+
+%% \MAB{Unfortunately the low-hanging fruit for this project was already
+%%   picked \cite{patra2016learning}, so I believe you should focus on
+%%   taming implementation-specific behavior and/or the testing
+%%   infrastructure (i.e. how to organize all those fuzzers and make them
+%%   work together). You might also want to mention the possibility of
+%%   fuzzing
+%%   \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
+%%   directly: LLVM already has (some) support for targeting WebAssembly,
+%%   which means that we'll be able to run, in the near future, pretty
+%%   much every language with an LLVM-backed compiler in a browser.}
 
@@
 \end{document}
+
+%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
+%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
+%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL
+%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly

### 2018-05-12 docs/google-research-awards-latam/main.tex
adding example. Igor, *please* double-check what I wrote and fill the gaps (references left to add)

@@
 % \setlength{\bibsep}{0pt plus 0.3ex}
+\usepackage[margin=1cm]{caption}
 \usepackage{titlesec}
@@
 \usepackage{color}
+\usepackage{xcolor}
 \definecolor{darkred}{rgb}{0.5,0,0}
@@
 \newcommand{\Comment}[1]{}
+\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
 
@@
 changes in engine implementations~\cite{kangax} that could lead to
-errors, including regressions.  Test generation can help reduce the
+errors, including regressions. Automated test generation can help reduce the
 cost of testing, but the lack of executable specifications is an
-important obstacle for finding functional errors.
+important obstacle. In particular, it is an obstable to find functional errors.
 
@@
 
-\begin{wrapfigure}[12]{r}[0pt]{0.45\textwidth}
+\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
   \vspace{-5ex}
-%\begin{figure}[htbp]
   \centering
   \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
-  \label{fig:workflow}
-  \caption{Fuzzing Infrastructure.}
-%\end{figure}
+  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
+  \vspace{-5ex}  
 \end{wrapfigure}
@@
 process. Figure~\ref{fig:workflow} shows a generic pipeline of a
-fuzzer, instantiated to our problem. In our case, JS files are
+fuzzer, instantiated to our problem. Arrows indicate data flow; lines
+with no arrow denote encapsulation. In our case, JS files are
 provided as seeded inputs to bootstrap the process. These files can
@@
 linters. Once the input is found to be valid, the infrastructure
-invokes the oracle to check correctness. In case either all engines
+invokes the oracle to check correctness. In case all engines
 consider the test output consistent (\ie{}, all pass or all fail), the
-infrastructure discards the given input. Otherwise, it considers that
+infrastructure discards the corresponding input. Otherwise, it considers that
 input as potentially fault-revealing and interesting. Currently, we
-classify those alarms in two groups: HI and LO. The HI group includes
+classify alarms in two groups: HI and LO. The HI group includes
 those warnings that manifest execution errors spawned directly by the
@@
 
+Although there are many features yet to implement in our
+infrastructure, the basic workflow described in
+Section~\ref{sec:design} is functional. This section shows preliminary
+results providing some evidence that finding bugs in runtime engines is
+promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
+issue trackers of different engines in the period of a month. For
+example, bug \# 6 was manifested by the JS code \CodeIn{var a =
+  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
+  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
+  version of the fuzzed code.}. In the original version of this code the \CodeIn{valueOf} function returned
+the empty string, whose integer representation according to the spec
+should be zero\Fix{check part of spec to link}. The modified
+code returns a string representation of an invalid hexadecimal
+value. The engines should not be able to evaluate that string at
+the assertion expression\Fix{explain why}. MS Chakra, however, is able to parse it
+returning a null object. In addition, the test passes as it converts
+null to zero.
+
 \newcommand{\checkm}{Y}
 \newcommand{\crossmark}{N}
-
 \begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
-  \vspace{-6ex}
+  \vspace{-4ex}
   \scriptsize
@@
 \end{wraptable}
-
-Although there are many features yet to implement in our
-infrastructure, the basic workflow described in
-Section~\ref{sec:design} is already functional. Table~\ref{tab:bugs}
-shows the list of bugs we reported on issue trackers of different
-engines in the period of a month. So far, six of the bugs we reported
+So far, six of the bugs we reported
 were confirmed, two of which were fixed. One bug report we
@@
 implementations.
-
 Note from the table that, with the exception of one case, all bug
@@
 \item Explore different strategies to reduce the number of false
-  positives. For example, mining issue trackers for similar bug
-  reports.
+  positives as to facilitate the inspection process. For example,
+  mining issue trackers for similar bug reports is a candidate alternative.
 
@@
   WebAssembly~\cite{webassembly}, a new binary format already
-  supported by major browsers. 
+  supported by major browsers. In principle, our infrastructure is
+  agnostic to the runtime engine used. We are eager to explore other
+  sources of bugs, especially in very new engines.
+
 \end{itemize}

### 2018-05-13 docs/google-research-awards-latam/main.tex
polishing + pass on abstract

@@
 \begin{abstract}
-  \Fix{...}
+JavaScript (JS) is a fundamental programming language for the
+web. Finding bugs in JavaScript engines is an important
+problem. Differential testing of JS engines is a promising approach to
+that end. This proposal describes our testing infrastructure, current
+results, and some upcoming features to improve the bug-finding
+process.
 \end{abstract}
@@
 applied in a variety of
-contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
+contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
+to mitigate with the lack of oracles problem,
 but it has not been thoroughly explored to find functional bugs in JS
@@
 process. Figure~\ref{fig:workflow} shows a generic pipeline of a
-fuzzer, instantiated to our problem. Arrows indicate data flow; lines
+fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
 with no arrow denote encapsulation. In our case, JS files are
@@
 produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
-infrastructure needs to detect and discard syntactically invalid
-inputs. Semantically invalid inputs are detected dynamically or with
-linters. Once the input is found to be valid, the infrastructure
+infrastructure can discard syntactically invalid
+inputs using an external parser for the input language; semantically
+invalid inputs can be prevented with with linters. Once the input is
+found to be likely valid, the infrastructure
 invokes the oracle to check correctness. In case all engines
@@
 rest of the warnings. We found empirically that \Fix{XX\%} of the
-warnings analyzed in the HI group were confirmed (see
-Section~\ref{sec:results})
+warnings analyzed in the HI group were confirmed.
 
@@
 
-Although there are many features yet to implement in our
-infrastructure, the basic workflow described in
-Section~\ref{sec:design} is functional. This section shows preliminary
-results providing some evidence that finding bugs in runtime engines is
+%% Although there are many features yet to implement in our
+%% infrastructure,
+
+The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
+results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
 promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
@@
   === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
-  version of the fuzzed code.}. In the original version of this code the \CodeIn{valueOf} function returned
-the empty string, whose integer representation according to the spec
-should be zero\Fix{check part of spec to link}. The modified
+  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
+the empty string, whose integer representation, according to the spec,
+should be zero\Fix{igor, please look for the part of spec and add link}. The modified
 code returns a string representation of an invalid hexadecimal
-value. The engines should not be able to evaluate that string at
-the assertion expression\Fix{explain why}. MS Chakra, however, is able to parse it
-returning a null object. In addition, the test passes as it converts
-null to zero.
-
+value\Fix{igor, how do we know this is invalid?}. As such, the engines
+are not expected to evaluate that string at the assertion expression;
+hence test execution is expected to fail. Chakra,
+however, is able to parse the string as a number. It returns a null
+object, which is then converted to zero, making the test to pass.
 \newcommand{\checkm}{Y}
 \newcommand{\crossmark}{N}
-\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
-  \vspace{-4ex}
+\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
+  \vspace{-2ex}
   \scriptsize
@@
 \end{wraptable}
+
 So far, six of the bugs we reported
@@
 now, we did not find any bug on SpiderMonkey and V8. Finally, it is
-worth noting that seven of the 13 JS files that manifested
-discrepancies were produced with fuzzing (column ``Fuzz''). This
-emphasizes the importance of continuously collecting test suites from
+worth noting that six of the 13 JS files that manifested
+discrepancies were \emph{not} produced with fuzzing (column
+``Fuzz''). These are test files from suites of different engines. This
+observation emphasizes the importance of continuously collecting test suites from
 multiple sources; today, we use test suites from six different open

### 2018-05-14 docs/google-research-awards-latam/main.tex
updated related works

--- 2018-05-12 docs/google-research-awards-latam/main.tex
@@
 \usepackage{cite}
-\usepackage{multirow}
 \usepackage{lipsum}
@@
 \begin{abstract}
-  \Fix{...}
+...
 \end{abstract}
@@
   bigger change compared to prior releases, called by the name of
-  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
+  ECMAScript6 (ES6)~\cite{es6-features}} to accomodate pressing
 demands of the community and these changes often entail sensible
@@
 
-Differential testing\cite{McKeeman98differentialtesting} has been
-applied in a variety of
+The novelty of our proposal is the use of multiple engine
+implementations (\eg{}, Google's V8, Microsoft's Chakra, etc.) to
+assess input validity and to check output correctness. Differential
+testing\cite{McKeeman98differentialtesting} has been applied in a
+variety of
 contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17},
 but it has not been thoroughly explored to find functional bugs in JS
-engines. The closest work was done by Patra and
-Pradel~\cite{patra2016learning}, where they evaluated their proposed
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies. This project aims to provide an adaptable
-infrastructure for differential testing of runtime engines, such as
-the JS engine or WebAssembly's. The sensible parts of the
-infrastructure are the checks of input validity (as to reduce
-waste/cost) and output correctness (as to reduce false positives).
+engines. Patra and Pradel ran a small study, published in 2016 as
+a tech report~\cite{patra2016learning}, where they found
+discrepancies\Fix{confirm if they reported bugs}. The Mozilla
+jsfunfuzz\Fix{elaborate a bit}.\Mar{Mateus, check if this sounds
+  correct/fair to you and try to elaborate the jsfunfuzz part.}
+
+\Fix{finalize}
 
@@
 Fuzzing is a popular technique to generate new test inputs from
-existing inputs~\cite{fuzz-testing-history} with the typical goal of
-finding crashes. Several fuzzing methods have been proposed in the
-past, varying with respect to how new inputs are generated (\eg{},
-coverage-based~\cite{afl,honggfuzz},
-grammar-based~\cite{grammarinator,jsfunfuzz}, and
-random-based~\cite{radamsa}) and whether or not coverage information
-is taken into account in the fuzzing
-process. Figure~\ref{fig:workflow} shows a generic pipeline of a
-fuzzer, instantiated to our problem. In our case, JS files are
-provided as seeded inputs to bootstrap the process. These files can
-originate from the test suites of the engine codebases or from the bug
-reports in their issue trackers. The fuzzing infrastructure selects
-randomly one of the inputs to fuzz with a given tool, say the
-black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
-produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
-infrastructure needs to detect and discard syntactically invalid
-inputs. Semantically invalid inputs are detected dynamically or with
-linters. Once the input is found to be valid, the infrastructure
-invokes the oracle to check correctness. In case either all engines
-consider the test output consistent (\ie{}, all pass or all fail), the
-infrastructure discards the given input. Otherwise, it considers that
-input as potentially fault-revealing and interesting. Currently, we
-classify those alarms in two groups: HI and LO. The HI group includes
-those warnings that manifest execution errors spawned directly by the
-test (or its close neighborhood) whereas the LO group includes the
-rest of the warnings. We found empirically that \Fix{XX\%} of the
-warnings analyzed in the HI group were confirmed (see
-Section~\ref{sec:results})
+existing inputs\Fix{cite} with the typical goal of finding
+crashes. Several fuzzing methods have been proposed in the past,
+varying with respect to how new inputs are generated (\eg{},
+mutation-based\Fix{cite}, grammar-based\Fix{cite}, and
+random-based\Fix{cite}) and whether or not coverage information is
+taken into account in the fuzzing process. Figure~\ref{fig:workflow}
+shows a generic pipeline of a fuzzer, instantiated to our problem. In
+our case, JS files are provided as seeded inputs to bootstrap the
+process. These files can originate from the test suites of the engine
+codebases or from the bug reports in their issue trackers. The fuzzing
+infrastrucutre selects randomly one of the inputs to fuzz with a given
+tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing
+iteration produces a new file. For grammar-agnostic fuzzers, like
+Radamsa, the infrastructure needs to detect and discard syntactically
+invalid inputs. Semantically invalid inputs are detected dynamically
+or with linters. Once the input is found to be valid, the
+infrastructure invokes the oracle to check correctness. In case either
+all engines consider the test output consistent (\ie{}, all pass or
+all fail), the infrastructure discards the given input. Otherwise, it
+considers that input as potentially fault-revaling and
+interesting. Currently, we classify those alarms in two groups: HI and
+LO. The HI group includes those warnings that manifest execution
+errors spawned directly by the test (or its close neighborhood)
+whereas the LO group includes the rest of the warnings. We found
+empirically that \Fix{XX\%} of the warnings analyzed in the HI group
+were confirmed (see Section~\ref{sec:results})
 
-%% \section{Related Work}
+\section{Related Work}
+% Differential testing with fuzzing can improve the quality of programs
+% Yang et al. \cite{yang-2011-finding}
+
+In Patra and Pradel \cite{patra2016learning} was described a new black-box fuzzer tool 
+that uses generative and probabilistic models to generate the entries. To evaluate the fuzzer,
+Patra and Pradel uses JavaScript and HTML documents to improve the javascript engines
+in Firefox and Chrome
+
+Hodovan and Kiss \cite{hodovan-fuzzinator} exposes the Fuzzinator\footnote{https://github.com/renatahodovan/fuzzinator}
+a random testing framework that uses distincts fuzzers to generate and ran test cases one-by-one in different
+program components. Fuzzinator was evaluated on JerryScript\footnote{http://jerryscript.net} 
+engine
+
 %% \Mar{rule of thumb: explain the
@@
 
+\MAB{Unfortunately the low-hanging fruit for this project was already
+  picked \cite{patra2016learning}, so I believe you should focus on
+  taming implementation-specific behavior and/or the testing
+  infrastructure (i.e. how to organize all those fuzzers and make them
+  work together). You might also want to mention the possibility of
+  fuzzing
+  \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
+  directly: LLVM already has (some) support for targeting WebAssembly,
+  which means that we'll be able to run, in the near future, pretty
+  much every language with an LLVM-backed compiler in a browser.}
+
 \section{Current Results}
@@
 
-\newcommand{\checkm}{Y}
-\newcommand{\crossmark}{N}
+\Igor{
+  Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
+  that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
+  bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
+  At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
+  and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
+  due the engine does not follows the specification and dozens of others warnings already been
+  reported previously.
 
-\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
-  \vspace{-6ex}
-  \scriptsize
-  \centering
-  \caption{List of bug reports issued by our team from April 12 to May
-    10, 2018.}
-  \label{tab:bugs}
-  \begin{tabular}{cccccc}
-    \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
-    \midrule    
-    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
-    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
-    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
-    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
-    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
-    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
-    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
-    \\
-    \midrule
-    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
-                        & \checkm &                       &
-    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
-    \midrule    
-    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
-    \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
-                        &                        &        &
-    JavascriptCore & New &
-    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
-    \\
-    \midrule    
-    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
-    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
-    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
-   \bottomrule     
-  \end{tabular}
-\end{wraptable}
+  The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
+  that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
+  The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
+  \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
+  the unary plus converts the variable to an integer if it is a valid value
+  otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
+  see that we set automatically this testcase as high priority because it is a failure by assertion.
+  The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
+  It was necessary a manual inspection to check if it is a real bug, we observed that 
+  ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
+  the unary plus converts null to 0.
+}
+\Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
+\Igor{Coloco outro caso de bug reportado?}
 
-Although there are many features yet to implement in our
-infrastructure, the basic workflow described in
-Section~\ref{sec:design} is already functional. Table~\ref{tab:bugs}
-shows the list of bugs we reported on issue trackers of different
-engines in the period of a month. So far, six of the bugs we reported
-were confirmed, two of which were fixed. One bug report we
-submitted was rejected on the basis that the offending JS file
-manifested an expected incompatibility across engine
-implementations.
-
-Note from the table that, with the exception of one case, all bug
-reports still waiting for confirmation are associated with the
-JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
-showed that the triage process is very slow for that engine. As of
-now, we did not find any bug on SpiderMonkey and V8. Finally, it is
-worth noting that seven of the 13 JS files that manifested
-discrepancies were produced with fuzzing (column ``Fuzz''). This
-emphasizes the importance of continuously collecting test suites from
-multiple sources; today, we use test suites from six different open
-source engines, including a total of \Fix{38.9K} test files.
-
-%% \Igor{
-%%   Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
-%%   that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
-%%   bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
-%%   At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
-%%   and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
-%%   due the engine does not follows the specification and dozens of others warnings already been
-%%   reported previously.
-
-%%   The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
-%%   that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
-%%   The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
-%%   \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
-%%   the unary plus converts the variable to an integer if it is a valid value
-%%   otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
-%%   see that we set automatically this testcase as high priority because it is a failure by assertion.
-%%   The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
-%%   It was necessary a manual inspection to check if it is a real bug, we observed that 
-%%   ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
-%%   the unary plus converts null to 0.
-%% }
-%% \Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
-%% \Igor{Coloco outro caso de bug reportado?}
-
-%\input{bugs}
-%\input{bug_table}
-
-\section{Future Steps}
-
-The list below shows future tasks for this project.
-
-\begin{itemize}
-\item Integrate different fuzzers, including AFL~\cite{afl},
-  HonggFuzz~\cite{honggfuzz}, jsfunfuzz~\cite{jsfunfuzz}, and
-  Grammarinator~\cite{grammarinator}.
-
-\item Find balance between generational strategies (, which often
-  produce valid but simple inputs) and mutational strategies (, which
-  often produce complex but invalid inputs) for fuzzing.
-
-\item Explore different strategies to reduce the number of false
-  positives. For example, mining issue trackers for similar bug
-  reports.
-
-\item Use our infrastructure to find bugs on
-  WebAssembly~\cite{webassembly}, a new binary format already
-  supported by major browsers. 
-\end{itemize}
-
-%% \MAB{Unfortunately the low-hanging fruit for this project was already
-%%   picked \cite{patra2016learning}, so I believe you should focus on
-%%   taming implementation-specific behavior and/or the testing
-%%   infrastructure (i.e. how to organize all those fuzzers and make them
-%%   work together). You might also want to mention the possibility of
-%%   fuzzing
-%%   \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
-%%   directly: LLVM already has (some) support for targeting WebAssembly,
-%%   which means that we'll be able to run, in the near future, pretty
-%%   much every language with an LLVM-backed compiler in a browser.}
+\input{bugs}
+\input{bug_table}
 
@@
 \end{document}
-
-%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
-%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
-%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL
-%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly

### 2018-05-14 docs/google-research-awards-latam/main.tex

--- 2018-05-13 docs/google-research-awards-latam/main.tex
@@
 
-%% \section{Related Work}
+\section{Related Work}
+% Differential testing with fuzzing can improve the quality of programs
+% Yang et al. \cite{yang-2011-finding}
+
+In Patra and Pradel \cite{patra2016learning} was described a new black-box fuzzer tool 
+that uses generative and probabilistic models to generate the entries. To evaluate the fuzzer,
+Patra and Pradel uses JavaScript and HTML documents to improve the javascript engines
+in Firefox and Chrome
+
+Hodovan and Kiss \cite{hodovan-fuzzinator} exposes the Fuzzinator\footnote{https://github.com/renatahodovan/fuzzinator}
+a random testing framework that uses distincts fuzzers to generate and ran test cases one-by-one in different
+program components. Fuzzinator was evaluated on JerryScript\footnote{http://jerryscript.net} 
+engine
+
 %% \Mar{rule of thumb: explain the

### 2018-05-14 docs/google-research-awards-latam/main.tex
update paper results

--- 2018-05-13 docs/google-research-awards-latam/main.tex
@@
 
-%% \section{Related Work}
+% \section{Related Work}
+% Differential testing with fuzzing can improve the quality of programs
+% Yang et al. \cite{yang-2011-finding}
+
 %% \Mar{rule of thumb: explain the
@@
   === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
-  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
-the empty string, whose integer representation, according to the spec,
-should be zero\Fix{igor, please look for the part of spec and add link}. The modified
+  version of the fuzzed code.}. In the original version of this code 
+  \Igor{this code is the original fuzzed code, not the minimized version. we can use just (+``\textbackslash{}x00''===0)}, 
+  the \CodeIn{valueOf} function returned
+the empty string, whose integer representation, according to the spec of Unary Plus\cite{unary-plus},
+should be zero. The modified
 code returns a string representation of an invalid hexadecimal
-value\Fix{igor, how do we know this is invalid?}. As such, the engines
+value\Fix{igor, how do we know this is invalid?}\Igor{0x00 = NULL terminator \url{http://www.asciitable.com}, but is not a "null" keyword (+null is equal 0)}. As such, the engines
 are not expected to evaluate that string at the assertion expression;
@@
 however, is able to parse the string as a number. It returns a null
-object, which is then converted to zero, making the test to pass.
+object, which is then converted to zero, making the test to pass. \Igor{according the technical explanation:\\
+the function String::toDouble should check the length, instead of null terminator. \url{https://github.com/Microsoft/ChakraCore/commit/98fbc297e2b2781bc4d6ed3ff360dba8d18c1eda}}
 \newcommand{\checkm}{Y}

### 2018-05-14 docs/google-research-awards-latam/main.tex
adding vilas

--- 2018-05-14 docs/google-research-awards-latam/main.tex
@@
 
-    Contact at Google:~Martin Barbella (mbarbella@google.com)
+    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)
 
@@
 
-\section{Related Work}
+% \section{Related Work}
 % Differential testing with fuzzing can improve the quality of programs
 % Yang et al. \cite{yang-2011-finding}
-
-In Patra and Pradel \cite{patra2016learning} was described a new black-box fuzzer tool 
-that uses generative and probabilistic models to generate the entries. To evaluate the fuzzer,
-Patra and Pradel uses JavaScript and HTML documents to improve the javascript engines
-in Firefox and Chrome
-
-Hodovan and Kiss \cite{hodovan-fuzzinator} exposes the Fuzzinator\footnote{https://github.com/renatahodovan/fuzzinator}
-a random testing framework that uses distincts fuzzers to generate and ran test cases one-by-one in different
-program components. Fuzzinator was evaluated on JerryScript\footnote{http://jerryscript.net} 
-engine
 
@@
   \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
-  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
-  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
-the empty string, whose integer representation, according to the spec,
-should be zero\Fix{igor, please look for the part of spec and add link}. The modified
-code returns a string representation of an invalid hexadecimal
-value\Fix{igor, how do we know this is invalid?}. As such, the engines
-are not expected to evaluate that string at the assertion expression;
-hence test execution is expected to fail. Chakra,
-however, is able to parse the string as a number. It returns a null
-object, which is then converted to zero, making the test to pass.
+  === 0)\}}. 
+  The \CodeIn{valueOf} is an object property that returns the primitive value
+  of the specific object\cite{valueof} and in the original version of this code,
+  the \CodeIn{valueOf} function returns an empty string.
+  The modified code returns a string representation of an embedded null terminator
+  value. 
+  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{Object.ToNumber(a.valueOf())} 
+  that converts a variable to a number, otherwise the return should be the 
+  value NaN (Not a Number) \cite{unary-plus}.
+  As such, the engines evaluate that unary plus as a NaN value 
+  at the assertion expression; hence test execution is expected to fail. 
+  Chakra, however, is able to parse the string as a number zero, making the test to pass.
+
 \newcommand{\checkm}{Y}
@@
   \caption{List of bug reports issued by our team from April 12 to May
-    10, 2018.}
+    24, 2018.}
   \label{tab:bugs}
@@
     \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
-                        & \checkm &                       &
+                        &  &                       &
     JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
@@
     12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
-    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
+    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
+    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
+    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
+    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
+    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
    \bottomrule     
@@
 
-So far, six of the bugs we reported
+So far, eight of the bugs we reported
 were confirmed, two of which were fixed. One bug report we
@@
 \item Integrate different fuzzers, including AFL~\cite{afl},
-  HonggFuzz~\cite{honggfuzz}, jsfunfuzz~\cite{jsfunfuzz}, and
+  HonggFuzz~\cite{honggfuzz}, LibFuzzer~\cite{libfuzzer}, jsfunfuzz~\cite{jsfunfuzz}, and
   Grammarinator~\cite{grammarinator}.

### 2018-05-14 docs/google-research-awards-latam/main.tex
adding vilas

--- 2018-05-14 docs/google-research-awards-latam/main.tex
@@
   \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
-  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
-  version of the fuzzed code.}. In the original version of this code, the \CodeIn{valueOf} function returned
-the empty string, whose integer representation, according to the spec,
-should be zero\Fix{igor, please look for the part of spec and add link}. The modified
-code returns a string representation of an invalid hexadecimal
-value\Fix{igor, how do we know this is invalid?}. As such, the engines
-are not expected to evaluate that string at the assertion expression;
-hence test execution is expected to fail. Chakra,
-however, is able to parse the string as a number. It returns a null
-object, which is then converted to zero, making the test to pass.
+  === 0)\}}. 
+\Igor{
+  The \CodeIn{valueOf} is an object property that returns the primitive value
+  of the specific object\cite{valueof} and in the original version of this code,
+  the \CodeIn{valueOf} function returns an empty string.
+  The modified code returns a string representation of an embedded null terminator
+  value. 
+  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{String.ToNumber(a.valueOf())} 
+  that converts a variable to a number, but if the value cannot be converted, 
+  the return should be the value NaN (Not a Number) \cite{unary-plus}.
+  As such, the engines evaluate that unary plus as a NaN value 
+  at the assertion expression; hence test execution is expected to fail. 
+  Chakra, however, is able to parse the string as a number zero, making the test to pass.
+}
 \newcommand{\checkm}{Y}

### 2018-05-14 docs/google-research-awards-latam/main.tex
pass on results

@@
 
-    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)
+    Contact at Google:~Martin Barbella (mbarbella@google.com)
 
@@
 \Igor{
-  The \CodeIn{valueOf} is an object property that returns the primitive value
-  of the specific object\cite{valueof} and in the original version of this code,
+  The \CodeIn{valueOf} function is a primitive value of
+  a String object and in the original version of this code,
   the \CodeIn{valueOf} function returns an empty string.
@@
   value. 
-  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{String.ToNumber(a.valueOf())} 
-  that converts a variable to a number, but if the value cannot be converted, 
-  the return should be the value NaN (Not a Number) \cite{unary-plus}.
+  The unary plus\cite{unary-plus} ``\CodeIn{+a}" in this case is equivalent to 
+  \CodeIn{String.ToNumber(a.valueOf())} that
+  converts a variable to a number, but if 
+  the value cannot be converted, the return should be the value NaN (Not a Number).
   As such, the engines evaluate that unary plus as a NaN value 

### 2018-05-15 docs/google-research-awards-latam/main.tex
pass on results
merge

--- 2018-05-14 docs/google-research-awards-latam/main.tex
@@
 
-    Contact at Google:~Martin Barbella (mbarbella@google.com) and Vilas Jagannath (vilasshekharbj@gmail.com)
+    Contacts:~Martin Barbella (mbarbella@google.com), Vilas Jagannath (vilasshekharbj@gmail.com)
 
@@
 JavaScript (JS) is a fundamental programming language for the
-web. Finding bugs in JavaScript engines is an important
-problem. Differential testing of JS engines is a promising approach to
-that end. This proposal describes our testing infrastructure, current
-results, and some upcoming features to improve the bug-finding
-process.
+web. Finding bugs in JavaScript engines is an important problem. This
+proposal describes our differential testing infrastructure for testing
+JS engines, our current results, and upcoming features to improve
+bug-finding of JS engines.
 \end{abstract}
@@
 
-The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
+The workflow described in Section~\ref{sec:design} is currently functional. This section shows preliminary
 results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is

### 2018-05-15 docs/google-research-awards-latam/main.tex
polish igor text (still some PL-related inconsistencies)

@@
 cost of testing, but the lack of executable specifications is an
-important obstacle. In particular, it is an obstable to find functional errors.
+important obstacle. In particular, it is an obstacle to find functional errors.
 
@@
 
-The workflow described in Section~\ref{sec:design} is currently functional. This section shows preliminary
-results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
-promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
-issue trackers of different engines in the period of a month. For
-example, bug \# 6 was manifested by the JS code \CodeIn{var a =
-  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
-  === 0)\}}. 
-\Igor{
-  The \CodeIn{valueOf} is an object property that returns the primitive value
-  of the specific object\cite{valueof} and in the original version of this code,
-  the \CodeIn{valueOf} function returns an empty string.
-  The modified code returns a string representation of an embedded null terminator
-  value. 
-  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{String.ToNumber(a.valueOf())} 
-  that converts a variable to a number, but if the value cannot be converted, 
-  the return should be the value NaN (Not a Number) \cite{unary-plus}.
-  As such, the engines evaluate that unary plus as a NaN value 
-  at the assertion expression; hence test execution is expected to fail. 
-  Chakra, however, is able to parse the string as a number zero, making the test to pass.
-}
+The workflow described in Section~\ref{sec:design} is currently
+functional. This section shows preliminary results obtained with our
+infrastructure providing some evidence that finding bugs in JS runtime
+engines is promising. Table~\ref{tab:bugs} shows the list of bugs we
+reported on issue trackers of different engines in the period of a
+month. For example, bug \# 6 was manifested by the JS code \CodeIn{var
+  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
+  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
+function that returns a primitive value identifying the target
+object~\cite{valueof}. That function returns an empty string in the
+original version of this code. The modified version of the code
+returns a string representation of a null character (called
+\CodeIn{NUL} in ascii).
+The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
+is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
+that converts a string to a number, but if the string cannot be
+converted, the expression should evaluate to NaN (Not a Number)
+\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
+plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
+expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.
+
 \newcommand{\checkm}{Y}
@@
 %%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
-%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL
-%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly
+%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
+%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
+%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
+%%  LocalWords:  cgi tmp

### 2018-05-25 docs/google-research-awards-latam/main.tex

--- 2018-05-15 docs/google-research-awards-latam/main.tex
@@
 
-    Contacts:~Martin Barbella (mbarbella@google.com), Vilas Jagannath (vilasshekharbj@gmail.com)
+    Contact at Google:~Martin Barbella (mbarbella@google.com)
 
@@
 JavaScript (JS) is a fundamental programming language for the
-web. Finding bugs in JavaScript engines is an important problem. This
-proposal describes our differential testing infrastructure for testing
-JS engines, our current results, and upcoming features to improve
-bug-finding of JS engines.
+web. Finding bugs in JavaScript engines is an important
+problem. Differential testing of JS engines is a promising approach to
+that end. This proposal describes our testing infrastructure, current
+results, and some upcoming features to improve the bug-finding
+process.
 \end{abstract}
@@
 
-The workflow described in Section~\ref{sec:design} is currently functional. This section shows preliminary
+The basic workflow described in Section~\ref{sec:design} is functional. This section shows preliminary
 results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is

### 2018-05-25 docs/google-research-awards-latam/main.tex
merge

--- 2018-05-15 docs/google-research-awards-latam/main.tex
@@
 infrastructure providing some evidence that finding bugs in JS runtime
-engines is promising. Table~\ref{tab:bugs} shows the list of bugs we
+engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
 reported on issue trackers of different engines in the period of a

### 2018-05-25 docs/google-research-awards-latam/main.tex
final pass. Igor, please fix the todos (or let me know if you can't)

@@
 \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
-\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
+\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
 \newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
@@
 JS engines, our current results, and upcoming features to improve
-bug-finding of JS engines.
+bug-finding in JS engines.
 \end{abstract}
@@
   ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
-demands of the community and these changes often entail sensible
+demands of the community. These changes often entail sensible
 changes in engine implementations~\cite{kangax} that could lead to
@@
 contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
-to mitigate with the lack of oracles problem,
+to mitigate the oracle problem,
 but it has not been thoroughly explored to find functional bugs in JS
@@
 language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies. This project aims to provide an adaptable
+discrepancies. This project aims at building and evaluating an
 infrastructure for differential testing of runtime engines, such as
@@
 grammar-based~\cite{grammarinator,jsfunfuzz}, and
-random-based~\cite{radamsa}) and whether or not coverage information
-is taken into account in the fuzzing
-process. Figure~\ref{fig:workflow} shows a generic pipeline of a
+random-based~\cite{radamsa}). Figure~\ref{fig:workflow} shows a generic pipeline of a
 fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
 with no arrow denote encapsulation. In our case, JS files are
-provided as seeded inputs to bootstrap the process. These files can
+provided as seeds to bootstrap the process. These files can
 originate from the test suites of the engine codebases or from the bug
@@
 input as potentially fault-revealing and interesting. Currently, we
-classify alarms in two groups: HI and LO. The HI group includes
+classify alarms in the HI and LO groups. The HI group includes
 those warnings that manifest execution errors spawned directly by the
@@
 
-%% Although there are many features yet to implement in our
-%% infrastructure,
-
-The workflow described in Section~\ref{sec:design} is currently
-functional. This section shows preliminary results obtained with our
-infrastructure providing some evidence that finding bugs in JS runtime
-engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
-reported on issue trackers of different engines in the period of a
-month. For example, bug \# 6 was manifested by the JS code \CodeIn{var
-  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
-  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
-function that returns a primitive value identifying the target
-object~\cite{valueof}. That function returns an empty string in the
-original version of this code. The modified version of the code
-returns a string representation of a null character (called
-\CodeIn{NUL} in ascii).
-The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
-is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
-that converts a string to a number, but if the string cannot be
-converted, the expression should evaluate to NaN (Not a Number)
-\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
-plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
-expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.
-
 \newcommand{\checkm}{Y}
 \newcommand{\crossmark}{N}
-\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
-  \vspace{-2ex}
+\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}
+  \vspace{-3ex}
   \scriptsize
@@
 
+%% Although there are many features yet to implement in our
+%% infrastructure,
+
+The workflow described in Section~\ref{sec:design} is currently
+functional. This section shows preliminary results obtained with our
+infrastructure providing some evidence that finding bugs in JS runtime
+engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
+reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
+  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
+  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
+function that returns a primitive value identifying the target
+object~\cite{valueof}. That function returns an empty string in the
+original version of this code. The modified version of the code
+returns a string representation of a null character (called
+\CodeIn{NUL} in ascii).
+The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
+is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
+that converts a string to a number, but if the string cannot be
+converted, the expression should evaluate to NaN (Not a Number)
+\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
+plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
+expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.
+
 So far, eight of the bugs we reported
@@
 implementations.
-Note from the table that, with the exception of one case, all bug
+Note from the table that all bug
 reports still waiting for confirmation are associated with the
@@
 showed that the triage process is very slow for that engine. As of
-now, we did not find any bug on SpiderMonkey and V8. Finally, it is
-worth noting that six of the 13 JS files that manifested
+now, we did not find any new bug on SpiderMonkey and V8; the bugs we
+found were duplicates and were not reported. Finally, it is
+worth noting that\Fix{ six of the 13 JS files}\Mar{update this!} that manifested
 discrepancies were \emph{not} produced with fuzzing (column
@@
 
-\item Use our infrastructure to find bugs on
-  WebAssembly~\cite{webassembly}, a new binary format already
+\item Look for bugs in WebAssembly~\cite{webassembly}, a new binary format already
   supported by major browsers. In principle, our infrastructure is

### 2018-05-25 docs/google-research-awards-latam/main.tex
pass on paper and updated bugs_found.txt

@@
 test (or its close neighborhood) whereas the LO group includes the
-rest of the warnings. We found empirically that \Fix{XX\%} of the
-warnings analyzed in the HI group were confirmed.
+rest of the warnings. \Igor{We found empirically that 88\% of the
+issues reported are included in the HI group and 58\% of them was confirmed}.
 
@@
 \CodeIn{NUL} in ascii).
-The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
-is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
-that converts a string to a number, but if the string cannot be
-converted, the expression should evaluate to NaN (Not a Number)
-\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
+\Igor{The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
+is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
+that converts a string to a number, otherwise the operation returns NaN 
+(Not a Number)\cite{unary-plus}}. For this case, \Igor{isto esta correto? $\rightarrow$ all engines but} Chakra evaluate the unary
 plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
@@
 
-So far, eight of the bugs we reported
+So far, ten of the bugs we reported
 were confirmed, two of which were fixed. One bug report we
@@
 found were duplicates and were not reported. Finally, it is
-worth noting that\Fix{ six of the 13 JS files}\Mar{update this!} that manifested
+worth noting that \Igor{7 out of 17} JS files that manifested
 discrepancies were \emph{not} produced with fuzzing (column
@@
 observation emphasizes the importance of continuously collecting test suites from
-multiple sources; today, we use test suites from six different open
-source engines, including a total of \Fix{38.9K} test files.
+multiple sources; today, we use test suites from seven different open
+source engines, including a total of 30K test files.
 

### 2018-06-04 paper/paper.tex
paper sketch

--- 2018-05-25 docs/google-research-awards-latam/main.tex
@@
-\documentclass[11pt]{article}
-%\documentclass[dvips,11pt]{article}
+%\documentclass[conference]{IEEEtran}
+\documentclass[10pt,conference,anonymous]{IEEEtran}
+\IEEEoverridecommandlockouts
 
-% \usepackage{natbib}
-% \setlength{\bibsep}{0pt plus 0.3ex}
-\usepackage[margin=1cm]{caption}
-\usepackage{titlesec}
-\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
-%,nohead,nofoot
-%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
-\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
-%\usepackage[margin=1in,includeheadfoot]{geometry}
-\usepackage{url}
-\usepackage{cite}
-\usepackage{multirow}
-\usepackage{lipsum}
-\usepackage{booktabs}
-\usepackage{tabularx}
-\usepackage{wrapfig}
-\usepackage{microtype}
-\usepackage{hyperref}
-\usepackage{listings}
-\usepackage{subfigure}
-% ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
-\let\OLDthebibliography\thebibliography
-\renewcommand\thebibliography[1]{
-  \OLDthebibliography{#1}
-  \setlength{\parskip}{0pt}
-  \setlength{\itemsep}{0pt plus 0.3ex}
-}
-
-\usepackage[pdftex]{graphicx}
-\usepackage{url}
-\usepackage{color}
-\usepackage{xcolor}
-\definecolor{darkred}{rgb}{0.5,0,0}
-\definecolor{darkgreen}{rgb}{0,0.5,0}
-\definecolor{darkblue}{rgb}{0,0,0.5}
-\definecolor{darkaquamarine}{rgb}{0.2,0.4,0.3}
-%% macros
-\newcommand{\ie}{i.e.}
-\newcommand{\eg}{e.g.}
-\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
-\newcommand{\Mar}[1]{\textbf{[[Marcelo:~}{\color{blue} #1}\textbf{]]}}
-\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
-\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
-\newcommand{\Comment}[1]{}
-\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}
-
-%% \setlength{\oddsidemargin}{0.25in}
-%% \setlength{\textwidth}{6.5in}
-%% \setlength{\topmargin}{0in}
-%% \setlength{\textheight}{8.5in}
-
-%\renewcommand\Affilfont{\fontsize{9}{10.8}\itshape}
-% These force using more of the margins that is the default style
+\input{packages}
+\input{macros}
 
@@
 
-\title{Finding Bugs in JavaScript Engines with Differential Testing}
-\author{}
-\date{}
+\title{Finding Bugs in JavaScript Engines with Differential
+  Testing---an Experience Report}
 
-% You can leave out "date" and it will be added automatically for today
-% You can change the "\today" date to any text you like
-
-\makeatletter
-\def\maketitle{%
-  \par{\centering\large\textbf{\@title}\normalsize\par}\vspace{3ex}%
-  \par{\@author}%
-  \par}
-\makeatother
+%% \author{
+%% \IEEEauthorblockN{Sabrina Souto}
+%% \IEEEauthorblockA{State University of Para\'iba\\
+%% Para\'iba, Brazil\\
+%% sabrinadfs@gmail.com}
+%% \and
+%% \IEEEauthorblockN{Marcelo d'Amorim}
+%% \IEEEauthorblockA{Federal University of Pernambuco\\
+%%   Pernambuco, Brazil\\
+%%   damorim@cin.ufpe.br}
+%% \and
+%% \IEEEauthorblockN{Rohit Gheyi}
+%% \IEEEauthorblockA{Federal University of Campina Grande\\
+%%   Para\'iba, Brazil\\
+%%   rohit@dsc.ufcg.edu.br}
+%% }
 
@@
 
-\vspace{-2ex}
-\small    
-\begin{table}[h!] 
-  \centering%% Centro de Inform\'atica - CIn \\
-  \begin{tabular*}{.85\linewidth}{l}
-
-    Marcelo d'Amorim and Igor Sim\~oes (M.Sc. student)\\
-
-    Postal Address: Av. Jornalista Anibal Fernandes, S/N. Cidade
-    Universit\'aria, PE, Brazil, 50.740-560 \\
-
-    Email addresses: \{damorim, isol2\}@cin.ufpe.br\\
-
-    Phones: +55 (81) 2126-8430,
-    ext. 4379 [work], +55 (81) 98800-2010 [mobile]\\
-
-    Affiliation: Federal University of Pernambuco, Department of
-    Computer Science\\
-
-    Contacts:~Martin Barbella (mbarbella@google.com), Vilas Jagannath (vilasshekharbj@gmail.com)
-
-  \end{tabular*}
-\end{table}
-\normalsize
-
-\vspace{-2ex}
 \begin{abstract}
-JavaScript (JS) is a fundamental programming language for the
-web. Finding bugs in JavaScript engines is an important problem. This
-proposal describes our differential testing infrastructure for testing
-JS engines, our current results, and upcoming features to improve
-bug-finding in JS engines.
 \end{abstract}
 
-\section{Problem Space}
+\begin{IEEEkeywords}
+...
+\end{IEEEkeywords}
 
-%% Its niche is front-end and
-%% back-end web development\Comment{, supported several frameworks and
-%%   runtimes (\eg{}, Express.js and Node.js)}.
+\section{Introduction}
 
-%% In fact, bugs in JS implementations are often reported by
-%% the general public, some of which were reported by our team.
-%% (confirmed by engine developers; see
-%% Section~\ref{sec:results}) using a prototype of our solution (see
-%% Section~\ref{sec:design}).
+JavaScript (\js{}) is one of the most popular programming languages of
+today~\cite{business-insider,stackify}. The \js{} specification
+changes relatively frequently to accommodate the pressing demands of
+the community. For example, the JS specification went through a severe
+change recently called by the name of ECMAScript6
+(ES6)~\cite{es6-features}.  These changes often entail sensible
+changes in engine implementations~\cite{kangax} that could lead to
+errors, including regressions. Automated techniques can help finding
+bugs, but the lack of executable specifications limits their ability
+to detect errors not manifested by universal oracles.
 
-JavaScript (JS) is one of the most popular programming languages of
-today~\cite{business-insider,stackify} largely because of its
-widespread use on the web. As common in software, the JS specification
-changes regularly\footnote{Recently, the specification went through a
-  bigger change compared to prior releases, called by the name of
-  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
-demands of the community. These changes often entail sensible
-changes in engine implementations~\cite{kangax} that could lead to
-errors, including regressions. Automated test generation can help reduce the
-cost of testing, but the lack of executable specifications is an
-important obstacle. In particular, it is an obstacle to find functional errors.
-
-%\vspace{-1ex}
-\begin{center}
-\fbox{
-  \begin{minipage}{13.5cm}
-    \centering \textit{The goal of this project is to find bugs in
-      implementations of JavaScript engines by leveraging diversity
-      across implementations.}
-  \end{minipage}
-}
-\end{center}
-%\vspace{-1ex}
-
-Differential testing\cite{McKeeman98differentialtesting} has been
-applied in a variety of
-contexts\cite{Brumley-etal-ss07,Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
-to mitigate the oracle problem,
-but it has not been thoroughly explored to find functional bugs in JS
+This paper reports on a study to find those kinds of bugs in
+JavaScript engines. The goal of the study is to improve quality of
+existing \js{} engines by improving the bug finding process. We used
+differential testing~\cite{Brumley-etal-ss07}, a technique that has
+been applied in a variety of
+contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
+to address the oracle problem. Differential testing leverages the
+diversity across system's implementations to detect anomalous
+behavior. \Mar{this needs work$\rightarrow$}
+\Fix{but it has not been thoroughly explored to find functional bugs in JS
 engines. The closest work was done by Patra and
@@
 infrastructure are the checks of input validity (as to reduce
-waste/cost) and output correctness (as to reduce false positives).
+waste/cost) and output correctness (as to reduce false positives).}
 
-\section{Design Space}
+\section{Infrastructure}
 \label{sec:design}
 
-\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
-  \vspace{-5ex}
+%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
+\begin{figure}[h]
   \centering
   \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
-  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
-  \vspace{-5ex}  
-\end{wrapfigure}
-Fuzzing is a popular technique to generate new test inputs from
-existing inputs~\cite{fuzz-testing-history} with the typical goal of
-finding crashes. Several fuzzing methods have been proposed in the
-past, varying with respect to how new inputs are generated (\eg{},
-coverage-based~\cite{afl,honggfuzz},
+  \caption{\label{fig:workflow}Infrastructure.}
+\end{figure}
+
+Figure~\ref{fig:workflow} illustrates the workflow of the
+infrastructure we used in this study. Arrowed lines indicate control
+flow (dashed) and data flow (filled); lines with no arrow denote
+encapsulation. The bug-finding process takes on input JS files
+originating from the regression test suites of various JS engines. It
+is worth noting that we found online regression suites for a total of
+\Fix{YY} JS engines.\Mar{show table with name and count of JS files}
+If input fuzzing~\cite{fuzz-testing-history} is not selected, the
+oracle checks whether or not the output is consistent across all
+engine implementations. In case the test passes in all engines or
+fails in all engines (\ie{}, the output is consistent), the
+infrastructure discards the corresponding input. Otherwise, it
+considers the input as potentially fault-revealing; hence interesting
+for human inspection. If fuzzing is selected, new inputs are obtained
+from a given input using some off-the-shelf fuzzer; the workflow is
+similar to that of no fuzzing. Several fuzzing methods have been
+proposed in the past, varying with respect to how new inputs are
+generated (\eg{}, coverage-based~\cite{afl,honggfuzz},
 grammar-based~\cite{grammarinator,jsfunfuzz}, and
-random-based~\cite{radamsa}). Figure~\ref{fig:workflow} shows a generic pipeline of a
-fuzzer infrastructure, instantiated to our problem. Arrows indicate data flow; lines
-with no arrow denote encapsulation. In our case, JS files are
-provided as seeds to bootstrap the process. These files can
-originate from the test suites of the engine codebases or from the bug
-reports in their issue trackers. The fuzzing infrastructure selects
-randomly one of the inputs to fuzz with a given tool, say the
-black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
-produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
-infrastructure can discard syntactically invalid
-inputs using an external parser for the input language; semantically
-invalid inputs can be prevented with with linters. Once the input is
-found to be likely valid, the infrastructure
-invokes the oracle to check correctness. In case all engines
-consider the test output consistent (\ie{}, all pass or all fail), the
-infrastructure discards the corresponding input. Otherwise, it considers that
-input as potentially fault-revealing and interesting. Currently, we
-classify alarms in the HI and LO groups. The HI group includes
-those warnings that manifest execution errors spawned directly by the
-test (or its close neighborhood) whereas the LO group includes the
-rest of the warnings. \Igor{We found empirically that 88\% of the
-issues reported are included in the HI group and 58\% of them was confirmed}.
+random-based~\cite{radamsa}). \Mar{which ones we covered? why is this
+  relevant?}
+
+The infrastructure outputs a list of warnings for human inspection.
+To reduce the number of false alarms, we clustered warnings in two
+groups, reflecting their likelihood to manifest a real bug. The HI
+group includes those inputs that manifest anomaly directly by the test
+(or its close neighborhood) as opposed to anomaly in some JS
+function. The rationale is that the test was able to execute to
+completion without violating any internal checks of the API, but
+failed to satisfy some check of the test. The LO group, in contrast,
+includes those cases where the anomaly was observed executing some JS
+function. We found that engine implementations often check
+pre-conditions of API functions differently, leading to premature
+failures. Most of the inputs in this category failed to satisfy the
+pre-condition check of some, but not all engines. Although we did find
+real bugs from warnings manifested in this category, the proportion is
+much lower compared to the HI category--only 12\% of the reals bugs we
+found originated from the LO category.\Mar{can we detect dups mining
+  issue trackers?}
+
+\Mar{show real examples of HI and LO and provide the
+  rationale for such classification.}
+
+%% selects randomly one of the inputs to fuzz with a
+%% given tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration produces a new
+%% file. For grammar-agnostic fuzzers, like Radamsa, the infrastructure
+%% can discard syntactically invalid inputs using an external parser for
+%% the input language; semantically invalid inputs can be prevented with
+%% with linters. Once the input is found to be likely valid, the
+%% infrastructure invokes the oracle to check correctness.
 
@@
 \newcommand{\crossmark}{N}
-\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}
+%\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}
+
+\begin{table*}
   \vspace{-3ex}
-  \scriptsize
+%  \scriptsize
   \centering
@@
   \end{tabular}
-\end{wraptable}
+\end{table*}
 
@@
 returns a string representation of a null character (called
-\CodeIn{NUL} in ascii).
-\Igor{The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
+\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
 is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
 that converts a string to a number, otherwise the operation returns NaN 
-(Not a Number)\cite{unary-plus}}. For this case, \Igor{isto esta correto? $\rightarrow$ all engines but} Chakra evaluate the unary
+(Not a Number)\cite{unary-plus}. For this case, Chakra evaluates the unary
 plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
@@
 found were duplicates and were not reported. Finally, it is
-worth noting that \Igor{7 out of 17} JS files that manifested
+worth noting that 7 of the 17 JS files that manifested
 discrepancies were \emph{not} produced with fuzzing (column
@@
 
-%% \Igor{
-%%   Nowadays, we used six javascript engines suites with approximately 2K of javascript files 
-%%   that could be fuzzed. Currently, using our infrastructure we reported \Fix{13}
-%%   bugs so far. The Table~\ref{tab:bugs} exposes all bugs found and reported by our team.
-%%   At this moment, the status are: \Fix{6} issues was tagged as new, \Fix{4} was confirmed
-%%   and \Fix{2} of them was merged and closed. Unfortunally, \Fix{1} of them was rejected
-%%   due the engine does not follows the specification and dozens of others warnings already been
-%%   reported previously.
+%\section*{Acknowledgment}
 
-%%   The Figure~\ref{fig:bug-chakra} exposes a fuzzed file generated by radamsa in our environment, it was observed
-%%   that the fuzzer replace the empty string at Line 3 and replace it with the hexadecimal value "\textbackslash x00".
-%%   The bug manifests in Line 7, according to ES6 specification on Mozilla dev website
-%%   \footnote{Unary Plus \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Operators/Arithmetic_Operators}},
-%%   the unary plus converts the variable to an integer if it is a valid value
-%%   otherwise returns NaN. The Figure~\ref{fig:pattern} shows the log output from our infrastructure,
-%%   see that we set automatically this testcase as high priority because it is a failure by assertion.
-%%   The differential test across all engines, shows a unexpected behaviour of ChakraCore engine that passes in this test case.
-%%   It was necessary a manual inspection to check if it is a real bug, we observed that 
-%%   ChakraCore indentify "\textbackslash x00" as a null terminator instead of invalid parser object making
-%%   the unary plus converts null to 0.
-%% }
-%% \Fix{nao estou conseguindo mesclar dois listings com subfigure, por favor alguem tenta fazer isso por mim.}
-%% \Igor{Coloco outro caso de bug reportado?}
-
-%\input{bugs}
-%\input{bug_table}
-
-\section{Future Steps}
-
-The list below shows future tasks for this project.
-
-\begin{itemize}
-\item Integrate different fuzzers, including AFL~\cite{afl},
-  HonggFuzz~\cite{honggfuzz}, LibFuzzer~\cite{libfuzzer}, jsfunfuzz~\cite{jsfunfuzz}, and
-  Grammarinator~\cite{grammarinator}.
-
-\item Find balance between generational strategies (, which often
-  produce valid but simple inputs) and mutational strategies (, which
-  often produce complex but invalid inputs) for fuzzing.
-
-\item Explore different strategies to reduce the number of false
-  positives as to facilitate the inspection process. For example,
-  mining issue trackers for similar bug reports is a candidate alternative.
-
-\item Look for bugs in WebAssembly~\cite{webassembly}, a new binary format already
-  supported by major browsers. In principle, our infrastructure is
-  agnostic to the runtime engine used. We are eager to explore other
-  sources of bugs, especially in very new engines.
-
-\end{itemize}
-
-%% \MAB{Unfortunately the low-hanging fruit for this project was already
-%%   picked \cite{patra2016learning}, so I believe you should focus on
-%%   taming implementation-specific behavior and/or the testing
-%%   infrastructure (i.e. how to organize all those fuzzers and make them
-%%   work together). You might also want to mention the possibility of
-%%   fuzzing
-%%   \href{https://developer.mozilla.org/en-US/docs/WebAssembly}{WebAssembly}
-%%   directly: LLVM already has (some) support for targeting WebAssembly,
-%%   which means that we'll be able to run, in the near future, pretty
-%%   much every language with an LLVM-backed compiler in a browser.}
-
-\section{Data Policy}
-
-The results produced with this research will be made available to the
-public and to the research community.  All tools and data sets
-developed will be available online, and the software will be released
-under an open source license.
-
-\footnotesize
+%\bibliographystyle{IEEEtran}
 \bibliographystyle{plain}
-\bibliography{tmp}
+\bibliography{references,../docs/google-research-awards-latam/tmp}
 
 \end{document}
-
-%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
-%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
-%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
-%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
-%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
-%%  LocalWords:  cgi tmp

### 2018-06-05 paper/paper.tex
adding gitignore

@@
 \IEEEoverridecommandlockouts
+
+%% Marcelo added this
+\makeatletter
+\renewcommand\footnoterule{%
+  \kern-3\p@
+  \hrule\@width.4\columnwidth
+  \kern2.6\p@}
+  \makeatother
 
@@
 JavaScript engines. The goal of the study is to improve quality of
-existing \js{} engines by improving the bug finding process. We used
+existing \js{} engines by improving the bug-finding process. We used
 differential testing~\cite{Brumley-etal-ss07}, a technique that has
@@
 originating from the regression test suites of various JS engines. It
-is worth noting that we found online regression suites for a total of
-\Fix{YY} JS engines.\Mar{show table with name and count of JS files}
-If input fuzzing~\cite{fuzz-testing-history} is not selected, the
-oracle checks whether or not the output is consistent across all
-engine implementations. In case the test passes in all engines or
-fails in all engines (\ie{}, the output is consistent), the
-infrastructure discards the corresponding input. Otherwise, it
-considers the input as potentially fault-revealing; hence interesting
-for human inspection. If fuzzing is selected, new inputs are obtained
-from a given input using some off-the-shelf fuzzer; the workflow is
-similar to that of no fuzzing. Several fuzzing methods have been
-proposed in the past, varying with respect to how new inputs are
-generated (\eg{}, coverage-based~\cite{afl,honggfuzz},
+is worth noting that we mined the repositories of JS engines and found
+a total of \Fix{XX} JS files associated with \Fix{YY} test suite.\Mar{show table with name and count of JS files}
+
+The bug-finding process works as follows.  Considering the case of a
+single input file, the oracle checks whether or not the output
+produced for that file is consistent across all engine
+implementations. In case the test passes in all engines or fails in
+all engines (\ie{}, the output is consistent), the infrastructure
+discards the corresponding input. Otherwise, it considers the input as
+potentially fault-revealing; hence interesting for human
+inspection. Considering the case fuzzing~\cite{fuzz-testing-history}
+is selected, new inputs are obtained from a given input using some
+off-the-shelf fuzzer\footnote{Several fuzzing methods have been proposed in
+the past, varying with respect to how new inputs are generated (\eg{},
+coverage-based~\cite{afl,honggfuzz},
 grammar-based~\cite{grammarinator,jsfunfuzz}, and
-random-based~\cite{radamsa}). \Mar{which ones we covered? why is this
-  relevant?}
+random-based~\cite{radamsa}).}. The workflow is similar to that of no
+fuzzing. In this case, however, multiple warnings can be produced for
+a given seed input.
 
@@
 groups, reflecting their likelihood to manifest a real bug. The HI
-group includes those inputs that manifest anomaly directly by the test
-(or its close neighborhood) as opposed to anomaly in some JS
-function. The rationale is that the test was able to execute to
-completion without violating any internal checks of the API, but
-failed to satisfy some check of the test. The LO group, in contrast,
-includes those cases where the anomaly was observed executing some JS
-function. We found that engine implementations often check
-pre-conditions of API functions differently, leading to premature
-failures. Most of the inputs in this category failed to satisfy the
-pre-condition check of some, but not all engines. Although we did find
-real bugs from warnings manifested in this category, the proportion is
-much lower compared to the HI category--only 12\% of the reals bugs we
-found originated from the LO category.\Mar{can we detect dups mining
-  issue trackers?}
-
-\Mar{show real examples of HI and LO and provide the
-  rationale for such classification.}
-
-%% selects randomly one of the inputs to fuzz with a
-%% given tool, say the black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration produces a new
-%% file. For grammar-agnostic fuzzers, like Radamsa, the infrastructure
-%% can discard syntactically invalid inputs using an external parser for
-%% the input language; semantically invalid inputs can be prevented with
-%% with linters. Once the input is found to be likely valid, the
-%% infrastructure invokes the oracle to check correctness.
-
-% \section{Related Work}
-% Differential testing with fuzzing can improve the quality of programs
-% Yang et al. \cite{yang-2011-finding}
-
-%% \Mar{rule of thumb: explain the
-%%   contribution/novelty, then results achieved, and then how it relates
-%% with our proposal.}
-%% \Mar{this is not clear$\rightarrow$}Yang et al. \cite{yang-2011-finding} proposed CSmith\footnote{\url{http://embed.cs.utah.edu/csmith/}}, a grammar-fuzzer 
-%% of C programs to generate invalid entries\Fix{the goal of a
-%%    fuzzer is to generate valid inputs/entries. this is strange}\MAB{the
-%%   goal is to generate valid programs without undefined behavior to
-%%   facilitate differential testing} and
-%% find bugs in several C compilers\Fix{it is strange that you don't mention differential
-%%   testing, which is central in CSmith, and the use of LLVM and GCC as
-%%   oracles.}.\Mar{this is just listing fuzzers. don't do this. try to
-%%   follow rule of thumb above.}Similar fuzzers involving grammar and rules are found in Holler et al. \cite{holler-2012-fuzzing} 
-%% that exposes the LangFuzz to generate entries based in code fragments 
-%% (language grammar, sample code, test suite) and the tool Mozilla 
-%% Funfuzz\footnote{\url{https://github.com/MozillaSecurity/funfuzz}}
-%% that implements a fuzzer based on JavaScript language to improve the 
-%% testing for SpiderMonkey engine, the interpreter of Mozilla Firefox.
-%% \Fix{...}
+group includes those inputs where execution manifests anomaly in the
+test code (or its close neighborhood) as opposed to some internal JS
+function. The rationale is that the test in this group executed
+without violating any internal checks of the API.
+The LO group, in contrast, includes those cases where the anomaly
+was observed executing some JS function. We found that engine
+implementations often check pre-conditions of API functions
+differently, leading to premature failures. Although we did find real bugs from warnings manifested
+in this category, the proportion is much lower compared to the HI
+category--only 12\% of the reals bugs we found originated from the LO
+category. \Mar{show real examples of HI and LO and provide the
+  rationale for such classification.} \Mar{can we detect dups mining issue trackers?}
 
@@
 
-The workflow described in Section~\ref{sec:design} is currently
-functional. This section shows preliminary results obtained with our
-infrastructure providing some evidence that finding bugs in JS runtime
-engines with differential testing is promising. Table~\ref{tab:bugs} shows the list of bugs we
-reported on issue trackers of different engines in the period of 42 days. For example, bug \# 6 was manifested by the JS code \CodeIn{var
-  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
-  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
-function that returns a primitive value identifying the target
-object~\cite{valueof}. That function returns an empty string in the
-original version of this code. The modified version of the code
-returns a string representation of a null character (called
-\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
-is equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
-that converts a string to a number, otherwise the operation returns NaN 
-(Not a Number)\cite{unary-plus}. For this case, Chakra evaluates the unary
-plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
-expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.
-
-So far, ten of the bugs we reported
+This section shows results obtained under our
+infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
+reported on issue trackers of different engines in the period of 42
+days. So far, ten of the bugs we reported
 were confirmed, two of which were fixed. One bug report we
@@
 
+\vspace{1ex}\noindent\textbf{Bug \# 6.} The JS code \CodeIn{var a = \{valueOf:~function()\{return
+  ``\textbackslash{}x00''\}\} assert(+a === 0)\}} 
+manifested a bug in the \js{} engine Chakra.  The object
+property \CodeIn{valueOf} stores a function that returns a primitive
+value identifying the target object~\cite{valueof}. The original
+version of this code returns an empty string whereas the version of
+the code modified by the Radamsa fuzzer~\cite{radamsa} returns a string
+representation of a null character (called \CodeIn{NUL} in ascii). The
+unary plus expression ``\CodeIn{+a}", appearing in the assertion, is
+equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
+that converts a string to a number, otherwise the operation returns
+NaN (Not a Number)\cite{unary-plus}. For this case, Chakra evaluates
+the unary plus to NaN as expected, as the null character cannot be
+converted. As result, the test fails as expected. Chakra, in contrast,
+incorrectly converts the string to zero, making the test to pass. All
+other engines fail on this test. As Table~\ref{tab:bugs} shows, the
+Chakra team fixed the issue soon after we reported the problem.
+
 %\section*{Acknowledgment}

### 2018-06-08 paper/paper.tex
adjusting figures

@@
 
-\title{Finding Bugs in JavaScript Engines with Differential
+\title{Finding Functional Bugs in JavaScript Engines with Differential
   Testing---an Experience Report}
@@
 %\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
-\begin{figure}[h]
+\begin{figure}[t]
   \centering
-  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
+%  \includegraphics[trim=20 350 200
+%    0,clip,width=0.35\textwidth]{google-awards-workflow}
+  \includegraphics[trim=0 250 0 0,clip,width=0.5\textwidth]{google-awards-workflow}  
   \caption{\label{fig:workflow}Infrastructure.}
@@
 Figure~\ref{fig:workflow} illustrates the workflow of the
-infrastructure we used in this study. Arrowed lines indicate control
-flow (dashed) and data flow (filled); lines with no arrow denote
-encapsulation. The bug-finding process takes on input JS files
-originating from the regression test suites of various JS engines. It
-is worth noting that we mined the repositories of JS engines and found
-a total of \Fix{XX} JS files associated with \Fix{YY} test suite.\Mar{show table with name and count of JS files}
+infrastructure we used in this study. Boxes denote encapsulation,
+arrowed lines indicate control flow (dashed) and data flow (filled),
+and the cyclic icons denote repetition. In this case, it indicates
+that each test file will be proceseed in separate and, if fuzzing is
+selected, a single file can be processed multiple times--one for each
+of its fuzzed variants. The bug-finding process takes on input JS
+files from regression test suites of various JS
+engines. Table~\ref{tab:test-suites} shows the JS sources we mined
+from online repositories of various open-source engines. Overall, we
+found a total of \Fix{XX} JS files.
 
-The bug-finding process works as follows.  Considering the case of a
-single input file, the oracle checks whether or not the output
+\begin{table}[h]
+  \centering
+  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
+  \begin{tabular}{ccc}
+    \toprule
+    TestSuite & Source & \# JS files \\
+    \midrule
+    \Fix{duktape} & - & - \\
+    \Fix{jerryjs} & - & - \\
+    \Fix{jsi} & - & - \\
+    \Fix{tiny} & - & - \\
+    \Fix{mozilla} & - & - \\
+    v8.test.benchmarks.data & - & - \\
+    webkit.jstests.es6 & - & - \\
+    webkit.jstests.microbenchmarks & - & - \\
+   \bottomrule     
+  \end{tabular}
+\end{table}
+
+The bug-finding process works as follows.  Considering the case
+fuzzing is not selected, as illustrated in the inner box at the bottom
+of the figure, the oracle checks whether or not the output
 produced for that file is consistent across all engine
@@
 potentially fault-revealing; hence interesting for human
-inspection. Considering the case fuzzing~\cite{fuzz-testing-history}
+inspection. Considering the case where fuzzing~\cite{fuzz-testing-history}
 is selected, new inputs are obtained from a given input using some
@@
 implementations often check pre-conditions of API functions
-differently, leading to premature failures. Although we did find real bugs from warnings manifested
-in this category, the proportion is much lower compared to the HI
-category--only 12\% of the reals bugs we found originated from the LO
+differently, leading to premature failures which manifest themselves as
+discrepancy in our infrastructure. Although we did find real bugs from
+warnings in the LO group, the proportion was much lower compared to the HI
+group--only 12\% of the reals bugs we found originated from the LO
 category. \Mar{show real examples of HI and LO and provide the
-  rationale for such classification.} \Mar{can we detect dups mining issue trackers?}
+  rationale for such classification.} \Mar{can we detect dups mining
+  issue trackers?}
 
-\section{Current Results}
-\label{sec:results}
-
-\newcommand{\checkm}{Y}
-\newcommand{\crossmark}{N}
-%\begin{wraptable}[20]{t}[0pt]{0.5\textwidth}
-
-\begin{table*}
+\begin{table*}[ht!]
   \vspace{-3ex}
@@
 
+\section{Methodology}
+\label{sec:methodology}
+
+\Fix{talk about students...}
+
+\subsection{Constants.}~We used the following engines in
+this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
+Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
+(WebKit)~\Fix{cite}. We selected these engines based on
+popularity. Note that they represent the main players in web
+technology. \Fix{versions}
+
+\subsection{Dependent and Independent variables.}
+
+Our dependent/effect variable is bug-finding ability. We consider a
+search successful only if it lends in a bug confirmed by developers or
+the affected engine. For the independent experimental variables, we
+considered: seeds, fuzzing strategy, and combination of fuzzers. In
+short, our experiment assesses the impact of these factors in
+bug-finding ability.
+
+Considering the seed factor, we want to observe how often fuzzing
+really helps. In the limit, all bugs could be found without extra
+inputs, \ie{}, executing the seed input on each engine and comparing
+their outcomes. Considering the fuzzing strategy, it is important to
+understand whether a particular strategy or implementation is
+prominent. Finally, \Fix{not sure if we should consider this
+  dimension...}
+
+\section{Bugs Found}
+\label{sec:results}
+
 %% Although there are many features yet to implement in our
@@
 
-This section shows results obtained under our
+This section shows results obtained with our
 infrastructure. Table~\ref{tab:bugs} shows the list of bugs we

### 2018-06-10 paper/paper.tex
pass on methodology

@@
 Figure~\ref{fig:workflow} illustrates the workflow of the
-infrastructure we used in this study. Boxes denote encapsulation,
-arrowed lines indicate control flow (dashed) and data flow (filled),
-and the cyclic icons denote repetition. In this case, it indicates
-that each test file will be proceseed in separate and, if fuzzing is
-selected, a single file can be processed multiple times--one for each
-of its fuzzed variants. The bug-finding process takes on input JS
-files from regression test suites of various JS
+infrastructure we used in this study. Boxes denote encapsulation;
+arrowed lines indicate control flow (dashed) and data flow
+(filled). The cyclic icons denote repetition--the leftmost cyclic icon
+indicates that each file in the input list will be analyzed in
+separate and the rightmost icon indicates that a single file will be
+processed multiple times in fuzzing mode. The bug-finding process
+takes on input JS files from regression test suites of various JS
 engines. Table~\ref{tab:test-suites} shows the JS sources we mined
@@
 fuzzing is not selected, as illustrated in the inner box at the bottom
-of the figure, the oracle checks whether or not the output
-produced for that file is consistent across all engine
-implementations. In case the test passes in all engines or fails in
-all engines (\ie{}, the output is consistent), the infrastructure
-discards the corresponding input. Otherwise, it considers the input as
-potentially fault-revealing; hence interesting for human
-inspection. Considering the case where fuzzing~\cite{fuzz-testing-history}
-is selected, new inputs are obtained from a given input using some
-off-the-shelf fuzzer\footnote{Several fuzzing methods have been proposed in
-the past, varying with respect to how new inputs are generated (\eg{},
+of the figure, the oracle checks whether or not the output produced
+for that file is consistent across all engine implementations. In case
+the test passes in all engines or fails in all engines (\ie{}, the
+output is consistent), the infrastructure discards the corresponding
+input (mark ....). Otherwise, it considers the input as potentially
+fault-revealing; hence interesting for human inspection. Considering
+the case where fuzzing~\cite{fuzz-testing-history} is selected, new
+inputs are obtained from a given input using some off-the-shelf
+fuzzer\footnote{Several fuzzing methods have been proposed in the
+  past, varying with respect to how new inputs are generated (\eg{},
   coverage-based~\cite{afl,honggfuzz},
   grammar-based~\cite{grammarinator,jsfunfuzz}, and
-random-based~\cite{radamsa}).}. The workflow is similar to that of no
-fuzzing. In this case, however, multiple warnings can be produced for
-a given seed input.
+  random-based~\cite{radamsa}).}. The workflow is similar to that of
+no fuzzing. In this case, however, multiple warnings can be produced
+for a given seed input.
 
@@
 (WebKit)~\Fix{cite}. We selected these engines based on
-popularity. Note that they represent the main players in web
-technology. \Fix{versions}
+popularity~\Fix{cite}. Considering fuzzing tools, we used
+representatives of the most popular approaches to fuzzing. For
+random-based fuzzing, we used Radamsa~\cite{radamsa}; for
+coverage-based fuzzing, we used
+\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
+generative-based fuzzing, we used
+\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
+be found elsewhere~\cite{fuzz-bart}.
 
@@
 
-Our dependent/effect variable is bug-finding ability. We consider a
-search successful only if it lends in a bug confirmed by developers or
-the affected engine. For the independent experimental variables, we
-considered: seeds, fuzzing strategy, and combination of fuzzers. In
-short, our experiment assesses the impact of these factors in
-bug-finding ability.
+The independent variable of our experiment is the fuzzing strategy as
+represented by various fuzzing tools. Our dependent variables are (i)
+the ratio of bugs found with fuzzing as opposed to no fuzzing and (ii)
+and the ratio of bugs found for each fuzzing strategy. We consider a
+search successful only if it lends in a bug confirmed by the
+developers of the affected engine. In short, our experiment assesses
+the impact of these factors in bug-finding ability.
 
-Considering the seed factor, we want to observe how often fuzzing
-really helps. In the limit, all bugs could be found without extra
-inputs, \ie{}, executing the seed input on each engine and comparing
-their outcomes. Considering the fuzzing strategy, it is important to
-understand whether a particular strategy or implementation is
-prominent. Finally, \Fix{not sure if we should consider this
-  dimension...}
+Considering the ratio of bugs found with fuzzing versus no fuzzing, we
+want to observe how often fuzzing really helps. In the limit, all bugs
+could be found without extra inputs, \ie{}, simply executing the seed
+inputs on each engine and comparing their outcomes. Recall that we
+mined test suites from a variety of sources. Considering the fuzzing
+strategy, it is important to understand whether a fuzzing strategy is
+particularly prominent.
 

### 2018-06-13 paper/paper.tex
pass on intro

@@
 
-\title{Finding Functional Bugs in JavaScript Engines with Differential
-  Testing---an Experience Report}
+\title{Should I Fuzz my Inputs or Improve my Test Suite? Lessons from
+  Differential Testing Runtime Engines.}
 
@@
 \begin{abstract}
+Differential testing has shown to be a successful approach to finding
+bugs in compilers and runtime engines. This paper assesses the impact
+that the fuzzing strategy and the test suites have in bug-finging
+ability. We focused on JavaScript and WebAssembly runtime
+engines. \Fix{...}
 \end{abstract}
@@
 
-JavaScript (\js{}) is one of the most popular programming languages of
-today~\cite{business-insider,stackify}. The \js{} specification
-changes relatively frequently to accommodate the pressing demands of
-the community. For example, the JS specification went through a severe
-change recently called by the name of ECMAScript6
-(ES6)~\cite{es6-features}.  These changes often entail sensible
-changes in engine implementations~\cite{kangax} that could lead to
-errors, including regressions. Automated techniques can help finding
-bugs, but the lack of executable specifications limits their ability
-to detect errors not manifested by universal oracles.
+JavaScript (\js{}) is one of the most popular programming languages
+for the web today~\cite{business-insider,stackify}. The interest of
+the community in the JS ecossystem incentivizes improvements both in
+the language and their runtime engine implementations. It is natural
+to expect that such improvements will entail sensible changes in
+engine implementations~\cite{kangax} that could lead to
+errors. Finding bugs on JS engines is therefore and important
+problem. Automated techniques, such as Fuzz Testing~\cite{fuzz-bart},
+have shown successful at finding universal errors, such as memory
+errors~\cite{libfuzzer-tutorial}. However, they don't address the
+problem of finding functional errors that could arise when an engine
+does not adhere to the specification.
 
 This paper reports on a study to find those kinds of bugs in
-JavaScript engines. The goal of the study is to improve quality of
-existing \js{} engines by improving the bug-finding process. We used
-differential testing~\cite{Brumley-etal-ss07}, a technique that has
-been applied in a variety of
+JavaScript engines.\Mar{revise...a study answer questions? the
+  statement is more propositive.} The goal of the study is to improve
+quality of existing \js{} engines by improving the bug-finding
+process. We used differential testing~\cite{Brumley-etal-ss07}, a
+technique that has been applied in a variety of
 contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
@@
 diversity across system's implementations to detect anomalous
-behavior. \Mar{this needs work$\rightarrow$}
-\Fix{but it has not been thoroughly explored to find functional bugs in JS
-engines. The closest work was done by Patra and
-Pradel~\cite{patra2016learning}, where they evaluated their proposed
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies. This project aims at building and evaluating an
-infrastructure for differential testing of runtime engines, such as
-the JS engine or WebAssembly's. The sensible parts of the
-infrastructure are the checks of input validity (as to reduce
+behavior. \Mar{this needs work$\rightarrow$} \Fix{but it has not been
+  thoroughly explored to find functional bugs in JS engines. The
+  closest work was done by Patra and Pradel~\cite{patra2016learning},
+  where they evaluated their proposed language-agnostic fuzzer to find
+  cross-browser HTML+JS discrepancies. This project aims at building
+  and evaluating an infrastructure for differential testing of runtime
+  engines, such as the JS engine or WebAssembly's. The sensible parts
+  of the infrastructure are the checks of input validity (as to reduce
   waste/cost) and output correctness (as to reduce false positives).}
@@
 
-\begin{table*}[ht!]
+\begin{table*}[h!]
   \vspace{-3ex}
@@
 
-\Fix{talk about students...}
+The goal of this study is to assess the impact of fuzzing in finding
+bugs with differential testing.
 
@@
 representatives of the most popular approaches to fuzzing. For
-random-based fuzzing, we used Radamsa~\cite{radamsa}; for
-coverage-based fuzzing, we used
+random-based fuzzing we used Radamsa~\cite{radamsa}; for
+coverage-based fuzzing we used
 \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-generative-based fuzzing, we used
+generative-based fuzzing we used
 \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
@@
 The independent variable of our experiment is the fuzzing strategy as
-represented by various fuzzing tools. Our dependent variables are (i)
-the ratio of bugs found with fuzzing as opposed to no fuzzing and (ii)
-and the ratio of bugs found for each fuzzing strategy. We consider a
+implemented by various fuzzing tools. Our dependent variables are (i)
+the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
+the ratio of bugs found with each fuzzing strategy. We consider a
 search successful only if it lends in a bug confirmed by the
-developers of the affected engine. In short, our experiment assesses
-the impact of these factors in bug-finding ability.
-
-Considering the ratio of bugs found with fuzzing versus no fuzzing, we
-want to observe how often fuzzing really helps. In the limit, all bugs
+developers of the affected engine.  The rationale for considering the
+ratio of bugs found with fuzzing versus no fuzzing is to observe how
+often fuzzing really helps in this scenario. In the limit, all bugs
 could be found without extra inputs, \ie{}, simply executing the seed
 inputs on each engine and comparing their outcomes. Recall that we
-mined test suites from a variety of sources. Considering the fuzzing
-strategy, it is important to understand whether a fuzzing strategy is
-particularly prominent.
+mined test suites from a variety of sources. The rationale for
+considering the fuzzing strategy is to understand to which extent each
+strategy--as implemented by representative tools--helps in this
+context.
 
@@
 
+\Mar{justify why we discuss these bugs} \Mar{discuss other bugs}
+
 \vspace{1ex}\noindent\textbf{Bug \# 6.} The JS code \CodeIn{var a = \{valueOf:~function()\{return
@@
 
+\section{Results}
+
+\subsection{Fuzzing versus No Fuzzing}
+
+\subsection{Fuzzing Strategy}
+
+\section{Related Work}
+
+RFC-Directed Differential Testing of Certificate Validation in SSL/TLS Implementations...[ICSE18]
+
 %\section*{Acknowledgment}

### 2018-06-28 paper/paper.tex
add seeds discussion and grammar-based fuzzers section (wip)

@@
 takes on input JS files from regression test suites of various JS
-engines. Table~\ref{tab:test-suites} shows the JS sources we mined
+engines.
+
+\Igor{
+\subsection{Populating seed files.}~This section describes 
+how we found valid javascript files based on 
+existing sources on the open-source repositories.
+Originally, we mined JS engines repositories that we 
+support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) and 
+we found a total of \Fix{XX} files of regression suites and 
+benchmarks testing involving javascript files.
+Latelly, we need to increase our input seeds through existing
+open-sources projects that involves javascript engines.
+We mined repositories from GitHub based on these requirements:
+\begin{itemize}
+  \item The project must be an open-source project and at least 1K stars from community.
+  \item The repository must have JavaScript tests included.
+  \item The tests should be plug-and-play and/or easy integration.
+\end{itemize}
+
+We wrote a query to mine these repositories on GitHub
+\CodeIn{\url{https://api.github.com/search/repositories?q=javascript-engine&sort=stars&order=desc}}\Fix{wip}
+and we follow the requirements ignoring invalid projects.
+\Fix{discuss wip}
+
+Table~\ref{tab:test-suites} shows the JS sources we mined
 from online repositories of various open-source engines. Overall, we
-found a total of \Fix{XX} JS files.
+found a total of \Fix{30K} JS files.
+}
+\Igor{
+\begin{itemize}
+  \item discuss about changes in seeds for run in our infraestructure (wip)
+  \item discuss about generating new files via fuzzers grammar-based (wip)
+  \item discuss about mutation fuzzers (wip)
+\end{itemize}
+}
 
@@
     \midrule
-    \Fix{duktape} & - & - \\
-    \Fix{jerryjs} & - & - \\
-    \Fix{jsi} & - & - \\
-    \Fix{tiny} & - & - \\
+    \Fix{duktape} & - & 997 \\
+    \Fix{jerryjs} & - & 1.803 \\
+    \Fix{jsi} & - & 99 \\
+    \Fix{tiny} & - & 44 \\
     \Fix{mozilla} & - & - \\
-    v8.test.benchmarks.data & - & - \\
-    webkit.jstests.es6 & - & - \\
-    webkit.jstests.microbenchmarks & - & - \\
+    v8.test.benchmarks.data & - & 64 \\
+    webkit.jstests.es6 & - & 605 \\
+    webkit.jstests.microbenchmarks & - & 426 \\
    \bottomrule     
@@
     \midrule    
-    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
-    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
-    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
+    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
     4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
     5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
-    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
     7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
@@
     \midrule    
-    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
+    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
     \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                         &                        &        &
@@
     \midrule    
-    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
+    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
     12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
-    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
-    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
     15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
     16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
-    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
+    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
+    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}\\
    \bottomrule     
@@
 \subsection{Constants.}~We used the following engines in
-this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
-Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
-(WebKit)~\Fix{cite}. We selected these engines based on
+this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
+Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
+(WebKit)~\cite{jsc2018repo}. We selected these engines based on
 popularity~\Fix{cite}. Considering fuzzing tools, we used
@@
 context.
+
+\Igor{
+\subsection{Grammar-based Fuzzers}
+Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
+Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
+we try to integrate several grammar-based fuzzers, for example 
+Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
+and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
+after several runs it was observed that this approach was ineffective
+due the amount of invalid files and/or files without discrepancies. For example, if we ran 
+Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
+\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
+are js files that shows undefined variables and due the differential testing in our environment
+all engines will raise a SyntaxError and this approach was not relevant to our experiment.
+}
 

### 2018-07-03 paper/paper.tex
minor fix
updating paper (wip)

--- 2018-06-13 paper/paper.tex
@@
 from online repositories of various open-source engines. Overall, we
-found a total of \Fix{XX} JS files.
+found a total of almost 36,5K JS files.
 
@@
     \midrule
-    \Fix{duktape} & - & - \\
-    \Fix{jerryjs} & - & - \\
-    \Fix{jsi} & - & - \\
-    \Fix{tiny} & - & - \\
-    \Fix{mozilla} & - & - \\
-    v8.test.benchmarks.data & - & - \\
-    webkit.jstests.es6 & - & - \\
-    webkit.jstests.microbenchmarks & - & - \\
+    Duktape & \href{https://github.com/svaarala/duktape}{GitHub} & 997 \\
+    JerryJS & \href{https://github.com/jerryscript-project/jerryscript}{GitHub} & 1.803 \\
+    JSI & \href{https://github.com/technosaurus/jsish}{GitHub} & 99 \\
+    Tiny-js & \href{https://github.com/gfwilliams/tiny-js}{GitHub} & 44 \\
+    Mozilla & \href{-}{-} & 32414 \\
+    V8.test.benchmarks.data & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 64 \\
+    WebKit.jstests.es6 & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 605 \\
+    WebKit.jstests.microbenchmarks & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 426 \\
    \bottomrule     
@@
   \centering
-  \caption{List of bug reports issued by our team from April 12 to May
+  \caption{List of bug reports issued by our team
     24, 2018.}
   \label{tab:bugs}
-  \begin{tabular}{cccccc}
+  \begin{tabular}{cccccccc}
     \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
+    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
     \midrule    
-    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
-    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
-    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
-    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
-    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
-    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
+    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
+    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
+    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
     7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
+    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
     \\
     \midrule
-    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
+    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                         &  &                       &
-    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
+    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
     \midrule    
-    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
+    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
     \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\
                         &                        &        &
     JavascriptCore & New &
-    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
+    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
     \\
     \midrule    
-    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
-    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
-    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
-    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
-    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
-    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
-    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
+    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
+    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
+    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
+    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
+    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
+    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
+    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
    \bottomrule     
@@
 The goal of this study is to assess the impact of fuzzing in finding
-bugs with differential testing.
+bugs with differential testing. In this section, we discuss
+the methodology applied to prepare our environment for the experiments.
+The dependents and independents variables
+will be discuss in Section~\ref{sec:results}.
 
-\subsection{Constants.}~We used the following engines in
-this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
-Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
-(WebKit)~\Fix{cite}. We selected these engines based on
+\subsection{Engines.}~We used the following engines in
+this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
+Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
+(WebKit)~\cite{jsc2018repo}. We selected these engines based on
 popularity~\Fix{cite}. Considering fuzzing tools, we used
@@
 
-\subsection{Dependent and Independent variables.}
+\subsection{Seeds.}~This section describes 
+how we found valid javascript files based on 
+existing sources on the open-source repositories.
+Originally, we looking JS engines repositories that we 
+support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) getting
+their regression suites and benchmarks testing involving javascript files.
+In addition, we mined repositories from GitHub based on the following criteria:
+\begin{itemize}
+  \item The project must be an open-source project and at least 1K stars from community.
+  \item The repository must have JavaScript tests included.
+  \item The tests should be plug-and-play and/or easy integration.
+\end{itemize}
 
-The independent variable of our experiment is the fuzzing strategy as
-implemented by various fuzzing tools. Our dependent variables are (i)
-the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
-the ratio of bugs found with each fuzzing strategy. We consider a
-search successful only if it lends in a bug confirmed by the
-developers of the affected engine.  The rationale for considering the
-ratio of bugs found with fuzzing versus no fuzzing is to observe how
-often fuzzing really helps in this scenario. In the limit, all bugs
-could be found without extra inputs, \ie{}, simply executing the seed
-inputs on each engine and comparing their outcomes. Recall that we
-mined test suites from a variety of sources. The rationale for
-considering the fuzzing strategy is to understand to which extent each
-strategy--as implemented by representative tools--helps in this
-context.
+We focused on JavaScript Engines for its capacity to testing the
+interpreter with pure JS files. The Figure~\ref{fig:query} 
+illustrates the query to the Github API as an HTTP request, the result 
+is sorted in descending order of stars. Initially, we obtained
+a total of \Fix{XX} projects. Manually, we follow the criteria to exclude 
+invalid projects and we obtained a total of \Fix{XX} repositories.
+
+\begin{figure}
+  \centering
+  \begin{lstlisting}
+https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
+  \end{lstlisting}
+  \caption{\label{fig:query}
+  Query to the GitHub API for JS engines projects that contains at least 1K of stars from community.\Fix{fix query}
+  }
+\end{figure}
+
+Due the variance of engines implementations, many projects uses distinct frameworks for testing 
+and require external libs to run their testing suites. We try to use only the JS file with minor fixes
+to support our environment. These fixes are composed by an assertion function that throws an Error that
+we can capture by our infraestruture. 
+% For example to run the JerryScript tests it was necessary 
+% use the unit-test package to run it, but with our changes we added the assertion
+% does not have an assertion in the test file
+% \Fix{add code to explain}
+
+\subsection{Fuzzers}
+Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
+Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
+we try to integrate several grammar-based fuzzers, for example 
+Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
+and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
+after several runs it was observed that this approach was ineffective
+due the amount of invalid files and/or files without discrepancies. For example, if we ran 
+Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
+\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
+are js files that shows undefined variables and due the differential testing in our environment
+all engines will raise a SyntaxError and this approach was not relevant to our experiment.
 
 \section{Bugs Found}
-\label{sec:results}
+\label{sec:bugs}
 
@@
 found were duplicates and were not reported. Finally, it is
-worth noting that 7 of the 17 JS files that manifested
+worth noting that 8 of the 19 JS files that manifested
 discrepancies were \emph{not} produced with fuzzing (column
@@
 \section{Results}
+\label{sec:results}
+
+\Igor{
+  In this section we discuss our findings to reach
+  bugs in JS engines. Our experiments shows that fuzzing existents files
+  still effective over the inputs without fuzzing.
+}
+
+\subsection{Dependent and Independent variables.}
+
+The independent variable of our experiment is the fuzzing strategy as
+implemented by various fuzzing tools. Our dependent variables are (i)
+the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
+the ratio of bugs found with each fuzzing strategy. We consider a
+search successful only if it lends in a bug confirmed by the
+developers of the affected engine.  The rationale for considering the
+ratio of bugs found with fuzzing versus no fuzzing is to observe how
+often fuzzing really helps in this scenario. In the limit, all bugs
+could be found without extra inputs, \ie{}, simply executing the seed
+inputs on each engine and comparing their outcomes. Recall that we
+mined test suites from a variety of sources. The rationale for
+considering the fuzzing strategy is to understand to which extent each
+strategy--as implemented by representative tools--helps in this
+context.
 
 \subsection{Fuzzing versus No Fuzzing}
+\Fix{nao entendi muito sobre essa subsection... 
+seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
+\Igor{
+  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
+  o sistema robusto nao significa que esta livre de bugs, ao contrario,
+  estamos testando-o com simples entradas a partir de testes de regressao 
+  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
+  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
+  existentes em projetos open-sources eh uma maneira de
+  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
+  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.
+
+  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
+  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
+  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
+  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
+  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
+  \Fix{discuss}
+}
 
 \subsection{Fuzzing Strategy}
+\Igor{
+  Para realizar nossos experimentos, tivemos que decidir qual as 
+  melhores abordagens para aumentar a efetividade dos fuzzers.
+  Os fuzzers mutacionais se mostraram mais eficientes em relacao
+  aos fuzzers geracionais, entao focamos neste ponto.
+  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
+  default para realizar a mutacao em arquivos existentes.
+  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
+  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
+  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
+  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
+  radamsa, gerando arquivos mais relevantes.
+  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
+  é um arquivo de teste relevante, seguindo estes requisitos:
+  \begin{itemize}
+    \item it contains only unicode text
+    \item it is parseable (i.e., it is structurally well-formed)
+    \item it does not contain engine-specific functions  
+    \item it does not empty
+  \end{itemize}
+
+}
 

### 2018-07-03 paper/paper.tex
pass on structure

@@
 
-\title{Should I Fuzz my Inputs or Improve my Test Suite? Lessons from
-  Differential Testing Runtime Engines.}
+%Should I Fuzz my Inputs or Improve my Tests? 
+\title{Lessons Learned from Differential Testing JS Engines}
 
@@
 
+%% page numbering -M
+\thispagestyle{plain}
+\pagestyle{plain}
+
+%% JavaScript (\js{}) is a popular programming language for the
+%% web. Finding errors in JS runtime engines is an important problem.
 \begin{abstract}
-Differential testing has shown to be a successful approach to finding
-bugs in compilers and runtime engines. This paper assesses the impact
-that the fuzzing strategy and the test suites have in bug-finging
-ability. We focused on JavaScript and WebAssembly runtime
-engines. \Fix{...}
+This paper assesses the impact of Differential Testing (DT) to find
+functional bugs in JS engines. This is an important problem given the
+importance of JS today. DT has shown successful in finding bugs in
+compilers and runtimes, but has not been thoroughly explored in this
+important domain. Our study \Fix{...}
 \end{abstract}
@@
 
-JavaScript (\js{}) is one of the most popular programming languages
-for the web today~\cite{business-insider,stackify}. The interest of
-the community in the JS ecossystem incentivizes improvements both in
-the language and their runtime engine implementations. It is natural
-to expect that such improvements will entail sensible changes in
-engine implementations~\cite{kangax} that could lead to
-errors. Finding bugs on JS engines is therefore and important
-problem. Automated techniques, such as Fuzz Testing~\cite{fuzz-bart},
-have shown successful at finding universal errors, such as memory
-errors~\cite{libfuzzer-tutorial}. However, they don't address the
-problem of finding functional errors that could arise when an engine
-does not adhere to the specification.
+JavaScript (\js{}) is today one of the most popular programming
+languages for the web~\cite{business-insider,stackify}. The interest
+of the community for the language encourages constant improvements in
+its specification and implementations. It is natural to expect that
+such improvements will entail sensible changes in runtime
+engines~\cite{kangax}; changes that could lead to errors. Finding bugs
+on JS engines is an important problem. In this paper, we are
+particularly interested in finding functional (non-crash) bugs.
 
-This paper reports on a study to find those kinds of bugs in
-JavaScript engines.\Mar{revise...a study answer questions? the
-  statement is more propositive.} The goal of the study is to improve
-quality of existing \js{} engines by improving the bug-finding
-process. We used differential testing~\cite{Brumley-etal-ss07}, a
-technique that has been applied in a variety of
-contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
-to address the oracle problem. Differential testing leverages the
-diversity across system's implementations to detect anomalous
-behavior. \Mar{this needs work$\rightarrow$} \Fix{but it has not been
+Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
+approach that has been applied in a variety of contexts to find
+functional
+bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
+automates test generation in scenarios where multiple implementations
+of a system exist. It leverages the diversity across system's
+implementations to detect anomalous behavior. This paper reports the
+results of a study we conducted to assess the impact of DT in finding
+bugs on \js{} engines.
+
+\Mar{this needs work$\rightarrow$} \Fix{but it has not been
   thoroughly explored to find functional bugs in JS engines. The
@@
 arrowed lines indicate control flow (dashed) and data flow
-(filled). The cyclic icons denote repetition--the leftmost cyclic icon
+(filled). The cycle icons denote repetition--the leftmost icon
 indicates that each file in the input list will be analyzed in
-separate and the rightmost icon indicates that a single file will be
+separate whereas the rightmost icon indicates that a single file will be
 processed multiple times in fuzzing mode. The bug-finding process
 takes on input JS files from regression test suites of various JS
-engines. Table~\ref{tab:test-suites} shows the JS sources we mined
-from online repositories of various open-source engines. Overall, we
-found a total of almost 36,5K JS files.
-
-\begin{table}[h]
-  \centering
-  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
-  \begin{tabular}{ccc}
-    \toprule
-    TestSuite & Source & \# JS files \\
-    \midrule
-    Duktape & \href{https://github.com/svaarala/duktape}{GitHub} & 997 \\
-    JerryJS & \href{https://github.com/jerryscript-project/jerryscript}{GitHub} & 1.803 \\
-    JSI & \href{https://github.com/technosaurus/jsish}{GitHub} & 99 \\
-    Tiny-js & \href{https://github.com/gfwilliams/tiny-js}{GitHub} & 44 \\
-    Mozilla & \href{-}{-} & 32414 \\
-    V8.test.benchmarks.data & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 64 \\
-    WebKit.jstests.es6 & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 605 \\
-    WebKit.jstests.microbenchmarks & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 426 \\
-   \bottomrule     
-  \end{tabular}
-\end{table}
+engines.
 
@@
 groups, reflecting their likelihood to manifest a real bug. The HI
-group includes those inputs where execution manifests anomaly in the
-test code (or its close neighborhood) as opposed to some internal JS
-function. The rationale is that the test in this group executed
-without violating any internal checks of the API.
-The LO group, in contrast, includes those cases where the anomaly
-was observed executing some JS function. We found that engine
-implementations often check pre-conditions of API functions
-differently, leading to premature failures which manifest themselves as
-discrepancy in our infrastructure. Although we did find real bugs from
-warnings in the LO group, the proportion was much lower compared to the HI
-group--only 12\% of the reals bugs we found originated from the LO
-category. \Mar{show real examples of HI and LO and provide the
-  rationale for such classification.} \Mar{can we detect dups mining
-  issue trackers?}
+group includes those inputs where execution manifests anomaly during
+the execution of the test code or its close neighborhood\Comment{ as
+  opposed to that of some internal JS function}. The rationale is that
+the test in this group executed without violating any internal checks
+of the API.  The LO group, in contrast, includes those cases where the
+anomaly was observed during the execution of some API function. We
+found that engine implementations often check pre-conditions of API
+functions differently. It can happen, for example, that one engine
+enforces a pre-condition that another engine does not. In those cases,
+our infrastructure would observe a discrepancy that is more likely to
+be associated with a bug in the (fuzzed) test; not the code. Although
+we did find real bugs from warnings in the LO group, the proportion
+was much lower compared to the HI group--only 12\% of the reals bugs
+we found originated from the LO category. \Mar{show real examples of
+  HI and LO and provide the rationale for such classification.}
+\Mar{can we detect dups mining issue trackers?}
 
@@
 
-\section{Methodology}
+\section{Objects of Study}
 \label{sec:methodology}
 
-The goal of this study is to assess the impact of fuzzing in finding
-bugs with differential testing. In this section, we discuss
-the methodology applied to prepare our environment for the experiments.
-The dependents and independents variables
-will be discuss in Section~\ref{sec:results}.
+This section discusses the objects we used in our study.
 
-\subsection{Engines.}~We used the following engines in
-this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
-Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
-(WebKit)~\cite{jsc2018repo}. We selected these engines based on
-popularity~\Fix{cite}. Considering fuzzing tools, we used
-representatives of the most popular approaches to fuzzing. For
+%% methodology we used in our study.  The
+%% dependent and independent variables will be discuss in
+%% Section~\ref{sec:results}.
+
+\subsection{Engines}
+\label{sec:methodology:engines}~We selected the most popular JS
+engines on the web~\Fix{cite} to focus our bug-finding efforts, namely
+Microsoft's Chakra~\cite{chakra2018repo}, Google's
+v8~\cite{v82018repo}, Mozilla's
+SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
+(WebKit)~\cite{jsc2018repo}.
+
+\subsection{Seed JS files}~We considered in our study test suites
+associated with all four JS engines we analyzed
+(section~\ref{sec:methodology:engines}). In addition, we mined test
+suites from other repositories based on the following criteria:
+\begin{itemize}
+  \item The project must be an open-source project and at least 1K stars from community.
+  \item The repository must have JavaScript tests included.
+  \item The tests should be plug-and-play and/or easy
+    integration.\Mar{not clear what you mean}
+\end{itemize}
+
+Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
+used.\Mar{identify sources assoc. with the four analyzed engines.} The results of this query is sorted in descending order of
+stars. Initially, we obtained a total of \Fix{XX} projects. Manually,
+we follow the criteria to exclude invalid projects and we obtained a
+total of \Fix{XX} repositories. Table~\ref{tab:test-suites} shows the
+JS sources we considered. Overall, we found a total of \totfiles{} JS
+files.\Mar{Briefly explain these names}
+
+\begin{table}[h]
+  \centering
+  \caption{\label{tab:test-suites}Test Suites}
+  \begin{tabular}{ccr}
+    \toprule
+    TestSuite & Source & \# JS files \\
+    \midrule
+    Duktape & \cite{duktape} & 997 \\
+    JerryJS & \cite{jerryscript} & 1,803 \\
+    JSI & \cite{jsi} & 99 \\
+    Tiny-js & \cite{tinyjs} & 44 \\
+    Mozilla & \Fix{??} & 32,414 \\
+    V8.test.benchmarks.data & \Fix{??} & 64 \\
+    WebKit.jstests.es6 & \Fix{??} & 605 \\
+    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
+    \midrule
+     &  & 36,452 \\
+   \bottomrule     
+  \end{tabular}
+\end{table}
+
+\begin{figure}
+  \centering
+  \begin{lstlisting}
+https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
+  \end{lstlisting}
+  \caption{\label{fig:query}
+  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
+  }
+\end{figure}
+
+It is worth noting that many projects use distinct frameworks for
+testing and require external libraries to run their testing
+suites. For some projects, we made small changes in the testing
+infrastructure to be able to uniformly run the test in all
+engines.\Mar{not entirely clear what you did to support
+  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
+to support our environment. These fixes are composed by an assertion
+function that throws an Error that we can capture by our
+infraestruture.
+
+% For example to run the JerryScript tests it was necessary 
+% use the unit-test package to run it, but with our changes we added the assertion
+% does not have an assertion in the test file
+% \Fix{add code to explain}
+
+\subsection{Fuzzers}
+
+\Mar{revise...}~We used representatives of popular fuzzing approaches. For
 random-based fuzzing we used Radamsa~\cite{radamsa}; for
@@
 
-\subsection{Seeds.}~This section describes 
-how we found valid javascript files based on 
-existing sources on the open-source repositories.
-Originally, we looking JS engines repositories that we 
-support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) getting
-their regression suites and benchmarks testing involving javascript files.
-In addition, we mined repositories from GitHub based on the following criteria:
-\begin{itemize}
-  \item The project must be an open-source project and at least 1K stars from community.
-  \item The repository must have JavaScript tests included.
-  \item The tests should be plug-and-play and/or easy integration.
-\end{itemize}
-
-We focused on JavaScript Engines for its capacity to testing the
-interpreter with pure JS files. The Figure~\ref{fig:query} 
-illustrates the query to the Github API as an HTTP request, the result 
-is sorted in descending order of stars. Initially, we obtained
-a total of \Fix{XX} projects. Manually, we follow the criteria to exclude 
-invalid projects and we obtained a total of \Fix{XX} repositories.
-
-\begin{figure}
-  \centering
-  \begin{lstlisting}
-https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
-  \end{lstlisting}
-  \caption{\label{fig:query}
-  Query to the GitHub API for JS engines projects that contains at least 1K of stars from community.\Fix{fix query}
-  }
-\end{figure}
-
-Due the variance of engines implementations, many projects uses distinct frameworks for testing 
-and require external libs to run their testing suites. We try to use only the JS file with minor fixes
-to support our environment. These fixes are composed by an assertion function that throws an Error that
-we can capture by our infraestruture. 
-% For example to run the JerryScript tests it was necessary 
-% use the unit-test package to run it, but with our changes we added the assertion
-% does not have an assertion in the test file
-% \Fix{add code to explain}
-
-\subsection{Fuzzers}
 Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).

### 2018-07-05 paper/paper.tex
pass

@@
 
-Figure~\ref{fig:workflow} illustrates the workflow of the
-infrastructure we used in this study. Boxes denote encapsulation;
+Figure~\ref{fig:workflow} illustrates the infrastructure we used in
+this study.
+The bug-finding process
+takes on input JS files from regression test suites of various JS
+engines and generates warnings on output. Boxes in the figure denote encapsulation;
 arrowed lines indicate control flow (dashed) and data flow
@@
 indicates that each file in the input list will be analyzed in
-separate whereas the rightmost icon indicates that a single file will be
-processed multiple times in fuzzing mode. The bug-finding process
-takes on input JS files from regression test suites of various JS
-engines.
-
-The bug-finding process works as follows.  Considering the case
-fuzzing is not selected, as illustrated in the inner box at the bottom
+separate whereas the rightmost icon shows that a single file will be
+fuzzed multiple times. The bug-finding process works as follows.  Considering the case
+where fuzzing is not selected, as illustrated in the inner box at the bottom
 of the figure, the oracle checks whether or not the output produced
@@
 output is consistent), the infrastructure discards the corresponding
-input (mark ....). Otherwise, it considers the input as potentially
+input. Otherwise, it considers the input as potentially
 fault-revealing; hence interesting for human inspection. Considering
@@
 inputs are obtained from a given input using some off-the-shelf
-fuzzer\footnote{Several fuzzing methods have been proposed in the
+fuzzer. Several fuzzing methods have been proposed in the
   past, varying with respect to how new inputs are generated (\eg{},
@@
   grammar-based~\cite{grammarinator,jsfunfuzz}, and
-  random-based~\cite{radamsa}).}. The workflow is similar to that of
-no fuzzing. In this case, however, multiple warnings can be produced
+  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
+  fuzzers we selected. The workflow of the infrastructure with fuzzing
+  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
 for a given seed input.
@@
 To reduce the number of false alarms, we clustered warnings in two
-groups, reflecting their likelihood to manifest a real bug. The HI
-group includes those inputs where execution manifests anomaly during
-the execution of the test code or its close neighborhood\Comment{ as
+groups, reflecting their likelihood to manifest a real bug. Warnings
+in the HI group are associated with the cases when the anomaly has been
+detected during the execution of the test code or its close neighborhood\Comment{ as
   opposed to that of some internal JS function}. The rationale is that
 the test in this group executed without violating any internal checks
-of the API.  The LO group, in contrast, includes those cases where the
-anomaly was observed during the execution of some API function. We
-found that engine implementations often check pre-conditions of API
+of the API. In constrast, warnings in the LO group reflect the cases where the
+anomaly was observed during the execution of some standard JS
+function\Mar{is this correct? what are those?}. We
+found that different engines often check the pre-conditions of those
 functions differently. It can happen, for example, that one engine
-enforces a pre-condition that another engine does not. In those cases,
+enforces a pre-condition that another engine does not\Mar{why is that?
+that should not happen if the spec was fully documented and engines
+properly implemented those checks. Explain and give example.}. In those cases,
 our infrastructure would observe a discrepancy that is more likely to
@@
 we found originated from the LO category. \Mar{show real examples of
-  HI and LO and provide the rationale for such classification.}
+  HI and LO.}
 \Mar{can we detect dups mining issue trackers?}
@@
 Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
-used.\Mar{identify sources assoc. with the four analyzed engines.} The results of this query is sorted in descending order of
-stars. Initially, we obtained a total of \Fix{XX} projects. Manually,
-we follow the criteria to exclude invalid projects and we obtained a
-total of \Fix{XX} repositories. Table~\ref{tab:test-suites} shows the
-JS sources we considered. Overall, we found a total of \totfiles{} JS
-files.\Mar{Briefly explain these names}
+used to find projects with JS files\Mar{why the query is so specific?
+  as per ``q=javascript-engine''? Need to be consistent to what you
+  are saying an coherent to what you actually did.}. The query sorts
+results in descending order in the number of stars\Mar{sorting is only
+  relevant if you set a limit on the number of projects you will
+  analyze. What limit is that?}. The resulting list includes a total
+of \Fix{XX} projects. A total of \Fix{...}  projects remained after
+removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
+the JS sources we considered for each of these selected
+projects..\Mar{identify the sources assoc. with the four analyzed
+  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
+files.\Mar{Briefly explain these sources.}
 
-\begin{table}[h]
+\begin{figure}[h]
   \centering
-  \caption{\label{tab:test-suites}Test Suites}
+  \begin{lstlisting}
+https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
+  \end{lstlisting}
+  \caption{\label{fig:query}
+  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
+  }
+\end{figure}
+
+\begin{table}[t]
+  \centering
+  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
+      name (if possible) to facilitate reference in the paper. Use the
+  full path in the URL (citation) to indicate where one can find those
+  files.}}
   \begin{tabular}{ccr}
@@
 
-\begin{figure}
-  \centering
-  \begin{lstlisting}
-https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
-  \end{lstlisting}
-  \caption{\label{fig:query}
-  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
-  }
-\end{figure}
-
-It is worth noting that many projects use distinct frameworks for
+It is worth noting that some projects use distinct frameworks for
 testing and require external libraries to run their testing
-suites. For some projects, we made small changes in the testing
-infrastructure to be able to uniformly run the test in all
+suites. For these projects, we needed to make small changes in the testing
+infrastructure to be able to uniformly run tests in all
 engines.\Mar{not entirely clear what you did to support
@@
 \subsection{Fuzzers}
+\label{sec:objects:fuzzers}
 

### 2018-07-06 paper/paper.tex
explaining questions/dimensions

@@
 %Should I Fuzz my Inputs or Improve my Tests? 
-\title{Lessons Learned from Differential Testing JS Engines}
+\title{Differential Testing Runtime Engines--Lessons Learned from the
+  JavaScript Domain}
 
@@
 engines~\cite{kangax}; changes that could lead to errors. Finding bugs
-on JS engines is an important problem. In this paper, we are
-particularly interested in finding functional (non-crash) bugs.
+on JS engines is an important problem.
 
@@
 of a system exist. It leverages the diversity across system's
-implementations to detect anomalous behavior. This paper reports the
-results of a study we conducted to assess the impact of DT in finding
-bugs on \js{} engines.
+implementations to detect anomalous behavior.
+%% WHAT WE DID
+This paper reports the results of a study we conducted to assess the
+ability of DT to find bugs on \js{} engines.  We analyzed
+the impact of two orthogonal dimensions: test mining and fuzzing. The
+first dimension, test mining, considers the effect that \js{} test
+files mined from the repository of a given open-source engine have in
+detecting functional bugs in other engines. The second dimension,
+fuzzing, considers the impact of fuzzing the mined files in bug
+detection.
+%% WHAT WE FOUND
+To sum, we found that \Fix{...}
 
-\Mar{this needs work$\rightarrow$} \Fix{but it has not been
-  thoroughly explored to find functional bugs in JS engines. The
-  closest work was done by Patra and Pradel~\cite{patra2016learning},
-  where they evaluated their proposed language-agnostic fuzzer to find
-  cross-browser HTML+JS discrepancies. This project aims at building
-  and evaluating an infrastructure for differential testing of runtime
-  engines, such as the JS engine or WebAssembly's. The sensible parts
-  of the infrastructure are the checks of input validity (as to reduce
-  waste/cost) and output correctness (as to reduce false positives).}
+%% LIST OF CONTRIBUTIONS
+This paper makes the following contributions \Fix{...}
 
@@
 
-\begin{table*}[h!]
-  \vspace{-3ex}
-%  \scriptsize
-  \centering
-  \caption{List of bug reports issued by our team
-    24, 2018.}
-  \label{tab:bugs}
-  \begin{tabular}{cccccccc}
-    \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
-    \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
-    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
-    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
-    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
-    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
-    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
-    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
-    \\
-    \midrule
-    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
-                        &  &                       &
-    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
-    \midrule    
-    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
-    \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\
-                        &                        &        &
-    JavascriptCore & New &
-    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
-    \\
-    \midrule    
-    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
-    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
-    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
-    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
-    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
-    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
-    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
-    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
-    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
-   \bottomrule     
-  \end{tabular}
-\end{table*}
-
 \section{Objects of Study}
@@
 This section discusses the objects we used in our study.
-
-%% methodology we used in our study.  The
-%% dependent and independent variables will be discuss in
-%% Section~\ref{sec:results}.
 
@@
 
-\subsection{Seed JS files}~We considered in our study test suites
+\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
 associated with all four JS engines we analyzed
@@
 
+\section{Results}
+\label{sec:results}
+
+In this study, we analyzed the impact of two orthogonal dimensions in
+bug finding: test mining and fuzzing. The first dimension focuses on
+the impact of new inputs in bug finding whereas the second dimension
+focuses on the impact of variations of existing inputs in bug finding.
+
+\subsection{Test Mining}
+
+In this experiment, we ran all tests (see Section~\ref{sec:seeds})
+using our infrastructure in no-fuzzing mode. We inspected all warnings
+reported by our tool and, for those we found suspicious, we filed a
+bug report in the corresponding bug tracker.
+
+\Igor{  
+  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
+  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
+  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
+  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
+  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
+  \Fix{discuss}
+}
+
+%% \Fix{nao entendi muito sobre essa subsection... 
+%% seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
+%% \Igor{
+%%   Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
+%%   o sistema robusto nao significa que esta livre de bugs, ao contrario,
+%%   estamos testando-o com simples entradas a partir de testes de regressao 
+%%   de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
+%%   para novos testcases. Partindo disso, realizar fuzzer em arquivos 
+%%   existentes em projetos open-sources eh uma maneira de
+%%   aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
+%%   uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.
+
+\subsection{Fuzzing}
+
+The rationale for considering fuzzing as a dimension of study is to
+assess the extent to which changing existing inputs helps in finding
+new bugs. We measured this ability both in absolute terms and
+relatively to the number of bugs found with the seed inputs in
+no-fuzzing mode.
+
+\Igor{
+  Para realizar nossos experimentos, tivemos que decidir qual as 
+  melhores abordagens para aumentar a efetividade dos fuzzers.
+  Os fuzzers mutacionais se mostraram mais eficientes em relacao
+  aos fuzzers geracionais, entao focamos neste ponto.
+  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
+  default para realizar a mutacao em arquivos existentes.
+  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
+  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
+  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
+  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
+  radamsa, gerando arquivos mais relevantes.
+  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
+  é um arquivo de teste relevante, seguindo estes requisitos:
+  \begin{itemize}
+    \item it contains only unicode text
+    \item it is parseable (i.e., it is structurally well-formed)
+    \item it does not contain engine-specific functions  
+    \item it does not empty
+  \end{itemize}
+
+}
+
 \section{Bugs Found}
@@
 %% infrastructure,
+
+\begin{table*}[h!]
+  \vspace{-3ex}
+%  \scriptsize
+  \centering
+  \caption{List of bug reports issued by our team
+    24, 2018.}
+  \label{tab:bugs}
+  \begin{tabular}{cccccccc}
+    \toprule
+    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
+    \midrule    
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
+    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
+    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
+    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
+    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
+    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
+    \\
+    \midrule
+    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
+                        &  &                       &
+    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
+    \midrule    
+    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
+    \midrule    
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\
+                        &                        &        &
+    JavascriptCore & New &
+    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
+    \\
+    \midrule    
+    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
+    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
+    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
+    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
+    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
+    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
+    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
+   \bottomrule     
+  \end{tabular}
+\end{table*}
 
@@
 
-\section{Results}
-\label{sec:results}
+\section{Related Work}
 
-\Igor{
-  In this section we discuss our findings to reach
-  bugs in JS engines. Our experiments shows that fuzzing existents files
-  still effective over the inputs without fuzzing.
-}
-
-\subsection{Dependent and Independent variables.}
-
-The independent variable of our experiment is the fuzzing strategy as
-implemented by various fuzzing tools. Our dependent variables are (i)
-the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
-the ratio of bugs found with each fuzzing strategy. We consider a
-search successful only if it lends in a bug confirmed by the
-developers of the affected engine.  The rationale for considering the
-ratio of bugs found with fuzzing versus no fuzzing is to observe how
-often fuzzing really helps in this scenario. In the limit, all bugs
-could be found without extra inputs, \ie{}, simply executing the seed
-inputs on each engine and comparing their outcomes. Recall that we
-mined test suites from a variety of sources. The rationale for
-considering the fuzzing strategy is to understand to which extent each
-strategy--as implemented by representative tools--helps in this
-context.
-
-\subsection{Fuzzing versus No Fuzzing}
-\Fix{nao entendi muito sobre essa subsection... 
-seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
-\Igor{
-  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
-  o sistema robusto nao significa que esta livre de bugs, ao contrario,
-  estamos testando-o com simples entradas a partir de testes de regressao 
-  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
-  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
-  existentes em projetos open-sources eh uma maneira de
-  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
-  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.
-
-  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
-  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
-  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
-  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
-  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
-  \Fix{discuss}
-}
-
-\subsection{Fuzzing Strategy}
-\Igor{
-  Para realizar nossos experimentos, tivemos que decidir qual as 
-  melhores abordagens para aumentar a efetividade dos fuzzers.
-  Os fuzzers mutacionais se mostraram mais eficientes em relacao
-  aos fuzzers geracionais, entao focamos neste ponto.
-  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
-  default para realizar a mutacao em arquivos existentes.
-  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
-  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
-  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
-  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
-  radamsa, gerando arquivos mais relevantes.
-  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
-  é um arquivo de teste relevante, seguindo estes requisitos:
-  \begin{itemize}
-    \item it contains only unicode text
-    \item it is parseable (i.e., it is structurally well-formed)
-    \item it does not contain engine-specific functions  
-    \item it does not empty
-  \end{itemize}
-
-}
-
-\section{Related Work}
+\Fix{The
+  closest work to ours was done by Patra and Pradel~\cite{patra2016learning},
+  where they evaluated their proposed language-agnostic fuzzer to find
+  cross-browser HTML+JS discrepancies. This project aims at building
+  and evaluating an infrastructure for differential testing of runtime
+  engines, such as the JS engine or WebAssembly's. The sensible parts
+  of the infrastructure are the checks of input validity (as to reduce
+  waste/cost) and output correctness (as to reduce false positives).}
 

### 2018-07-06 paper/paper.tex
pass on reviews

--- 2018-07-05 paper/paper.tex
@@
   \item The repository must have JavaScript tests included.
-  \item The tests should be plug-and-play and/or easy
-    integration.\Mar{not clear what you mean}
+  \item It does not use external libraries 
 \end{itemize}
@@
 Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
-used to find projects with JS files\Mar{why the query is so specific?
-  as per ``q=javascript-engine''? Need to be consistent to what you
-  are saying an coherent to what you actually did.}. The query sorts
-results in descending order in the number of stars\Mar{sorting is only
-  relevant if you set a limit on the number of projects you will
-  analyze. What limit is that?}. The resulting list includes a total
-of \Fix{XX} projects. A total of \Fix{...}  projects remained after
+used to find javascript engines projects defined by the keyword "javascript-engine". 
+The resulting list includes a total of 33 projects.
+A total of \Fix{...}  projects remained after
 removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
@@
   \begin{lstlisting}
-https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
+https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
   \end{lstlisting}
@@
 engines.\Mar{not entirely clear what you did to support
-  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
+  this.$\rightarrow$}\Igor{wip}We aimed to use only the JS file with minor fixes
 to support our environment. These fixes are composed by an assertion
@@
 \subsection{Fuzzing versus No Fuzzing}
-\Fix{nao entendi muito sobre essa subsection... 
-seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
 \Igor{
+  Para identificar a eficacia e eficiencia da nossa abordagem, 
+  foi necessario identificar se seeds de diferentes engenhos 
+  sao efetivos em
+
   Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 

### 2018-07-07 paper/paper.tex
pass on section III

@@
 
-\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
+\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
 associated with all four JS engines we analyzed
-(section~\ref{sec:methodology:engines}). In addition, we mined test
-suites from other repositories based on the following criteria:
-\begin{itemize}
-  \item The project must be an open-source project and at least 1K stars from community.
-  \item The repository must have JavaScript tests included.
-  \item It does not use external libraries 
-\end{itemize}
-
-Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
-used to find javascript engines projects defined by the keyword "javascript-engine". 
-The resulting list includes a total of 33 projects.
-A total of \Fix{...}  projects remained after
-removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
-the JS sources we considered for each of these selected
-projects..\Mar{identify the sources assoc. with the four analyzed
-  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
-files.\Mar{Briefly explain these sources.}
+(section~\ref{sec:methodology:engines}). In addition, we mined tests
+from other GitHub repositories based on the following selection
+criteria--the project must have received at least 1K stars and the
+project must not use external libraries. Figure~\ref{fig:query}
+illustrates the GitHub API query~\cite{github-rest-api} we used to
+find javascript engines projects defined by the keyword
+``javascript-engine''\Mar{is this a label or two keywords?}.  The
+resulting list included a total of 33 projects.  A total of \Fix{4?}
+projects remained after removing projects that \Fix{...}.\Mar{explique
+como o numero baixou tanto.}
 
@@
   \caption{\label{fig:query}
-  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
+  Query used to find JS engine projects with over 1K stars.
   }
 \end{figure}
+
+Table~\ref{tab:test-suites} shows the JS sources we considered for
+each of the selected projects.\Mar{identify the sources assoc. with
+  the four analyzed engines. you said in the first sentence this is
+  one source.}  Overall, we found a total of \totfiles{} JS
+files.\Mar{Briefly explain these sources.} It is worth noting that some projects use distinct frameworks for
+testing and require external libraries to run their testing
+suites. For these projects, we needed to make small changes in the testing
+infrastructure to be able to uniformly run tests in all
+engines.\Mar{not entirely clear what you did to support
+  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
+  que em portugues). isto
+  nao deveria levar tempo que justifique escrever wip.}We aimed to use only the JS file with minor fixes
+to support our environment. These fixes are composed by an assertion
+function that throws an Error that we can capture by our
+infraestruture.
 
@@
 \end{table}
-
-It is worth noting that some projects use distinct frameworks for
-testing and require external libraries to run their testing
-suites. For these projects, we needed to make small changes in the testing
-infrastructure to be able to uniformly run tests in all
-engines.\Mar{not entirely clear what you did to support
-  this.$\rightarrow$}\Igor{wip}We aimed to use only the JS file with minor fixes
-to support our environment. These fixes are composed by an assertion
-function that throws an Error that we can capture by our
-infraestruture.
 

### 2018-07-08 paper/paper.tex
explaining fuzzers

@@
 
-\Mar{revise...}~We used representatives of popular fuzzing approaches. For
-random-based fuzzing we used Radamsa~\cite{radamsa}; for
-coverage-based fuzzing we used
-\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-generative-based fuzzing we used
-\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-be found elsewhere~\cite{fuzz-bart}.
+In the following, we describe the list of fuzzers we analyzed. We
+initially considered generational grammar-based fuzzers and mutational
+fuzzers.
 
-Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
-Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
-we try to integrate several grammar-based fuzzers, for example 
-Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
-and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
-after several runs it was observed that this approach was ineffective
-due the amount of invalid files and/or files without discrepancies. For example, if we ran 
-Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
-\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
-are js files that shows undefined variables and due the differential testing in our environment
-all engines will raise a SyntaxError and this approach was not relevant to our experiment.
+Grammar-based fuzzers generate a new file using the grammar of the
+language whose inputs should be fuzzed. Intuitively, those fuzzers
+implement a traversal of the production rules of the input grammar to
+create syntax trees, which are then pretty-printed. Consequently, this
+approach produces inputs that are syntatically valid by construction.
+We analyzed two grammar-based
+fuzzers--Grammarinator~\cite{grammarinator} and
+QuickFuzz~\cite{grieco2016quickfuzz}.  Unfortunately none was
+effective out of the box. Given the bound limits we defined, we were
+unable to find any discrepancy in the inputs those tools generated. To
+sum, the tools produced a high percentage of semantically-invalid
+inputs such as \Fix{give one or two concrete examples--variable usage
+  without definition?} that we needed to discard and the valid inputs
+manifested no discrepancies. For example, we produced 10K inputs with
+Grammarinator and only \Fix{X} were valid. With QuickFuzz, we were
+able to produce \Fix{Y, Y$>$Y?} valid inputs as it contains some
+heuristics to avoid generation of semantically-invalid
+inputs. Nonetheless, running those inputs in our infrastructure we
+were unable to find discrepancies. Inpecting the valid inputs we found
+that they produced only very simple inputs. \Mar{are there weights
+  associated with production rules besides the depth you can set?}
+
+%% Our
+%% infrastructure supports any grammar fuzzer with a few
+%% adjusts. However, we try to integrate several grammar-based fuzzers,
+%% for example
+%% and \Fix{others fuzzers} to
+%% generate new JavaScript files based on grammar, but after several runs
+%% it was observed that this approach was ineffective due the amount of
+%% invalid files and/or files without discrepancies.
+%% For example, if we
+%% ran Grammarinator to generate 1K JS files ten times with a random seed
+%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
+%% environment almost \Fix{XX\%} are js files that shows undefined
+%% variables and due the differential testing in our environment all
+%% engines will raise a SyntaxError and this approach was not relevant to
+%% our experiment.
+
+%% We initially considered used representatives of popular fuzzing approaches. For
+%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
+%% coverage-based fuzzing we used
+%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
+%% generative-based fuzzing we used
+%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
+%% be found elsewhere~\cite{fuzz-bart}.
+
+\Fix{do the same as above for coverage-based fuzzing}
+
+\Fix{do the same as above for black-box fuzzing}
 

### 2018-07-08 paper/paper.tex
another pass on III.C

@@
 
-\Fix{do the same as above for coverage-based fuzzing}
+\Mar{------------ estou aqui -M}
 
-\Fix{do the same as above for black-box fuzzing}
+\Fix{quick on mutational fuzzers}
+
+Coverage-based fuzzers like American Fuzz Loop (AFL)~\cite{afl} and
+libfuzzer~\cite{libfuzzer} run tests inputs in coverage-instrumented
+versions of the program under testing. The typical approach to input
+generation of this kind of fuzzer is evolutionary--they try to
+minimize the distances to still uncovered branches of the
+program. AFL, for instance, takes the instrumented program binary and
+one input seed and produces on output crash inputs. Considering our
+context of application, we needed to build one runtime engine to
+collect coverage information for fuzzing; we chose v8. (There are
+options in LLVM clang for that~\cite{libfuzzer}.)  Unfortunately, we
+found that most of the inputs produced violate the JS grammar and the
+fuzzing task can take days even when considering one seed. That
+happens because the entire decision tree of the engine is explored,
+including the branches associated with the lexer and parser. For this
+reason, Google promotes the creation of fuzz targets associated with
+specific program functions. Although that approach has shown very
+effective, it requires domain knowledge to create the calling context
+for the fuzz target. For those reason, coverage-based fuzzers were not
+considered in this study.
+
+\Fix{...do the same as above for black-box fuzzing. explain what kinds of
+inputs they can generate.}
 
@@
   \centering
-  \caption{List of bug reports issued by our team
-    24, 2018.}
+  \caption{List of bug reports issued by our team since April,
+    2018. The analysis of warnings was not uninterrupted.}
   \label{tab:bugs}

### 2018-07-09 paper/paper.tex
pass on comments (wip)

@@
 detected during the execution of the test code or its close neighborhood\Comment{ as
-  opposed to that of some internal JS function}. The rationale is that
+  opposed to that of some internal JS function}, \Igor{crashes (ie. FatalError) and core dumps 
+  are considered HI group as well}. The rationale is that
 the test in this group executed without violating any internal checks
@@
 anomaly was observed during the execution of some standard JS
-function\Mar{is this correct? what are those?}. We
+function.
+\Mar{is this correct? what are those?}\Igor{Yeah, it's okay}We
 found that different engines often check the pre-conditions of those
 functions differently. It can happen, for example, that one engine
-enforces a pre-condition that another engine does not\Mar{why is that?
-that should not happen if the spec was fully documented and engines
-properly implemented those checks. Explain and give example.}. In those cases,
+enforces a pre-condition that another engine does not, 
+% \Mar{why is that?
+% that should not happen if the spec was fully documented and engines
+% properly implemented those checks. Explain and give example.}
+\Igor{these cases happen because the specification describes how a function
+should work, however the internal implementation is defined by the engine developers}.
+In those cases,
 our infrastructure would observe a discrepancy that is more likely to
@@
   HI and LO.}
+\Igor{For example, a bug caught by our environment and reported as LO priority was reported 
+on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
+this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
+the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
+the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
+at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
+it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
+only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
+the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
+Until now, the issue was confirmed and waiting for merge/closed.
+\Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
+}
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function},
+  }
+  \begin{lstlisting}
+function* g1() {
+  for (var x = yield in {}) ;
+}
+var it = g1();
+assertEq(it.next().done, false);
+assertEq(it.next().done, true);
+  \end{lstlisting}
+  \normalsize
+  \caption{Bug caught by our environment as LO priority.}
+  \label{fig:lo-priority}
+  \end{figure}
+
+An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
+This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
+initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
+integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
+during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
+this is an intentional behavior of engine that crash the process if it runs out of memory
+\footnote{Chakra issue \#4979 \url{https://github.com/Microsoft/ChakraCore/issues/4979}}.
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+function test() {
+  return typeof String.prototype.repeat === "function"
+    && "foo".repeat(657604378) === "foofoofoo";
+}
+if (!test())
+  throw new Error("Test failed");
+  \end{lstlisting}
+  \normalsize
+  \caption{Warning captured as HI priority.}
+  \label{fig:hi-priority}
+  \end{figure}
+
 \Mar{can we detect dups mining issue trackers?}
+\Igor{
+  acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
+  Tenho umas consideracoes:
+  \begin{itemize}
+    \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
+    se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
+    \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
+    \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
+  \end{itemize}
+}
 
@@
 illustrates the GitHub API query~\cite{github-rest-api} we used to
-find javascript engines projects defined by the keyword
-``javascript-engine''\Mar{is this a label or two keywords?}.  The
-resulting list included a total of 33 projects.  A total of \Fix{4?}
-projects remained after removing projects that \Fix{...}.\Mar{explique
-como o numero baixou tanto.}
+find javascript engines projects defined by the label
+``javascript-engine''.  The resulting list included a total of 33 projects.
+\Igor{
+  Due the GitHub does not supports to get the repository files via API, we
+  analyzed manually each of them. It was observed that sixteen projects
+  are invalid for us due the uses NodeJS that our engine cannot support it,
+  empty repositories and browser support as well and another 13 projects 
+  does not have a test module in their repository.
+  A total of 4 projects remained after the manual inspection, two of them
+  are added before, for example the V8\footnote{The official mirror of the V8 Git repository \url{https://github.com/v8/v8}}
+  and V7\footnote{V7 Embedded JavaScript engine \url{https://github.com/cesanta/v7}} repositories.
+  The Duktape and JerryScript tests are the seeds that we integrate on our infraestruture.
+  The repositories of JSI and TinyJS are found manually and was incorpored also even less 1K of stars.
+}
 
@@
     Duktape & \cite{duktape} & 997 \\
-    JerryJS & \cite{jerryscript} & 1,803 \\
+    JerryScript & \cite{jerryscript} & 1,803 \\
     JSI & \cite{jsi} & 99 \\

### 2018-07-09 paper/paper.tex
discussing mutational fuzzers + dos2unix on references.bib

@@
 
-\Mar{------------ estou aqui -M}
-
-\Fix{quick on mutational fuzzers}
-
-Coverage-based fuzzers like American Fuzz Loop (AFL)~\cite{afl} and
-libfuzzer~\cite{libfuzzer} run tests inputs in coverage-instrumented
-versions of the program under testing. The typical approach to input
-generation of this kind of fuzzer is evolutionary--they try to
-minimize the distances to still uncovered branches of the
-program. AFL, for instance, takes the instrumented program binary and
-one input seed and produces on output crash inputs. Considering our
-context of application, we needed to build one runtime engine to
-collect coverage information for fuzzing; we chose v8. (There are
-options in LLVM clang for that~\cite{libfuzzer}.)  Unfortunately, we
-found that most of the inputs produced violate the JS grammar and the
-fuzzing task can take days even when considering one seed. That
-happens because the entire decision tree of the engine is explored,
-including the branches associated with the lexer and parser. For this
-reason, Google promotes the creation of fuzz targets associated with
-specific program functions. Although that approach has shown very
-effective, it requires domain knowledge to create the calling context
-for the fuzz target. For those reason, coverage-based fuzzers were not
-considered in this study.
+Mutational fuzzers can be either white-box (coverage-based) or
+black-box. Coverage-based fuzzers like American Fuzz Loop
+(AFL)~\cite{afl} and libfuzzer~\cite{libfuzzer} run tests inputs
+against instrumented versions of the program under testing with the
+typical goal of finding univeral errors like crashes and buffer
+overflows. The instrumentation adds code to collect coverage and
+monitor properties\footnote{ There are options in the clang toolchain
+  to build programs with fuzzing
+  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
+  for property checking~\cite{clang-documentation}.}. The typical
+approach to input generation is evolutionary--these fuzzers try to
+minimize the distances to still-uncovered branches of the
+program. AFL, for instance, takes the instrumented program binary
+(say, a JS engine) and one seed input to that program (say, a JS
+program) and produces on output fault-revealing inputs. Considering
+our context of application, we needed to instrument one runtime engine
+for fuzzing; we chose v8 for this. Unfortunately, we found that most
+of the inputs produced by AFL violate the JS grammar. Furthermore, the
+fuzzing task took days even when considering only one seed and there
+is no simple way to guide the exploration. That happens because the
+fuzzer aims to explore the entire decision tree induced from the
+engine's main function, including the branches associated with the
+lexer and the parser. For that reasons, coverage-based fuzzers were
+not considered in this study. It is worth mentioning that Google
+mitigates that problem by promoting developers to create fuzz targets
+for specific program functions\Fix{cite}. Although that approach has
+shown very effective, it requires domain knowledge to create the
+calling context to invoke the fuzz target.
 

### 2018-07-09 paper/paper.tex
another pass on III.C

@@
 
-In the following, we describe the list of fuzzers we analyzed. We
-initially considered generational grammar-based fuzzers and mutational
-fuzzers.
+%% In the following, we describe the list of fuzzers we analyzed. We
+%% initially considered generational grammar-based fuzzers and mutational
+%% fuzzers.
 
-Grammar-based fuzzers generate a new file using the grammar of the
-language whose inputs should be fuzzed. Intuitively, those fuzzers
-implement a traversal of the production rules of the input grammar to
-create syntax trees, which are then pretty-printed. Consequently, this
-approach produces inputs that are syntatically valid by construction.
-We analyzed two grammar-based
-fuzzers--Grammarinator~\cite{grammarinator} and
-QuickFuzz~\cite{grieco2016quickfuzz}.  Unfortunately none was
-effective out of the box. Given the bound limits we defined, we were
-unable to find any discrepancy in the inputs those tools generated. To
-sum, the tools produced a high percentage of semantically-invalid
-inputs such as \Fix{give one or two concrete examples--variable usage
-  without definition?} that we needed to discard and the valid inputs
-manifested no discrepancies. For example, we produced 10K inputs with
-Grammarinator and only \Fix{X} were valid. With QuickFuzz, we were
-able to produce \Fix{Y, Y$>$Y?} valid inputs as it contains some
-heuristics to avoid generation of semantically-invalid
-inputs. Nonetheless, running those inputs in our infrastructure we
-were unable to find discrepancies. Inpecting the valid inputs we found
-that they produced only very simple inputs. \Mar{are there weights
-  associated with production rules besides the depth you can set?}
+Fuzzers are typically categorized in two main groups--those that build
+inputs anew (generational) and those that modify existing inputs
+(mutational). We used two black-box mutational
+fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
+in this study. In the following, we provide rationale for this
+selection.
+
+Generational fuzzers are typically grammar-based. These fuzzers
+generate a new file using the grammar of the language whose inputs
+should be fuzzed. Intuitively, those fuzzers implement a traversal of
+the production rules of the input grammar to create syntax trees,
+which are then pretty-printed. Consequently, this approach produces
+inputs that are syntactically valid by construction.  We analyzed two
+grammar-based fuzzers--Grammarinator~\cite{grammarinator} and
+QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately none
+was effective out of the box. Given the bound limits we defined on the
+number of inputs to generate and the depth of exploration in the
+syntax tree, we were unable to find discrepancies on the inputs those
+tools generated. To sum, the tools produced a high percentage of
+semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
+  examples--variable usage without definition?}) that we needed to
+discard and the valid inputs manifested no discrepancies. For example,
+we produced 10K inputs with Grammarinator and only \Fix{X} of those
+were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
+valid inputs as it contains some heuristics to circumvent violation of
+certain type rules such as \Fix{variable used must be
+  defined?}. Nonetheless, running those inputs in our infrastructure
+we were unable to find discrepancies. Inpecting those inputs, we
+realized that they reflected very simple scenarios. \Mar{are there
+  weights associated with production rules besides the depth you can
+  set?} To sum, we did not consider this kind of fuzzer in this
+study\Fix{...}
 
@@
 
-Mutational fuzzers can be either white-box (coverage-based) or
-black-box. Coverage-based fuzzers like American Fuzz Loop
-(AFL)~\cite{afl} and libfuzzer~\cite{libfuzzer} run tests inputs
+Mutational fuzzers can be either white-box or
+black-box. White-box mutational fuzzers are typically
+coverage-based. American Fuzz Loop
+(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of
+this kind of fuzzers. These fuzzers run tests inputs
 against instrumented versions of the program under testing with the
 typical goal of finding univeral errors like crashes and buffer
-overflows. The instrumentation adds code to collect coverage and
-monitor properties\footnote{ There are options in the clang toolchain
-  to build programs with fuzzing
+overflows. The instrumentation adds code to collect branch coverage and
+monitor specific properties\footnote{There are options in the clang
+  toolchain to build programs with fuzzing
   instrumentation~\cite{libfuzzer}. clang provides several sanitizers
@@
 (say, a JS engine) and one seed input to that program (say, a JS
-program) and produces on output fault-revealing inputs. Considering
-our context of application, we needed to instrument one runtime engine
-for fuzzing; we chose v8 for this. Unfortunately, we found that most
-of the inputs produced by AFL violate the JS grammar. Furthermore, the
-fuzzing task took days even when considering only one seed and there
-is no simple way to guide the exploration. That happens because the
-fuzzer aims to explore the entire decision tree induced from the
-engine's main function, including the branches associated with the
-lexer and the parser. For that reasons, coverage-based fuzzers were
-not considered in this study. It is worth mentioning that Google
-mitigates that problem by promoting developers to create fuzz targets
-for specific program functions\Fix{cite}. Although that approach has
-shown very effective, it requires domain knowledge to create the
-calling context to invoke the fuzz target.
+program) and produces on output fault-revealing inputs, if
+found. Considering our context of application, we needed to instrument
+one runtime engine for fuzzing; we chose v8. Unfortunately, we found
+that most of the inputs produced by AFL violate the JS
+grammar. Furthermore, the fuzzing task took days, even when considering
+only one seed and there is no simple way to guide the
+exploration. That happens because the fuzzer aims to explore the
+entire decision tree induced from the engine's main function,
+including the branches associated with the lexer and the parser. For
+those reasons, coverage-based fuzzers were not considered in this
+study. It is worth mentioning that Google mitigates that problem by
+promoting developers to create fuzz targets for specific program
+functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although that approach has shown very effective,
+it requires domain knowledge to create the calling context to invoke
+the fuzz target.
 

### 2018-07-10 paper/paper.tex
minor changes on intro

@@
 the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure discards the corresponding
-input. Otherwise, it considers the input as potentially
+output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
 fault-revealing; hence interesting for human inspection. Considering
@@
 detected during the execution of the test code or its close neighborhood\Comment{ as
-  opposed to that of some internal JS function}, \Igor{crashes (ie. FatalError) and core dumps 
-  are considered HI group as well}. The rationale is that
+  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
+  are considered HI group as well. The rationale is that
 the test in this group executed without violating any internal checks
@@
 function.
-\Mar{is this correct? what are those?}\Igor{Yeah, it's okay}We
+\Mar{is this correct? what are those?}We
 found that different engines often check the pre-conditions of those
@@
   HI and LO.}
-\Igor{For example, a bug caught by our environment and reported as LO priority was reported 
-on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
-this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
-the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
-the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
-at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
-it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
-only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
-the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
-Until now, the issue was confirmed and waiting for merge/closed.
-\Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
-}
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function},
-  }
-  \begin{lstlisting}
-function* g1() {
-  for (var x = yield in {}) ;
-}
-var it = g1();
-assertEq(it.next().done, false);
-assertEq(it.next().done, true);
-  \end{lstlisting}
-  \normalsize
-  \caption{Bug caught by our environment as LO priority.}
-  \label{fig:lo-priority}
-  \end{figure}
 
-An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
-This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
-initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
-integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
-during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
-this is an intentional behavior of engine that crash the process if it runs out of memory
-\footnote{Chakra issue \#4979 \url{https://github.com/Microsoft/ChakraCore/issues/4979}}.
+\subsection{ES6 design}
+\Fix{to appear}
+% no-bug low console output
 
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
-function test() {
-  return typeof String.prototype.repeat === "function"
-    && "foo".repeat(657604378) === "foofoofoo";
-}
-if (!test())
-  throw new Error("Test failed");
-  \end{lstlisting}
-  \normalsize
-  \caption{Warning captured as HI priority.}
-  \label{fig:hi-priority}
-  \end{figure}
+% bug high console output
 
@@
 \subsection{Seed JS files\label{sec:seeds}}~We considered test suites
-associated with all four JS engines we analyzed
-(section~\ref{sec:methodology:engines}). In addition, we mined tests
-from other GitHub repositories based on the following selection
-criteria--the project must have received at least 1K stars and the
-project must not use external libraries. Figure~\ref{fig:query}
-illustrates the GitHub API query~\cite{github-rest-api} we used to
-find javascript engines projects defined by the label
-``javascript-engine''.  The resulting list included a total of 33 projects.
+associated with all \Fix{four} JS engines we analyzed
+(section~\ref{sec:methodology:engines}).
 \Igor{
-  Due the GitHub does not supports to get the repository files via API, we
-  analyzed manually each of them. It was observed that sixteen projects
-  are invalid for us due the uses NodeJS that our engine cannot support it,
-  empty repositories and browser support as well and another 13 projects 
-  does not have a test module in their repository.
-  A total of 4 projects remained after the manual inspection, two of them
-  are added before, for example the V8\footnote{The official mirror of the V8 Git repository \url{https://github.com/v8/v8}}
-  and V7\footnote{V7 Embedded JavaScript engine \url{https://github.com/cesanta/v7}} repositories.
-  The Duktape and JerryScript tests are the seeds that we integrate on our infraestruture.
-  The repositories of JSI and TinyJS are found manually and was incorpored also even less 1K of stars.
+  We selected only the seeds that supports integration without external dependencies. 
+  In addition, we found in public repositories (ie. GitHub) several kinds of projects 
+  that contains javascript files, however, the most of them uses nodejs that have 
+  internal functions that our engines does not support. 
+  We found a total of four engines projects that we can integrate to our seeds 
+  with minor fixes on the files, due the "assertion function" is missing in some cases.
 }
-
-\begin{figure}[h]
-  \centering
-  \begin{lstlisting}
-https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000
-  \end{lstlisting}
-  \caption{\label{fig:query}
-  Query used to find JS engine projects with over 1K stars.
-  }
-\end{figure}
 
@@
   \centering
-  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
-      name (if possible) to facilitate reference in the paper. Use the
-  full path in the URL (citation) to indicate where one can find those
-  files.}}
+  \caption{\label{tab:test-suites}Test Suites
+  % \Mar{try to use a single
+  %     name (if possible) to facilitate reference in the paper. Use the
+  % full path in the URL (citation) to indicate where one can find those
+  % files.}
+  }
   \begin{tabular}{ccr}
@@
     Tiny-js & \cite{tinyjs} & 44 \\
-    Mozilla & \Fix{??} & 32,414 \\
-    V8.test.benchmarks.data & \Fix{??} & 64 \\
-    WebKit.jstests.es6 & \Fix{??} & 605 \\
-    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
+    Mozilla & \cite{mozilla} & 32,414 \\
+    V8 & \cite{v8} & 64 \\
+    WebKit & \cite{webkit} & 1031 \\
+    % Chakra & \cite{chakracore} & 2632 \\
     \midrule
@@
     16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
-    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
-    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
+    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
+    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
     19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
+    20 & 7/10 & quickfuzz & JavaScriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & x\\
+    21 & 7/10 & quickfuzz & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & x\\    
+    \midrule
+    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{quickfuzz} & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{x}\\
+                        &  &                       &
+    JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187519}{\#187519}  &   & \\
    \bottomrule     
@@
 
+\subsection{False Positives Bugs}
+
+An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
+This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
+initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
+integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
+during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
+this is an intentional behavior of engine that crash the process if it runs out of memory
+\cite{bug4979}.
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+function test() {
+  return typeof String.prototype.repeat === "function"
+    && "foo".repeat(657604378) === "foofoofoo";
+}
+if (!test())
+  throw new Error("Test failed");
+  \end{lstlisting}
+  \normalsize
+  \caption{Warning captured as HI priority.}
+  \label{fig:hi-priority}
+  \end{figure}
+
+% \subsection{LO bugs}
+% 
+% \Igor{For example, a bug caught by our environment and reported as LO priority was reported 
+% on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
+% this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
+% the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
+% the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
+% at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
+% it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
+% only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
+% the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
+% Until now, the issue was confirmed and waiting for merge/closed.
+% \Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
+% }
+% \begin{figure}[h!]
+%   \centering
+%   \scriptsize
+%   \lstset{escapeinside={@}{@},
+%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%     numberstyle=\tiny,
+%     morekeywords={assertEq, var, yield, in, function},
+%   }
+%   \begin{lstlisting}
+% function* g1() {
+%   for (var x = yield in {}) ;
+% }
+% var it = g1();
+% assertEq(it.next().done, false);
+% assertEq(it.next().done, true);
+%   \end{lstlisting}
+%   \normalsize
+%   \caption{Bug caught by our environment as LO priority.}
+%   \label{fig:lo-priority}
+%   \end{figure}
+
 \section{Related Work}

### 2018-07-10 paper/paper.tex
pass on comments
pass on igor text

@@
 
+\section{ES6 design}
+\Fix{to appear}
+
 \section{Infrastructure}
@@
 of the API. In constrast, warnings in the LO group reflect the cases where the
-anomaly was observed during the execution of some standard JS
-function.
-\Mar{is this correct? what are those?}We
-found that different engines often check the pre-conditions of those
+anomaly was observed during the execution of functions from standard JS
+libraries.\Mar{what is that exactly? can we cite? is that only spec or
+actually code as most of java.* libraries.}We
+found that different engines often check pre-conditions of those
 functions differently. It can happen, for example, that one engine
-enforces a pre-condition that another engine does not, 
+enforces a weaker pre-condition compared to another.
 % \Mar{why is that?
@@
 \Igor{these cases happen because the specification describes how a function
-should work, however the internal implementation is defined by the engine developers}.
+should work, however the internal implementation is defined by the
+engine developers}\Mar{If you confirm that there is no code in specs
+  (see comment above), what would be those abstract
+  functions/interfaces that you mentioned to me the other day?}.
 In those cases,
@@
 we found originated from the LO category. \Mar{show real examples of
-  HI and LO.}
+  HI and LO. Use the stacktraces to explain what is going on.}
 
-\subsection{ES6 design}
-\Fix{to appear}
 % no-bug low console output

### 2018-07-10 paper/paper.tex
pass on igor comments

@@
 \label{sec:methodology:engines}~We selected the most popular JS
-engines on the web~\Fix{cite} to focus our bug-finding efforts, namely
+engines on the web~\Fix{ha alguma referencia que de suporte a isto?} to focus our bug-finding efforts, namely
 Microsoft's Chakra~\cite{chakra2018repo}, Google's
@@
 
-\subsection{Seed JS files\label{sec:seeds}}~We considered test suites
-associated with all \Fix{four} JS engines we analyzed
-(section~\ref{sec:methodology:engines}).
-\Igor{
-  We selected only the seeds that supports integration without external dependencies. 
-  In addition, we found in public repositories (ie. GitHub) several kinds of projects 
-  that contains javascript files, however, the most of them uses nodejs that have 
-  internal functions that our engines does not support. 
-  We found a total of four engines projects that we can integrate to our seeds 
-  with minor fixes on the files, due the "assertion function" is missing in some cases.
-}
+\subsection{Seed JS files\label{sec:seeds}}~
+We selected test files from several public projects from GitHub. We
+looked for self-contained tests from JS engine projects, initially
+using the GitHub REST API\Fix{cite}. We noticed that some of the tests
+we found depend on external libraries, which not all engines we use
+(see Section~\ref{sec:methodology:engines}) support. We decided to
+discard those. For example, many tests we found required a
+nodejs\Fix{cite} runtime for execution. Overall, we considered the
+test suites of three of the four engines mentioned in
+Section~\ref{sec:methodology:engines} and four other engines.
+
+\Mar{vc. jah nao fala disto no paragrafo a seguir? se sim, junte os dois.}
+We
+implemented minor changes on test files with fixable file dependencies. For
+example, some of the files used assertion functions defined in their
+projects; we replaced those with our definitions.\Mar{not sure if this
+  is a good example; why one would like to redefine assertion? why
+  didn't you incorporate the assertion function to your infra?}
 
 Table~\ref{tab:test-suites} shows the JS sources we considered for
-each of the selected projects.\Mar{identify the sources assoc. with
-  the four analyzed engines. you said in the first sentence this is
-  one source.}  Overall, we found a total of \totfiles{} JS
-files.\Mar{Briefly explain these sources.} It is worth noting that some projects use distinct frameworks for
-testing and require external libraries to run their testing
-suites. For these projects, we needed to make small changes in the testing
-infrastructure to be able to uniformly run tests in all
-engines.\Mar{not entirely clear what you did to support
+each of the selected projects. Overall, we found a total of
+\totfiles{} JS files. It is worth noting that some projects use
+distinct frameworks for testing and require external libraries to run
+their testing suites. For these projects, we needed to make small
+changes in the testing infrastructure to be able to uniformly run
+tests in all engines.\Mar{not entirely clear what you did to support
   this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
-  que em portugues). isto
-  nao deveria levar tempo que justifique escrever wip.}We aimed to use only the JS file with minor fixes
-to support our environment. These fixes are composed by an assertion
+  que em portugues). isto nao deveria levar tempo que justifique
+  escrever wip.}We aimed to use only the JS file with minor fixes to
+support our environment. These fixes are composed by an assertion
 function that throws an Error that we can capture by our
@@
     \midrule
+    Mozilla & \cite{mozilla} & 32,414 \\
+    V8 & \cite{v8} & 64 \\
+    WebKit & \cite{webkit} & 1,031 \\
+    \midrule    
     Duktape & \cite{duktape} & 997 \\
@@
     Tiny-js & \cite{tinyjs} & 44 \\    
-    Mozilla & \cite{mozilla} & 32,414 \\
-    V8 & \cite{v8} & 64 \\
-    WebKit & \cite{webkit} & 1031 \\
     % Chakra & \cite{chakracore} & 2632 \\

### 2018-07-11 paper/paper.tex
correction in text

@@
 which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction.  We analyzed two
-grammar-based fuzzers--Grammarinator~\cite{grammarinator} and
-QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately none
-was effective out of the box. Given the bound limits we defined on the
-number of inputs to generate and the depth of exploration in the
-syntax tree, we were unable to find discrepancies on the inputs those
-tools generated. To sum, the tools produced a high percentage of
+inputs that are syntactically valid by construction.  We analyzed
+three grammar-based fuzzers--Grammarinator~\cite{grammarinator},
+jsfunfuzz~\cite{jsfunfuzz}, and
+QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately, none
+of those was effective out of the box. Given the bound limits we
+defined on the number of inputs to generate and the exploration depth
+of the syntax tree, we were unable to find discrepancies on the inputs
+those tools generated. To sum, the tools produced a high percentage of
 semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
@@
 discard and the valid inputs manifested no discrepancies. For example,
-we produced 10K inputs with Grammarinator and only \Fix{X} of those
+we produced 100K inputs with Grammarinator and only \Fix{X} of those
 were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
@@
 we were unable to find discrepancies. Inpecting those inputs, we
-realized that they reflected very simple scenarios. \Mar{are there
+realized that they reflected very simple scenarios.\Comment{ \Mar{are there
   weights associated with production rules besides the depth you can
-  set?} To sum, we did not consider this kind of fuzzer in this
-study\Fix{...}
+  set?}} Although grammar-based fuzzers has been shown effective to
+find real bugs\Fix{cite some jsfunfuzz bug reports}, generating
+valid inputs is very time-consuming, especially for the context of
+differential testing. For this reason, we did not consider those fuzzers.
 
@@
 
-Mutational fuzzers can be either white-box or
-black-box. White-box mutational fuzzers are typically
-coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of
-this kind of fuzzers. These fuzzers run tests inputs
-against instrumented versions of the program under testing with the
-typical goal of finding univeral errors like crashes and buffer
-overflows. The instrumentation adds code to collect branch coverage and
-monitor specific properties\footnote{There are options in the clang
-  toolchain to build programs with fuzzing
-  instrumentation~\cite{libfuzzer}. clang provides several sanitizers
-  for property checking~\cite{clang-documentation}.}. The typical
-approach to input generation is evolutionary--these fuzzers try to
-minimize the distances to still-uncovered branches of the
-program. AFL, for instance, takes the instrumented program binary
-(say, a JS engine) and one seed input to that program (say, a JS
-program) and produces on output fault-revealing inputs, if
+Mutational fuzzers can be either white-box or black-box. White-box
+mutational fuzzers are typically coverage-based. American Fuzz Loop
+(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
+kind of fuzzers. These fuzzers run tests inputs against instrumented
+versions of the program under testing with the typical goal of finding
+univeral errors like crashes and buffer overflows. The instrumentation
+adds code to collect branch coverage and to monitor specific
+properties\footnote{There are options in the clang toolchain to build
+  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
+  provides several sanitizers for property
+  checking~\cite{clang-documentation}.}. AFL use coverage to determine
+inputs that uncover a new branch and deserve fuzzing whereas libFuzzer
+uses evolutionary generation--it tries to minimize the distances to
+still-uncovered branches of the program. AFL takes the instrumented
+program binary (say, a JS engine) and one seed input to that program
+(say, a JS program) and produces on output fault-revealing inputs, if
 found. Considering our context of application, we needed to instrument
@@
 that most of the inputs produced by AFL violate the JS
-grammar. Furthermore, the fuzzing task took days, even when considering
-only one seed and there is no simple way to guide the
-exploration. That happens because the fuzzer aims to explore the
-entire decision tree induced from the engine's main function,
-including the branches associated with the lexer and the parser. For
-those reasons, coverage-based fuzzers were not considered in this
-study. It is worth mentioning that Google mitigates that problem by
-promoting developers to create fuzz targets for specific program
-functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although that approach has shown very effective,
-it requires domain knowledge to create the calling context to invoke
-the fuzz target.
+grammar. Furthermore, the fuzzing task can take daysfor a single seed
+input and there is no simple way to guide the
+exploration~\Fix{cite}. That happens because the fuzzer aims to
+explore the entire decision tree induced from the engine's main
+function, including the branches associated with the lexer and the
+parser. For those reasons, coverage-based fuzzers were not considered
+in this study. It is worth mentioning that Google mitigates that
+problem with libFuzzer by asking developers to create fuzz targets for
+specific program
+functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
+that approach has shown very effective, it requires domain knowledge
+to create the calling context to invoke the fuzz target.
 

### 2018-07-11 paper/paper.tex
minor changes in infra

--- 2018-07-10 paper/paper.tex
@@
 
-\section{ES6 design}
-\Fix{to appear}
-
 \section{Infrastructure}
@@
 the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
+output is consistent), the infrastructure discards the corresponding
+input. Otherwise, it considers the input as potentially
 fault-revealing; hence interesting for human inspection. Considering
@@
 of the API. In constrast, warnings in the LO group reflect the cases where the
-anomaly was observed during the execution of functions from standard JS
-libraries.\Mar{what is that exactly? can we cite? is that only spec or
-actually code as most of java.* libraries.}We
-found that different engines often check pre-conditions of those
+anomaly was observed during the execution of some standard JS
+function. In addiction, we observed that several testcases run loops that can 
+affect the time-consuming of an execution, we decided to use an watcher to check 
+if an test consumes more than 5 seconds to run, if exceed this condition we stop 
+the engine execution and considered these cases as TIMEOUT error. These tests are 
+labeled as LO group.
+\Mar{is this correct? what are those?}We
+found that different engines often check the pre-conditions of those
 functions differently. It can happen, for example, that one engine
-enforces a weaker pre-condition compared to another.
+enforces a pre-condition that another engine does not, 
 % \Mar{why is that?
@@
 \Igor{these cases happen because the specification describes how a function
-should work, however the internal implementation is defined by the
-engine developers}\Mar{If you confirm that there is no code in specs
-  (see comment above), what would be those abstract
-  functions/interfaces that you mentioned to me the other day?}.
+should work, however the internal implementation is defined by the engine developers}.
 In those cases,
@@
 we found originated from the LO category. \Mar{show real examples of
-  HI and LO. Use the stacktraces to explain what is going on.}
+  HI and LO.}
+
+\Igor{
+  We defined if an warning is in HI or LO group according to console output.
+  The error stream in the output shows relevant informations that we can 
+  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
+  considered as a HI group, the stream output came from V8 engine. The error message 
+  shows informations related to the assertion code (see at line 2) 
+  that thows an Error exception. This case was considered as HI groups and after 
+  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
+}
+
+% bug high console output
+This a case of a warning reported as HI priority, the Figure~\ref{} shows
+the output console of V8 engine. We consider this case as a HI group due 
+the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
+throw new Error("Test Failed");
+  ^
+Error: Test Failed
+  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
+  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
+\end{lstlisting}
+\normalsize
+\caption{Warning captured as HI priority.}
+\label{fig:hi-priority}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+\begin{minipage}{.45\textwidth}
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
+  void code()
+  {
+
+  }
+  \end{lstlisting}
+  \end{minipage}\vfill
+  \begin{minipage}{.45\textwidth}
+    \scriptsize
+    \lstset{escapeinside={@}{@},
+      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+      basicstyle=\ttfamily\scriptsize, boxpos=c,
+      numberstyle=\tiny,
+      morekeywords={assertEq, var, yield, in, function, 
+      typeof, return, throw, new, Error, if},
+    }
+  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
+  void code()
+  {
+
+  }
+  \end{lstlisting}
+  \end{minipage}
+  \caption{Warning captured as HI priority.}
+  \label{fig:lo-priority}
+\end{figure}
 
 % no-bug low console output
-
-% bug high console output
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+\end{lstlisting}
+\normalsize
+\caption{Warning captured as HI priority.}
+\label{fig:lo-priority}
+\end{figure}
 
@@
 }
+
+\subsection{ES6 design}
+\Fix{to appear}
 
@@
 during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
-this is an intentional behavior of engine that crash the process if it runs out of memory
-\cite{bug4979}.
+this is an intentional behavior of engine that crash the process if it runs out of memory.
 

### 2018-07-11 paper/paper.tex
pass on infra

--- 2018-07-10 paper/paper.tex
@@
 \section{ES6 design}
+\label{sec:es6-design}
+The EcmaScript is a language specification maintained by 
+a committee called TC39 (Technical Committee) that follows 
+standard rules proposed by ISO/ETC JTC 1 - 
+Information Technology since 1996~\cite{es6-website}.
+The latest version of EcmaScript commonly called ES6
+
 \Fix{to appear}
@@
 anomaly was observed during the execution of functions from standard JS
-libraries.\Mar{what is that exactly? can we cite? is that only spec or
-actually code as most of java.* libraries.}We
-found that different engines often check pre-conditions of those
+libraries. For example, according to the latest version of ES6 specification\cite{es6-spec},
+they
+\Mar{what is that exactly? can we cite? is that only spec or
+actually code as most of java.* libraries.}
+We found that different engines often check pre-conditions of those
 functions differently. It can happen, for example, that one engine
@@
   functions/interfaces that you mentioned to me the other day?}.
+\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
+due the capacity of a fuzzer add an infinite repetition statement. We expected that
+each test process can running utmost 5 seconds, if exceed this condition we stop 
+the process and add a output message of a TIMEOUT error.}
 In those cases,
@@
 
-% no-bug low console output
+\Igor{
+  We defined if an warning is in HI or LO group according to console output.
+  The error stream in the output shows relevant informations that we can 
+  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
+  considered as a HI group, the stream output came from V8 engine. The error message 
+  shows informations related to the assertion code (see at line 2) 
+  that thows an Error exception. This case was considered as HI groups and after 
+  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
+}
 
 % bug high console output
+This a case of a warning reported as HI priority, the Figure~\ref{} shows
+the output console of V8 engine. We consider this case as a HI group due 
+the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
+throw new Error("Test Failed");
+  ^
+Error: Test Failed
+  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
+  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
+\end{lstlisting}
+\normalsize
+\caption{Warning captured as HI priority.}
+\label{fig:hi-priority}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering
+\begin{minipage}{.45\textwidth}
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
+  void code()
+  {
+
+  }
+  \end{lstlisting}
+  \end{minipage}\vfill
+  \begin{minipage}{.45\textwidth}
+    \scriptsize
+    \lstset{escapeinside={@}{@},
+      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+      basicstyle=\ttfamily\scriptsize, boxpos=c,
+      numberstyle=\tiny,
+      morekeywords={assertEq, var, yield, in, function, 
+      typeof, return, throw, new, Error, if},
+    }
+  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
+  void code()
+  {
+
+  }
+  \end{lstlisting}
+  \end{minipage}
+  \caption{Warning captured as HI priority.}
+  \label{fig:lo-priority}
+\end{figure}
+
+% no-bug low console output
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+\end{lstlisting}
+\normalsize
+\caption{Warning captured as HI priority.}
+\label{fig:lo-priority}
+\end{figure}
 
@@
     \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
-    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
-    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
-    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
-    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
-    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & WebKit \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\
+    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & WebKit    \\
+    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScript      \\
+    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & Mozilla      \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScript   \\
     7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
+    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & Mozilla
     \\
     \midrule
-    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
+    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{Mozilla}\\
                         &  &                       &
@@
     \midrule    
-    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
+    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScript\\
     \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\
                         &                        &        &
@@
     \midrule    
-    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
-    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
-    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
-    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
-    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
-    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
-    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
-    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
-    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
-    20 & 7/10 & quickfuzz & JavaScriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & x\\
-    21 & 7/10 & quickfuzz & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & x\\    
+    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
+    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScript \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & V8\\
+    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & WebKit\\
+    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & Mozilla\\
+    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & Webkit\\
+    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
+    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
+    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
+    21 & 7/10 & quickfuzz & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
     \midrule
-    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{quickfuzz} & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{x}\\
+    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{\crossmark} & Chakra & Confirmed & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{JerryScript}\\
                         &  &                       &
     JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187519}{\#187519}  &   & \\
+    \midrule
+    23 & 7/12 & \crossmark & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
    \bottomrule     

### 2018-07-11 paper/paper.tex
revisions after talking to igor about escli-host

--- 2018-07-11 paper/paper.tex
@@
 %    0,clip,width=0.35\textwidth]{google-awards-workflow}
-  \includegraphics[trim=0 250 0 0,clip,width=0.5\textwidth]{google-awards-workflow}  
+  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}  
   \caption{\label{fig:workflow}Infrastructure.}
@@
 Figure~\ref{fig:workflow} illustrates the infrastructure we used in
-this study.
-The bug-finding process
-takes on input JS files from regression test suites of various JS
-engines and generates warnings on output. Boxes in the figure denote encapsulation;
-arrowed lines indicate control flow (dashed) and data flow
-(filled). The cycle icons denote repetition--the leftmost icon
-indicates that each file in the input list will be analyzed in
+this study.  The bug-finding process takes on input JS files from
+regression test suites of various JS engines and generates warnings on
+output. Boxes in the figure denote encapsulation; arrowed lines
+indicate data flow. The cycle icons denote repetition--the leftmost
+icon indicates that each file in the input list will be analyzed in
 separate whereas the rightmost icon shows that a single file will be
-fuzzed multiple times. The bug-finding process works as follows.  Considering the case
-where fuzzing is not selected, as illustrated in the inner box at the bottom
-of the figure, the oracle checks whether or not the output produced
-for that file is consistent across all engine implementations. In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
-fault-revealing; hence interesting for human inspection. Considering
-the case where fuzzing~\cite{fuzz-testing-history} is selected, new
-inputs are obtained from a given input using some off-the-shelf
-fuzzer. Several fuzzing methods have been proposed in the
-  past, varying with respect to how new inputs are generated (\eg{},
-  coverage-based~\cite{afl,honggfuzz},
-  grammar-based~\cite{grammarinator,jsfunfuzz}, and
-  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
-  fuzzers we selected. The workflow of the infrastructure with fuzzing
-  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
-for a given seed input.
+fuzzed multiple times. The bug-finding process works as follows.
+Considering the case where fuzzing is not selected, the oracle checks
+whether or not the output produced for the input file is consistent
+across all engine implementations. In case the test passes in all
+engines or fails in all engines (\ie{}, the output is consistent), the
+infrastructure discards the test. Otherwise, it considers the input as
+potentially fault-revealing; hence interesting for human
+inspection. We used the open-source eshost-cli
+project~\cite{eshost-cli} for that. Microsoft uses eshost-cli to check
+functional discrepancies in the Chakra JS engine. Considering the case
+where fuzzing~\cite{fuzz-testing-history} is selected, new inputs are
+obtained from a given input using some off-the-shelf fuzzer. The
+workflow with fuzzing is similar to the workflow without fuzzing. In
+this case, however, the checker can produce multiple warnings for a
+given input. Several fuzzing methods have been proposed in the past,
+varying with respect to how new inputs are
+generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.
+Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
 

### 2018-07-11 paper/paper.tex
pass on IV.A

@@
 \subsection{Engines}
-\label{sec:methodology:engines}~We selected the most popular JS
-engines on the web~\Fix{ha alguma referencia que de suporte a isto?} to focus our bug-finding efforts, namely
-Microsoft's Chakra~\cite{chakra2018repo}, Google's
-v8~\cite{v82018repo}, Mozilla's
-SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
-(WebKit)~\cite{jsc2018repo}.
+\label{sec:methodology:engines}~We selected 
+JS engines according to the following criteria.
+
+\begin{itemize}
+\item Released latest version after Jan 1, 2018
+\item Contains more than 1K starts, if on GitHub  
+\item Uses a public issue tracker
+\end{itemize}
+
+The first criterion focuses on actively maintained projects whereas
+the second criterion focuses on popular cases. As we wanted to report
+bugs, we also looked for project with public issue trackers.
+Table~\ref{tab:engines} shows the engines we selected in this
+study. We made an exception to the second criterion with
+XS~\Fix{cite}. As the project is young, \Fix{created in xx.yy.zz}), we
+thought there was insufficient time to obtain 1K stars for XS. We
+still considered this project as it seems to be attracting interest
+from the community\Fix{is this true?}. It is worth noting that we used
+JSVU~\cite{jsvu} to automatically install and configure versions of
+different JS engines in our host environment. This is important as we
+aim to use the most recent stable versions of each engine as to avoid
+reporting old and already-fixed bugs to developers.
+
+\begin{table}[t]
+  \centering
+  \caption{\label{tab:engines}Engines Analyzed}
+  \begin{tabular}{ccr}
+    \toprule
+    Name & URL & \# Stars \\
+    \midrule
+    MS's Chakra & \cite{chakra2018repo} & - \\
+    Google's v8 & \cite{v82018repo} & - \\
+    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
+    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
+   \bottomrule     
+  \end{tabular}
+\end{table}
 
@@
     \toprule
-    TestSuite & Source & \# JS files \\
+    Name & Source & \# JS files \\
     \midrule

### 2018-07-12 paper/paper.tex
pass on intro

@@
 approach that has been applied in a variety of contexts to find
-functional
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
+functional bugs in
+software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
 automates test generation in scenarios where multiple implementations
-of a system exist. It leverages the diversity across system's
+of a system exist. DT leverages the diversity across system's
 implementations to detect anomalous behavior.
 %% WHAT WE DID
-This paper reports the results of a study we conducted to assess the
-ability of DT to find bugs on \js{} engines.  We analyzed
-the impact of two orthogonal dimensions: test mining and fuzzing. The
-first dimension, test mining, considers the effect that \js{} test
-files mined from the repository of a given open-source engine have in
-detecting functional bugs in other engines. The second dimension,
-fuzzing, considers the impact of fuzzing the mined files in bug
-detection.
+This paper reports the results of a study we conducted to (i) assess
+the reliability of existing JS engines and to (ii) evaluate the
+importance of different factors when using DT for bug finding. More
+precisely, we analyzed the impact of two orthogonal factors in the use
+of DT: test mining and fuzzing. The first dimension, test mining,
+considers the effect that \js{} test files mined from the repository
+of a given open-source engine have in detecting functional bugs in
+other engines. The second dimension, fuzzing, considers the impact of
+fuzzing the mined files in bug detection.
 %% WHAT WE FOUND

### 2018-07-13 paper/paper.tex
adding R scripts

@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 20 0 0,clip,width=0.25\textwidth]{R/barplot}  
+  \caption{\label{fig:workflow}HI and LO warnings reports by each fuzzer.}
+\end{figure}
+
 \Igor{
@@
 
-\subsection{False Positives Bugs}
+\subsection{False Positives}
 

### 2018-07-13 paper/paper.tex
minor fixes

@@
 Information Technology since 1996~\cite{es6-website}.
-The latest version of EcmaScript commonly called ES6
-
-\Fix{to appear}
+Along the year, a new version of EcmaScript (the latest version is ES2017) adds
+new features and minor fixes for the language. \Fix{discutir mais sobre isso}
 
@@
 anomaly was observed during the execution of functions from standard JS
-libraries. For example, according to the latest version of ES6 specification\cite{es6-spec},
-they
+libraries.
 \Mar{what is that exactly? can we cite? is that only spec or
@@
   functions/interfaces that you mentioned to me the other day?}.
+For example, the latest version of ES specs~\cite{es6-spec} describes that,
+the function \CodeIn{Number.toPrecision(precision)}, in general,
+returns a String containing the Number value represented either 
+in decimal exponential notation or in decimal fixed notation, 
+if precision is defined~\cite{es6-toPrecision}. The Number object uses a 
+property called
+
 \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
@@
   \begin{lstlisting}
-seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
-throw new Error("Test Failed");
-  ^
-Error: Test Failed
-  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
-  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
 \end{lstlisting}
 \normalsize
-\caption{Warning captured as HI priority.}
+\caption{Warning captured as LO priority.}
 \label{fig:hi-priority}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering
-\begin{minipage}{.45\textwidth}
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
-  void code()
-  {
-
-  }
-  \end{lstlisting}
-  \end{minipage}\vfill
-  \begin{minipage}{.45\textwidth}
-    \scriptsize
-    \lstset{escapeinside={@}{@},
-      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-      basicstyle=\ttfamily\scriptsize, boxpos=c,
-      numberstyle=\tiny,
-      morekeywords={assertEq, var, yield, in, function, 
-      typeof, return, throw, new, Error, if},
-    }
-  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
-  void code()
-  {
-
-  }
-  \end{lstlisting}
-  \end{minipage}
-  \caption{Warning captured as HI priority.}
-  \label{fig:lo-priority}
 \end{figure}
@@
 tests in all engines.\Mar{not entirely clear what you did to support
-  this.$\rightarrow$}\Igor{wip}\Mar{apenas explique o que fez (mesmo
+  this.$\rightarrow$}\Mar{apenas explique o que fez (mesmo
   que em portugues). isto nao deveria levar tempo que justifique

### 2018-07-13 paper/paper.tex
update engines

@@
 actually code as most of java.* libraries.}
+\Igor{seems like an API. They define the language behavior; grammar;
+values to static variables; the methods for each "class"(Object)...
+These irregularities appears on engine implementation, 
+maybe an wrong if statement and so on.}
 We found that different engines often check pre-conditions of those
@@
   functions/interfaces that you mentioned to me the other day?}.
-For example, the latest version of ES specs~\cite{es6-spec} describes that,
+\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
 the function \CodeIn{Number.toPrecision(precision)}, in general,
-returns a String containing the Number value represented either 
-in decimal exponential notation or in decimal fixed notation, 
-if precision is defined~\cite{es6-toPrecision}. The Number object uses a 
-property called
-
+if precision is defined the method returns a String 
+containing the Number value represented either 
+in decimal exponential notation or in decimal 
+fixed notation~\cite{es6-toPrecision}. The Number object uses a 
+property that the specification describes as approximately so when we use 
+toPrecision with a bigger precision, the values of each engine may vary, this
+could be considered as a case of incompatibility by engine design.}
+In those cases, our infrastructure would observe a discrepancy that is more likely to
+be associated with a bug in the (fuzzed) test; not the code. Although
+we did find real bugs from warnings in the LO group, the proportion
+was much lower compared to the HI group--only 12\% of the reals bugs
+we found originated from the LO category.
 \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
@@
 the process and add a output message of a TIMEOUT error.}
-In those cases,
-our infrastructure would observe a discrepancy that is more likely to
-be associated with a bug in the (fuzzed) test; not the code. Although
-we did find real bugs from warnings in the LO group, the proportion
-was much lower compared to the HI group--only 12\% of the reals bugs
-we found originated from the LO category. \Mar{show real examples of
+
+\Mar{show real examples of
   HI and LO. Use the stacktraces to explain what is going on.}
@@
 % bug high console output
-This a case of a warning reported as HI priority, the Figure~\ref{} shows
-the output console of V8 engine. We consider this case as a HI group due 
-the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}
+% This a case of a warning reported as HI priority, the Figure~\ref{} shows
+% the output console of V8 engine. We consider this case as a HI group due 
+% the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}
 
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
-\end{lstlisting}
-\normalsize
-\caption{Warning captured as LO priority.}
-\label{fig:hi-priority}
-\end{figure}
+% \begin{figure}[h!]
+%   \centering
+%   \scriptsize
+%   \lstset{escapeinside={@}{@},
+%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%     numberstyle=\tiny,
+%     morekeywords={assertEq, var, yield, in, function, 
+%     typeof, return, throw, new, Error, if},
+%   }
+%   \begin{lstlisting}
+% \end{lstlisting}
+% \normalsize
+% \caption{Warning captured as LO priority.}
+% \label{fig:hi-priority}
+% \end{figure}
 
 % no-bug low console output
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
-\end{lstlisting}
-\normalsize
-\caption{Warning captured as HI priority.}
-\label{fig:lo-priority}
-\end{figure}
+% \begin{figure}[h!]
+%   \centering
+%   \scriptsize
+%   \lstset{escapeinside={@}{@},
+%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%     numberstyle=\tiny,
+%     morekeywords={assertEq, var, yield, in, function, 
+%     typeof, return, throw, new, Error, if},
+%   }
+%   \begin{lstlisting}
+% \end{lstlisting}
+% \normalsize
+% \caption{Warning captured as HI priority.}
+% \label{fig:lo-priority}
+% \end{figure}
 
@@
 }
-
-\subsection{ES6 design}
-\Fix{to appear}
 
@@
     \midrule
-    MS's Chakra & \cite{chakra2018repo} & - \\
-    Google's v8 & \cite{v82018repo} & - \\
+    MS's Chakra & \cite{chakra2018repo} & 7200+ \\
+    Google's v8 & \cite{v82018repo} & 9800+ \\
     Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
     Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
+    Mozilla's Rhino & \cite{rhino2018repo} & 1800+ \\
+    JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
    \bottomrule     

### 2018-07-13 paper/paper.tex
fixes

@@
 Information Technology since 1996~\cite{es6-website}.
-Along the year, a new version of EcmaScript (the latest version is ES2017) adds
+Every year, a new version of EcmaScript (the latest version is ES2017) adds
 new features and minor fixes for the language. \Fix{discutir mais sobre isso}
@@
 we did find real bugs from warnings in the LO group, the proportion
-was much lower compared to the HI group--only 12\% of the reals bugs
+was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
 we found originated from the LO category.
@@
 \Igor{
-  We defined if an warning is in HI or LO group according to console output.
+  We defined if a warning is in HI or LO group according to console output.
   The error stream in the output shows relevant informations that we can 
-  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
-  considered as a HI group, the stream output came from V8 engine. The error message 
-  shows informations related to the assertion code (see at line 2) 
-  that thows an Error exception. This case was considered as HI groups and after 
-  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
+  process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
+  outputs based on the stream output came from Chakra engine. 
+  % The error message shows informations related to the assertion code (see at line 2) 
+  % that thows an Error exception. This case was considered as HI groups and after 
+  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
 }
+
+% \begin{figure}[h!]
+%   \centering
+%   \scriptsize
+%   \lstset{escapeinside={@}{@},
+%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%     numberstyle=\tiny,
+%     morekeywords={assertEq, var, yield, in, function, 
+%     typeof, return, throw, new, Error, if},
+%   }
+% \begin{lstlisting}
+
+% \end{lstlisting}
+% \normalsize
+% \caption{Warning captured as HI priority.}
+% \label{fig:hi-priority}
+% \end{figure}
 
@@
 % \begin{lstlisting}
+% function test() {
+%   var buffer = new ArrayBuffer(64);
+%   var view = new DataView(buffer);
+%   view.setInt8 (0, 0x80);
+%   -return view.getInt8(0) === -0x80;
+
+%   // radamsa fuzzing
+%   +return view.getInt8(-1770523502845470856862803727694) === -0x80;
+%   }
+
+%   if (!test())
+%       throw new Error("Test Failed");
 % \end{lstlisting}
 % \normalsize
-% \caption{Warning captured as LO priority.}
+% \caption{Warning captured as HI priority.}
 % \label{fig:hi-priority}
@@
 study. We made an exception to the second criterion with
-XS~\Fix{cite}. As the project is young, \Fix{created in xx.yy.zz}), we
+XS~\Fix{cite}. As the project is young, created in Oct 2017, we
 thought there was insufficient time to obtain 1K stars for XS. We
 still considered this project as it seems to be attracting interest
-from the community\Fix{is this true?}. It is worth noting that we used
+from the community\Fix{is this true?}
+\Igor{eu pensei sobre isso, acho que nao eh relevante colocar o XS sendo 
+que ele eh uma engine para iot/embarcados, temos como exemplo o 
+JerryScript que tambem tem o mesmo proposito e esta ha bem mais tempo
+que ele. Por mim, utilizamos apenas o Jerry ou os dois (e compara-los ja que 
+sao similares), oq vc acha?}. It is worth noting that we used
 JSVU~\cite{jsvu} to automatically install and configure versions of
@@
 Section~\ref{sec:methodology:engines} and four other engines.
-
-\Mar{vc. jah nao fala disto no paragrafo a seguir? se sim, junte os dois.}
-We
-implemented minor changes on test files with fixable file dependencies. For
-example, some of the files used assertion functions defined in their
-projects; we replaced those with our definitions.\Mar{not sure if this
-  is a good example; why one would like to redefine assertion? why
-  didn't you incorporate the assertion function to your infra?}
-
 Table~\ref{tab:test-suites} shows the JS sources we considered for
@@
 distinct frameworks for testing and require external libraries to run
-their testing suites. For these projects, we needed to make small
+their testing suites. 
+For these projects, we needed to make small
 changes in the testing infrastructure to be able to uniformly run
-tests in all engines.\Mar{not entirely clear what you did to support
-  this.$\rightarrow$}\Mar{apenas explique o que fez (mesmo
-  que em portugues). isto nao deveria levar tempo que justifique
-  escrever wip.}We aimed to use only the JS file with minor fixes to
-support our environment. These fixes are composed by an assertion
-function that throws an Error that we can capture by our
-infraestruture.
+tests in all engines. For example, some of the files does not use assertion 
+functions defined in their projects; we replaced those with our definitions.
+\Mar{not sure if this
+  is a good example; why one would like to redefine assertion? why
+  didn't you incorporate the assertion function to your infra?}
+\Igor{sim, poderiamos fazer isso. Porem, lembro que alguns testcases por exemplo usam 
+algo diferente de "assert", outras usam alguma funcao interna 
+que apenas uma engine suporta. Eu posso analisar melhor aqui nossas seeds 
+e ver um jeito global de resolver isso, como se fosse um "shell.js" da nossa 
+ferramenta.}
 
@@
     \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & WebKit \\ 
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & LO & WebKit \\ 
     2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\

### 2018-07-13 paper/paper.tex
added xs info

@@
     JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+    Moddable's XS & \cite{xs2018repo} & 140+ \\
    \bottomrule     

### 2018-07-14 paper/paper.tex
engine tables

--- 2018-07-13 paper/paper.tex
@@
   \caption{\label{tab:engines}Engines Analyzed}
-  \begin{tabular}{ccr}
+  \begin{tabular}{cccr}
     \toprule
-    Name & URL & \# Stars \\
+    Group & Name & URL & \# Stars \\
     \midrule
-    MS's Chakra & \cite{chakra2018repo} & 7200+ \\
-    Google's v8 & \cite{v82018repo} & 9800+ \\
-    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
-    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
-    Mozilla's Rhino & \cite{rhino2018repo} & 1800+ \\
-    JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
+    Google & v8 & \cite{v82018repo} & 9800+ \\
+    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
+    Moddable & XS & \cite{xs2018repo} & 140+ \\
+    \midrule
+    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
+    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
    \bottomrule     

### 2018-07-14 paper/paper.tex
pass on section III

@@
 Every year, a new version of EcmaScript (the latest version is ES2017) adds
-new features and minor fixes for the language. \Fix{discutir mais sobre isso}
+new features and minor fixes for the language. \Fix{discutir mais
+  sobre isso}
+
+\Mar{what is that exactly? can we cite? is that only spec or actually
+  code as most of java.* libraries.}  \Igor{seems like an API. They
+  define the language behavior; grammar; values to static variables;
+  the methods for each "class"(Object)...  These irregularities
+  appears on engine implementation, maybe an wrong if statement and so
+  on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
+  explanation in some forum/tutorial and explain **when** you
+  undertand the JS ecosystem design and can explain with confidence.}
+
+\Mar{explain what is an **acceptable** incompatibilities. cite example
+bug reports.}
+\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
+the function \CodeIn{Number.toPrecision(precision)}, in general,
+if precision is defined the method returns a String 
+containing the Number value represented either 
+in decimal exponential notation or in decimal 
+fixed notation~\cite{es6-toPrecision}. The Number object uses a 
+property that the specification describes as approximately so when we use 
+toPrecision with a bigger precision, the values of each engine may vary, this
+could be considered as a case of incompatibility by engine
+design.}\Mar{I don't understand the example very well and don't understand the
+  relationship with HI/LO.}
 
@@
 groups, reflecting their likelihood to manifest a real bug. Warnings
-in the HI group are associated with the cases when the anomaly has been
-detected during the execution of the test code or its close neighborhood\Comment{ as
-  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
-  are considered HI group as well. The rationale is that
-the test in this group executed without violating any internal checks
-of the API. In constrast, warnings in the LO group reflect the cases where the
-anomaly was observed during the execution of functions from standard JS
-libraries.
-\Mar{what is that exactly? can we cite? is that only spec or
-actually code as most of java.* libraries.}
-\Igor{seems like an API. They define the language behavior; grammar;
-values to static variables; the methods for each "class"(Object)...
-These irregularities appears on engine implementation, 
-maybe an wrong if statement and so on.}
-We found that different engines often check pre-conditions of those
-functions differently. It can happen, for example, that one engine
-enforces a weaker pre-condition compared to another.
+in the HI group are associated with the cases where the anomaly has
+been detected in during the execution of test code or its close
+%% the rationale we provide is related to the above; not crashes
+neighborhood. The rationale is that the test in this group executed
+without violating any internal checks of the API. In constrast,
+warnings in the LO group reflect the cases where the anomaly was
+observed during the execution of functions from standard JS libraries\Fix{check}.
+  We found that different engines often check pre-conditions of
+those functions differently. It can happen, for example, that one
+engine enforces a weaker pre-condition compared to another.
 % \Mar{why is that?
@@
 % properly implemented those checks. Explain and give example.}
-\Igor{these cases happen because the specification describes how a function
-should work, however the internal implementation is defined by the
-engine developers}\Mar{If you confirm that there is no code in specs
-  (see comment above), what would be those abstract
-  functions/interfaces that you mentioned to me the other day?}.
-\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
-the function \CodeIn{Number.toPrecision(precision)}, in general,
-if precision is defined the method returns a String 
-containing the Number value represented either 
-in decimal exponential notation or in decimal 
-fixed notation~\cite{es6-toPrecision}. The Number object uses a 
-property that the specification describes as approximately so when we use 
-toPrecision with a bigger precision, the values of each engine may vary, this
-could be considered as a case of incompatibility by engine design.}
+%% \Igor{these cases happen because the specification describes how a function
+%% should work, however the internal implementation is defined by the
+%% engine developers}\Mar{If you confirm that there is no code in specs
+%%   (see comment above), what would be those abstract
+%%   functions/interfaces that you mentioned to me the other day?}.
 In those cases, our infrastructure would observe a discrepancy that is more likely to
-be associated with a bug in the (fuzzed) test; not the code. Although
+be associated with a bug in the fuzzed test; not the code. Although
 we did find real bugs from warnings in the LO group, the proportion
@@
 we found originated from the LO category.
-\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
-due the capacity of a fuzzer add an infinite repetition statement. We expected that
-each test process can running utmost 5 seconds, if exceed this condition we stop 
-the process and add a output message of a TIMEOUT error.}
 
-\Mar{show real examples of
-  HI and LO. Use the stacktraces to explain what is going on.}
+% I think this will make the definition of HI/LO weaker. We can
+% elaborate this later. for example, in the evaluation.
+%% \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
+%% due the capacity of a fuzzer add an infinite repetition statement. We expected that
+%% each test process can running utmost 5 seconds, if exceed this condition we stop 
+%% the process and add a output message of a TIMEOUT error.}
 
@@
   % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
-}
+}\Mar{igor, first add the real example then draft the discussion}
 
@@
   \end{itemize}
-}
+}\Mar{i think this is not the proper place to
+  add this. discuss this with me.}
 

### 2018-07-14 paper/paper.tex
pass on Section IV

@@
 
-The first criterion focuses on actively maintained projects whereas
-the second criterion focuses on popular cases. As we wanted to report
-bugs, we also looked for project with public issue trackers.
-Table~\ref{tab:engines} shows the engines we selected in this
-study. We made an exception to the second criterion with
-XS~\Fix{cite}. As the project is young, created in Oct 2017, we
-thought there was insufficient time to obtain 1K stars for XS. We
-still considered this project as it seems to be attracting interest
-from the community\Fix{is this true?}
-\Igor{eu pensei sobre isso, acho que nao eh relevante colocar o XS sendo 
-que ele eh uma engine para iot/embarcados, temos como exemplo o 
-JerryScript que tambem tem o mesmo proposito e esta ha bem mais tempo
-que ele. Por mim, utilizamos apenas o Jerry ou os dois (e compara-los ja que 
-sao similares), oq vc acha?}. It is worth noting that we used
-JSVU~\cite{jsvu} to automatically install and configure versions of
+We look for highly-maintained (as per the first criterion) and popular
+(as per the second criterion) projects. As we wanted to report bugs,
+we also looked for project with public issue trackers.
+It is worth noting that we used
+GoogleChromeLab's JSVU~\cite{jsvu} to automatically install and configure versions of
 different JS engines in our host environment. This is important as we
@@
 
+%% Table~\ref{tab:engines} shows the engines we selected in this
+%% study. We made an exception to the second criterion with
+%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
+%% thought there was insufficient time to obtain 1K stars for XS. We
+%% still considered this project as it seems to be attracting interest
+%% from the community\Fix{is this true?}
+
 \begin{table}[t]
   \centering
-  \caption{\label{tab:engines}Engines Analyzed}
+  \caption{\label{tab:engines}Engines Analyzed.}
   \begin{tabular}{cccr}
@@
     Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
-    Moddable & XS & \cite{xs2018repo} & 140+ \\
+%    Moddable & XS & \cite{xs2018repo} & 140+ \\
     \midrule
@@
 looked for self-contained tests from JS engine projects, initially
-using the GitHub REST API\Fix{cite}. We noticed that some of the tests
-we found depend on external libraries, which not all engines we use
-(see Section~\ref{sec:methodology:engines}) support. We decided to
-discard those. For example, many tests we found required a
-nodejs\Fix{cite} runtime for execution. Overall, we considered the
-test suites of three of the four engines mentioned in
+using the GitHub REST API~\cite{github-rest-api}. We noticed that some
+of the tests we found depend on external libraries, which not all
+engines we use (see Section~\ref{sec:methodology:engines}) support. We
+decided to discard those. For example, many tests we found required a
+Node.js runtime~\cite{node} for execution. We considered the offical
+TC-39~\cite{tc39-github} conformance test suite for the ECMA262
+specification~\cite{ecmas262-spec}. Furthermore, we considered test
+suites of three of the four engines mentioned in
 Section~\ref{sec:methodology:engines} and four other engines.
@@
 each of the selected projects. Overall, we found a total of
-\totfiles{} JS files. It is worth noting that some projects use
+\totfiles{} JS files. It is worth noting that some test suites use
 distinct frameworks for testing and require external libraries to run
-their testing suites. 
-For these projects, we needed to make small
-changes in the testing infrastructure to be able to uniformly run
-tests in all engines. For example, some of the files does not use assertion 
-functions defined in their projects; we replaced those with our definitions.
-\Mar{not sure if this
-  is a good example; why one would like to redefine assertion? why
-  didn't you incorporate the assertion function to your infra?}
-\Igor{sim, poderiamos fazer isso. Porem, lembro que alguns testcases por exemplo usam 
-algo diferente de "assert", outras usam alguma funcao interna 
-que apenas uma engine suporta. Eu posso analisar melhor aqui nossas seeds 
-e ver um jeito global de resolver isso, como se fosse um "shell.js" da nossa 
-ferramenta.}
+their testing suites.  For these projects, we needed to make small
+changes in the testing infrastructure to be able to run the tests
+uniformly across all engines. More precisely, we needed to mock
+functions, related to the test harness, which are only available to
+certain engines.
 
@@
   \centering
-  \caption{\label{tab:test-suites}Test Suites
-  % \Mar{try to use a single
-  %     name (if possible) to facilitate reference in the paper. Use the
-  % full path in the URL (citation) to indicate where one can find those
-  % files.}
-  }
+  \caption{\label{tab:test-suites}Test Suites. The sections of the
+    table show, respectively, the TC-39 conformance test suite, suites
+    from engines we analyzed, and other suites.}
   \begin{tabular}{ccr}
@@
     Name & Source & \# JS files \\
+    \midrule
+    TS-39 & \cite{ecma262-conformance-suite} & \Fix{-} \\
     \midrule

### 2018-07-16 paper/paper.tex
pass on results

--- 2018-07-14 paper/paper.tex
@@
   \caption{\label{tab:engines}Engines Analyzed}
-  \begin{tabular}{cccr}
+  \begin{tabular}{ccr}
     \toprule
-    Group & Name & URL & \# Stars \\
+    Name & URL & \# Stars \\
     \midrule
-    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
-    Google & v8 & \cite{v82018repo} & 9800+ \\
-    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
-    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
-    Moddable & XS & \cite{xs2018repo} & 140+ \\
-    \midrule
-    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
-    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
+    MS's Chakra & \cite{chakra2018repo} & 7200+ \\
+    Google's v8 & \cite{v82018repo} & 9800+ \\
+    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
+    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
+    Mozilla's Rhino & \cite{rhino2018repo} & 1800+ \\
+    JerryScript's JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+    Moddable's XS & \cite{xs2018repo} & 140+ \\
    \bottomrule     
@@
 \Igor{
+  After ran all our mined seeds (see \ref{sec:seeds}) without fuzzing we found 
+  a total of \Fix{arg}
   Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 

### 2018-07-16 paper/paper.tex
fix seeds table

--- 2018-07-14 paper/paper.tex
@@
     \midrule
-    TS-39 & \cite{ecma262-conformance-suite} & \Fix{-} \\
+    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
     \midrule
-    Mozilla & \cite{mozilla} & 32,414 \\
+    Mozilla & \cite{mozilla} & 2,633 \\
     V8 & \cite{v8} & 64 \\
@@
 \Igor{
-  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
-  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
-  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
+  No total, foram obtidos \nofuzzingAll{} warnings, sendo estes \nofuzzingHigh{}
+  com priority HI e \nofuzzingLow{} do grupo LO. Nos analisamos cuidadosamente
+  cada warning reportado pela ferramenta, a fim de encontrar bugs reais nos engenhos
+  javascript. Nosso estudo revelou que dos \nofuzzingHigh{} do grupo HI, 
+  \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
+  \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
+
+  A diversidade de suites de testes influencia na busca de bugs nao descobertos
+  pelo proprio projeto do engenhos. Por exemplo, cerca de \Fix{62} warnings 
+  foram obtidos do repositorio da Mozilla, 12 na suite do JerryScript, 
+  9 sao do WebKit e 2 sao do V8 e Duktape, respectivamente. 
+  Os warnings encontrados em sua maioria sao dos engenhos do 
+  Chakra e do JavascriptCore.
+
+  A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
   quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
@@
   \Fix{discuss}
+
+  % Nosso estudo revelou que dos \tableBugsNum{} bugs reportados pelo nosso time, 
+  % apenas \Fix{10} nao foram fuzzados \Fix{43.4\%},
+  % Apesar do engenhos do V8 e SpiderMonkey
+  % serem os mais robustos em relacao aos demais, tambem 
+  % foram encontrados warnings nestes engenhos, porem
 }
@@
     \midrule
-    23 & 7/12 & \crossmark & Chakra & New  & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
+    23 & 7/12 & \crossmark & Chakra & Dup (\#10) & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
+    24 & 7/17 & \crossmark & SpiderMonkey & New & \href{https://bugzilla.mozilla.org/show_bug.cgi?id=1476321}{\#1476321} & HI & JerryScript\\
    \bottomrule
@@
 JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
-showed that the triage process is very slow for that engine. As of
-now, we did not find any new bug on SpiderMonkey and V8; the bugs we
-found were duplicates and were not reported. Finally, it is
-worth noting that 8 of the 19 JS files that manifested
+showed that the triage process is very slow for that engine. 
+\Igor{
+The bugs reported on Chakra's bug tracker was defined as confirmed, 
+however the bugs are included on a milestone for the next release
+following an internal priority.
+}
+As of now, we did not find any new bug on SpiderMonkey and V8; 
+the bugs we found were duplicates and were not reported. Finally, it is
+worth noting that \Fix{11 of the 19} JS files that manifested
 discrepancies were \emph{not} produced with fuzzing (column

### 2018-07-18 paper/paper.tex
comment unrelated text and adding important discussion with c. holler

--- 2018-07-16 paper/paper.tex
@@
 
+\subsection{Expected Inconsistencies}
+
+\Mar{answer from C. Holler. Think through this...}
+
+1) The stack depth in JS is often close to the real (native) C stack depth, nevertheless observable by JS through recursion.
+This causes differential behavior even on the same engine when JITs are enabled or disabled, as the stack frame sizes vary.
+LangFuzz in particular produces a lot of recursions and hits these problems even more often than jsfunfuzz.
+
+2) JS has some "undefined behavior", such as the enumeration order of object properties in certain cases.
+In our engine, we have an --enable-more-deterministic mode (build option) to solve some of these issues.
+
+3) JS naturally has some observable differential behavior in global objects, e.g.
+Math.random, Date, etc.
+These can often be mocked to solve these issues, but fuzzers can be surprisingly effective to find more of these sources or even get the old objects back somehow.
+
 % \begin{figure}[h!]
@@
 
-\Mar{can we detect dups mining issue trackers?}
-\Igor{
-  acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
-  Tenho umas consideracoes:
-  \begin{itemize}
-    \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
-    se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
-    \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
-    \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
-  \end{itemize}
-}\Mar{i think this is not the proper place to
-  add this. discuss this with me.}
+%% \Mar{can we detect dups mining issue trackers?}
+%% \Igor{
+%%   acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
+%%   Tenho umas consideracoes:
+%%   \begin{itemize}
+%%     \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
+%%     se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
+%%     \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
+%%     \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
+%%   \end{itemize}
+%% }\Mar{i think this is not the proper place to
+%%   add this. discuss this with me.}
 
@@
 \Igor{  
-  After ran all our mined seeds (see \ref{sec:seeds}) without fuzzing we found 
-  a total of \Fix{arg}
   Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 

### 2018-07-18 docs/google-research-awards-latam/main.tex

@@
 test (or its close neighborhood) whereas the LO group includes the
-rest of the warnings. \Igor{We found empirically that 88\% of the
-issues reported are included in the HI group and 58\% of them was confirmed}.
+rest of the warnings. We found that 88\% of the
+issues reported are from the HI group.
 
@@
 %%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
-%%  LocalWords:  cgi tmp
+%%  LocalWords:  cgi tmp Cidade ToNumber LibFuzzer

### 2018-07-18 paper/paper.tex
moving text
pass on intro

--- 2018-07-18 paper/paper.tex
@@
 of a system exist. DT leverages the diversity across system's
-implementations to detect anomalous behavior.
+implementations to detect anomalous behavior. For example, Mozilla
+runs JS files--created with the grammar-based fuzzer
+jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
+SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
+across configurations. They use this technique since 2002 and have
+been able to find over 270 bugs since
+then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
+Cross-engine differential testing checks correctness by comparing the
+output produced by \emph{different} engines on a given
+input~\cite{patra2016learning}. The availability on the web of public
+implementations of JS engines (see Table~\ref{tab:engines}) and test
+suites makes this bug-finding approach very appealing.
+
 %% WHAT WE DID
@@
   relationship with HI/LO.}
+
+\subsection{Randomness and Undefined Behavior}
+
+\Mar{answer from C. Holler. Think through this...}
+
+1) The stack depth in JS is often close to the real (native) C stack depth, nevertheless observable by JS through recursion.
+This causes differential behavior even on the same engine when JITs are enabled or disabled, as the stack frame sizes vary.
+LangFuzz in particular produces a lot of recursions and hits these problems even more often than jsfunfuzz.
+
+2) JS has some "undefined behavior", such as the enumeration order of object properties in certain cases.
+In our engine, we have an --enable-more-deterministic mode (build option) to solve some of these issues.
+
+3) JS naturally has some observable differential behavior in global objects, e.g.
+Math.random, Date, etc.
+These can often be mocked to solve these issues, but fuzzers can be surprisingly effective to find more of these sources or even get the old objects back somehow.
 
@@
 }\Mar{igor, first add the real example then draft the discussion}
-
-\subsection{Expected Inconsistencies}
-
-\Mar{answer from C. Holler. Think through this...}
-
-1) The stack depth in JS is often close to the real (native) C stack depth, nevertheless observable by JS through recursion.
-This causes differential behavior even on the same engine when JITs are enabled or disabled, as the stack frame sizes vary.
-LangFuzz in particular produces a lot of recursions and hits these problems even more often than jsfunfuzz.
-
-2) JS has some "undefined behavior", such as the enumeration order of object properties in certain cases.
-In our engine, we have an --enable-more-deterministic mode (build option) to solve some of these issues.
-
-3) JS naturally has some observable differential behavior in global objects, e.g.
-Math.random, Date, etc.
-These can often be mocked to solve these issues, but fuzzers can be surprisingly effective to find more of these sources or even get the old objects back somehow.
 

### 2018-07-19 paper/paper.tex
pass on results

--- 2018-07-18 paper/paper.tex
@@
     \midrule
-    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
+    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 45,144 \\
     \midrule
@@
     \midrule
-     &  & 36,452 \\
+     &  & 51,815 \\
    \bottomrule     
@@
   No total, foram obtidos \nofuzzingAll{} warnings, sendo estes \nofuzzingHigh{}
-  com priority HI e \nofuzzingLow{} do grupo LO. Nos analisamos cuidadosamente
-  cada warning reportado pela ferramenta, a fim de encontrar bugs reais nos engenhos
-  javascript. Nosso estudo revelou que dos \nofuzzingHigh{} do grupo HI, 
+  pertencentes aos buckets com prioridade HI e \nofuzzingLow{} da prioridade LO. 
+  N\'os analisamos com rigor cada log gerado, sempre checando as 
+  especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
+  javascript que violem condições da especificacao ou apresentem discrepancias
+  entre outputs dos engenhos.
+  Nosso estudo revelou que dos \nofuzzingHigh{} buckets do grupo HI, 
   \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
@@
     \midrule    
-    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
+    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
     12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
@@
     18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
-    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
+    19 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
     20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
-    21 & 7/10 & quickfuzz & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
-    \midrule
-    \multirow{2}{*}{22}  & \multirow{2}{*}{7/10} &  \multirow{2}{*}{\crossmark} & Chakra & Confirmed & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & \multirow{2}{*}{HI} & \multirow{2}{*}{JerryScript}\\
-                        &  &                       &
-    JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187519}{\#187519}  &   & \\
-    \midrule
-    23 & 7/12 & \crossmark & Chakra & Dup (\#10) & \href{https://github.com/Microsoft/ChakraCore/issues/5453}{\#5453} & HI & JerryScript\\
-    24 & 7/17 & \crossmark & SpiderMonkey & New & \href{https://bugzilla.mozilla.org/show_bug.cgi?id=1476321}{\#1476321} & HI & JerryScript\\
+    22 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & HI & JerryScript\\
+    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
+    23 & 7/18 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
+    24 & 7/18 & \crossmark & JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & HI & JerryScript\\
    \bottomrule

### 2018-07-19 paper/paper.tex
pass on results

@@
 
-\Igor{
-  We defined if a warning is in HI or LO group according to console output.
-  The error stream in the output shows relevant informations that we can 
-  process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
-  outputs based on the stream output came from Chakra engine. 
+% \Igor{
+%   We defined if a warning is in HI or LO group according to console output.
+%   The error stream in the output shows relevant informations that we can 
+%   process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
+%   outputs based on the stream output came from Chakra engine. 
   % The error message shows informations related to the assertion code (see at line 2) 
@@
   % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
-}\Mar{igor, first add the real example then draft the discussion}
+% }\Mar{igor, first add the real example then draft the discussion}
 
@@
 \Igor{
-  No total, foram obtidos \nofuzzingAll{} warnings, sendo estes \nofuzzingHigh{}
-  pertencentes aos buckets com prioridade HI e \nofuzzingLow{} da prioridade LO. 
-  N\'os analisamos com rigor cada log gerado, sempre checando as 
+  No total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
+  pertencentes aos buckets com prioridade HI e \nofuzzLowTotal{} da prioridade LO. 
+  Durante 3 meses, n\'os analisamos com rigor cada log gerado, sempre checando as 
   especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
   javascript que violem condições da especificacao ou apresentem discrepancias
-  entre outputs dos engenhos.
-  Nosso estudo revelou que dos \nofuzzingHigh{} buckets do grupo HI, 
+  entre as saidas de cada engenhos.
+  Nosso estudo revelou que dos \nofuzzHighTotal{} buckets do grupo HI, 
   \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
@@
 
-  A diversidade de suites de testes influencia na busca de bugs nao descobertos
-  pelo proprio projeto do engenhos. Por exemplo, cerca de \Fix{62} warnings 
-  foram obtidos do repositorio da Mozilla, 12 na suite do JerryScript, 
-  9 sao do WebKit e 2 sao do V8 e Duktape, respectivamente. 
-  Os warnings encontrados em sua maioria sao dos engenhos do 
-  Chakra e do JavascriptCore.
+  A diversidade de suites de testes influenciou na busca de bugs nao descobertos
+  pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
+  foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
+  foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
+  \nofuzzWebKit{} sao do WebKit e \nofuzzGoogleDuktap{} para o V8 e o Duktape, 
+  os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
+  engines.
 

### 2018-07-20 seeds/JerryJS/regression_edited/array-prototype-foreach.js
Refactoring seeds folder

@@ -1,50 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-// Copyright JS Foundation and other contributors, http://js.foundation
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//     http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-
-var array = ["foo", [], Infinity, 4]
-
-function f(arg1, arg2, arg3) {
-  assert(arg1 === array[arg2]);
-  assert(arg3 === array);
-}
-
-array.forEach(f);
-
-// Checking behavior when unable to get length
-var obj = {};
-Object.defineProperty(obj, 'length', { 'get' : function () {throw new ReferenceError ("foo"); } });
-obj.forEach = Array.prototype.forEach;
-
-try {
-  obj.forEach(f);
-  assert(false);
-} catch (e) {
-  assert(e.message === "foo");
-  assert(e instanceof ReferenceError);
-}
-
-// Checking behavior when unable to get element
-var obj = {}
-obj.length = 1;
-Object.defineProperty(obj, '0', { 'get' : function () {throw new ReferenceError ("foo"); } });
-obj.forEach = Array.prototype.forEach
-
-try {
-  obj.forEach(f);
-  assert(false);
-} catch (e) {
-  assert(e.message === "foo");
-  assert(e instanceof ReferenceError);
-}

### 2018-07-20 seeds/JerryJS/regression_edited/for-parse.js

@@ -1,44 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-// Copyright JS Foundation and other contributors, http://js.foundation
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//     http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-
-function parse(txt) {
-  try {
-    eval(txt)
-    assert(false)
-  } catch (e) {
-    assert(e instanceof SyntaxError)
-  }
-}
-
-parse("for (;;;) print('hello')") 
-parse("for (,,) print('hello')") 
-parse("for (i = 0; i < 10; i++; ) print('i: ' + i)") 
-parse("for (i = 0; i < 10; i++)")
-parse("for i = 0; i < 10; i++ {}")
-parse("for (i = 0;; i < 10; i++) {}")
-parse("for (i = 0; j = 1; i < 10; i++) print('i: '+ i + ' j: ' + j)")
-parse("for (i = 0 j = 5;i<10 || j<10; i++, j++) {}")
-parse("for (i = 0, j = 5; i < 10 || j < 10; i++ j++) {}")
-parse("for (i = 0, j = 5; i < 10 j < 10; i++, j++) {}")
-
-var doubleFor =
-"for (i = 0; i < 5; i++) { "+ 
-"  for (j = 0; j < 5; j++) { print('i: ' + i + ' j: ' + j) }";
-parse(doubleFor)
-
-var doubleFor2 =
-"for (i = 0; i < 5; i++) { "+ 
-"  for (j = 0; j < 5; j++) { print('i: ' + i + ' j: ' + j)";
-parse(doubleFor2)

### 2018-07-20 seeds/JerryJS/regression_edited/global-parsefloat.js

@@ -1,88 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-// Copyright JS Foundation and other contributors, http://js.foundation
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//     http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-
-assert(parseFloat("1") === 1);
-assert(parseFloat("+1") === 1);
-assert(parseFloat("-1") === -1);
-assert(parseFloat("1.2") === 1.2);
-assert(parseFloat("+1.2") === 1.2);
-assert(parseFloat("-1.2") === -1.2);
-assert(parseFloat("1.2e3") === 1200);
-assert(parseFloat("+1.2e3") === 1200);
-assert(parseFloat("-1.2e3") === -1200);
-assert(parseFloat("   \n\t  1.2e3") === 1200);
-assert(parseFloat("03.02e1") === 30.2);
-assert(parseFloat("003.") === 3);
-assert(parseFloat(".2e3") === 200);
-assert(parseFloat("1.e3") === 1000);
-assert(parseFloat("1.2e") === 1.2);
-assert(parseFloat("1.e") === 1);
-assert(parseFloat("1.e3") === 1000);
-assert(parseFloat("1e3") === 1000);
-assert(parseFloat("1e") === 1);
-assert(parseFloat("1.2e3foo") === 1200);
-assert(isNaN(parseFloat("foo1.2e3foo")));
-assert(parseFloat("Infinity") === Infinity);
-assert(parseFloat("-Infinity") === -Infinity);
-assert(parseFloat("Infinityfoo") === Infinity);
-assert(parseFloat("-Infinityfoo") === -Infinity);
-assert(isNaN(parseFloat("")));
-assert(isNaN(parseFloat(".")));
-assert(isNaN(parseFloat("..")));
-assert(isNaN(parseFloat("+")));
[…]

### 2018-07-20 seeds/JerryJS/regression_edited/global.js

@@ -1,17 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-// Copyright JS Foundation and other contributors, http://js.foundation
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//     http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-
-
-assert (this.hasOwnProperty !== undefined);

### 2018-07-20 seeds/JerryJS/regression_edited/logical.js

@@ -1,26 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-// Copyright JS Foundation and other contributors, http://js.foundation
-//
-// Licensed under the Apache License, Version 2.0 (the "License");
-// you may not use this file except in compliance with the License.
-// You may obtain a copy of the License at
-//
-//     http://www.apache.org/licenses/LICENSE-2.0
-//
-// Unless required by applicable law or agreed to in writing, software
-// distributed under the License is distributed on an "AS IS" BASIS
-// WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-// See the License for the specific language governing permissions and
-// limitations under the License.
-
-assert((!false) === true);
-
-assert((true || true) === true);
-assert((false || true) === true);
-assert((false || false) === false);
-assert((true || false) === true);
-
-assert((true && true) === true);
-assert((true && false) === false);
-assert((false && true) === false);
-assert((false && false) === false);

### 2018-07-20 seeds/JerryJS/regression_edited/template_string.js

@@ -1,93 +1,0 @@
-function assert(isTrue){if (! isTrue) { throw new Error('Test failed')}}
-/* Copyright JS Foundation and other contributors, http://js.foundation
- *
- * Licensed under the Apache License, Version 2.0 (the "License");
- * you may not use this file except in compliance with the License.
- * You may obtain a copy of the License at
- *
- *     http://www.apache.org/licenses/LICENSE-2.0
- *
- * Unless required by applicable law or agreed to in writing, software
- * distributed under the License is distributed on an "AS IS" BASIS
- * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
- * See the License for the specific language governing permissions and
- * limitations under the License.
- */
-
-function must_throw (str)
-{
-  try
-  {
-    eval ("switch (1) { default: " + str + "}");
-    assert (false);
-  }
-  catch (e)
-  {
-  }
-
-  try
-  {
-    eval (str);
-    assert (false);
-  }
-  catch (e)
-  {
-  }
-}
-
-var a = 'A';
-var b = 'B';
-
-switch (1)
-{
-default:
-
-  ``
-  `abc`
-  `ab${a+b}${ `x` }c`
-
-  assert (`` === '');
-  assert (`abc` === 'abc');
-  assert (`ab\
-  c` === 'ab  c');
-  assert (`ab
-  c` === 'ab\n  c');
-
-  assert (`prefix${a}` === 'prefixA');
-  assert (`${a}postfix` === 'Apostfix');
-  assert (`prefix${a}postfix` === 'prefixApostfix');
-
-  assert (`${a}${b}` === 'AB');
-  assert (`${a},${b}` === 'A,B');
-  assert (`${a}${b}${a}${b}` === 'ABAB');
-  assert (`${a},${b},${a},${b}` === 'A,B,A,B');
-  assert (`$${a},${b},${a},${b}$` === '$A,B,A,B$');
-
-  assert (`\${}` === '${}');
-  assert (`$\{}` === '${}');
-  assert (`x${  `y` + `z`  }x` === 'xyzx');
-  assert (`x${  `y` , `z`  }x` === 'xzx');
-
-  function f(x) { return x + 1; }
-
-  /* Precedence. */
-  var c = 1;
-  assert (`x${  f(1) * f(2)  }x${ c = 4 }` === 'x6x4');
-  assert (c === 4);
-  assert (`m${0 || 93}n${7 && 0}o` === 'm93n0o');
-
[…]

### 2018-07-20 seeds/Tiny-js.tests/test010.js

@@ -1,6 +1,0 @@
-assert = function(is_true){if (!(is_true)) {throw new Error("Test failed")}} 
-// double function calls
-function a(x) { return x+2; }
-function b(x) { return a(x)+1; }
-result = a(3)==5 && b(3)==6;
-assert(result);

### 2018-07-20 seeds/Tiny-js.tests/test030.js

@@ -1,6 +1,0 @@
-assert = function(is_true){if (!(is_true)) {throw new Error("Test failed")}} 
-// test for array join
-var a = [1,2,4,5,7];
-
-result = a.join(",")=="1,2,4,5,7";
-assert(result);

### 2018-07-20 seeds/grammarinator/test_367bb815afed4d0009f914bbd059b20d.js

@@ -1,1 +1,0 @@
-switch(!{}){};

### 2018-07-20 seeds/grammarinator/test_42547a9852e23843199f3934209f42dd.js

@@ -1,1 +1,0 @@
-continue_໌୯_ేৄ‍︳;break$‌ೌ＿༘

### 2018-07-20 seeds/grammarinator/test_458b20efb625646c03d2624bcc903501.js

@@ -1,1 +1,0 @@
-debuggercontinue

### 2018-07-20 seeds/grammarinator/test_514c050bc1db7b6603afbf740e4b29e2.js

@@ -1,1 +1,0 @@
-var\u5B83=this

### 2018-07-20 seeds/grammarinator/test_5c2d24edf0f3c19a136fa12b2547130b.js

@@ -1,1 +1,0 @@
-$:debugger

### 2018-07-20 seeds/grammarinator/test_7cf2cedde48113974f4f8ec412539f88.js

@@ -1,1 +1,0 @@
-break\u1004‍္;

### 2018-07-20 seeds/grammarinator/test_de29fc1ce381e5a43d7af0b6a95c892d.js

@@ -1,1 +1,0 @@
-break_break

### 2018-07-20 seeds/mozilla/non262/Array/sort-array-with-holes-and-undefined.js

@@ -29,4 +29,4 @@ assertEq(a.hasOwnProperty(3), false);
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/non262/Date/fractions.js

@@ -21,4 +21,4 @@ new Date(0).setMonth(1.5);
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/non262/Function/arguments-property-attributes.js

@@ -95,4 +95,4 @@ assertEq(strictLengthDesc.configurable, true);
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("All tests passed!");
+//print("All tests passed!");

### 2018-07-20 seeds/mozilla/non262/Function/function-bind.js

@@ -285,4 +285,4 @@ assertEq(typeof passim, "function");
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("All tests passed!");
+//print("All tests passed!");

### 2018-07-20 seeds/mozilla/non262/JSON/stringify-toJSON-arguments.js

@@ -31,4 +31,4 @@ assertEq(JSON.stringify(obj), '{"p":17}');
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/non262/extensions/__proto__.js

@@ -50,4 +50,4 @@ assertEq(desc.configurable, true);
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/non262/extensions/function-properties.js

@@ -18,4 +18,4 @@ assertEq(foo.caller, null);
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/non262/extensions/regress-381304.js

@@ -21,7 +21,7 @@ function test()
  
   var obj;
 
-  print('1');
+//print('1');
 
   obj = {
     set inn(value) {this.for = value;}, 
@@ -32,7 +32,7 @@ function test()
   actual = obj.toSource();
   compareSource(expect, actual, summary + ': 1');
 
-  print('2');
+//print('2');
 
   obj = {
     set in(value) {this.for = value;}, 
@@ -43,7 +43,7 @@ function test()
   actual = obj.toSource();
   compareSource(expect, actual, summary + ': 2');
 
-  print('3');
+//print('3');
 
   obj = {
     set inn(value) {this.for = value;}, 
@@ -54,7 +54,7 @@ function test()
   actual = obj.toSource();
   compareSource(expect, actual, summary + ': 4');
 
-  print('4');
+//print('4');
 
   obj = {
     set in(value) {this.for = value;}, 

### 2018-07-20 seeds/mozilla/non262/extensions/regress-480579.js

@@ -27,7 +27,7 @@ function test()
   b = {__proto__: a};
   c = {__proto__: b};
   for (i = 0; i < 2; i++) {
-    print(actual += c.x);
+//printactual += c.x);
     b.x = 2;
   }
 

### 2018-07-20 seeds/mozilla/non262/regress/regress-360969-02.js

@@ -29,4 +29,4 @@ reportCompare(expect, actual, summary);
 
 var stop = new Date();
 
-print('Elapsed time: ' + Math.floor((stop - start)/1000) + ' seconds');
+// print('Elapsed time: ' + Math.floor((stop - start)/1000) + ' seconds');

### 2018-07-20 seeds/mozilla/non262/regress/regress-465220.js

@@ -28,7 +28,7 @@ function test()
     var s = "";
     for (var i = 0; i < 5; i++)
       s += o + o;
-    print(s);
+//prints);
     actual = 'No Exception';
   }
   catch(ex)

### 2018-07-20 seeds/mozilla/non262/syntax/let-as-label.js

@@ -32,4 +32,4 @@ assertThrowsInstanceOf(() => eval(" 'use strict' \n l\\u0065t: 42;"), SyntaxErro
 if (typeof reportCompare === "function")
   reportCompare(true, true);
 
-print("Tests complete");
+//print("Tests complete");

### 2018-07-20 seeds/mozilla/shell.js

@@ -131,6 +131,18 @@
     global.assertEq = assertEq;
   }
 
+  // jsfuzz fix: add assertion function
+  var assert = global.assert;
+  if (typeof assert !== "function") {
+    assert = function assert(condition) {
+      if (!(condition)) {
+        throw new Error("Test failed");
+      }
+    };
+    global.assert = assert;
+  }
+  // end jsfuzz fix
+
   function assertEqArray(actual, expected) {
     var len = actual.length;
     assertEq(len, expected.length, "mismatching array lengths");
@@ -373,7 +385,7 @@
     // if running under reftest, let it handle result reporting.
     if (!runningInBrowser) {
       if (testcase.passed) {
-        print(PASSED + description);
+        // print(PASSED + description);
       } else {
         reportFailure(description + " : " + output);
       }
@@ -532,7 +544,7 @@
   // This function uses the shell's print function. When running tests in the
   // browser, browser.js overrides this function to write to the page.
   function writeHeaderToLog(string) {
-    print(string);
+    // print(string);
   }
   global.writeHeaderToLog = writeHeaderToLog;
 
@@ -577,3 +589,2554 @@
 })(this);
 
 var DESCRIPTION;
+/* -*- indent-tabs-mode: nil; js-indent-level: 2 -*- */
+
+/* This Source Code Form is subject to the terms of the Mozilla Public
+ * License, v. 2.0. If a copy of the MPL was not distributed with this
+ * file, You can obtain one at http://mozilla.org/MPL/2.0/. */
+
+(function(global) {
+
+  /*
+   * completesNormally(CODE) returns true if evaluating CODE (as eval
+   * code) completes normally (rather than throwing an exception).
+   */
+  global.completesNormally = function completesNormally(code) {
+    try {
+      eval(code);
+      return true;
+    } catch (exception) {
+      return false;
+    }
+  }
+
+  /*
+   * raisesException(EXCEPTION)(CODE) returns true if evaluating CODE (as
+   * eval code) throws an exception object that is an instance of EXCEPTION,
+   * and returns false if it throws any other error or evaluates
+   * successfully. For example: raises(TypeError)("0()") == true.
+   */
+  global.raisesException = function raisesException(exception) {
+    return function (code) {
+      try {
+	eval(code);
+	return false;
+      } catch (actual) {
+	return actual instanceof exception;
+      }
+    };
+  };
+
+  /*
[…]

### 2018-07-20 seeds/seeds_info.py

@@ -1,0 +1,45 @@
+import os, glob
+
+def scanfolder(root_path, _format='*.js'):
+    ignore_files = ['assert.js', 'shell.js', 'utils.js', 'run.js']
+    total = []
+    for path, dirs, files in os.walk(root_path):
+        for d in dirs:
+            for f in glob.iglob(os.path.join(path, d, _format)):
+                if os.path.basename(f) not in ignore_files:
+                    total.append(f)
+    return total
+
+pwd = os.path.dirname(os.path.realpath(__file__))
+
+v8_path = os.path.join(pwd, 'v8')
+mozilla_path = os.path.join(pwd, 'mozilla')
+test262_path = os.path.join(pwd, 'test262')
+jsi_path = os.path.join(pwd, 'JSI')
+jerryjs_path = os.path.join(pwd, 'JerryJS')
+tinyjs_path = os.path.join(pwd, 'TinyJS')
+webkitjs_path = os.path.join(pwd, 'WebKit')
+duktape_path = os.path.join(pwd, 'DukTape')
+
+tests_test262 = scanfolder(test262_path)
+tests_mozilla = scanfolder(mozilla_path)
+tests_jerryjs = scanfolder(jerryjs_path)
+tests_webkit = scanfolder(webkitjs_path)
+tests_duktape = scanfolder(duktape_path)
+tests_jsi = scanfolder(jsi_path)
+tests_v8 = scanfolder(v8_path)
+tests_tinyjs = scanfolder(tinyjs_path)
+
+total = len(tests_v8 + tests_mozilla + tests_test262 + tests_jsi + tests_jerryjs + tests_tinyjs + tests_webkit + tests_duktape)
+
+with open('README.md', 'w') as doc:
+    doc.write('# SEED INFO\n')
+    doc.write('## Number of seeds: {}\n'.format(total))
+    doc.write('## Test262: {}\n'.format(len(tests_test262)))
+    doc.write('## Mozilla: {}\n'.format(len(tests_mozilla)))
+    doc.write('## JerryJS: {}\n'.format(len(tests_jerryjs)))
+    doc.write('## WebKit: {}\n'.format(len(tests_webkit)))
+    doc.write('## Duktape: {}\n'.format(len(tests_duktape)))
+    doc.write('## JSI: {}\n'.format(len(tests_jsi)))
+    doc.write('## V8: {}\n'.format(len(tests_v8)))
+    doc.write('## TinyJS: {}\n'.format(len(tests_tinyjs)))

### 2018-07-20 seeds/test262/annexB/language/expressions/template-literal/legacy-octal-escape-sequence-strict.js

@@ -1,0 +1,18 @@
+// Copyright (C) 2014 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+es6id: 12.2.8
+description: >
+    The expression within the template should be evaluated according to the
+    semantics of the surrounding context.
+    The SV of EscapeSequence :: HexEscapeSequence is the SV of the
+    HexEscapeSequence.
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [onlyStrict]
+---*/
+
+// throw new Error("Test262: This statement should not be evaluated.");
+
+`${'\07'}`;

### 2018-07-20 seeds/test262/built-ins/Atomics/wait/nan-for-timeout.js

@@ -1,0 +1,43 @@
+// Copyright (C) 2018 Amal Hussein.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-atomics.wait
+description: >
+  NaN timeout arg should result in an infinite timeout
+info: |
+  Atomics.wait( typedArray, index, value, timeout )
+
+  4.Let q be ? ToNumber(timeout).
+    ...
+    Undefined    Return NaN.
+  5.If q is NaN, let t be +∞, else let t be max(q, 0)
+
+includes: [atomicsHelper.js]
+features: [Atomics, SharedArrayBuffer, TypedArray]
+---*/
+
+const RUNNING = 1;
+
+$262.agent.start(`
+  $262.agent.receiveBroadcast(function(sab) {
+    const i32a = new Int32Array(sab);
+    Atomics.add(i32a, ${RUNNING}, 1);
+
+    $262.agent.report(Atomics.wait(i32a, 0, 0, NaN));  // NaN => +Infinity
+    $262.agent.leaving();
+  });
+`);
+
+const i32a = new Int32Array(
+  new SharedArrayBuffer(Int32Array.BYTES_PER_ELEMENT * 4)
+);
+
+$262.agent.broadcast(i32a.buffer);
+$262.agent.waitUntil(i32a, RUNNING, 1);
+
+// Try to yield control to ensure the agent actually started to wait.
+$262.agent.tryYield();
+
+assert.sameValue(Atomics.wake(i32a, 0), 1, 'Atomics.wake(i32a, 0) returns 1');
+assert.sameValue($262.agent.getReport(), "ok", '$262.agent.getReport() returns "ok"');

### 2018-07-20 seeds/test262/built-ins/Atomics/wake/bad-range.js

@@ -1,0 +1,26 @@
+// Copyright (C) 2017 Mozilla Corporation.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-atomics.wake
+description: >
+  Test range checking of Atomics.wake on arrays that allow atomic operations
+info: |
+  Atomics.wake( typedArray, index, count )
+
+  1. Let buffer be ? ValidateSharedIntegerTypedArray(typedArray, true).
+  ..
+
+includes: [testAtomics.js]
+features: [ArrayBuffer, Atomics, DataView, SharedArrayBuffer, Symbol, TypedArray]
+---*/
+
+const i32a = new Int32Array(
+  new SharedArrayBuffer(Int32Array.BYTES_PER_ELEMENT * 4)
+);
+
+testWithAtomicsOutOfBoundsIndices(function(IdxGen) {
+  assert.throws(RangeError, function() {
+    Atomics.wake(i32a, IdxGen(i32a), 0);
+  }, '`Atomics.wake(i32a, IdxGen(i32a), 0)` throws RangeError');
+});

### 2018-07-20 seeds/test262/built-ins/Atomics/wake/wake-all.js

@@ -1,0 +1,51 @@
+// Copyright (C) 2017 Mozilla Corporation.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-atomics.wake
+description: >
+  Test that Atomics.wake wakes all waiters if that's what the count is.
+includes: [atomicsHelper.js]
+features: [Atomics, SharedArrayBuffer, TypedArray]
+---*/
+
+const WAIT_INDEX = 0;             // Waiters on this will be woken
+const RUNNING = 1;                // Accounting of live agents
+const NUMAGENT = 3;
+const BUFFER_SIZE = 4;
+
+for (var i = 0; i < NUMAGENT; i++) {
+  $262.agent.start(`
+    $262.agent.receiveBroadcast(function(sab) {
+      const i32a = new Int32Array(sab);
+      Atomics.add(i32a, ${RUNNING}, 1);
+
+      $262.agent.report("A " + Atomics.wait(i32a, ${WAIT_INDEX}, 0));
+      $262.agent.leaving();
+    });
+  `);
+}
+
+const i32a = new Int32Array(
+  new SharedArrayBuffer(Int32Array.BYTES_PER_ELEMENT * BUFFER_SIZE)
+);
+
+$262.agent.broadcast(i32a.buffer);
+
+// Wait for agents to be running.
+$262.agent.waitUntil(i32a, RUNNING, NUMAGENT);
+
+// Try to yield control to ensure the agent actually started to wait. If we
+// don't, we risk sending the wakeup before agents are sleeping, and we hang.
+$262.agent.tryYield();
+
+// Wake all waiting on WAIT_INDEX, should be 3 always, they won't time out.
+assert.sameValue(
+  Atomics.wake(i32a, WAIT_INDEX),
+  NUMAGENT,
+  'Atomics.wake(i32a, WAIT_INDEX) returns the value of `NUMAGENT`'
+);
+
+for (var i = 0; i < NUMAGENT; i++) {
+  assert.sameValue($262.agent.getReport(), 'A ok', 'The value of reports[i] is "A ok"');
+}

### 2018-07-20 seeds/test262/built-ins/Atomics/wake/wake-zero.js

@@ -1,0 +1,56 @@
+// Copyright (C) 2017 Mozilla Corporation.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-atomics.wake
+description: >
+  Test that Atomics.wake wakes zero waiters if that's what the count is.
+includes: [atomicsHelper.js]
+features: [Atomics, SharedArrayBuffer, TypedArray]
+---*/
+
+const WAIT_INDEX = 0;             // Agents wait here
+const RUNNING = 1;                // Accounting of live agents here
+const WAKECOUNT = 0;
+const NUMAGENT = 3;
+const BUFFER_SIZE = 4;
+
+const TIMEOUT = $262.agent.timeouts.long;
+
+for (var i = 0; i < NUMAGENT; i++) {
+  $262.agent.start(`
+    $262.agent.receiveBroadcast(function(sab) {
+      const i32a = new Int32Array(sab);
+      Atomics.add(i32a, ${RUNNING}, 1);
+
+      // Waiters that are not woken will time out eventually.
+      $262.agent.report(Atomics.wait(i32a, ${WAIT_INDEX}, 0, ${TIMEOUT}));
+      $262.agent.leaving();
+    });
+  `);
+}
+
+const i32a = new Int32Array(
+  new SharedArrayBuffer(Int32Array.BYTES_PER_ELEMENT * BUFFER_SIZE)
+);
+
+$262.agent.broadcast(i32a.buffer);
+
+// Wait for agents to be running.
+$262.agent.waitUntil(i32a, RUNNING, NUMAGENT);
+
+// Try to yield control to ensure the agent actually started to wait.
+$262.agent.tryYield();
+
+assert.sameValue(
+  Atomics.wake(i32a, WAIT_INDEX, WAKECOUNT),
+  WAKECOUNT,
+  'Atomics.wake(i32a, WAIT_INDEX, WAKECOUNT) returns the value of `WAKECOUNT`'
+);
+
+// Try to sleep past the timeout.
+$262.agent.trySleep(TIMEOUT);
+
+for (var i = 0; i < NUMAGENT; i++) {
+  assert.sameValue($262.agent.getReport(), 'timed-out', '$262.agent.getReport() returns "timed-out"');
+}

### 2018-07-20 seeds/test262/built-ins/RegExp/property-escapes/character-class-range-start.js

@@ -1,0 +1,20 @@
+// Copyright 2018 Mathias Bynens. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Mathias Bynens
+description: >
+  NonemptyClassRanges :: ClassAtom - ClassAtom ClassRanges
+
+  It is a Syntax Error if IsCharacterClass of the first ClassAtom is
+  true or IsCharacterClass of the second ClassAtom is true.
+esid: sec-patterns-static-semantics-early-errors
+negative:
+  phase: parse
+  type: SyntaxError
+features: [regexp-unicode-property-escapes]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+/[\p{Hex}--]/u;

### 2018-07-20 seeds/test262/built-ins/RegExp/property-escapes/loose-matching-05-negated.js

@@ -1,0 +1,18 @@
+// Copyright 2018 Mathias Bynens. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Mathias Bynens
+description: >
+  Loose matching must not be applied when matching properties and values in
+  Unicode property escapes.
+esid: sec-static-semantics-unicodematchproperty-p
+negative:
+  phase: parse
+  type: SyntaxError
+features: [regexp-unicode-property-escapes]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+/\P{Ascii}/u;

### 2018-07-20 seeds/test262/built-ins/RegExp/property-escapes/non-binary-property-without-value-Script_Extensions-equals.js

@@ -1,0 +1,17 @@
+// Copyright 2018 Mathias Bynens. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Mathias Bynens
+description: >
+  Non-binary properties without a value must throw in Unicode property escapes.
+esid: sec-static-semantics-unicodematchproperty-p
+negative:
+  phase: parse
+  type: SyntaxError
+features: [regexp-unicode-property-escapes]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+/\p{Script_Extensions=}/u;

### 2018-07-20 seeds/test262/built-ins/RegExp/property-escapes/non-existent-binary-property-negated.js

@@ -1,0 +1,17 @@
+// Copyright 2018 Mathias Bynens. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Mathias Bynens
+description: >
+  Non-existent properties must not be supported in Unicode property escapes.
+esid: sec-static-semantics-unicodematchproperty-p
+negative:
+  phase: parse
+  type: SyntaxError
+features: [regexp-unicode-property-escapes]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+/\P{UnknownBinaryProperty}/u;

### 2018-07-20 seeds/test262/language/block-scope/syntax/redeclaration/function-declaration-attempt-to-redeclare-with-var-declaration.js

@@ -1,0 +1,22 @@
+// This file was procedurally generated from the following sources:
+// - src/declarations/redeclare-with-var-declaration.case
+// - src/declarations/redeclare-allow-var/block-attempt-to-redeclare-function-declaration.template
+/*---
+description: redeclaration with VariableDeclaration (FunctionDeclaration in BlockStatement)
+esid: sec-block-static-semantics-early-errors
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    Block : { StatementList }
+
+    It is a Syntax Error if any element of the LexicallyDeclaredNames of
+    StatementList also occurs in the VarDeclaredNames of StatementList.
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+{ function f() {} var f; }

### 2018-07-20 seeds/test262/language/expressions/arrow-function/syntax/early-errors/arrowparameters-bindingidentifier-identifier-strict-futurereservedword.js

@@ -1,0 +1,27 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+es6id: 14.2
+description: >
+    ArrowParameters[Yield] :
+      BindingIdentifier[?Yield]
+
+    (12.1)
+    BindingIdentifier[Yield] :
+      Identifier[~Yield] yield
+
+    Identifier :
+      IdentifierName but not ReservedWord
+
+    ReservedWord : FutureReservedWord
+
+    Strict Mode
+
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [onlyStrict]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+var af = package => 1;

### 2018-07-20 seeds/test262/language/expressions/async-arrow-function/early-errors-arrow-formals-contains-super-call.js

@@ -1,0 +1,15 @@
+// Copyright 2016 Microsoft, Inc. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Brian Terlson <brian.terlson@microsoft.com>
+esid: pending
+description: It is a syntax error if FormalParameters contains SuperCall is true
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+async(foo = super()) => {}

### 2018-07-20 seeds/test262/language/expressions/async-function/early-errors-expression-body-contains-super-call.js

@@ -1,0 +1,15 @@
+// Copyright 2016 Microsoft, Inc. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Brian Terlson <brian.terlson@microsoft.com>
+esid: pending
+description: It is a syntax error if AsyncFunctionBody contains SuperCall is true
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+(async function foo (foo) { super() })

### 2018-07-20 seeds/test262/language/expressions/async-function/named-rest-params-trailing-comma-early-error.js

@@ -1,0 +1,34 @@
+// This file was procedurally generated from the following sources:
+// - src/function-forms/rest-params-trailing-comma-early-error.case
+// - src/function-forms/syntax/async-func-expr-named.template
+/*---
+description: It's a syntax error if a FunctionRestParameter is followed by a trailing comma (async function named expression)
+esid: sec-async-function-definitions
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    14.6 Async Function Definitions
+
+    AsyncFunctionExpression :
+      async function BindingIdentifier ( FormalParameters ) { AsyncFunctionBody }
+
+
+    Trailing comma in the parameters list
+
+    14.1 Function Definitions
+
+    FormalParameters[Yield, Await] :
+        [empty]
+        FunctionRestParameter[?Yield, ?Await]
+        FormalParameterList[?Yield, ?Await]
+        FormalParameterList[?Yield, ?Await] ,
+        FormalParameterList[?Yield, ?Await] , FunctionRestParameter[?Yield, ?Await]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+(async function f(...a,) {
+  
+});

### 2018-07-20 seeds/test262/language/expressions/async-function/nameless-dflt-params-rest.js

@@ -1,0 +1,41 @@
+// This file was procedurally generated from the following sources:
+// - src/function-forms/dflt-params-rest.case
+// - src/function-forms/syntax/async-func-expr-nameless.template
+/*---
+description: RestParameter does not support an initializer (async function nameless expression)
+esid: sec-async-function-definitions
+features: [default-parameters]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    14.6 Async Function Definitions
+
+    AsyncFunctionExpression :
+      async function ( FormalParameters ) { AsyncFunctionBody }
+
+    14.1 Function Definitions
+
+    Syntax
+
+    FunctionRestParameter[Yield] :
+
+      BindingRestElement[?Yield]
+
+    13.3.3 Destructuring Binding Patterns
+
+    Syntax
+
+    BindingRestElement[Yield] :
+
+      ...BindingIdentifier[?Yield]
+      ...BindingPattern[?Yield]
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+(async function(...x = []) {
+  
+});

### 2018-07-20 seeds/test262/language/expressions/async-generator/dstr-dflt-ary-ptrn-rest-not-final-id.js

@@ -1,0 +1,40 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-not-final-id.case
+// - src/dstr-binding/default/async-gen-func-expr-dflt.template
+/*---
+description: Rest element (identifier) may not be followed by any element (async generator function expression (default parameter))
+esid: sec-asyncgenerator-definitions-evaluation
+features: [async-iteration]
+flags: [generated, async]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    AsyncGeneratorExpression : async [no LineTerminator here] function * ( FormalParameters ) {
+        AsyncGeneratorBody }
+
+        [...]
+        3. Let closure be ! AsyncGeneratorFunctionCreate(Normal, FormalParameters,
+           AsyncGeneratorBody, scope, strict).
+        [...]
+
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var callCount = 0;
+var f;
+f = async function*([...x, y] = [1, 2, 3]) {
+  
+  callCount = callCount + 1;
+};
+
+f().next().then(() => {
+    assert.sameValue(callCount, 1, 'invoked exactly once');
+}).then($DONE, $DONE);

### 2018-07-20 seeds/test262/language/expressions/async-generator/dstr-named-ary-ptrn-rest-not-final-id.js

@@ -1,0 +1,40 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-not-final-id.case
+// - src/dstr-binding/default/async-gen-func-named-expr.template
+/*---
+description: Rest element (identifier) may not be followed by any element (async generator named function expression)
+esid: sec-asyncgenerator-definitions-evaluation
+features: [async-iteration]
+flags: [generated, async]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    AsyncGeneratorExpression : async [no LineTerminator here] function * BindingIdentifier
+        ( FormalParameters ) { AsyncGeneratorBody }
+
+        [...]
+        7. Let closure be ! AsyncGeneratorFunctionCreate(Normal, FormalParameters,
+           AsyncGeneratorBody, funcEnv, strict).
+        [...]
+
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var callCount = 0;
+var f;
+f = async function* h([...x, y]) {
+  
+  callCount = callCount + 1;
+};
+
+f([1, 2, 3]).next().then(() => {
+    assert.sameValue(callCount, 1, 'invoked exactly once');
+}).then($DONE, $DONE);

### 2018-07-20 seeds/test262/language/expressions/async-generator/named-yield-as-identifier-reference-escaped.js

@@ -1,0 +1,31 @@
+// This file was procedurally generated from the following sources:
+// - src/async-generators/yield-as-identifier-reference-escaped.case
+// - src/async-generators/syntax/async-expression-named.template
+/*---
+description: yield is a reserved keyword within generator function bodies and may not be used as an identifier reference. (Named async generator expression)
+esid: prod-AsyncGeneratorExpression
+features: [async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    Async Generator Function Definitions
+
+    AsyncGeneratorExpression :
+      async [no LineTerminator here] function * BindingIdentifier ( FormalParameters ) {
+        AsyncGeneratorBody }
+
+
+    IdentifierReference : Identifier
+
+    It is a Syntax Error if this production has a [Yield] parameter and
+    StringValue of Identifier is "yield".
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var gen = async function *g() {
+  void yi\u0065ld;
+};

### 2018-07-20 seeds/test262/language/expressions/class/async-gen-meth-dflt-params-duplicates.js

@@ -1,0 +1,66 @@
+// This file was procedurally generated from the following sources:
+// - src/function-forms/dflt-params-duplicates.case
+// - src/function-forms/syntax/cls-expr-async-gen-meth.template
+/*---
+description: It is a Syntax Error if BoundNames of FormalParameters contains any duplicate elements. (class expression async generator method)
+esid: sec-class-definitions-runtime-semantics-evaluation
+features: [default-parameters, async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassExpression : class BindingIdentifieropt ClassTail
+
+    1. If BindingIdentifieropt is not present, let className be undefined.
+    2. Else, let className be StringValue of BindingIdentifier.
+    3. Let value be the result of ClassDefinitionEvaluation of ClassTail
+       with argument className.
+    [...]
+
+    14.5.14 Runtime Semantics: ClassDefinitionEvaluation
+
+    21. For each ClassElement m in order from methods
+        a. If IsStatic of m is false, then
+           i. Let status be the result of performing
+              PropertyDefinitionEvaluation for m with arguments proto and
+              false.
+        [...]
+
+    Runtime Semantics: PropertyDefinitionEvaluation
+
+    AsyncGeneratorMethod :
+        async [no LineTerminator here] * PropertyName ( UniqueFormalParameters )
+            { AsyncGeneratorBody }
+
+    1. Let propKey be the result of evaluating PropertyName.
+    2. ReturnIfAbrupt(propKey).
+    3. If the function code for this AsyncGeneratorMethod is strict mode code, let strict be true.
+       Otherwise let strict be false.
+    4. Let scope be the running execution context's LexicalEnvironment.
+    5. Let closure be ! AsyncGeneratorFunctionCreate(Method, UniqueFormalParameters,
+       AsyncGeneratorBody, scope, strict).
+    [...]
+
+
+    14.1.2 Static Semantics: Early Errors
+
+    StrictFormalParameters : FormalParameters
+
+    - It is a Syntax Error if BoundNames of FormalParameters contains any
+      duplicate elements.
+
+    FormalParameters : FormalParameterList
+
+    - It is a Syntax Error if IsSimpleParameterList of FormalParameterList is
+      false and BoundNames of FormalParameterList contains any duplicate
+      elements.
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+0, class {
+  async *method(x = 0, x) {
+    
+  }
+};

### 2018-07-20 seeds/test262/language/expressions/class/async-gen-method-static-yield-as-label-identifier-escaped.js

@@ -1,0 +1,36 @@
+// This file was procedurally generated from the following sources:
+// - src/async-generators/yield-as-label-identifier-escaped.case
+// - src/async-generators/syntax/async-class-expr-static-method.template
+/*---
+description: yield is a reserved keyword within generator function bodies and may not be used as a label identifier. (Static async generator method as a ClassExpression element)
+esid: prod-AsyncGeneratorMethod
+features: [async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassElement :
+      static MethodDefinition
+
+    MethodDefinition :
+      AsyncGeneratorMethod
+
+    Async Generator Function Definitions
+
+    AsyncGeneratorMethod :
+      async [no LineTerminator here] * PropertyName ( UniqueFormalParameters ) { AsyncGeneratorBody }
+
+
+    LabelIdentifier : Identifier
+
+    It is a Syntax Error if this production has a [Yield] parameter and
+    StringValue of Identifier is "yield".
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var C = class { static async *gen() {
+    yi\u0065ld: ;
+}};

### 2018-07-20 seeds/test262/language/expressions/class/dstr-meth-static-dflt-ary-ptrn-rest-init-ary.js

@@ -1,0 +1,81 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-ary.case
+// - src/dstr-binding/default/cls-expr-meth-static-dflt.template
+/*---
+description: Reset element (nested array pattern) does not support initializer (static class expression method (default parameter))
+esid: sec-class-definitions-runtime-semantics-evaluation
+es6id: 14.5.16
+features: [destructuring-binding, default-parameters]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassExpression : class BindingIdentifieropt ClassTail
+
+    1. If BindingIdentifieropt is not present, let className be undefined.
+    2. Else, let className be StringValue of BindingIdentifier.
+    3. Let value be the result of ClassDefinitionEvaluation of ClassTail
+       with argument className.
+    [...]
+
+    14.5.14 Runtime Semantics: ClassDefinitionEvaluation
+
+    21. For each ClassElement m in order from methods
+        a. If IsStatic of m is false, then
+        b. Else,
+           Let status be the result of performing PropertyDefinitionEvaluation for
+           m with arguments F and false.
+    [...]
+
+    14.3.8 Runtime Semantics: DefineMethod
+
+    MethodDefinition : PropertyName ( StrictFormalParameters ) { FunctionBody }
+
+    [...]
+    6. Let closure be FunctionCreate(kind, StrictFormalParameters, FunctionBody,
+       scope, strict). If functionPrototype was passed as a parameter then pass its
+       value as the functionPrototype optional argument of FunctionCreate.
+    [...]
+
+    9.2.1 [[Call]] ( thisArgument, argumentsList)
+
+    [...]
+    7. Let result be OrdinaryCallEvaluateBody(F, argumentsList).
+    [...]
+
+    9.2.1.3 OrdinaryCallEvaluateBody ( F, argumentsList )
+
+    1. Let status be FunctionDeclarationInstantiation(F, argumentsList).
+    [...]
+
+    9.2.12 FunctionDeclarationInstantiation(func, argumentsList)
+
+    [...]
+    23. Let iteratorRecord be Record {[[iterator]]:
+        CreateListIterator(argumentsList), [[done]]: false}.
+    24. If hasDuplicates is true, then
+        [...]
+    25. Else,
[…]

### 2018-07-20 seeds/test262/language/expressions/class/err-field-delete-call-expression-privatename.js

@@ -1,0 +1,32 @@
+// This file was procedurally generated from the following sources:
+// - src/class-fields/call-expression-privatename.case
+// - src/class-fields/delete-error/cls-expr-field-delete.template
+/*---
+description: Syntax error if you call delete on call expressions . privatename (in field)
+esid: sec-class-definitions-static-semantics-early-errors
+features: [class, class-fields-private, class-fields-public]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    Static Semantics: Early Errors
+
+      UnaryExpression : delete UnaryExpression
+
+      It is a Syntax Error if the UnaryExpression is contained in strict mode code and the derived UnaryExpression is PrimaryExpression : IdentifierReference , MemberExpression : MemberExpression.PrivateName , or CallExpression : CallExpression.PrivateName .
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+var C = class {
+  #x;
+  g = this.f;
+  x = delete g().#x;
+
+  f() {
+    return this;
+  }
+}

### 2018-07-20 seeds/test262/language/expressions/class/err-method-delete-member-expression-privatename.js

@@ -1,0 +1,33 @@
+// This file was procedurally generated from the following sources:
+// - src/class-fields/member-expression-privatename.case
+// - src/class-fields/delete-error/cls-expr-method-delete.template
+/*---
+description: Syntax error if you call delete on member expressions . privatename (in method)
+esid: sec-class-definitions-static-semantics-early-errors
+features: [class-fields-private, class]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    Static Semantics: Early Errors
+
+      UnaryExpression : delete UnaryExpression
+
+      It is a Syntax Error if the UnaryExpression is contained in strict mode code and the derived UnaryExpression is PrimaryExpression : IdentifierReference , MemberExpression : MemberExpression.PrivateName , or CallExpression : CallExpression.PrivateName .
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+var C = class {
+  #x;
+
+  x() {
+    
+    delete this.#x;
+  }
+
+  
+}

### 2018-07-20 seeds/test262/language/expressions/class/fields-string-name-propname-constructor.js

@@ -1,0 +1,32 @@
+// This file was procedurally generated from the following sources:
+// - src/class-fields/propname-constructor.case
+// - src/class-fields/propname-error/cls-expr-string-name.template
+/*---
+description: class fields forbid PropName 'constructor' (early error -- PropName of StringLiteral is forbidden)
+esid: sec-class-definitions-static-semantics-early-errors
+features: [class, class-fields-public]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    Static Semantics: PropName
+    ...
+    LiteralPropertyName : StringLiteral
+      Return the String value whose code units are the SV of the StringLiteral.
+
+    
+    // This test file tests the following early error:
+    Static Semantics: Early Errors
+
+      ClassElement : FieldDefinition;
+        It is a Syntax Error if PropName of FieldDefinition is "constructor".
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+var C = class {
+  'constructor';
+};

### 2018-07-20 seeds/test262/language/expressions/class/gen-meth-static-dflt-params-duplicates.js

@@ -1,0 +1,87 @@
+// This file was procedurally generated from the following sources:
+// - src/function-forms/dflt-params-duplicates.case
+// - src/function-forms/syntax/cls-expr-gen-meth-static.template
+/*---
+description: It is a Syntax Error if BoundNames of FormalParameters contains any duplicate elements. (static class expression generator method)
+esid: sec-class-definitions-runtime-semantics-evaluation
+features: [default-parameters, generators]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassExpression : class BindingIdentifieropt ClassTail
+
+    1. If BindingIdentifieropt is not present, let className be undefined.
+    2. Else, let className be StringValue of BindingIdentifier.
+    3. Let value be the result of ClassDefinitionEvaluation of ClassTail
+       with argument className.
+    [...]
+
+    14.5.14 Runtime Semantics: ClassDefinitionEvaluation
+
+    21. For each ClassElement m in order from methods
+        a. If IsStatic of m is false, then
+        b. Else,
+           Let status be the result of performing PropertyDefinitionEvaluation
+           for m with arguments F and false.
+    [...]
+
+    14.4.13 Runtime Semantics: PropertyDefinitionEvaluation
+
+    GeneratorMethod :
+        * PropertyName ( StrictFormalParameters ) { GeneratorBody }
+
+    1. Let propKey be the result of evaluating PropertyName.
+    2. ReturnIfAbrupt(propKey).
+    3. If the function code for this GeneratorMethod is strict mode code,
+       let strict be true. Otherwise let strict be false.
+    4. Let scope be the running execution context's LexicalEnvironment.
+    5. Let closure be GeneratorFunctionCreate(Method,
+       StrictFormalParameters, GeneratorBody, scope, strict).
+
+    9.2.1 [[Call]] ( thisArgument, argumentsList)
+
+    [...]
+    7. Let result be OrdinaryCallEvaluateBody(F, argumentsList).
+    [...]
+
+    9.2.1.3 OrdinaryCallEvaluateBody ( F, argumentsList )
+
+    1. Let status be FunctionDeclarationInstantiation(F, argumentsList).
+    [...]
+
+    9.2.12 FunctionDeclarationInstantiation(func, argumentsList)
+
+    [...]
+    23. Let iteratorRecord be Record {[[iterator]]:
+        CreateListIterator(argumentsList), [[done]]: false}.
[…]

### 2018-07-20 seeds/test262/language/expressions/conditional/in-condition.js

@@ -1,0 +1,22 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+esid: sec-conditional-operator
+es6id: 12.13
+description: >
+  The expression's LogicalORExpression sub-expression cannot include the `in`
+  keyword in contexts where it is disallowed.
+info: |
+  Syntax
+
+  ConditionalExpression[In, Yield] :
+    LogicalORExpression[?In, ?Yield]
+    LogicalORExpression[?In, ?Yield] ? AssignmentExpression[+In, ?Yield] : AssignmentExpression[?In, ?Yield]
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+for ('' in {} ? 0 : 0; false; ) ;

### 2018-07-20 seeds/test262/language/expressions/generators/dstr-ary-ptrn-rest-init-obj.js

@@ -1,0 +1,60 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-obj.case
+// - src/dstr-binding/default/gen-func-expr.template
+/*---
+description: Reset element (nested object pattern) does not support initializer (generator function expression)
+esid: sec-generator-function-definitions-runtime-semantics-evaluation
+es6id: 14.4.14
+features: [generators, destructuring-binding]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    GeneratorExpression : function * ( FormalParameters ) { GeneratorBody }
+
+        [...]
+        3. Let closure be GeneratorFunctionCreate(Normal, FormalParameters,
+           GeneratorBody, scope, strict).
+        [...]
+
+    9.2.1 [[Call]] ( thisArgument, argumentsList)
+
+    [...]
+    7. Let result be OrdinaryCallEvaluateBody(F, argumentsList).
+    [...]
+
+    9.2.1.3 OrdinaryCallEvaluateBody ( F, argumentsList )
+
+    1. Let status be FunctionDeclarationInstantiation(F, argumentsList).
+    [...]
+
+    9.2.12 FunctionDeclarationInstantiation(func, argumentsList)
+
+    [...]
+    23. Let iteratorRecord be Record {[[iterator]]:
+        CreateListIterator(argumentsList), [[done]]: false}.
+    24. If hasDuplicates is true, then
+        [...]
+    25. Else,
+        b. Let formalStatus be IteratorBindingInitialization for formals with
+           iteratorRecord and env as arguments.
+    [...]
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var callCount = 0;
+var f;
+f = function*([...{ x } = []]) {
+  
+  callCount = callCount + 1;
+};
+
+f([]).next();
+assert.sameValue(callCount, 1, 'generator function invoked exactly once');

### 2018-07-20 seeds/test262/language/expressions/generators/named-yield-identifier-spread-strict.js

@@ -1,0 +1,44 @@
+// This file was procedurally generated from the following sources:
+// - src/generators/yield-identifier-spread-strict.case
+// - src/generators/default/expression-named.template
+/*---
+description: It's an early error if the AssignmentExpression is a function body with yield as an identifier in strict mode. (Named generator expression)
+esid: prod-GeneratorExpression
+features: [object-spread, generators]
+flags: [generated, onlyStrict]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    14.4 Generator Function Definitions
+
+    GeneratorExpression:
+      function * BindingIdentifier opt ( FormalParameters ) { GeneratorBody }
+
+
+    Spread Properties
+
+    PropertyDefinition[Yield]:
+      (...)
+      ...AssignmentExpression[In, ?Yield]
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var callCount = 0;
+
+var gen = function *g() {
+  callCount += 1;
+  return {
+       ...(function() {
+          var yield;
+          throw new Test262Error();
+       }()),
+    }
+};
+
+var iter = gen();
+
+
+
+assert.sameValue(callCount, 1);

### 2018-07-20 seeds/test262/language/expressions/object/dstr-meth-dflt-ary-ptrn-rest-init-id.js

@@ -1,0 +1,63 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-id.case
+// - src/dstr-binding/default/meth-dflt.template
+/*---
+description: Reset element (identifier) does not support initializer (method (default parameter))
+esid: sec-runtime-semantics-definemethod
+es6id: 14.3.8
+features: [destructuring-binding, default-parameters]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    MethodDefinition : PropertyName ( StrictFormalParameters ) { FunctionBody }
+
+    [...]
+    6. Let closure be FunctionCreate(kind, StrictFormalParameters,
+       FunctionBody, scope, strict). If functionPrototype was passed as a
+       parameter then pass its value as the functionPrototype optional argument
+       of FunctionCreate.
+    [...]
+
+    9.2.1 [[Call]] ( thisArgument, argumentsList)
+
+    [...]
+    7. Let result be OrdinaryCallEvaluateBody(F, argumentsList).
+    [...]
+
+    9.2.1.3 OrdinaryCallEvaluateBody ( F, argumentsList )
+
+    1. Let status be FunctionDeclarationInstantiation(F, argumentsList).
+    [...]
+
+    9.2.12 FunctionDeclarationInstantiation(func, argumentsList)
+
+    [...]
+    23. Let iteratorRecord be Record {[[iterator]]:
+        CreateListIterator(argumentsList), [[done]]: false}.
+    24. If hasDuplicates is true, then
+        [...]
+    25. Else,
+        b. Let formalStatus be IteratorBindingInitialization for formals with
+           iteratorRecord and env as arguments.
+    [...]
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var callCount = 0;
+var obj = {
+  method([...x = []] = []) {
+    
+    callCount = callCount + 1;
+  }
+};
+
+obj.method();
+assert.sameValue(callCount, 1, 'method invoked exactly once');

### 2018-07-20 seeds/test262/language/identifiers/val-const-via-escape-hex4.js

@@ -1,0 +1,16 @@
+// Copyright (c) 2012 Ecma International.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es5id: 7.6-34
+description: >
+    7.6 - SyntaxError expected: reserved words used as Identifier
+    Names in UTF8: const (const)
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+var co\u006est = 123;

### 2018-07-20 seeds/test262/language/identifiers/val-else-via-escape-hex.js

@@ -1,0 +1,16 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es6id: 11.6
+description: >
+    SyntaxError expected: reserved words used as Identifier
+    Names in UTF8: else (else)
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+var \u{65}lse = 123;

### 2018-07-20 seeds/test262/language/identifiers/val-else.js

@@ -1,0 +1,15 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es6id: 11.6
+description: >
+    SyntaxError expected: reserved words used as Identifier
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+var else = 123;

### 2018-07-20 seeds/test262/language/identifiers/val-void-via-escape-hex4.js

@@ -1,0 +1,16 @@
+// Copyright (c) 2012 Ecma International.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es5id: 7.6-16
+description: >
+    7.6 - SyntaxError expected: reserved words used as Identifier
+    Names in UTF8: void (void)
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+var \u0076\u006f\u0069\u0064 = 123;

### 2018-07-20 seeds/test262/language/identifiers/val-while-via-escape-hex.js

@@ -1,0 +1,16 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es6id: 11.6
+description: >
+    SyntaxError expected: reserved words used as Identifier
+    Names in UTF8: while
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+var \u{77}\u{68}\u{69}\u{6c}\u{65} = 123;

### 2018-07-20 seeds/test262/language/import/escaped-as-import-specifier.js

@@ -1,0 +1,26 @@
+// Copyright (C) 2017 André Bargull. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-grammar-notation
+description: >
+  The `as` contextual keyword must not contain Unicode escape sequences.
+info: |
+  Terminal symbols of the lexical, RegExp, and numeric string grammars are shown
+  in fixed width font, both in the productions of the grammars and throughout this
+  specification whenever the text directly refers to such a terminal symbol. These
+  are to appear in a script exactly as written. All terminal symbol code points
+  specified in this way are to be understood as the appropriate Unicode code points
+  from the Basic Latin range, as opposed to any similar-looking code points from
+  other Unicode ranges.
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [module]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+export var a = 0;
+
+import {a \u0061s b} from "./escaped-as-import-specifier.js";

### 2018-07-20 seeds/test262/language/line-terminators/S7.3_A2.2_T2.js

@@ -1,0 +1,19 @@
+// Copyright 2009 the Sputnik authors.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+info: CARRIAGE RETURN (U+000D) within strings is not allowed
+es5id: 7.3_A2.2_T2
+description: Insert real CARRIAGE RETURN into string
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+//CHECK#1
+"
+str
+ing
+";

### 2018-07-20 seeds/test262/language/literals/numeric/octal-invalid-leading.js

@@ -1,0 +1,23 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+es6id: 11.8.3
+description: Octal-integer-literal-like sequence with a leading 0
+info: |
+    OctalIntegerLiteral ::
+      0o OctalDigits
+      0O OctalDigits
+    OctalDigits ::
+      OctalDigit
+      OctalDigits OctalDigit
+    OctalDigit :: one of
+      0 1 2 3 4 5 6 7
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+00o0;

### 2018-07-20 seeds/test262/language/literals/regexp/u-invalid-non-empty-class-ranges.js

@@ -1,0 +1,31 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+esid: sec-pattern-semantics
+es6id: 21.2.2
+description: >
+    NonEmptyClassRangesNoDash production cannot specify a multi-character set
+info: |
+    The production
+    NonemptyClassRangesNoDash::ClassAtomNoDash-ClassAtomClassRanges evaluates
+    as follows:
+
+    1. Evaluate ClassAtomNoDash to obtain a CharSet A.
+    2. Evaluate ClassAtom to obtain a CharSet B.
+    3. Evaluate ClassRanges to obtain a CharSet C.
+    4. Call CharacterRange(A, B) and let D be the resulting CharSet.
+
+    21.2.2.15.1 Runtime Semantics: CharacterRange Abstract Operation
+
+    1. If A does not contain exactly one character or B does not contain
+       exactly one character, throw a SyntaxError exception.
+
+    The `u` flag precludes the Annex B extension that enables this pattern.
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+/[--\d]/u;

### 2018-07-20 seeds/test262/language/literals/string/S7.8.4_A7.2_T4.js

@@ -1,0 +1,16 @@
+// Copyright 2009 the Sputnik authors.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+info: "UnicodeEscapeSequence :: u HexDigit (one, two or three time) is incorrect"
+es5id: 7.8.4_A7.2_T4
+description: ":: HexDigit :: A"
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+//CHECK#1
+"\uAA"

### 2018-07-20 seeds/test262/language/module-code/early-export-unresolvable.js

@@ -1,0 +1,17 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+es6id: 15.2.1.1
+description: >
+    It is a Syntax Error if any element of the ExportedBindings of
+    ModuleItemList does not also occur in either the VarDeclaredNames of
+    ModuleItemList, or the LexicallyDeclaredNames of ModuleItemList.
+flags: [module]
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+export { unresolvable };

### 2018-07-20 seeds/test262/language/module-code/early-import-as-arguments.js

@@ -1,0 +1,35 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: ImportedBinding is a BindingIdentifier and cannot be "arguments"
+esid: sec-imports
+info: |
+    ImportSpecifier :
+      ImportedBinding
+      IdentifierName as ImportedBinding
+
+    ImportedBinding :
+      BindingIdentifier
+
+    12.1.1 Static Semantics : Early Errors
+
+    BindingIdentifier : Identifier
+
+    - It is a Syntax Error if the code matched by this production is contained
+      in strict mode code and the StringValue of Identifier is "arguments" or
+      "eval".
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [module]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+// Create an appropriately-named ExportEntry in order to avoid false positives
+// (e.g. cases where the implementation does not generate the expected early
+// error but does produce a SyntaxError for unresolvable bindings).
+var x;
+export { x };
+
+import { x as arguments } from './early-import-as-arguments.js';

### 2018-07-20 seeds/test262/language/module-code/parse-err-decl-pos-export-class-expr-meth-gen-static.js

@@ -1,0 +1,15 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: Expression cannot contain an `export` declaration
+esid: sec-modules
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [module]
+features: [generators]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+(class { static *method() { export default null; } });

### 2018-07-20 seeds/test262/language/module-code/parse-err-decl-pos-import-class-expr-meth-gen-static.js

@@ -1,0 +1,15 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: Expression cannot contain an `import` declaration
+esid: sec-modules
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [module]
+features: [generators]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+(class { static *method() { import v from './decl-pos-import-class-expr-meth-gen-static.js'; } });

### 2018-07-20 seeds/test262/language/module-code/parse-err-decl-pos-import-try-catch.js

@@ -1,0 +1,16 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: Statement cannot contain an `import` declaration
+esid: sec-modules
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [module]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+try { } catch (err) {
+  import v from './decl-pos-import-try-catch.js';
+}

### 2018-07-20 seeds/test262/language/module-code/privatename-not-valid-earlyerr-module-1.js

@@ -1,0 +1,23 @@
+// Copyright (C) 2017 Valerie Young. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+esid: sec-module-semantics-static-semantics-early-errors
+description: Early error when referencing privatename in constructor without being declared in class fields
+info: |
+  Static Semantics: Early Errors
+  Module : ModuleBody
+    It is a Syntax Error if AllPrivateNamesValid of ModuleBody with an empty List as an argument is false.
+features: [class, class-fields-private]
+flags: [module]
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+class C {
+  constructor() {
+    this.#x;
+  }
+}

### 2018-07-20 seeds/test262/language/punctuators/S7.7_A2_T1.js

@@ -1,0 +1,17 @@
+// Copyright 2009 the Sputnik authors.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+info: |
+    Punctuator cannot be expressed as a Unicode escape sequence consisting of
+    six characters, namely \u plus four hexadecimal digits
+es5id: 7.7_A2_T1
+description: Try to use {} as a Unicode \u007B\u007D
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+\u007B\u007D;

### 2018-07-20 seeds/test262/language/statements/async-function/early-errors-declaration-eval-in-formal-parameters.js

@@ -1,0 +1,16 @@
+// Copyright 2016 Microsoft, Inc. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+author: Brian Terlson <brian.terlson@microsoft.com>
+esid: pending
+description: It is a SyntaxError if FormalParameters contains eval in strict mode
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [onlyStrict]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+async function foo (eval) {  }

### 2018-07-20 seeds/test262/language/statements/async-generator/dflt-params-rest.js

@@ -1,0 +1,45 @@
+// This file was procedurally generated from the following sources:
+// - src/function-forms/dflt-params-rest.case
+// - src/function-forms/syntax/async-gen-func-decl.template
+/*---
+description: RestParameter does not support an initializer (async generator function declaration)
+esid: sec-asyncgenerator-definitions-instantiatefunctionobject
+features: [default-parameters, async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    AsyncGeneratorDeclaration : async [no LineTerminator here] function * BindingIdentifier
+        ( FormalParameters ) { AsyncGeneratorBody }
+
+        [...]
+        3. Let F be ! AsyncGeneratorFunctionCreate(Normal, FormalParameters, AsyncGeneratorBody,
+            scope, strict).
+        [...]
+
+
+    14.1 Function Definitions
+
+    Syntax
+
+    FunctionRestParameter[Yield] :
+
+      BindingRestElement[?Yield]
+
+    13.3.3 Destructuring Binding Patterns
+
+    Syntax
+
+    BindingRestElement[Yield] :
+
+      ...BindingIdentifier[?Yield]
+      ...BindingPattern[?Yield]
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+async function* f(...x = []) {
+  
+}

### 2018-07-20 seeds/test262/language/statements/async-generator/dstr-dflt-ary-ptrn-rest-not-final-obj.js

@@ -1,0 +1,38 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-not-final-obj.case
+// - src/dstr-binding/default/async-gen-func-decl-dflt.template
+/*---
+description: Rest element (object binding pattern) may not be followed by any element (async generator function declaration (default parameter))
+esid: sec-asyncgenerator-definitions-instantiatefunctionobject
+features: [async-iteration]
+flags: [generated, async]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    AsyncGeneratorDeclaration : async [no LineTerminator here] function * BindingIdentifier
+        ( FormalParameters ) { AsyncGeneratorBody }
+
+        [...]
+        3. Let F be ! AsyncGeneratorFunctionCreate(Normal, FormalParameters, AsyncGeneratorBody,
+            scope, strict).
+        [...]
+
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var callCount = 0;
+async function* f([...{ x }, y] = [1, 2, 3]) {
+  
+  callCount = callCount + 1;
+};
+f().next().then(() => {
+    assert.sameValue(callCount, 1, 'invoked exactly once');
+}).then($DONE, $DONE);

### 2018-07-20 seeds/test262/language/statements/class/async-method-await-as-binding-identifier.js

@@ -1,0 +1,36 @@
+// This file was procedurally generated from the following sources:
+// - src/async-functions/await-as-binding-identifier.case
+// - src/async-functions/syntax/async-class-decl-method.template
+/*---
+description: await is a reserved keyword within generator function bodies and may not be used as a binding identifier. (Async method as a ClassDeclaration element)
+esid: prod-AsyncMethod
+features: [async-functions]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassElement :
+      MethodDefinition
+
+    MethodDefinition :
+      AsyncMethod
+
+    Async Function Definitions
+
+    AsyncMethod :
+      async [no LineTerminator here] PropertyName ( UniqueFormalParameters ) { AsyncFunctionBody }
+
+
+    BindingIdentifier : Identifier
+
+    It is a Syntax Error if this production has a [Await] parameter and
+    StringValue of Identifier is "await".
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+class C { async method() {
+    var await;
+}}

### 2018-07-20 seeds/test262/language/statements/class/class-name-ident-static.js

@@ -1,0 +1,27 @@
+// Copyright (C) 2018 André Bargull. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-class-definitions
+description: >
+  `static` is not a valid class-name identifier.
+info: |
+  12.1.1 Static Semantics: Early Errors
+
+  Identifier : IdentifierName but not ReservedWord
+
+  It is a Syntax Error if this phrase is contained in strict mode code and the
+  StringValue of IdentifierName is: "implements", "interface", "let", "package",
+  "private", "protected", "public", "static", or "yield".
+
+  10.2.1 Strict Mode Code
+
+  All parts of a ClassDeclaration or a ClassExpression are strict mode code.
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+class static {}

### 2018-07-20 seeds/test262/language/statements/class/dstr-async-gen-meth-static-dflt-ary-ptrn-rest-init-id.js

@@ -1,0 +1,64 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-id.case
+// - src/dstr-binding/default/cls-decl-async-gen-meth-static-dflt.template
+/*---
+description: Reset element (identifier) does not support initializer (static class expression async generator method (default parameter))
+esid: sec-runtime-semantics-bindingclassdeclarationevaluation
+features: [async-iteration]
+flags: [generated, async]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassDeclaration : class BindingIdentifier ClassTail
+
+    1. Let className be StringValue of BindingIdentifier.
+    2. Let value be the result of ClassDefinitionEvaluation of ClassTail with
+       argument className.
+    [...]
+
+    14.5.14 Runtime Semantics: ClassDefinitionEvaluation
+
+    21. For each ClassElement m in order from methods
+        a. If IsStatic of m is false, then
+        b. Else,
+           Let status be the result of performing PropertyDefinitionEvaluation for
+           m with arguments F and false.
+    [...]
+
+    Runtime Semantics: PropertyDefinitionEvaluation
+
+    AsyncGeneratorMethod :
+        async [no LineTerminator here] * PropertyName ( UniqueFormalParameters )
+            { AsyncGeneratorBody }
+
+    1. Let propKey be the result of evaluating PropertyName.
+    2. ReturnIfAbrupt(propKey).
+    3. If the function code for this AsyncGeneratorMethod is strict mode code, let strict be true.
+       Otherwise let strict be false.
+    4. Let scope be the running execution context's LexicalEnvironment.
+    5. Let closure be ! AsyncGeneratorFunctionCreate(Method, UniqueFormalParameters,
+       AsyncGeneratorBody, scope, strict).
+    [...]
+
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+
+var callCount = 0;
+class C {
+  static async *method([...x = []] = []) {
+    
+    callCount = callCount + 1;
+  }
+};
+
+C.method().next().then(() => {
[…]

### 2018-07-20 seeds/test262/language/statements/class/gen-method-yield-identifier-spread-strict.js

@@ -1,0 +1,52 @@
+// This file was procedurally generated from the following sources:
+// - src/generators/yield-identifier-spread-strict.case
+// - src/generators/default/class-decl-method.template
+/*---
+description: It's an early error if the AssignmentExpression is a function body with yield as an identifier in strict mode. (Geenerator method as a ClassDeclaration element)
+esid: prod-GeneratorMethod
+features: [object-spread, generators]
+flags: [generated, onlyStrict]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    ClassElement :
+      MethodDefinition
+
+    MethodDefinition :
+      GeneratorMethod
+
+    14.4 Generator Function Definitions
+
+    GeneratorMethod :
+      * PropertyName ( UniqueFormalParameters ) { GeneratorBody }
+
+
+    Spread Properties
+
+    PropertyDefinition[Yield]:
+      (...)
+      ...AssignmentExpression[In, ?Yield]
+
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var callCount = 0;
+
+class C { *gen() {
+    callCount += 1;
+    return {
+         ...(function() {
+            var yield;
+            throw new Test262Error();
+         }()),
+      }
+}}
+
+var gen = C.prototype.gen;
+
+var iter = gen();
+
+
+
+assert.sameValue(callCount, 1);

### 2018-07-20 seeds/test262/language/statements/class/privatename-not-valid-earlyerr-script-6.js

@@ -1,0 +1,22 @@
+// Copyright (C) 2017 Valerie Young. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+esid: sec-scripts-static-semantics-early-errors
+description: Early error when referencing privatename outside of class.
+info: |
+  Static Semantics: Early Errors
+    Script : ScriptBody
+    1. Let names be an empty List.
+      ...
+    3. If AllPrivateNamesValid of ScriptBody with the argument names is false, throw a SyntaxError exception.
+features: [class, class-fields-private]
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+class C {}
+
+new C().#x;

### 2018-07-20 seeds/test262/language/statements/class/syntax/early-errors/class-body-static-method-contains-direct-super.js

@@ -1,0 +1,21 @@
+// Copyright (C) 2015 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+es6id: 14.5.1
+description: >
+    ClassElement : static MethodDefinition
+
+    It is a Syntax Error if HasDirectSuper of MethodDefinition is true.
+
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+class A {
+  static method() {
+    super();
+  }
+}
+

### 2018-07-20 seeds/test262/language/statements/for-await-of/async-gen-dstr-var-async-ary-ptrn-rest-not-final-id.js

@@ -1,0 +1,64 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding-for-await/ary-ptrn-rest-not-final-id.case
+// - src/dstr-binding-for-await/default/for-await-of-async-gen-var-async.template
+/*---
+description: Rest element (identifier) may not be followed by any element (for-await-of statement)
+esid: sec-for-in-and-for-of-statements-runtime-semantics-labelledevaluation
+features: [destructuring-binding, async-iteration]
+flags: [generated, async]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    IterationStatement :
+        for await ( ForDeclaration of AssignmentExpression ) Statement
+
+    [...]
+    2. Return ? ForIn/OfBodyEvaluation(ForDeclaration, Statement, keyResult,
+        lexicalBinding, labelSet, async).
+
+    13.7.5.13 Runtime Semantics: ForIn/OfBodyEvaluation
+
+    [...]
+    4. Let destructuring be IsDestructuring of lhs.
+    [...]
+    6. Repeat
+       [...]
+       j. If destructuring is false, then
+          [...]
+       k. Else
+          i. If lhsKind is assignment, then
+             [...]
+          ii. Else if lhsKind is varBinding, then
+              [...]
+          iii. Else,
+               1. Assert: lhsKind is lexicalBinding.
+               2. Assert: lhs is a ForDeclaration.
+               3. Let status be the result of performing BindingInitialization
+                  for lhs passing nextValue and iterationEnv as arguments.
+          [...]
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var iterCount = 0;
+var asyncIter = (async function*() {
+  yield* [[1, 2, 3]];
+})();
+
+async function *fn() {
+  for await (var [...x, y] of asyncIter) {
+    
+
+    iterCount += 1;
+  }
+}
+
+fn().next()
+  .then(() => assert.sameValue(iterCount, 1, 'iteration occurred as expected'), $DONE)
+  .then($DONE, $DONE);

### 2018-07-20 seeds/test262/language/statements/for-in/dstr-obj-prop-elem-init-yield-ident-invalid.js

@@ -1,0 +1,33 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-assignment/obj-prop-elem-init-yield-ident-invalid.case
+// - src/dstr-assignment/syntax/for-in.template
+/*---
+description: When a `yield` token appears within the Initializer of an AssignmentElement and outside of a generator function body, it should behave as an IdentifierReference. (For..in statement)
+esid: sec-for-in-and-for-of-statements-runtime-semantics-labelledevaluation
+es6id: 13.7.5.11
+features: [destructuring-binding]
+flags: [generated, onlyStrict]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    IterationStatement :
+      for ( LeftHandSideExpression of AssignmentExpression ) Statement
+
+    1. Let keyResult be the result of performing ? ForIn/OfHeadEvaluation(« »,
+       AssignmentExpression, iterate).
+    2. Return ? ForIn/OfBodyEvaluation(LeftHandSideExpression, Statement,
+       keyResult, assignment, labelSet).
+
+    13.7.5.13 Runtime Semantics: ForIn/OfBodyEvaluation
+
+    [...]
+    4. If destructuring is true and if lhsKind is assignment, then
+       a. Assert: lhs is a LeftHandSideExpression.
+       b. Let assignmentPattern be the parse of the source text corresponding to
+          lhs using AssignmentPattern as the goal symbol.
+    [...]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+for ({ x: x = yield } in [{}]) ;

### 2018-07-20 seeds/test262/language/statements/for-in/labelled-fn-stmt-let.js

@@ -1,0 +1,18 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: It is a Syntax Error if IsLabelledFunction(Statement) is true.
+negative:
+  phase: parse
+  type: SyntaxError
+esid: sec-semantics-static-semantics-early-errors
+es6id: 13.7.1.1
+info: |
+    Although Annex B describes an extension which permits labelled function
+    declarations outside of strict mode, this early error is applied regardless
+    of the language mode.
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+for (let x in {}) label1: label2: function f() {}

### 2018-07-20 seeds/test262/language/statements/for-of/dstr-let-ary-ptrn-rest-init-id.js

@@ -1,0 +1,58 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-id.case
+// - src/dstr-binding/default/for-of-let.template
+/*---
+description: Reset element (identifier) does not support initializer (for-of statement)
+esid: sec-for-in-and-for-of-statements-runtime-semantics-labelledevaluation
+es6id: 13.7.5.11
+features: [destructuring-binding]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    IterationStatement :
+        for ( ForDeclaration of AssignmentExpression ) Statement
+
+    [...]
+    3. Return ForIn/OfBodyEvaluation(ForDeclaration, Statement, keyResult,
+       lexicalBinding, labelSet).
+
+    13.7.5.13 Runtime Semantics: ForIn/OfBodyEvaluation
+
+    [...]
+    3. Let destructuring be IsDestructuring of lhs.
+    [...]
+    5. Repeat
+       [...]
+       h. If destructuring is false, then
+          [...]
+       i. Else
+          i. If lhsKind is assignment, then
+             [...]
+          ii. Else if lhsKind is varBinding, then
+              [...]
+          iii. Else,
+               1. Assert: lhsKind is lexicalBinding.
+               2. Assert: lhs is a ForDeclaration.
+               3. Let status be the result of performing BindingInitialization
+                  for lhs passing nextValue and iterationEnv as arguments.
+          [...]
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var iterCount = 0;
+
+for (let [...x = []] of [[]]) {
+  
+
+  iterCount += 1;
+}
+
+assert.sameValue(iterCount, 1, 'Iteration occurred as expected');

### 2018-07-20 seeds/test262/language/statements/for-of/head-lhs-invalid-asnmt-ptrn-ary.js

@@ -1,0 +1,20 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+description: Invalid destructuring assignment pattern (array literal)
+info: |
+    It is a Syntax Error if LeftHandSideExpression is either an ObjectLiteral
+    or an ArrayLiteral and if the lexical token sequence matched by
+    LeftHandSideExpression cannot be parsed with no tokens left over using
+    AssignmentPattern as the goal symbol.
+esid: sec-for-in-and-for-of-statements-static-semantics-early-errors
+es6id: 13.7.5
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+for ([(x, y)] of []) {}

### 2018-07-20 seeds/test262/language/statements/for-of/let-array-with-newline.js

@@ -1,0 +1,21 @@
+// Copyright (C) 2017 André Bargull. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-for-in-and-for-of-statements
+description: >
+  ExpressionStatement has a lookahead restriction for `let [`.
+info: |
+  ExpressionStatement[Yield, Await] :
+    [lookahead ∉ { {, function, async [no LineTerminator here] function, class, let [ }]
+    Expression[+In, ?Yield, ?Await] ;
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [noStrict]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+for (var x of []) let
+[a] = 0;

### 2018-07-20 seeds/test262/language/statements/generators/dstr-dflt-ary-ptrn-rest-init-obj.js

@@ -1,0 +1,58 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-init-obj.case
+// - src/dstr-binding/default/gen-func-decl-dflt.template
+/*---
+description: Reset element (nested object pattern) does not support initializer (generator function declaration (default parameter))
+esid: sec-generator-function-definitions-runtime-semantics-instantiatefunctionobject
+es6id: 14.4.12
+features: [generators, destructuring-binding, default-parameters]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    GeneratorDeclaration : function * ( FormalParameters ) { GeneratorBody }
+
+        [...]
+        2. Let F be GeneratorFunctionCreate(Normal, FormalParameters,
+           GeneratorBody, scope, strict).
+        [...]
+
+    9.2.1 [[Call]] ( thisArgument, argumentsList)
+
+    [...]
+    7. Let result be OrdinaryCallEvaluateBody(F, argumentsList).
+    [...]
+
+    9.2.1.3 OrdinaryCallEvaluateBody ( F, argumentsList )
+
+    1. Let status be FunctionDeclarationInstantiation(F, argumentsList).
+    [...]
+
+    9.2.12 FunctionDeclarationInstantiation(func, argumentsList)
+
+    [...]
+    23. Let iteratorRecord be Record {[[iterator]]:
+        CreateListIterator(argumentsList), [[done]]: false}.
+    24. If hasDuplicates is true, then
+        [...]
+    25. Else,
+        b. Let formalStatus be IteratorBindingInitialization for formals with
+           iteratorRecord and env as arguments.
+    [...]
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+var callCount = 0;
+function* f([...{ x } = []] = []) {
+  
+  callCount = callCount + 1;
+};
+f().next();
+assert.sameValue(callCount, 1, 'generator function invoked exactly once');

### 2018-07-20 seeds/test262/language/statements/if/if-fun-no-else-strict.js

@@ -1,0 +1,25 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: AnnexB extension not honored in strict mode (IfStatement without an else clause in the global scope)
+esid: sec-if-statement
+es6id: 13.6
+flags: [onlyStrict]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    The following rules for IfStatement augment those in 13.6:
+
+    IfStatement[Yield, Return]:
+        if ( Expression[In, ?Yield] ) FunctionDeclaration[?Yield] else Statement[?Yield, ?Return]
+        if ( Expression[In, ?Yield] ) Statement[?Yield, ?Return] else FunctionDeclaration[?Yield]
+        if ( Expression[In, ?Yield] ) FunctionDeclaration[?Yield] else FunctionDeclaration[?Yield]
+        if ( Expression[In, ?Yield] ) FunctionDeclaration[?Yield]
+
+    The above rules are only applied when parsing code that is not strict mode code.
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+if (true) function f() {}

### 2018-07-20 seeds/test262/language/statements/let/dstr-ary-ptrn-rest-not-final-obj.js

@@ -1,0 +1,33 @@
+// This file was procedurally generated from the following sources:
+// - src/dstr-binding/ary-ptrn-rest-not-final-obj.case
+// - src/dstr-binding/default/let-stmt.template
+/*---
+description: Rest element (object binding pattern) may not be followed by any element (`let` statement)
+esid: sec-let-and-const-declarations-runtime-semantics-evaluation
+es6id: 13.3.1.4
+features: [destructuring-binding]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    LexicalBinding : BindingPattern Initializer
+
+    1. Let rhs be the result of evaluating Initializer.
+    2. Let value be GetValue(rhs).
+    3. ReturnIfAbrupt(value).
+    4. Let env be the running execution context's LexicalEnvironment.
+    5. Return the result of performing BindingInitialization for BindingPattern
+       using value and env as the arguments.
+
+    13.3.3 Destructuring Binding Patterns
+    ArrayBindingPattern[Yield] :
+        [ Elisionopt BindingRestElement[?Yield]opt ]
+        [ BindingElementList[?Yield] ]
+        [ BindingElementList[?Yield] , Elisionopt BindingRestElement[?Yield]opt ]
+---*/
+// throw "Test262: This statement should not be evaluated.";
+
+let [...{ x }, y] = [1, 2, 3];
+
+

### 2018-07-20 seeds/test262/language/statements/return/S12.9_A1_T4.js

@@ -1,0 +1,19 @@
+// Copyright 2009 the Sputnik authors.  All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+info: Appearing of "return" without a function body leads to syntax error
+es5id: 12.9_A1_T4
+description: Checking if execution of "return" with no function fails
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+//////////////////////////////////////////////////////////////////////////////
+//CHECK#1
+return;
+//
+//////////////////////////////////////////////////////////////////////////////

### 2018-07-20 seeds/test262/language/statements/switch/syntax/redeclaration/async-generator-declaration-attempt-to-redeclare-with-const-declaration.js

@@ -1,0 +1,23 @@
+// This file was procedurally generated from the following sources:
+// - src/declarations/redeclare-with-const-declaration.case
+// - src/declarations/redeclare/switch-attempt-to-redeclare-async-generator-declaration.template
+/*---
+description: redeclaration with const-LexicalDeclaration (AsyncGeneratorDeclaration in SwitchStatement)
+esid: sec-switch-statement-static-semantics-early-errors
+features: [async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    SwitchStatement : switch ( Expression ) CaseBlock
+
+    It is a Syntax Error if the LexicallyDeclaredNames of CaseBlock contains any
+    duplicate entries.
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+switch (0) { case 1: async function* f() {} default: const f = 0; }

### 2018-07-20 seeds/test262/language/statements/switch/syntax/redeclaration/async-generator-declaration-attempt-to-redeclare-with-generator-declaration.js

@@ -1,0 +1,23 @@
+// This file was procedurally generated from the following sources:
+// - src/declarations/redeclare-with-generator-declaration.case
+// - src/declarations/redeclare/switch-attempt-to-redeclare-async-generator-declaration.template
+/*---
+description: redeclaration with GeneratorDeclaration (AsyncGeneratorDeclaration in SwitchStatement)
+esid: sec-switch-statement-static-semantics-early-errors
+features: [generators, async-iteration]
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    SwitchStatement : switch ( Expression ) CaseBlock
+
+    It is a Syntax Error if the LexicallyDeclaredNames of CaseBlock contains any
+    duplicate entries.
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+switch (0) { case 1: async function* f() {} default: function* f() {} }

### 2018-07-20 seeds/test262/language/statements/switch/syntax/redeclaration/let-declaration-attempt-to-redeclare-with-function-declaration.js

@@ -1,0 +1,22 @@
+// This file was procedurally generated from the following sources:
+// - src/declarations/redeclare-with-function-declaration.case
+// - src/declarations/redeclare-allow-sloppy-function/switch-attempt-to-redeclare-let-declaration.template
+/*---
+description: redeclaration with FunctionDeclaration (LexicalDeclaration (let) in SwitchStatement)
+esid: sec-switch-statement-static-semantics-early-errors
+flags: [generated]
+negative:
+  phase: parse
+  type: SyntaxError
+info: |
+    SwitchStatement : switch ( Expression ) CaseBlock
+
+    It is a Syntax Error if the LexicallyDeclaredNames of CaseBlock contains any
+    duplicate entries.
+
+---*/
+
+
+// throw "Test262: This statement should not be evaluated.";
+
+switch (0) { case 1: let f; default: function f() {} }

### 2018-07-20 seeds/test262/language/statements/try/catch-parameter-boundnames-restriction-arguments-negative-early.js

@@ -1,0 +1,16 @@
+// Copyright (c) 2017 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+
+/*---
+esid: sec-strict-mode-of-ecmascript
+description: >
+    It is a SyntaxError if a CatchParameter occurs within strict mode code and BoundNames of CatchParameter contains either eval or arguments (13.15.1).
+negative:
+  phase: parse
+  type: SyntaxError
+flags: [onlyStrict]
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+try { } catch (arguments) { }

### 2018-07-20 seeds/test262/language/statements/try/early-catch-duplicates.js

@@ -1,0 +1,16 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+esid: sec-try-statement-static-semantics-early-errors
+es6id: 13.15.1
+description: >
+    It is a Syntax Error if BoundNames of CatchParameter contains any duplicate
+    elements.
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+try { } catch ([x, x]) {}

### 2018-07-20 seeds/test262/language/statements/with/decl-let.js

@@ -1,0 +1,15 @@
+// Copyright (C) 2016 the V8 project authors. All rights reserved.
+// This code is governed by the BSD license found in the LICENSE file.
+/*---
+description: Lexical declaration (let) not allowed in statement position
+esid: sec-with-statement
+es6id: 13.11
+flags: [noStrict]
+negative:
+  phase: parse
+  type: SyntaxError
+---*/
+
+// throw "Test262: This statement should not be evaluated.";
+
+with ({}) let x;

### 2018-07-20 paper/paper.tex
Refactoring seeds folder
pass on intro and es section

@@
 of the community for the language encourages constant improvements in
-its specification and implementations. It is natural to expect that
-such improvements will entail sensible changes in runtime
-engines~\cite{kangax}; changes that could lead to errors. Finding bugs
-on JS engines is an important problem.
+its specification and implementations (see
+Section~\ref{sec:es6-design}). It is natural to expect that such
+improvements will entail sensible changes in runtime
+engines~\cite{kangax}; changes that could lead to errors. Even small
+changes can have a large impact in practice. For example, in October
+2014 a new attribute added to the Array datatype caused a bug that
+resulted in MS Outlook web not working under
+Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
+sum, finding bugs on JS engines is an important problem.
 
 Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
-approach that has been applied in a variety of contexts to find
-functional bugs in
+approach that has been applied in a variety of contexts to find bugs
+in
 software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
@@
 then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
-Cross-engine differential testing checks correctness by comparing the
-output produced by \emph{different} engines on a given
-input~\cite{patra2016learning}. The availability on the web of public
+Cross-engine differential testing, in contrast, checks correctness by
+comparing the output produced by \emph{different} engines on a given
+input~\cite{patra2016learning}. The availability of public
 implementations of JS engines (see Table~\ref{tab:engines}) and test
-suites makes this bug-finding approach very appealing.
+suites makes this bug-finding approach appealing.
 
@@
 the reliability of existing JS engines and to (ii) evaluate the
-importance of different factors when using DT for bug finding. More
-precisely, we analyzed the impact of two orthogonal factors in the use
-of DT: test mining and fuzzing. The first dimension, test mining,
-considers the effect that \js{} test files mined from the repository
-of a given open-source engine have in detecting functional bugs in
-other engines. The second dimension, fuzzing, considers the impact of
-fuzzing the mined files in bug detection.
+importance of different factors when using DT. More precisely, we
+analyzed the impact of two orthogonal factors in DT: test mining and
+fuzzing. The first factor, test mining, considers the effect that
+\js{} test files mined from the repositories of open-source engines
+have in detecting functional bugs in other engines. The second factor,
+fuzzing, considers the impact in bug detection of fuzzing these files.
 %% WHAT WE FOUND
@@
 
-\section{ES6 design}
+\section{EcmaScript}
 \label{sec:es6-design}
-The EcmaScript is a language specification maintained by 
-a committee called TC39 (Technical Committee) that follows 
-standard rules proposed by ISO/ETC JTC 1 - 
-Information Technology since 1996~\cite{es6-website}.
-Every year, a new version of EcmaScript (the latest version is ES2017) adds
-new features and minor fixes for the language. \Fix{discutir mais
-  sobre isso}
+
+ECMAScript (\es{}) emerged with the goal to standardize variants of
+JavaScript, such as Netscape's JavaScript and Microsoft's JScript. The
+\es{} specification is maintained by the TC39~\cite{tc39-github}
+technical committee under the regulation of Ecma
+International~\cite{es6-website}.  Every year, a new version of the
+specification is delivered with new features and minor fixes. The
+canonical spec today is
+ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
+versions and supporting engines can be found elsewhere~\cite{kangax}.
+
+\subsection{Engines Design}
 
@@
   undertand the JS ecosystem design and can explain with confidence.}
+
+\subsection{Implementation-Dependent Behavior}
+\label{sec:imp-dep-behavior}
+
+The \es{} spec uses the label ``implementation-dependent'' to indicate
+cases where each engine developer can decide how to implement some
+aspect of a functionality. In these cases, execution may differ from
+engine to engine. One of the reasons implementation-dependent behavior
+exists is to enable compiler optimizations. For example, the
+\mcodeid{for-in} loop does not clearly specify the iteration
+order~\cite{for-in-undefined} and different engines capitalize on
+that.
 
@@
   relationship with HI/LO.}
+
+\subsection{Undefined Behavior}
+\label{sec:undef-behavior}
+
+Undefined behavior is not a feature of the C
+language~\cite{c-undefined}.
+
+\Mar{mention strict?}
+
+\subsection{Unintentional Discrepancies}
+
+It is worth to recall that there is no formal specification for \es{};
+the specification is written in natural language. As such, differences
+in behavior from one engine to another, other than those mentioned
+above (Sections~\ref{sec:imp-dep-behavior}
+and~\ref{sec:undef-behavior}), can occur. But these discrepancies are
+not acceptable.
 
@@
     table show, respectively, the TC-39 conformance test suite, suites
-    from engines we analyzed, and other suites.}
+    from engines we analyzed, and suites from other engines.}
   \begin{tabular}{ccr}
@@
 
-  A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
-  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
-  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
-  \Fix{discuss}
+  % A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
+  % quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
+  % devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
 

### 2018-07-25 paper/paper.tex
fix results

--- 2018-07-19 paper/paper.tex
@@
     \midrule
-    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 45,144 \\
+    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
     \midrule
     Mozilla & \cite{mozilla} & 2,633 \\
-    V8 & \cite{v8} & 64 \\
+    V8 & \cite{v8} & 74 \\
     WebKit & \cite{webkit} & 1,031 \\
     \midrule    
-    Duktape & \cite{duktape} & 997 \\
-    JerryScript & \cite{jerryscript} & 1,803 \\
-    JSI & \cite{jsi} & 99 \\
-    Tiny-js & \cite{tinyjs} & 44 \\    
+    Duktape & \cite{duktape} & 1,195 \\ 
+    JerryScript & \cite{jerryscript} & 1,950 \\
+    JSI & \cite{jsi} & 98 \\
+    Tiny-js & \cite{tinyjs} & 48 \\    
     % Chakra & \cite{chakracore} & 2632 \\
     \midrule
-     &  & 51,815 \\
+     &  & 38,305 \\
    \bottomrule     
@@
 
-  A diversidade de suites de testes influenciou na busca de bugs nao descobertos
-  pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
-  foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
-  foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
-  \nofuzzWebKit{} sao do WebKit e \nofuzzGoogleDuktap{} para o V8 e o Duktape, 
-  os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
-  engines.
+  % A diversidade de suites de testes influenciou na busca de bugs nao descobertos
+  % pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
+  % foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
+  % foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
+  % \nofuzzWebKit{} sao do WebKit e \nofuzzGoogle{}Duktap{} para o V8 e o Duktape, 
+  % os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
+  % engines.
 
-  A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
-  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
-  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
-  \Fix{discuss}
+  % A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
+  % quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
+  % devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
 

### 2018-07-25 paper/paper.tex

--- 2018-07-20 paper/paper.tex
@@
 
-  A diversidade de suites de testes influenciou na busca de bugs nao descobertos
-  pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
-  foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
-  foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
-  \nofuzzWebKit{} sao do WebKit e \nofuzzGoogleDuktap{} para o V8 e o Duktape, 
-  os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
-  engines.
+  % A diversidade de suites de testes influenciou na busca de bugs nao descobertos
+  % pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
+  % foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
+  % foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
+  % \nofuzzWebKit{} sao do WebKit e \nofuzzGoogle{}Duktap{} para o V8 e o Duktape, 
+  % os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
+  % engines.
 

### 2018-07-30 paper/paper.tex
pass on result
adjusting text

--- 2018-07-20 paper/paper.tex
@@
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
-sum, finding bugs on JS engines is an important problem.
+sum, finding bugs in JS engines is an important problem specially
+because of the speed the specification evolves and the availability of
+various public engines.
 
@@
 SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
-across configurations. They use this technique since 2002 and have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, some of which are security bugs.
+across different configurations of the same build (\eg{}, enabling or
+not eager JIT compilation). They use this technique since 2002 and
+have been able to find over 270 bugs since
+then~\cite{jsfunfuzz-at-mozilla}, including security bugs.
 Cross-engine differential testing, in contrast, checks correctness by
 comparing the output produced by \emph{different} engines on a given
-input~\cite{patra2016learning}. The availability of public
-implementations of JS engines (see Table~\ref{tab:engines}) and test
-suites makes this bug-finding approach appealing.
+input~\cite{patra2016learning}. Although different implementations of
+JS engines today (see Table~\ref{tab:engines}), this technique is not
+used in practice.
 
@@
 analyzed the impact of two orthogonal factors in DT: test mining and
-fuzzing. The first factor, test mining, considers the effect that
-\js{} test files mined from the repositories of open-source engines
-have in detecting functional bugs in other engines. The second factor,
-fuzzing, considers the impact in bug detection of fuzzing these files.
+fuzzing. The first factor--\emph{test mining}--considers the effect
+that \js{} test files mined from the repositories of open-source
+engines have in detecting functional bugs in other engines. The second
+factor--\emph{fuzzing}--considers the impact in bug detection of
+fuzzing these files.
 %% WHAT WE FOUND
@@
 
-\section{EcmaScript}
+\section{JavaScript}
 \label{sec:es6-design}
 
-ECMAScript (\es{}) emerged with the goal to standardize variants of
-JavaScript, such as Netscape's JavaScript and Microsoft's JScript. The
-\es{} specification is maintained by the TC39~\cite{tc39-github}
-technical committee under the regulation of Ecma
-International~\cite{es6-website}.  Every year, a new version of the
-specification is delivered with new features and minor fixes. The
-canonical spec today is
+JavaScript engines are virtual machines that parse source code and
+compile it in bytecodes. These engines implement some version of
+ECMAScript\footnote{The name JavaScript still prevails today,
+  certainly for historical reasons.} (\es{}), which emerged with the
+goal to standardize variants of the language, such as Netscape's
+JavaScript and Microsoft's JScript. The \es{} specification is
+regulated by Ecma International~\cite{es6-website} under the
+TC39~\cite{tc39-github} technical committee.  Every year, a new
+version of the \es{} specification is produced with new features and
+minor fixes. The canonical spec today is
 ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
-versions and supporting engines can be found elsewhere~\cite{kangax}.
+versions and supporting engines are publicly available~\cite{kangax}.
+In the following, we briefly describe different sources of
+discrepancies that can emerge across different engine implementations
+as results of the active changes in the \es{} specification.
 
-\subsection{Engines Design}
+%% \Mar{what is that exactly? can we cite? is that only spec or actually
+%%   code as most of java.* libraries.}  \Igor{seems like an API. They
+%%   define the language behavior; grammar; values to static variables;
+%%   the methods for each "class"(Object)...  These irregularities
+%%   appears on engine implementation, maybe an wrong if statement and so
+%%   on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
+%%   explanation in some forum/tutorial and explain **when** you
+%%   undertand the JS ecosystem design and can explain with confidence.}
 
-\Mar{what is that exactly? can we cite? is that only spec or actually
-  code as most of java.* libraries.}  \Igor{seems like an API. They
-  define the language behavior; grammar; values to static variables;
-  the methods for each "class"(Object)...  These irregularities
-  appears on engine implementation, maybe an wrong if statement and so
-  on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
-  explanation in some forum/tutorial and explain **when** you
-  undertand the JS ecosystem design and can explain with confidence.}
-
-\subsection{Implementation-Dependent Behavior}
+\subsection{Undefined (Implementation-Dependent) Behavior}
 \label{sec:imp-dep-behavior}
@@
 \mcodeid{for-in} loop does not clearly specify the iteration
-order~\cite{for-in-undefined} and different engines capitalize on
-that.
+order~\cite{so-forin-undefined,javascript-in-chrome} and different
+engines capitalize on that~\cite{for-in-undefined}. As another
+example, \Fix{...}
 
@@
 
-\subsection{Undefined Behavior}
-\label{sec:undef-behavior}
+\subsection{Randomness}
 
-Undefined behavior is not a feature of the C
-language~\cite{c-undefined}.
+\sloppy Some elements in JS have non-deterministic behavior (\eg{},
+Math.random and Date). A test that make decisions based on these
+elements could, in principle, produce different outcomes on different
+runs. Carefully-written test cases should not manifest this kind of
+flakiness~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
+fuzzed test files are more likely to manifest them.
 
-\Mar{mention strict?}
+\subsection{\Fix{Other}}
 
-\subsection{Unintentional Discrepancies}
+1) The stack depth in JS is often close to the real (native) C stack
+depth, nevertheless observable by JS through recursion. This causes
+differential behavior even on the same engine when JITs are enabled or
+disabled, as the stack frame sizes vary. LangFuzz in particular
+produces a lot of recursions and hits these problems even more often
+than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
+  could be different.}
+
+\subsection{Bugs}
 
@@
 not acceptable.
-
-\subsection{Randomness and Undefined Behavior}
-
-\Mar{answer from C. Holler. Think through this...}
-
-1) The stack depth in JS is often close to the real (native) C stack depth, nevertheless observable by JS through recursion.
-This causes differential behavior even on the same engine when JITs are enabled or disabled, as the stack frame sizes vary.
-LangFuzz in particular produces a lot of recursions and hits these problems even more often than jsfunfuzz.
-
-2) JS has some "undefined behavior", such as the enumeration order of object properties in certain cases.
-In our engine, we have an --enable-more-deterministic mode (build option) to solve some of these issues.
-
-3) JS naturally has some observable differential behavior in global objects, e.g.
-Math.random, Date, etc.
-These can often be mocked to solve these issues, but fuzzers can be surprisingly effective to find more of these sources or even get the old objects back somehow.
 
@@
 decided to discard those. For example, many tests we found required a
-Node.js runtime~\cite{node} for execution. We considered the offical
-TC-39~\cite{tc39-github} conformance test suite for the ECMA262
-specification~\cite{ecmas262-spec}. Furthermore, we considered test
-suites of three of the four engines mentioned in
+Node.js runtime~\cite{node} for execution. The main source of test
+cases is the offical TC-39~\cite{tc39-github} conformance test suite
+for the ECMA262 specification~\cite{ecmas262-spec}. This test suite
+contains 87\% of all the tests we used. Furthermore, we
+considered test suites of three of the four engines mentioned in
 Section~\ref{sec:methodology:engines} and four other engines.
@@
 distinct frameworks for testing and require external libraries to run
-their testing suites.  For these projects, we needed to make small
+the tests.  For these projects, we needed to make small
 changes in the testing infrastructure to be able to run the tests
 uniformly across all engines. More precisely, we needed to mock
-functions, related to the test harness, which are only available to
+some functions, related to the test harness, which are only available to
 certain engines.
@@
 which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction.  We analyzed
-three grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz}, and
-QuickFuzz~\cite{quickfuzz,grieco2016quickfuzz}.  Unfortunately, none
-of those was effective out of the box. Given the bound limits we
-defined on the number of inputs to generate and the exploration depth
-of the syntax tree, we were unable to find discrepancies on the inputs
-those tools generated. To sum, the tools produced a high percentage of
-semantically-invalid inputs (\eg{}, \Fix{give one or two concrete
-  examples--variable usage without definition?}) that we needed to
-discard and the valid inputs manifested no discrepancies. For example,
-we produced 100K inputs with Grammarinator and only \Fix{X} of those
-were valid. With QuickFuzz, we were able to produce \Fix{Y, Y$>$Y?}
-valid inputs as it contains some heuristics to circumvent violation of
-certain type rules such as \Fix{variable used must be
-  defined?}. Nonetheless, running those inputs in our infrastructure
-we were unable to find discrepancies. Inpecting those inputs, we
-realized that they reflected very simple scenarios.\Comment{ \Mar{are there
-  weights associated with production rules besides the depth you can
-  set?}} Although grammar-based fuzzers has been shown effective to
-find real bugs\Fix{cite some jsfunfuzz bug reports}, generating
-valid inputs is very time-consuming, especially for the context of
-differential testing. For this reason, we did not consider those fuzzers.
+inputs that are syntactically valid by construction. We analyzed four
+grammar-based fuzzers--Grammarinator~\cite{grammarinator},
+jsfunfuzz~\cite{jsfunfuzz},
+LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
+Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
+were effective out of the box. For example, we produced 100K inputs
+with Grammarinator and only \Fix{X} of those were valid. With
+Megadeth, we were able to produce \Fix{Y, Y$>$Y?}  valid inputs as it
+contains some heuristics to circumvent violations of certain type
+rules such as \Fix{variable used must be defined?}. Nonetheless,
+running those inputs in our infrastructure we were unable to find
+discrepancies. Inpecting those inputs, we realized that they reflected
+very simple scenarios. To sum, a high percentage of inputs that
+Grammarinator and Megadeth generated were semantically-invalid that we
+needed to discard whereas the valid inputs manifested no
+discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
+that, in addition to the issues mentioned above, it produces inputs
+that use functions that are only available in the SpiderMonkey
+engine. We would need either to mock those functions in other engines
+or to discard those tests. Considering
+LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
+publicly available. One fundamental issue associated with generational
+fuzzers in our context is that the tests they produce do not contain
+assertions; to enable the integration of this kind of fuzzers in our
+infrastructure, we would need to look for discrepancies across
+compiler messages.  All in all, although grammar-based fuzzers have
+been shown effective to find real
+bugs~\cite{Holler:2012:FCF:2362793.2362831}, generating valid inputs,
+albeit promising conceptually, still requires some engineering
+effort. For this reason, we did not consider those fuzzers in this
+study.
 
@@
   checking~\cite{clang-documentation}.}. AFL use coverage to determine
-inputs that uncover a new branch and deserve fuzzing whereas libFuzzer
-uses evolutionary generation--it tries to minimize the distances to
-still-uncovered branches of the program. AFL takes the instrumented
-program binary (say, a JS engine) and one seed input to that program
-(say, a JS program) and produces on output fault-revealing inputs, if
-found. Considering our context of application, we needed to instrument
-one runtime engine for fuzzing; we chose v8. Unfortunately, we found
-that most of the inputs produced by AFL violate the JS
-grammar. Furthermore, the fuzzing task can take daysfor a single seed
-input and there is no simple way to guide the
-exploration~\Fix{cite}. That happens because the fuzzer aims to
-explore the entire decision tree induced from the engine's main
-function, including the branches associated with the lexer and the
-parser. For those reasons, coverage-based fuzzers were not considered
-in this study. It is worth mentioning that Google mitigates that
-problem with libFuzzer by asking developers to create fuzz targets for
+inputs that uncover a new branch and hence should be fuzzed more
+whereas libFuzzer uses evolutionary generation--it tries to minimize
+the distances to still-uncovered branches of the program. AFL takes
+the instrumented program binary (say, a JS engine) and one seed input
+to that program (say, a JS program) and produces on output
+fault-revealing inputs, if found. Considering our context of
+application, we needed to instrument one runtime engine for fuzzing;
+we chose v8. Unfortunately, we found that most of the inputs produced
+by AFL violate the JS grammar. Furthermore, the fuzzing task can take
+days for a single seed input and there is no simple way to guide the
+exploration\footnote{Exchanged emails with the tool author.}. That
+happens because the fuzzer aims to explore the entire decision tree
+induced from the engine's main function, including the branches
+associated with the higher layers of the compiler (\eg{}, lexer and
+parser). It is worth mentioning that Google mitigates that problem
+with libFuzzer by asking developers to create fuzz targets for
 specific program
@@
 that approach has shown very effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target.
+to create the calling context to invoke the fuzz target. For those
+reasons, coverage-based fuzzers were not considered in this study.
 
-\Fix{...do the same as above for black-box fuzzing. explain what kinds of
-inputs they can generate.}
+We uses two black-box mutational fuzzers in this
+study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
+fuzzers require no instrumentation and domain-knowledge. They mutate
+\emph{existing} inputs randomly. The strenght of the approach is
+limited by the supported mutation operators, which are typically
+simple, and the quality of the test suite. We chose \radamsa\ and
+\quickfuzz\ \Fix{...}
 
@@
 \end{document}
+
+%%  LocalWords:  bytecodes JScript Ecma

### 2018-07-31 paper/paper.tex
adding plots

@@
   \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
-
-  A diversidade de suites de testes influenciou na busca de bugs nao descobertos
-  pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
-  foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
-  foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
-  \nofuzzWebKit{} sao do WebKit e \nofuzzGoogleDuktap{} para o V8 e o Duktape, 
-  os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
-  engines.
+}
+  % A diversidade de suites de testes influenciou na busca de bugs nao descobertos
+  % pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
+  % foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
+  % foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
+  % \nofuzzWebKit{} sao do WebKit e \nofuzzGoogle{} para o V8 e o Duktape, 
+  % os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
+  % engines.
 
@@
   % foram encontrados warnings nestes engenhos, porem
-}
 
@@
   \centering
-  \includegraphics[trim=0 20 0 0,clip,width=0.25\textwidth]{R/barplot}  
-  \caption{\label{fig:workflow}HI and LO warnings reports by each fuzzer.}
+  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
+  \caption{\label{fig:distribution}Distribution of lo and hi warnings
+   in buckets.}
 \end{figure}

### 2018-07-31 paper/paper.tex
quick pass on results

--- 2018-07-30 paper/paper.tex
@@
 
+\Mar{explain what is a bucket (we refer to it later).}
 The infrastructure outputs a list of warnings for human inspection.
@@
 
-In this study, we analyzed the impact of two orthogonal dimensions in
-bug finding: test mining and fuzzing. The first dimension focuses on
-the impact of new inputs in bug finding whereas the second dimension
-focuses on the impact of variations of existing inputs in bug finding.
+The overarching goal of our study is to identify the ability of simple
+techniques to find bugs in \js\ engines with cross-engine differential
+testing.  We analyzed the impact of two orthogonal dimensions: test
+mining and fuzzing. The first dimension focuses on the impact of
+inputs, mined from the web, in bug finding whereas the second
+dimension focuses on the impact of fuzzing these inputs in bug
+finding.
+
+We describe the methodology we used in this experiment in the
+following. Recall that our tool produces warnings on output organized
+in buckets (Section~\ref{sec:design}). Each bucket describes a
+warnings--one per file (fuzzed or not)--and can be of ``lo'' or ``hi''
+importance, according to the heuristic we
+defined. Figure~\ref{fig:distribution} shows the distribution of
+warnings reported per bucket. Observe that in some cases the number of
+files per bucket is very high; it would be infeasible to manually
+inspect all of them. For that, we inspected each and every reported
+bucket but only one file per bucket. For the cases we found
+suspicious, we filed a bug report in the bug tracker. In some cases,
+we used the Mozila lithium tool~\cite{lithium} to minimize the test
+case. Table~\ref{tab:summary-of-results} summarizes the number of
+buckets of each category per execution mode. \Fix{elaborate}
+
+\begin{table}[t]
+  \centering
+  \caption{\label{tab:summary-of-results}Summary of results.}
+  \begin{tabular}{ccrr}
+    \toprule
+    mode & type & \# buckets & \% positive buckets \\ 
+    \midrule
+    \multirow{2}{*}{no-fuzz} & lo & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} \\
+                             & hi & \Fix{.} & \Fix{.} \\    
+    \bottomrule     
+  \end{tabular}
+\end{table}
 
@@
 In this experiment, we ran all tests (see Section~\ref{sec:seeds})
-using our infrastructure in no-fuzzing mode. We inspected all warnings
-reported by our tool and, for those we found suspicious, we filed a
-bug report in the corresponding bug tracker.
+using our infrastructure in no-fuzzing mode. The goal is to identify
+the impact of using publicly available tests on ..........
 

### 2018-07-31 paper/paper.tex
pass on results

--- 2018-07-31 paper/paper.tex
@@
 \Igor{
-  No total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
-  pertencentes aos buckets com prioridade HI e \nofuzzLowTotal{} da prioridade LO. 
-  Durante 3 meses, n\'os analisamos com rigor cada log gerado, sempre checando as 
-  especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
-  javascript que violem condições da especificacao ou apresentem discrepancias
-  entre as saidas de cada engenhos.
-  Nosso estudo revelou que dos \nofuzzHighTotal{} buckets do grupo HI, 
-  \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
-  \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
+  % Ao total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
+  % pertencentes aos buckets com prioridade HI e \nofuzzLowTotal{} da prioridade LO. 
+  % Durante 3 meses, n\'os analisamos com rigor cada log gerado, sempre checando as 
+  % especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
+  % javascript que violem condições da especificacao ou apresentem discrepancias
+  % entre as saidas de cada engenhos.
+  % Nosso estudo revelou que dos \nofuzzHighTotal{} buckets do grupo HI, 
+  % \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
+  % \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
 }
@@
     21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
-    23 & 7/18 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
+    23 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
     24 & 7/18 & \crossmark & JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & HI & JerryScript\\
+    25 & 7/27 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5548}{\#5548} & HI & Test262\\
+    26 & 7/27 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5549}{\#5549} & HI & Test262\\
    \bottomrule

### 2018-07-31 paper/paper.tex
minor fixes on methodology

@@
 following. Recall that our tool produces warnings on output organized
-in buckets (Section~\ref{sec:design}). Each bucket describes a
-warnings--one per file (fuzzed or not)--and can be of ``lo'' or ``hi''
-importance, according to the heuristic we
+in buckets (Section~\ref{sec:design}). Each bucket includes a set of
+warnings and each warning is related to one file.  A bucket is of
+``lo'' or ``hi'' importance, according to the heuristic we
 defined. Figure~\ref{fig:distribution} shows the distribution of
-warnings reported per bucket. Observe that in some cases the number of
-files per bucket is very high; it would be infeasible to manually
-inspect all of them. For that, we inspected each and every reported
-bucket but only one file per bucket. For the cases we found
-suspicious, we filed a bug report in the bug tracker. In some cases,
-we used the Mozila lithium tool~\cite{lithium} to minimize the test
-case. Table~\ref{tab:summary-of-results} summarizes the number of
+warnings reported per bucket. Observe that, in some cases, the number
+of files per bucket is very high; it would be impractical to manually
+inspect all of them. For that, we inspected each and every bucket but
+only inspected one file per bucket. For the cases we found the warning
+suspicious, we analyzed the parts of the documentation related to the
+problem and, if still suspicious, we looked on the bug tracker of the
+affected engine for potential duplicates. If none was reported, we
+filed a bug report in the bug tracker including the test input that
+manifested the potential problem and explaining the reasons we were
+suspicious. In some cases, we used the Mozila lithium
+tool~\cite{lithium} to minimize the test case. For the cases of false
+positive warnings, we classified the reason and moved to the next
+bucket. Table~\ref{tab:summary-of-results} summarizes the number of
 buckets of each category per execution mode. \Fix{elaborate}

### 2018-07-31 paper/paper.tex
.
pass on results

--- 2018-07-31 paper/paper.tex
@@
 
-In this study, we analyzed the impact of two orthogonal dimensions in
-bug finding: test mining and fuzzing. The first dimension focuses on
-the impact of new inputs in bug finding whereas the second dimension
-focuses on the impact of variations of existing inputs in bug finding.
+The overarching goal of our study is to identify the ability of simple
+techniques to find bugs in \js\ engines with cross-engine differential
+testing.  We analyzed the impact of two orthogonal dimensions in this
+study: test mining and fuzzing. The first dimension focuses on the
+impact of inputs, mined from the web, in bug finding whereas the
+second dimension focuses on the impact of fuzzing these inputs.
 
-\subsection{Test Mining}
+In the following, we describe the methodology we used in this
+experiment. Recall that our tool outputs a set of buckets, that each
+bucket includes a set of warnings, that each warning is related to one
+file, and that a bucket is of ``lo'' or ``hi'' importance, according
+to the heuristic we defined. Figure~\ref{fig:distribution} shows the
+distribution of number of warnings per bucket. We use the the label
+``nofuzz'' to refer to the experiment that analyzed the impact of test
+mining as we do not use fuzzing in that experiment and use the names
+of the fuzzing tools to refer to the results obtained with those
+tools. We inspected each and every bucket for bugs, but observe that
+the number of files per bucket is very high in some cases (\eg{},
+nofuzz [hi]). As such, it would be impractical to manually inspect all
+the files in the bucket. For that reason, we only inspected one file
+per bucket. For the cases we found the warning suspicious, we analyzed
+the parts of the documentation related to the problem and, if still
+suspicious, we looked on the bug tracker of the affected engine for
+potential duplicates. If none was reported, we filed a bug report in
+the bug tracker including the test input that manifested the potential
+problem and explaining the reasons we were suspicious. In some cases,
+we used the Mozila lithium tool~\cite{lithium} to minimize the test
+case. For the cases of false positives, we classified the reason for
+the misclassification and moved to the next
+bucket. Table~\ref{tab:summary-of-results} summarizes our results. It
+shows, for each execution mode and category of bucket (\ie{}, hi or
+lo), the total number of files involved, the number of buckets
+reported, and the percentage of those that resulted in a bug
+report. \Fix{elaborate summary} We elaborate those results in the
+following.
 
-In this experiment, we ran all tests (see Section~\ref{sec:seeds})
-using our infrastructure in no-fuzzing mode. We inspected all warnings
-reported by our tool and, for those we found suspicious, we filed a
-bug report in the corresponding bug tracker.
+\begin{table}[t]
+  \centering
+  \caption{\label{tab:summary-of-results}Summary of results.}
+  \begin{tabular}{ccrrr}
+    \toprule
+    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{2}{c}{buckets} \\
+    \cline{4-5}    
+    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\% positive} \\
+    \midrule
+    \multirow{2}{*}{no-fuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
+                             & hi & \Fix{.} & \Fix{.} & \Fix{.} \\    
+    \bottomrule     
+  \end{tabular}
+\end{table}
+
+\subsection{No Fuzzing}
+
+This section reports the results obtained without fuzzing. The goal is
+to observe the impact of the mined test cases in revealing
+differential bugs. In this experiment, we ran all tests (see
+Section~\ref{sec:seeds}) using our infrastructure in no-fuzzing
+mode.
 
@@
 
-The rationale for considering fuzzing as a dimension of study is to
-assess the extent to which changing existing inputs helps in finding
-new bugs. We measured this ability both in absolute terms and
-relatively to the number of bugs found with the seed inputs in
-no-fuzzing mode.
+This section reports the results obtained by fuzzing inputs with
+existing tools. It is important to mention that, to avoid experimental
+noise, we did not consider the \Fix{XX} files (\Fix{2.8\%} of the
+total) reported in the previous experiment, \ie{}, we only fuzzed test
+files whose output is consistent across all engines analyzed.
 

### 2018-07-31 paper/paper.tex
fix results

@@
     \midrule
-    \multirow{2}{*}{no-fuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
-    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{no-fuzz} & lo & \nofuzzFilesLO{} & \nofuzzLOTotal{} & 34.3\% \\
+    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & 70\% \\
     \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
@@
 \Igor{
+  Apos este experimento, foram obtidos \nofuzzAll{} buckets sendo destes \nofuzzHITotal
+
   % Ao total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
@@
 existing tools. It is important to mention that, to avoid experimental
-noise, we did not consider the \Fix{XX} files (\Fix{2.8\%} of the
+noise, we did not consider the \nofuzzTotalFiles{} files (\Fix{2.8\%} of the
 total) reported in the previous experiment, \ie{}, we only fuzzed test
@@
 
-\Igor{
-  Para realizar nossos experimentos, tivemos que decidir qual as 
-  melhores abordagens para aumentar a efetividade dos fuzzers.
-  Os fuzzers mutacionais se mostraram mais eficientes em relacao
-  aos fuzzers geracionais, entao focamos neste ponto.
-  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
-  default para realizar a mutacao em arquivos existentes.
-  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
-  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
-  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
-  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
-  radamsa, gerando arquivos mais relevantes.
-  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
-  é um arquivo de teste relevante, seguindo estes requisitos:
-  \begin{itemize}
-    \item it contains only unicode text
-    \item it is parseable (i.e., it is structurally well-formed)
-    \item it does not contain engine-specific functions  
-    \item it does not empty
-  \end{itemize}
+% \Igor{
+%   Para realizar nossos experimentos, tivemos que decidir qual as 
+%   melhores abordagens para aumentar a efetividade dos fuzzers.
+%   Os fuzzers mutacionais se mostraram mais eficientes em relacao
+%   aos fuzzers geracionais, entao focamos neste ponto.
+%   Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
+%   default para realizar a mutacao em arquivos existentes.
+%   O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
+%   deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
+%   pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
+%   O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
+%   radamsa, gerando arquivos mais relevantes.
+%   Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
+%   é um arquivo de teste relevante, seguindo estes requisitos:
+%   \begin{itemize}
+%     \item it contains only unicode text
+%     \item it is parseable (i.e., it is structurally well-formed)
+%     \item it does not contain engine-specific functions  
+%     \item it does not empty
+%   \end{itemize}
 
-}
+% }
 

### 2018-07-31 paper/paper.tex
adding discussion section and one par on it

@@
 
-The overarching goal of our study is to identify the ability of simple
-techniques to find bugs in \js\ engines with cross-engine differential
-testing.  We analyzed the impact of two orthogonal dimensions in this
-study: test mining and fuzzing. The first dimension focuses on the
-impact of inputs, mined from the web, in bug finding whereas the
-second dimension focuses on the impact of fuzzing these inputs.
+The overarching goal of our study is to identify the ability of
+cross-engine differential testing to find bugs in \js\ engines.  We
+analyzed the impact of two orthogonal dimensions in this study: test
+mining and fuzzing. The first dimension focuses on the impact of
+inputs, mined from the web, in bug finding whereas the second
+dimension focuses on the impact of fuzzing these inputs.
 
@@
 \Igor{
-  Apos este experimento, foram obtidos \nofuzzAll{} buckets sendo destes \nofuzzHITotal
+  Neste experimento, obtemos \nofuzzAll{} buckets distintos, a proporcao \'e de 
+  \nofuzzHITotal{} HI e apenas \nofuzzLOTotal{} LO. Como descrito anteriormente,
+  n\'os analisamos e discutimos se estas discrepancias reportadas pela ferramenta sao 
+  casos de bugs reais ou casos de falso positivos.
+  Nesta analise, nos observamos que cerca de \Fix{63} buckets sao duplicados, ou seja,
+  estes warnings foram reportados anteriormente nos issues trackers dos engenhos 
+  ou podem ser encontrados casos similares em buckets distintos. Um exemplo claro dos 
+  buckets duplicados podem ser encontrados atraves dos testes da suite Test262,
+  onde esta suite cobre as especificacoes da linguagem em arquivos distintos e que
+  podem conter mensagens de erro diferentes.
 
@@
 
+\section{Discussion}
+
+It is important to highlight that our treatment on both dimensions of
+analysis--test mining and fuzzing--could be improved by selecting more
+test cases or using more advanced fuzzing tools. The main rationale is
+that if these techinques perform well with the objects we used
+(Section~\ref{sec:methodology}) then the approach would perform even
+better with more elaborate objects.
+
+\Fix{...}
+
 \section{Related Work}

### 2018-07-31 paper/paper.tex
pass on results

@@
 
-The overarching goal of our study is to identify the ability of
-cross-engine differential testing to find bugs in \js\ engines.  We
-analyzed the impact of two orthogonal dimensions in this study: test
-mining and fuzzing. The first dimension focuses on the impact of
-inputs, mined from the web, in bug finding whereas the second
-dimension focuses on the impact of fuzzing these inputs.
+The overarching goal of our study is to identify the ability of simple
+techniques to find bugs in \js\ engines with cross-engine differential
+testing.  We analyzed the impact of two orthogonal dimensions in this
+study: test mining and fuzzing. The first dimension focuses on the
+impact of inputs, mined from the web, in bug finding whereas the
+second dimension focuses on the impact of fuzzing these inputs.
 
@@
 
-\section{Discussion}
-
-It is important to highlight that our treatment on both dimensions of
-analysis--test mining and fuzzing--could be improved by selecting more
-test cases or using more advanced fuzzing tools. The main rationale is
-that if these techinques perform well with the objects we used
-(Section~\ref{sec:methodology}) then the approach would perform even
-better with more elaborate objects.
-
-\Fix{...}
-
 \section{Related Work}

### 2018-07-31 paper/paper.tex
pass on false positives

--- 2018-07-31 paper/paper.tex
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
+  \caption{\label{fig:distribution}Distribution of lo and hi warnings
+   in buckets.}
+\end{figure}
+
 The overarching goal of our study is to identify the ability of
@@
 inputs, mined from the web, in bug finding whereas the second
-dimension focuses on the impact of fuzzing these inputs.
+dimension focuses on the impact of fuzzing those inputs.
 
@@
 suspicious, we looked on the bug tracker of the affected engine for
-potential duplicates. If none was reported, we filed a bug report in
-the bug tracker including the test input that manifested the potential
-problem and explaining the reasons we were suspicious. In some cases,
-we used the Mozila lithium tool~\cite{lithium} to minimize the test
-case. For the cases of false positives, we classified the reason for
-the misclassification and moved to the next
-bucket. Table~\ref{tab:summary-of-results} summarizes our results. It
-shows, for each execution mode and category of bucket (\ie{}, hi or
-lo), the total number of files involved, the number of buckets
-reported, and the percentage of those that resulted in a bug
-report. \Fix{elaborate summary} We elaborate those results in the
-following.
+potential duplicates. If none was reported, we filed a bug report
+including the test input that manifested the potential problem and
+explaining the reasons we were suspicious. In some cases, we used the
+Mozila lithium tool~\cite{lithium} to minimize the test case. For the
+cases of false positives, we identified the source of false positive
+and moved to the next bucket. Table~\ref{tab:summary-of-results}
+summarizes our results. It shows, for each execution mode and category
+of bucket (\ie{}, hi or lo), the total number of files involved, the
+number of buckets reported by our infrastructure, the number of those
+that we classified as bug-revealing, and the number of those that we
+filed a bug report. The difference between the last two columns
+indicate the number of duplicates, \ie{}, the cases of
+already-reported bugs. As expected, the hit ratio for the ``hi'' group
+is higher.
 
@@
   \caption{\label{tab:summary-of-results}Summary of results.}
-  \begin{tabular}{ccrrr}
+  \begin{tabular}{ccrrrr}
     \toprule
-    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{2}{c}{buckets} \\
-    \cline{4-5}    
-    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\% positive} \\
+    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
+    \cline{4-6}    
+    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
+    \multicolumn{1}{c}{\# pos. filed} \\
     \midrule
-    \multirow{2}{*}{no-fuzz} & lo & \nofuzzFilesLO{} & \nofuzzLOTotal{} & 34.3\% \\
-    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & 70\% \\
-    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
-    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
-    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
-                             & hi & \Fix{.} & \Fix{.} & \Fix{.} \\    
+    \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
+    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
+    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
+                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
+    \bottomrule     
+  \end{tabular}
+\end{table}
+
+Table~\ref{tab:false-positives} shows the distribution of false
+positives per source. A false positive is a bucket that did not reveal
+a bug. We identified five sources of imprecision. The source ``not yet
+implemented'' indicates that the engine does not implement some part
+of the specification. For example, at the time of writing, Chakra does
+not implement various properties from the \CodeIn{Symbol} object. The
+source ``invalid input'' indicates that the test violated some part of
+the specification. For example, the test indirectly invoked some
+function with unexpected arguments\Fix{provide concrete example}. In
+all cases that we analyzed, that happened because fuzzing produced an
+invalid test input. Note that no false positives of this kind appears
+under the column nofuzz. The source ``timeout/ome'' indicates that the
+test times out (we used a 3s time budget) or runs out of memory. That
+happens because engines implement different set of optimizations. For
+example, only \jsc{} implements tail-call optimization to avoid tail
+recursion. Consequently, for a certain input, it finishes execution
+quickly whereas other engines time out. The source
+``implementation-dependent'' is as defined in
+Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
+source ``future feature'' corresponds to the case where some feature
+will be part of the spec in the future but implementing it is
+facultative.\Fix{provide concrete example}
+
+\begin{table}[t]
+  \centering
+  \caption{\label{tab:false-positives}Distribution of false
+    positives buckets per source.}
+  \begin{tabular}{crrr}
+    \toprule
+              & nofuzz & \radamsa\ & \quickfuzz\ \\
+%    duplicate & 63      & - & - \\
+    not yet implemented & 8 & - & - \\
+    invalid input & 0 & - & - \\
+    timeout/ome & 13 & - & - \\
+    implementation-dependent & 3 & - & - \\
+    future feature & 3 & - & - \\
     \bottomrule     
@@
 files whose output is consistent across all engines analyzed.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
-  \caption{\label{fig:distribution}Distribution of lo and hi warnings
-   in buckets.}
-\end{figure}
 
@@
 
-%%  LocalWords:  bytecodes JScript Ecma
+%%  LocalWords:  bytecodes JScript Ecma ome

### 2018-08-01 paper/paper.tex
refactoring to restablish coherence

@@
 cross-engine differential testing to find bugs in \js\ engines. We
-analyzed the impact of two orthogonal dimensions in this study: test
-mining and fuzzing. The first dimension focuses on the impact of
-inputs, mined from the web, in bug finding whereas the second
-dimension focuses on the impact of fuzzing those inputs.
-
-In the following, we describe the methodology we used in this
-experiment. Recall that our tool outputs a set of buckets, that each
+organized our study in two parts. First, we investigated the stability
+of the engines we analyzed. The intuition is that discovered bugs
+would have low relevance if the engines are unstable. Then, we
+analyzed the impact of using cross-engine differential testing to find
+bugs in \js{} engines.
+
+\subsection{Stability of Engines}
+
+We evaluated stability using different source of test cases. We used
+the official \js{} conformance test suite and test suites developed
+independently by each engine developing team. The Test262 suite is the
+primary suite that we used to assess stability of engines. We ran this
+suite once per day for seven consecutive days. Table~\ref{tab:test262}
+shows results. To sum, we observed that \Fix{...}
+
+\begin{table}[h]
+  \centering
+  \caption{\label{tab:test262}Results of Test262.}
+  \begin{tabular}{crrrrrrr}
+    \toprule
+           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
+    \jsc{} & - & - & - & - & - & - & - \\
+    \veight{} & - & - & - & - & - & - & - \\
+    \chakra{} & - & - & - & - & - & - & - \\
+    \smonkey{} & - & - & - & - & - & - & - \\
+    \bottomrule 
+  \end{tabular}
+\end{table}
+
+We expanded these results by looking for tests from different
+sources. \Fix{elaborate} Table~\ref{tab:cross-testing} shows
+results. To sum, we observed that \Fix{...}
+
+\begin{table}[h]
+  \centering
+  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
+  \begin{tabular}{crrrr}
+    \toprule
+    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
+    Mozilla & - & - & - & -  \\
+    v8 & - & - & - & -  \\
+    WebKit & - & - & - & -  \\
+    Duktape & - & - & - & -  \\
+    JerryScript & - & - & - & -  \\
+    JSI & - & - & - & -  \\
+    Tiny-js & - & - & - & -  \\
+    \bottomrule 
+  \end{tabular}
+\end{table}
+
+%% Our infrastructure reported a total of \nofuzzAll{} buckets, including
+%% \lo{} and \hi{}, that resulted in \nofuzzBugs{} bug reports. Of the
+%% total of \nofuzzAll{} buckets, we found that \nofuzzDuplicates\ were
+%% duplicates and \nofuzzFalsePositives\ were false positives. Most of
+%% the cases of duplicates were related to the Test262 conformance test
+%% suite, which all \js{} should strive to pass but we found that it is
+%% not uncommon for the engines to fail on some of these. For example,
+%% \veight{} \nofuzzFalsePositives
+
+\subsection{Differential Testing}
+
+In the following, we describe the methodology we used to asses the
+impact of cross-engine differential testing in finding bugs on \js{}
+engines. Recall that our tool outputs a set of buckets, that each
 bucket includes a set of warnings, that each warning is related to one
@@
     \midrule
-    \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
-    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
+    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
+    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
     \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
@@
     positives buckets per source.}
-  \begin{tabular}{crrr}
+  \begin{tabular}{crr}
     \toprule
-              & nofuzz & \radamsa\ & \quickfuzz\ \\
-%    duplicate & 63      & - & - \\
-    not yet implemented & 8 & - & - \\
-    invalid input & 0 & - & - \\
-    timeout/ome & 13 & - & - \\
-    implementation-dependent & 3 & - & - \\
-    future feature & 3 & - & - \\
+    & \radamsa\ & \quickfuzz\ \\
+    %% not yet implemented & 8 & - & - \\
+    %% invalid input & 0 & - & - \\
+    %% timeout/ome & 13 & - & - \\
+    %% implementation-dependent & 3 & - & - \\
+    %% future feature & 3 & - & - \\
+    not yet implemented & - & - \\
+    invalid input & - & - \\
+    timeout/ome & - & - \\
+    implementation-dependent & - & - \\
+    future feature & - & - \\
     \bottomrule     
@@
 \end{table}
-
-\subsection{No Fuzzing}
-
-This section reports the results obtained without fuzzing. The goal is
-to observe the impact of the mined test cases in revealing
-differential bugs. In this experiment, we ran all tests (see
-Section~\ref{sec:seeds}) using our infrastructure in no-fuzzing
-mode.
 

### 2018-08-01 paper/paper.tex
pass on results

@@
 %Should I Fuzz my Inputs or Improve my Tests? 
-\title{Differential Testing Runtime Engines--Lessons Learned from the
-  JavaScript Domain}
+\title{Assessing Reliability of JavaScript Engines by Leveraging Diversity}
 
@@
 of the community for the language encourages constant improvements in
-its specification and implementations (see
-Section~\ref{sec:es6-design}). It is natural to expect that such
-improvements will entail sensible changes in runtime
-engines~\cite{kangax}; changes that could lead to errors. Even small
-changes can have a large impact in practice. For example, in October
-2014 a new attribute added to the Array datatype caused a bug that
+its specification and implementations. It is natural to expect that
+such improvements entails sensible changes in runtime engines. Even
+small changes can have a large impact in practice. For example, in
+October 2014 a new attribute added to Array objects caused a bug that
 resulted in MS Outlook web not working under
@@
 because of the speed the specification evolves and the availability of
-various public engines.
+various public engines today~\cite{kangax}.
 
-Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
-approach that has been applied in a variety of contexts to find bugs
-in
-software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. It
+%% WHAT WE DID
+This paper reports the results of a study we conducted to assess
+reliability of existing JS engines by leveraging implementation
+diversity in two orthogonal ways. The first method considered is
+\emph{test transplantation}. This approach evaluates the effects that
+running \js{} test files from a given engine have in detecting bugs in
+other engines. The intuition is that when bugs are found in some
+engine implementation a test case is created and added to the
+regression suite. Those test inputs often check interesting corner
+cases that could reveal bugs in different engine implementations. The
+second method considered is \emph{cross-engine differential
+  testing}. This method fuzzes existing inputs, using existing
+techniques, and then compares the output produced by different engines
+using a differential oracle. One possible cause of output discrepancy
+is a bug. It is worth noting that Differential
+Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
+contexts to find bugs in
+software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
 automates test generation in scenarios where multiple implementations
@@
 have been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security bugs.
-Cross-engine differential testing, in contrast, checks correctness by
-comparing the output produced by \emph{different} engines on a given
-input~\cite{patra2016learning}. Although different implementations of
-JS engines today (see Table~\ref{tab:engines}), this technique is not
-used in practice.
+then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
+contrast, cross-engine differential testing--the technique used in
+this work--checks correctness by comparing the output produced by
+\emph{different engines} on a fuzzed
+input~\cite{patra2016learning}. This approach is not popularized,
+certainly because it is more challenging to fully automate--a number
+of legitimate reasons exist, other than a bug, for a test execution to
+manifest discrepancy (see Table~\ref{tab:false-positives}).
 
-%% WHAT WE DID
-This paper reports the results of a study we conducted to (i) assess
-the reliability of existing JS engines and to (ii) evaluate the
-importance of different factors when using DT. More precisely, we
-analyzed the impact of two orthogonal factors in DT: test mining and
-fuzzing. The first factor--\emph{test mining}--considers the effect
-that \js{} test files mined from the repositories of open-source
-engines have in detecting functional bugs in other engines. The second
-factor--\emph{fuzzing}--considers the impact in bug detection of
-fuzzing these files.
 %% WHAT WE FOUND
@@
 
-\section{Infrastructure}
+\section{Differential Testing Infrastructure}
 \label{sec:design}
@@
 
-Figure~\ref{fig:workflow} illustrates the infrastructure we used in
-this study.  The bug-finding process takes on input JS files from
-regression test suites of various JS engines and generates warnings on
-output. Boxes in the figure denote encapsulation; arrowed lines
-indicate data flow. The cycle icons denote repetition--the leftmost
-icon indicates that each file in the input list will be analyzed in
-separate whereas the rightmost icon shows that a single file will be
-fuzzed multiple times. The bug-finding process works as follows.
-Considering the case where fuzzing is not selected, the oracle checks
-whether or not the output produced for the input file is consistent
-across all engine implementations. In case the test passes in all
+Figure~\ref{fig:workflow} illustrates the infrastructure we used for
+differential testing.  The bug-finding process takes on input JS files
+from regression test suites of various JS engines and generates
+warnings on output. Boxes in the figure denote encapsulation; arrowed
+lines indicate data flow. The cycle icons denote repetition--the
+leftmost icon indicates that each file in the input list will be
+analyzed in separate whereas the rightmost icon shows that a single
+file will be fuzzed multiple times. The bug-finding process works as
+follows.
+
+New inputs are obtained for a given test input using some
+off-the-shelf input fuzzer~\cite{fuzz-testing-history}.\Comment{
+  Several fuzzing methods have been proposed in the past, varying with
+  respect to how new inputs are
+  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
+Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+The oracle checks whether or not the output produced for the fuzzed
+file is consistent across all engines. In case the test passes in all
 engines or fails in all engines (\ie{}, the output is consistent), the
@@
 potentially fault-revealing; hence interesting for human
-inspection. We used the open-source eshost-cli
-project~\cite{eshost-cli} for that. Microsoft uses eshost-cli to check
-functional discrepancies in the Chakra JS engine. Considering the case
-where fuzzing~\cite{fuzz-testing-history} is selected, new inputs are
-obtained from a given input using some off-the-shelf fuzzer. The
-workflow with fuzzing is similar to the workflow without fuzzing. In
-this case, however, the checker can produce multiple warnings for a
-given input. Several fuzzing methods have been proposed in the past,
-varying with respect to how new inputs are
-generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.
-Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+inspection. Note that a number of reasons exist, other than a bug, to
+explain discrepancy (see Table~\ref{tab:false-positives}). We used the
+open-source eshost-cli project~\cite{eshost-cli} for checking output
+discrepancy. Microsoft uses that tool in the Chakra JS engine.
+
+%The checker can produce multiple warnings for a given input.
+
+The infrastructure outputs a list of warnings for human inspection.
+To reduce the number of false alarms, we classified warnings in two
+kinds, reflecting their likelihood to manifest a real bug. Warnings of
+the kind ``\hi{}'' are associated with the cases where the anomaly has
+been detected in the execution of the test code or its harness. The
+rationale is that the test in this group executed without violating
+any internal checks of the API. In constrast, warnings in the
+``\lo{}'' group reflect the cases where the anomaly was observed
+during the execution of functions not related to the test itself. We
+found that different engines often check pre-conditions of those
+functions differently. It can happen, for example, that one engine
+enforces a weaker pre-condition compared to another and that is
+acceptable.  In those cases, our infrastructure would observe a
+discrepancy that is more likely to be associated with an invalid input
+produced by the fuzzer, \ie{}, a bug in the test not the
+code. Although we did find real bugs from ``\lo{}'' warnings, the
+proportion was much lower compared to the ``\hi{}'' warnings. Overall,
+only \Fix{12\%} of the reals bugs we found originated from ``\lo{}''
+warnings.
 
 \Mar{explain what is a bucket (we refer to it later).}
-The infrastructure outputs a list of warnings for human inspection.
-To reduce the number of false alarms, we clustered warnings in two
-groups, reflecting their likelihood to manifest a real bug. Warnings
-in the HI group are associated with the cases where the anomaly has
-been detected in during the execution of test code or its close
-%% the rationale we provide is related to the above; not crashes
-neighborhood. The rationale is that the test in this group executed
-without violating any internal checks of the API. In constrast,
-warnings in the LO group reflect the cases where the anomaly was
-observed during the execution of functions from standard JS libraries\Fix{check}.
-  We found that different engines often check pre-conditions of
-those functions differently. It can happen, for example, that one
-engine enforces a weaker pre-condition compared to another.
-% \Mar{why is that?
-% that should not happen if the spec was fully documented and engines
-% properly implemented those checks. Explain and give example.}
-%% \Igor{these cases happen because the specification describes how a function
-%% should work, however the internal implementation is defined by the
-%% engine developers}\Mar{If you confirm that there is no code in specs
-%%   (see comment above), what would be those abstract
-%%   functions/interfaces that you mentioned to me the other day?}.
-In those cases, our infrastructure would observe a discrepancy that is more likely to
-be associated with a bug in the fuzzed test; not the code. Although
-we did find real bugs from warnings in the LO group, the proportion
-was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
-we found originated from the LO category.
-
-% I think this will make the definition of HI/LO weaker. We can
-% elaborate this later. for example, in the evaluation.
-%% \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
-%% due the capacity of a fuzzer add an infinite repetition statement. We expected that
-%% each test process can running utmost 5 seconds, if exceed this condition we stop 
-%% the process and add a output message of a TIMEOUT error.}
-
-% \Igor{
-%   We defined if a warning is in HI or LO group according to console output.
-%   The error stream in the output shows relevant informations that we can 
-%   process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
-%   outputs based on the stream output came from Chakra engine. 
-  % The error message shows informations related to the assertion code (see at line 2) 
-  % that thows an Error exception. This case was considered as HI groups and after 
-  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
-% }\Mar{igor, first add the real example then draft the discussion}
-
-% \begin{figure}[h!]
-%   \centering
-%   \scriptsize
-%   \lstset{escapeinside={@}{@},
-%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%     numberstyle=\tiny,
-%     morekeywords={assertEq, var, yield, in, function, 
-%     typeof, return, throw, new, Error, if},
-%   }
-% \begin{lstlisting}
-
-% \end{lstlisting}
-% \normalsize
-% \caption{Warning captured as HI priority.}
-% \label{fig:hi-priority}
-% \end{figure}
-
-% bug high console output
-% This a case of a warning reported as HI priority, the Figure~\ref{} shows
-% the output console of V8 engine. We consider this case as a HI group due 
-% the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}
-
-% \begin{figure}[h!]
-%   \centering
-%   \scriptsize
-%   \lstset{escapeinside={@}{@},
-%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%     numberstyle=\tiny,
-%     morekeywords={assertEq, var, yield, in, function, 
-%     typeof, return, throw, new, Error, if},
-%   }
-% \begin{lstlisting}
-% function test() {
-%   var buffer = new ArrayBuffer(64);
-%   var view = new DataView(buffer);
-%   view.setInt8 (0, 0x80);
-%   -return view.getInt8(0) === -0x80;
-
-%   // radamsa fuzzing
-%   +return view.getInt8(-1770523502845470856862803727694) === -0x80;
-%   }
-
-%   if (!test())
-%       throw new Error("Test Failed");
-% \end{lstlisting}
-% \normalsize
-% \caption{Warning captured as HI priority.}
-% \label{fig:hi-priority}
-% \end{figure}
-
-% no-bug low console output
-% \begin{figure}[h!]
-%   \centering
-%   \scriptsize
-%   \lstset{escapeinside={@}{@},
-%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%     numberstyle=\tiny,
-%     morekeywords={assertEq, var, yield, in, function, 
-%     typeof, return, throw, new, Error, if},
-%   }
-%   \begin{lstlisting}
-% \end{lstlisting}
-% \normalsize
-% \caption{Warning captured as HI priority.}
-% \label{fig:lo-priority}
-% \end{figure}
-
-%% \Mar{can we detect dups mining issue trackers?}
-%% \Igor{
-%%   acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
-%%   Tenho umas consideracoes:
-%%   \begin{itemize}
-%%     \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
-%%     se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
-%%     \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
-%%     \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
-%%   \end{itemize}
-%% }\Mar{i think this is not the proper place to
-%%   add this. discuss this with me.}
 
@@
 (as per the second criterion) projects. As we wanted to report bugs,
-we also looked for project with public issue trackers.
-It is worth noting that we used
-GoogleChromeLab's JSVU~\cite{jsvu} to automatically install and configure versions of
+we also looked for project with public issue
+trackers. Table~\ref{tab:engines} lists the engines we analyzed in
+this work. It is worth noting that we used GoogleChromeLab's JSVU
+tool~\cite{jsvu} to automatically install and configure versions of
 different JS engines in our host environment. This is important as we
@@
     \toprule
-    Group & Name & URL & \# Stars \\
+    Team & Name & URL & \# Stars \\
     \midrule
@@
     Google & v8 & \cite{v82018repo} & 9800+ \\
-    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
     Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
 %    Moddable & XS & \cite{xs2018repo} & 140+ \\
-    \midrule
-    \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
-    & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
+    %% \midrule
+    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
+    Mozilla & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
    \bottomrule     
@@
 
-We uses two black-box mutational fuzzers in this
+We used two black-box mutational fuzzers in this
 study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
@@
 simple, and the quality of the test suite. We chose \radamsa\ and
-\quickfuzz\ \Fix{...}
+\quickfuzz\ \Fix{...elaborate...}
 
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
-  \caption{\label{fig:distribution}Distribution of lo and hi warnings
-   in buckets.}
-\end{figure}
-
-The overarching goal of our study is to identify the ability of
-cross-engine differential testing to find bugs in \js\ engines. We
-organized our study in two parts. First, we investigated the stability
-of the engines we analyzed. The intuition is that discovered bugs
-would have low relevance if the engines are unstable. Then, we
-analyzed the impact of using cross-engine differential testing to find
-bugs in \js{} engines.
+Recall that the goal of our study is to assess reliability of
+\js\ engines by leveraging the rich diversity of implementations in
+this domain. We report results in three parts. First, we report on the
+stability of the engines we analyzed using the EcmaScript standard
+conformance test suite Test262~\cite{ecma262-conformance-suite}. The
+intuition is that the bugs we discover would have low relevance if the
+engines are unstable (\ie{}, too fragile). Second, we report results
+obtained with test transplantation. The hypothesis is that test cases
+written for one engine may reveal bugs in different engines. The
+rationale is that the domain of possible inputs is just too large;
+consequently, test suites of a given engine will cover scenarios and
+corner cases uncovered by another engine.  Third, we analyzed the
+impact of using cross-engine differential testing to find bugs in
+\js{} engines. \Fix{hypothesis/rationale}
 
@@
 
-We evaluated stability using different source of test cases. We used
-the official \js{} conformance test suite and test suites developed
-independently by each engine developing team. The Test262 suite is the
-primary suite that we used to assess stability of engines. We ran this
-suite once per day for seven consecutive days. Table~\ref{tab:test262}
-shows results. To sum, we observed that \Fix{...}
+We evaluated stability with Test262~\cite{ecma262-conformance-suite},
+the official \js{} conformance test suite for the ECMA262
+specification. We ran this suite once per day for seven consecutive
+days. Table~\ref{tab:test262} shows the number of failures over this
+period. It is important to note that failures are expected as it takes
+time for engines to adjust to the spec. It is also important to
+highlight that some engines, namely \smonkey{}, \Fix{...}, have
+variants of Test262 as part of their regression test suite\Mar{with
+  fewer tests?}. We used the official version instead. To sum, we
+observed that \Fix{...} \Mar{check connection with kangax report}
 
@@
 \end{table}
+
+\subsection{Test Transplantation}
 
@@
 
-\subsection{Differential Testing}
+\subsection{Cross-Engine Differential Testing}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
+  \caption{\label{fig:distribution}Distribution of lo and hi warnings
+   in buckets.}
+\end{figure}
 
@@
 %\bibliographystyle{IEEEtran}
+\balance
 \bibliographystyle{plain}

### 2018-08-01 paper/paper.tex
fix

--- 2018-07-31 paper/paper.tex
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
-  \caption{\label{fig:distribution}Distribution of lo and hi warnings
-   in buckets.}
-\end{figure}
-
-The overarching goal of our study is to identify the ability of
-cross-engine differential testing to find bugs in \js\ engines.  We
-analyzed the impact of two orthogonal dimensions in this study: test
-mining and fuzzing. The first dimension focuses on the impact of
-inputs, mined from the web, in bug finding whereas the second
-dimension focuses on the impact of fuzzing those inputs.
+The overarching goal of our study is to identify the ability of simple
+techniques to find bugs in \js\ engines with cross-engine differential
+testing.  We analyzed the impact of two orthogonal dimensions in this
+study: test mining and fuzzing. The first dimension focuses on the
+impact of inputs, mined from the web, in bug finding whereas the
+second dimension focuses on the impact of fuzzing these inputs.
 
@@
 suspicious, we looked on the bug tracker of the affected engine for
-potential duplicates. If none was reported, we filed a bug report
-including the test input that manifested the potential problem and
-explaining the reasons we were suspicious. In some cases, we used the
-Mozila lithium tool~\cite{lithium} to minimize the test case. For the
-cases of false positives, we identified the source of false positive
-and moved to the next bucket. Table~\ref{tab:summary-of-results}
-summarizes our results. It shows, for each execution mode and category
-of bucket (\ie{}, hi or lo), the total number of files involved, the
-number of buckets reported by our infrastructure, the number of those
-that we classified as bug-revealing, and the number of those that we
-filed a bug report. The difference between the last two columns
-indicate the number of duplicates, \ie{}, the cases of
-already-reported bugs. As expected, the hit ratio for the ``hi'' group
-is higher.
+potential duplicates. If none was reported, we filed a bug report in
+the bug tracker including the test input that manifested the potential
+problem and explaining the reasons we were suspicious. In some cases,
+we used the Mozila lithium tool~\cite{lithium} to minimize the test
+case. For the cases of false positives, we classified the reason for
+the misclassification and moved to the next
+bucket. Table~\ref{tab:summary-of-results} summarizes our results. It
+shows, for each execution mode and category of bucket (\ie{}, hi or
+lo), the total number of files involved, the number of buckets
+reported, and the percentage of those that resulted in a bug
+report. \Fix{elaborate summary} We elaborate those results in the
+following.
 
@@
   \caption{\label{tab:summary-of-results}Summary of results.}
-  \begin{tabular}{ccrrrr}
+  \begin{tabular}{ccrrr}
     \toprule
-    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
-    \cline{4-6}    
-    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
-    \multicolumn{1}{c}{\# pos. filed} \\
+    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{2}{c}{buckets} \\
+    \cline{4-5}    
+    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\% positive} \\
     \midrule
-    \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
-    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
-    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. A false positive is a bucket that did not reveal
-a bug. We identified five sources of imprecision. The source ``not yet
-implemented'' indicates that the engine does not implement some part
-of the specification. For example, at the time of writing, Chakra does
-not implement various properties from the \CodeIn{Symbol} object. The
-source ``invalid input'' indicates that the test violated some part of
-the specification. For example, the test indirectly invoked some
-function with unexpected arguments\Fix{provide concrete example}. In
-all cases that we analyzed, that happened because fuzzing produced an
-invalid test input. Note that no false positives of this kind appears
-under the column nofuzz. The source ``timeout/ome'' indicates that the
-test times out (we used a 3s time budget) or runs out of memory. That
-happens because engines implement different set of optimizations. For
-example, only \jsc{} implements tail-call optimization to avoid tail
-recursion. Consequently, for a certain input, it finishes execution
-quickly whereas other engines time out. The source
-``implementation-dependent'' is as defined in
-Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
-source ``future feature'' corresponds to the case where some feature
-will be part of the spec in the future but implementing it is
-facultative.\Fix{provide concrete example}
-
-\begin{table}[t]
-  \centering
-  \caption{\label{tab:false-positives}Distribution of false
-    positives buckets per source.}
-  \begin{tabular}{crrr}
-    \toprule
-              & nofuzz & \radamsa\ & \quickfuzz\ \\
-%    duplicate & 63      & - & - \\
-    not yet implemented & 8 & - & - \\
-    invalid input & 0 & - & - \\
-    timeout/ome & 13 & - & - \\
-    implementation-dependent & 3 & - & - \\
-    future feature & 3 & - & - \\
+    \multirow{2}{*}{no-fuzz} & lo & \nofuzzFilesLO{} & \nofuzzLOTotal{} & 34.3\% \\
+    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & 70\% \\
+    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
+    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
+    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
+                             & hi & \Fix{.} & \Fix{.} & \Fix{.} \\    
     \bottomrule     
@@
   onde esta suite cobre as especificacoes da linguagem em arquivos distintos e que
-  podem conter mensagens de erro diferentes.
+  podem conter mensagens de erro diferentes para um mesmo warning.
+
+  Nos separamos os buckets considerados falso positivos de acordo com
 
@@
 files whose output is consistent across all engines analyzed.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
+  \caption{\label{fig:distribution}Distribution of lo and hi warnings
+   in buckets.}
+\end{figure}
 
@@
 
-%%  LocalWords:  bytecodes JScript Ecma ome
+%%  LocalWords:  bytecodes JScript Ecma

### 2018-08-01 paper/paper.tex
fix table I
pass on results

@@
 %Should I Fuzz my Inputs or Improve my Tests? 
-\title{Assessing Reliability of JavaScript Engines by Leveraging Diversity}
+\title{Assessing the Reliability of JavaScript Engines by Leveraging Diversity}
 
@@
     \midrule
-    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{-} \\
-    Google & v8 & \cite{v82018repo} & 9800+ \\
+    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
+    Google & \veight{} & \cite{v82018repo} & 9800+ \\
 %    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
-    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
+    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
 %    Moddable & XS & \cite{xs2018repo} & 140+ \\
@@
     %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
-    Mozilla & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{-} \\
+    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
    \bottomrule     
@@
 of the tests we found depend on external libraries, which not all
-engines we use (see Section~\ref{sec:methodology:engines}) support. We
-decided to discard those. For example, many tests we found required a
-Node.js runtime~\cite{node} for execution. The main source of test
-cases is the offical TC-39~\cite{tc39-github} conformance test suite
-for the ECMA262 specification~\cite{ecmas262-spec}. This test suite
-contains 87\% of all the tests we used. Furthermore, we
-considered test suites of three of the four engines mentioned in
-Section~\ref{sec:methodology:engines} and four other engines.
-Table~\ref{tab:test-suites} shows the JS sources we considered for
-each of the selected projects. Overall, we found a total of
-\totfiles{} JS files. It is worth noting that some test suites use
-distinct frameworks for testing and require external libraries to run
-the tests.  For these projects, we needed to make small
-changes in the testing infrastructure to be able to run the tests
-uniformly across all engines. More precisely, we needed to mock
-some functions, related to the test harness, which are only available to
-certain engines.
+engines we use support. We decided to discard those. For example, many
+tests we found required a Node.js runtime~\cite{node} for
+execution. The main source of test cases is the offical
+TC-39~\cite{tc39-github} conformance test suite for the ECMA262
+specification~\cite{ecmas262-spec}. This test suite contains 87\% of
+all the tests we used. We also considered test suites of three of the
+four engines mentioned in Section~\ref{sec:methodology:engines} and
+four other engines. We did not consider tests from the \chakra{}
+repository because of their intensive use of Chakra-specific
+objects. Table~\ref{tab:test-suites} shows the breakdown of tests we
+considered. Overall, we found a total of \totfiles{} JS files.
+
+It is also worth mentioning that some engines use custom shell,
+including a harness with custom assertions, to run tests.  For these,
+we needed to make small changes in the testing infrastructure to be
+able to run the tests uniformly across all engines. More precisely, we
+needed to mock non-portable harness functions, which are only
+available to certain engines.
 
@@
     Mozilla & \cite{mozilla} & 2,633 \\
-    V8 & \cite{v8} & 74 \\
-    WebKit & \cite{webkit} & 1,031 \\
+    \veight{} & \cite{v8} & 74 \\
+    \jsc{} & \cite{webkit} & 1,031 \\
     \midrule    
@@
 the official \js{} conformance test suite for the ECMA262
-specification. We ran this suite once per day for seven consecutive
+specification. We ran this suite once a day for seven consecutive
 days. Table~\ref{tab:test262} shows the number of failures over this
@@
 time for engines to adjust to the spec. It is also important to
-highlight that some engines, namely \smonkey{}, \Fix{...}, have
-variants of Test262 as part of their regression test suite\Mar{with
-  fewer tests?}. We used the official version instead. To sum, we
-observed that \Fix{...} \Mar{check connection with kangax report}
+highlight that all engines we analyzed, but \chakra{}, use some
+variant of the Test262 suite as part of their regression
+process\Mar{with fewer tests?}. We used the official version
+instead\Mar{, which updates tests regularly?}. To sum, we observed
+that \Fix{...} \Mar{justify regressions using the kangax report}
 
@@
     test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
+    \midrule
+    \jsc{} & - & - & - & -  \\
+    \veight{} & - & - & - & -  \\
+%    \chakra{} & - & - & - & -  \\
     Mozilla & - & - & - & -  \\
-    v8 & - & - & - & -  \\
-    WebKit & - & - & - & -  \\
     Duktape & - & - & - & -  \\
@@
 %% \veight{} \nofuzzFalsePositives
+
+\begin{table*}[h!]
+  \vspace{-3ex}
+%  \scriptsize
+  \centering
+  \caption{List of bug reports issued as result of test transplantation.}
+  \label{tab:bugs}
+  \begin{tabular}{cccccccc}
+    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
+    \midrule    
+    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
+   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
+   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
+   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
+                       &  &                       &
+    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
+   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
+   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
+   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
+   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
+   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
+  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
+   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
+   \bottomrule
+  \end{tabular}
+\end{table*}
 
@@
   \label{tab:bugs}
-  \begin{tabular}{cccccccc}
+  \begin{tabular}{ccccccccc}
     \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
+    Issue\#    & Date & Fuzz & Engine  & Status  &
+    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
     \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & LO & WebKit \\ 
-    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\
-    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & WebKit    \\
-    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScript      \\
-    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & Mozilla      \\
-    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScript   \\
-    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & Mozilla
-    \\
-    \midrule
-    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{Mozilla}\\
-                        &  &                       &
-    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
-    \midrule    
-    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScript\\
-    \midrule    
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
+    & \Fix{x} & LO & WebKit \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
+    & \Fix{x} & HI & WebKit \\
+    3  & 4/14 & radamsa & JavascriptCore  & New &
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
+    } & \Fix{x}  & HI & WebKit    \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
+    & \Fix{x} & HI & JerryScript   \\
+    9  & 4/29 & radamsa & JavascriptCore  & New  &
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
+    } & \Fix{x}  & HI  & JerryScript\\
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  &
+    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
+    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                         &                        &        &
     JavascriptCore & New &
-    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
-    \\
-    \midrule    
-    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
-    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
-    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScript \\
-    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & V8\\
-    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & WebKit\\
-    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & Mozilla\\
-    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & Webkit\\
-    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
-    19 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
-    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
-    22 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & HI & JerryScript\\
-    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
-    23 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
-    24 & 7/18 & \crossmark & JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & HI & JerryScript\\
-    25 & 7/27 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5548}{\#5548} & HI & Test262\\
-    26 & 7/27 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5549}{\#5549} & HI & Test262\\
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
+    & \Fix{x} &  & \\
+    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
+    & \Fix{x} & LO & Mozilla \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
+    & \Fix{x} & HI & JerryScript \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
+    & \Fix{x} & HI & V8\\
+    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
+    & \Fix{x} & HI & Webkit\\
+    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
+    & \Fix{x} & HI & JerryScript\\
+    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
+    & \Fix{x} & HI & JerryScript\\
+    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
+    & \Fix{x} & HI & JerryScript\\
    \bottomrule

### 2018-08-01 paper/paper.tex
another pass on results

@@
   \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Infrastructure.}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
 \end{figure}
@@
     \midrule
-     &  & 38,305 \\
+     &  & \totalTestFiles{} \\
    \bottomrule     
@@
 Recall that the goal of our study is to assess reliability of
-\js\ engines by leveraging the rich diversity of implementations in
-this domain. We report results in three parts. First, we report on the
-stability of the engines we analyzed using the EcmaScript standard
-conformance test suite Test262~\cite{ecma262-conformance-suite}. The
-intuition is that the bugs we discover would have low relevance if the
-engines are unstable (\ie{}, too fragile). Second, we report results
-obtained with test transplantation. The hypothesis is that test cases
-written for one engine may reveal bugs in different engines. The
-rationale is that the domain of possible inputs is just too large;
-consequently, test suites of a given engine will cover scenarios and
-corner cases uncovered by another engine.  Third, we analyzed the
-impact of using cross-engine differential testing to find bugs in
-\js{} engines. \Fix{hypothesis/rationale}
+\js\ engines by leveraging implementation diversity, which is
+specially rich in this domain. We report results in three
+parts. First, we report on the stability of the engines we analyzed
+using the Test262 standard conformance test suite for
+EcmaScript~\cite{ecma262-conformance-suite}. The intuition is that the
+bugs we discover throughout this study would have low relevance if the
+engines are too fragile. Second, we report results obtained with test
+transplantation. The hypothesis is that test cases written for one
+engine may reveal bugs in different engines. The rationale is that the
+domain of possible inputs is too large; consequently, we expect that
+test suites of a given engine cover scenarios and corner cases
+uncovered by another engine. Third, we analyzed the impact of using
+cross-engine differential testing to find bugs. The hypothesis is that
+even black-box fuzzers can expose important bugs.
 
 \subsection{Stability of Engines}
+\label{sec:stability}
 
@@
   \centering
-  \caption{\label{tab:test262}Results of Test262.}
+  \caption{\label{tab:test262}Number of failures in Test262 over
+    a 7-day period.}
   \begin{tabular}{crrrrrrr}
@@
 \subsection{Test Transplantation}
+\label{sec:transplantation}
 
-We expanded these results by looking for tests from different
-sources. \Fix{elaborate} Table~\ref{tab:cross-testing} shows
-results. To sum, we observed that \Fix{...}
+This section reports results obtained with test
+transplantation. Table~\ref{tab:cross-testing} shows the number of
+failures that each engine produces on a different test suite. To sum,
+we observed that \Fix{...}
 
@@
   \centering
-  \caption{\label{tab:cross-testing}Crossed execution of test suites..}
+  \caption{\label{tab:cross-testing}Number of failures observed exchanging
+  test suites.}
   \begin{tabular}{crrrr}
@@
 
-\begin{table*}[h!]
+We inspected each of those failures in detail according to the
+following methodology. \Fix{..elaborate..}
+Figure~\ref{tab:test-transplantation-bugs} shows
+results. \Fix{...elaborate...}
+
+\begin{table*}[t]
   \vspace{-3ex}
@@
   \caption{List of bug reports issued as result of test transplantation.}
-  \label{tab:bugs}
+  \label{tab:test-transplantation-bugs}
   \begin{tabular}{cccccccc}
@@
 
-In the following, we describe the methodology we used to asses the
+This section reports the results obtained by fuzzing inputs, running
+those inputs on different engines, and checking the outcomes with a
+differential oracle (see Figure~\ref{fig:workflow}).
+
+\subsubsection{Methodology}
+In the following, we describe the methodology we used to assess the
 impact of cross-engine differential testing in finding bugs on \js{}
-engines. Recall that our tool outputs a set of buckets, that each
-bucket includes a set of warnings, that each warning is related to one
-file, and that a bucket is of ``lo'' or ``hi'' importance, according
-to the heuristic we defined. Figure~\ref{fig:distribution} shows the
-distribution of number of warnings per bucket. We use the the label
-``nofuzz'' to refer to the experiment that analyzed the impact of test
-mining as we do not use fuzzing in that experiment and use the names
-of the fuzzing tools to refer to the results obtained with those
-tools. We inspected each and every bucket for bugs, but observe that
-the number of files per bucket is very high in some cases (\eg{},
-nofuzz [hi]). As such, it would be impractical to manually inspect all
-the files in the bucket. For that reason, we only inspected one file
-per bucket. For the cases we found the warning suspicious, we analyzed
-the parts of the documentation related to the problem and, if still
-suspicious, we looked on the bug tracker of the affected engine for
-potential duplicates. If none was reported, we filed a bug report
-including the test input that manifested the potential problem and
-explaining the reasons we were suspicious. In some cases, we used the
-Mozila lithium tool~\cite{lithium} to minimize the test case. For the
-cases of false positives, we identified the source of false positive
-and moved to the next bucket. Table~\ref{tab:summary-of-results}
-summarizes our results. It shows, for each execution mode and category
-of bucket (\ie{}, hi or lo), the total number of files involved, the
-number of buckets reported by our infrastructure, the number of those
-that we classified as bug-revealing, and the number of those that we
-filed a bug report. The difference between the last two columns
-indicate the number of duplicates, \ie{}, the cases of
-already-reported bugs. As expected, the hit ratio for the ``hi'' group
-is higher.
+engines. To avoid experimental noise, we did \emph{not} fuzz test
+files that failed in some engine as per results reported in
+Sections~\ref{sec:stability} and~\ref{sec:transplantation}. The
+intuition is that we want to make sure that the bug was not
+coincidental, \ie{}, the scenario where fuzzing produces an
+fault-revealing input based on a test that was already
+fault-revealing. That decision ensures that we can establish
+cause-effect relationship between fuzzing and the observation of
+discrepancy. For that reason, we discarded a total of \Fix{???} test
+files from a total of \totalTestFiles{}.Recall that our tool outputs a
+set of buckets, that each bucket includes a set of warnings, that each
+warning is related to one file, and that a bucket is of ``lo'' or
+``hi'' importance, according to the heuristic we
+defined. Figure~\ref{fig:distribution} shows the distribution of
+number of warnings reported per bucket. We use the names of the
+fuzzing tools to refer to the results obtained with those tools. We
+inspected each and every bucket for bugs, but observe that the number
+of files per bucket is very high in some cases. As such, it would be
+impractical to manually inspect all the files in the bucket. For that
+reason, we only inspected one file per bucket. For the cases we found
+the warning suspicious, we analyzed the parts of the documentation
+related to the problem and, if still suspicious, we looked on the bug
+tracker of the affected engine for potential duplicates. If none was
+reported, we filed a bug report including the test input that
+manifested the potential problem and explaining the reasons we were
+suspicious. In some cases, we used the Mozila lithium
+tool~\cite{lithium} to minimize the test case. For the cases of false
+positives, we identified the source of false positive and moved to the
+next bucket.
 
-\begin{table}[t]
+\subsubsection{Results}
+Table~\ref{tab:summary-of-results} summarizes our results. It shows,
+for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
+of files involved, the number of buckets reported by our
+infrastructure, the number of those that we classified as
+bug-revealing (positive), and the number of those that we filed a bug
+report. The difference between the last two columns corresponds to the
+number of duplicates, \ie{}, the cases of bugs already reported in the
+corresponding issue tracker. As expected, the hit ratio for the ``hi''
+group is higher, indicating that chances of filing a bug report for a
+``hi'' warning is higher.
+
+\begin{table}[h]
   \centering
@@
 Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. A false positive is a bucket that did not reveal
-a bug. We identified five sources of imprecision. The source ``not yet
-implemented'' indicates that the engine does not implement some part
-of the specification. For example, at the time of writing, Chakra does
-not implement various properties from the \CodeIn{Symbol} object. The
-source ``invalid input'' indicates that the test violated some part of
-the specification. For example, the test indirectly invoked some
-function with unexpected arguments\Fix{provide concrete example}. In
-all cases that we analyzed, that happened because fuzzing produced an
-invalid test input. Note that no false positives of this kind appears
-under the column nofuzz. The source ``timeout/ome'' indicates that the
-test times out (we used a 3s time budget) or runs out of memory. That
-happens because engines implement different set of optimizations. For
-example, only \jsc{} implements tail-call optimization to avoid tail
-recursion. Consequently, for a certain input, it finishes execution
-quickly whereas other engines time out. The source
+positives per source. A false positive is a bucket that did not lend
+itself in a bug report. We identified five sources of imprecision. The
+source ``not yet implemented'' indicates that the engine does not
+implement some part of the specification. For example, at the time of
+writing, Chakra does not implement various properties from the
+\CodeIn{Symbol} object. The source ``invalid input'' indicates that
+the test violated some part of the specification. For example, the
+test indirectly invoked some function with unexpected
+arguments\Fix{provide concrete example}. In all cases that we
+analyzed, that happened because fuzzing produced an invalid test
+input. The source ``timeout/ome''\footnote{ome is for out of memory
+  error.} indicates that the test times out (we used a 3s time budget)
+or runs out of memory. That happens because engines implement
+different optimizations. For example, we found that only \jsc{}
+implements tail-call optimization to avoid tail
+recursion. Consequently, for a certain input, \jsc{} finishes
+execution quickly whereas other engines time out. The source
 ``implementation-dependent'' is as defined in
 Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
-source ``future feature'' corresponds to the case where some feature
-will be part of the spec in the future but implementing it is
-facultative.\Fix{provide concrete example}
+source ``future feature'' corresponds to the case where a feature will
+be part of the spec but some engines already implemented it, making a
+test that uses the feature to pass only in those engines.
 
@@
 \end{table}
-
-\Igor{
-  Neste experimento, obtemos \nofuzzAll{} buckets distintos, a proporcao \'e de 
-  \nofuzzHITotal{} HI e apenas \nofuzzLOTotal{} LO. Como descrito anteriormente,
-  n\'os analisamos e discutimos se estas discrepancias reportadas pela ferramenta sao 
-  casos de bugs reais ou casos de falso positivos.
-  Nesta analise, nos observamos que cerca de \Fix{63} buckets sao duplicados, ou seja,
-  estes warnings foram reportados anteriormente nos issues trackers dos engenhos 
-  ou podem ser encontrados casos similares em buckets distintos. Um exemplo claro dos 
-  buckets duplicados podem ser encontrados atraves dos testes da suite Test262,
-  onde esta suite cobre as especificacoes da linguagem em arquivos distintos e que
-  podem conter mensagens de erro diferentes para um mesmo warning.
-
-  Nos separamos os buckets considerados falso positivos de acordo com
-
-  % Ao total, foram obtidos \nofuzzAll{} warnings, sendo estes \nofuzzHighTotal{}
-  % pertencentes aos buckets com prioridade HI e \nofuzzLowTotal{} da prioridade LO. 
-  % Durante 3 meses, n\'os analisamos com rigor cada log gerado, sempre checando as 
-  % especificacoes do EcmaScript, a fim de encontrar bugs reais nos engenhos
-  % javascript que violem condições da especificacao ou apresentem discrepancias
-  % entre as saidas de cada engenhos.
-  % Nosso estudo revelou que dos \nofuzzHighTotal{} buckets do grupo HI, 
-  % \nofuzzHighReport{} foram reportados enquanto que no grupo LO, apenas 
-  % \nofuzzLowReport{} possuiam bugs reais (ratio HI $>$ LO).
-}
-  % A diversidade de suites de testes influenciou na busca de bugs nao descobertos
-  % pelo proprio projeto do engenhos. Por exemplo, cerca de \nofuzzTC{} buckets 
-  % foram encontrados usando a suite do TC-39, alem de \nofuzzMozilla{} warnings 
-  % foram obtidos do repositorio da Mozilla, \nofuzzJerry{} na suite do JerryScript, 
-  % \nofuzzWebKit{} sao do WebKit e \nofuzzGoogle{} para o V8 e o Duktape, 
-  % os arquivos dos repositorios do TinyJS e JSI nao mostraram discrepancias entre as
-  % engines.
-
-  % A importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
-  % quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
-  % devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
-
-  % Nosso estudo revelou que dos \tableBugsNum{} bugs reportados pelo nosso time, 
-  % apenas \Fix{10} nao foram fuzzados \Fix{43.4\%},
-  % Apesar do engenhos do V8 e SpiderMonkey
-  % serem os mais robustos em relacao aos demais, tambem 
-  % foram encontrados warnings nestes engenhos, porem
-
-%% \Fix{nao entendi muito sobre essa subsection... 
-%% seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
-%% \Igor{
-%%   Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
-%%   o sistema robusto nao significa que esta livre de bugs, ao contrario,
-%%   estamos testando-o com simples entradas a partir de testes de regressao 
-%%   de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
-%%   para novos testcases. Partindo disso, realizar fuzzer em arquivos 
-%%   existentes em projetos open-sources eh uma maneira de
-%%   aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
-%%   uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.
-
-\subsection{Fuzzing}
-
-This section reports the results obtained by fuzzing inputs with
-existing tools. It is important to mention that, to avoid experimental
-noise, we did not consider the \nofuzzTotalFiles{} files (\Fix{2.8\%} of the
-total) reported in the previous experiment, \ie{}, we only fuzzed test
-files whose output is consistent across all engines analyzed.
 

### 2018-08-01 paper/paper.tex
minor fixed in table

@@
   \centering
-  \caption{List of bug reports issued by our team since April,
-    2018. The analysis of warnings was not uninterrupted.}
+  \caption{List of bug reports issued as result of cross-engine
+    differential testing.}
   \label{tab:bugs}
@@
     } & \Fix{x}  & HI & WebKit    \\
-    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
+    4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
     & \Fix{x} & HI & JerryScript   \\
-    9  & 4/29 & radamsa & JavascriptCore  & New  &
+    5  & 4/29 & radamsa & JavascriptCore  & New  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
     } & \Fix{x}  & HI  & JerryScript\\
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  &
+    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
     \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
@@
     & \Fix{x} &  & \\
-    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
+    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
     & \Fix{x} & LO & Mozilla \\
-    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
+    8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
     & \Fix{x} & HI & JerryScript \\
-    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
+    9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
     & \Fix{x} & HI & V8\\
-    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
+    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
     & \Fix{x} & HI & Webkit\\
-    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
+    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
     & \Fix{x} & HI & JerryScript\\
-    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
+    12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
     & \Fix{x} & HI & JerryScript\\
-    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
+    13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}

### 2018-08-01 paper/paper.tex
added V8 results

--- 2018-08-01 paper/paper.tex
@@
 %Should I Fuzz my Inputs or Improve my Tests? 
-\title{Assessing the Reliability of JavaScript Engines by Leveraging Diversity}
+\title{Assessing Reliability of JavaScript Engines by Leveraging Diversity}
 
@@
     \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
-    Google & \veight{} & \cite{v82018repo} & 9800+ \\
+    Apple & JavaScriptCore (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
+    Google & v8 & \cite{v82018repo} & 9800+ \\
 %    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
+    Microsoft & Chakra & \cite{chakra2018repo} & 7200+ \\
 %    Moddable & XS & \cite{xs2018repo} & 140+ \\
@@
     %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
+    Mozilla & SpiderMonkey & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
    \bottomrule     
@@
 of the tests we found depend on external libraries, which not all
-engines we use support. We decided to discard those. For example, many
-tests we found required a Node.js runtime~\cite{node} for
-execution. The main source of test cases is the offical
-TC-39~\cite{tc39-github} conformance test suite for the ECMA262
-specification~\cite{ecmas262-spec}. This test suite contains 87\% of
-all the tests we used. We also considered test suites of three of the
-four engines mentioned in Section~\ref{sec:methodology:engines} and
-four other engines. We did not consider tests from the \chakra{}
-repository because of their intensive use of Chakra-specific
-objects. Table~\ref{tab:test-suites} shows the breakdown of tests we
-considered. Overall, we found a total of \totfiles{} JS files.
-
-It is also worth mentioning that some engines use custom shell,
-including a harness with custom assertions, to run tests.  For these,
-we needed to make small changes in the testing infrastructure to be
-able to run the tests uniformly across all engines. More precisely, we
-needed to mock non-portable harness functions, which are only
-available to certain engines.
+engines we use (see Section~\ref{sec:methodology:engines}) support. We
+decided to discard those. For example, many tests we found required a
+Node.js runtime~\cite{node} for execution. The main source of test
+cases is the offical TC-39~\cite{tc39-github} conformance test suite
+for the ECMA262 specification~\cite{ecmas262-spec}. This test suite
+contains 87\% of all the tests we used. Furthermore, we
+considered test suites of three of the four engines mentioned in
+Section~\ref{sec:methodology:engines} and four other engines.
+Table~\ref{tab:test-suites} shows the JS sources we considered for
+each of the selected projects. Overall, we found a total of
+\totfiles{} JS files. It is worth noting that some test suites use
+distinct frameworks for testing and require external libraries to run
+the tests.  For these projects, we needed to make small
+changes in the testing infrastructure to be able to run the tests
+uniformly across all engines. More precisely, we needed to mock
+some functions, related to the test harness, which are only available to
+certain engines.
 
@@
     Mozilla & \cite{mozilla} & 2,633 \\
-    \veight{} & \cite{v8} & 74 \\
-    \jsc{} & \cite{webkit} & 1,031 \\
+    V8 & \cite{v8} & 74 \\
+    WebKit & \cite{webkit} & 1,031 \\
     \midrule    
@@
 the official \js{} conformance test suite for the ECMA262
-specification. We ran this suite once a day for seven consecutive
+specification. We ran this suite once per day for seven consecutive
 days. Table~\ref{tab:test262} shows the number of failures over this
@@
 time for engines to adjust to the spec. It is also important to
-highlight that all engines we analyzed, but \chakra{}, use some
-variant of the Test262 suite as part of their regression
-process\Mar{with fewer tests?}. We used the official version
-instead\Mar{, which updates tests regularly?}. To sum, we observed
-that \Fix{...} \Mar{justify regressions using the kangax report}
+highlight that some engines, namely \smonkey{}, \Fix{...}, have
+variants of Test262 as part of their regression test suite\Mar{with
+  fewer tests?}. We used the official version instead. To sum, we
+observed that \Fix{...} \Mar{check connection with kangax report}
 
@@
     test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
-    \midrule
-    \jsc{} & - & - & - & -  \\
-    \veight{} & - & - & - & -  \\
-%    \chakra{} & - & - & - & -  \\
-    Mozilla & - & - & - & -  \\
-    Duktape & - & - & - & -  \\
-    JerryScript & - & - & - & -  \\
-    JSI & - & - & - & -  \\
-    Tiny-js & - & - & - & -  \\
+    Mozilla & - & 333 & - & -  \\
+    v8 & - & - & - & -  \\
+    WebKit & - & 11 & - & -  \\
+    Duktape & - & 80 & - & -  \\
+    JerryScript & - & 92 & - & -  \\
+    JSI & - & 14 & - & -  \\
+    Tiny-js & - & 11 & - & -  \\
     \bottomrule 
@@
 %% \veight{} \nofuzzFalsePositives
-
-\begin{table*}[h!]
-  \vspace{-3ex}
-%  \scriptsize
-  \centering
-  \caption{List of bug reports issued as result of test transplantation.}
-  \label{tab:bugs}
-  \begin{tabular}{cccccccc}
-    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
-    \midrule    
-    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
-   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
-   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
-   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
-                       &  &                       &
-    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
-   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
-   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
-   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
-   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
-   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
-  10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
-   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
-   \bottomrule
-  \end{tabular}
-\end{table*}
 
@@
   \label{tab:bugs}
-  \begin{tabular}{ccccccccc}
+  \begin{tabular}{cccccccc}
     \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  &
-    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
+    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
     \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
-    & \Fix{x} & LO & WebKit \\ 
-    2  & 4/12 & radamsa & Chakra   & Rejected  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
-    & \Fix{x} & HI & WebKit \\
-    3  & 4/14 & radamsa & JavascriptCore  & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
-    } & \Fix{x}  & HI & WebKit    \\
-    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
-    & \Fix{x} & HI & JerryScript   \\
-    9  & 4/29 & radamsa & JavascriptCore  & New  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & \Fix{x}  & HI  & JerryScript\\
-    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  &
-    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
-    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
+    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & LO & WebKit \\ 
+    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & WebKit \\
+    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & WebKit    \\
+    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScript      \\
+    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & Mozilla      \\
+    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScript   \\
+    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
+    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & Mozilla
+    \\
+    \midrule
+    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{Mozilla}\\
+                        &  &                       &
+    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
+    \midrule    
+    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScript\\
+    \midrule    
+    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\
                         &                        &        &
     JavascriptCore & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
-    & \Fix{x} &  & \\
-    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
-    & \Fix{x} & LO & Mozilla \\
-    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
-    & \Fix{x} & HI & JerryScript \\
-    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
-    & \Fix{x} & HI & V8\\
-    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
-    & \Fix{x} & HI & Webkit\\
-    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
-    & \Fix{x} & HI & JerryScript\\
-    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
-    & \Fix{x} & HI & JerryScript\\
-    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
-    & \Fix{x} & HI & JerryScript\\
+    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
+    \\
+    \midrule    
+    11 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & Mozilla \\
+    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & Mozilla \\
+    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScript \\
+    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & V8\\
+    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & WebKit\\
+    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & Mozilla\\
+    17 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & Webkit\\
+    18 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScript\\
+    19 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & WebKit\\
+    20 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520} & HI & JerryScript\\
+    22 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442} & HI & JerryScript\\
+    21 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443} & HI & JerryScript\\
+    23 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478} & HI & Mozilla\\
+    24 & 7/18 & \crossmark & JavascriptCore & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & HI & JerryScript\\
+    25 & 7/27 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5548}{\#5548} & HI & Test262\\
+    26 & 7/27 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5549}{\#5549} & HI & Test262\\
    \bottomrule

### 2018-08-02 paper/paper.tex
cosmetic
pass on abstract and intro

--- 2018-08-01 paper/paper.tex
@@
 %Should I Fuzz my Inputs or Improve my Tests? 
-\title{Assessing the Reliability of JavaScript Engines by Leveraging Diversity}
+\title{Leveraging Diversity to Find Bugs\\ in JavaScript Engines}
 
@@
 \begin{abstract}
-This paper assesses the impact of Differential Testing (DT) to find
-functional bugs in JS engines. This is an important problem given the
-importance of JS today. DT has shown successful in finding bugs in
-compilers and runtimes, but has not been thoroughly explored in this
-important domain. Our study \Fix{...}
+JavaScript is a very popular programming language today. Checking
+reliability of JavaScript engines is therefore an important
+problem. This paper reports on a study to assess reliability of
+JavaScript engines by leveraging the rich diversity of open-source
+implementations. We explored two methods for that---test
+transplantation and cross-engine differential testing. Test
+transplatation evaluates the effects of running test suites of a given
+engine in another engine. Cross-engine differential testing evaluates
+the effects of fuzzing existing inputs and then comparing the output
+produced by different engines with a differential oracle. Our results
+indicate that \Fix{...}
 \end{abstract}
@@
 \begin{IEEEkeywords}
-...
+JavaScript; Diversity; Software Testing
 \end{IEEEkeywords}
@@
 resulted in MS Outlook web not working under
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
-sum, finding bugs in JS engines is an important problem specially
-because of the speed the specification evolves and the availability of
-various public engines today~\cite{kangax}.
+Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
+bugs in JS engines is therefore an important problem. It is also
+challenging because of the speed the specification
+evolves~\cite{ecmas262-spec-repo} and the fact that the behavior of
+various language elements is undefined~\cite{so-undefined-behavior}
+(\ie{} left for the implementation to define).
 
@@
 diversity in two orthogonal ways. The first method considered is
-\emph{test transplantation}. This approach evaluates the effects that
+\emph{test transplantation}. This method evaluates the effects that
 running \js{} test files from a given engine have in detecting bugs in
-other engines. The intuition is that when bugs are found in some
-engine implementation a test case is created and added to the
-regression suite. Those test inputs often check interesting corner
-cases that could reveal bugs in different engine implementations. The
-second method considered is \emph{cross-engine differential
-  testing}. This method fuzzes existing inputs, using existing
-techniques, and then compares the output produced by different engines
-using a differential oracle. One possible cause of output discrepancy
-is a bug. It is worth noting that Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find bugs in
-software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
+other engines. The intuition is that when a bug is found in some
+engine a test case is created and added to the regression suite. Those
+test inputs often check interesting scenarios that could reveal bugs
+in different engine implementations. The second method considered is
+\emph{cross-engine differential testing}. This method fuzzes existing
+inputs~\cite{fuzz-testing-history} and then compares the output
+produced by different engines using a differential oracle. One
+possible cause of output discrepancy is a bug. It is worth noting that
+Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
+a variety of contexts to find
+bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
 automates test generation in scenarios where multiple implementations
@@
 contrast, cross-engine differential testing--the technique used in
-this work--checks correctness by comparing the output produced by
-\emph{different engines} on a fuzzed
-input~\cite{patra2016learning}. This approach is not popularized,
-certainly because it is more challenging to fully automate--a number
-of legitimate reasons exist, other than a bug, for a test execution to
-manifest discrepancy (see Table~\ref{tab:false-positives}).
+this work--checks functional correctness by comparing the output
+produced by \emph{different engines} on a fuzzed
+input~\cite{patra2016learning}. This approach has not been
+popularized, certainly because it is more challenging to fully
+automate--a number of legitimate reasons exist, other than a bug, for
+a test execution to manifest discrepancy (see
+Table~\ref{tab:false-positives}). This study quantifies human effort
+to find these bugs using this method.
 
@@
 \label{sec:es6-design}
+\label{sec:imp-dep-behavior}
 
@@
 versions and supporting engines are publicly available~\cite{kangax}.
+
+It is worth noting that undefined behavior makes differential testing
+more challenging.
+
 In the following, we briefly describe different sources of
@@
 
-%% \Mar{what is that exactly? can we cite? is that only spec or actually
-%%   code as most of java.* libraries.}  \Igor{seems like an API. They
-%%   define the language behavior; grammar; values to static variables;
-%%   the methods for each "class"(Object)...  These irregularities
-%%   appears on engine implementation, maybe an wrong if statement and so
-%%   on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
-%%   explanation in some forum/tutorial and explain **when** you
-%%   undertand the JS ecosystem design and can explain with confidence.}
+The \es{} spec uses the label ``implementation-dependent'' to indicate
+cases where each engine developer can decide how to implement some
+aspect of a functionality. In these cases, the behavior of some
+language element may differ from engine to engine. One reason this
+flexibility in the spec exists is to enable compiler
+optimizations. For example, the \mcodeid{for-in} loop does not clearly
+specify the iteration
+order~\cite{so-forin-undefined,javascript-in-chrome} and different
+engines capitalize on that~\cite{for-in-undefined}.  As another
+example, the latest version of the \es{} specification states that if
+the \mcodeid{Number.toPrecision()} function is called with more than
+one argument, then the behavior is
+implementation-dependent~\cite{es6-toPrecision}. Various other cases
+like this exist in the specification.
 
 \subsection{Undefined (Implementation-Dependent) Behavior}
-\label{sec:imp-dep-behavior}
 
-The \es{} spec uses the label ``implementation-dependent'' to indicate
-cases where each engine developer can decide how to implement some
-aspect of a functionality. In these cases, execution may differ from
-engine to engine. One of the reasons implementation-dependent behavior
-exists is to enable compiler optimizations. For example, the
-\mcodeid{for-in} loop does not clearly specify the iteration
-order~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that~\cite{for-in-undefined}. As another
-example, \Fix{...}
-
-\Mar{explain what is an **acceptable** incompatibilities. cite example
-bug reports.}
-\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
-the function \CodeIn{Number.toPrecision(precision)}, in general,
-if precision is defined the method returns a String 
-containing the Number value represented either 
-in decimal exponential notation or in decimal 
-fixed notation~\cite{es6-toPrecision}. The Number object uses a 
-property that the specification describes as approximately so when we use 
-toPrecision with a bigger precision, the values of each engine may vary, this
-could be considered as a case of incompatibility by engine
-design.}\Mar{I don't understand the example very well and don't understand the
-  relationship with HI/LO.}
+%% \Mar{explain what is an **acceptable** incompatibilities. cite example
+%% bug reports.}
+%% \Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
+%% the function \CodeIn{Number.toPrecision(precision)}, in general,
+%% if precision is defined the method returns a String 
+%% containing the Number value represented either 
+%% in decimal exponential notation or in decimal 
+%% fixed notation. The Number object uses a 
+%% property that the specification describes as approximately so when we use 
+%% toPrecision with a bigger precision, the values of each engine may vary, this
+%% could be considered as a case of incompatibility by engine
+%% design.}\Mar{I don't understand the example very well and don't understand the
+%%   relationship with HI/LO.}
 
@@
     \toprule
-           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
+    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
+    \midrule
     \jsc{} & - & - & - & - & - & - & - \\
@@
     \toprule
-    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
+    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
     \midrule
-    \jsc{} & - & - & - & -  \\
+    Versions (18.07) & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
+    \midrule
+    \jsc{} & - & 11 & - & -  \\
     \veight{} & - & - & - & -  \\
 %    \chakra{} & - & - & - & -  \\
-    Mozilla & - & - & - & -  \\
-    Duktape & - & - & - & -  \\
-    JerryScript & - & - & - & -  \\
-    JSI & - & - & - & -  \\
-    Tiny-js & - & - & - & -  \\
+    Mozilla & - & 333 & - & -  \\
+    Duktape & - & 80 & - & -  \\
+    JerryScript & - & 92 & - & -  \\
+    JSI & - & 14 & - & -  \\
+    Tiny-js & - & 11 & - & -  \\
+    \midrule
+    Versions (01.08) & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
+    \midrule
+    \jsc{} & \Fix{10} & 11 & 107 & 157   \\
+    \veight{} & 29 & \Fix{0} & 0 & 0  \\
+%    \chakra{} & - & - & - & -  \\
+    Mozilla & 741 & 286 & \Fix{178} & 476   \\
+    Duktape & 238 & 80 & 202 & 85   \\
+    JerryScript & 94 & 89 & 90 & 91   \\
+    JSI & 35 & 14 & 14 & 14   \\
+    Tiny-js & 11 & 11 & 11 & 11  \\
     \bottomrule 

### 2018-08-02 paper/paper.tex
pass on intro

--- 2018-08-02 paper/paper.tex
@@
 JavaScript (\js{}) is today one of the most popular programming
-languages for the web~\cite{business-insider,stackify}. The interest
-of the community for the language encourages constant improvements in
-its specification and implementations. It is natural to expect that
-such improvements entails sensible changes in runtime engines. Even
-small changes can have a large impact in practice. For example, in
+languages around~\cite{business-insider,stackify}, with significant
+penetration in the segments of web development, mobile, and even for
+client and server coding for the Internet of
+Things~(IoT)~\cite{simply-technologies}.
+
+The interest of the community for the language encourages constant
+improvements in its specification and implementations.  It is natural
+to expect that language improvements entails sensible implementation
+changes. Even small changes can have high impact. For example, in
 October 2014 a new attribute added to Array objects caused a bug that
-resulted in MS Outlook web not working under
+resulted in the web app for the MS Outlook Calendar not working under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
-bugs in JS engines is therefore an important problem. It is also
-challenging because of the speed the specification
-evolves~\cite{ecmas262-spec-repo} and the fact that the behavior of
-various language elements is undefined~\cite{so-undefined-behavior}
-(\ie{} left for the implementation to define).
+bugs in JS engines is therefore an important problem given the range
+of applications that could be affected. It is also challenging as
+specifications evolve constantly and are incomplete. More
+specifically, the evolution of the \js\ specification makes it hard to
+assess if a test fails because of a bug or because of some missing
+feature. The publicly-available Kangax compatibility
+table~\cite{kangax} highlights this problem; it relates features with
+the engines that (partially) support them. For similar reason, one
+could misclassify a test failure as a bug when the failure could be,
+in fact, caused by some undefined behavior in the spec. To note that
+many of these cases exist as it can be observed by searching for
+``implementation-dependent'' in the ES6 spec
+document~\cite{ecmas262-spec}.
 
@@
 reliability of existing JS engines by leveraging implementation
-diversity in two orthogonal ways. The first method considered is
-\emph{test transplantation}. This method evaluates the effects that
-running \js{} test files from a given engine have in detecting bugs in
-other engines. The intuition is that when a bug is found in some
-engine a test case is created and added to the regression suite. Those
-test inputs often check interesting scenarios that could reveal bugs
-in different engine implementations. The second method considered is
-\emph{cross-engine differential testing}. This method fuzzes existing
-inputs~\cite{fuzz-testing-history} and then compares the output
-produced by different engines using a differential oracle. One
-possible cause of output discrepancy is a bug. It is worth noting that
+diversity in two orthogonal ways: test transplantation and
+cross-engine differential testing.  \emph{Test transplantation}
+evaluates the effects that running \js{} test files from a given
+engine have in detecting bugs in other engines. The intuition is that
+when a bug is found in some engine a test case is created and added to
+the regression suite. Those test inputs often check interesting
+scenarios that could reveal bugs in different engine
+implementations. \emph{Cross-engine differential testing} evaluates
+the bug-finding ability of fuzzing existing
+inputs~\cite{fuzz-testing-history} and then comparing the output
+produced by different engines using a differential oracle. One of
+various causes of output discrepancy is a bug. It is worth noting that
 Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
@@
 input~\cite{patra2016learning}. This approach has not been
-popularized, certainly because it is more challenging to fully
-automate--a number of legitimate reasons exist, other than a bug, for
-a test execution to manifest discrepancy (see
+popularized, certainly because it is impractical to fully automate--a
+number of legitimate reasons exist, other than a bug, for a test
+execution to manifest discrepancy (see
 Table~\ref{tab:false-positives}). This study quantifies human effort
@@
 JavaScript engines are virtual machines that parse source code and
-compile it in bytecodes. These engines implement some version of
-ECMAScript\footnote{The name JavaScript still prevails today,
-  certainly for historical reasons.} (\es{}), which emerged with the
-goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript. The \es{} specification is
+compile it in bytecodes. These engines implement some version of the
+ECMAScript (\es{}), which emerged with the goal to standardize
+variants of the language, such as Netscape's JavaScript and
+Microsoft's JScript\footnote{The name JavaScript still prevails today,
+  certainly for historical reasons.}. The \es{} specification is
 regulated by Ecma International~\cite{es6-website} under the
@@
 minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
-versions and supporting engines are publicly available~\cite{kangax}.
+ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
 
-It is worth noting that undefined behavior makes differential testing
-more challenging.
+%% In the following, we briefly describe different sources of
+%% discrepancies that can emerge across different engine implementations
+%% as results of the active changes in the \es{} specification.
 
-In the following, we briefly describe different sources of
-discrepancies that can emerge across different engine implementations
-as results of the active changes in the \es{} specification.
+.........
+A compatibility table relating features and supporting engines is
+publicly available~\cite{kangax}.
 
-The \es{} spec uses the label ``implementation-dependent'' to indicate
+Another
+challenge is undefined (or implementation-dependent) behavior. The
+\es{} spec uses the label ``implementation-dependent'' to indicate
 cases where each engine developer can decide how to implement some

### 2018-08-02 paper/paper.tex
pass on section 2

@@
 
-JavaScript engines are virtual machines that parse source code and
-compile it in bytecodes. These engines implement some version of the
-ECMAScript (\es{}), which emerged with the goal to standardize
-variants of the language, such as Netscape's JavaScript and
-Microsoft's JScript\footnote{The name JavaScript still prevails today,
-  certainly for historical reasons.}. The \es{} specification is
-regulated by Ecma International~\cite{es6-website} under the
-TC39~\cite{tc39-github} technical committee.  Every year, a new
-version of the \es{} specification is produced with new features and
-minor fixes. The canonical spec today is
+JavaScript engines are virtual machines that parse source code,
+compile it in bytecodes, and run these bytecodes. These engines
+implement some version of the ECMAScript (\es{}), which emerged with
+the goal to standardize variants of the language, such as Netscape's
+JavaScript and Microsoft's JScript\footnote{The name JavaScript still
+  prevails today, certainly for historical reasons.}. The \es{}
+specification is regulated by Ecma International~\cite{es6-website}
+under the TC39~\cite{tc39-github} technical committee.  Every year, a
+new version of the \es{} specification is produced with new features
+and minor fixes. The canonical spec today is
 ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
@@
 %% as results of the active changes in the \es{} specification.
+%% .........
+%% A compatibility table relating features and supporting engines is
+%% publicly available~\cite{kangax}.
 
-.........
-A compatibility table relating features and supporting engines is
-publicly available~\cite{kangax}.
-
-Another
-challenge is undefined (or implementation-dependent) behavior. The
-\es{} spec uses the label ``implementation-dependent'' to indicate
-cases where each engine developer can decide how to implement some
-aspect of a functionality. In these cases, the behavior of some
-language element may differ from engine to engine. One reason this
-flexibility in the spec exists is to enable compiler
-optimizations. For example, the \mcodeid{for-in} loop does not clearly
-specify the iteration
+Both the specification and implementation of JavaScript are
+incomplete. Certain parts of the specification are undefined; it is
+responsibility of engine engineers to decide how to implement these
+functionalities. The JavaScript spec uses the label
+``implementation-dependent'' to indicate these cases, where behavior
+may differ from engine to engine. One reason this flexibility in the
+spec exists is to enable compiler optimizations. For example, the
+\mcodeid{for-in} loop does not clearly specify the iteration
 order~\cite{so-forin-undefined,javascript-in-chrome} and different
@@
 implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like this exist in the specification.
+like these exist in the specification. Such gap also exists at the
+implementation level. Given the speed the specification changes and
+the complexity of the language some features are not fully implemented
+as can be observed by the Kangax compatibility table~\cite{kangax}.
 
-\subsection{Undefined (Implementation-Dependent) Behavior}
+\sloppy It is also worth noting that, as in other languages, some
+elements in JS have non-deterministic behavior (\eg{},
+\mcodeid{Math.random} and \mcodeid{Date}). A test that make decisions
+based on these elements could, in principle, produce different
+outcomes on different runs. Carefully-written test cases should not
+manifest this kind of
+flakiness~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
+fuzzed test files could are more likely, intuitively, to manifest
+them.
 
-%% \Mar{explain what is an **acceptable** incompatibilities. cite example
-%% bug reports.}
-%% \Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
-%% the function \CodeIn{Number.toPrecision(precision)}, in general,
-%% if precision is defined the method returns a String 
-%% containing the Number value represented either 
-%% in decimal exponential notation or in decimal 
-%% fixed notation. The Number object uses a 
-%% property that the specification describes as approximately so when we use 
-%% toPrecision with a bigger precision, the values of each engine may vary, this
-%% could be considered as a case of incompatibility by engine
-%% design.}\Mar{I don't understand the example very well and don't understand the
-%%   relationship with HI/LO.}
+As mentioned previously, all those aspects make testing \js\ engines
+more challenging.
 
-\subsection{Randomness}
+%\subsection{Randomness}
 
-\sloppy Some elements in JS have non-deterministic behavior (\eg{},
-Math.random and Date). A test that make decisions based on these
-elements could, in principle, produce different outcomes on different
-runs. Carefully-written test cases should not manifest this kind of
-flakiness~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
-fuzzed test files are more likely to manifest them.
+%\subsection{\Fix{Other}}
 
-\subsection{\Fix{Other}}
-
-1) The stack depth in JS is often close to the real (native) C stack
-depth, nevertheless observable by JS through recursion. This causes
-differential behavior even on the same engine when JITs are enabled or
-disabled, as the stack frame sizes vary. LangFuzz in particular
-produces a lot of recursions and hits these problems even more often
-than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-  could be different.}
-
-\subsection{Bugs}
-
-It is worth to recall that there is no formal specification for \es{};
-the specification is written in natural language. As such, differences
-in behavior from one engine to another, other than those mentioned
-above (Sections~\ref{sec:imp-dep-behavior}
-and~\ref{sec:undef-behavior}), can occur. But these discrepancies are
-not acceptable.
+%% 1) The stack depth in JS is often close to the real (native) C stack
+%% depth, nevertheless observable by JS through recursion. This causes
+%% differential behavior even on the same engine when JITs are enabled or
+%% disabled, as the stack frame sizes vary. LangFuzz in particular
+%% produces a lot of recursions and hits these problems even more often
+%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
+%%   could be different.}
 
@@
 Figure~\ref{fig:workflow} illustrates the infrastructure we used for
-differential testing.  The bug-finding process takes on input JS files
-from regression test suites of various JS engines and generates
-warnings on output. Boxes in the figure denote encapsulation; arrowed
-lines indicate data flow. The cycle icons denote repetition--the
-leftmost icon indicates that each file in the input list will be
-analyzed in separate whereas the rightmost icon shows that a single
-file will be fuzzed multiple times. The bug-finding process works as
-follows.
+differential testing, which is related to part of the study discussed
+in this paper.  The bug-finding process takes on input JS files from
+regression test suites of various JS engines and generates warnings on
+output. Boxes in the figure denote encapsulation; arrowed lines
+indicate data flow. The cycle icons denote repetition--the leftmost
+icon indicates that each file in the input list will be analyzed in
+separate whereas the rightmost icon shows that a single file will be
+fuzzed multiple times. The bug-finding process works as follows.
 

### 2018-08-02 paper/paper.tex
pass on section 2

@@
 
-The infrastructure outputs a list of warnings for human inspection.
-To reduce the number of false alarms, we classified warnings in two
-kinds, reflecting their likelihood to manifest a real bug. Warnings of
-the kind ``\hi{}'' are associated with the cases where the anomaly has
-been detected in the execution of the test code or its harness. The
-rationale is that the test in this group executed without violating
-any internal checks of the API. In constrast, warnings in the
-``\lo{}'' group reflect the cases where the anomaly was observed
-during the execution of functions not related to the test itself. We
-found that different engines often check pre-conditions of those
-functions differently. It can happen, for example, that one engine
-enforces a weaker pre-condition compared to another and that is
-acceptable.  In those cases, our infrastructure would observe a
-discrepancy that is more likely to be associated with an invalid input
-produced by the fuzzer, \ie{}, a bug in the test not the
-code. Although we did find real bugs from ``\lo{}'' warnings, the
-proportion was much lower compared to the ``\hi{}'' warnings. Overall,
-only \Fix{12\%} of the reals bugs we found originated from ``\lo{}''
-warnings.
+Recall that a warning can be results of various causes other than a
+bug (see Table~\ref{tab:false-positives}). To facilitate inspection,
+the infrastructure groups and prioritize these warnings. Considering
+prioritization, we classified warnings in two kinds, reflecting their
+likelihood to manifest a real bug. Warnings of the kind ``\hi{}'' are
+associated with the cases where the anomaly has been detected in the
+execution of the test code or its harness. The rationale is that the
+test in this group executed without violating any internal checks of
+the API. In constrast, warnings in the ``\lo{}'' group reflect the
+cases where the anomaly was observed during the execution of functions
+not related to the test itself. We found that different engines often
+check pre-conditions of those functions differently. It can happen,
+for example, that one engine enforces a weaker pre-condition compared
+to another and that is acceptable.\Mar{example!} In those cases, our
+infrastructure would observe a discrepancy that is more likely to be
+associated with an invalid input produced by the fuzzer, \ie{}, it is
+a bug in the test not the code. Although we did find real bugs from
+``\lo{}'' warnings, the proportion was much lower compared to
+``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
+found originated from ``\lo{}'' warnings.
 

### 2018-08-03 paper/paper.tex
pass on sections III, IV.B, and first par. section V

@@
 
+Figure~\ref{fig:workflow} illustrates the infrastructure we used for
+differential testing, use in part of our study. The bug-finding
+process takes on input JS files from regression test suites of various
+JS engines and generates warnings on output. Boxes in the figure
+denote encapsulation; arrowed lines indicate data flow. The cycle
+icons denote repetition--the leftmost icon indicates that each file in
+the input list will be analyzed in separate whereas the rightmost icon
+shows that a single file will be fuzzed multiple times.
+
 %\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
-\begin{figure}[t]
+\begin{figure}[h]
   \centering
@@
 
-Figure~\ref{fig:workflow} illustrates the infrastructure we used for
-differential testing, which is related to part of the study discussed
-in this paper.  The bug-finding process takes on input JS files from
-regression test suites of various JS engines and generates warnings on
-output. Boxes in the figure denote encapsulation; arrowed lines
-indicate data flow. The cycle icons denote repetition--the leftmost
-icon indicates that each file in the input list will be analyzed in
-separate whereas the rightmost icon shows that a single file will be
-fuzzed multiple times. The bug-finding process works as follows.
-
-New inputs are obtained for a given test input using some
-off-the-shelf input fuzzer~\cite{fuzz-testing-history}.\Comment{
-  Several fuzzing methods have been proposed in the past, varying with
-  respect to how new inputs are
+The bug-finding process works as follows. New inputs are obtained for
+a given test input using some off-the-shelf input
+fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
+  have been proposed in the past, varying with respect to how new
+  inputs are
   generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
@@
 explain discrepancy (see Table~\ref{tab:false-positives}). We used the
-open-source eshost-cli project~\cite{eshost-cli} for checking output
-discrepancy. Microsoft uses that tool in the Chakra JS engine.
+open-source eshost-cli project~\cite{eshost-cli}, also used at
+Microsoft, for checking output discrepancy.
 
@@
 
-Recall that a warning can be results of various causes other than a
-bug (see Table~\ref{tab:false-positives}). To facilitate inspection,
-the infrastructure groups and prioritize these warnings. Considering
-prioritization, we classified warnings in two kinds, reflecting their
-likelihood to manifest a real bug. Warnings of the kind ``\hi{}'' are
-associated with the cases where the anomaly has been detected in the
-execution of the test code or its harness. The rationale is that the
-test in this group executed without violating any internal checks of
-the API. In constrast, warnings in the ``\lo{}'' group reflect the
-cases where the anomaly was observed during the execution of functions
-not related to the test itself. We found that different engines often
-check pre-conditions of those functions differently. It can happen,
-for example, that one engine enforces a weaker pre-condition compared
-to another and that is acceptable.\Mar{example!} In those cases, our
-infrastructure would observe a discrepancy that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-a bug in the test not the code. Although we did find real bugs from
-``\lo{}'' warnings, the proportion was much lower compared to
-``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
-found originated from ``\lo{}'' warnings.
+Recall that a warning can be manifested for reasons other than a bug
+and there is no clear way to distiguish those cases automatically (see
+Table~\ref{tab:false-positives}). A human needs to inspect the warning
+to diagnose the discrepancy. To facilitate inspection, the
+infrastructure prioritize these warnings and clusters them in
+groups. Considering prioritization, we classified warnings in two
+kinds, reflecting their likelihood to manifest a real bug. Warnings of
+the kind ``\hi{}'' are associated with the cases where the test code
+executed to completion without violating any internal checks but it
+violated assertions declared in the test itself or its harness. The
+rationale is that the input is valid--considering the checks declared
+in the API functions--but, still, it manifests discrepancy through
+violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
+in the ``\lo{}'' group reflect the cases where the anomaly was
+observed during the execution of functions not related to the test
+itself. We found that different engines often check pre-conditions of
+those functions differently. It can happen, for example, that one
+engine enforces a weaker pre-condition on a function input compared to
+another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
+observe a discrepancy that is more likely to be associated with an
+invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
+in the test code not the engine (library or runtime) code. Although we
+did find real bugs from ``\lo{}'' warnings, the proportion was much
+lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
+reals bugs we found originated from ``\lo{}'' warnings.
 
@@
 execution. The main source of test cases is the offical
-TC-39~\cite{tc39-github} conformance test suite for the ECMA262
+Test262~\cite{tc39-github} conformance test suite for the ECMA262
 specification~\cite{ecmas262-spec}. This test suite contains 87\% of
@@
 four engines mentioned in Section~\ref{sec:methodology:engines} and
-four other engines. We did not consider tests from the \chakra{}
-repository because of their intensive use of Chakra-specific
-objects. Table~\ref{tab:test-suites} shows the breakdown of tests we
-considered. Overall, we found a total of \totfiles{} JS files.
+four other engines. Table~\ref{tab:test-suites} shows the breakdown of
+tests we considered. Overall, we found a total of \totfiles{} JS
+files. We did not consider tests from the \chakra{} repository because
+they depend on non-portable objects. Notice that the number of tests
+in \veight\ is low. That happens because many tests in \veight{} are
+inherited from Mozilla and \jsc{}; we discarded those to avoid
+repetition and to give credit where it is due. The \veight{} test
+suite contains other tests, but, as in \chakra{}, these tests use
+non-portable testing objects that we still did not mock.
 
-It is also worth mentioning that some engines use custom shell,
-including a harness with custom assertions, to run tests.  For these,
+It is also worth mentioning that some engines use a custom shell to
+run tests, including a harness with specific assertions.  For these,
 we needed to make small changes in the testing infrastructure to be
@@
 \emph{existing} inputs randomly. The strenght of the approach is
-limited by the supported mutation operators, which are typically
-simple, and the quality of the test suite. We chose \radamsa\ and
-\quickfuzz\ \Fix{...elaborate...}
+limited by the quality of the test suite and the supported mutation
+operators, which are typically simple. We chose \radamsa\ and
+\quickfuzz\ \Fix{...elaborate...} \Mar{I mention below that these
+  fuzzers ``only make valid changes in literals of the
+  language''. Please confirm and explain that still this is
+  interesting!}
 
@@
 
-Recall that the goal of our study is to assess reliability of
-\js\ engines by leveraging implementation diversity, which is
-specially rich in this domain. We report results in three
-parts. First, we report on the stability of the engines we analyzed
-using the Test262 standard conformance test suite for
-EcmaScript~\cite{ecma262-conformance-suite}. The intuition is that the
-bugs we discover throughout this study would have low relevance if the
-engines are too fragile. Second, we report results obtained with test
-transplantation. The hypothesis is that test cases written for one
-engine may reveal bugs in different engines. The rationale is that the
-domain of possible inputs is too large; consequently, we expect that
-test suites of a given engine cover scenarios and corner cases
-uncovered by another engine. Third, we analyzed the impact of using
-cross-engine differential testing to find bugs. The hypothesis is that
-even black-box fuzzers can expose important bugs.
+The goal of our study is to assess reliability of \js\ engines by
+leveraging implementation diversity, which is specially rich in this
+domain. We report results in three parts. First, we report on the
+stability of the engines we analyzed using the Test262 standard
+conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
+(Section~\ref{sec:stability}). The intuition is that the bugs we
+discover throughout this study would have low relevance if the engines
+are too fragile. Second, we report results obtained with test
+transplantation (Section~\ref{sec:transplantation}). The rationale is
+that the domain of possible inputs is too large; consequently, we
+expect that test suites written for a given engine cover scenarios and
+corner cases uncovered by another engine. To sum, we hope that that
+test cases written for one engine could reveal bugs in different
+engines as opposed to only manifesting false alarms such as those that
+could emerge from implementation-dependent behavior. Third, we
+analyzed the impact of using cross-engine differential testing to find
+bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
+rationale is that even black-box fuzzers that typicaly make valid
+changes only in literals of the language could expose important
+bugs. All in all, we want to assess the impact of simple approaches
+that leverage on diversity to find bugs in \js\ engines with the goal
+of assessing their reliability.
 
@@
 \subsection{Cross-Engine Differential Testing}
+\label{sec:cross-engine-diff-testing-results}
 

### 2018-08-03 paper/paper.tex
fix table with new build (02.08)

@@
     \midrule
-    Versions (18.07) & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
-    \midrule
-    \jsc{} & - & 11 & - & -  \\
-    \veight{} & - & - & - & -  \\
+    \Fix{Versions (18.07)} & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
+    \midrule
+    \jsc{} & - & 11 & 107 & 157  \\
+    \veight{} & 29 & - & 0 & 0  \\
 %    \chakra{} & - & - & - & -  \\
-    Mozilla & - & 333 & - & -  \\
-    Duktape & - & 80 & - & -  \\
-    JerryScript & - & 92 & - & -  \\
-    JSI & - & 14 & - & -  \\
-    Tiny-js & - & 11 & - & -  \\
-    \midrule
-    Versions (01.08) & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
+    Mozilla & 748 & 287 & - & 475  \\
+    Duktape & 238 & 80 & 202 & 85  \\
+    JerryScript & 91 & 92 & 90 & 91  \\
+    JSI & 35 & 14 & 14 & 14  \\
+    Tiny-js & 11 & 11 & - & 11  \\
+    \midrule
+    \Fix{Versions (01.08)} & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
     \midrule
@@
     Mozilla & 741 & 286 & \Fix{178} & 476   \\
+    Duktape & 238 & 80 & 202 & 85   \\
+    JerryScript & 94 & 89 & 90 & 91   \\
+    JSI & 35 & 14 & 14 & 14   \\
+    Tiny-js & 11 & 11 & 11 & 11  \\
+    \midrule
+    \Fix{Versions (02.08)} & 234515 & 7.0.144 & 62.0b13 & 1.10.1 \\
+    \midrule
+    \jsc{} & - & 11 & 107 & 157   \\
+    \veight{} & 29 & - & 0 & 0  \\
+%    \chakra{} & - & - & - & -  \\
+    Mozilla & 741 & 286 & - & 475   \\
     Duktape & 238 & 80 & 202 & 85   \\

### 2018-08-03 paper/paper.tex
fix table IV

--- 2018-08-03 paper/paper.tex
@@
     \midrule
-    Versions (18.07) & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
+    \Fix{Versions (01.08)} & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
     \midrule
-    \jsc{} & - & 11 & - & -  \\
-    \veight{} & - & - & - & -  \\
+    \jsc{} & - & 1 & 97 & 147   \\
+    \veight{} & 29 & - & 0 & 0  \\
 %    \chakra{} & - & - & - & -  \\
-    Mozilla & - & 333 & - & -  \\
-    Duktape & - & 80 & - & -  \\
-    JerryScript & - & 92 & - & -  \\
-    JSI & - & 14 & - & -  \\
-    Tiny-js & - & 11 & - & -  \\
-    \midrule
-    Versions (01.08) & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
-    \midrule
-    \jsc{} & \Fix{10} & 11 & 107 & 157   \\
-    \veight{} & 29 & \Fix{0} & 0 & 0  \\
-%    \chakra{} & - & - & - & -  \\
-    Mozilla & 741 & 286 & \Fix{178} & 476   \\
-    Duktape & 238 & 80 & 202 & 85   \\
-    JerryScript & 94 & 89 & 90 & 91   \\
-    JSI & 35 & 14 & 14 & 14   \\
-    Tiny-js & 11 & 11 & 11 & 11  \\
+    \smonkey{} & 563 & 108 & 0 & 298   \\
+    Duktape & 165 & 7 & 129 & 12   \\
+    JerryScript & 26 & 21 & 22 & 23   \\
+    JSI & 21 & 0 & 0 & 0   \\
+    Tiny-js & 0 & 0 & 0 & 0  \\
     \bottomrule 

### 2018-08-06 paper/paper.tex
fix table IV
fix table nofuzz
merging
merge
update table

@@
     \midrule
-    Mozilla & \cite{mozilla} & 2,633 \\
-    \veight{} & \cite{v8} & 74 \\
-    \jsc{} & \cite{webkit} & 1,031 \\
+    \jsc{} & \cite{webkit} & 1,021 \\
+    \smonkey\ & \cite{mozilla} & 2,116 \\
+    \veight{} & \cite{v8} & 57 \\
     \midrule    
-    Duktape & \cite{duktape} & 1,195 \\ 
-    JerryScript & \cite{jerryscript} & 1,950 \\
-    JSI & \cite{jsi} & 98 \\
-    Tiny-js & \cite{tinyjs} & 48 \\    
+    Duktape & \cite{duktape} & 921 \\ 
+    JerryScript & \cite{jerryscript} & 1,878 \\
+    JSI & \cite{jsi} & 63 \\
+    Tiny-js & \cite{tinyjs} & 37 \\    
     % Chakra & \cite{chakracore} & 2632 \\
@@
     \midrule
-    \Fix{Versions (01.08)} & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
-    \midrule
-    \jsc{} & - & 1 & 97 & 147   \\
+    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
+    \Comment{
+      Lembrar dos testes que os testes da propria engine falham:
+      V8 0 
+      JSC 6 
+      Spidermonkey 58
+    }
+    \jsc{} & - & 9 & 10 & 58   \\
     \veight{} & 29 & - & 0 & 0  \\
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 563 & 108 & 0 & 298   \\
-    Duktape & 165 & 7 & 129 & 12   \\
-    JerryScript & 26 & 21 & 22 & 23   \\
-    JSI & 21 & 0 & 0 & 0   \\
+    \smonkey{} & 218 & 107 & - & 279 \\
+    Duktape & 0 & 4 & 4 & 1   \\
+    JerryScript & 23 & 25 & 22 & 23   \\
+    JSI & 0 & 0 & 0 & 0   \\
     Tiny-js & 0 & 0 & 0 & 0  \\

### 2018-08-06 paper/paper.tex
pass on V.B

@@
 inherited from Mozilla and \jsc{}; we discarded those to avoid
-repetition and to give credit where it is due. The \veight{} test
-suite contains other tests, but, as in \chakra{}, these tests use
-non-portable testing objects that we still did not mock.
+repetition and to give credit where it is due. For all engines engines
+we found test using non-portable functions that we detected by running
+the test on a different engine. We needed to discard those.
 
@@
 
-This section reports results obtained with test
-transplantation. Table~\ref{tab:cross-testing} shows the number of
-failures that each engine produces on a different test suite. To sum,
-we observed that \Fix{...}
+This section reports the failures observed when running a test suites
+on an engine for which those tests were not run
+before. Table~\ref{tab:cross-testing} shows the number of failures for
+each pair of test suite and engine. The first column shows the test
+suites whereas the first row shows the engines. We use a dash (``-'')
+to indicate that we did not consider the combinations that associated
+a test suite with the engine that originated them; failures in those
+cases would either indicate regressions or flaky tests as opposed to
+an unknown bug for that engine. We also discarded such test cases from
+consideration in other engines as we wanted the test to pass on its
+originating engine; a failure in that case would be a stronger
+indicative of a bug.
+
+To sum, we observed that, considering this dataset, the Mozilla
+\smonkey\ was the engine that failed the least whereas the Microsoft
+engine \chakra\ failed the most. The \smonkey\ test suite also
+revealed more failures than any other, perhaps as expected,
+considering that it is the suite with more tests (see
+Table~\ref{tab:test-suites}). This suggests that the investiment in
+testing paid off in this case.
 
@@
     Tiny-js & 0 & 0 & 0 & 0  \\
+    \midrule
+   \textbf{total} & 270 & 145 & 36 & 361 \\
     \bottomrule 

### 2018-08-06 paper/paper.tex
minor fix
pass on text

@@
 
-%% Our infrastructure reported a total of \nofuzzAll{} buckets, including
-%% \lo{} and \hi{}, that resulted in \nofuzzBugs{} bug reports. Of the
-%% total of \nofuzzAll{} buckets, we found that \nofuzzDuplicates\ were
-%% duplicates and \nofuzzFalsePositives\ were false positives. Most of
-%% the cases of duplicates were related to the Test262 conformance test
-%% suite, which all \js{} should strive to pass but we found that it is
-%% not uncommon for the engines to fail on some of these. For example,
-%% \veight{} \nofuzzFalsePositives
-
-We inspected each of those failures in detail according to the
-following methodology. \Fix{..elaborate..}
+The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
+false and true positives observed with test transplantation. The top
+piechart shows false alarms.  It is important to stress that all the
+``transplanted'' tests should have passed in these cases. The absolute
+number of tests is shown in parentheses to the right side of the
+explanation for the false positive. The sources of false alarm are as
+follows:
+
+\begin{itemize}
+  \item \textbf{Undefined.} Implementation-dependent behavior as per
+    ECMA262 specification~\cite{ecmas262-spec}. For example, \Fix{XXX}
+  \item \textbf{Timeout/OME\footnote{ome is for out of memory
+      error.}.} Because target engine does not optimize code as the
+    original engine did, test fails to finish at the time limit
+    specified in the test or runs out of memory. For example, we found
+    that only \jsc{} implements tail-call optimization to avoid tail
+    recursion.
+  \item \textbf{Not implemented.} Test fails because it covers
+    function in the spec which is yet to be implemented. For example,
+    at the time of writing, Chakra did not implement various
+    properties from the \mcodeid{Symbol} object. A test that refers to
+    this object will fail in \chakra{}.
+  \item \textbf{Future Feature.} Test fails because it uses a feature
+    that is available in the original engine, but still not standard,
+    and the target engine does not support that feature. For example,
+    \Fix{XXX}
+  \item \textbf{Error message mismatch.} Test fails because it
+    compares an error message, which is not portable across
+    engines. For example, \Fix{a test from the engine XXX compares the
+      string encapsulated in the object of type YYY. The engine ZZZ
+      fails because it produces the string AAA while expecting the
+      string BBB.}
+\end{itemize}
+
+In summary, we observed that \Fix{...elaborate...}
+
+Considering true positives, \Fix{...elaborate...}
+
+\begin{figure}[h]
+  \centering
+  \subfloat[\label{fig:falsepositives}False Positives]{%
+    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
+  }
+  \label{1a}\hfill
+  \subfloat[\label{fig:truepositives}True Positives]{%
+    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
+  }
+  \label{1b}\\
+  \caption{\label{fig:piecharts-transplantation}False and True positives.}
+\end{figure}
+
 Figure~\ref{tab:test-transplantation-bugs} shows
@@
 positives per source. A false positive is a bucket that did not lend
-itself in a bug report. We identified five sources of imprecision. The
-source ``not yet implemented'' indicates that the engine does not
-implement some part of the specification. For example, at the time of
-writing, Chakra does not implement various properties from the
-\CodeIn{Symbol} object. The source ``invalid input'' indicates that
-the test violated some part of the specification. For example, the
-test indirectly invoked some function with unexpected
-arguments\Fix{provide concrete example}. In all cases that we
-analyzed, that happened because fuzzing produced an invalid test
-input. The source ``timeout/ome''\footnote{ome is for out of memory
-  error.} indicates that the test times out (we used a 3s time budget)
-or runs out of memory. That happens because engines implement
-different optimizations. For example, we found that only \jsc{}
-implements tail-call optimization to avoid tail
-recursion. Consequently, for a certain input, \jsc{} finishes
-execution quickly whereas other engines time out. The source
-``implementation-dependent'' is as defined in
-Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
-source ``future feature'' corresponds to the case where a feature will
-be part of the spec but some engines already implemented it, making a
-test that uses the feature to pass only in those engines.
+itself in a bug report. The sources of imprecision are as defined in
+Section~\ref{sec:transplantation} with the addition of one, which
+emerges with fuzzing. The source ``invalid input'' indicates that the
+test violated some part of the specification. For example, the test
+indirectly invoked some function with unexpected arguments\Fix{provide
+  concrete example}.
 
@@
     & \radamsa\ & \quickfuzz\ \\
-    %% not yet implemented & 8 & - & - \\
-    %% invalid input & 0 & - & - \\
-    %% timeout/ome & 13 & - & - \\
-    %% implementation-dependent & 3 & - & - \\
-    %% future feature & 3 & - & - \\
-    not yet implemented & - & - \\
-    invalid input & - & - \\
-    timeout/ome & - & - \\
-    implementation-dependent & - & - \\
-    future feature & - & - \\
+    Undefined & - & - \\
+    Timeout/OME & - & - \\
+    Not Implemented & - & - \\
+    Future Feature & - & - \\
+    Error Message Mismatch & - & - \\    
+    Invalid Input & - & - \\    
     \bottomrule     

### 2018-08-07 paper/paper.tex
minor comments on V.B

@@
 
-This section reports the failures observed when running a test suites
-on an engine for which those tests were not run
-before. Table~\ref{tab:cross-testing} shows the number of failures for
-each pair of test suite and engine. The first column shows the test
-suites whereas the first row shows the engines. We use a dash (``-'')
-to indicate that we did not consider the combinations that associated
-a test suite with the engine that originated them; failures in those
+This section reports the results of test transplantion, \ie{}, we
+analyzed the failures observed when running a test suite on an engine
+other than the engine where the test suite
+originated.
+
+Table~\ref{tab:cross-testing} shows the number of failures for each
+pair of test suite and engine. The first column shows the test suites
+and the first row shows the engines that run those tests. We use a
+dash (``-'') to indicate that we did not consider the combinations
+that associated a test suite with its parent engine; failures in those
 cases would either indicate regressions or flaky tests as opposed to
-an unknown bug for that engine. We also discarded such test cases from
-consideration in other engines as we wanted the test to pass on its
-originating engine; a failure in that case would be a stronger
-indicative of a bug.
-
-To sum, we observed that, considering this dataset, the Mozilla
+an unknown bug for that engine. We did not run the test cases that
+fail on its parent engine in any other engines; we wanted all tests to
+pass on their parent engine as a failure in that case would be a
+stronger indicative of a bug. In total, 64 test cases were discarded
+for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
+tests (\ie{}, 28369-31276-64) were considered in this experiment.  We
+observed from the table that, considering this dataset, the Mozilla
 \smonkey\ was the engine that failed the least whereas the Microsoft
@@
       V8 0 
-      JSC 6 
+      JSC 2 
       Spidermonkey 58

### 2018-08-07 paper/paper.tex
update values

--- 2018-08-06 paper/paper.tex
@@
     and the target engine does not support that feature. For example,
-    \Fix{XXX}
+    \Fix{XXX} \Igor{Creio que neste experimento, essa funcao nao vai 
+    aparecer. Identificamos isto em alguns testes da suite test262(nao estamos utilizando ela aqui).}
   \item \textbf{Error message mismatch.} Test fails because it
     compares an error message, which is not portable across
-    engines. For example, \Fix{a test from the engine XXX compares the
-      string encapsulated in the object of type YYY. The engine ZZZ
-      fails because it produces the string AAA while expecting the
-      string BBB.}
+    engines. For example, \Igor{
+      a test from the engine \jsc{} uses an assert function called
+      \CodeIn{shouldThrow} that expects an specific error message. In this test, 
+      all engines throws the Error as expected, however only the message 
+      on \jsc{} engine match with the string expected in the test case.
+    }
 \end{itemize}
@@
    11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
+   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
+   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
    \bottomrule

### 2018-08-07 paper/paper.tex
fix results

@@
   \item \textbf{Undefined.} Implementation-dependent behavior as per
-    ECMA262 specification~\cite{ecmas262-spec}. For example, \Fix{XXX}
+    ECMA262 specification~\cite{ecmas262-spec}. For example, 
+    \Igor{a test from JerryScript suite uses a function \CodeIn{Number.toPrecision([precision])}
+    that returns a string representing the number object in
+    fixed-point or exponential notation rounded to precision. According to ES specifications(cite)
+    built-ins that involves Math functions are implementation-dependent 
+    approximation to the real value.
+    }
   \item \textbf{Timeout/OME\footnote{ome is for out of memory

### 2018-08-07 paper/paper.tex
pass on V.B

@@
 for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
-tests (\ie{}, 28369-31276-64) were considered in this experiment.  We
-observed from the table that, considering this dataset, the Mozilla
+test files (\ie{}, 38369-31276-64) were considered in this experiment,
+which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
+these, 812 failures were observed (3.25\% of the runs) across
+\textbf{543} distinct files (7.72\% of the files). We analyzed each of
+these file in separate to identify if the failure was fault-revealing
+or a false positive.
+
+We observed from the table that, considering this dataset, the Mozilla
 \smonkey\ was the engine that failed the least whereas the Microsoft
@@
 considering that it is the suite with more tests (see
-Table~\ref{tab:test-suites}). This suggests that the investiment in
-testing paid off in this case.
+Table~\ref{tab:test-suites}).
+
+%% This suggests that the investiment in
+%% testing paid off in this case.
 
@@
 ``transplanted'' tests should have passed in these cases. The absolute
-number of tests is shown in parentheses to the right side of the
-explanation for the false positive. The sources of false alarm are as
-follows:
+number of tests in each category is shown in parentheses to the
+right-side of the label of a slice, nameing the source of false
+positive. The sources are as follows:
 
 \begin{itemize}
-  \item \textbf{Undefined.} Implementation-dependent behavior as per
-    ECMA262 specification~\cite{ecmas262-spec}. For example, 
-    \Igor{a test from JerryScript suite uses a function \CodeIn{Number.toPrecision([precision])}
-    that returns a string representing the number object in
-    fixed-point or exponential notation rounded to precision. According to ES specifications(cite)
-    built-ins that involves Math functions are implementation-dependent 
-    approximation to the real value.
-    }
+  \item \textbf{Undefined Behavior.} False positives of this kind are
+    manifested when tests cover implementation-dependent behavior, as
+    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
+    example, one of the tests from \jerry\ uses the function
+    \CodeIn{Number.toPrecision([precision])}, which translates a
+    number to a string, considering a given number of significant
+    digits. The floating-point approximation of the real value is
+    implementation-dependent, making the test to pass only in
+    \chakra\ for that test.
+
   \item \textbf{Timeout/OME\footnote{ome is for out of memory
-      error.}.} Because target engine does not optimize code as the
-    original engine did, test fails to finish at the time limit
-    specified in the test or runs out of memory. For example, we found
-    that only \jsc{} implements tail-call optimization to avoid tail
-    recursion.
-  \item \textbf{Not implemented.} Test fails because it covers
-    function in the spec which is yet to be implemented. For example,
-    at the time of writing, Chakra did not implement various
-    properties from the \mcodeid{Symbol} object. A test that refers to
-    this object will fail in \chakra{}.
-  \item \textbf{Future Feature.} Test fails because it uses a feature
-    that is available in the original engine, but still not standard,
-    and the target engine does not support that feature. For example,
-    \Fix{XXX} \Igor{Creio que neste experimento, essa funcao nao vai 
-    aparecer. Identificamos isto em alguns testes da suite test262(nao estamos utilizando ela aqui).}
-  \item \textbf{Error message mismatch.} Test fails because it
-    compares an error message, which is not portable across
-    engines. For example, \Igor{
-      a test from the engine \jsc{} uses an assert function called
-      \CodeIn{shouldThrow} that expects an specific error message. In this test, 
-      all engines throws the Error as expected, however only the message 
-      on \jsc{} engine match with the string expected in the test case.
-    }
+      error.}.} False positives of this kind manifest when the target
+    engine that runs the test do not optimize code as the original
+    engine. For that, tests fail to finish at the time budget or runs
+    out of memory.\Comment{For example, we found that only \jsc{} implements
+    tail-call optimization to avoid tail recursion.}\Mar{concrete example!}
+
+  \item \textbf{Not implemented.} False positives of this kind
+    manifest when a test fails because it covers a function that is
+    part of the official spec, but is not implemented in the target
+    engine. For example, at the time of writing, Chakra does not
+    implement various properties from the \mcodeid{Symbol} object.
+
+  \item \textbf{Unknown.} This source corresponds to the cases we were
+    unable to confidently diagnose the failure.
+
+  %% \item \textbf{Error message mismatch.} Test fails because it
+  %%   compares an error message, which is not portable across
+  %%   engines. For example, \Igor{
+  %%     a test from the engine \jsc{} uses an assert function called
+  %%     \CodeIn{shouldThrow} that expects an specific error message. In this test, 
+  %%     all engines throws the Error as expected, however only the message 
+  %%     on \jsc{} engine match with the string expected in the test case.
+  %%   }
 \end{itemize}
@@
 itself in a bug report. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of one, which
-emerges with fuzzing. The source ``invalid input'' indicates that the
-test violated some part of the specification. For example, the test
-indirectly invoked some function with unexpected arguments\Fix{provide
-  concrete example}.
+Section~\ref{sec:transplantation} with the addition of two new
+sources, which we did not observe before. The source ``Invalid Input''
+indicates that the test violated some part of the specification. For
+example, the test indirectly invoked some function with unexpected
+arguments\Fix{provide concrete example}. The source ``Upcoming
+Feature'' indicates that the test fails because it uses a feature that
+is available in the original engine, but it is still not standard, and
+the target engine does not support that feature. For example,
+\Fix{provide concrete example}
 
@@
     Not Implemented & - & - \\
-    Future Feature & - & - \\
+    Upcoming Feature & - & - \\
     Error Message Mismatch & - & - \\    

### 2018-08-07 paper/paper.tex
pass on V.B.

@@
     implementation-dependent, making the test to pass only in
-    \chakra\ for that test.
+    \chakra\ for that test. \Igor{ Several tests explores 
+    the error message from a function violation, due the error
+    message string is distinct and the type of Error is equal,
+    we considered these cases as undefined behavior too.
+    }
 
@@
     out of memory.\Comment{For example, we found that only \jsc{} implements
-    tail-call optimization to avoid tail recursion.}\Mar{concrete example!}
+    tail-call optimization to avoid tail recursion.}
+    \Igor{
+      For example, a testcase from \jsc{} suite explores the tail call
+      to optimize the recursion, the test uses a recursive function that
+      should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
+      only the \jsc{} supports tail-call optimization and the testcase 
+      passes without failures. Another case can be found in JerryScript suite
+      that uses a repetition statement to concatenate long strings 
+      exponentially, causing an out of memory error. The engines used 
+      supports the flags to increase memory, however we prefer to use 
+      the default engine build.
+    }
 
@@
     engine. For example, at the time of writing, Chakra does not
-    implement various properties from the \mcodeid{Symbol} object.
+    implement various properties from the \mcodeid{Symbol} object, 
+    \Igor{these implementation are in experimental mode 
+    (ie. activating with flag -ES6Experimental)}.
 
@@
     unable to confidently diagnose the failure.
+    \Igor{
+      We observed that some tests are not valid due
+      not corresponds to the ES6 specifications,
+      we skip these warnings.
+    }
 
@@
    13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
+   14 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & \Fix{x} & JerryScript\\
+   15 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & \Fix{x} & JerryScript\\
    \bottomrule

### 2018-08-07 paper/paper.tex
revising comments from igor

@@
     implementation-dependent, making the test to pass only in
-    \chakra\ for that test. \Igor{ Several tests explores 
-    the error message from a function violation, due the error
-    message string is distinct and the type of Error is equal,
-    we considered these cases as undefined behavior too.
-    }
+    \chakra\ for that test. As another example, some tests from
+    \Fix{Y} use the implementation-dependent description message\Mar{what is the
+      name of the property?} encapsulated in an \CodeIn{Error} object
+    in assertions. As such, those tests fail in all engines but \Fix{Y}.
 
   \item \textbf{Timeout/OME\footnote{ome is for out of memory
-      error.}.} False positives of this kind manifest when the target
-    engine that runs the test do not optimize code as the original
-    engine. For that, tests fail to finish at the time budget or runs
-    out of memory.\Comment{For example, we found that only \jsc{} implements
-    tail-call optimization to avoid tail recursion.}
-    \Igor{
-      For example, a testcase from \jsc{} suite explores the tail call
-      to optimize the recursion, the test uses a recursive function that
-      should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
-      only the \jsc{} supports tail-call optimization and the testcase 
-      passes without failures. Another case can be found in JerryScript suite
-      that uses a repetition statement to concatenate long strings 
-      exponentially, causing an out of memory error. The engines used 
-      supports the flags to increase memory, however we prefer to use 
-      the default engine build.
-    }
+      error.}.} False positives of this kind manifest because the
+    engine that runs the test does not optimize the code as the
+    original engine and that has an effect in the test outcome.  The
+    test may fail to finish at the time budget or runs out of
+    memory. For example, a test case from \jsc{} defines a function
+    with a tail-call recursion. The test fails in all engines but
+    \jsc{}, which implements tail-call optimization.
+
+    %% \Igor{
+    %%   For example, a testcase from \jsc{} suite explores the tail call
+    %%   to optimize the recursion, the test uses a recursive function that
+    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
+    %%   only the \jsc{} supports tail-call optimization and the testcase 
+    %%   passes without failures. Another case can be found in JerryScript suite
+    %%   that uses a repetition statement to concatenate long strings 
+    %%   exponentially, causing an out of memory error. The engines used 
+    %%   supports the flags to increase memory, however we prefer to use 
+    %%   the default engine build.
+    %% }
 
@@
     engine. For example, at the time of writing, Chakra does not
-    implement various properties from the \mcodeid{Symbol} object, 
-    \Igor{these implementation are in experimental mode 
-    (ie. activating with flag -ES6Experimental)}.
-
-  \item \textbf{Unknown.} This source corresponds to the cases we were
-    unable to confidently diagnose the failure.
-    \Igor{
-      We observed that some tests are not valid due
-      not corresponds to the ES6 specifications,
-      we skip these warnings.
-    }
+    implement by default various properties from the \mcodeid{Symbol}
+    object. These properties are only available activating ES6
+    experimental mode with the flag \CodeIn{-ES6Experimental}.
+
+  \item \textbf{Unknown.} This category corresponds to the cases we
+    were unable to confidently diagnose the failure.  \Igor{ We
+      observed that some tests are not valid due not corresponds to
+      the ES6 specifications, we skip these warnings.  }\Mar{Igor,
+      this is not well-formed english and I don't understand what you
+      want to say.}
 

### 2018-08-08 paper/paper.tex
pass on results

--- 2018-08-07 paper/paper.tex
@@
 
+\Igor{
+  To generate our priority between engines we classified our bugs confirmed 
+  based on the priority that the devs of the bug trackers that we explore. 
+  We defined 3 levels of priority called P1, P2 and P3. P1 is related to
+  the engine cores that involves crashes and parsers errors. P2 is related
+  to ES spec conformance and P3 refer to bugs related to bugs in general, for example
+  invalid message outputs, Automatic Semicolon Insertion(ASI) and compatibility issues.
+}
+
 \begin{table*}[t]
@@
   \begin{tabular}{cccccccc}
-    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
+    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
     \midrule    
-    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
-   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
-   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
+    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
+   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
+   3  & 4/29 & Chakra  & \textbf{Confirmed}   &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
-   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
-                       &  &                       &
+   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
+                       &  &
     JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
-   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
-   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
-   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
-   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
-   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
-   10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
-   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
-   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
-   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
-   14 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & \Fix{x} & JerryScript\\
-   15 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & \Fix{x} & JerryScript\\
+   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
+   6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
+   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
+   8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
+   9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
+   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
+   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
+   12 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
+   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
+   14 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & \Fix{x} & JerryScript\\
+   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & \Fix{x} & JerryScript\\
+   16 & 8/08  & V8 & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & \Fix{x} & JerryScript\\
+   15 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & \Fix{x} & JerryScript\\
    \bottomrule

### 2018-08-08 paper/paper.tex
updated severity

--- 2018-08-07 paper/paper.tex
@@
 
+\Igor{
+  JSC Severity doc \url{https://webkit.org/bug-prioritization/}
+  Chakra usa label para definir prioridades, porem neste doc nao ha explicacao das severidades
+  \url{https://github.com/Microsoft/ChakraCore/wiki/Label-Glossary}. Contudo, se clicar nessas 
+  labels vai direcionar para as issues e la pode-se ver a severidade de cada.
+  V8 guidelines \url{https://www.chromium.org/for-testers/bug-reporting-guidelines/chromium-bug-labels}
+}
+
 \begin{table*}[t]
@@
   \begin{tabular}{cccccccc}
-    \toprule Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
+    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
     \midrule    
-    1  & 4/18 & \crossmark & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & \Fix{x} & JerryScript      \\
-   2  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & \Fix{x} & Mozilla      \\
-   3  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & \Fix{x} & Mozilla \\
-   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{\Fix{x}} & \multirow{2}{*}{Mozilla}\\
-                       &  &                       &
+    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & JerryScript      \\
+   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & Mozilla      \\
+   3  & 4/29 & Chakra  & \textbf{Confirmed}   &
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & Mozilla \\
+   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{2} & \multirow{2}{*}{Mozilla}\\
+                       &  &
     JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
-   5 & 5/02 & \crossmark & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & \Fix{x} & Mozilla \\
-   6 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & \Fix{x} & \jsc{}\\
-   7 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & \Fix{x} & Mozilla\\
-   8 & 6/28 & \crossmark & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & \Fix{x} & \jsc{}\\
-   9 & 7/10 & \crossmark & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & \Fix{x} & JerryScript\\
-   10 & 7/18 & \crossmark & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & \Fix{x} & Mozilla\\
-   11 & 7/18 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & \Fix{x} & JerryScript\\
-   12 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & \Fix{x} & JerryScript\\
-   13 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & \Fix{x} & JerryScript\\
-   14 & 8/07 & \crossmark & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & \Fix{x} & JerryScript\\
-   15 & 8/07 & \crossmark & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & \Fix{x} & JerryScript\\
+   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & Mozilla \\
+   6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & 2 & \jsc{}\\
+   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & Mozilla\\
+   8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & 2 & \jsc{}\\
+   9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & 2 & JerryScript\\
+   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & Mozilla\\
+   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & JerryScript\\
+   12 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & - & JerryScript\\
+   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & JerryScript\\
+   14 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & - & JerryScript\\
+   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & JerryScript\\
+   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & JerryScript\\
+   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & JerryScript\\
    \bottomrule

### 2018-08-08 paper/paper.tex
updated table V

@@
     1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & JerryScript      \\
-   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & Mozilla      \\
+   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
    3  & 4/29 & Chakra  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & Mozilla \\
-   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{2} & \multirow{2}{*}{Mozilla}\\
+    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & \smonkey{} \\
+   \midrule
+    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                        &  &
-    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
-   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & Mozilla \\
+    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
+   \midrule
+   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
    6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & Mozilla\\
+   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & \smonkey{}\\
    8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & 2 & \jsc{}\\
    9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & 2 & JerryScript\\
-   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & Mozilla\\
+   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & \smonkey{}\\
    11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & JerryScript\\
@@
     Issue\#    & Date & Fuzz & Engine  & Status  &
-    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
+    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
     \midrule    
@@
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
-    & \Fix{x} & LO & WebKit \\ 
+    & 2 & LO & \jsc{} \\ 
     2  & 4/12 & radamsa & Chakra   & Rejected  &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
-    & \Fix{x} & HI & WebKit \\
+    & - & HI & \jsc{} \\
     3  & 4/14 & radamsa & JavascriptCore  & New &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
-    } & \Fix{x}  & HI & WebKit    \\
+    } & -  & HI & \jsc{}    \\
     4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
-    & \Fix{x} & HI & JerryScript   \\
+    & 2 & HI & JerryScript   \\
     5  & 4/29 & radamsa & JavascriptCore  & New  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & \Fix{x}  & HI  & JerryScript\\
+    } & -  & HI  & JerryScript\\
+    \midrule
     \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
@@
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
-    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
+    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                         &                        &        &
@@
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
-    & \Fix{x} &  & \\
+    & - &  & \\
+    \midrule
     7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
-    & \Fix{x} & LO & Mozilla \\
+    & 2 & LO & \smonkey{} \\
     8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
-    & \Fix{x} & HI & JerryScript \\
+    & 3 & HI & JerryScript \\
     9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
-    & \Fix{x} & HI & V8\\
+    & 2 & HI & \veight{}\\
     10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
-    & \Fix{x} & HI & Webkit\\
+    & 2 & HI & \jsc{}\\
     11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
-    & \Fix{x} & HI & JerryScript\\
+    & 2 & HI & JerryScript\\
     12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
-    & \Fix{x} & HI & JerryScript\\
+    & 2 & HI & JerryScript\\
     13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
     \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
-    & \Fix{x} & HI & JerryScript\\
+    & 2 & HI & JerryScript\\
    \bottomrule

### 2018-08-08 paper/paper.tex
pass on intro

@@
 languages around~\cite{business-insider,stackify}, with significant
-penetration in the segments of web development, mobile, and even for
-client and server coding for the Internet of
-Things~(IoT)~\cite{simply-technologies}.
-
-The interest of the community for the language encourages constant
-improvements in its specification and implementations.  It is natural
-to expect that language improvements entails sensible implementation
-changes. Even small changes can have high impact. For example, in
-October 2014 a new attribute added to Array objects caused a bug that
-resulted in the web app for the MS Outlook Calendar not working under
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
-bugs in JS engines is therefore an important problem given the range
-of applications that could be affected. It is also challenging as
-specifications evolve constantly and are incomplete. More
-specifically, the evolution of the \js\ specification makes it hard to
-assess if a test fails because of a bug or because of some missing
+penetration in various segments including, web development, mobile,
+and, more recently, the Internet of
+Things~(IoT)~\cite{simply-technologies}. The interest of the community
+for the language encourages constant improvements in its specification
+and implementations. It is natural to expect that such improvements
+lead to sensible implementation changes. Even small changes can have
+high impact. For example, in October 2014 a new attribute added to
+Array objects caused a bug in the MS Outlook Calendar web app under
+Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
+
+Finding bugs in \js\ engines is an important problem given the range
+of applications that could be affected with those bugs. It is also
+challenging as specifications are incomplete and evolve
+frequently. Consequently, it is often non-trivial to assess if a test
+fails because of a bug or because of some other reason. For example, a
+test may fail because the engine does not fully implement some
 feature. The publicly-available Kangax compatibility
-table~\cite{kangax} highlights this problem; it relates features with
-the engines that (partially) support them. For similar reason, one
-could misclassify a test failure as a bug when the failure could be,
-in fact, caused by some undefined behavior in the spec. To note that
-many of these cases exist as it can be observed by searching for
-``implementation-dependent'' in the ES6 spec
-document~\cite{ecmas262-spec}.
+table~\cite{kangax} highlights this problem--it relates features of
+\js\ with the engines that support them. As another example of a
+failure that is not caused by a bug, a test that passes in one engine
+could legitimately fail in another engines because of some undefined
+behavior in the spec\footnote{These cases of undefined behavior can be
+  localized by searching for the string ``implementation-dependent''
+  in the ES6 spec document~\cite{ecmas262-spec}.}.
+
+%% when a bug is found in some engine a test case is created and added to
+%% the regression suite. Those test inputs often check interesting
+%% scenarios that could reveal bugs in different engine
+%% implementations.
 
 %% WHAT WE DID
-This paper reports the results of a study we conducted to assess
-reliability of existing JS engines by leveraging implementation
-diversity in two orthogonal ways: test transplantation and
-cross-engine differential testing.  \emph{Test transplantation}
-evaluates the effects that running \js{} test files from a given
-engine have in detecting bugs in other engines. The intuition is that
-when a bug is found in some engine a test case is created and added to
-the regression suite. Those test inputs often check interesting
-scenarios that could reveal bugs in different engine
-implementations. \emph{Cross-engine differential testing} evaluates
-the bug-finding ability of fuzzing existing
-inputs~\cite{fuzz-testing-history} and then comparing the output
+The goal of this paper is to assess reliability of popular
+\js\ engines. The paper reports the results of a study that evaluates
+the effectiveness of two complementary diversity-aware techniques to
+find bugs in \js\ engines. \emph{Test transplantation} leverages
+diversity of test cases to find bugs. It evaluates the effects that
+running \js{} test files from a given engine have in detecting bugs in
+other engines. The intuition is that developers design test cases
+differently; hence replaying the test in a different engine may reveal
+unanticipated problems. \emph{Cross-engine differential testing}
+evaluates the ability of leveraging diversity of engine
+implementations to find bugs. More precisely, it fuzzes existing test
+inputs~\cite{fuzz-testing-history} and then compares the output
 produced by different engines using a differential oracle. One of
@@
 implementations to detect anomalous behavior. For example, Mozilla
-runs JS files--created with the grammar-based fuzzer
-jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
+runs JS files\footnote{These files are created with the grammar-based fuzzer
+  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
 SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
@@
 produced by \emph{different engines} on a fuzzed
-input~\cite{patra2016learning}. This approach has not been
-popularized, certainly because it is impractical to fully automate--a
+input~\cite{patra2016learning} as opposed to different builds of the
+same engine. This approach has not been
+popularized, certainly, because it is still not practical to fully automate--a
 number of legitimate reasons exist, other than a bug, for a test

### 2018-08-08 paper/paper.tex
pass on some sections

@@
 
-\section{Differential Testing Infrastructure}
-\label{sec:design}
-
-Figure~\ref{fig:workflow} illustrates the infrastructure we used for
-differential testing, use in part of our study. The bug-finding
-process takes on input JS files from regression test suites of various
-JS engines and generates warnings on output. Boxes in the figure
-denote encapsulation; arrowed lines indicate data flow. The cycle
-icons denote repetition--the leftmost icon indicates that each file in
-the input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
-\begin{figure}[h]
-  \centering
-%  \includegraphics[trim=20 350 200
-%    0,clip,width=0.35\textwidth]{google-awards-workflow}
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-\end{figure}
-
-The bug-finding process works as follows. New inputs are obtained for
-a given test input using some off-the-shelf input
-fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
-  have been proposed in the past, varying with respect to how new
-  inputs are
-  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
-Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
-The oracle checks whether or not the output produced for the fuzzed
-file is consistent across all engines. In case the test passes in all
-engines or fails in all engines (\ie{}, the output is consistent), the
-infrastructure discards the test. Otherwise, it considers the input as
-potentially fault-revealing; hence interesting for human
-inspection. Note that a number of reasons exist, other than a bug, to
-explain discrepancy (see Table~\ref{tab:false-positives}). We used the
-open-source eshost-cli project~\cite{eshost-cli}, also used at
-Microsoft, for checking output discrepancy.
-
-%The checker can produce multiple warnings for a given input.
-
-Recall that a warning can be manifested for reasons other than a bug
-and there is no clear way to distiguish those cases automatically (see
-Table~\ref{tab:false-positives}). A human needs to inspect the warning
-to diagnose the discrepancy. To facilitate inspection, the
-infrastructure prioritize these warnings and clusters them in
-groups. Considering prioritization, we classified warnings in two
-kinds, reflecting their likelihood to manifest a real bug. Warnings of
-the kind ``\hi{}'' are associated with the cases where the test code
-executed to completion without violating any internal checks but it
-violated assertions declared in the test itself or its harness. The
-rationale is that the input is valid--considering the checks declared
-in the API functions--but, still, it manifests discrepancy through
-violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
-in the ``\lo{}'' group reflect the cases where the anomaly was
-observed during the execution of functions not related to the test
-itself. We found that different engines often check pre-conditions of
-those functions differently. It can happen, for example, that one
-engine enforces a weaker pre-condition on a function input compared to
-another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
-observe a discrepancy that is more likely to be associated with an
-invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
-in the test code not the engine (library or runtime) code. Although we
-did find real bugs from ``\lo{}'' warnings, the proportion was much
-lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
-reals bugs we found originated from ``\lo{}'' warnings.
-
-\Mar{explain what is a bucket (we refer to it later).}
-
 \section{Objects of Study}
@@
 
+\subsubsection{Differential Testing Infrastructure}
+\label{sec:design}
+
+Figure~\ref{fig:workflow} illustrates the infrastructure we used for
+differential testing, use in part of our study. The bug-finding
+process takes on input JS files from regression test suites of various
+JS engines and generates warnings on output. Boxes in the figure
+denote encapsulation; arrowed lines indicate data flow. The cycle
+icons denote repetition--the leftmost icon indicates that each file in
+the input list will be analyzed in separate whereas the rightmost icon
+shows that a single file will be fuzzed multiple times.
+
+%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
+\begin{figure}[t!]
+  \centering
+%  \includegraphics[trim=20 350 200
+%    0,clip,width=0.35\textwidth]{google-awards-workflow}
+  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+\end{figure}
+
+The bug-finding process works as follows. New inputs are obtained for
+a given test input using some off-the-shelf input
+fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
+  have been proposed in the past, varying with respect to how new
+  inputs are
+  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
+Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+The oracle checks whether or not the output produced for the fuzzed
+file is consistent across all engines. In case the test passes in all
+engines or fails in all engines (\ie{}, the output is consistent), the
+infrastructure discards the test. Otherwise, it considers the input as
+potentially fault-revealing; hence interesting for human
+inspection. Note that a number of reasons exist, other than a bug, to
+explain discrepancy (see Table~\ref{tab:false-positives}). We used the
+open-source eshost-cli project~\cite{eshost-cli}, also used at
+Microsoft, for checking output discrepancy.
+
+%The checker can produce multiple warnings for a given input.
+
+Recall that a warning can be manifested for reasons other than a bug
+and there is no clear way to distiguish those cases automatically (see
+Table~\ref{tab:false-positives}). A human needs to inspect the warning
+to diagnose the discrepancy. To facilitate inspection, the
+infrastructure prioritize these warnings and clusters them in
+groups. Considering prioritization, we classified warnings in two
+kinds, reflecting their likelihood to manifest a real bug. Warnings of
+the kind ``\hi{}'' are associated with the cases where the test code
+executed to completion without violating any internal checks but it
+violated assertions declared in the test itself or its harness. The
+rationale is that the input is valid--considering the checks declared
+in the API functions--but, still, it manifests discrepancy through
+violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
+in the ``\lo{}'' group reflect the cases where the anomaly was
+observed during the execution of functions not related to the test
+itself. We found that different engines often check pre-conditions of
+those functions differently. It can happen, for example, that one
+engine enforces a weaker pre-condition on a function input compared to
+another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
+observe a discrepancy that is more likely to be associated with an
+invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
+in the test code not the engine (library or runtime) code. Although we
+did find real bugs from ``\lo{}'' warnings, the proportion was much
+lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
+reals bugs we found originated from ``\lo{}'' warnings.
+
+\Mar{explain what is a bucket (we refer to it later).}
+
 \section{Results}
@@
 false and true positives observed with test transplantation. The top
-piechart shows false alarms.  It is important to stress that all the
+piechart shows false alarms, which means that all
 ``transplanted'' tests should have passed in these cases. The absolute
 number of tests in each category is shown in parentheses to the
-right-side of the label of a slice, nameing the source of false
+right-side of each slice label, naming the source of false
 positive. The sources are as follows:
@@
   \item \textbf{Unknown.} This category corresponds to the cases we
-    were unable to confidently diagnose the failure.  \Igor{ We
-      observed that some tests are not valid due not corresponds to
-      the ES6 specifications, we skip these warnings.  }\Mar{Igor,
-      this is not well-formed english and I don't understand what you
-      want to say.}
+    were unable to confidently diagnose the failure.
 
@@
 
-In summary, we observed that \Fix{...elaborate...}
-
-Considering true positives, \Fix{...elaborate...}
+We observed that the sources of false positives were relatively
+uniformly distributed, with the categories ``Unknown'' and
+``Undefined'' holding more representation with \Fix{X and Y} reports,
+respectively. Considering the true positives, we found a reasonable
+number of duplicate reports, but not enough high to justify attempting
+to automate the detection of duplicates. Section~\ref{sec:bugs}
+exemplifies cases of false and true positives.
 
@@
 \end{figure}
-
-Figure~\ref{tab:test-transplantation-bugs} shows
-results. \Fix{...elaborate...}
-
-\Igor{
-  JSC Severity doc \url{https://webkit.org/bug-prioritization/}
-  Chakra usa label para definir prioridades, porem neste doc nao ha explicacao das severidades
-  \url{https://github.com/Microsoft/ChakraCore/wiki/Label-Glossary}. Contudo, se clicar nessas 
-  labels vai direcionar para as issues e la pode-se ver a severidade de cada.
-  V8 guidelines \url{https://www.chromium.org/for-testers/bug-reporting-guidelines/chromium-bug-labels}
-}
 
@@
 
+Figure~\ref{tab:test-transplantation-bugs} lists all bugs we found
+with test transplantation. The first column shows the identifier we
+assigned to the bug, column ``Date'' shows the date the bug was
+reported in the format ``m/dd'', column ``Engine'' shows the affected
+engine, column ``Status'' indicates the status of the bug report at
+the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
+''Fixed''), column ``Url'' shows the web address for the corresponding
+post in the bug tracking system where the discussion thread with
+engine developers can be found (de-anonymized upon request), column
+``Severity'' shows the severity level for confirmed bugs, and,
+finally, column ``Suite'' shows the name of the engine that originated
+the test. Considering severity levels, it is important to note that
+\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
+Chakra~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
+use only two. As usual, the smallest the severity value the highest
+the severity of the bug. We use a dash (``-'') as the severity level
+for bugs with pending confirmation.
+
+Of the \Fix{17} bugs we reported with test transplantation, \Fix{9}
+were analyzed and moved from the status ``New'' to ``Confirmed''
+(\ie{}, no bug we reported was rejected). Of these, \Fix{8} of them
+are severity-2 bugs.  \chakra{} was the engine with the highest number
+of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
+fixed. Considering the remaining engines, \veight{} confirmed one
+bug. Curiously, Google engineers confirmed that report in a few
+hours. Athough we did not find any showstopper critical bugs, most of
+the bugs are seemingly important as per the categorization given by
+engineers. Analyzing the issue tracker of \chakra, we found that
+severity-1 bugs are rare.
+
 \subsection{Cross-Engine Differential Testing}
 \label{sec:cross-engine-diff-testing-results}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
-  \caption{\label{fig:distribution}Distribution of lo and hi warnings
-   in buckets.}
-\end{figure}
 
@@
 next bucket.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
+  \caption{\label{fig:distribution}Distribution of lo and hi warnings
+   in buckets.}
+\end{figure}
 

### 2018-08-09 paper/paper.tex
pass on abstract and intro

@@
 \begin{abstract}
-JavaScript is a very popular programming language today. Checking
-reliability of JavaScript engines is therefore an important
-problem. This paper reports on a study to assess reliability of
-JavaScript engines by leveraging the rich diversity of open-source
-implementations. We explored two methods for that---test
+JavaScript is a very popular programming language today, permeating
+different domains of application. Several JavaScript engines compete
+for dominance and bugs on these engines are not rare. One important
+reason for that is the language specification, which is incomplete and
+evolves frequently.
+
+This paper reports on a study to assess reliability
+of JavaScript engines by leveraging the rich diversity of open-source
+implementations. For that, we explored two methods---test
 transplantation and cross-engine differential testing. Test
-transplatation evaluates the effects of running test suites of a given
+transplantation evaluates the effects of running test suites of a given
 engine in another engine. Cross-engine differential testing evaluates
 the effects of fuzzing existing inputs and then comparing the output
-produced by different engines with a differential oracle. Our results
-indicate that \Fix{...}
+produced by different engines with a differential oracle.
+
+Our results indicate that \Fix{...}
 \end{abstract}
@@
 lead to sensible implementation changes. Even small changes can have
-high impact. For example, in October 2014 a new attribute added to
-Array objects caused a bug in the MS Outlook Calendar web app under
+high practical impact. For example, in October 2014 a new attribute
+added to Array objects resulted in the MS Outlook Calendar web app
+stop working under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
+Intuitively, developing reliable engines is difficult because
+specifications are incomplete and evolve frequently.
 
 Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging as specifications are incomplete and evolve
-frequently. Consequently, it is often non-trivial to assess if a test
-fails because of a bug or because of some other reason. For example, a
-test may fail because the engine does not fully implement some
-feature. The publicly-available Kangax compatibility
-table~\cite{kangax} highlights this problem--it relates features of
-\js\ with the engines that support them. As another example of a
-failure that is not caused by a bug, a test that passes in one engine
-could legitimately fail in another engines because of some undefined
+of applications that could be affected with those
+bugs. It\Comment{Finding bugs in \js\ engines} is also
+challenging. For example, a test that passes in one engine could
+legitimately fail in a different engine because of some undefined
 behavior in the spec\footnote{These cases of undefined behavior can be
   localized by searching for the string ``implementation-dependent''
-  in the ES6 spec document~\cite{ecmas262-spec}.}.
+  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
+a test may fail because the engine does not fully implement some
+feature. The publicly-available Kangax compatibility
+table~\cite{kangax} relates features of \js\ with the engines that
+support them. To sum, it is often non-trivial to assess if a test
+fails because of a bug or because of some other reason making test
+automation more challenging.
 
@@
 \js\ engines. The paper reports the results of a study that evaluates
-the effectiveness of two complementary diversity-aware techniques to
-find bugs in \js\ engines. \emph{Test transplantation} leverages
+the effectiveness of two complementary diversity-aware testing techniques. \emph{Test transplantation} leverages
 diversity of test cases to find bugs. It evaluates the effects that
@@
   jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
-SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
+\smonkey{} engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
 across different configurations of the same build (\eg{}, enabling or
@@
     Google & \veight{} & \cite{v82018repo} & 9800+ \\
-%    JerryScript & JerryScript & \cite{jerryscript2018repo} & 3100+ \\
+%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
     Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
@@
 tests we found required a Node.js runtime~\cite{node} for
-execution. The main source of test cases is the offical
+execution. The main source of test cases is the official
 Test262~\cite{tc39-github} conformance test suite for the ECMA262
@@
     Duktape & \cite{duktape} & 921 \\ 
-    JerryScript & \cite{jerryscript} & 1,878 \\
+    \jerry{} & \cite{jerryscript} & 1,878 \\
     JSI & \cite{jsi} & 63 \\
     Tiny-js & \cite{tinyjs} & 37 \\    
-    % Chakra & \cite{chakracore} & 2632 \\
+    % \chakra{} & \cite{chakracore} & 2632 \\
     \midrule
@@
 
-% For example to run the JerryScript tests it was necessary 
+% For example to run the \jerry{} tests it was necessary 
 % use the unit-test package to run it, but with our changes we added the assertion
@@
 running those inputs in our infrastructure we were unable to find
-discrepancies. Inpecting those inputs, we realized that they reflected
+discrepancies. Inspecting those inputs, we realized that they reflected
 very simple scenarios. To sum, a high percentage of inputs that
@@
 that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the SpiderMonkey
+that use functions that are only available in the \smonkey{}
 engine. We would need either to mock those functions in other engines
@@
 versions of the program under testing with the typical goal of finding
-univeral errors like crashes and buffer overflows. The instrumentation
+universal errors like crashes and buffer overflows. The instrumentation
 adds code to collect branch coverage and to monitor specific
@@
 fuzzers require no instrumentation and domain-knowledge. They mutate
-\emph{existing} inputs randomly. The strenght of the approach is
+\emph{existing} inputs randomly. The strength of the approach is
 limited by the quality of the test suite and the supported mutation
@@
 
-\subsubsection{Differential Testing Infrastructure}
+\section{Differential Testing Infrastructure}
 \label{sec:design}
@@
 Recall that a warning can be manifested for reasons other than a bug
-and there is no clear way to distiguish those cases automatically (see
+and there is no clear way to distinguish those cases automatically (see
 Table~\ref{tab:false-positives}). A human needs to inspect the warning
@@
 in the API functions--but, still, it manifests discrepancy through
-violation of an assertion declared in the test.\Mar{example!} In constrast, warnings
+violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
 in the ``\lo{}'' group reflect the cases where the anomaly was
@@
 bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale is that even black-box fuzzers that typicaly make valid
+rationale is that even black-box fuzzers that typically make valid
 changes only in literals of the language could expose important
@@
 instead\Mar{, which updates tests regularly?}. To sum, we observed
-that \Fix{...} \Mar{justify regressions using the kangax report}
+that \Fix{...} \Mar{justify regressions using the Kangax report}
 
@@
 
-This section reports the results of test transplantion, \ie{}, we
+This section reports the results of test transplantation, \ie{}, we
 analyzed the failures observed when running a test suite on an engine
@@
     Duktape & 0 & 4 & 4 & 1   \\
-    JerryScript & 23 & 25 & 22 & 23   \\
+    \jerry{} & 23 & 25 & 22 & 23   \\
     JSI & 0 & 0 & 0 & 0   \\
@@
     %%   only the \jsc{} supports tail-call optimization and the testcase 
-    %%   passes without failures. Another case can be found in JerryScript suite
+    %%   passes without failures. Another case can be found in \jerry{} suite
     %%   that uses a repetition statement to concatenate long strings 
@@
     part of the official spec, but is not implemented in the target
-    engine. For example, at the time of writing, Chakra does not
+    engine. For example, at the time of writing, \chakra{} does not
     implement by default various properties from the \mcodeid{Symbol}
@@
     \midrule    
-    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & JerryScript      \\
-   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
-   3  & 4/29 & Chakra  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & \smonkey{} \\
-   \midrule
-    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
+    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
+   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
+   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
+   \midrule
+    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                        &  &
@@
    5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
-   6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & \smonkey{}\\
-   8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & 2 & \jsc{}\\
-   9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & 2 & JerryScript\\
-   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & \smonkey{}\\
-   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & JerryScript\\
-   12 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & - & JerryScript\\
-   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & JerryScript\\
-   14 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & - & JerryScript\\
-   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & JerryScript\\
-   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & JerryScript\\
-   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & JerryScript\\
+   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
+   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
+   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
+   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
+   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
+   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
+   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
+   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
+   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
+   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
+   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
    \bottomrule
@@
 \jsc{} uses five different severity levels~\cite{jsc-severity} whereas
-Chakra~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
+\chakra{}~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
 use only two. As usual, the smallest the severity value the highest
@@
 bug. Curiously, Google engineers confirmed that report in a few
-hours. Athough we did not find any showstopper critical bugs, most of
+hours. Although we did not find any showstopper critical bugs, most of
 the bugs are seemingly important as per the categorization given by
@@
 manifested the potential problem and explaining the reasons we were
-suspicious. In some cases, we used the Mozila lithium
+suspicious. In some cases, we used the Mozilla lithium
 tool~\cite{lithium} to minimize the test case. For the cases of false
@@
     \midrule    
-    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
+    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
     & 2 & LO & \jsc{} \\ 
-    2  & 4/12 & radamsa & Chakra   & Rejected  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
+    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
     & - & HI & \jsc{} \\
@@
     } & -  & HI & \jsc{}    \\
-    4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
-    & 2 & HI & JerryScript   \\
+    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
+    & 2 & HI & \jerry{}   \\
     5  & 4/29 & radamsa & JavascriptCore  & New  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & -  & HI  & JerryScript\\
+    } & -  & HI  & \jerry{}\\
     \midrule
     \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
-    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
+    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
     & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
@@
     & 2 & LO & \smonkey{} \\
-    8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
-    & 3 & HI & JerryScript \\
-    9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
+    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
+    & 3 & HI & \jerry{} \\
+    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
     & 2 & HI & \veight{}\\
@@
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
-    & 2 & HI & JerryScript\\
-    12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
+    & 2 & HI & \jerry{}\\
+    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
-    & 2 & HI & JerryScript\\
-    13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
-    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
-    & 2 & HI & JerryScript\\
+    & 2 & HI & \jerry{}\\
+    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
+    & 2 & HI & \jerry{}\\
    \bottomrule
@@
 reports still waiting for confirmation are associated with the
-JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
+\jsc{} engine (JSC). A closer look at the JSC issue tracker
 showed that the triage process is very slow for that engine. 
 \Igor{
-The bugs reported on Chakra's bug tracker was defined as confirmed, 
+The bugs reported on \chakra{}'s bug tracker was defined as confirmed, 
 however the bugs are included on a milestone for the next release
@@
 }
-As of now, we did not find any new bug on SpiderMonkey and V8; 
+As of now, we did not find any new bug on \smonkey{} and V8; 
 the bugs we found were duplicates and were not reported. Finally, it is
@@
   ``\textbackslash{}x00''\}\} assert(+a === 0)\}} 
-manifested a bug in the \js{} engine Chakra.  The object
+manifested a bug in the \js{} engine \chakra{}.  The object
 property \CodeIn{valueOf} stores a function that returns a primitive
@@
 that converts a string to a number, otherwise the operation returns
-NaN (Not a Number)\cite{unary-plus}. For this case, Chakra evaluates
+NaN (Not a Number)\cite{unary-plus}. For this case, \chakra{} evaluates
 the unary plus to NaN as expected, as the null character cannot be
-converted. As result, the test fails as expected. Chakra, in contrast,
+converted. As result, the test fails as expected. \chakra{}, in contrast,
 incorrectly converts the string to zero, making the test to pass. All
 other engines fail on this test. As Table~\ref{tab:bugs} shows, the
-Chakra team fixed the issue soon after we reported the problem.
+\chakra{} team fixed the issue soon after we reported the problem.
 
@@
 initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
-integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
+integer 3 to a big integer number. We reported this case in \chakra{} due a core dumps that occurs
 during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
@@
 % \Igor{For example, a bug caught by our environment and reported as LO priority was reported 
-% on Chakra engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
+% on \chakra{} engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
 % this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
@@
 % it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
-% only Chakra engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
+% only \chakra{} engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
 % the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
@@
 
-%%  LocalWords:  bytecodes JScript Ecma ome
+%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
+%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU
+%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
+%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
+%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
+%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
+%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC
+%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii
+%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
+%%  LocalWords:  SSL TLS ICSE

### 2018-08-09 paper/paper.tex
update seeds table

@@
     from engines we analyzed, and suites from other engines.}
-  \begin{tabular}{ccr}
+  \begin{tabular}{ccrc}
     \toprule
-    Name & Source & \# JS files \\
-    \midrule
-    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 \\
-    \midrule
-    \jsc{} & \cite{webkit} & 1,021 \\
-    \smonkey\ & \cite{mozilla} & 2,116 \\
-    \veight{} & \cite{v8} & 57 \\
-    \midrule    
-    Duktape & \cite{duktape} & 921 \\ 
-    \jerry{} & \cite{jerryscript} & 1,878 \\
-    JSI & \cite{jsi} & 63 \\
-    Tiny-js & \cite{tinyjs} & 37 \\    
+    Name & Source & \# JS files & \# JS files final \\
+    \midrule
+    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 & 29,846\\
+    \midrule
+    \jsc{} & \cite{webkit} & 1,031 & 1,021 \\
+    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 \\
+    \veight{} & \cite{v8} & 75 & 57 \\
+    \midrule    
+    Duktape & \cite{duktape} & 1,195 & 921\\ 
+    \jerry{} & \cite{jerryscript} & 1,951 & 1,878\\
+    JSI & \cite{jsi} & 99 & 63 \\
+    Tiny-js & \cite{tinyjs} & 49 & 37 \\    
     % \chakra{} & \cite{chakracore} & 2632 \\
     \midrule
-     &  & \totalTestFiles{} \\
+     &  & \totalTestFiles{} & \totalTestFilesFilter{} \\
    \bottomrule     
@@
    14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
+   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
    16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\

### 2018-08-09 paper/paper.tex
explaining test cases

@@
   \centering
-  \caption{\label{tab:engines}Engines Analyzed.}
+  \caption{\label{tab:engines}Engines analyzed.}
   \begin{tabular}{cccr}
@@
 four other engines. Table~\ref{tab:test-suites} shows the breakdown of
-tests we considered. Overall, we found a total of \totfiles{} JS
-files. We did not consider tests from the \chakra{} repository because
-they depend on non-portable objects. Notice that the number of tests
-in \veight\ is low. That happens because many tests in \veight{} are
+tests we considered. Column ``original'' shows the test cases for each
+test suite. Overall, we found a total of \totfiles{} JS files. We did
+not consider tests from the \chakra{} repository because they depend
+on non-portable objects. Notice that the number of tests in
+\veight\ is low. That happens because many tests in \veight{} are
 inherited from Mozilla and \jsc{}; we discarded those to avoid
-repetition and to give credit where it is due. For all engines engines
-we found test using non-portable functions that we detected by running
-the test on a different engine. We needed to discard those.
+repetition and to give credit where it is due. Column
+``compile-in-all'' shows the number of test cases for which all four
+engines we analyzed do not throw compile-time error. We discarded
+tests that manifest compile errors as they clearly indicate missing
+features; these tests use non-portable names (\eg{}, \jsc{}'s
+\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
+or use functions that, although being part of the spec, not all
+engines currently support. Finally, column ``no-fail-in-all'' shows
+the tests for which all engines
+pass. Section~\ref{sec:transplantation} discusses these failures, some
+of which are indicative of bugs. The tests under this column will be
+used to create new, potentially fault-revealing, tests. For that, it
+is important to assure that all of them pass.
 
@@
 
+ %% The table shows the
+ %%    number of test cases in each test suite considered: TC-39
+ %%    conformance test suite, suites from engines we analyzed, and
+ %%    suites from other engines.
+
 \begin{table}[t]
   \centering
-  \caption{\label{tab:test-suites}Test Suites. The sections of the
-    table show, respectively, the TC-39 conformance test suite, suites
-    from engines we analyzed, and suites from other engines.}
-  \begin{tabular}{ccrc}
+  \caption{\label{tab:test-suites}Number of test cases per
+    suite. Column ``original'' shows the original size of the test
+    suite, column ``compile-in-all'' shows the number of test cases
+    for which engines do not throw compile error (\eg{}, undefined
+    name), and column ``no-fail-all'' shows the number of test cases
+    that pass in all four engines we analyzed.}
+  \begin{tabular}{ccrrr}
     \toprule
-    Name & Source & \# JS files & \# JS files final \\
-    \midrule
-    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 & 29,846\\
-    \midrule
-    \jsc{} & \cite{webkit} & 1,031 & 1,021 \\
-    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 \\
-    \veight{} & \cite{v8} & 75 & 57 \\
-    \midrule    
-    Duktape & \cite{duktape} & 1,195 & 921\\ 
-    \jerry{} & \cite{jerryscript} & 1,951 & 1,878\\
-    JSI & \cite{jsi} & 99 & 63 \\
-    Tiny-js & \cite{tinyjs} & 49 & 37 \\    
+    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
+    \multicolumn{3}{c}{\# JS files} \\
+    \cline{3-5}
+                               &         & original & compile-in-all &  no-fail-in-all \\
+    \midrule
+    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
+    29,846 & - \\
+    \midrule
+    \jsc{} & \cite{webkit} & 1,031 & 1,021 & -\\
+    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & -\\
+    \veight{} & \cite{v8} & 75 & 57 & -\\
+    \midrule    
+    Duktape & \cite{duktape} & 1,195 & 921 & -\\ 
+    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & -\\
+    JSI & \cite{jsi} & 99 & 63 & -\\
+    Tiny-js & \cite{tinyjs} & 49 & 37 & -\\    
     % \chakra{} & \cite{chakracore} & 2632 \\
     \midrule
-     &  & \totalTestFiles{} & \totalTestFilesFilter{} \\
+     &  & \totalTestFiles{} & \totalTestFilesFilter{} & -\\
    \bottomrule     
@@
 
+\Mar{remember to say that we use dataset Table II''compile-in-all''.}
+
 This section reports the results of test transplantation, \ie{}, we

### 2018-08-09 paper/paper.tex
updated Table II
updated table III
minor fix

@@
 \item Released latest version after Jan 1, 2018
-\item Contains more than 1K starts, if on GitHub  
+\item Contains more than 1K stars on GitHub  
 \item Uses a public issue tracker
@@
     TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
-    29,846 & - \\
-    \midrule
-    \jsc{} & \cite{webkit} & 1,031 & 1,021 & -\\
-    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & -\\
-    \veight{} & \cite{v8} & 75 & 57 & -\\
-    \midrule    
-    Duktape & \cite{duktape} & 1,195 & 921 & -\\ 
-    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & -\\
-    JSI & \cite{jsi} & 99 & 63 & -\\
-    Tiny-js & \cite{tinyjs} & 49 & 37 & -\\    
+    29,846 & 18,943 \\
+    \midrule
+    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
+    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
+    \veight{} & \cite{v8} & 75 & 57 & 57\\
+    \midrule
+    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
+    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
+    JSI & \cite{jsi} & 99 & 63 & 63\\
+    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
     % \chakra{} & \cite{chakracore} & 2632 \\
     \midrule
-     &  & \totalTestFiles{} & \totalTestFilesFilter{} & -\\
+     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
    \bottomrule 
@@
     \midrule
-    \jsc{} & - & - & - & - & - & - & - \\
-    \veight{} & - & - & - & - & - & - & - \\
-    \chakra{} & - & - & - & - & - & - & - \\
-    \smonkey{} & - & - & - & - & - & - & - \\
+    \jsc{} & 4330 & 4330 & 4330 & - & - & - & - \\
+    \veight{} & 3404 & 3404 & 3401 & - & - & - & - \\
+    \chakra{} & 9104 & 9104 & 9104 & - & - & - & - \\
+    \smonkey{} & 3943 & 3943 & 3943 & - & - & - & - \\
     \bottomrule 

### 2018-08-10 paper/paper.tex
pass on prio and clusterization

@@
 four other engines. Table~\ref{tab:test-suites} shows the breakdown of
-tests we considered. Column ``original'' shows the test cases for each
-test suite. Overall, we found a total of \totfiles{} JS files. We did
-not consider tests from the \chakra{} repository because they depend
-on non-portable objects. Notice that the number of tests in
+tests we considered. Overall, we found a total of \totfiles{} JS
+files. Column ``original'' shows the test cases for each
+test suite. We did not consider tests from the \chakra{} repository because they depend
+on non-portable objects and notice that the number of tests in
 \veight\ is low. That happens because many tests in \veight{} are
@@
 
-Figure~\ref{fig:workflow} illustrates the infrastructure we used for
-differential testing, use in part of our study. The bug-finding
-process takes on input JS files from regression test suites of various
-JS engines and generates warnings on output. Boxes in the figure
-denote encapsulation; arrowed lines indicate data flow. The cycle
-icons denote repetition--the leftmost icon indicates that each file in
-the input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
 %\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
@@
 
+Figure~\ref{fig:workflow} illustrates the infrastructure for
+differential testing, which is used in part of this study. It takes on
+input a list of JS files and generates warnings on output. Boxes in
+the figure denote encapsulation, arrowed lines denote data flow, and
+the cycle icons denote repetition--the leftmost icon indicates that
+each file in the input list will be analyzed in separate whereas the
+rightmost icon shows that a single file will be fuzzed multiple times.
 The bug-finding process works as follows. New inputs are obtained for
@@
 infrastructure prioritize these warnings and clusters them in
-groups. Considering prioritization, we classified warnings in two
-kinds, reflecting their likelihood to manifest a real bug. Warnings of
-the kind ``\hi{}'' are associated with the cases where the test code
+groups.
+
+\subsection{Prioritization}
+
+Considering prioritization, we classified warnings in two kinds,
+reflecting their likelihood to manifest a real bug. Warnings of the
+kind ``\hi{}'' are associated with the cases where the test code
 executed to completion without violating any internal checks but it
 violated assertions declared in the test itself or its harness. The
-rationale is that the input is valid--considering the checks declared
-in the API functions--but, still, it manifests discrepancy through
-violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
-in the ``\lo{}'' group reflect the cases where the anomaly was
-observed during the execution of functions not related to the test
-itself. We found that different engines often check pre-conditions of
-those functions differently. It can happen, for example, that one
-engine enforces a weaker pre-condition on a function input compared to
-another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
-observe a discrepancy that is more likely to be associated with an
-invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
-in the test code not the engine (library or runtime) code. Although we
-did find real bugs from ``\lo{}'' warnings, the proportion was much
-lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
-reals bugs we found originated from ``\lo{}'' warnings.
+rationale is that the input is more likely to be valid as it it did
+not raise exceptions during the execution of the application code,
+but, it manifests discrepancy through violation of an assertion
+declared in the test. In contrast, warnings in the ``\lo{}'' group are
+more likely to be asssociated with invalid inputs. They reflect the
+cases where the anomaly is observed during the execution of functions
+not related to the test itself. We found that different engines often
+check pre-conditions of those functions differently. It can happen,
+for example, that one engine enforces a weaker pre-condition on a
+function input compared to another engine and that is acceptable. In
+those cases, the infrastructure would observe a discrepancy that is
+more likely to be associated with an invalid input produced by the
+fuzzer, \ie{}, it is likely to be a bug in the test code not the
+engine (library or runtime) code. Although we did find real bugs from
+``\lo{}'' warnings, the proportion was much lower compared to
+``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
+found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
+  explain why LO can still be a bug.}
+
+\subsection{Clusterization}
 
 \Mar{explain what is a bucket (we refer to it later).}
+
+Figure~\ref{fig:err-messages} shows the error messages produced by a
+\lo warning. Note that all message appear to be related to the same
+problem.
+
+\begin{figure}[h]
+\begin{tabular}{ll}
+\veight{} & ``Unexpected end of input''\\
+\jsc{} & ``Unexpected end of script''\\
+\smonkey{} & ``Expected expression, got end of script''
+\end{tabular}
+\caption{\label{fig:err-messages}Example error messages associated
+  with a \lo{} warning. In this case, the test passes in \chakra.}
+\end{figure}
 

### 2018-08-10 paper/paper.tex
polishing prioritization

@@
 potentially fault-revealing; hence interesting for human
-inspection. Note that a number of reasons exist, other than a bug, to
-explain discrepancy (see Table~\ref{tab:false-positives}). We used the
-open-source eshost-cli project~\cite{eshost-cli}, also used at
+inspection. The infrastructure uses the
+open-source tool eshost-cli~\cite{eshost-cli}, also used at
 Microsoft, for checking output discrepancy.
@@
 
-Recall that a warning can be manifested for reasons other than a bug
-and there is no clear way to distinguish those cases automatically (see
-Table~\ref{tab:false-positives}). A human needs to inspect the warning
-to diagnose the discrepancy. To facilitate inspection, the
-infrastructure prioritize these warnings and clusters them in
-groups.
+Note that a number of reasons exist, other than a bug, to explain
+discrepancy (see Table~\ref{tab:false-positives}) and there is no
+clear way to distinguish false and true positives automatically. As
+such, a human needs to inspect the warning to classify the issue. To
+facilitate inspection, we prioritized warnings and clustered them in
+groups. We describe these strategies in the following.
 
@@
 Considering prioritization, we classified warnings in two kinds,
-reflecting their likelihood to manifest a real bug. Warnings of the
+reflecting their likelihood of manifesting a real bug. Warnings of the
 kind ``\hi{}'' are associated with the cases where the test code
-executed to completion without violating any internal checks but it
+executed to completion without violating any internal checks, but it
 violated assertions declared in the test itself or its harness. The
@@
 more likely to be asssociated with invalid inputs. They reflect the
-cases where the anomaly is observed during the execution of functions
-not related to the test itself. We found that different engines often
+cases where the anomaly is observed during the execution of functions,
+which are part of the application. We found that different engines often
 check pre-conditions of those functions differently. It can happen,
 for example, that one engine enforces a weaker pre-condition on a
-function input compared to another engine and that is acceptable. In
+function input compared to another engine and that is acceptable. For
+instance, it is acceptable to pass values greater than \Fix{x} to
+function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}. In
 those cases, the infrastructure would observe a discrepancy that is

### 2018-08-10 paper/paper.tex
pass on tables

--- 2018-08-09 paper/paper.tex
@@
 \item Released latest version after Jan 1, 2018
-\item Contains more than 1K stars on GitHub  
+\item Contains more than 1K starts, if on GitHub  
 \item Uses a public issue tracker
@@
    12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
+   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
    14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
    15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
-   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
    17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\

### 2018-08-10 paper/paper.tex
fixes

@@
 reals bugs we found originated from ``\lo{}'' warnings.
+\Igor{
+  Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
+  casos reportados como LO tambem podem ser considerados como um true positive.
+  Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
+  se um teste falha antes da linha em que ha uma assercao, entao a falha
+  ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
+  possivel observar um caso de bug obtido em um bucket classificado como LO.
+  Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
+  posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
+  maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
+  de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
+  lancar Offset is outside the bounds.
+
+  Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
+  Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
+  correto seria usar um levantar um erro
+}
+
+\begin{figure}[!h]
+  \centering
+  \begin{lstlisting}
+    var buffer = new ArrayBuffer(64);
+    var view = new DataView(buffer);
+    view.setInt8(0,0x80);
+    assert(view.getInt8(-1770523502845470856) === -0x80);
+
+    Outputs:
+    #### V8
+    RangeError: Offset is outside the bounds of the DataView
+    #### Chakra
+    RangeError: DataView operation access beyond specified buffer length
+    #### SpiderMonkey
+    RangeError: invalid or out-of-range index
+    #### JavaScriptCore
+    RangeError: byteOffset cannot be negative
+  \end{lstlisting}
+  \caption{\label{fig:lo-truepositive}True positive example in LO warnings.}
+\end{figure}
 

### 2018-08-10 paper/paper.tex

--- 2018-08-10 paper/paper.tex
@@
 
+\Igor{
+  Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
+  casos reportados como LO tambem podem ser considerados como um true positive.
+  Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
+  se um teste falha antes da linha em que ha uma assercao, entao a falha
+  ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
+  possivel observar um caso de bug obtido em um bucket classificado como LO.
+  Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
+  posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
+  maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
+  de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
+  lancar Offset is outside the bounds.
+
+  Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
+  Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
+  correto seria usar um levantar um erro
+}
+
+\begin{figure}[!h]
+  \centering
+  \begin{lstlisting}
+    var buffer = new ArrayBuffer(64);
+    var view = new DataView(buffer);
+    view.setInt8(0,0x80);
+    assert(view.getInt8(-1770523502845470856) === -0x80);
+
+    Outputs:
+    #### V8
+    RangeError: Offset is outside the bounds of the DataView
+    #### Chakra
+    RangeError: DataView operation access beyond specified buffer length
+    #### SpiderMonkey
+    RangeError: invalid or out-of-range index
+    #### JavaScriptCore
+    RangeError: byteOffset cannot be negative
+  \end{lstlisting}
+  \caption{\label{fig:lo-truepositive}True positive example in LO warnings.}
+\end{figure}
+
 \section{Results}

### 2018-08-10 paper/paper.tex
incorporating Igor's explanation

@@
 cases where the anomaly is observed during the execution of functions,
-which are part of the application. We found that different engines often
-check pre-conditions of those functions differently. It can happen,
-for example, that one engine enforces a weaker pre-condition on a
-function input compared to another engine and that is acceptable. For
-instance, it is acceptable to pass values greater than \Fix{x} to
-function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}. In
-those cases, the infrastructure would observe a discrepancy that is
-more likely to be associated with an invalid input produced by the
-fuzzer, \ie{}, it is likely to be a bug in the test code not the
-engine (library or runtime) code. Although we did find real bugs from
-``\lo{}'' warnings, the proportion was much lower compared to
-``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
-found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
-  explain why LO can still be a bug.}
+which are part of the application. We found that different engines
+often check pre-conditions of those functions differently. It can
+happen, for example, that one engine enforces a weaker pre-condition
+on a function input compared to another engine and that is
+acceptable. For instance, it is acceptable to pass values greater than
+\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
+\Fix{z}. In those cases, the infrastructure would observe a
+discrepancy that is more likely to be associated with an invalid input
+produced by the fuzzer, \ie{}, it is likely to be a bug in the test
+code not the engine (library or runtime) code. It is worth noting that
+``\lo'' warnings can be bug
+revealing. Figure~\ref{fig:lo-truepositive} shows one of these
+cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
+object and stores an 8-bit integer at the 0 position. According to the
+specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
+exception should be thrown if a negative value is passed to the
+function \CodeIn{ToIndex}, indirectly called by the test case. In this
+case, however, the \chakra{} engine did not throw any exception, which
+violates the spec. This bug was fixed by developers after our bug
+report and is no longer present in the most recent release of
+\chakra. Despite that counter-example, most bugs we found emerged from
+``\hi{}'' warnings.
+
+%% \Igor{
+%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
+%%   casos reportados como LO tambem podem ser considerados como um true positive.
+%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
+%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
+%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
+%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
+%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
+%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
+%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
+%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
+%%   lancar Offset is outside the bounds.
+
+%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
+%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
+%%   correto seria usar um levantar um erro
+%% }
 
@@
 
-\begin{figure}[h]
-\begin{tabular}{ll}
-\veight{} & ``Unexpected end of input''\\
-\jsc{} & ``Unexpected end of script''\\
-\smonkey{} & ``Expected expression, got end of script''
-\end{tabular}
-\caption{\label{fig:err-messages}Example error messages associated
-  with a \lo{} warning. In this case, the test passes in \chakra.}
-\end{figure}
-
-\Igor{
-  Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
-  casos reportados como LO tambem podem ser considerados como um true positive.
-  Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
-  se um teste falha antes da linha em que ha uma assercao, entao a falha
-  ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
-  possivel observar um caso de bug obtido em um bucket classificado como LO.
-  Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
-  posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
-  maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
-  de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
-  lancar Offset is outside the bounds.
-
-  Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
-  Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
-  correto seria usar um levantar um erro
-}
+%% \begin{figure}[h]
+%% \begin{tabular}{ll}
+%% \veight{} & ``Unexpected end of input''\\
+%% \jsc{} & ``Unexpected end of script''\\
+%% \smonkey{} & ``Expected expression, got end of script''
+%% \end{tabular}
+%% \caption{\label{fig:err-messages}Example error messages associated
+%%   with a \lo{} warning. In this case, the test passes in \chakra.}
+%% \end{figure}
 
@@
 
-    Outputs:
-    #### V8
-    RangeError: Offset is outside the bounds of the DataView
-    #### Chakra
-    RangeError: DataView operation access beyond specified buffer length
-    #### SpiderMonkey
-    RangeError: invalid or out-of-range index
-    #### JavaScriptCore
-    RangeError: byteOffset cannot be negative
+Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
+1. RangeError: Offset is outside the bounds of the DataView
+2. RangeError: byteOffset cannot be negative
+3. RangeError: invalid or out-of-range index
   \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}True positive example in LO warnings.}
+  \caption{\label{fig:lo-truepositive}True positive example of LO
+    warnings.}
 \end{figure}

### 2018-08-10 paper/paper.tex
pass on clusterization

@@
 
-\Mar{explain what is a bucket (we refer to it later).}
-
-Figure~\ref{fig:err-messages} shows the error messages produced by a
-\lo warning. Note that all message appear to be related to the same
-problem.
-
-%% \begin{figure}[h]
-%% \begin{tabular}{ll}
-%% \veight{} & ``Unexpected end of input''\\
-%% \jsc{} & ``Unexpected end of script''\\
-%% \smonkey{} & ``Expected expression, got end of script''
-%% \end{tabular}
-%% \caption{\label{fig:err-messages}Example error messages associated
-%%   with a \lo{} warning. In this case, the test passes in \chakra.}
-%% \end{figure}
+Clusterization helps to group tests that fail for similar reasons. We
+only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
+that arise from the test case, which are typically
+distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
+error messages produced by a ``\lo'' warning. Any warning, including
+this one, that has this same message signature will be included in the
+same cluster, which we may also refer as a ``bucket''.
 
@@
   \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}True positive example of LO
-    warnings.}
+  \caption{\label{fig:lo-truepositive}True positive example of a ``\lo''
+    warning.}
 \end{figure}

### 2018-08-10 paper/paper.tex
updated table bugs found

@@
    12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & \jerry{}\\
+   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
    14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & \jerry{}\\
+   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
    16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
@@
     & 2 & HI & \jerry{}   \\
-    5  & 4/29 & radamsa & JavascriptCore  & New  &
+    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & -  & HI  & \jerry{}\\
+    } & 2  & HI  & \jerry{}\\
     \midrule

### 2018-08-14 paper/paper.tex
minor change in IV.A (prioritization)

@@
 
-Considering prioritization, we classified warnings in two kinds,
+We classified warnings in two types,
 reflecting their likelihood of manifesting a real bug. Warnings of the
@@
 not raise exceptions during the execution of the application code,
-but, it manifests discrepancy through violation of an assertion
-declared in the test. In contrast, warnings in the ``\lo{}'' group are
+but, it manifested discrepancy through the violation of an assertion
+declared in the test. In contrast, warnings of type ``\lo{}'' are
 more likely to be asssociated with invalid inputs. They reflect the
@@
 on a function input compared to another engine and that is
-acceptable. For instance, it is acceptable to pass values greater than
+acceptable.\Comment{ For instance, it is acceptable to pass values greater than
 \Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
-\Fix{z}. In those cases, the infrastructure would observe a
+\Fix{z}.} In those cases, the infrastructure would observe a
 discrepancy that is more likely to be associated with an invalid input
 produced by the fuzzer, \ie{}, it is likely to be a bug in the test
-code not the engine (library or runtime) code. It is worth noting that
-``\lo'' warnings can be bug
-revealing. Figure~\ref{fig:lo-truepositive} shows one of these
+code not the engine (library or runtime) code. However, as expected, our heuristic
+is not precise---``\lo'' warnings can 
+reveal bugs. Figure~\ref{fig:lo-truepositive} shows one of these
 cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
@@
 case, however, the \chakra{} engine did not throw any exception, which
-violates the spec. This bug was fixed by developers after our bug
+violates the spec. This case of undocumented precondition, reported
+and handled by developers as a bug, was fixed by developers after our bug
 report and is no longer present in the most recent release of
-\chakra. Despite that counter-example, most bugs we found emerged from
+\chakra. Despite that case, most bugs we found emerged from
 ``\hi{}'' warnings.

### 2018-08-14 paper/paper.tex
pass

@@
 
-\Fix{The
-  closest work to ours was done by Patra and Pradel~\cite{patra2016learning},
-  where they evaluated their proposed language-agnostic fuzzer to find
-  cross-browser HTML+JS discrepancies. This project aims at building
-  and evaluating an infrastructure for differential testing of runtime
-  engines, such as the JS engine or WebAssembly's. The sensible parts
-  of the infrastructure are the checks of input validity (as to reduce
-  waste/cost) and output correctness (as to reduce false positives).}
-
-RFC-Directed Differential Testing of Certificate Validation in SSL/TLS Implementations...[ICSE18]
+\subsection{Testing \js{} Engines}
+\label{sec:testing-js-engines}
+The closest work to ours was done by Patra and
+Pradel~\cite{patra2016learning}, where they proposed a
+language-agnostic fuzzer to find cross-browser HTML+JS
+discrepancies. Their work aims at building and evaluating an
+infrastructure for differential testing of runtime engines, such as JS
+engines nd WebAssembly engines. The sensible parts of the
+infrastructure are the checks of input validity (as to reduce
+waste/cost) and output correctness (as to reduce false
+positives). Patra and Pradel work differs from ours in that their main
+contribution is analytical whereas our main contribution is
+empirical--we aim at assessing reliability of \js\ engines and find
+bugs on them using simple approaches, such as test transplantation.
+
+Several fuzzing techniques have been proposed recently\Fix{...elaborate...}
+
+\subsection{Differential Testing}
+Several different applications of differential testing have been
+proposed in recent years. Chen and
+colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
+technique to generate X.509 certificates based on Request For
+Proposals (RFC) as specification with the goal of detecting bugs in
+different SSL/TLS implementations. Those bugs can comprimise security
+of servers which rely on these certificates to properly authenticate
+the parties involved in a communication session. Lidbury and
+colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
+colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
+focusing on finding bugs in programs for graphic cards (\eg{},
+OpenCL). These programs use the Single-Instruction Multiple-Data
+(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
+application of differential testing that received most attention to
+date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
+the use of a generator of sentences from grammars to test correctness
+of automatically generated parsers. After that, significant progress
+has been made. Yang and
+colleagues~\cite{Yang:2011:FUB:1993498.1993532} have proposed CSmith
+to randomly create C programs from a grammar, for a subset of C, and
+then check the output of these programs in different compilers (\eg{},
+GCC and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
+proposed the idea of ``equivalence modulo inputs'', which creates
+variants of program which should have equivalent behavior compared to
+the original, but for which the compiler manifests
+discrepancy. Differential testing has also been applied to test
+refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
+symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
+and to test disassemblers and binary
+lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609}. All
+in all, it has shown to be flexible and effective for a wide range of
+applications. Surprisingly, not much work has been done on
+differential testing of \js\ engines. Mozilla uses differential
+testing to look for discrepanices across different configurations of
+the same version of its \smonkey\ engine (using the ``compare\_jit''
+flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
+across engines. Patra and Pradel evaluated their fuzzing strategy on
+different browsers~\cite{patra2016learning} (see
+Section~\ref{sec:testing-js-engines}).
+
+\subsection{Testing \js\ Programs}
+Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
+lightweight approach to detect conflicts in \js\ libraries that occur
+when names introduced by different libraries collide. This problem was
+found to be common as the design of \js\ allows for overlaps in
+namespaces. A similar problem has been investigated by Nguyen and
+colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
+colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
+programs, which are popular in the context of Content Management
+Systems as WordPress. The focus of this paper is on testing
+\js\ engines as opposed to \js\ programs. Our goal is therefore
+orthogonal to theirs.
+
+\section{Conclusions}
+
+\Fix{...}
 

### 2018-08-15 paper/paper.tex
pass on related work

@@
 
-Several fuzzing techniques have been proposed recently\Fix{...elaborate...}
+Several fuzzing techniques have been proposed
+recently\Fix{...elaborate...}
 
@@
 of automatically generated parsers. After that, significant progress
-has been made. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} have proposed CSmith
-to randomly create C programs from a grammar, for a subset of C, and
-then check the output of these programs in different compilers (\eg{},
-GCC and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed the idea of ``equivalence modulo inputs'', which creates
-variants of program which should have equivalent behavior compared to
-the original, but for which the compiler manifests
+has been made. Lammel and Shulte proposed Geno to cross-check XPath
+implementations using grammar-based testing with controllable
+combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
+colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
+randomly create C programs from a grammar, for a subset of C, and then
+check the output of these programs in different compilers (\eg{}, GCC
+and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
+proposed ``equivalence modulo inputs'', which creates variants of
+program which should have equivalent behavior compared to the
+original, but for which the compiler manifests
 discrepancy. Differential testing has also been applied to test
@@
 flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their fuzzing strategy on
-different browsers~\cite{patra2016learning} (see
-Section~\ref{sec:testing-js-engines}).
+across engines. Patra and Pradel evaluated their language-agnostic
+fuzzing strategy using differential testing. Their focuses on finding
+differential bugs across multiple
+browsers~\cite{patra2016learning}. As such they specialized their
+fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
+contrast to Patra and Pradel, we did not propose new techniques; our
+contribution was empirical.
 

### 2018-08-15 paper/paper.tex
done related work

@@
 
-Several fuzzing techniques have been proposed
-recently\Fix{...elaborate...}
+Fuzzing is an active area of investigation with development of new
+techniques both in academia and industry. Several fuzzing tools exist
+focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
+different fuzzing strategies and tools. Existing techniques prioritize
+automation with a focus on finding crashes; see the sanitizers used in
+libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
+important for these tools that a warning reveals something potentially
+alarming as a crash given that fuzzing is a time-consuming operation,
+\ie{}, the ratio of bugs found per inputs generated is often very low.
+Our approach contrasts with that aim as we focus on finding errors
+manifested on the output, which rarely result in crashes and,
+consequently, would go undetected by current fuzzing approaches. It is
+should be noted, however, that such problems are not unimportant as
+per the severity levels reported in
+Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
 

### 2018-08-15 paper/abstract.tex
adding abstract in a different file to facilitate last-minute word counting

JavaScript is a popular programming language today. Several engine
implementations compete for market dominance. Although a specification
and a conformance test suite exist to guide engine development, bugs
occur and have important consequences given the language
popularity. One reason for the difficulty in implementing correct
engines stems from the fact that the specification is incomplete and
evolves frequently.

This paper reports on a study we ran to evaluate the importance of
diversity in finding bugs on this domain. For that, we explored two
simple diversity-aware methods---test transplantation and cross-engine
differential testing. Test transplantation evaluates the effects of
running test suites of a given engine in another engine. Cross-engine
differential testing evaluates the effects of fuzzing existing inputs
and then comparing the output produced by different engines with a
differential oracle.

We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, most of which
confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs
(\noBugsTransplantationConfirmed{} confirmed) and differential testing
revealed \noBugsDifferentialTesting{} bugs
(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
that most of these bugs affected only two engines--Apple's
\jsc{} (\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found
only one bug in Google \veight{} and none in Mozilla's
\smonkey{}. Although our experience indicates that more research needs
be done to automate parts of the inspection process, our results show
that exploring diversity is a valuable help to find bugs in JavaScript
engines.

### 2018-08-15 paper/paper.tex
adding abstract in a different file to facilitate last-minute word counting

@@
 \begin{abstract}
-JavaScript is a very popular programming language today, permeating
-different domains of application. Several JavaScript engines compete
-for dominance and bugs on these engines are not rare. One important
-reason for that is the language specification, which is incomplete and
-evolves frequently.
-
-This paper reports on a study to assess reliability
-of JavaScript engines by leveraging the rich diversity of open-source
-implementations. For that, we explored two methods---test
-transplantation and cross-engine differential testing. Test
-transplantation evaluates the effects of running test suites of a given
-engine in another engine. Cross-engine differential testing evaluates
-the effects of fuzzing existing inputs and then comparing the output
-produced by different engines with a differential oracle.
-
-Our results indicate that \Fix{...}
+  \input{abstract}
 \end{abstract}

### 2018-08-16 paper/paper.tex
minor fixes

--- 2018-08-15 paper/paper.tex
@@
 stronger indicative of a bug. In total, 64 test cases were discarded
-for that reason--6 from \jsc{} and 58 from \smonkey. In total, 7,029
+for that reason--6 from \jsc{} and 57 from \smonkey. In total, 7,029
 test files (\ie{}, 38369-31276-64) were considered in this experiment,
@@
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 279 \\
+    \smonkey{} & 217 & 106 & - & 278 \\
     Duktape & 0 & 4 & 4 & 1   \\
@@
    6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 & 5/21  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
+   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
    8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
@@
    11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
-   12 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   13 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
-   14 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   15 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
-   16 & 8/08  & V8 & \textbf{Assigned} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
-   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
+   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
+   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
+   14 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
+   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
+   16 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
+   17 & 8/08  & V8 & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   18 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
    \bottomrule

### 2018-08-16 paper/abstract.tex
pass on abstract and intro

@@
 JavaScript is a popular programming language today. Several engine
-implementations compete for market dominance. Although a specification
-and a conformance test suite exist to guide engine development, bugs
+implementations compete for market dominance. Although specification
+and conformance test suite exist to guide engine development, bugs
 occur and have important consequences given the language
@@
 This paper reports on a study we ran to evaluate the importance of
-diversity in finding bugs on this domain. For that, we explored two
+diversity in finding bugs on JavaScript engines. For that, we explored two
 simple diversity-aware methods---test transplantation and cross-engine

### 2018-08-16 paper/paper.tex
pass on abstract and intro

--- 2018-08-15 paper/paper.tex
@@
 JavaScript (\js{}) is today one of the most popular programming
-languages around~\cite{business-insider,stackify}, with significant
-penetration in various segments including, web development, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification
-and implementations. It is natural to expect that such improvements
-lead to sensible implementation changes. Even small changes can have
-high practical impact. For example, in October 2014 a new attribute
-added to Array objects resulted in the MS Outlook Calendar web app
-stop working under
+languages around~\cite{business-insider,stackify}, with penetration in
+various segments including, web development, mobile, and, more
+recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
+interest of the community for the language encourages constant
+improvements in its specification and implementations. It is natural
+to expect that such improvements lead to sensible changes in engine
+implementation. Even small changes can have high practical impact. For
+example, in October 2014 a new attribute added to Array objects
+resulted in the MS Outlook Calendar web app stop working under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
@@
 feature. The publicly-available Kangax compatibility
-table~\cite{kangax} relates features of \js\ with the engines that
+table~\cite{kangax} relates \js\ features with the engines that
 support them. To sum, it is often non-trivial to assess if a test
@@
 %% WHAT WE DID
-The goal of this paper is to assess reliability of popular
-\js\ engines. The paper reports the results of a study that evaluates
-the effectiveness of two complementary diversity-aware testing techniques. \emph{Test transplantation} leverages
-diversity of test cases to find bugs. It evaluates the effects that
-running \js{} test files from a given engine have in detecting bugs in
-other engines. The intuition is that developers design test cases
-differently; hence replaying the test in a different engine may reveal
-unanticipated problems. \emph{Cross-engine differential testing}
-evaluates the ability of leveraging diversity of engine
-implementations to find bugs. More precisely, it fuzzes existing test
+This paper reports on a study we ran to evaluate the importance of
+diversity in finding bugs on JavaScript engines. We evaluated
+effectiveness of two complementary diversity-aware testing
+techniques. \emph{Test transplantation} leverages diversity of test
+cases to find bugs. It evaluates the effects that running \js{} test
+files from a given engine have in detecting bugs in other engines. The
+intuition is that developers design test cases differently; hence
+replaying the test in a different engine may reveal unanticipated
+problems. \emph{Cross-engine differential testing} evaluates the
+ability of leveraging diversity of engine implementations to find
+bugs. More precisely, it fuzzes existing test
 inputs~\cite{fuzz-testing-history} and then compares the output
 produced by different engines using a differential oracle. One of
-various causes of output discrepancy is a bug. It is worth noting that
-Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
-a variety of contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
-automates test generation in scenarios where multiple implementations
-of a system exist. DT leverages the diversity across system's
-implementations to detect anomalous behavior. For example, Mozilla
-runs JS files\footnote{These files are created with the grammar-based fuzzer
-  jsfunfuzz~\cite{jsfunfuzz}. Look for option ``compare\_jit'' from funfuzz.} against different configurations of their
-\smonkey{} engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
-across different configurations of the same build (\eg{}, enabling or
-not eager JIT compilation). They use this technique since 2002 and
+various causes of output discrepancy is a bug.
+
+%% It automates test generation in scenarios where multiple
+%% implementations of a system exist. DT leverages diversity across
+%% system's implementations to detect anomalous behavior.
+
+\emph{Related Ideas.}  It is worth noting that Differential
+Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
+contexts to find
+bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
+It has shown to be specially practical in scenarios where the
+observation of difference gives a strong signal of a real problem. For
+example, Mozilla runs JS files\footnote{These files are created with
+  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
+  ``compare\_jit'' from funfuzz.} against different configurations of
+a given build of their \smonkey\ engine (\eg{}, trying to enable or
+not eager JIT compilation). In that setting, test outcomes are
+expected to be identical. Mozilla uses this approach since 2002 and
 have been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
-contrast, cross-engine differential testing--the technique used in
-this work--checks functional correctness by comparing the output
-produced by \emph{different engines} on a fuzzed
-input~\cite{patra2016learning} as opposed to different builds of the
-same engine. This approach has not been
-popularized, certainly, because it is still not practical to fully automate--a
-number of legitimate reasons exist, other than a bug, for a test
-execution to manifest discrepancy (see
-Table~\ref{tab:false-positives}). This study quantifies human effort
-to find these bugs using this method.
-
-%% WHAT WE FOUND
-To sum, we found that \Fix{...}
+then~\cite{jsfunfuzz-at-mozilla}, including security
+bugs. Cross-engine differential testing, in contrast, has not been
+popularized to similar extent. One possible reason is that it is still
+not practical to fully automate the technique. In contrast to other
+applications of differential testing, a number of legitimate reasons
+exist, other than a bug, for a test execution to manifest discrepancy
+(see Table~\ref{tab:false-positives}). Recently, Patra and
+Pradel~\cite{patra2016learning} explored the idea. They proposed a
+language-agnostic fuzzer to find cross-browser HTML+JS
+discrepancies. Their main contribution is analytical whereas our main
+contribution is empirical--goal is to evaluate ability and cost of
+simple diversity-aware approaches to find bugs in \js\ engines.
+
+\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
+Google, Microsoft, and Mozilla. Our results indicate that both
+techniques revealed several bugs, most of which confirmed by
+developers. Test transplantation revealed \noBugsTransplantation{}
+bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
+testing revealed \noBugsDifferentialTesting{} bugs
+(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
+that most of these bugs affected only two engines--Apple's \jsc{}
+(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
+one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
+our experience indicates that more research needs be done to automate
+parts of the inspection process, our results show that exploring
+diversity is a valuable help to find bugs in JavaScript engines.
 
 %% LIST OF CONTRIBUTIONS
-This paper makes the following contributions \Fix{...}
+This paper makes the following contributions.
+\begin{itemize}
+  \item We ran a comprehensive study to analyze the effectiveness of
+    simple diversity-aware techniques to find bugs in highly-popular
+    \js\ engines.
+
+  \item We reported more than \Fix{50} bugs on these engines over a
+    period of 5 months.
+
+  \item We offered insights on how to reduce cost of analyzing
+    warnings reported by diversity-aware techniques and make the
+    approach more practical.
+
+  \item We made our testing infrastructure, results, and experimental
+    scripts available to the public. (upon request for anonimity.)
+\end{itemize}
 
@@
 expect that test suites written for a given engine cover scenarios and
-corner cases uncovered by another engine. To sum, we hope that that
+corner cases uncovered by another engine. To sum, we conjecture that
 test cases written for one engine could reveal bugs in different
-engines as opposed to only manifesting false alarms such as those that
-could emerge from implementation-dependent behavior. Third, we
+engines as opposed to only manifesting false alarms. Third, we
 analyzed the impact of using cross-engine differential testing to find
@@
 changes only in literals of the language could expose important
-bugs. All in all, we want to assess the impact of simple approaches
-that leverage on diversity to find bugs in \js\ engines with the goal
-of assessing their reliability.
+bugs. All in all, we want to assess the impact of practical approaches
+that leverage diversity to find bugs in \js\ engines.
 
@@
 
+\begin{figure}[h]
+  \centering
+  \subfloat[\label{fig:falsepositives}False Positives]{%
+    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
+  }
+  \label{1a}\hfill
+  \subfloat[\label{fig:truepositives}True Positives]{%
+    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
+  }
+  \label{1b}\\
+  \caption{\label{fig:piecharts-transplantation}False and True positives.}
+\end{figure}
+
 \begin{itemize}
@@
 
-\begin{figure}[h]
-  \centering
-  \subfloat[\label{fig:falsepositives}False Positives]{%
-    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
-  }
-  \label{1a}\hfill
-  \subfloat[\label{fig:truepositives}True Positives]{%
-    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
-  }
-  \label{1b}\\
-  \caption{\label{fig:piecharts-transplantation}False and True positives.}
-\end{figure}
-
-\begin{table*}[t]
-  \vspace{-3ex}
+\begin{table}[t!]
+\setlength{\tabcolsep}{2pt}    
+%  \vspace{-3ex}
 %  \scriptsize
   \centering
-  \caption{List of bug reports issued as result of test transplantation.}
+  \caption{List of bug reports issued as result of test
+    transplantation. Url columns anonymized.}
   \label{tab:test-transplantation-bugs}
@@
   \end{tabular}
-\end{table*}
-
-Figure~\ref{tab:test-transplantation-bugs} lists all bugs we found
+\end{table}
+
+Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
 with test transplantation. The first column shows the identifier we

### 2018-08-16 paper/paper.tex
pass on methodology

@@
 \subsection{Clusterization}
+\label{sec:clusterization}
 
@@
 
-This section reports the results obtained by fuzzing inputs, running
-those inputs on different engines, and checking the outcomes with a
-differential oracle (see Figure~\ref{fig:workflow}).
+This section reports the results obtained with differential
+testing. More precisely, we report results obtained by fuzzing test
+inputs, running those inputs on different engines, and checking the
+outcomes with a differential oracle (see Figure~\ref{fig:workflow}).
 
 \subsubsection{Methodology}
-In the following, we describe the methodology we used to assess the
-impact of cross-engine differential testing in finding bugs on \js{}
-engines. To avoid experimental noise, we did \emph{not} fuzz test
-files that failed in some engine as per results reported in
-Sections~\ref{sec:stability} and~\ref{sec:transplantation}. The
-intuition is that we want to make sure that the bug was not
-coincidental, \ie{}, the scenario where fuzzing produces an
+The methodology we used to assess the effectiveness of cross-engine
+differential testing is as follows. To avoid experimental noise, we
+only fuzz test files that pass in all engines. The intuition is that
+we wanted to avoid the scenario where fuzzing produces a
 fault-revealing input based on a test that was already
-fault-revealing. That decision ensures that we can establish
+fault-revealing. This decision ensures that we can establish
 cause-effect relationship between fuzzing and the observation of
-discrepancy. For that reason, we discarded a total of \Fix{???} test
-files from a total of \totalTestFiles{}.Recall that our tool outputs a
-set of buckets, that each bucket includes a set of warnings, that each
-warning is related to one file, and that a bucket is of ``lo'' or
-``hi'' importance, according to the heuristic we
-defined. Figure~\ref{fig:distribution} shows the distribution of
-number of warnings reported per bucket. We use the names of the
-fuzzing tools to refer to the results obtained with those tools. We
-inspected each and every bucket for bugs, but observe that the number
-of files per bucket is very high in some cases. As such, it would be
-impractical to manually inspect all the files in the bucket. For that
-reason, we only inspected one file per bucket. For the cases we found
-the warning suspicious, we analyzed the parts of the documentation
-related to the problem and, if still suspicious, we looked on the bug
-tracker of the affected engine for potential duplicates. If none was
-reported, we filed a bug report including the test input that
-manifested the potential problem and explaining the reasons we were
-suspicious. In some cases, we used the Mozilla lithium
-tool~\cite{lithium} to minimize the test case. For the cases of false
-positives, we identified the source of false positive and moved to the
-next bucket.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.40\textwidth]{R/histograms/histograms.pdf}  
-  \caption{\label{fig:distribution}Distribution of lo and hi warnings
-   in buckets.}
-\end{figure}
+discrepancy. Column ``no-fail-in-all'' from
+Table~\ref{tab:test-suites} shows that a total of
+\totalTestFilesPassInAll\ tests satisfy this restriction.
+
+\vspace{1ex}
+\noindent\textbf{Exploratory Phase.} For the first four months of the
+study, our inspection process was exploratory.  Our goal in this phase
+was to learn the extent to which \lo\ warnings could reveal bugs. We
+realized that if we found that the ratio of bugs from \lo\ warnings
+was rather low, we could focus our inspection efforts only on
+\hi\ warnings. That finding would be important to reduce inspection
+cost and guide future developments of this approach. To run this
+experiment, we trained eight students in analyzing the warnings that
+our infrastructure produces. The students were enrolled in a
+graduate-level testing class. We listed warnings in a spreadsheet and
+requested students to update an ``owner'' column indicating who was
+working on it, but we did not enforce an order on the warnings the
+students should inspect. Recall from Section~\ref{sec:clusterization}
+that we clustered \lo\ warnings in buckets. For that reason, we only
+listed one \lo\ warning per representative class/bucket in the
+spreadsheet. First, we explained the possible sources of false alarms
+with examples and then we asked the students to use the following
+procedure when finding a suspicious warning. Analyze the parts of the
+spec related to the problem and, if still suspicious, look for
+potential duplicates on the bug tracker of the affected engine using
+related keywords. If none was reported, indicate in the spreadsheet
+that that warning is potentially fault-revealing. We encouraged
+students to use lithium~\cite{lithium} to minimize long test cases;
+the tests from the Mozilla suite are often longer than others. Only
+after the co-authors checked the potential bugs, a bug report was
+filed.
+
+\vspace{1ex}
+\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
+exploratory phase confirmed our expectations that most of the bugs
+found during the initial four months of investigation were related to
+\hi\ warnings. For that reason, we changed our inspection
+strategy. This time, only the co-authors inspected the bugs using a
+similar discipline as before. However, the set of warnings inspected
+and the order of inspection changed. We restricted our analysis to
+\hi\ warnings and, aware that we would be unable to analyze each and
+every warning reported, we grouped those warnings per engine,
+analyzing each group in a round-robin fashion. The rationale was to
+give attention to each engine more uniformly, enabling more fair
+comparison across engines. We repeated the following routine until
+Aug. 22, 2018. We sampled five warnings associated with the group of a
+given engine, analyzed these warnings, and moved to the group of
+warnings associated with the next engine.
 
@@
     \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
+    \midrule
+    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
     \midrule    
@@
     & 2 & HI & \jerry{}\\
+    \midrule        
+    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
+    \midrule    
    \bottomrule

### 2018-08-16 paper/paper.tex
update results

@@
     \midrule
-    \jsc{} & 4330 & 4330 & 4330 & - & - & - & - \\
-    \veight{} & 3404 & 3404 & 3401 & - & - & - & - \\
-    \chakra{} & 9104 & 9104 & 9104 & - & - & - & - \\
-    \smonkey{} & 3943 & 3943 & 3943 & - & - & - & - \\
+    \jsc{} & 2278 & - & - & - & - & - & - \\
+    \veight{} & 1213 & - & - & - & - & - & - \\
+    \chakra{} & 7041 & - & - & - & - & - & - \\
+    \smonkey{} & 1761 & - & - & - & - & - & - \\
     \bottomrule 

### 2018-08-16 paper/paper.tex
minor changes

@@
 \vspace{1ex}
-\noindent\textbf{Exploratory Phase.} For the first four months of the
+\noindent\textbf{Exploratory Phase.} For the first three months of the
 study, our inspection process was exploratory.  Our goal in this phase
@@
 exploratory phase confirmed our expectations that most of the bugs
-found during the initial four months of investigation were related to
+found during the initial three months of investigation were related to
 \hi\ warnings. For that reason, we changed our inspection

### 2018-08-16 paper/paper.tex
revised tables

@@
 \subsubsection{Results}
+\Mar{revise text...}
+\Fix{
 Table~\ref{tab:summary-of-results} summarizes our results. It shows,
@@
 group is higher, indicating that chances of filing a bug report for a
-``hi'' warning is higher.
+``hi'' warning is higher.}
 
@@
   \centering
-  \caption{\label{tab:summary-of-results}Summary of results.}
-  \begin{tabular}{ccrrrr}
+  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
+  \begin{tabular}{crr}
     \toprule
-    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
-    \cline{4-6}    
-    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
-    \multicolumn{1}{c}{\# pos. filed} \\
-    \midrule
-    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
-    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
-    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
-                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
+    & \# buckets & avg. \# files per bucket \\
+    \midrule
+    \radamsa{} & & \\
+    \quickfuzz{} & & \\    
+    \bottomrule     
+  \end{tabular}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption{\label{tab:summary-hi}Number of \hi\ warning
+    reports per engine.}
+  \begin{tabular}{crrrr}
+    \toprule
+    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey \\
+    \midrule
+    \radamsa{} & & \\
+    \quickfuzz{} & & \\    
     \bottomrule     

### 2018-08-17 paper/paper.tex
adding plot and massaging text

@@
 
-The goal of our study is to assess reliability of \js\ engines by
-leveraging implementation diversity, which is specially rich in this
-domain. We report results in three parts. First, we report on the
-stability of the engines we analyzed using the Test262 standard
-conformance test suite for EcmaScript~\cite{ecma262-conformance-suite}
+\Mar{REVISE}The goal of our study is to assess reliability of \js\ engines by
+leveraging implementation diversity. We organized our study in three
+parts. First, we report on the stability of the engines we analyzed
+using the Test262 standard conformance test suite for
+EcmaScript~\cite{ecma262-conformance-suite}
 (Section~\ref{sec:stability}). The intuition is that the bugs we
@@
 changes only in literals of the language could expose important
-bugs. All in all, we want to assess the impact of practical approaches
-that leverage diversity to find bugs in \js\ engines.
-
-\subsection{Stability of Engines}
+bugs.
+
+\subsection{Summary of Results}
+\label{sec:summary}
+
+Figure~\ref{fig:summary}...
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
+  \caption{\label{fig:summary}Summary of results.}
+\end{figure}
+
+\subsection{Test Transplantation}
+\label{sec:transplantation}
 \label{sec:stability}
 
-We evaluated stability with Test262~\cite{ecma262-conformance-suite},
+\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
 the official \js{} conformance test suite for the ECMA262
@@
 \end{table}
-
-\subsection{Test Transplantation}
-\label{sec:transplantation}
 
@@
 
-\subsubsection{Results}
-\Mar{revise text...}
-\Fix{
-Table~\ref{tab:summary-of-results} summarizes our results. It shows,
-for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
-of files involved, the number of buckets reported by our
-infrastructure, the number of those that we classified as
-bug-revealing (positive), and the number of those that we filed a bug
-report. The difference between the last two columns corresponds to the
-number of duplicates, \ie{}, the cases of bugs already reported in the
-corresponding issue tracker. As expected, the hit ratio for the ``hi''
-group is higher, indicating that chances of filing a bug report for a
-``hi'' warning is higher.}
+\subsubsection{Results} Table~\ref{tab:summary-lo} shows statistics of \lo\ warnings obtained
+when fuzzing inputs with different tools. Column ``\# buckets'' show
+the number of buckets associated with ``\lo'' warnings whereas column
+``avg. \# files per bucket'' show the average number of files per
+bucket. Note that \Fix{...}
 
@@
 \end{table}
+
+Table~\ref{tab:summary-hi} shows the number of \hi\ warnings reported
+per engine. Recall that we did not cluster \hi\ warnings as there was
+not clear clustering criteria to use for that. Note that \Fix{...}
 
@@
 
-% \Igor{
-%   Para realizar nossos experimentos, tivemos que decidir qual as 
-%   melhores abordagens para aumentar a efetividade dos fuzzers.
-%   Os fuzzers mutacionais se mostraram mais eficientes em relacao
-%   aos fuzzers geracionais, entao focamos neste ponto.
-%   Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
-%   default para realizar a mutacao em arquivos existentes.
-%   O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
-%   deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
-%   pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
-%   O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
-%   radamsa, gerando arquivos mais relevantes.
-%   Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
-%   é um arquivo de teste relevante, seguindo estes requisitos:
-%   \begin{itemize}
-%     \item it contains only unicode text
-%     \item it is parseable (i.e., it is structurally well-formed)
-%     \item it does not contain engine-specific functions  
-%     \item it does not empty
-%   \end{itemize}
-
-% }
-
-\section{Bugs Found}
-\label{sec:bugs}
-
-%% Although there are many features yet to implement in our
-%% infrastructure,
+Table~\ref{tab:bugs} shows the list of bugs we reported with
+differential testing across five months of analysis. The table is
+organized in two sections. The top section shows results obtained
+during the exploratory phase of the study and the bottom section shows
+the results obtained during the non-exploratory phase. The table shows
+the date the bug was reported (``Date''), the fuzzing tool used to
+detect the bug (``Fuzz''), the \js\ engine affected (``Engine''), the
+status of the bug report as of Aug. 24, 2018 (``Status''), the Url of
+the bug report (``Url''), the severity of the bug report
+(``Severity''), the priority that we assigned to the warning that
+revealed the bug (``Priority''), and the test suite from the original
+test input (``Suite'').
+
+\Mar{REVISE}So far, ten of the bugs we
+reported were confirmed, two of which were fixed. One bug report we
+submitted was rejected on the basis that the offending JS file
+manifested an expected incompatibility across engine implementations.
+Note from the table that all bug reports still waiting for
+confirmation are associated with the \jsc{} engine (JSC). A closer
+look at the JSC issue tracker showed that the triage process is very
+slow for that engine.  \Igor{ The bugs reported on \chakra{}'s bug
+  tracker was defined as confirmed, however the bugs are included on a
+  milestone for the next release following an internal priority.  } As
+of now, we did not find any new bug on \smonkey{} and V8; the bugs we
+found were duplicates and were not reported. Finally, it is worth
+noting that \Fix{11 of the 19} JS files that manifested discrepancies
+were \emph{not} produced with fuzzing (column ``Fuzz''). These are
+test files from suites of different engines. This observation
+emphasizes the importance of continuously collecting test suites from
+multiple sources; today, we use test suites from seven different open
+source engines, including a total of 30K test files.
 
@@
 
-This section shows results obtained with our
-infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
-reported on issue trackers of different engines in the period of 42
-days. So far, ten of the bugs we reported
-were confirmed, two of which were fixed. One bug report we
-submitted was rejected on the basis that the offending JS file
-manifested an expected incompatibility across engine
-implementations.
-Note from the table that all bug
-reports still waiting for confirmation are associated with the
-\jsc{} engine (JSC). A closer look at the JSC issue tracker
-showed that the triage process is very slow for that engine. 
-\Igor{
-The bugs reported on \chakra{}'s bug tracker was defined as confirmed, 
-however the bugs are included on a milestone for the next release
-following an internal priority.
-}
-As of now, we did not find any new bug on \smonkey{} and V8; 
-the bugs we found were duplicates and were not reported. Finally, it is
-worth noting that \Fix{11 of the 19} JS files that manifested
-discrepancies were \emph{not} produced with fuzzing (column
-``Fuzz''). These are test files from suites of different engines. This
-observation emphasizes the importance of continuously collecting test suites from
-multiple sources; today, we use test suites from seven different open
-source engines, including a total of 30K test files.
+\section{Bugs Found}
+\label{sec:bugs}
 
@@
 
-\vspace{1ex}\noindent\textbf{Bug \# 6.} The JS code \CodeIn{var a = \{valueOf:~function()\{return
-  ``\textbackslash{}x00''\}\} assert(+a === 0)\}} 
-manifested a bug in the \js{} engine \chakra{}.  The object
-property \CodeIn{valueOf} stores a function that returns a primitive
-value identifying the target object~\cite{valueof}. The original
-version of this code returns an empty string whereas the version of
-the code modified by the Radamsa fuzzer~\cite{radamsa} returns a string
-representation of a null character (called \CodeIn{NUL} in ascii). The
-unary plus expression ``\CodeIn{+a}", appearing in the assertion, is
-equivalent to the abstract operation \CodeIn{ToNumber(a.valueOf())}
-that converts a string to a number, otherwise the operation returns
-NaN (Not a Number)\cite{unary-plus}. For this case, \chakra{} evaluates
-the unary plus to NaN as expected, as the null character cannot be
-converted. As result, the test fails as expected. \chakra{}, in contrast,
+\sloppy
+\vspace{1ex}\noindent\textbf{Bug \# \Fix{6}.} The JS code \CodeIn{\{var a =
+  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
+  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
+The object property \CodeIn{valueOf} stores a function that returns a
+primitive value identifying the target object~\cite{valueof}. The
+original version of this code returns an empty string whereas the
+version of the code modified by the Radamsa fuzzer~\cite{radamsa}
+returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
+used in the assertion, is equivalent to the operation
+\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
+otherwise the operation returns NaN (Not a
+Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
+  chakra did that it would be fine, no?} evaluates the unary
+plus to NaN as expected, as the null character cannot be converted. As
+result, the test fails as expected. \chakra{}, in contrast,
 incorrectly converts the string to zero, making the test to pass. All

### 2018-08-18 paper/paper.tex
polishing summary plot
added data to tables
pass on paper

@@
 
-\Mar{REVISE}The goal of our study is to assess reliability of \js\ engines by
+The goal of our study is to assess reliability of \js\ engines by
 leveraging implementation diversity. We organized our study in three
 parts. First, we report on the stability of the engines we analyzed
-using the Test262 standard conformance test suite for
+using the official Test262 conformance test suite for
 EcmaScript~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). The intuition is that the bugs we
-discover throughout this study would have low relevance if the engines
-are too fragile. Second, we report results obtained with test
-transplantation (Section~\ref{sec:transplantation}). The rationale is
-that the domain of possible inputs is too large; consequently, we
-expect that test suites written for a given engine cover scenarios and
-corner cases uncovered by another engine. To sum, we conjecture that
-test cases written for one engine could reveal bugs in different
-engines as opposed to only manifesting false alarms. Third, we
-analyzed the impact of using cross-engine differential testing to find
-bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale is that even black-box fuzzers that typically make valid
-changes only in literals of the language could expose important
-bugs.
-
-\subsection{Summary of Results}
-\label{sec:summary}
-
-Figure~\ref{fig:summary}...
+(Section~\ref{sec:stability}). In the limit, bugs would have low
+relevance if the engines are too unreliable. Second, we report results
+obtained with test transplantation
+(Section~\ref{sec:transplantation}). The rationale is that the domain
+of possible inputs is too large; consequently, we expect that test
+suites written for a given engine cover scenarios and corner cases
+uncovered by another engine. To sum, we conjecture that test cases
+written for one engine could reveal bugs in different engines as
+opposed to only manifesting false alarms. Third, we analyzed the
+impact of using cross-engine differential testing to find bugs
+(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
+is that black-box fuzzers could expose important bugs.
+
+\vspace{1ex}
+\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
+summary of the bugs we reported. The figure shows the distribution of
+status of bug reports per engine. Note that several of these reports
+were not reviewed yet, \ie, they did not receive a label ``confirmed''
+or ``rejected'' from the development team. Note also that we did not
+find bugs in the Mozilla \smonkey\ engine and that several of the bugs
+we reported were already fixed and incorporated to the latest release
+of corresponding engines.
 
@@
   \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
-  \caption{\label{fig:summary}Summary of results.}
+  \includegraphics[trim=0 120 0 150,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked}  
+  \caption{\label{fig:summary}Summary of bug reports per engine and status.}
 \end{figure}
+
+\subsection{Conformance}
+\label{sec:stability}
+
+\begin{wraptable}[12]{r}{0.25\textwidth}  
+  \centering
+  \caption{\label{tab:test262}Percentage of passing tests on
+    the Test262 conformance suite.\Mar{Please, use percentages.}}
+  \small
+  \begin{tabular}{crr}
+    \toprule
+    engine & \% passsing \\
+    \midrule
+    \jsc{} & \Fix{2278}\\
+    \veight{} & \Fix{1213} \\
+    \chakra{} & \Fix{7041} \\
+    \smonkey{} & \Fix{1761} \\
+    \bottomrule 
+  \end{tabular}
+  \normalsize
+\end{wraptable}
+
+We used the official conformance test suite
+Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
+engines to the \js\ standard. We ran the suite once a day for seven
+consecutive days from the period of 16 to 22 of August,
+2018. Table~\ref{tab:test262} shows the average number of passing
+tests over this period. It is important to note that failures are
+expected as it takes time for engines to adjust to the
+spec.\Mar{...mention the variance was negligible...} We noticed that
+all four engines we analyzed but \chakra{} use some variant of the
+Test262 suite as part of their regression process, but we used the
+same version in this experiment, the one available from the Test262
+web site~\cite{ecma262-conformance-suite}. Results show that there are
+still many unsupported cases as can be observed from the percentages
+in the table, but the number of passing tests is high, with
+\veight\ and \jsc\ performing better compared to others and
+\chakra\ performing well worse than others. It is important to
+highlight that failures in this test suite indicates missing features
+as opposed to bugs. However, note that \chakra\ is both the engine
+that has the lowest passing ratio in the conformance test suite and
+the one we were able to find more confirmed bugs (as per
+Figure~\ref{fig:summary}). We conjecture that the development age of
+the engine--Chakra is the newest engine\Fix{find DOB of
+  Chakra}--justify both observations.
+
+%% The rationale is that lack of support
+%% to features (as measured by conformance testing) and reliability of
+%% engines (as measured in this study) may have some relationship.
 
@@
 \label{sec:transplantation}
-\label{sec:stability}
-
-\Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
-the official \js{} conformance test suite for the ECMA262
-specification. We ran this suite once a day for seven consecutive
-days. Table~\ref{tab:test262} shows the number of failures over this
-period. It is important to note that failures are expected as it takes
-time for engines to adjust to the spec. It is also important to
-highlight that all engines we analyzed, but \chakra{}, use some
-variant of the Test262 suite as part of their regression
-process\Mar{with fewer tests?}. We used the official version
-instead\Mar{, which updates tests regularly?}. To sum, we observed
-that \Fix{...} \Mar{justify regressions using the Kangax report}
-
-\begin{table}[h]
-  \centering
-  \caption{\label{tab:test262}Number of failures in Test262 over
-    a 7-day period.}
-  \begin{tabular}{crrrrrrr}
-    \toprule
-    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
-    \midrule
-    \jsc{} & 2278 & - & - & - & - & - & - \\
-    \veight{} & 1213 & - & - & - & - & - & - \\
-    \chakra{} & 7041 & - & - & - & - & - & - \\
-    \smonkey{} & 1761 & - & - & - & - & - & - \\
-    \bottomrule 
-  \end{tabular}
-\end{table}
 
@@
 %% testing paid off in this case.
-
 \begin{table}[h]

### 2018-08-18 paper/paper.tex
pass on transplantation

--- 2018-08-17 paper/paper.tex
@@
   \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.4\textwidth]{R/stackedbar/stacked}  
+  \includegraphics[trim=0 120 0 150,clip,width=0.4\textwidth,scale=0.3]{R/stackedbar/stacked}  
   \caption{\label{fig:summary}Summary of results.}
@@
 \label{sec:stability}
-
+\Igor{
+  Marcelo, de acordo com os resultados obtidos, prefiro retirar
+  esse paragrafo e tabela, nao houve perda/aumento de falhas nesses
+  ultimos 7 dias, acho que valeria a pena se fizessemos isso 1 vez por semana
+  durante os ultimos meses.
+}
 \Mar{REVISE}We evaluated stability with Test262~\cite{ecma262-conformance-suite},
@@
     \midrule
-    \jsc{} & 2278 & - & - & - & - & - & - \\
-    \veight{} & 1213 & - & - & - & - & - & - \\
-    \chakra{} & 7041 & - & - & - & - & - & - \\
-    \smonkey{} & 1761 & - & - & - & - & - & - \\
+    \jsc{} & 2278 & 2278 & 2278 & 2278 & 2278 & 2278 & - \\
+    \veight{} & 1213 & 1213 & 1213 & 1213 & 1213 & 1213 & - \\
+    \chakra{} & 7041 & 7041 & 7041 & 7041 & 7041 & 7041 & - \\
+    \smonkey{} & 1761 & 1761 & 1761 & 1761 & 1761 & 1761 & - \\
     \bottomrule 
@@
     \midrule
-    \radamsa{} & & \\
+    \radamsa{} & \Fix{62} & \Fix{1.62 (101/62)}\\
     \quickfuzz{} & & \\    

### 2018-08-20 paper/paper.tex
pass on abstract and intro

--- 2018-08-18 paper/paper.tex
@@
 to expect that such improvements lead to sensible changes in engine
-implementation. Even small changes can have high practical impact. For
+implementation. In fact, even small changes can have high practical impact. For
 example, in October 2014 a new attribute added to Array objects
@@
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-Intuitively, developing reliable engines is difficult because
-specifications are incomplete and evolve frequently.
 
@@
 fails because of a bug or because of some other reason making test
-automation more challenging.
-
-%% when a bug is found in some engine a test case is created and added to
-%% the regression suite. Those test inputs often check interesting
-%% scenarios that could reveal bugs in different engine
-%% implementations.
+automation more challenging. Intuitively, developing reliable engines
+is difficult because specifications are intentionally incomplete--for
+development flexibility--and evolve frequently.
 
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). In that setting, test outcomes are
+not eager JIT compilation). As the same engine is used, test outcomes are
 expected to be identical. Mozilla uses this approach since 2002 and

### 2018-08-20 paper/paper.tex
pass on V.C

@@
 every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion. The rationale was to
-give attention to each engine more uniformly, enabling more fair
-comparison across engines. We repeated the following routine until
-Aug. 22, 2018. We sampled five warnings associated with the group of a
-given engine, analyzed these warnings, and moved to the group of
-warnings associated with the next engine.
+analyzing each group in a round-robin fashion.  At each iteration, we
+analyzed \Fix{five} warnings in each group. A warning belongs to the
+group of a given engine if only that engine manifests distinct
+behavior, \ie{}, it produces a distinct output compared to others. We
+separated in a distinct group the warnings for which two engines
+diverge. The rationale for this methodology was to give attention to
+each engine more uniformly, enabling more fair comparison across
+engines.
 

### 2018-08-20 paper/paper.tex
pass on results

--- 2018-08-20 paper/paper.tex
@@
 to expect that such improvements lead to sensible changes in engine
-implementation. In fact, even small changes can have high practical impact. For
+implementation. Even small changes can have high practical impact. For
 example, in October 2014 a new attribute added to Array objects
@@
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
+Intuitively, developing reliable engines is difficult because
+specifications are incomplete and evolve frequently.
 
@@
 fails because of a bug or because of some other reason making test
-automation more challenging. Intuitively, developing reliable engines
-is difficult because specifications are intentionally incomplete--for
-development flexibility--and evolve frequently.
+automation more challenging.
+
+%% when a bug is found in some engine a test case is created and added to
+%% the regression suite. Those test inputs often check interesting
+%% scenarios that could reveal bugs in different engine
+%% implementations.
 
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). As the same engine is used, test outcomes are
+not eager JIT compilation). In that setting, test outcomes are
 expected to be identical. Mozilla uses this approach since 2002 and
@@
     \toprule
-    engine & \% passsing \\
+    engine & \% passing \\
     \midrule
@@
     \midrule
-    \radamsa{} & & \\
-    \quickfuzz{} & & \\    
+    \radamsa{} & \Fix{82} & \Fix{3 (241/82)}\\
+    \quickfuzz{} & \Fix{38} & \Fix{2 (87/38)} \\
     \bottomrule
@@
     reports per engine.}
-  \begin{tabular}{crrrr}
+  \begin{tabular}{crrrrr}
     \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey \\
-    \midrule
-    \radamsa{} & & \\
-    \quickfuzz{} & & \\    
+    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & 2+\\
+    \midrule
+    \radamsa{} & 30 & 8 & 121 & 5 & \\
+    \quickfuzz{} & & & & & \\    
     \bottomrule     

### 2018-08-20 paper/abstract.tex

--- 2018-08-15 paper/abstract.tex
@@
-JavaScript is a popular programming language today. Several engine
-implementations compete for market dominance. Although a specification
-and a conformance test suite exist to guide engine development, bugs
-occur and have important consequences given the language
-popularity. One reason for the difficulty in implementing correct
-engines stems from the fact that the specification is incomplete and
-evolves frequently.
+JavaScript is a very popular programming language today. Several
+engine implementations compete for market dominance. Although a
+specification document and an conformance test suite exist to guide
+engine development, bugs occur and have important practical
+consequences. One reason for the difficulty in implementing correct
+engines stems from the fact that the specification is intentionally
+incomplete and evolves frequently.
 
 This paper reports on a study we ran to evaluate the importance of
-diversity in finding bugs on this domain. For that, we explored two
-simple diversity-aware methods---test transplantation and cross-engine
-differential testing. Test transplantation evaluates the effects of
-running test suites of a given engine in another engine. Cross-engine
-differential testing evaluates the effects of fuzzing existing inputs
+diversity to find functional bugs in JavaScript engines. For that, we used two
+simple diversity-aware techniques--test transplantation and cross-engine
+differential testing. The first technique\Comment{Test transplantation} evaluates the effects of
+running test suites of a given engine in another engine. The second technique\Comment{Cross-engine
+differential testing} evaluates the effects of fuzzing existing inputs
 and then comparing the output produced by different engines with a
@@
 (\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
-that most of these bugs affected only two engines--Apple's
+that most of these bugs affected two engines--Apple's
 \jsc{} (\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found
-only one bug in Google \veight{} and none in Mozilla's
-\smonkey{}. Although our experience indicates that more research needs
-be done to automate parts of the inspection process, our results show
-that exploring diversity is a valuable help to find bugs in JavaScript
-engines.
+only \Fix{one} bug in Google \veight{} and none in Mozilla's
+\smonkey{}. Although more research needs to be done to optimizie 
+warning triaging, our results show that exploring diversity is a
+valuable help to find bugs in JavaScript engines.

### 2018-08-20 paper/paper.tex
pass on results

--- 2018-08-20 paper/paper.tex
@@
     reports per engine.}
-  \begin{tabular}{crrrr}
+  \begin{tabular}{crrrrr}
     \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey \\
-    \midrule
-    \radamsa{} & & \\
-    \quickfuzz{} & & \\    
+    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & 2+\\
+    \midrule
+    \radamsa{} & 30 & 4 & 121 & 3 & 143\\
+    \quickfuzz{} & & & & & \\    
     \bottomrule     
@@
     & \radamsa\ & \quickfuzz\ \\
-    Undefined & - & - \\
-    Timeout/OME & - & - \\
-    Not Implemented & - & - \\
+    Undefined & 18 & - \\
+    Timeout/OME & 23 & - \\
+    Not Implemented & 19 & - \\
     Upcoming Feature & - & - \\
-    Error Message Mismatch & - & - \\    
-    Invalid Input & - & - \\    
+    Error Message Mismatch & 3 & - \\    
+    Invalid Input & 10 & - \\    
     \bottomrule     

### 2018-08-21 paper/paper.tex
another pass

@@
 
-%% \author{
-%% \IEEEauthorblockN{Sabrina Souto}
-%% \IEEEauthorblockA{State University of Para\'iba\\
-%% Para\'iba, Brazil\\
-%% sabrinadfs@gmail.com}
-%% \and
-%% \IEEEauthorblockN{Marcelo d'Amorim}
-%% \IEEEauthorblockA{Federal University of Pernambuco\\
-%%   Pernambuco, Brazil\\
-%%   damorim@cin.ufpe.br}
-%% \and
-%% \IEEEauthorblockN{Rohit Gheyi}
-%% \IEEEauthorblockA{Federal University of Campina Grande\\
-%%   Para\'iba, Brazil\\
-%%   rohit@dsc.ufcg.edu.br}
-%% }
+\author{
+\IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
+\IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
+\{isol2,damorim\}@cin.ufpe.br}
+}
 
@@
 leveraging implementation diversity. We organized our study in three
-parts. First, we report on the stability of the engines we analyzed
+parts. First, we report on the conformance of the engines we analyzed
 using the official Test262 conformance test suite for
@@
 suites written for a given engine cover scenarios and corner cases
-uncovered by another engine. To sum, we conjecture that test cases
-written for one engine could reveal bugs in different engines as
-opposed to only manifesting false alarms. Third, we analyzed the
+uncovered by another engine.\Comment{ To sum, we conjecture that test
+  cases written for one engine could reveal bugs in different engines
+  as opposed to only manifesting false alarms.} Third, we analyzed the
 impact of using cross-engine differential testing to find bugs
-(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
-is that black-box fuzzers could expose important bugs.
+(Section~\ref{sec:cross-engine-diff-testing-results}). Differential
+testing has been used in several contexts to address the oracle
+problem~\cite{barr-etal-tse2015}. Intuitively, using differential
+testing to find functional bugs across engine implementation could be
+promising.
 
@@
 status of bug reports per engine. Note that several of these reports
-were not reviewed yet, \ie, they did not receive a label ``confirmed''
-or ``rejected'' from the development team. Note also that we did not
-find bugs in the Mozilla \smonkey\ engine and that several of the bugs
-we reported were already fixed and incorporated to the latest release
-of corresponding engines.
+hold the status ``new'', which indicates that they were not reviewed
+yet by the development team. Note also that we did not find bugs in
+the Mozilla \smonkey\ engine and that several of the bugs we reported
+were already fixed and incorporated in the latest release of
+corresponding engines. Overall, discarding bug report with the ``new''
+label, we reported \noBugsTotalConfirmed{} bugs.
 
@@
 
+%% It is important to note that failures are
+%% expected as it takes time for engines to adjust to the
+%% spec.
+
 We used the official conformance test suite
 Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ standard. We ran the suite once a day for seven
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this test. However, we
+expect that results provide indication of engine's maturity. In the
+limit, it is not desirable to flood bug reports on engines at early
+stages of development. We ran the suite once a day for seven
 consecutive days from the period of 16 to 22 of August,
 2018. Table~\ref{tab:test262} shows the average number of passing
-tests over this period. It is important to note that failures are
-expected as it takes time for engines to adjust to the
-spec.\Mar{...mention the variance was negligible...} We noticed that
-all four engines we analyzed but \chakra{} use some variant of the
-Test262 suite as part of their regression process, but we used the
-same version in this experiment, the one available from the Test262
-web site~\cite{ecma262-conformance-suite}. Results show that there are
+tests over this period. The variance of results was negligible; for
+that reasons, we omited standard deviations. We noticed that all four
+engines we analyzed but \chakra{} use some variant of the Test262
+suite as part of their regression process, but we used the same
+version in this experiment; the one available from the Test262 web
+site~\cite{ecma262-conformance-suite}. Results show that there are
 still many unsupported cases as can be observed from the percentages
 in the table, but the number of passing tests is high, with
-\veight\ and \jsc\ performing better compared to others and
+\veight\ and \smonkey\ performing better compared to others and
 \chakra\ performing well worse than others. It is important to
-highlight that failures in this test suite indicates missing features
-as opposed to bugs. However, note that \chakra\ is both the engine
-that has the lowest passing ratio in the conformance test suite and
-the one we were able to find more confirmed bugs (as per
-Figure~\ref{fig:summary}). We conjecture that the development age of
-the engine--Chakra is the newest engine\Fix{find DOB of
-  Chakra}--justify both observations.
+highlight that failures in this conformance test suite indicates
+missing features as opposed to bugs. However, note that \chakra\ is
+both the engine that has the lowest passing ratio in the conformance
+test suite and the one we were able to find more bugs. Although it is
+possible to find correlation between the percentage of passing tests
+in Test262 (as per Table~\ref{tab:test262}) and reliability as
+measured by the number of bugs found (as per
+Figure~\ref{fig:summary}), we do not not expect causality. We
+conjecture that the development age of the engine--Chakra is the
+newest engine\Fix{find DOB of Chakra}--justify the incidental
+correlation.
 
@@
 
-\Mar{remember to say that we use dataset Table II''compile-in-all''.}
-
-This section reports the results of test transplantation, \ie{}, we
-analyzed the failures observed when running a test suite on an engine
-other than the engine where the test suite
-originated.
-
-Table~\ref{tab:cross-testing} shows the number of failures for each
-pair of test suite and engine. The first column shows the test suites
-and the first row shows the engines that run those tests. We use a
-dash (``-'') to indicate that we did not consider the combinations
-that associated a test suite with its parent engine; failures in those
-cases would either indicate regressions or flaky tests as opposed to
-an unknown bug for that engine. We did not run the test cases that
-fail on its parent engine in any other engines; we wanted all tests to
-pass on their parent engine as a failure in that case would be a
-stronger indicative of a bug. In total, 64 test cases were discarded
-for that reason--6 from \jsc{} and 57 from \smonkey. In total, 7,029
-test files (\ie{}, 38369-31276-64) were considered in this experiment,
-which involved 24,922 test runs (\ie, (7029*4)-1021-57-2116).  Of
-these, 812 failures were observed (3.25\% of the runs) across
-\textbf{543} distinct files (7.72\% of the files). We analyzed each of
-these file in separate to identify if the failure was fault-revealing
-or a false positive.
+This section reports results of test transplantation. We analyzed the
+failures observed when running a test suite original from a given
+engine in another engine. Intuitively, we want to assess how promising
+is to use knowledge of developers of a given engine to find bugs in a
+different engine.
+
+Table~\ref{tab:cross-testing} shows the number of failures observed
+for each pair of test suite and engine. The first column shows the
+test suites and the first row shows the engines that run those
+tests. We use a dash (``-'') to indicate that we did not consider the
+combinations that associate a test suite with its parent engine;
+failures in those cases would either indicate regressions or flaky
+tests as opposed to unknown bugs for that engine. We did not run test
+cases that fail on its parent engine in any other engines; we wanted
+all tests to pass on their parent engine as that would indicate that
+the test case is coherent and can be used. In total, 64 test cases
+were discarded for that reason--6 from \jsc{} and 57 from
+\smonkey. Furthermore, we required that a test does not manifest
+compile errors as we want to focus on bugs in code not in tests. For
+that reason, we used the tests listed under the column
+``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
+\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
+  ``compile-in-all'' and not ``origina'' as these numbers
+  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
+  were considered in this experiment, which involved 24,922 test runs
+  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were observed
+(3.25\% of the runs) across \textbf{543} distinct files (7.72\% of the
+files). We analyzed each of these files in separate as to classify if
+the failure was fault-revealing or a false positive.
+
+\Mar{-------------------- estou aqui}
 

### 2018-08-22 paper/paper.tex
pass on results

@@
   were considered in this experiment, which involved 24,922 test runs
-  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were observed
-(3.25\% of the runs) across \textbf{543} distinct files (7.72\% of the
-files). We analyzed each of these files in separate as to classify if
-the failure was fault-revealing or a false positive.
-
-\Mar{-------------------- estou aqui}
-
-We observed from the table that, considering this dataset, the Mozilla
-\smonkey\ was the engine that failed the least whereas the Microsoft
-engine \chakra\ failed the most. The \smonkey\ test suite also
-revealed more failures than any other, perhaps as expected,
-considering that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
+  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
+manifested (3.25\% of the runs) across \textbf{543} distinct files
+(7.72\% of the files). A developer with experience in \js\ analyzed
+each of these files in separate as to classify if the failure was
+fault-revealing or not (\ie{}, a false positive).  We observed from
+the table that, considering this dataset, the Mozilla \smonkey\ was
+the engine that failed the least whereas the Microsoft engine
+\chakra\ failed the most. The \smonkey\ test suite also revealed more
+failures than any other, as expected, considering that it is the suite
+with more tests (see Table~\ref{tab:test-suites}).
 
@@
 The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
-false and true positives observed with test transplantation. The top
-piechart shows false alarms, which means that all
-``transplanted'' tests should have passed in these cases. The absolute
-number of tests in each category is shown in parentheses to the
-right-side of each slice label, naming the source of false
-positive. The sources are as follows:
+distribution of false and true positives in this experiment. The
+piechart at the top shows false alarms. The absolute number of tests
+in each category is shown in parentheses to the right-side of each
+slice label, which names the source of false positive. The sources of
+false positives are as follows:
 
@@
     original engine and that has an effect in the test outcome.  The
-    test may fail to finish at the time budget or runs out of
-    memory. For example, a test case from \jsc{} defines a function
-    with a tail-call recursion. The test fails in all engines but
-    \jsc{}, which implements tail-call optimization.
-
-    %% \Igor{
-    %%   For example, a testcase from \jsc{} suite explores the tail call
-    %%   to optimize the recursion, the test uses a recursive function that
-    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
-    %%   only the \jsc{} supports tail-call optimization and the testcase 
-    %%   passes without failures. Another case can be found in \jerry{} suite
-    %%   that uses a repetition statement to concatenate long strings 
-    %%   exponentially, causing an out of memory error. The engines used 
-    %%   supports the flags to increase memory, however we prefer to use 
-    %%   the default engine build.
-    %% }
+    test may fail to finish at the specified time budget or it exceeds
+    the memory budget. For example, a test case from the \jsc{} suite
+    defines a function with a tail-call recursion. The test fails in
+    all engines but \jsc{}, which implements tail-call optimization,
+    which enables the test to finish execution fast.
 
@@
     part of the official spec, but is not implemented in the target
-    engine. For example, at the time of writing, \chakra{} does not
-    implement by default various properties from the \mcodeid{Symbol}
-    object. These properties are only available activating ES6
-    experimental mode with the flag \CodeIn{-ES6Experimental}.
-
-  \item \textbf{Unknown.} This category corresponds to the cases we
-    were unable to confidently diagnose the failure.
-
-  %% \item \textbf{Error message mismatch.} Test fails because it
-  %%   compares an error message, which is not portable across
-  %%   engines. For example, \Igor{
-  %%     a test from the engine \jsc{} uses an assert function called
-  %%     \CodeIn{shouldThrow} that expects an specific error message. In this test, 
-  %%     all engines throws the Error as expected, however only the message 
-  %%     on \jsc{} engine match with the string expected in the test case.
-  %%   }
+    engine yet. For example, at the time of writing, \chakra{} does
+    not implement by default various properties from the
+    \mcodeid{Symbol} object. These properties are only available
+    activating the ES6 experimental mode with the flag
+    \CodeIn{-ES6Experimental}.
+
+  \item \textbf{Unknown.} This category includes the cases we were
+    unable to confidently diagnose the failure but we suspected it was
+    a false alarm.
+
 \end{itemize}
 
-We observed that the sources of false positives were relatively
-uniformly distributed, with the categories ``Unknown'' and
-``Undefined'' holding more representation with \Fix{X and Y} reports,
-respectively. Considering the true positives, we found a reasonable
-number of duplicate reports, but not enough high to justify attempting
-to automate the detection of duplicates. Section~\ref{sec:bugs}
-exemplifies cases of false and true positives.
+We observed that ``Unknown'' and ``Undefined'' were the most
+predominant sources of false positives. Considering true positives, we
+found a reasonable number of duplicate reports, but not enough high to
+justify attempting to automate the detection of duplicates.
 
@@
 the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
-''Fixed''), column ``Url'' shows the web address for the corresponding
-post in the bug tracking system where the discussion thread with
-engine developers can be found (de-anonymized upon request), column
+''Fixed''), column ``Url'' shows the web address for the
+bug report entry in the bug tracking system (de-anonymized upon request), column
 ``Severity'' shows the severity level for confirmed bugs, and,
 finally, column ``Suite'' shows the name of the engine that originated
-the test. Considering severity levels, it is important to note that
-\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
-\chakra{}~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
-use only two. As usual, the smallest the severity value the highest
-the severity of the bug. We use a dash (``-'') as the severity level
-for bugs with pending confirmation.
-
-Of the \Fix{17} bugs we reported with test transplantation, \Fix{9}
-were analyzed and moved from the status ``New'' to ``Confirmed''
-(\ie{}, no bug we reported was rejected). Of these, \Fix{8} of them
-are severity-2 bugs.  \chakra{} was the engine with the highest number
-of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
+the test.
+
+Considering severity levels, it is important to note that \jsc{} uses
+five levels~\cite{jsc-severity} whereas
+\chakra{}~\cite{chakra-severity} and
+\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
+smallest the severity value the highest the severity of the bug. We
+use a dash (``-'') as the severity level for bugs with pending
+confirmation.  No bug we reported in this experiment was rejected.  Of
+the \Fix{17} bugs we reported in this experiment, \Fix{9} were
+analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
+\Fix{8} are severity-2 bugs.  \chakra{} was the engine with the
+highest number of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
 fixed. Considering the remaining engines, \veight{} confirmed one
 bug. Curiously, Google engineers confirmed that report in a few
-hours. Although we did not find any showstopper critical bugs, most of
-the bugs are seemingly important as per the categorization given by
-engineers. Analyzing the issue tracker of \chakra, we found that
-severity-1 bugs are rare.
+hours. We found that development teams of other engines, specially
+\jsc\, took much longer to analyze bug reports as can be observed by
+some pending reports from April 2018. Although we did not find any
+showstopper critical bugs, most of the bugs are seemingly important as
+per the categorization given by engineers. Analyzing the issue tracker
+of \chakra, we found that severity-1 bugs are rare.
+
+Overall, we found these results promising given that precision (\ie{}
+the ratio of true positives over all reports) needs to take into
+account the cost of inspecting the warning~\cite{harman-ohearn-2018};
+it took a week for the developer to inspect the set of warnings
+entirely. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
+seems a low rate, but it took approximately \Fix{x} days to find
+\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} show samples
+of false and true positives.
 
@@
 inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle (see Figure~\ref{fig:workflow}).
+outcomes with a differential oracle.  We configured our infrastructure
+(see Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files
+per input file, \ie{}, the number of fuzzing iterations can exceed the
+number above as we discard syntactically invalid files.
 
 \subsubsection{Methodology}
-The methodology we used to assess the effectiveness of cross-engine
-differential testing is as follows. To avoid experimental noise, we
-only fuzz test files that pass in all engines. The intuition is that
-we wanted to avoid the scenario where fuzzing produces a
-fault-revealing input based on a test that was already
-fault-revealing. This decision ensures that we can establish
-cause-effect relationship between fuzzing and the observation of
-discrepancy. Column ``no-fail-in-all'' from
-Table~\ref{tab:test-suites} shows that a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction.
+The methodology we used to assess effectiveness of this technique is
+as follows. To avoid experimental noise, we only fuzz test files that
+pass in all engines.  This corresponds to the tests appearing under
+the column ``no-fail-in-all'' from Table~\ref{tab:test-suites}--a
+total of \totalTestFilesPassInAll\ tests satisfy this restriction.
+The intuition is that we wanted to avoid the scenario where fuzzing
+produces a fault-revealing input based on a test that was already
+revealing failures on some engine. This decision ensures that we can
+establish cause-effect relationship between fuzzing and the
+observation of discrepancy.
 
@@
 \noindent\textbf{Exploratory Phase.} For the first three months of the
-study, our inspection process was exploratory.  Our goal in this phase
-was to learn the extent to which \lo\ warnings could reveal bugs. We
-realized that if we found that the ratio of bugs from \lo\ warnings
-was rather low, we could focus our inspection efforts only on
-\hi\ warnings. That finding would be important to reduce inspection
-cost and guide future developments of this approach. To run this
-experiment, we trained eight students in analyzing the warnings that
-our infrastructure produces. The students were enrolled in a
+study, our inspection process was exploratory.  In this phase, we
+wanted to learn whether or not black-box fuzzers could reveal real
+bugs and how effective \lo\ warnings were relative to
+\hi\ warnings. Considering the choice of fuzzers, we did find several
+bugs with \radamsa\, but only some with \quickfuzz. The rationale for
+studying the the \hi\ and \lo\ warning classification was that if we
+found that the ratio of bugs from \lo\ warnings was rather low, we
+could focus our inspection efforts only on \hi\ warnings as we
+expected the number of warnings to increase dramatically compared to
+the previous experiment. That finding would be important to reduce
+inspection cost and guide future developments of this approach. To run
+this experiment, we trained eight students in analyzing the warnings
+that our infrastructure produces. The students were enrolled in a
 graduate-level testing class. We listed warnings in a spreadsheet and
-requested students to update an ``owner'' column indicating who was
-working on it, but we did not enforce an order on the warnings the
-students should inspect. Recall from Section~\ref{sec:clusterization}
-that we clustered \lo\ warnings in buckets. For that reason, we only
-listed one \lo\ warning per representative class/bucket in the
-spreadsheet. First, we explained the possible sources of false alarms
-with examples and then we asked the students to use the following
-procedure when finding a suspicious warning. Analyze the parts of the
-spec related to the problem and, if still suspicious, look for
-potential duplicates on the bug tracker of the affected engine using
-related keywords. If none was reported, indicate in the spreadsheet
-that that warning is potentially fault-revealing. We encouraged
-students to use lithium~\cite{lithium} to minimize long test cases;
-the tests from the Mozilla suite are often longer than others. Only
-after the co-authors checked the potential bugs, a bug report was
-filed.
+requested the students to update an ``owner'' column indicating who
+was working on it, but we did not enforce a strict order on the
+warnings the students should inspect. Recall from
+Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
+buckets. For that reason, we only listed one \lo\ warning per
+representative class/bucket in the spreadsheet. First, we explained,
+through examples, the possible sources of false alarms they could find
+and then we asked the students to use the following procedure when
+finding a suspicious warning. Analyze the parts of the spec related to
+the problem and, if still suspicious, look for potential duplicates on
+the bug tracker of the affected engine using related keywords. If none
+was reported, indicate in the spreadsheet that that warning is
+potentially fault-revealing. We encouraged students to use
+lithium~\cite{lithium} to minimize long test cases; the tests from the
+Mozilla suite are often longer than others. Only after the co-authors
+checked the potential bugs, a bug report was filed. Each student found
+at least one bug using this methodology.
 
@@
 
-\subsubsection{Results} Table~\ref{tab:summary-lo} shows statistics of \lo\ warnings obtained
-when fuzzing inputs with different tools. Column ``\# buckets'' show
-the number of buckets associated with ``\lo'' warnings whereas column
-``avg. \# files per bucket'' show the average number of files per
-bucket. Note that \Fix{...}
+\subsubsection{Results} In this section we discuss results obtained
+across these two phases of the experiment. Table~\ref{tab:summary-lo}
+shows statistics of \lo\ warnings obtained when fuzzing inputs with
+different tools. Column ``\# buckets'' shows the number of buckets
+associated with ``\lo'' warnings, column ``\# files'' shows the total
+number of files involved in these warnings, and column ``avg. \# files
+per bucket'' show the average number of files per bucket. Note that
+the difference of files per bucket across fuzzers was not very
+significant.
 
@@
   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-  \begin{tabular}{crr}
+  \begin{tabular}{crrr}
     \toprule
-    & \# buckets & avg. \# files per bucket \\
-    \midrule
-    \radamsa{} & \Fix{82} & \Fix{3 (241/82)}\\
-    \quickfuzz{} & \Fix{38} & \Fix{2 (87/38)} \\
+    & \# buckets & \# files & avg. \# files per bucket \\
+    \midrule
+    \radamsa{} & 82 & 241 & 2.9 \\
+    \quickfuzz{} & 38 & 87 & 2.3 \\
     \bottomrule
@@
 
-Table~\ref{tab:summary-hi} shows the number of \hi\ warnings reported
-per engine. Recall that we did not cluster \hi\ warnings as there was
-not clear clustering criteria to use for that. Note that \Fix{...}
+Table~\ref{tab:summary-hi} shows statistics for \hi\ warnings; recall
+from Section~\ref{sec:clusterization} that we do not cluster
+\hi\ warnings\Comment{ as there was no clear clustering criteria to
+  use for that}. This table breaks down \hi\ warning by the affected
+engine, \ie, the engine manifesting a distinct output among those
+analyzed. Column ``+1'' show the cases where more than one engine
+disagree on the output. Note that the ordering of engines considering
+this metric is consistent with the one observed on
+Table~\ref{tab:cross-testing}, with \chakra\ and then \jsc\ associated
+with more warnings/failures compared to other engines.
+%\veight\ and \smonkey.
 
@@
     \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & 2+\\
+    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
     \midrule
@@
 
-\begin{table}[t]
+\begin{table}[h]
   \centering

### 2018-08-22 paper/paper.tex
pass on results

@@
 
-This section reports results of test transplantation. We analyzed the
-failures observed when running a test suite original from a given
-engine in another engine. Intuitively, we want to assess how promising
-is to use knowledge of developers of a given engine to find bugs in a
-different engine.
+This section reports results of test transplantation. More
+specifically, we analyzed the failures observed when running a test
+suite original from a given engine in another engine. Intuitively, we
+want to assess how effective is the idea of cross-fertilization of
+knowledge among \js\ developers.
+
+\vspace{0.5ex}
+\subsubsection{Methodology}
+\label{sec:methodology}
+In this experiment we analyzed each failure observed in a test
+execution. A developer with experience in \js\ analyzed each files in
+separate and classified the failure as potentially fault-revealing or
+not (\ie{}, a false positive). The co-authors supervised the
+classification process as to validate correctness. For the cases the
+developer classified the failures as potentially fault-revealing, one
+of the co-authors carefully inspected the case and reported the bug
+(or re-classified the failure as a false alarm).
+
+\vspace{0.5ex}
+\subsubsection{Results}
+\label{sec:results}
 
@@
 manifested (3.25\% of the runs) across \textbf{543} distinct files
-(7.72\% of the files). A developer with experience in \js\ analyzed
-each of these files in separate as to classify if the failure was
-fault-revealing or not (\ie{}, a false positive).  We observed from
+(7.72\% of the files). We observed from
 the table that, considering this dataset, the Mozilla \smonkey\ was
@@
 
-The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
-distribution of false and true positives in this experiment. The
-piechart at the top shows false alarms. The absolute number of tests
-in each category is shown in parentheses to the right-side of each
-slice label, which names the source of false positive. The sources of
-false positives are as follows:
+The sources of false positives found in this experiment are as
+follows: \textbf{Undefined Behavior.} False positives of this kind are
+manifested when tests cover implementation-dependent behavior, as
+defined in the ECMA262 specification~\cite{ecmas262-spec}. For
+example, one of the tests from \jerry\ uses the function
+\CodeIn{Number.toPrecision([precision])}, which translates a number to
+a string, considering a given number of significant digits. The
+floating-point approximation of the real value is
+implementation-dependent, making the test to pass only in \chakra\ for
+that test. As another example, some tests from \Fix{Y} use the
+implementation-dependent description message\Mar{what is the name of
+  the property?} encapsulated in an \CodeIn{Error} object in
+assertions. As such, those tests fail in all engines but
+\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
+    error.}.} False positives of this kind manifest because the engine
+that runs the test does not optimize the code as the original engine
+and that has an effect in the test outcome.  The test may fail to
+finish at the specified time budget or it exceeds the memory
+budget. For example, a test case from the \jsc{} suite defines a
+function with a tail-call recursion. The test fails in all engines but
+\jsc{}, which implements tail-call optimization, which enables the
+test to finish execution fast. \textbf{Not implemented.} False
+positives of this kind manifest when a test fails because it covers a
+function that is part of the official spec, but is not implemented in
+the target engine yet. For example, at the time of writing, \chakra{}
+does not implement by default various properties from the
+\mcodeid{Symbol} object. These properties are only available
+activating the ES6 experimental mode with the flag
+\CodeIn{-ES6Experimental}. \Mar{revise this.}\textbf{Unknown.} This
+category includes the cases we were unable to confidently diagnose the
+failure but we suspected it was a false alarm.
 
@@
 
-\begin{itemize}
-  \item \textbf{Undefined Behavior.} False positives of this kind are
-    manifested when tests cover implementation-dependent behavior, as
-    defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-    example, one of the tests from \jerry\ uses the function
-    \CodeIn{Number.toPrecision([precision])}, which translates a
-    number to a string, considering a given number of significant
-    digits. The floating-point approximation of the real value is
-    implementation-dependent, making the test to pass only in
-    \chakra\ for that test. As another example, some tests from
-    \Fix{Y} use the implementation-dependent description message\Mar{what is the
-      name of the property?} encapsulated in an \CodeIn{Error} object
-    in assertions. As such, those tests fail in all engines but \Fix{Y}.
-
-  \item \textbf{Timeout/OME\footnote{ome is for out of memory
-      error.}.} False positives of this kind manifest because the
-    engine that runs the test does not optimize the code as the
-    original engine and that has an effect in the test outcome.  The
-    test may fail to finish at the specified time budget or it exceeds
-    the memory budget. For example, a test case from the \jsc{} suite
-    defines a function with a tail-call recursion. The test fails in
-    all engines but \jsc{}, which implements tail-call optimization,
-    which enables the test to finish execution fast.
-
-  \item \textbf{Not implemented.} False positives of this kind
-    manifest when a test fails because it covers a function that is
-    part of the official spec, but is not implemented in the target
-    engine yet. For example, at the time of writing, \chakra{} does
-    not implement by default various properties from the
-    \mcodeid{Symbol} object. These properties are only available
-    activating the ES6 experimental mode with the flag
-    \CodeIn{-ES6Experimental}.
-
-  \item \textbf{Unknown.} This category includes the cases we were
-    unable to confidently diagnose the failure but we suspected it was
-    a false alarm.
-
-\end{itemize}
-
-We observed that ``Unknown'' and ``Undefined'' were the most
-predominant sources of false positives. Considering true positives, we
-found a reasonable number of duplicate reports, but not enough high to
-justify attempting to automate the detection of duplicates.
+The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
+distribution of false and true positives in this experiment. The
+piechart at the top shows false alarms. The absolute number of tests
+in each category is shown in parentheses to the right-side of each
+slice label naming the source of false positive.  We observed that
+``Unknown'' and ``Undefined'' were the most predominant
+sources. Considering true positives, we found a reasonable number of
+duplicate reports, but not enough high to justify attempting to
+automate the detection of duplicates.
 
@@
 
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
-with test transplantation. The first column shows the identifier we
+Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
+test transplantation. The first column shows the identifier we
 assigned to the bug, column ``Date'' shows the date the bug was
@@
 the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
-''Fixed''), column ``Url'' shows the web address for the
-bug report entry in the bug tracking system (de-anonymized upon request), column
+''Fixed''), column ``Url'' shows the web address for the bug report
+entry in the bug tracking system (de-anonymized upon request), column
 ``Severity'' shows the severity level for confirmed bugs, and,
 finally, column ``Suite'' shows the name of the engine that originated
-the test.
-
-Considering severity levels, it is important to note that \jsc{} uses
-five levels~\cite{jsc-severity} whereas
+the test. Considering severity levels, it is important to note that
+\jsc{} uses five levels~\cite{jsc-severity} whereas
 \chakra{}~\cite{chakra-severity} and
@@
 analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
-\Fix{8} are severity-2 bugs.  \chakra{} was the engine with the
-highest number of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
-fixed. Considering the remaining engines, \veight{} confirmed one
-bug. Curiously, Google engineers confirmed that report in a few
+\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
+critical bugs, most of the bugs are seemingly important as per the
+categorization given by engineers. Analyzing the issue tracker of
+\chakra, we found that severity-1 bugs are rare. Considering the bugs
+confirmed by developers, \chakra{} was the engine with the highest
+number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
+remaining engines, \veight{} developers confirmed \Fix{one} bug we
+reported. Curiously, Google engineers confirmed that report in a few
 hours. We found that development teams of other engines, specially
 \jsc\, took much longer to analyze bug reports as can be observed by
-some pending reports from April 2018. Although we did not find any
-showstopper critical bugs, most of the bugs are seemingly important as
-per the categorization given by engineers. Analyzing the issue tracker
-of \chakra, we found that severity-1 bugs are rare.
-
-Overall, we found these results promising given that precision (\ie{}
+some pending reports from April 2018.
+
+Overall, we found these results promising given that precision (\ie{},
 the ratio of true positives over all reports) needs to take into
-account the cost of inspecting the warning~\cite{harman-ohearn-2018};
-it took a week for the developer to inspect the set of warnings
-entirely. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
+account the cost of inspecting the failure~\cite{harman-ohearn-2018};
+it took a week for the developer to inspect the entire set of
+failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
 seems a low rate, but it took approximately \Fix{x} days to find
-\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} show samples
+\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
 of false and true positives.
+
+\begin{center}
+  \fbox{
+    \begin{minipage}{8cm}
+      \textit{Summary:}~Test transplantation is effective at finding
+      functional bugs. Although the inspection cost is non-negligible,
+      the approach was able to reveal several bugs in widely popular
+      engines.
+      \end{minipage}
+    }
+\end{center}
 
@@
 
+\vspace{0.5ex}
 \subsubsection{Methodology}
@@
 
-\vspace{1ex}
+\vspace{0.5ex}
 \noindent\textbf{Exploratory Phase.} For the first three months of the
@@
 
-\vspace{1ex}
+\vspace{0.5ex}
 \noindent\textbf{Non-Exploratory Phase.} Results obtained in the
@@
 
+\vspace{0.5ex}
 \subsubsection{Results} In this section we discuss results obtained
@@
 number of files involved in these warnings, and column ``avg. \# files
-per bucket'' show the average number of files per bucket. Note that
-the difference of files per bucket across fuzzers was not very
-significant.
+per bucket'' show the average number of files per bucket. Note that,
+although the number of buckets and files differ substantially across
+fuzzers, the difference of files per bucket was negligible.
 
@@
 
-Table~\ref{tab:summary-hi} shows statistics for \hi\ warnings; recall
+Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
 from Section~\ref{sec:clusterization} that we do not cluster
@@
   use for that}. This table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting a distinct output among those
+engine, \ie, the engine manifesting distinct output among those
 analyzed. Column ``+1'' show the cases where more than one engine
@@
 this metric is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and then \jsc\ associated
-with more warnings/failures compared to other engines.
+Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
+and second place, respectively, in number of warnings (resp.,
+failures) compared to other engines.
 %\veight\ and \smonkey.
@@
 Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. A false positive is a bucket that did not lend
-itself in a bug report. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. The source ``Invalid Input''
-indicates that the test violated some part of the specification. For
-example, the test indirectly invoked some function with unexpected
-arguments\Fix{provide concrete example}. The source ``Upcoming
-Feature'' indicates that the test fails because it uses a feature that
-is available in the original engine, but it is still not standard, and
+positives per source. The sources of imprecision are as defined in
+Section~\ref{sec:transplantation} with the addition of three new
+sources, which we did not observe before. These sources are
+highlighted with a ``*'' in the table. The source ``Invalid Input''
+indicates that the test input violated some part of the
+specification. For example, the test indirectly invoked some function
+with unexpected arguments; this happens because fuzzing is not
+sensitive to function specifications. The source ``Upcoming Feature''
+indicates that the test fails because it uses a feature that is
+available in the original engine, but it is still not standard, and
 the target engine does not support that feature. For example,
-\Fix{provide concrete example}
+\Fix{provide concrete example}. \Fix{explain error message mismatch}
 
@@
     & \radamsa\ & \quickfuzz\ \\
-    Undefined & 18 & - \\
+    Undefined Behavior & 18 & - \\
     Timeout/OME & 23 & - \\
     Not Implemented & 19 & - \\
-    Upcoming Feature & - & - \\
-    Error Message Mismatch & 3 & - \\    
-    Invalid Input & 10 & - \\    
+    * Invalid Input & 10 & - \\    
+    * Upcoming Feature & - & - \\
+    * Error Message Mismatch & 3 & - \\        
     \bottomrule     
@@
 
-Table~\ref{tab:bugs} shows the list of bugs we reported with
-differential testing across five months of analysis. The table is
+Table~\ref{tab:bugs} shows the list of bugs we reported. The table is
 organized in two sections. The top section shows results obtained
@@
 the results obtained during the non-exploratory phase. The table shows
-the date the bug was reported (``Date''), the fuzzing tool used to
-detect the bug (``Fuzz''), the \js\ engine affected (``Engine''), the
-status of the bug report as of Aug. 24, 2018 (``Status''), the Url of
-the bug report (``Url''), the severity of the bug report
-(``Severity''), the priority that we assigned to the warning that
-revealed the bug (``Priority''), and the test suite from the original
-test input (``Suite'').
-
-\Mar{REVISE}So far, ten of the bugs we
-reported were confirmed, two of which were fixed. One bug report we
-submitted was rejected on the basis that the offending JS file
-manifested an expected incompatibility across engine implementations.
-Note from the table that all bug reports still waiting for
-confirmation are associated with the \jsc{} engine (JSC). A closer
-look at the JSC issue tracker showed that the triage process is very
-slow for that engine.  \Igor{ The bugs reported on \chakra{}'s bug
-  tracker was defined as confirmed, however the bugs are included on a
-  milestone for the next release following an internal priority.  } As
-of now, we did not find any new bug on \smonkey{} and V8; the bugs we
-found were duplicates and were not reported. Finally, it is worth
-noting that \Fix{11 of the 19} JS files that manifested discrepancies
-were \emph{not} produced with fuzzing (column ``Fuzz''). These are
-test files from suites of different engines. This observation
-emphasizes the importance of continuously collecting test suites from
-multiple sources; today, we use test suites from seven different open
-source engines, including a total of 30K test files.
+the date the bug was reported (``Date''), the fuzzing tool used
+(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
+bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
+(``Url''), the severity of the bug report (``Severity''), the priority
+that we assigned to the warning that revealed the bug (``Priority''),
+and the test suite from the original test input (``Suite'').
+
+So far, ten of the bugs we reported were confirmed, two of
+which were fixed. One bug report we submitted was rejected on the
+basis that the offending JS file manifested an incompatibility across
+engine implementations that was expected.  Note from the table that
+all bug reports still waiting for confirmation are associated with the
+\jsc{} engine. A closer look at the \jsc{} issue tracker showed that
+their triage process is slow relative to \chakra's.\Comment{\Igor{ The bugs
+  reported on \chakra{}'s bug tracker was defined as confirmed,
+  however the bugs are included on a milestone for the next release
+  following an internal priority.  }} As of now, we did not find any
+new bug on \smonkey{} and V8; the bugs we found were duplicates and
+were not reported.
+
+%% Finally, it is worth noting that \Fix{11 of the 19}
+%% JS files that manifested discrepancies were \emph{not} produced with
+%% fuzzing (column ``Fuzz''). These are test files from suites of
+%% different engines. This observation emphasizes the importance of
+%% continuously collecting test suites from multiple sources; today, we
+%% use test suites from seven different open source engines, including a
+%% total of 30K test files.
 

### 2018-08-23 paper/paper.tex
pass on description of fuzzers

@@
 were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only \Fix{X} of those were valid. With
-Megadeth, we were able to produce \Fix{Y, Y$>$Y?}  valid inputs as it
-contains some heuristics to circumvent violations of certain type
-rules such as \Fix{variable used must be defined?}. Nonetheless,
-running those inputs in our infrastructure we were unable to find
-discrepancies. Inspecting those inputs, we realized that they reflected
-very simple scenarios. To sum, a high percentage of inputs that
-Grammarinator and Megadeth generated were semantically-invalid that we
-needed to discard whereas the valid inputs manifested no
+with Grammarinator and only few inputs were valid. With Megadeth, we
+were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
+contains some heuristics to circumvent violations of certain typing
+rules.\Comment{ such as \Fix{variable used must be defined?}.}
+Nonetheless, running those inputs in our infrastructure we were unable
+to find discrepancies. Inspecting those inputs, we realized that they
+reflected very simple scenarios. To sum, a high percentage of inputs
+that Grammarinator and Megadeth generated were semantically-invalid
+that we needed to discard whereas the valid inputs manifested no
 discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
@@
 LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. One fundamental issue associated with generational
-fuzzers in our context is that the tests they produce do not contain
-assertions; to enable the integration of this kind of fuzzers in our
-infrastructure, we would need to look for discrepancies across
-compiler messages.  All in all, although grammar-based fuzzers have
-been shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, generating valid inputs,
-albeit promising conceptually, still requires some engineering
-effort. For this reason, we did not consider those fuzzers in this
-study.
+publicly available. Another fundamental issue associated with
+generational fuzzers in our context is that the tests they produce do
+not contain assertions; to enable the integration of this kind of
+fuzzers in our infrastructure---we would need to look for
+discrepancies across compiler error messages as opposed to assertion
+violations.  All in all, although grammar-based fuzzers have been
+shown effective to find real
+bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
+fuzzers in this study for the reasons above.
 
@@
   provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL use coverage to determine
+  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
 inputs that uncover a new branch and hence should be fuzzed more
@@
 fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing;
-we chose v8. Unfortunately, we found that most of the inputs produced
+application, we needed to instrument one runtime engine for fuzzing.
+We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
 by AFL violate the JS grammar. Furthermore, the fuzzing task can take
@@
 specific program
-functions\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown very effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For those
-reasons, coverage-based fuzzers were not considered in this study.
+functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
+that approach has shown to be effective, it requires domain knowledge
+to create the calling context to invoke the fuzz target. For that, we
+decide not to consider coverage-based in this study.
 
@@
 limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose \radamsa\ and
-\quickfuzz\ \Fix{...elaborate...} \Mar{I mention below that these
-  fuzzers ``only make valid changes in literals of the
-  language''. Please confirm and explain that still this is
-  interesting!}
+operators, which are typically simple. We chose these specific fuzzers
+because, conceptually, one complements the other. \quickfuzz\ creates
+mutations like \radamsa. In contrast to \radamsa, \quickfuzz\ is aware
+of the \js\ syntax; it is able to replace subtrees of the syntax
+tree~\cite{grieco2016quickfuzz} with trees created anew.
 

### 2018-08-23 paper/paper.tex
pass on results

--- 2018-08-22 paper/paper.tex
@@
     TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
-    29,846 & 18,943 \\
+    29,846 & 17,639 \\
     \midrule
@@
    \midrule
-   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
+   5 & 5/02  & \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
    6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
@@
    10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
-   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
+   11 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
    12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
    13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   14 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
+   14 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
    15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   16 & 8/07  & JavascriptCore & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
-   17 & 8/08  & V8 & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
-   18 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
+   16 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
+   17 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   18 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
+   19 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
+   20 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
+   21 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
+   22 & 8/22  & \jsc{} & New &  & - & \smonkey{}\\
+   \midrule
+    \multirow{3}{*}{23}  & 
+    \multirow{3}{*}{8/22} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
+    &  &
+    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
+    &  &
+    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
+   \midrule
+   24 & 8/23  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
    \bottomrule
@@
     \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
+    \midrule
+    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
+    \multirow{2}{*}{radamsa} & \chakra{} & New &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
+    & - & \multirow{2}{*}{HI} & \multirow{2}{*}{Test262}\\    
+    & & &
+    \veight{} & New &
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
+    & - &  & \\
     \midrule   

### 2018-08-23 paper/paper.tex
pass on results

@@
     \midrule
-    \jsc{} & \Fix{2278}\\
-    \veight{} & \Fix{1213} \\
-    \chakra{} & \Fix{7041} \\
-    \smonkey{} & \Fix{1761} \\
+    \jsc{} & 92\%\\
+    \veight{} & 95\% \\
+    \chakra{} & 75\% \\
+    \smonkey{} & 93\% \\
     \bottomrule 
@@
   \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
+    reports per engine.\Fix{falta add test262}}
   \begin{tabular}{crrrrr}
@@
     \midrule
-    \radamsa{} & 30 & 4 & 121 & 3 & 143\\
-    \quickfuzz{} & & & & & \\    
+    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
+    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
     \bottomrule
@@
 with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. The source ``Upcoming Feature''
+sensitive to function specifications. \Igor{devemos remover isso da 
+etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
+The source ``Upcoming Feature''
 indicates that the test fails because it uses a feature that is
 available in the original engine, but it is still not standard, and
-the target engine does not support that feature. For example,
+the target engine does not support that feature}. For example,
 \Fix{provide concrete example}. \Fix{explain error message mismatch}
@@
     * Invalid Input & 10 & - \\    
-    * Upcoming Feature & - & - \\
+    % * Upcoming Feature & - & - \\
     * Error Message Mismatch & 3 & - \\        
@@
     \midrule
+    15 & 8/23 & quickfuzz & \jsc{} & New  &
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
+    & - & HI & Test262\\
+    15 & 8/23 & quickfuzz & \veight{} & New  &
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
+    & - & HI & Test262\\
    \bottomrule

### 2018-08-23 paper/paper.tex
changes on intro

@@
 
-JavaScript (\js{}) is today one of the most popular programming
-languages around~\cite{business-insider,stackify}, with penetration in
-various segments including, web development, mobile, and, more
-recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
-interest of the community for the language encourages constant
-improvements in its specification and implementations. It is natural
-to expect that such improvements lead to sensible changes in engine
-implementation. In fact, even small changes can have high practical impact. For
-example, in October 2014 a new attribute added to Array objects
-resulted in the MS Outlook Calendar web app stop working under
+JavaScript (\js{}) is one of the most popular programming languages
+today~\cite{redmonk-javascript,business-insider,stackify}, with
+penetration in various segments including, web development, mobile,
+and, more recently, the Internet of
+Things~(IoT)~\cite{simply-technologies}. The interest of the community
+for the language encourages constant improvements in its specification
+and implementations. It is natural to expect that such improvements
+lead to sensible changes in engine implementation. In fact, even small
+changes can have high practical impact. For example, in October 2014 a
+new attribute added to Array objects resulted in the MS Outlook
+Calendar web app failing under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
@@
 legitimately fail in a different engine because of some undefined
-behavior in the spec\footnote{These cases of undefined behavior can be
-  localized by searching for the string ``implementation-dependent''
-  in the ES6 spec document~\cite{ecmas262-spec}.}. As another example,
-a test may fail because the engine does not fully implement some
-feature. The publicly-available Kangax compatibility
-table~\cite{kangax} relates \js\ features with the engines that
-support them. To sum, it is often non-trivial to assess if a test
-fails because of a bug or because of some other reason making test
-automation more challenging. Intuitively, developing reliable engines
-is difficult because specifications are intentionally incomplete--for
-development flexibility--and evolve frequently.
+behavior in the spec. These cases of undefined behavior can be
+localized by searching for the string ``implementation-dependent'' in
+the ES6 spec document~\cite{ecmas262-spec}. As another example, a test
+may fail because the engine does not fully implement some feature. The
+publicly-available Kangax compatibility table~\cite{kangax} relates
+\js\ features with the engines that support them. To sum, it is often
+non-trivial to assess if a test fails because of a bug or because of
+some other reason making test automation more challenging. Developing
+reliable engines is difficult because specifications are intentionally
+incomplete as to enable flexibility during development and because
+they evolve frequently.
 
@@
 files from a given engine have in detecting bugs in other engines. The
-intuition is that developers design test cases differently; hence
-replaying the test in a different engine may reveal unanticipated
+intuition is that developers design test cases with different
+objectives in mind. Replaying these tests, written for a given engine,
+in a different engine may reveal unanticipated
 problems. \emph{Cross-engine differential testing} evaluates the
 ability of leveraging diversity of engine implementations to find
-bugs. More precisely, it fuzzes existing test
+bugs. More precisely, this technique fuzzes existing test
 inputs~\cite{fuzz-testing-history} and then compares the output
-produced by different engines using a differential oracle. One of
-various causes of output discrepancy is a bug.
+produced by different engines using a differential oracle. The
+intuition is that \Fix{...}
+
+%One of
+%various causes of output discrepancy is a bug.
 

### 2018-08-23 paper/paper.tex
pass

@@
 
-\author{
-\IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
-\IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
-\{isol2,damorim\}@cin.ufpe.br}
-}
+%% \author{
+%% \IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
+%% \IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
+%% \{isol2,damorim\}@cin.ufpe.br}
+%% }
 
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). As the same engine is used, test outcomes are
-expected to be identical. Mozilla uses this approach since 2002 and
-have been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
+not eager JIT compilation). As the same engine is used in this
+scenario, test outcomes are expected to be identical. The Mozilla team
+uses this approach since 2002; they have been able to find over 270
+bugs since then~\cite{jsfunfuzz-at-mozilla}, including security
 bugs. Cross-engine differential testing, in contrast, has not been
-popularized to similar extent. One possible reason is that it is still
-not practical to fully automate the technique. In contrast to other
+very popularized. One possible reason is that it is still not
+practical to fully automate the technique. In contrast to other
 applications of differential testing, a number of legitimate reasons
 exist, other than a bug, for a test execution to manifest discrepancy
-(see Table~\ref{tab:false-positives}). Recently, Patra and
-Pradel~\cite{patra2016learning} explored the idea. They proposed a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies. Their main contribution is analytical whereas our main
-contribution is empirical--goal is to evaluate ability and cost of
-simple diversity-aware approaches to find bugs in \js\ engines.
+(see Tables~\ref{fig:piecharts-transplantation} and
+~\ref{tab:false-positives}).
+
+%% Recently, Patra and
+%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
+%% find cross-browser HTML+JS discrepancies. The main difference of our
+%% work to theirs is in goal; our goal is to evaluate ability and cost of
+%% simple diversity-aware approaches to find bugs in \js\ engines.
+
+%% Their main contribution was
+%% analytical whereas our main contribution is empirical--
 
@@
   \caption{\label{tab:engines}Engines analyzed.}
-  \begin{tabular}{cccr}
+  \begin{tabular}{cccrr}
     \toprule
-    Team & Name & URL & \# Stars \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & \multicolumn{1}{c}{3300+} \\
-    Google & \veight{} & \cite{v82018repo} & 9800+ \\
-%    \jerry{} & \jerry{} & \cite{jerryscript2018repo} & 3100+ \\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ \\
-%    Moddable & XS & \cite{xs2018repo} & 140+ \\
-    %% \midrule
-    %% \multirow{2}{*}{Mozilla} & Rhino & \cite{rhino2018repo} & 1800+ \\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & \multicolumn{1}{c}{1100+} \\
+    Team & Name & URL & \# Stars  & DOB \\
+    \midrule
+    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
+    \multicolumn{1}{c}{3300+} & Jun 2001\\
+    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
+    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
+    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
+    \multicolumn{1}{c}{1100+} & Mar 1996\\
    \bottomrule     
@@
 fuzzers require no instrumentation and domain-knowledge. They mutate
-\emph{existing} inputs randomly. The strength of the approach is
+existing inputs randomly. The strength of the approach is
 limited by the quality of the test suite and the supported mutation
@@
 because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. In contrast to \radamsa, \quickfuzz\ is aware
+mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
 of the \js\ syntax; it is able to replace subtrees of the syntax
@@
 \label{sec:methodology}
-In this experiment we analyzed each failure observed in a test
-execution. A developer with experience in \js\ analyzed each files in
-separate and classified the failure as potentially fault-revealing or
-not (\ie{}, a false positive). The co-authors supervised the
-classification process as to validate correctness. For the cases the
+In this experiment, a developer with experience in \js\ analyzed each
+test file that reveals failure in a given engine and classified that
+file as potentially fault-revealing or not. The co-authors supervised
+the classification process to validate correctness. For the cases the
 developer classified the failures as potentially fault-revealing, one
-of the co-authors carefully inspected the case and reported the bug
-(or re-classified the failure as a false alarm).
+of the co-authors carefully inspected the case and reported the bug,
+if confirmed, or re-classified the failure as a false alarm.
 
@@
 activating the ES6 experimental mode with the flag
-\CodeIn{-ES6Experimental}. \Mar{revise this.}\textbf{Unknown.} This
+\CodeIn{-ES6Experimental}. \Mar{pela explicacao de
+  ``compile-in-all'', isto nao faz sentido.$\rightarrow$} \textbf{Non-Standanrd Element.} This kind
+corresponds to the cases the test case relies on some non-standard
+function or property of a standard object. \Mar{revise this.$\rightarrow$}\textbf{Unknown.} This
 category includes the cases we were unable to confidently diagnose the
@@
 
-\begin{figure}[h]
+%% \begin{figure}[h]
+%%   \centering
+%%   \subfloat[\label{fig:falsepositives}False Positives]{%
+%%     \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
+%%   }
+%%   \label{1a}\hfill
+%%   \subfloat[\label{fig:truepositives}True Positives]{%
+%%     \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
+%%   }
+%%   \label{1b}\\
+%%   \caption{\label{fig:piecharts-transplantation}False and True positives.}
+%% \end{figure}
+
+\begin{table}[h!]
+  \setlength{\tabcolsep}{4pt}    
   \centering
-  \subfloat[\label{fig:falsepositives}False Positives]{%
-    \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
-  }
-  \label{1a}\hfill
-  \subfloat[\label{fig:truepositives}True Positives]{%
-    \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
-  }
-  \label{1b}\\
-  \caption{\label{fig:piecharts-transplantation}False and True positives.}
-\end{figure}
-
-The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
-distribution of false and true positives in this experiment. The
-piechart at the top shows false alarms. The absolute number of tests
-in each category is shown in parentheses to the right-side of each
-slice label naming the source of false positive.  We observed that
-``Unknown'' and ``Undefined'' were the most predominant
-sources. Considering true positives, we found a reasonable number of
-duplicate reports, but not enough high to justify attempting to
-automate the detection of duplicates.
+  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
+  \begin{tabular}{ccr}
+    \toprule
+    & source &  \#\\
+    \midrule
+    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
+    & Timeout/OME & 13 \\
+    & Not Implemented & 21 \\
+    & Non-Standard Element & \Fix{132} \\
+    & Unknown & \Fix{-} \\
+    \midrule
+    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
+    & Bug & 24 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+%%  The piechart at the top
+%% shows false alarms. The absolute number of tests in each category is
+%% shown in parentheses to the right-side of each slice label naming the
+%% source of false positive.
 
 \begin{table}[t!]
-\setlength{\tabcolsep}{2pt}    
+\setlength{\tabcolsep}{5pt}    
 %  \vspace{-3ex}
@@
   \label{tab:test-transplantation-bugs}
-  \begin{tabular}{cccccccc}
-    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
-    \midrule    
-    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
-   2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
-   3  & 4/29 & \chakra{}  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}} & 2 & \smonkey{} \\
-   \midrule
-    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
-                       &  &
+  \begin{tabular}{rcccccc}
+    \toprule Issue\#\Comment{    & Date} & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
+    \midrule    
+    1  \Comment{& 4/18  }& JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
+   2  \Comment{& 4/23 }& \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
+
+   3  \Comment{& 4/29 }& \chakra{}  & \textbf{Confirmed}   &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}}
+    & 2 & \smonkey{} \\
+
+    \multirow{2}{*}{4}\Comment{& \multirow{2}{*}{4/29}} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
+                       &\Comment{  &}
     JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
-   \midrule
-   5 & 5/02  & \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
-   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
-   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
-   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
-   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
-   11 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
-   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
-   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   14 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
-   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   16 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
-   17 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
-   18 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
-   19 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
-   20 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
-   21 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
-   22 & 8/22  & \jsc{} & New &  & - & \smonkey{}\\
-   \midrule
-    \multirow{3}{*}{23}  & 
-    \multirow{3}{*}{8/22} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
-    &  &
+   5 \Comment{& 5/02  }& \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
+   6 \Comment{& 5/17  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
+   7 \Comment{& 5/21  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
+   8 \Comment{& 6/28  }& \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
+   9 \Comment{& 7/10  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
+   10 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
+   11 \Comment{& 7/18  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
+   12 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
+   13 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
+   14 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
+   15 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
+   16 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
+   17 \Comment{& 8/08  }& \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   18 \Comment{& 8/08  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
+   19 \Comment{& 8/16  }& \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
+   20 \Comment{& 8/22  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
+   21 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
+   22 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{?????????????????????}{???}} & - & \smonkey{}\\
+%   \midrule
+    \multirow{3}{*}{23}\Comment{& 
+    \multirow{3}{*}{8/22}} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
+    &  \Comment{&}
     \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
-    &  &
+    &  \Comment{&}
     \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
-   \midrule
-   24 & 8/23  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
+%   \midrule
+   24 \Comment{& 8/23  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
    \bottomrule
@@
 
+Table~\ref{fig:piecharts-transplantation} shows the distribution of
+false and true positives. Considering false positives, ``Undefined
+Behavior'' and ``Non-Standard Element'' were the most predominant
+sources. Considering true positives, we found a reasonable number of
+duplicate reports, but not enough high to justify attempting to
+automate the detection of duplicates.
 Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
 test transplantation. The first column shows the identifier we
-assigned to the bug, column ``Date'' shows the date the bug was
-reported in the format ``m/dd'', column ``Engine'' shows the affected
-engine, column ``Status'' indicates the status of the bug report at
-the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
-''Fixed''), column ``Url'' shows the web address for the bug report
-entry in the bug tracking system (de-anonymized upon request), column
-``Severity'' shows the severity level for confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test. Considering severity levels, it is important to note that
-\jsc{} uses five levels~\cite{jsc-severity} whereas
+assigned to the bug\Comment{, column ``Date'' shows the date the bug
+  was reported in the format ``m/dd'',} column ``Engine'' shows the
+affected engine, column ``Status'' indicates the status of the bug
+report at the time of the writing (\eg{},``New'', ``Rejected'',
+``Confirmed'', ``Fixed''). The status string appear in bold face for
+status ``Confirmed'' or higher (\ie{}, ``Assigned'' or ``Fixed'').
+Column ``Url'' shows the URL (de-anonymized upon request) for the bug report entry in the
+corresponding bug-tracking system, column ``Severity''
+shows the severity level for confirmed bugs, and, finally, column
+``Suite'' shows the name of the engine that originated the
+test. Note that bug reports \#4 and \#23 afected multiple engines.
+
+Considering severity levels, it is important to note that \jsc{}
+uses five levels~\cite{jsc-severity} whereas
 \chakra{}~\cite{chakra-severity} and
@@
 \begin{table}[h]
+  \setlength{\tabcolsep}{5pt}
   \centering
@@
 with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. \Igor{devemos remover isso da 
-etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-The source ``Upcoming Feature''
-indicates that the test fails because it uses a feature that is
-available in the original engine, but it is still not standard, and
-the target engine does not support that feature}. For example,
-\Fix{provide concrete example}. \Fix{explain error message mismatch}
+sensitive to function specifications.
+
+%% \Igor{devemos remover isso da 
+%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
+%% The source ``Upcoming Feature''
+%% indicates that the test fails because it uses a feature that is
+%% available in the original engine, but it is still not standard, and
+%% the target engine does not support that feature}. For example,
+%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
 
@@
   \caption{\label{tab:false-positives}Distribution of false
-    positives buckets per source.}
-  \begin{tabular}{crr}
+    and true positives.}
+  \begin{tabular}{ccrr}
     \toprule
-    & \radamsa\ & \quickfuzz\ \\
-    Undefined Behavior & 18 & - \\
-    Timeout/OME & 23 & - \\
-    Not Implemented & 19 & - \\
-    * Invalid Input & 10 & - \\    
-    % * Upcoming Feature & - & - \\
-    * Error Message Mismatch & 3 & - \\        
+    & & \radamsa\ & \quickfuzz\ \\
+    \midrule
+    \multirow{5}{*}{False Positives} & Undefined Behavior & 18 & - \\
+    & Timeout/OME & 23 & - \\
+    & Not Implemented & 19 & - \\
+    & * Invalid Input & 10 & - \\    
+    & * Error Message Mismatch & 3 & - \\
+    \midrule
+    \multirow{2}{*}{True Positives} & Duplicate & - \\
+    & Bug & - \\
     \bottomrule     
@@
     \midrule
-    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
-    \midrule    
+%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
+%    \midrule    
     1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
-    & 2 & LO & \jsc{} \\ 
+    & 2 & \lo{} & \jsc{} \\ 
     2  & 4/12 & radamsa & \chakra{}   & Rejected  &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
-    & - & HI & \jsc{} \\
+    & - & \hi{} & \jsc{} \\
     3  & 4/14 & radamsa & JavascriptCore  & New &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
-    } & -  & HI & \jsc{}    \\
+    } & -  & \hi{} & \jsc{}    \\
     4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
-    & 2 & HI & \jerry{}   \\
+    & 2 & \hi{} & \jerry{}   \\
     5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & 2  & HI  & \jerry{}\\
-    \midrule
+    } & 2  & \hi{}  & \jerry{}\\
     \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
@@
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
-    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
+    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
                         &                        &        &
@@
     & - &  & \\
-    \midrule
     7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
-    & 2 & LO & \smonkey{} \\
+    & 2 & \lo{} & \smonkey{} \\
     8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
-    & 3 & HI & \jerry{} \\
+    & 3 & \hi{} & \jerry{} \\
     9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
-    & 2 & HI & \veight{}\\
+    & 2 & \hi{} & \veight{}\\
     10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
-    & 2 & HI & \jsc{}\\
+    & 2 & \hi{} & \jsc{}\\
     11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
-    & 2 & HI & \jerry{}\\
+    & 2 & \hi{} & \jerry{}\\
     12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
-    & 2 & HI & \jerry{}\\
+    & 2 & \hi{} & \jerry{}\\
     13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
-    & 2 & HI & \jerry{}\\
-    \midrule        
-    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
-    \midrule
+    & 2 & \hi{} & \jerry{}\\
+%    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
     \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
@@
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
-    & - & \multirow{2}{*}{HI} & \multirow{2}{*}{Test262}\\    
+    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
     & & &
-    \veight{} & New &
+    \veight{} & \textbf{Confirmed} &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
     & - &  & \\
-    \midrule
     15 & 8/23 & quickfuzz & \jsc{} & New  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
-    & - & HI & Test262\\
-    15 & 8/23 & quickfuzz & \veight{} & New  &
+    & - & \hi{} & Test262\\
+    16 & 8/23 & quickfuzz & \veight{} & New  &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
-    & - & HI & Test262\\
+    & - & \hi{} & Test262\\
    \bottomrule
@@
 
-An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
+An example of a warning from the \hi{} group is defined in Figure~\ref{fig:hi-priority}. 
 This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
@@
   \normalsize
-  \caption{Warning captured as HI priority.}
+  \caption{Warning captured as \hi{} priority.}
   \label{fig:hi-priority}
@@
 The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}, where they proposed a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies. Their work aims at building and evaluating an
-infrastructure for differential testing of runtime engines, such as JS
-engines nd WebAssembly engines. The sensible parts of the
-infrastructure are the checks of input validity (as to reduce
-waste/cost) and output correctness (as to reduce false
-positives). Patra and Pradel work differs from ours in that their main
-contribution is analytical whereas our main contribution is
-empirical--we aim at assessing reliability of \js\ engines and find
-bugs on them using simple approaches, such as test transplantation.
+Pradel~\cite{patra2016learning}. Their work proposes a
+language-agnostic fuzzer to findcross-browser HTML+JS
+discrepancies. Their fuzzer can be used to find bugs in JS engines and
+WebAssembly engines. The sensible parts of the infrastructure they
+built are the checks of input validity (as to reduce waste/cost) and
+output correctness (as to reduce false positives). Patra and Pradel
+work is complementary to ours--in principle, we could use their fuzzer
+in our evaluation. The main difference of our work to theirs is in
+goal--we aim at assessing reliability of \js\ engines and find bugs on
+them using simple approaches whereas they aim at proposing a new
+technique.
 

### 2018-08-23 paper/paper.tex
fix results

--- 2018-08-23 paper/paper.tex
@@
    5 & 5/02  & \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
-   6 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
-   8 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
-   9 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
-   10 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
-   11 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
-   12 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
-   13 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   14 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
-   15 & 8/07  & \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   16 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
-   17 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
-   18 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
-   19 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
-   20 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
-   21 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
-   22 & 8/22  & \jsc{} & New &  & - & \smonkey{}\\
+   6 & 5/02  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=185211}{\#185211}} & - & \smonkey{}\\
+   7 & 5/17  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
+   8 & 5/21  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
+   9 & 6/28  & \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
+   10 & 7/10  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
+   11 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
+   12 & 7/18  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
+   13 & 7/18  & \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
+   14 & 8/07  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & 3 & \jerry{}\\
+   15 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
+   16 & 8/07  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & 3 & \jerry{}\\
+   17 & 8/07  & \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
+   18 & 8/08  & \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
+   19 & 8/08  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
+   20 & 8/16  & \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
+   21 & 8/22  & \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
+   22 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\   
    \midrule
@@
     &  &
-    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
+    \veight{} & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  2  & \\
     &  &
-    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
-   \midrule
-   24 & 8/23  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
+    \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  2  & \\
+   \midrule
+   24 & 8/22  & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
    \bottomrule
@@
     \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & New &
+    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
@@
     & & &
-    \veight{} & New &
+    \veight{} & \textbf{Confirmed} &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & - &  & \\
+    & 2 &  & \\
     \midrule

### 2018-08-24 paper/paper.tex
summary plots

--- 2018-08-23 paper/paper.tex
@@
 
+%Figure~\ref{fig:summary} summarizes the bugs we reported.
+
 \vspace{1ex}
-\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
-summary of the bugs we reported. The figure shows the distribution of
-status of bug reports per engine. Note that several of these reports
-hold the status ``new'', which indicates that they were not reviewed
-yet by the development team. Note also that we did not find bugs in
-the Mozilla \smonkey\ engine and that several of the bugs we reported
-were already fixed and incorporated in the latest release of
-corresponding engines. Overall, discarding bug report with the ``new''
-label, we reported \noBugsTotalConfirmed{} bugs.
-
-\begin{figure}[h]
+\noindent\textbf{Summary of Bugs.}~Figures~\ref{fig:stacked-engine}
+and~\ref{fig:stacked-technique} show bugs reports per engine and
+technique, respectively. Each stacked bar breaks down the bugs per
+status. Note that several of these bugs were already fixed and
+incorporated in the latest release of the corresponding
+engines. Overall, discarding bug report with the ``new'' status, we
+reported a total of \noBugsTotalConfirmed{} bugs. Considering the
+engines, the majority of bug reports targeted \chakra\ and
+\jsc. Considering the techniques, the number of bug reports issued
+and confirmed were similar. We found, however, that the cost of
+inspecting \Fix{...elaborate...}
+
+%% It is
+%% also worth noting that several of these reports hold the status
+%% ``new'', which indicates that they were not reviewed yet by the
+%% development team. Note also that we did not find bugs in the Mozilla
+%% \smonkey\ engine.
+
+\begin{figure}[t!]
   \centering
-  \includegraphics[trim=0 120 0 150,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked}  
-  \caption{\label{fig:summary}Summary of bug reports per engine and status.}
+  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
+    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \vspace{-5ex}
+  }\\
+  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
+    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
+    \vspace{-5ex}        
+  }
+  \caption{\label{fig:summary}Summary of bug reports.}
 \end{figure}
@@
 \begin{wraptable}[12]{r}{0.25\textwidth}
+  \vspace{-3ex}
   \centering
   \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.\Mar{Please, use percentages.}}
+    the Test262 conformance suite.}
   \small
@@
 \end{wraptable}
-
-%% It is important to note that failures are
-%% expected as it takes time for engines to adjust to the
-%% spec.
 
@@
 possible to find correlation between the percentage of passing tests
-in Test262 (as per Table~\ref{tab:test262}) and reliability as
+in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
 measured by the number of bugs found (as per
-Figure~\ref{fig:summary}), we do not not expect causality. We
-conjecture that the development age of the engine--Chakra is the
-newest engine\Fix{find DOB of Chakra}--justify the incidental
-correlation.
-
-%% The rationale is that lack of support
-%% to features (as measured by conformance testing) and reliability of
-%% engines (as measured in this study) may have some relationship.
+Figure~\ref{fig:summary}), we do not not imply causality.
 

### 2018-08-24 paper/paper.tex
abstract.tex and intro

@@
 JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{redmonk-javascript,business-insider,stackify}, with
-penetration in various segments including, web development, mobile,
+today~\cite{redmonk-javascript,business-insider,stackify} with
+penetration in various software development segments including, web, mobile,
 and, more recently, the Internet of
 Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification
-and implementations. It is natural to expect that such improvements
-lead to sensible changes in engine implementation. In fact, even small
+for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
+lead to sensible changes in engine implementations~\cite{kangax}. Even small
 changes can have high practical impact. For example, in October 2014 a

### 2018-08-24 paper/paper.tex
pass on intro

@@
 
+% ,business-insider
 JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{redmonk-javascript,business-insider,stackify} with
+today~\cite{redmonk-javascript,stackify} with
 penetration in various software development segments including, web, mobile,
@@
 new attribute added to Array objects resulted in the MS Outlook
-Calendar web app failing under
+Calendar web app, which is built in \js{}, failing under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
@@
 Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those
-bugs. It\Comment{Finding bugs in \js\ engines} is also
-challenging. For example, a test that passes in one engine could
-legitimately fail in a different engine because of some undefined
-behavior in the spec. These cases of undefined behavior can be
-localized by searching for the string ``implementation-dependent'' in
-the ES6 spec document~\cite{ecmas262-spec}. As another example, a test
-may fail because the engine does not fully implement some feature. The
-publicly-available Kangax compatibility table~\cite{kangax} relates
-\js\ features with the engines that support them. To sum, it is often
-non-trivial to assess if a test fails because of a bug or because of
-some other reason making test automation more challenging. Developing
-reliable engines is difficult because specifications are intentionally
-incomplete as to enable flexibility during development and because
-they evolve frequently.
+of applications that could be affected with those bugs. It is also
+challenging.  Specifications are intentionally incomplete as to enable
+development flexibility. In addition, they evolve frequently to
+accomodate the pressing demands from
+developers~\cite{ecmas262-spec-repo}. An official conformance test
+suites exist for \js~\cite{tc39-github}, but, naturally, many test
+scenarios are not covered in the suite. In addition, we noticed that a
+significant fraction (5 to 15\%) of the tests constantly fail on the
+most popular engines, reflecting the struggle of developers in keeping
+up with the pace of spec evolution (see Table~\ref{tab:test262}).
 
@@
 in a different engine may reveal unanticipated
-problems. \emph{Cross-engine differential testing} evaluates the
-ability of leveraging diversity of engine implementations to find
+problems. \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
 bugs. More precisely, this technique fuzzes existing test
@@
 produced by different engines using a differential oracle. The
-intuition is that \Fix{...}
+intuition is that similar inputs to those already tested may reveal
+problems. Our study measures the ability of these techniques in
+finding bugs and the impact of false positives, which
+can arise in both testing scenarios.
 
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). As the same engine is used in this
-scenario, test outcomes are expected to be identical. The Mozilla team
-uses this approach since 2002; they have been able to find over 270
-bugs since then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-very popularized. One possible reason is that it is still not
+not eager JIT compilation). A positive aspect of the aproach is that
+it can be fully automated. As the same engine is used, the outcomes of
+the test in both configurations are expected to be identical. The
+Mozilla team uses this approach since 2002; they have been able to
+find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
+security bugs. Cross-engine differential testing, in contrast, has not
+been widely popularized. One possible reason is that it is still not
 practical to fully automate the technique. In contrast to other
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}).
+~\ref{tab:false-positives}). This paper evaluates the potential
+benefits of diversity techniques, including DT. It provides data to
+support or not the decision for automation of these techniques.
 
@@
 %% LIST OF CONTRIBUTIONS
-This paper makes the following contributions.
+\emph{Contributions.}~This paper contributes the following:
 \begin{itemize}
@@
 
-  \item We offered insights on how to reduce cost of analyzing
-    warnings reported by diversity-aware techniques and make the
-    approach more practical.
+  %% \item We offered insights on how to reduce cost of analyzing
+  %%   warnings reported by diversity-aware techniques and make the
+  %%   approach more practical.
 
@@
     scripts available to the public. (upon request for anonimity.)
+
 \end{itemize}
@@
 
+For example, a test that passes in one engine could
+legitimately fail in a different engine because of some undefined
+behavior in the spec. The most recent
+\js\ specification~\cite{ecmas262-spec} documents several of these
+cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
+may fail because the engine does not fully implement some feature. The
+publicly-available Kangax compatibility table~\cite{kangax} relates
+\js\ features with the engines that support them. To sum, it is often
+non-trivial to assess if a test fails because of a bug or because of
+some other reason making test automation more challenging.
+
 \Fix{...}

### 2018-08-24 paper/paper.tex
pass on results

--- 2018-08-24 paper/paper.tex
@@
 
-%Figure~\ref{fig:summary} summarizes the bugs we reported.
-
 \vspace{1ex}
-\noindent\textbf{Summary of Bugs.}~Figures~\ref{fig:stacked-engine}
-and~\ref{fig:stacked-technique} show bugs reports per engine and
-technique, respectively. Each stacked bar breaks down the bugs per
-status. Note that several of these bugs were already fixed and
-incorporated in the latest release of the corresponding
-engines. Overall, discarding bug report with the ``new'' status, we
-reported a total of \noBugsTotalConfirmed{} bugs. Considering the
-engines, the majority of bug reports targeted \chakra\ and
-\jsc. Considering the techniques, the number of bug reports issued
-and confirmed were similar. We found, however, that the cost of
-inspecting \Fix{...elaborate...}
-
-%% It is
-%% also worth noting that several of these reports hold the status
-%% ``new'', which indicates that they were not reviewed yet by the
-%% development team. Note also that we did not find bugs in the Mozilla
-%% \smonkey\ engine.
-
-\begin{figure}[t!]
+\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows a
+summary of the bugs we reported. The figure shows the distribution of
+status of bug reports per engine. Note that several of these reports
+hold the status ``new'', which indicates that they were not reviewed
+yet by the development team. Note also that we did not find bugs in
+the Mozilla \smonkey\ engine and that several of the bugs we reported
+were already fixed and incorporated in the latest release of
+corresponding engines. Overall, discarding bug report with the ``new''
+label, we reported \noBugsTotalConfirmed{} bugs.
+
+\begin{figure}[h]
   \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
+  \includegraphics[trim=0 120 0 150,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked}  
+  \caption{\label{fig:summary}Summary of bug reports per engine and status.}
 \end{figure}
@@
 \begin{wraptable}[12]{r}{0.25\textwidth}  
-  \vspace{-3ex}
   \centering
   \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
+    the Test262 conformance suite.\Mar{Please, use percentages.}}
   \small
@@
 \end{wraptable}
+
+%% It is important to note that failures are
+%% expected as it takes time for engines to adjust to the
+%% spec.
 
@@
 possible to find correlation between the percentage of passing tests
-in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
+in Test262 (as per Table~\ref{tab:test262}) and reliability as
 measured by the number of bugs found (as per
-Figure~\ref{fig:summary}), we do not not imply causality.
+Figure~\ref{fig:summary}), we do not not expect causality. We
+conjecture that the development age of the engine--Chakra is the
+newest engine\Fix{find DOB of Chakra}--justify the incidental
+correlation.
+
+%% The rationale is that lack of support
+%% to features (as measured by conformance testing) and reliability of
+%% engines (as measured in this study) may have some relationship.
 
@@
 
-\begin{table}[t!]
-\setlength{\tabcolsep}{5pt}    
-%  \vspace{-3ex}
-%  \scriptsize
-  \centering
-  \caption{List of bug reports issued as result of test
-    transplantation. Url columns anonymized.}
-  \label{tab:test-transplantation-bugs}
-  \begin{tabular}{rcccccc}
-    \toprule Issue\#\Comment{    & Date} & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
-    \midrule    
-    1  \Comment{& 4/18  }& JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & \jerry{}      \\
-   2  \Comment{& 4/23 }& \chakra{}  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
-
-   3  \Comment{& 4/29 }& \chakra{}  & \textbf{Confirmed}   &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}}
-    & 2 & \smonkey{} \\
-
-    \multirow{2}{*}{4}\Comment{& \multirow{2}{*}{4/29}} & \chakra{} & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
-                       &\Comment{  &}
-    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
-   5 \Comment{& 5/02  }& \jsc{} & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
-   6 \Comment{& 5/17  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}} & 2 & \jsc{}\\
-   7 \Comment{& 5/21  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}} & 2 & \smonkey{}\\
-   8 \Comment{& 6/28  }& \chakra{} & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}} & 2 & \jsc{}\\
-   9 \Comment{& 7/10  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}} & 2 & \jerry{}\\
-   10 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}} & 2 & \smonkey{}\\
-   11 \Comment{& 7/18  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & \jerry{}\\
-   12 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}} & 2 & \jerry{}\\
-   13 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}} & - & \jerry{}\\
-   14 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & 2 & \jerry{}\\
-   15 \Comment{& 8/07  }& \chakra{} & New & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}} & - & \jerry{}\\
-   16 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & 2 & \jerry{}\\
-   17 \Comment{& 8/08  }& \veight{} & \textbf{Fixed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & \jerry{}\\
-   18 \Comment{& 8/08  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & \jerry{}\\
-   19 \Comment{& 8/16  }& \veight{} & WontFix & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}} & 2 & Duktape\\
-   20 \Comment{& 8/22  }& \chakra{} & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}} & 2 & \smonkey{}\\
-   21 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}} & - & \smonkey{}\\
-   22 \Comment{& 8/22  }& \jsc{} & New & \anonym{\href{?????????????????????}{???}} & - & \smonkey{}\\
-%   \midrule
-    \multirow{3}{*}{23}\Comment{& 
-    \multirow{3}{*}{8/22}} & \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}} & - & \multirow{3}{*}{\smonkey{}}\\
-    &  \Comment{&}
-    \veight{} & New & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} } &  -  & \\
-    &  \Comment{&}
-    \chakra{} & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} } &  -  & \\
-%   \midrule
-   24 \Comment{& 8/23  }& \jsc{} & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}} & - & \smonkey{}\\
-   \bottomrule
-  \end{tabular}
-\end{table}
+\input{table_transplantation}
 
@@
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & - &  & \\
+    & 2 &  & \\
     15 & 8/23 & quickfuzz & \jsc{} & New  &
@@
     & - & \hi{} & Test262\\
+    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
+    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
+    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
+    & & &
+    \jsc{} & New &
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
+    & - &  & \\
    \bottomrule

### 2018-08-24 paper/abstract.tex

@@
-JavaScript is a very popular programming language today. Several
-engine implementations compete for market dominance. Although a
-specification document and an conformance test suite exist to guide
+JavaScript is a very popular programming language today with several
+engine implementations competing for market dominance. Although a
+specification document and a conformance test suite exist to guide
 engine development, bugs occur and have important practical
-consequences. One reason for the difficulty in implementing correct
-engines stems from the fact that the specification is intentionally
+consequences. Implementing correct
+engines is challenging because the specification is intentionally
 incomplete and evolves frequently.
@@
 This paper reports on a study we ran to evaluate the importance of
-diversity to find functional bugs in JavaScript engines. For that, we used two
+diversity to find functional bugs in JavaScript engines. For that, we use two
 simple diversity-aware techniques--test transplantation and cross-engine

### 2018-08-24 paper/paper.tex

@@
 
+% ,business-insider
 JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{redmonk-javascript,business-insider,stackify}, with
-penetration in various segments including, web development, mobile,
+today~\cite{redmonk-javascript,stackify} with
+penetration in various software development segments including, web, mobile,
 and, more recently, the Internet of
 Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification
-and implementations. It is natural to expect that such improvements
-lead to sensible changes in engine implementation. In fact, even small
+for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
+lead to sensible changes in engine implementations~\cite{kangax}. Even small
 changes can have high practical impact. For example, in October 2014 a
 new attribute added to Array objects resulted in the MS Outlook
-Calendar web app failing under
+Calendar web app, which is built in \js{}, failing under
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.

### 2018-08-24 paper/paper.tex
pass on results
pass on javascript section

@@
 
-Both the specification and implementation of JavaScript are
+The specification and implementation of JavaScript are
 incomplete. Certain parts of the specification are undefined; it is
@@
 \mcodeid{for-in} loop does not clearly specify the iteration
-order~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that~\cite{for-in-undefined}.  As another
-example, the latest version of the \es{} specification states that if
-the \mcodeid{Number.toPrecision()} function is called with more than
-one argument, then the behavior is
+order of elements~\cite{so-forin-undefined,javascript-in-chrome} and different
+engines capitalize on that for optimization~\cite{for-in-undefined}.  As another
+example, the specification states that if
+the \mcodeid{Number.toPrecision()} function is called with multiple arguments then the floating-point approximation is
 implementation-dependent~\cite{es6-toPrecision}. Various other cases
@@
 as can be observed by the Kangax compatibility table~\cite{kangax}.
-
-\sloppy It is also worth noting that, as in other languages, some
+It is also worth noting that, as in other languages, some
 elements in JS have non-deterministic behavior (\eg{},
@@
 manifest this kind of
-flakiness~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
-fuzzed test files could are more likely, intuitively, to manifest
-them.
-
+flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
+fuzzed are more likely to manifest them.
 As mentioned previously, all those aspects make testing \js\ engines

### 2018-08-24 paper/paper.tex
pass on stacked data

@@
 
-\begin{table*}[h!]
-  \vspace{-3ex}
-%  \scriptsize
-  \centering
-  \caption{List of bug reports issued as result of cross-engine
-    differential testing.}
-  \label{tab:bugs}
-  \begin{tabular}{ccccccccc}
-    \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  &
-    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
-    \midrule
-%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
-%    \midrule    
-    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
-    & 2 & \lo{} & \jsc{} \\ 
-    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
-    & - & \hi{} & \jsc{} \\
-    3  & 4/14 & radamsa & JavascriptCore  & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
-    } & -  & \hi{} & \jsc{}    \\
-    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
-    & 2 & \hi{} & \jerry{}   \\
-    5  & 4/29 & radamsa & JavascriptCore  & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
-    } & 2  & \hi{}  & \jerry{}\\
-    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
-    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
-                        &                        &        &
-    JavascriptCore & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
-    & - &  & \\
-    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
-    & 2 & \lo{} & \smonkey{} \\
-    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
-    & 3 & \hi{} & \jerry{} \\
-    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
-    & 2 & \hi{} & \veight{}\\
-    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
-    & 2 & \hi{} & \jsc{}\\
-    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
-    & 2 & \hi{} & \jerry{}\\
-    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
-    & 2 & \hi{} & \jerry{}\\
-    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
-    & 2 & \hi{} & \jerry{}\\
-%    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
-    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & &
-    \veight{} & \textbf{Confirmed} &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & 2 &  & \\
-    15 & 8/23 & quickfuzz & \jsc{} & New  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
-    & - & \hi{} & Test262\\
-    16 & 8/23 & quickfuzz & \veight{} & New  &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
-    & - & \hi{} & Test262\\
-    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
-    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & & 
-    \jsc{} & New &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
-    & - &  & \\
-   \bottomrule
-  \end{tabular}
-\end{table*}
+\input{table_differential}
 

### 2018-08-24 paper/table_differential.tex

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule
%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
%    \midrule    
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & \jsc{}  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & 2  & \hi{}  & \jerry{}\\

    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule

    7 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & \textbf{\lo} & \smonkey{} \\
    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
    & 3 & \hi{} & \jerry{} \\
    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
    & 2 & \hi{} & \veight{}\\
    10 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & \hi{} & \jsc{}\\
    11 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & \hi{} & \jerry{}\\
    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & \hi{} & \jerry{}\\
    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
    & 2 & \hi{} & \jerry{}\\
    %    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\

    \midrule
    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & &
    \veight{} & \textbf{Confirmed} &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
    & 2 &  & \\
    \midrule

    15 & 8/23 & quickfuzz & \jsc{} & New  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
    & - & \hi{} & Test262\\
    16 & 8/23 & quickfuzz & \veight{} & New  &
    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
    & - & \hi{} & Test262\\

    \midrule
    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
    & & & 
    \jsc{} & New &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
    & - &  & \\
   \bottomrule
  \end{tabular}
\end{table*}

### 2018-08-24 paper/paper.tex

@@
 Test262~\cite{tc39-github} conformance test suite for the ECMA262
-specification~\cite{ecmas262-spec}. This test suite contains 87\% of
-all the tests we used. We also considered test suites of three of the
-four engines mentioned in Section~\ref{sec:methodology:engines} and
-four other engines. Table~\ref{tab:test-suites} shows the breakdown of
-tests we considered. Overall, we found a total of \totfiles{} JS
-files. Column ``original'' shows the test cases for each
-test suite. We did not consider tests from the \chakra{} repository because they depend
-on non-portable objects and notice that the number of tests in
-\veight\ is low. That happens because many tests in \veight{} are
-inherited from Mozilla and \jsc{}; we discarded those to avoid
-repetition and to give credit where it is due. Column
-``compile-in-all'' shows the number of test cases for which all four
-engines we analyzed do not throw compile-time error. We discarded
-tests that manifest compile errors as they clearly indicate missing
-features; these tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, although being part of the spec, not all
-engines currently support. Finally, column ``no-fail-in-all'' shows
-the tests for which all engines
-pass. Section~\ref{sec:transplantation} discusses these failures, some
-of which are indicative of bugs. The tests under this column will be
-used to create new, potentially fault-revealing, tests. For that, it
-is important to assure that all of them pass.
+specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
+  87\% of all the tests we used.} We also considered test suites of
+three of the four engines mentioned in
+Section~\ref{sec:methodology:engines} and four other engines. Overall,
+we selected a total of \totfiles{} JS
+files. Table~\ref{tab:test-suites} shows the breakdown of tests we
+considered. Column ``original'' shows the number of test cases for
+each test suite. We did not consider tests from the \chakra{}
+repository because they depend on non-portable objects. Notice that
+the number of tests in \veight\ is low. That happens because \veight{}
+uses many tests from Mozilla and \jsc{}; we discarded those to avoid
+repetition and to give credit where it is due. The columns
+``compile-in-all'' and ``no-fail-in-all'' correspond to the test files
+used, respectively, in the test transplantaion experiment and the
+differential testing experiment.
+
+Column ``compile-in-all'' shows the number of test cases whose
+execution does not throw errors because of an undefined variable or
+property. We capture these cases by looking for the presence of
+\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
+\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
+when test execution attempts to access an undefined variable
+(respectively, property of an object). We discarded those tests to
+avoid noise in the experiments as they clearly indicate some missing
+feature as opposed to bugs. For example, some tests use non-portable
+names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
+\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
+spec, not all engines currently support. We used the tests that lie
+within the circle that appears in the table in the evaluation of test
+transplantion, \ie{} the set ``compile-in-all'' minus set Test262. We
+did not consider tests from the conformance suite as they are more
+likely to indicate missing features as opposed to bugs. In addition,
+engine developers have access to these test and are encouraged to run
+them. Column ``no-fail-in-all'' shows the tests for which all engines
+pass. This test set is used in the evaluation of differential
+testing. Note that it is a proper subset of the ``compile-in-all''
+test set. The tests from this group are used as fuzzing seeds. The
+guarantee that they pass in all engines assures that, if discrepancies
+occur, they are related to the changes in the input as opposed to the
+original cause of failure.
 
 It is also worth mentioning that some engines use a custom shell to
-run tests, including a harness with specific assertions.  For these,
-we needed to make small changes in the testing infrastructure to be
-able to run the tests uniformly across all engines. More precisely, we
+run tests, including a harness with specific assertions.  For that, we
+needed to make minor changes in the testing infrastructure to be able
+to run the tests uniformly across all engines. More precisely, we
 needed to mock non-portable harness functions, which are only
@@
 
- %% The table shows the
- %%    number of test cases in each test suite considered: TC-39
- %%    conformance test suite, suites from engines we analyzed, and
- %%    suites from other engines.
+\newcommand\marktopleft[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-a) at (0,1.5ex) {};%
+}
+\newcommand\markbottomright[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-b) at (0,0) {};%
+    \tikz[overlay,remember picture,thick,dashed,inner sep=3pt]
+        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
+}
 
@@
     \midrule
-    \jsc{} & \cite{webkit} & 1,031 & 1,021 & 955\\
+    \jsc{} & \cite{webkit} & 1,031 &\marktopleft{c1} 1,021 & 955\\
     \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
@@
     JSI & \cite{jsi} & 99 & 63 & 63\\
-    Tiny-js & \cite{tinyjs} & 49 & 37 & 37\\
+    Tiny-js & \cite{tinyjs} & 49 & 37\markbottomright{c1} & 37\\
     % \chakra{} & \cite{chakracore} & 2632 \\
@@
 tests as opposed to unknown bugs for that engine. We did not run test
-cases that fail on its parent engine in any other engines; we wanted
-all tests to pass on their parent engine as that would indicate that
-the test case is coherent and can be used. In total, 64 test cases
+cases that fail on its parent engine in any other engine as that would indicate that
+the test case could be broken. In total, 64 test cases
 were discarded for that reason--6 from \jsc{} and 57 from

### 2018-08-24 paper/paper.tex
pass on section IV

@@
 
-Figure~\ref{fig:workflow} illustrates the infrastructure for
-differential testing, which is used in part of this study. It takes on
+\Comment{ Several fuzzing methods
+  have been proposed in the past, varying with respect to how new
+  inputs are
+  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
+
+Figure~\ref{fig:workflow} illustrates the 
+differential testing infrastructure used in part of this study. It takes on
 input a list of JS files and generates warnings on output. Boxes in
@@
 a given test input using some off-the-shelf input
-fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
-  have been proposed in the past, varying with respect to how new
-  inputs are
-  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
-Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
 The oracle checks whether or not the output produced for the fuzzed
@@
 engines or fails in all engines (\ie{}, the output is consistent), the
-infrastructure discards the test. Otherwise, it considers the input as
-potentially fault-revealing; hence interesting for human
+infrastructure ignores the input. Otherwise, it considers the input as
+potentially fault-revealing; hence, interesting for human
 inspection. The infrastructure uses the
@@
 
-Note that a number of reasons exist, other than a bug, to explain
-discrepancy (see Table~\ref{tab:false-positives}) and there is no
-clear way to distinguish false and true positives automatically. As
-such, a human needs to inspect the warning to classify the issue. To
+It is worth noting that a number of reasons exist, other than a bug,
+to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
+and ~\ref{tab:false-positives}) and there is no clear automatic
+approach to precisely distinguish false and true positives. As such, a
+human needs to inspect the warning to classify the issue. To
 facilitate inspection, we prioritized warnings and clustered them in
@@
 
-We classified warnings in two types,
-reflecting their likelihood of manifesting a real bug. Warnings of the
-kind ``\hi{}'' are associated with the cases where the test code
-executed to completion without violating any internal checks, but it
-violated assertions declared in the test itself or its harness. The
-rationale is that the input is more likely to be valid as it it did
-not raise exceptions during the execution of the application code,
-but, it manifested discrepancy through the violation of an assertion
-declared in the test. In contrast, warnings of type ``\lo{}'' are
-more likely to be asssociated with invalid inputs. They reflect the
-cases where the anomaly is observed during the execution of functions,
-which are part of the application. We found that different engines
-often check pre-conditions of those functions differently. It can
-happen, for example, that one engine enforces a weaker pre-condition
-on a function input compared to another engine and that is
-acceptable.\Comment{ For instance, it is acceptable to pass values greater than
-\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
-\Fix{z}.} In those cases, the infrastructure would observe a
-discrepancy that is more likely to be associated with an invalid input
-produced by the fuzzer, \ie{}, it is likely to be a bug in the test
-code not the engine (library or runtime) code. However, as expected, our heuristic
-is not precise---``\lo'' warnings can 
-reveal bugs. Figure~\ref{fig:lo-truepositive} shows one of these
-cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
-object and stores an 8-bit integer at the 0 position. According to the
+We classified warnings in two types, reflecting their likelihood of
+manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
+with the cases where the test code executed to completion without
+violating any internal checks, but it violated assertions declared in
+the test itself or its harness. The rationale is that the input is
+more likely to be valid as it it did not raise exceptions during the
+execution of the application code, but, it manifested discrepancy
+through the violation of an assertion declared in the test. In
+contrast, warnings of type ``\lo{}'' are more likely to be asssociated
+with invalid inputs. They reflect the cases where the anomaly is
+observed during the execution of functions, which are part of the
+application. We found that different engines often check
+pre-conditions of those functions differently. It can happen, for
+example, that one engine enforces a weaker pre-condition on a function
+input compared to another engine and that is acceptable.\Comment{ For
+  instance, it is acceptable to pass values greater than \Fix{x} to
+  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
+cases, the infrastructure would observe a discrepancy that is more
+likely to be associated with an invalid input produced by the fuzzer,
+\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
+bug in the engine code. However, as expected, our heuristic is not
+precise---``\lo'' warnings can reveal
+bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
+this example, the test instantiates an \CodeIn{ArrayBuffer} object and
+stores an 8-bit integer at the 0 position. According to the
 specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
@@
 function \CodeIn{ToIndex}, indirectly called by the test case. In this
-case, however, the \chakra{} engine did not throw any exception, which
-violates the spec. This case of undocumented precondition, reported
-and handled by developers as a bug, was fixed by developers after our bug
-report and is no longer present in the most recent release of
-\chakra. Despite that case, most bugs we found emerged from
-``\hi{}'' warnings.
+case, however, the \chakra{} engine did not throw any exception. This
+is a case of undocumented precondition, which is handled as a bug. It
+was fixed by \chakra\ developers and is no longer present in the most
+recent release of \chakra. Despite that case, most bugs we found
+emerged from ``\hi{}'' warnings.
 
@@
 this one, that has this same message signature will be included in the
-same cluster, which we may also refer as a ``bucket''.
+same ``bucket''. To maximize the hit ratio we remove references to
+code that may appear in the error messages.
 

### 2018-08-24 paper/table_differential.tex
pass on table_differential
pass on issues

@@
     & & &
-    \veight{} & \textbf{Confirmed} &
+    \veight{} & \textbf{Fixed} &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
@@
     & - & \hi{} & Test262\\
-    16 & 8/23 & quickfuzz & \veight{} & New  &
+    16 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
-    & - & \hi{} & Test262\\
+    & 2 & \hi{} & Test262\\
 

### 2018-08-24 paper/paper.tex
pass on section IV

@@
   \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}True positive example of a ``\lo''
-    warning.}
+  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
+    that led to a confirmed bug report in \chakra. The bug is caused
+    by a required precondition check in the implementation of function
+    \CodeIn{ToIndex} indirectly called by the test. }
 \end{figure}

### 2018-08-24 paper/paper.tex
pass on V.0

@@
 leveraging implementation diversity. We organized our study in three
-parts. First, we report on the conformance of the engines we analyzed
-using the official Test262 conformance test suite for
-EcmaScript~\cite{ecma262-conformance-suite}
+parts. First, we report on the conformance of the engines we studied
+using the official Test262 conformance
+suite~\cite{ecma262-conformance-suite}
 (Section~\ref{sec:stability}). In the limit, bugs would have low
@@
 obtained with test transplantation
-(Section~\ref{sec:transplantation}). The rationale is that the domain
-of possible inputs is too large; consequently, we expect that test
-suites written for a given engine cover scenarios and corner cases
-uncovered by another engine.\Comment{ To sum, we conjecture that test
-  cases written for one engine could reveal bugs in different engines
-  as opposed to only manifesting false alarms.} Third, we analyzed the
-impact of using cross-engine differential testing to find bugs
-(Section~\ref{sec:cross-engine-diff-testing-results}). Differential
-testing has been used in several contexts to address the oracle
-problem~\cite{barr-etal-tse2015}. Intuitively, using differential
-testing to find functional bugs across engine implementation could be
-promising.
+(Section~\ref{sec:transplantation}). The rationale is that developers
+consider different goals when writing test cases--suites written for a
+given engine should cover scenarios not covered by a different
+engine. Third, we analyzed the impact of using cross-engine
+differential testing to find bugs
+(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
+is that bugs may be detected using inputs which are similar to those
+already tested. Our broad goal is to evaluate ability of these simple
+diversity-aware techniques in bug finding.
 
@@
 \vspace{1ex}
-\noindent\textbf{Summary of Bugs.}~Figures~\ref{fig:stacked-engine}
-and~\ref{fig:stacked-technique} show bugs reports per engine and
-technique, respectively. Each stacked bar breaks down the bugs per
-status. Note that several of these bugs were already fixed and
-incorporated in the latest release of the corresponding
-engines. Overall, discarding bug report with the ``new'' status, we
-reported a total of \noBugsTotalConfirmed{} bugs. Considering the
-engines, the majority of bug reports targeted \chakra\ and
-\jsc. Considering the techniques, the number of bug reports issued
-and confirmed were similar. We found, however, that the cost of
-inspecting \Fix{...elaborate...}
-
+\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
+number of bug reports found per engine (\ref{fig:stacked-engine}) and
+technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
+the bugs per status (\eg{}, ``1-New''). The prefix number serves to
+indicate the ordering that status labels are assigned. Note that
+several of these reports have the label ``3-Fixed'', indicating that
+bug fixes have been incorporated into the code already.\Comment{
+  Depending on the issue date, the fix may be in the latest release of
+  the corresponding engines.} Overall, discarding bug report with the
+``1-New'' status, we reported a total of \noBugsTotalConfirmed{}
+bugs. We found that the majority of bug reports targeted the engines
+from Microsoft and Apple. Considering the techniques, the number of
+bug reports were similar, if we consider only those confirmed or
+fixed. Most of these bugs are of moderate severity. All in all, these
+simple techniques seem promising to improve reliability of engines
+that continuously evolve with their specifications.
+
+%% We found,
+%% however, that the cost of inspecting \Fix{...elaborate...}
 %% It is
@@
 
-\begin{figure}[t!]
+\begin{figure}[h!]
   \centering
@@
 
-\begin{wraptable}[12]{r}{0.25\textwidth}
-  \vspace{-3ex}
+We used the official conformance test suite
+Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this test. However, we
+expect that results provide indication of engine's maturity. In the
+\begin{wraptable}[10]{r}{0.25\textwidth}
+%  \vspace{-3ex}
   \centering
@@
   \normalsize
+  \vspace{-3ex}  
 \end{wraptable}
-
-We used the official conformance test suite
-Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this test. However, we
-expect that results provide indication of engine's maturity. In the
 limit, it is not desirable to flood bug reports on engines at early

### 2018-08-24 paper/paper.tex
halfway throw V.B.II

@@
 repetition and to give credit where it is due. The columns
-``compile-in-all'' and ``no-fail-in-all'' correspond to the test files
-used, respectively, in the test transplantaion experiment and the
-differential testing experiment.
-
-Column ``compile-in-all'' shows the number of test cases whose
-execution does not throw errors because of an undefined variable or
-property. We capture these cases by looking for the presence of
+``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
+the test transplantaion experiment and the differential testing
+experiment, respectively.
+
+Column ``pass-in-par.'' shows the number of test cases that pass in
+their parent engine. We discarded tests that fail in their parent
+engine as we could not reliably indicate the reason for the failure,
+so we assumed the test could be broken. We removed 63 test cases that
+fail for that reason--6 tests from \jsc{} and 57 tests from
+\smonkey. Column ``compile-in-all'' shows the number of test cases
+whose executions do not throw errors because of an undefined variable
+or property. We capture these cases by looking for the presence of
 \CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
@@
 \CodeIn{Error.lineNumber}) or use functions that, albeit part of the
-spec, not all engines currently support. We used the tests that lie
-within the circle that appears in the table in the evaluation of test
-transplantion, \ie{} the set ``compile-in-all'' minus set Test262. We
-did not consider tests from the conformance suite as they are more
-likely to indicate missing features as opposed to bugs. In addition,
-engine developers have access to these test and are encouraged to run
+spec, not all engines currently support. We used the
+\totalTestFilesForTestTransplantation{} tests included in the circle
+from the table in the evaluation of test transplantion, \ie{}, the
+difference between sets ``compile-in-all'' and Test262. We did not
+consider tests from the conformance suite as they are more likely to
+indicate missing features as opposed to bugs. In addition, engine
+developers have access to these test and are encouraged to run
 them. Column ``no-fail-in-all'' shows the tests for which all engines
@@
     that pass in all four engines we analyzed.}
-  \begin{tabular}{ccrrr}
+  \setlength{\tabcolsep}{2.5pt}      
+  \begin{tabular}{ccrrrr}
     \toprule
     \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{3}{c}{\# JS files} \\
-    \cline{3-5}
-                               &         & original & compile-in-all &  no-fail-in-all \\
+    \multicolumn{4}{c}{\# JS files} \\
+    \cline{3-6}
+                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
     \midrule
-    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
-    29,846 & 17,639 \\
+    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
     \midrule
-    \jsc{} & \cite{webkit} & 1,031 &\marktopleft{c1} 1,021 & 955\\
-    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
-    \veight{} & \cite{v8} & 75 & 57 & 57\\
+    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
+    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
+    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
     \midrule
-    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
-    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
-    JSI & \cite{jsi} & 99 & 63 & 63\\
-    Tiny-js & \cite{tinyjs} & 49 & 37\markbottomright{c1} & 37\\
-    % \chakra{} & \cite{chakracore} & 2632 \\
+    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
+    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
+    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
+    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
     \midrule
-     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
+     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
    \bottomrule 
@@
     by a required precondition check in the implementation of function
-    \CodeIn{ToIndex} indirectly called by the test. }
+    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
 \end{figure}
@@
 failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. We did not run test
-cases that fail on its parent engine in any other engine as that would indicate that
-the test case could be broken. In total, 64 test cases
-were discarded for that reason--6 from \jsc{} and 57 from
-\smonkey. Furthermore, we required that a test does not manifest
-compile errors as we want to focus on bugs in code not in tests. For
-that reason, we used the tests listed under the column
-``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
-\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
-  ``compile-in-all'' and not ``origina'' as these numbers
-  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
-  were considered in this experiment, which involved 24,922 test runs
-  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
-manifested (3.25\% of the runs) across \textbf{543} distinct files
-(7.72\% of the files). We observed from
-the table that, considering this dataset, the Mozilla \smonkey\ was
-the engine that failed the least whereas the Microsoft engine
-\chakra\ failed the most. The \smonkey\ test suite also revealed more
-failures than any other, as expected, considering that it is the suite
-with more tests (see Table~\ref{tab:test-suites}).
+tests as opposed to unknown bugs for that engine. As explained in
+Section~\ref{sec:seeds}, we used in this experiment the
+\totalTestFilesForTestTransplantation{} tests included in the circle
+from Table~\ref{tab:test-suites}. Running those tests we observed a
+total of 812 failures manifested across 543 distinct files (8.9\% of
+total). Table~\ref{tab:cross-testing} shows that, considering the
+engines analyzed, \smonkey\ was the engine that failed the least
+whereas \chakra\ was the engine that failed the most. The
+\smonkey\ test suite also revealed more failures than any other,
+perhaps as expected, considering that it is the suite with more tests
+(see Table~\ref{tab:test-suites}).
 

### 2018-08-25 paper/paper.tex
pass on results

--- 2018-08-24 paper/paper.tex
@@
 
-\Comment{ Several fuzzing methods
-  have been proposed in the past, varying with respect to how new
-  inputs are
-  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
-
-Figure~\ref{fig:workflow} illustrates the 
-differential testing infrastructure used in part of this study. It takes on
+Figure~\ref{fig:workflow} illustrates the infrastructure for
+differential testing, which is used in part of this study. It takes on
 input a list of JS files and generates warnings on output. Boxes in
@@
 a given test input using some off-the-shelf input
-fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+fuzzer~\cite{fuzz-testing-history}.\Comment{ Several fuzzing methods
+  have been proposed in the past, varying with respect to how new
+  inputs are
+  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
+Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
 The oracle checks whether or not the output produced for the fuzzed
@@
 engines or fails in all engines (\ie{}, the output is consistent), the
-infrastructure ignores the input. Otherwise, it considers the input as
-potentially fault-revealing; hence, interesting for human
+infrastructure discards the test. Otherwise, it considers the input as
+potentially fault-revealing; hence interesting for human
 inspection. The infrastructure uses the
@@
 
-It is worth noting that a number of reasons exist, other than a bug,
-to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
-and ~\ref{tab:false-positives}) and there is no clear automatic
-approach to precisely distinguish false and true positives. As such, a
-human needs to inspect the warning to classify the issue. To
+Note that a number of reasons exist, other than a bug, to explain
+discrepancy (see Table~\ref{tab:false-positives}) and there is no
+clear way to distinguish false and true positives automatically. As
+such, a human needs to inspect the warning to classify the issue. To
 facilitate inspection, we prioritized warnings and clustered them in
@@
 
-We classified warnings in two types, reflecting their likelihood of
-manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
-with the cases where the test code executed to completion without
-violating any internal checks, but it violated assertions declared in
-the test itself or its harness. The rationale is that the input is
-more likely to be valid as it it did not raise exceptions during the
-execution of the application code, but, it manifested discrepancy
-through the violation of an assertion declared in the test. In
-contrast, warnings of type ``\lo{}'' are more likely to be asssociated
-with invalid inputs. They reflect the cases where the anomaly is
-observed during the execution of functions, which are part of the
-application. We found that different engines often check
-pre-conditions of those functions differently. It can happen, for
-example, that one engine enforces a weaker pre-condition on a function
-input compared to another engine and that is acceptable.\Comment{ For
-  instance, it is acceptable to pass values greater than \Fix{x} to
-  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
-cases, the infrastructure would observe a discrepancy that is more
-likely to be associated with an invalid input produced by the fuzzer,
-\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
-bug in the engine code. However, as expected, our heuristic is not
-precise---``\lo'' warnings can reveal
-bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
-this example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
+We classified warnings in two types,
+reflecting their likelihood of manifesting a real bug. Warnings of the
+kind ``\hi{}'' are associated with the cases where the test code
+executed to completion without violating any internal checks, but it
+violated assertions declared in the test itself or its harness. The
+rationale is that the input is more likely to be valid as it it did
+not raise exceptions during the execution of the application code,
+but, it manifested discrepancy through the violation of an assertion
+declared in the test. In contrast, warnings of type ``\lo{}'' are
+more likely to be asssociated with invalid inputs. They reflect the
+cases where the anomaly is observed during the execution of functions,
+which are part of the application. We found that different engines
+often check pre-conditions of those functions differently. It can
+happen, for example, that one engine enforces a weaker pre-condition
+on a function input compared to another engine and that is
+acceptable.\Comment{ For instance, it is acceptable to pass values greater than
+\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
+\Fix{z}.} In those cases, the infrastructure would observe a
+discrepancy that is more likely to be associated with an invalid input
+produced by the fuzzer, \ie{}, it is likely to be a bug in the test
+code not the engine (library or runtime) code. However, as expected, our heuristic
+is not precise---``\lo'' warnings can 
+reveal bugs. Figure~\ref{fig:lo-truepositive} shows one of these
+cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
+object and stores an 8-bit integer at the 0 position. According to the
 specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
@@
 function \CodeIn{ToIndex}, indirectly called by the test case. In this
-case, however, the \chakra{} engine did not throw any exception. This
-is a case of undocumented precondition, which is handled as a bug. It
-was fixed by \chakra\ developers and is no longer present in the most
-recent release of \chakra. Despite that case, most bugs we found
-emerged from ``\hi{}'' warnings.
+case, however, the \chakra{} engine did not throw any exception, which
+violates the spec. This case of undocumented precondition, reported
+and handled by developers as a bug, was fixed by developers after our bug
+report and is no longer present in the most recent release of
+\chakra. Despite that case, most bugs we found emerged from
+``\hi{}'' warnings.
 
@@
 this one, that has this same message signature will be included in the
-same ``bucket''. To maximize the hit ratio we remove references to
-code that may appear in the error messages.
+same cluster, which we may also refer as a ``bucket''.
 
@@
   \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex} indirectly called by the test. }
+  \caption{\label{fig:lo-truepositive}True positive example of a ``\lo''
+    warning.}
 \end{figure}
@@
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 217 & 106 & - & 278 \\
+    \smonkey{} & 218 & 107 & - & 279 \\
     Duktape & 0 & 4 & 4 & 1   \\
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Bug \# \Fix{6}.} The JS code \CodeIn{\{var a =
+\vspace{1ex}\noindent\textbf{Bug \#4} The JS code \CodeIn{\{var a =
   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}

### 2018-08-25 paper/table_differential.tex
pass on results

@@
     & 2 & \textbf{\lo} & \jsc{} \\ 
-    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
+    2  & 4/12 & radamsa & \chakra{}   & WontFix  &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
@@
     & - &  & \\
+    \midrule
+    18 & 8/24 & quickfuzz & \jsc{}  & New &
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}
+    & - & \hi{} & Test262\\
    \bottomrule

### 2018-08-25 paper/paper.tex
polishing false positives explanation; adding fixes for igor

--- 2018-08-24 paper/paper.tex
@@
 
+%%  As another example, some tests from \Fix{Y} use the
+%% implementation-dependent description message\Mar{what is the name of
+%%   the property?} encapsulated in an \CodeIn{Error} object in
+%% assertions. As such, those tests fail in all engines but
+%% \Fix{Y}.
+
 The sources of false positives found in this experiment are as
@@
 floating-point approximation of the real value is
-implementation-dependent, making the test to pass only in \chakra\ for
-that test. As another example, some tests from \Fix{Y} use the
-implementation-dependent description message\Mar{what is the name of
-  the property?} encapsulated in an \CodeIn{Error} object in
-assertions. As such, those tests fail in all engines but
-\Fix{Y}. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind manifest because the engine
-that runs the test does not optimize the code as the original engine
-and that has an effect in the test outcome.  The test may fail to
-finish at the specified time budget or it exceeds the memory
-budget. For example, a test case from the \jsc{} suite defines a
-function with a tail-call recursion. The test fails in all engines but
-\jsc{}, which implements tail-call optimization, which enables the
-test to finish execution fast. \textbf{Not implemented.} False
-positives of this kind manifest when a test fails because it covers a
-function that is part of the official spec, but is not implemented in
-the target engine yet. For example, at the time of writing, \chakra{}
-does not implement by default various properties from the
-\mcodeid{Symbol} object. These properties are only available
-activating the ES6 experimental mode with the flag
-\CodeIn{-ES6Experimental}. \Mar{pela explicacao de
-  ``compile-in-all'', isto nao faz sentido.$\rightarrow$} \textbf{Non-Standanrd Element.} This kind
-corresponds to the cases the test case relies on some non-standard
-function or property of a standard object. \Mar{revise this.$\rightarrow$}\textbf{Unknown.} This
-category includes the cases we were unable to confidently diagnose the
-failure but we suspected it was a false alarm.
+implementation-dependent, making that test to pass only in
+\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
+    error.}.} False positives of this kind typically manifest when the
+engine that runs the test does not optimize the code as the original
+engine of the test. As result, the test fails to finish at the
+specified time budget or it exceeds the memory budget. For example, a
+test case from \jsc{} defines a function with a tail-call
+recursion. The test fails in all engines but \jsc{}, which implements
+tail-call optimization. \textbf{Not implemented.} False positives of
+this kind manifest when a test fails because it covers a function that
+is part of the official spec, but is not implemented in the target
+engine yet. For example, at the time of writing, \chakra{} does not
+implement by default various properties from the \mcodeid{Symbol}
+object. These properties are only available activating the ES6
+experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
+  nao consigo entender o porque deste caso nao dar aqueles erros
+  (ReferenceError/TypeError) que vc. me mostrou e estourar na
+  assercao. explique e de um exemplo concreto, por favor$\rightarrow$}
+\textbf{Non-Standard Element.} This kind corresponds to the cases the
+test case relies on some non-standard function or property of a
+standard object. \Mar{igor, ha alguma explicacao/intuicao para
+  explicar porque nao conseguir classificar
+  isto?.$\rightarrow$}\textbf{Unknown.} This category includes the
+cases we were unable to confidently diagnose the failure but we
+suspected it was a false alarm.
 
@@
 \input{table_transplantation}
+
+\Mar{----------------------------- estou aqui $\rightarrow$}
 

### 2018-08-25 paper/paper.tex
pass on results

--- 2018-08-24 paper/paper.tex
@@
     \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
-    & Timeout/OME & 13 \\
-    & Not Implemented & 21 \\
-    & Non-Standard Element & \Fix{132} \\
-    & Unknown & \Fix{-} \\
+    & Timeout/OME & 15 \\
+    & Not Implemented & 22 \\
+    & Non-Standard Element & 177 \\
+    & Unknown & 135 \\
     \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
+    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
     & Bug & 24 \\

### 2018-08-25 paper/paper.tex
pass on V.B

--- 2018-08-25 paper/paper.tex
@@
 
-We used the official conformance test suite
-Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this test. However, we
-expect that results provide indication of engine's maturity. In the
 \begin{wraptable}[10]{r}{0.25\textwidth}
@@
   \normalsize
-  \vspace{-3ex}  
 \end{wraptable}
+We used the official conformance test suite
+Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this test. However, we
+expect that results provide indication of engine's maturity. In the
 limit, it is not desirable to flood bug reports on engines at early
@@
 %% testing paid off in this case.
-\begin{table}[h]
+\begin{table}[t]
   \centering
@@
 
-\Mar{----------------------------- estou aqui $\rightarrow$}
+% (\eg{},``New'', ``Rejected'', ``Confirmed'', ``Fixed'')
 
@@
 assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',} column ``Engine'' shows the
-affected engine, column ``Status'' indicates the status of the bug
-report at the time of the writing (\eg{},``New'', ``Rejected'',
-``Confirmed'', ``Fixed''). The status string appear in bold face for
-status ``Confirmed'' or higher (\ie{}, ``Assigned'' or ``Fixed'').
-Column ``Url'' shows the URL (de-anonymized upon request) for the bug report entry in the
-corresponding bug-tracking system, column ``Severity''
-shows the severity level for confirmed bugs, and, finally, column
-``Suite'' shows the name of the engine that originated the
-test. Note that bug reports \#4 and \#23 afected multiple engines.
-
-Considering severity levels, it is important to note that \jsc{}
-uses five levels~\cite{jsc-severity} whereas
-\chakra{}~\cite{chakra-severity} and
-\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') as the severity level for bugs with pending
-confirmation.  No bug we reported in this experiment was rejected.  Of
+  was reported in the format ``m/dd'',}, column ``Engine'' shows the
+affected engine, column ``Status'' shows the status of the bug report
+at the time of the writing. The status string appears in bold face for
+status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
+Column ``Url'' shows the URL (de-anonymized upon request) for the bug
+report entry in the corresponding bug-tracking system, column
+``Severity'' shows the severity level for confirmed bugs, and,
+finally, column ``Suite'' shows the name of the engine that originated
+the test. Note that bug reports \#4 and \#23 afected multiple
+engines.
+
+Considering severity levels, it is worth noting that \jsc{} uses five
+levels~\cite{jsc-severity} whereas \chakra{}~\cite{chakra-severity}
+and \smonkey{}~\cite{mozilla-severity} use only three\Mar{e v8?}. As
+usual, the smallest the severity value the highest the severity of the
+bug. We use a dash (``-'') in place of the severity level for the
+cases where the bug report is pending confirmation.\Mar{por favor,
+  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
 the \Fix{17} bugs we reported in this experiment, \Fix{9} were
-analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
-\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
+promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
+are severity-2 bugs.  Although we did not find any showstopper
 critical bugs, most of the bugs are seemingly important as per the
 categorization given by engineers. Analyzing the issue tracker of
-\chakra, we found that severity-1 bugs are rare. Considering the bugs
-confirmed by developers, \chakra{} was the engine with the highest
-number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
-remaining engines, \veight{} developers confirmed \Fix{one} bug we
-reported. Curiously, Google engineers confirmed that report in a few
-hours. We found that development teams of other engines, specially
-\jsc\, took much longer to analyze bug reports as can be observed by
-some pending reports from April 2018.
-
-Overall, we found these results promising given that precision (\ie{},
-the ratio of true positives over all reports) needs to take into
-account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-it took a week for the developer to inspect the entire set of
-failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-seems a low rate, but it took approximately \Fix{x} days to find
-\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-of false and true positives.
+\chakra, we found that severity-1 bugs are indeed rare. Considering
+the bugs confirmed by developers, \chakra{} was the engine with the
+highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
+the remaining engines, \veight{} developers confirmed \Fix{two} of the
+\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
+engineers confirmed the report we issued in a few hours. We found that
+development teams of other engines, specially \jsc\, took much longer
+to analyze bug reports as can be observed in the \jsc\ stacked bar
+from Figure~\ref{fig:stacked-engine}.
+
+%% Overall, we found these results promising given that precision (\ie{},
+%% the ratio of true positives over all reports) needs to take into
+%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
+%% it took a week for the developer to inspect the entire set of
+%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
+%% seems a low rate, but it took approximately \Fix{x} days to find
+%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
+%% of false and true positives.
 
@@
       \textit{Summary:}~Test transplantation is effective at finding
-      functional bugs. Although the inspection cost is non-negligible,
-      the approach was able to reveal several bugs in widely popular
-      engines.
+      functional bugs. Although the cost of classifying failures was
+      non-negligible, the approach revealed several non-trivial bugs
+      in widely popular engines.
       \end{minipage}
@@
 \end{center}
+
+\Mar{----------------------------- estou aqui $\rightarrow$}
 

### 2018-08-25 paper/paper.tex
pass on fixes

--- 2018-08-25 paper/paper.tex
@@
   (ReferenceError/TypeError) que vc. me mostrou e estourar na
-  assercao. explique e de um exemplo concreto, por favor$\rightarrow$}
+  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
+}
+\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
+diferente da que usamos anteriormente. Por exemplo, existem testes que 
+estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
+o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
+}
 \textbf{Non-Standard Element.} This kind corresponds to the cases the

### 2018-08-25 paper/paper.tex
pass on fixes

@@
   explicar porque nao conseguir classificar
-  isto?.$\rightarrow$}\textbf{Unknown.} This category includes the
+  isto?.$\rightarrow$}
+  \Igor{Exemplos: Testes especificos do engenho que }
+  \textbf{Unknown.} This category includes the
 cases we were unable to confidently diagnose the failure but we

### 2018-08-25 paper/paper.tex
discussing table VIII

--- 2018-08-25 paper/paper.tex
@@
   (ReferenceError/TypeError) que vc. me mostrou e estourar na
-  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
-}
-\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
-diferente da que usamos anteriormente. Por exemplo, existem testes que 
-estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
-o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
-}
+  assercao. explique e de um exemplo concreto, por favor$\rightarrow$}
 \textbf{Non-Standard Element.} This kind corresponds to the cases the
@@
     \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
-    & Timeout/OME & 15 \\
-    & Not Implemented & 22 \\
-    & Non-Standard Element & 177 \\
-    & Unknown & 135 \\
-    \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
+    & Timeout/OME & 13 \\
+    & Not Implemented & 21 \\
+    & Non-Standard Element & \Fix{132} \\
+    & Unknown & \Fix{-} \\
+    \midrule
+    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
     & Bug & 24 \\
@@
 
-\Mar{----------------------------- estou aqui $\rightarrow$}
-
 \subsection{Cross-Engine Differential Testing}
@@
 inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.  We configured our infrastructure
-(see Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files
-per input file, \ie{}, the number of fuzzing iterations can exceed the
-number above as we discard syntactically invalid files.
+outcomes with a differential oracle.
 
@@
 \subsubsection{Methodology}
-The methodology we used to assess effectiveness of this technique is
-as follows. To avoid experimental noise, we only fuzz test files that
-pass in all engines.  This corresponds to the tests appearing under
-the column ``no-fail-in-all'' from Table~\ref{tab:test-suites}--a
-total of \totalTestFilesPassInAll\ tests satisfy this restriction.
-The intuition is that we wanted to avoid the scenario where fuzzing
-produces a fault-revealing input based on a test that was already
-revealing failures on some engine. This decision ensures that we can
+The experimental methodology we used is as follows. To avoid
+experimental noise, we only fuzz test files that pass in all
+engines--a total of \totalTestFilesPassInAll\ tests satisfy this
+restriction.  Those tests appear under the column ``no-fail-in-all''
+from Table~\ref{tab:test-suites}.  The intuition is that we wanted to
+avoid the scenario where fuzzing produces a fault-revealing input
+based on a test that was already revealing failures on some
+engine. This decision facilitates our inspection task; it helps us
 establish cause-effect relationship between fuzzing and the
-observation of discrepancy.
+observation of discrepancy.  We configured our infrastructure (see
+Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files per
+input file, \ie{}, the number of fuzzing iterations can exceed the
+number above as we discard syntactically invalid files.
+
+%%  That
+%% finding would be important to reduce inspection cost and guide future
+%% developments of this approach.
 
@@
 bugs and how effective \lo\ warnings were relative to
-\hi\ warnings. Considering the choice of fuzzers, we did find several
-bugs with \radamsa\, but only some with \quickfuzz. The rationale for
-studying the the \hi\ and \lo\ warning classification was that if we
-found that the ratio of bugs from \lo\ warnings was rather low, we
-could focus our inspection efforts only on \hi\ warnings as we
-expected the number of warnings to increase dramatically compared to
-the previous experiment. That finding would be important to reduce
-inspection cost and guide future developments of this approach. To run
-this experiment, we trained eight students in analyzing the warnings
-that our infrastructure produces. The students were enrolled in a
+\hi\ warnings. The rationale for studying the \hi\ and \lo\ warning
+classification was that if we realized that the ratio of bugs from
+\lo\ warnings was rather low, we could focus our inspection efforts
+only on \hi\ warnings as we expected the number of warnings to
+increase dramatically compared to the previous experiment. To run this
+experiment, we trained eight students in analyzing the warnings that
+our infrastructure produces. The students were enrolled in a
 graduate-level testing class. We listed warnings in a spreadsheet and
@@
 Mozilla suite are often longer than others. Only after the co-authors
-checked the potential bugs, a bug report was filed. Each student found
-at least one bug using this methodology.
+reviewed the diagnosis, a bug report was filed. Each student found at
+least one bug using this methodology.
 
@@
 exploratory phase confirmed our expectations that most of the bugs
-found during the initial three months of investigation were related to
+found during the initial period of investigation were related to
 \hi\ warnings. For that reason, we changed our inspection
@@
 \vspace{0.5ex}
-\subsubsection{Results} In this section we discuss results obtained
-across these two phases of the experiment. Table~\ref{tab:summary-lo}
+\subsubsection{Results} Table~\ref{tab:summary-lo}
 shows statistics of \lo\ warnings obtained when fuzzing inputs with
@@
 engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' show the cases where more than one engine
-disagree on the output. Note that the ordering of engines considering
-this metric is consistent with the one observed on
+analyzed. Column ``+1'' shows the cases where more than one engine
+disagree on the output. Note from the totals that the ordering of
+engines is consistent with the one observed on
 Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
-and second place, respectively, in number of warnings (resp.,
-failures) compared to other engines.
-%\veight\ and \smonkey.
+and second place, respectively, in number of warnings (/failures)
+compared to other engines.
 
@@
     \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
+    \midrule
+    \textbf{total} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} \\    
     \bottomrule
@@
 \end{table}
+
+\Mar{----------------------------- estou aqui $\rightarrow$}
 
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Bug \#4} The JS code \CodeIn{\{var a =
+\vspace{1ex}\noindent\textbf{Bug \# \Fix{6}.} The JS code \CodeIn{\{var a =
   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}

### 2018-08-25 paper/paper.tex

@@
     \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
-    & Timeout/OME & 13 \\
-    & Not Implemented & 21 \\
-    & Non-Standard Element & \Fix{132} \\
-    & Unknown & \Fix{-} \\
-    \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & 9 \\
+    & Timeout/OME & 15 \\
+    & Not Implemented & 22 \\
+    & Non-Standard Element & 177 \\
+    & Unknown & 135 \\
+    \midrule
+    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
     & Bug & 24 \\

### 2018-08-25 paper/paper.tex
pass on tables

@@
     \midrule
-    \radamsa{} & 82 & 241 & 2.9 \\
-    \quickfuzz{} & 38 & 87 & 2.3 \\
+    \radamsa{} & 82 & 319 & 3.8 \\
+    \quickfuzz{} & 78 & 218 & 2.7 \\
     \bottomrule
@@
   \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.\Fix{falta add test262}}
+    reports per engine.}
   \begin{tabular}{crrrrr}
@@
     \midrule
-    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
-    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
-    \midrule
-    \textbf{total} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} \\    
+    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
+    \quickfuzz{} & 81 & 62 & 649 & 13 & 369 \\
+    \midrule
+    \textbf{total} & 218 &  & 972 & 34 & 852 \\
     \bottomrule
@@
     \midrule
-    \multirow{5}{*}{False Positives} & Undefined Behavior & 18 & - \\
-    & Timeout/OME & 23 & - \\
-    & Not Implemented & 19 & - \\
+    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & - \\
+    & Timeout/OME & 23 &  \\
     & * Invalid Input & 10 & - \\    

### 2018-08-25 paper/paper.tex
pass V.C

--- 2018-08-25 paper/paper.tex
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation is effective at finding
+      \textit{Summary:}~Test transplantation was effective at finding
       functional bugs. Although the cost of classifying failures was
@@
 
-\Mar{----------------------------- estou aqui $\rightarrow$}
-
 Table~\ref{tab:false-positives} shows the distribution of false
 positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of three new
+Section~\ref{sec:transplantation} with the addition of two new
 sources, which we did not observe before. These sources are
@@
 with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications.
+sensitive to function specifications. The source ``Error Message Mismatch''
+indicates that \Mar{por favor, explique. nao consigo lembrar.}
 
@@
 
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table is
-organized in two sections. The top section shows results obtained
-during the exploratory phase of the study and the bottom section shows
-the results obtained during the non-exploratory phase. The table shows
-the date the bug was reported (``Date''), the fuzzing tool used
+%% The table is
+%% organized in two sections. The top section shows results obtained
+%% during the exploratory phase of the study and the bottom section shows
+%% the results obtained during the non-exploratory phase.
+
+Table~\ref{tab:bugs} shows the list of bugs we reported. The table
+shows the date the bug was reported (``Date''), the fuzzing tool used
 (``Fuzz''), the \js\ engine affected (``Engine''), the status of the
@@
 that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite'').
-
-So far, ten of the bugs we reported were confirmed, two of
-which were fixed. One bug report we submitted was rejected on the
-basis that the offending JS file manifested an incompatibility across
-engine implementations that was expected.  Note from the table that
-all bug reports still waiting for confirmation are associated with the
-\jsc{} engine. A closer look at the \jsc{} issue tracker showed that
-their triage process is slow relative to \chakra's.\Comment{\Igor{ The bugs
-  reported on \chakra{}'s bug tracker was defined as confirmed,
-  however the bugs are included on a milestone for the next release
-  following an internal priority.  }} As of now, we did not find any
-new bug on \smonkey{} and V8; the bugs we found were duplicates and
-were not reported.
+and the test suite from the original test input (``Suite''). So far,
+\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
+were fixed. Note that one bug report that we submitted was rejected on
+the basis that the offending JS file manifested an incompatibility
+across engine implementations that was cosidered to be acceptable. As
+of now, we did not find any new bugs on \smonkey{}; the bugs we found
+were duplicates and were not reported. In \veight{}, we reported two
+bugs, both of which were confirmed, with one fixed.
+
+%% Note from the table that all bug reports still waiting for
+%% confirmation are associated with the \jsc{} engine. A closer look at
+%% the \jsc{} issue tracker showed that their triage process is slow
+%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
+%%     bug tracker was defined as confirmed, however the bugs are
+%%     included on a milestone for the next release following an internal
+%%     priority.  }}
 
@@
 \input{table_differential}
+
+\begin{center}
+  \fbox{
+    \begin{minipage}{8cm}
+      \textit{Summary:}~Cross-engine differential testing was also
+      effective at finding several bugs in \js\ engines. However,
+      relative to test transplantation, it required substantial more
+      human effort, which may play a lesser role with improved
+      automation.
+      \end{minipage}
+    }
+\end{center}
+
+\subsection{Discussion}
+
+\Mar{----------------------------- estou aqui $\rightarrow$}
+
+For example, a test that passes in one engine could
+legitimately fail in a different engine because of some undefined
+behavior in the spec. The most recent
+\js\ specification~\cite{ecmas262-spec} documents several of these
+cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
+may fail because the engine does not fully implement some feature. The
+publicly-available Kangax compatibility table~\cite{kangax} relates
+\js\ features with the engines that support them. To sum, it is often
+non-trivial to assess if a test fails because of a bug or because of
+some other reason making test automation more challenging.
+
+\Fix{...}
 
@@
 
-For example, a test that passes in one engine could
-legitimately fail in a different engine because of some undefined
-behavior in the spec. The most recent
-\js\ specification~\cite{ecmas262-spec} documents several of these
-cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
-may fail because the engine does not fully implement some feature. The
-publicly-available Kangax compatibility table~\cite{kangax} relates
-\js\ features with the engines that support them. To sum, it is often
-non-trivial to assess if a test fails because of a bug or because of
-some other reason making test automation more challenging.
-
-\Fix{...}
-
 %\section*{Acknowledgment}

### 2018-08-25 paper/paper.tex

@@
     \midrule
-    \radamsa{} & 30 & 4 & 121 & 3 & 143 \\
-    \quickfuzz{} & 12 & 7 & 67 & 8 & 89 \\
+    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
+    \quickfuzz{} & 81 & 62 & 649 & 13 & 369 \\
     \midrule
-    \textbf{total} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} & \Fix{x} \\    
+    \textbf{total} & 218 &  & 972 & 34 & 852 \\
     \bottomrule

### 2018-08-25 paper/paper.tex
pass on tables

@@
     \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
-    \quickfuzz{} & 81 & 62 & 649 & 13 & 369 \\
+    \quickfuzz{} & 81 & 62 & 349 & 13 & 369 \\
     \midrule
-    \textbf{total} & 218 &  & 972 & 34 & 852 \\
+    \textbf{total} & 218 & 109 & 672 & 34 & 852 \\
     \bottomrule
@@
 indicates that \Mar{por favor, explique. nao consigo lembrar.}
+\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
+alterar o corpo da mensagem. Esta era a ideia, mas 
+}
 
@@
     \midrule
-    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & - \\
-    & Timeout/OME & 23 &  \\
-    & * Invalid Input & 10 & - \\    
-    & * Error Message Mismatch & 3 & - \\
+    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
+    & Timeout/OME & 28 & 13 \\
+    & * Invalid Input & 39 & 48 \\    
+    & * Error Message Mismatch & 41 & 12 \\
     \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & - \\
-    & Bug & - \\
+    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
+    & Bug & 12 & 6\\
     \bottomrule     

### 2018-08-25 paper/paper.tex
merging

@@
 
-\Mar{justify why we discuss these bugs} \Mar{discuss other bugs}
+This section discusses a selection of bugs. The selection criteria we
+used was: (i) to cover each of the engines we were able to find
+bugs--\chakra, \jsc, and \veight, and (ii) to cover a different
+technique--test transplantation and differential testing (with
+\radamsa\ and with \quickfuzz).
 

### 2018-08-25 paper/paper.tex
translating igor's explanation + adding comment

@@
 object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
-  nao consigo entender o porque deste caso nao dar aqueles erros
-  (ReferenceError/TypeError) que vc. me mostrou e estourar na
-  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
-}
-\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
-diferente da que usamos anteriormente. Por exemplo, existem testes que 
-estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
-o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
-}
-\textbf{Non-Standard Element.} This kind corresponds to the cases the
-test case relies on some non-standard function or property of a
-standard object. \Mar{igor, ha alguma explicacao/intuicao para
-  explicar porque nao conseguir classificar
-  isto?.$\rightarrow$}
-  \Igor{Exemplos: Testes especificos do engenho que }
-  \textbf{Unknown.} This category includes the
-cases we were unable to confidently diagnose the failure but we
-suspected it was a false alarm.
+experimental mode with the flag \CodeIn{-ES6Experimental}.
+%% \Mar{igor,
+%%   nao consigo entender o porque deste caso nao dar aqueles erros
+%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
+%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
+%% }
+%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
+%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
+%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
+%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
+%% }
+\textbf{Non-Standard Element.} These cases manifest when a function or
+an object property is undefined in the execution engine but we were
+unable to capture looking for error types like \CodeIn{ReferenceError}
+and \CodeIn{TypeError}. For example, we found cases where the test (or
+its harness) capture the corresponding exception, making the test to
+fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
+  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
+\Igor{Exemplos: Testes especificos do engenho que }\Mar{nao
+  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
+  seja mais especifico, por favor!}  \textbf{Unknown.} This category
+includes the cases we were unable to confidently diagnose the failure
+but we suspected it was a false alarm.
 
@@
     \midrule
-    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
+    \multirow{4}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
     & Timeout/OME & 28 & 13 \\

### 2018-08-25 paper/paper.tex
fix table V

--- 2018-08-25 paper/paper.tex
@@
   isto?.$\rightarrow$}
-  \Igor{Exemplos: Testes especificos do engenho que }
+  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
+  por exemplo cobre uma especificacao antiga onde o
+  teste esperava uma propriedade true, mas na documentacao 
+  cita que a propriedade tem que ser false.}
   \textbf{Unknown.} This category includes the
@@
     \midrule
-    \multirow{5}{*}{False Positives} & Undefined Behavior & 313 \\
+    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
     & Timeout/OME & 15 \\
     & Not Implemented & 22 \\
-    & Non-Standard Element & 177 \\
+    & Non-Standard Element & 119 \\
     & Unknown & 135 \\
@@
 alterar o corpo da mensagem. Esta era a ideia, mas 
+casos onde o fuzzer muda a msg em uma assercao 
+(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
+todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
+Porem, existem casos em que o teste falha por message mismatch, 
+mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
+Analisando os casos que encontramos dessa natureza, 
+a comparacao da mensagem aparece no report, 
+porem a discrepancia ocorre quando o teste nao mostra 
+essa mensagem (passa por motivos de invalid input). 
+Eu classifiquei como message mismatch, 
+mas creio que nesse caso seria invalid input. Pq se for message mis
 }

### 2018-08-25 paper/paper.tex
drafting discussion section

--- 2018-08-25 paper/paper.tex
@@
 
-\subsection{Discussion}
-
-\Mar{----------------------------- estou aqui $\rightarrow$}
-
-For example, a test that passes in one engine could
-legitimately fail in a different engine because of some undefined
-behavior in the spec. The most recent
-\js\ specification~\cite{ecmas262-spec} documents several of these
-cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
-may fail because the engine does not fully implement some feature. The
-publicly-available Kangax compatibility table~\cite{kangax} relates
-\js\ features with the engines that support them. To sum, it is often
-non-trivial to assess if a test fails because of a bug or because of
-some other reason making test automation more challenging.
-
-\Fix{...}
-
-\section{Bugs Found}
+\section{Discussion}
 \label{sec:bugs}
 
-This section discusses a selection of bugs. The selection criteria we
-used was: (i) to cover each of the engines we were able to find
-bugs--\chakra, \jsc, and \veight, and (ii) to cover a different
-technique--test transplantation and differential testing (with
-\radamsa\ and with \quickfuzz).
+\subsection{Example Bug Reports}
+
+This section discusses a selection of bugs reports. The selection
+criteria we used was: (i) to cover each of the engines we were able to
+find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
+successful technique--test transplantation and differential testing
+(with \radamsa\ and with \quickfuzz), and (iii) to cover a case of
+rejected bug report.
 
 \sloppy
-\vspace{1ex}\noindent\textbf{Bug \#4} The JS code \CodeIn{\{var a =
+\vspace{1ex}\noindent\textbf{Issue \#4.}\Mar{de que tabela?} The JS code \CodeIn{\{var a =
   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
@@
 
-\subsection{False Positives}
-
-An example of a warning from the \hi{} group is defined in Figure~\ref{fig:hi-priority}. 
-This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
-initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
-integer 3 to a big integer number. We reported this case in \chakra{} due a core dumps that occurs
-during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
-this is an intentional behavior of engine that crash the process if it runs out of memory.
+\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
+code snippet below shows an example input related to a bug report that
+we issued to the \chakra\ development team, but they did not accept.
+This is a testcase original from the \jsc{} suite that the
+\radamsa\ fuzzer modified. Instead of the long integer passed as
+argument to \CodeIn{"foo".repeat()}, the original test used the
+integer literal 3. The engine crashes on this input as result. The
+team answered that this was an incompatibility by design as the
+function repeat was not expected to receive such a long value.
 
@@
 }
-if (!test())
-  throw new Error("Test failed");
   \end{lstlisting}
   \normalsize
-  \caption{Warning captured as \hi{} priority.}
-  \label{fig:hi-priority}
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
 \end{figure}
+
+\subsection{Threats}
+
+\subsection{Lessons}
+
+\Mar{----------------------------- estou aqui $\rightarrow$}
+
+For example, a test that passes in one engine could
+legitimately fail in a different engine because of some undefined
+behavior in the spec. The most recent
+\js\ specification~\cite{ecmas262-spec} documents several of these
+cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
+may fail because the engine does not fully implement some feature. The
+publicly-available Kangax compatibility table~\cite{kangax} relates
+\js\ features with the engines that support them. To sum, it is often
+non-trivial to assess if a test fails because of a bug or because of
+some other reason making test automation more challenging.
+
+\Fix{...}
 

### 2018-08-25 paper/paper.tex
pass on threats to validity

--- 2018-08-25 paper/paper.tex
@@
 
+As it is the case for most empirical evaluations, there are both
+external and construct threats to validity associated to the results
+we presented. In terms of external validity, our results might not
+generalize to other test inputs and engines. To mitigate this threat,
+we carefully selected inputs from various sources and cleaned them
+according to a well-defined criteria. Considering the \js\ engines, we
+used engines associated with the most popular browsers in the
+market. In terms of construct validity, there might be errors in the
+implementation of our infrastructure. To mitigate this threat, we
+extensively inspected the results of our evaluation manually and, when
+we found the need for implementing a different component we kept the
+old one for cross-checking. For example, we used
+eshost-cli~\cite{eshost-cli} to validate our fork-join implementation
+of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
+efficiency, is tighly integrated to our infrastructure.
+
 \subsection{Lessons}

### 2018-08-25 paper/paper.tex
pass on fixes

--- 2018-08-25 paper/paper.tex
@@
   para explicar porque nao conseguir classificar isto?.$\rightarrow$}
-\Igor{Exemplos: Testes especificos do engenho que }\Mar{nao
+  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
+  por exemplo cobre uma especificacao antiga onde o
+  teste esperava uma propriedade true, mas na documentacao 
+  cita que a propriedade tem que ser false.}\Mar{nao
   entendi. isto nao acabaria quebrando por um dos motivos anteriores?
@@
 
-Considering severity levels, it is worth noting that \jsc{} uses five
-levels~\cite{jsc-severity} whereas \chakra{}~\cite{chakra-severity}
-and \smonkey{}~\cite{mozilla-severity} use only three\Mar{e v8?}. As
-usual, the smallest the severity value the highest the severity of the
-bug. We use a dash (``-'') in place of the severity level for the
-cases where the bug report is pending confirmation.\Mar{por favor,
+Considering severity levels, it is worth noting that \jsc{}~\cite{jsc-severity} 
+and \smonkey{}~\cite{mozilla-severity} uses five levels, 
+whereas \chakra{}~\cite{chakra-severity} and \veight{}~\cite{v8-severity} 
+use only three. As usual, the smallest the severity value the 
+highest the severity of the bug. We use a dash (``-'') 
+in place of the severity level for the cases where the bug 
+report is pending confirmation.\Mar{por favor,
   corrija estes numeros *com cuidado*! se possivel, use macros.} Of
@@
 Eu classifiquei como message mismatch, 
-mas creio que nesse caso seria invalid input. Pq se for message mis
+mas creio que nesse caso seria invalid input.
 }
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4.}\Mar{de que tabela?} The JS code \CodeIn{\{var a =
+\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
+The JS code \CodeIn{\{var a =
   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}

### 2018-08-25 paper/paper.tex
pass on lessons learned

--- 2018-08-25 paper/paper.tex
@@
       \textit{Summary:}~Cross-engine differential testing was also
-      effective at finding several bugs in \js\ engines. However,
-      relative to test transplantation, it required substantial more
-      human effort, which may play a lesser role with improved
-      automation.
+      effective at finding bugs in \js\ engines. However, compared to
+      test transplantation, it required substantial more human effort
+      per bug found.
       \end{minipage}
@@
 
-\subsection{Lessons}
-
-\Mar{----------------------------- estou aqui $\rightarrow$}
-
-For example, a test that passes in one engine could
-legitimately fail in a different engine because of some undefined
-behavior in the spec. The most recent
-\js\ specification~\cite{ecmas262-spec} documents several of these
-cases, which can be traced looking for the string ``implementation-dependent''. As another example, a test
-may fail because the engine does not fully implement some feature. The
-publicly-available Kangax compatibility table~\cite{kangax} relates
-\js\ features with the engines that support them. To sum, it is often
-non-trivial to assess if a test fails because of a bug or because of
-some other reason making test automation more challenging.
-
-\Fix{...}
-
-% \subsection{LO bugs}
-% 
-% \Igor{For example, a bug caught by our environment and reported as LO priority was reported 
-% on \chakra{} engine, the JS code can be found in Figure~\ref{fig:lo-priority}. In this case,
-% this is a seed from Mozilla suite (\CodeIn{mozilla/non262/statements/for-in-with-assignments.js}),
-% the warning was not caught by the \CodeIn{assertEq} function that compares if two arguments are equals, 
-% the bug appears inside the generator function\footnote{Generators \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Statements/function*}}
-% at line 2. According to ES6 specification\footnote{ES6 YieldExpression \url{https://www.ecma-international.org/ecma-262/8.0/index.html\#prod-YieldExpression}},
-% it is allowed the use of \CodeIn{yield in} in a \CodeIn{for} loop. In our infrastructure,
-% only \chakra{} engine fails with an error output \CodeIn{SyntaxError: Syntax error}, due
-% the output does not shows nothing related with assertions, we considered this one as a warning from LO group.
-% Until now, the issue was confirmed and waiting for merge/closed.
-% \Fix{checar ate o prazo de submissao. Essa issue esta confirmada e com commits, falta apenas o merge.}
-% }
-% \begin{figure}[h!]
-%   \centering
-%   \scriptsize
-%   \lstset{escapeinside={@}{@},
-%     numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%     numberstyle=\tiny,
-%     morekeywords={assertEq, var, yield, in, function},
-%   }
-%   \begin{lstlisting}
-% function* g1() {
-%   for (var x = yield in {}) ;
-% }
-% var it = g1();
-% assertEq(it.next().done, false);
-% assertEq(it.next().done, true);
-%   \end{lstlisting}
-%   \normalsize
-%   \caption{Bug caught by our environment as LO priority.}
-%   \label{fig:lo-priority}
-%   \end{figure}
+\subsection{Lessons Learned}
+
+We learned several lessons in this study:
+
+\begin{itemize}
+  \item The diversity-aware techniques we used in this study are great
+    at finding bugs in \js\ engines;
+  \item The cost of inpecting failures/warnings is high. Although the
+    inspection activity was not uninterrupted, it is safe to say that
+    each warning required a substantial amount of time to analyze for
+    potential false alarms;
+  \item Even simple black-box fuzzers can create surprisingly
+    interesting inputs;
+  \item Mozilla's \smonkey\ appears to be the most reliable
+    \js\ engine, with Google's \veight\ after it;
+  \item Reporting real bugs is a great way to train (and encourage)
+    students in software testing.
+\end{itemize}
 
@@
 
+\Mar{----------------------------- estou aqui $\rightarrow$}
+
 %\section*{Acknowledgment}

### 2018-08-25 paper/paper.tex

@@
 alterar o corpo da mensagem. Esta era a ideia, mas 
+casos onde o fuzzer muda a msg em uma assercao 
+(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
+todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
+Porem, existem casos em que o teste falha por message mismatch, 
+mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
+Analisando os casos que encontramos dessa natureza, 
+a comparacao da mensagem aparece no report, 
+porem a discrepancia ocorre quando o teste nao mostra 
+essa mensagem (passa por motivos de invalid input).
+Eu classifiquei como message mismatch, 
+mas creio que nesse caso seria invalid input.
 }

### 2018-08-25 paper/paper.tex
pass on lessons learned

--- 2018-08-25 paper/paper.tex
@@
 \begin{itemize}
-  \item The diversity-aware techniques we used in this study are great
+  \item The diversity-aware techniques we used are great
     at finding bugs in \js\ engines;
@@
     potential false alarms;
+  \item We have found more bugs with test transplantation than we have
+    with cross-engine differential testing. In addition, test
+    transplantation demanded less effort per bug;
   \item Even simple black-box fuzzers can create surprisingly
@@
   \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine, with Google's \veight\ after it;
+    \js\ engine we used, with Google's \veight\ after it;
   \item Reporting real bugs is a great way to train (and encourage)

### 2018-08-25 paper/paper.tex
pass on conclusion

@@
 \subsection{Lessons Learned}
+\label{sec:lessons}
 
@@
 \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%%% comentario de igor
+%%%%%%%%%%%%%%%%%%%%%%%
+%% sim, me refiro a testes que possuem algum comentário do que se trata aquele teste. Por exemplo os testes262, possuem comentários descrevendo o que o teste tem que fazer
+%% os testes da suite do mozilla são mais dificeis de debuggar... não dificeis de grosso modo, mas custava um pouco para identificar o real problema
 
@@
 
-\Mar{----------------------------- estou aqui $\rightarrow$}
-
-%\section*{Acknowledgment}
-
-%\bibliographystyle{IEEEtran}
+JavaScript is a very popular language. For that reason, bugs in engine
+implementations often affect lots of people and organizations.
+Implementing correct engines is challenging because the specification
+is intentionally incomplete and evolves frequently. Finding bugs is
+challenging for similar reasons. We conducted a study to evaluate two
+simple diversity-aware techniques--test transplantation and
+cross-engine differential testing. The first technique runs test
+suites of a given engine in another engine. The second technique
+fuzzes existing inputs and then compares the output produced by
+different engines with a differential oracle.
+
+Overall, we reported \Fix{XX} bugs in this study. Of which, \Fix{YY}
+were confirmed and \Fix{ZZ} were fixed by developers. Although more
+work is necessary to reduce cost of manual analysis, we found that
+both techniques we used are effective at finding bugs in the engines
+used in the most popular we browsers used
+today. Section~\ref{sec:lessons} elaborates on the lessons we learned
+in this study. The result data, the infrastructure, and experimental
+scripts we prepared to run this study are available upon request.
+
 \balance

### 2018-08-25 paper/abstract.tex
pass on abstract

@@
 This paper reports on a study we ran to evaluate the importance of
-diversity to find functional bugs in JavaScript engines. For that, we use two
-simple diversity-aware techniques--test transplantation and cross-engine
-differential testing. The first technique\Comment{Test transplantation} evaluates the effects of
-running test suites of a given engine in another engine. The second technique\Comment{Cross-engine
-differential testing} evaluates the effects of fuzzing existing inputs
-and then comparing the output produced by different engines with a
-differential oracle.
+diversity to find functional bugs in JavaScript engines. For that, we
+use two simple diversity-aware techniques---test transplantation and
+cross-engine differential testing. The first technique runs test
+suites of a given engine in another engine. The second technique
+fuzzes existing inputs and then compares the output produced by
+different engines with a differential oracle.
 
@@
 experiments--Apple, Google, Microsoft, and Mozilla. Our results
-indicate that both techniques revealed several bugs, most of which
-confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs
-(\noBugsTransplantationConfirmed{} confirmed) and differential testing
-revealed \noBugsDifferentialTesting{} bugs
-(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
-that most of these bugs affected two engines--Apple's
+indicate that both techniques revealed several bugs, many of which
+confirmed by developers. We reported \noBugsTransplantation{} bugs
+with test transplantation (with \noBugsTransplantationConfirmed{} bugs
+confirmed and \noBugsTransplantationFixed{} fixed) and reported
+\noBugsDifferentialTesting{} bugs with differential testing
+(with \noBugsDifferentialTestingConfirmed{} confirmed
+and \noBugsDifferentialTestingFixed{} fixed). Furthermore, results
+indicate that most of these bugs affected two engines--Apple's
 \jsc{} (\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found

### 2018-08-25 paper/table_differential.tex
pass on fixes
pass on abstract, macros, and tables

@@
   \label{tab:bugs}
-  \begin{tabular}{ccccccccc}
+  \begin{tabular}{rcccccccc}
     \toprule
@@
 
-    \midrule
-    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
+    6 & 4/30  & radamsa & \chakra{} & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
-    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
-                        &                        &        &
+    & 2 & \hi{} & TinyJS\\
+
+    7                    & 4/30                       &  radamsa   &
     \jsc{} & New &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
-    & - &  & \\
-    \midrule
+    & - & \hi{} & TinyJS \\
 
-    7 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
+    8 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
     & 2 & \textbf{\lo} & \smonkey{} \\
-    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
+    9 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
     & 3 & \hi{} & \jerry{} \\
-    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
+    10 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
     & 2 & \hi{} & \veight{}\\
-    10 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
+    11 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
     & 2 & \hi{} & \jsc{}\\
-    11 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
+    12 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
     & 2 & \hi{} & \jerry{}\\
-    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
+    13 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
     & 2 & \hi{} & \jerry{}\\
-    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
+    14 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
@@
 
-    \midrule
-    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
+    15 & 8/21  & radamsa & \chakra{} & \textbf{Confirmed} &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & &
+    & - & \hi{} & Test262\\
+
+    16 & 8/21 & radamsa &
     \veight{} & \textbf{Fixed} &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & 2 &  & \\
-    \midrule
+    & 2 & \hi{} & Test262 \\
 
-    15 & 8/23 & quickfuzz & \jsc{} & New  &
+    17 & 8/23 & quickfuzz & \jsc{} & New  &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
     & - & \hi{} & Test262\\
-    16 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
+    18 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
     \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
@@
 
-    \midrule
-    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
-    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
+    19 & 8/24  & quickfuzz & \chakra{} & New &
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & & 
+    & - & \hi{} & Test262\\
+
+    20 & 8/24 &  quickfuzz & 
     \jsc{} & New &
     \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
-    & - &  & \\
-    \midrule
-    18 & 8/24 & quickfuzz & \jsc{}  & New &
+    & - & \hi{} & Test262 \\
+
+    21 & 8/24 & quickfuzz & \jsc{}  & New &
     \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}

### 2018-08-25 paper/paper.tex
pass on abstract, macros, and tables
checking macros

@@
 
-\emph{Results.}~\Fix{REVISE}We considered engines from four major players--Apple,
+\emph{Results.}~We considered engines from four major players--Apple,
 Google, Microsoft, and Mozilla. Our results indicate that both
@@
 developers. Test transplantation revealed \noBugsTransplantation{}
-bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
-testing revealed \noBugsDifferentialTesting{} bugs
-(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
-that most of these bugs affected only two engines--Apple's \jsc{}
-(\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found only
-one bug in Google \veight{} and none in Mozilla's \smonkey{}. Although
-our experience indicates that more research needs be done to automate
-parts of the inspection process, our results show that exploring
-diversity is a valuable help to find bugs in JavaScript engines.
+bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
+\noBugsTransplantationFixed{} were fixed) whereas differential testing
+revealed \noBugsDifferentialTesting{} bugs (of which,
+\noBugsDifferentialTestingConfirmed{} were confirmed and
+\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
+indicate that most of these bugs affected two engines--Apple's \jsc{}
+and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
+bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
+none in Mozilla's \smonkey{}. Our results indicate that both
+techniques were successful at finding bugs, but, overall, test
+transplantation demanded less effort compared to differential testing
+per bug found. Although our experience indicates that more research
+needs be done to automate parts of the inspection process, our results
+show that exploring diversity is a valuable help to find bugs in
+JavaScript engines.
 
@@
   \item We ran a comprehensive study to analyze the effectiveness of
-    simple diversity-aware techniques to find bugs in highly-popular
-    \js\ engines.
-
-  \item We reported more than \Fix{50} bugs on these engines over a
-    period of 5 months.
+    simple diversity-aware techniques to find functional bugs in
+     popular \js\ engines;
+
+  \item We reported a total of \totalBugsReported{} bugs on these
+    engines. Of which, \totalBugsConfirmed{} confirmed and
+    \totalBugsFixed{} fixed;
 
@@
   Depending on the issue date, the fix may be in the latest release of
-  the corresponding engines.} Overall, discarding bug report with the
-``1-New'' status, we reported a total of \noBugsTotalConfirmed{}
-bugs. We found that the majority of bug reports targeted the engines
+  the corresponding engines.} Overall, discarding bug reports with the
+``1-New'' status, we reported a total of \totalBugsConfirmed{}
+bugs. We found that the vast majority of bug reports targeted the engines
 from Microsoft and Apple. Considering the techniques, the number of
@@
 \begin{figure}[h!]
+%  \vspace{-2ex}  
   \centering
@@
   \caption{\label{fig:summary}Summary of bug reports.}
+%  \vspace{-3ex}
 \end{figure}
@@
 
-\begin{wraptable}[10]{r}{0.25\textwidth}
+%\begin{wraptable}[10]{r}{0.25\textwidth}
 %  \vspace{-3ex}
+%\end{wraptable}
+\
+\begin{table}[t]
   \centering
@@
   \normalsize
-\end{wraptable}
+\end{table}
+
 We used the official conformance test suite
@@
 
-\begin{table}[h!]
+\begin{table}[t!]
   \setlength{\tabcolsep}{4pt}    
@@
 finally, column ``Suite'' shows the name of the engine that originated
-the test. Note that bug reports \#4 and \#23 afected multiple
-engines.
+the test.
+
+%Note that bug reports \#4 and \#23 afected multiple engines.
 

### 2018-08-25 paper/paper.tex
added bug found

--- 2018-08-25 paper/paper.tex
@@
 developers. Test transplantation revealed \noBugsTransplantation{}
-bugs (\noBugsTransplantationConfirmed{} confirmed) and differential
+bugs (\noBugsTransplantationConfirmed{} confirmed, \noBugsTransplantationFixed{} fixed) and differential
 testing revealed \noBugsDifferentialTesting{} bugs
-(\noBugsDifferentialTestingConfirmed{}). Furthermore, results indicate
+(\noBugsDifferentialTestingConfirmed{} confirmed and \noBugsDifferentialTestingFixed{} fixed). Furthermore, results indicate
 that most of these bugs affected only two engines--Apple's \jsc{}
@@
 \chakra{} team fixed the issue soon after we reported the problem.
+
+\vspace{1ex}\noindent\textbf{Issue \#16, Table~\ref{tab:cross-testing}.}
+\Igor{
+  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
+  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
+  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
+  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
+  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
+  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
+  function declaration. The fuzzer removes the function declaration and 
+  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
+  the break statement should throw an early error (in this case a SyntaxError) 
+  if the break statement is not nested in an iterational or a switch statement. All engines works
+  as expected but \veight{} pass without failures.
+}
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assert, assertEq, var, yield, in, function, eval,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+// Original file
+eval(
+"{ 
+    function f() { 
+      return 'declaration'; 
+    } 
+ }
+ assert.sameValue(typeof f, 'function');
+ \assert.sameValue(f(), 'declaration');"
+);
+------------------------------------------
+// Fuzzed file
+eval(function b (a) {
+  break;
+});
+  \end{lstlisting}
+  \normalsize
+  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
+  and reported in \veight{} engine}
+\end{figure}
 
@@
 \begin{itemize}
-  \item The diversity-aware techniques we used are great
+  \item The diversity-aware techniques we used in this study are great
     at finding bugs in \js\ engines;
@@
     potential false alarms;
-  \item We have found more bugs with test transplantation than we have
-    with cross-engine differential testing. In addition, test
-    transplantation demanded less effort per bug;
   \item Even simple black-box fuzzers can create surprisingly
@@
   \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we used, with Google's \veight\ after it;
+    \js\ engine, with Google's \veight\ after it;
   \item Reporting real bugs is a great way to train (and encourage)

### 2018-08-25 paper/abstract.tex

@@
 confirmed by developers. We reported \noBugsTransplantation{} bugs
-with test transplantation (with \noBugsTransplantationConfirmed{} bugs
+with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
 confirmed and \noBugsTransplantationFixed{} fixed) and reported
 \noBugsDifferentialTesting{} bugs with differential testing
-(with \noBugsDifferentialTestingConfirmed{} confirmed
-and \noBugsDifferentialTestingFixed{} fixed). Furthermore, results
-indicate that most of these bugs affected two engines--Apple's
-\jsc{} (\percJSC{}) and Microsoft's \chakra{} (\percChakra{}); we found
-only \Fix{one} bug in Google \veight{} and none in Mozilla's
-\smonkey{}. Although more research needs to be done to optimizie 
-warning triaging, our results show that exploring diversity is a
-valuable help to find bugs in JavaScript engines.
+(\noBugsDifferentialTestingConfirmed{} of these confirmed
+and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
+most of these bugs affected two engines--Apple's
+\jsc{} and Microsoft's \chakra{}. To sum, our results show that
+exploring diversity is effective to find bugs in JavaScript engines.
+
+%% Although more research needs to be done to optimizie 
+%% warning triaging,
+
+%% ; we found
+%% only \Fix{one} bug in Google \veight{} and none in Mozilla's
+%% \smonkey{}

### 2018-08-25 paper/paper.tex
pass on conclusion

--- 2018-08-25 paper/paper.tex
@@
 
-Overall, we reported \Fix{XX} bugs in this study. Of which, \Fix{YY}
-were confirmed and \Fix{ZZ} were fixed by developers. Although more
-work is necessary to reduce cost of manual analysis, we found that
-both techniques we used are effective at finding bugs in the engines
-used in the most popular we browsers used
-today. Section~\ref{sec:lessons} elaborates on the lessons we learned
-in this study. The result data, the infrastructure, and experimental
-scripts we prepared to run this study are available upon request.
+Overall, we reported \totalBugsReported\ bugs in this study. Of which,
+\totalBugsConfirmed\ were confirmed by developers and
+\totalBugsConfirmed\ were fixed. Although more work is necessary to
+reduce cost of manual analysis, we found that both techniques we used
+are effective at finding bugs in
+\js\ engines. Section~\ref{sec:lessons} elaborates on the lessons
+learned from this study. The result data, infrastructure, and
+experimental scripts we prepared to run this study are available upon
+request. Future work includes mining test inputs from alternative
+sources (\eg{}, bug trackers) and predicting likelihood of false
+positives as to guide human effort on the most promising warnings
+first.
 

### 2018-08-25 paper/paper.tex
pass on bugs found

--- 2018-08-25 paper/paper.tex
@@
 \Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
-alterar o corpo da mensagem. Esta era a ideia, mas 
-casos onde o fuzzer muda a msg em uma assercao 
-(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
-todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
-Porem, existem casos em que o teste falha por message mismatch, 
-mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
-Analisando os casos que encontramos dessa natureza, 
-a comparacao da mensagem aparece no report, 
-porem a discrepancia ocorre quando o teste nao mostra 
-essa mensagem (passa por motivos de invalid input).
-Eu classifiquei como message mismatch, 
-mas creio que nesse caso seria invalid input.
+alterar o corpo da mensagem. Casos onde o fuzzer muda a msg em uma assercao 
+(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")').
 }
@@
 \end{figure}
+
+\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
+\Igor{to appear...}
 

### 2018-08-25 paper/paper.tex
pass on discussion

@@
 
+%% \CodeIn{\{var a =
+%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
+%%   assert(+a === 0)\}}
+
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
-The JS code \CodeIn{\{var a =
-  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the Radamsa fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
-used in the assertion, is equivalent to the operation
+\vspace{1ex}\noindent\textbf{Issue \#4,
+  Table~\Fix{XX}.}  The code snippet below show a bug
+in \chakra{}.
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+{var a =
+  {valueOf:~function(){ return "\x00"}}
+  assert(+a === 0)}
+  \end{lstlisting}
+  \normalsize
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
+\end{figure}
+
+The object property \CodeIn{valueOf} stores a function
+that returns a primitive value identifying the target
+object~\cite{valueof}. The original version of this code returns an
+empty string whereas the version of the code modified by the \radamsa{}
+fuzzer~\cite{radamsa} returns a string representation of a null
+character (\CodeIn{NUL} in ascii). The unary plus expression
+``\CodeIn{+a}", used in the assertion, is equivalent to the operation
 \CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
@@
 Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
-  chakra did that it would be fine, no?} evaluates the unary
-plus to NaN as expected, as the null character cannot be converted. As
-result, the test fails as expected. \chakra{}, in contrast,
-incorrectly converts the string to zero, making the test to pass. All
-other engines fail on this test. As Table~\ref{tab:bugs} shows, the
+  chakra did that it would be fine, no?} evaluates the unary plus to
+NaN as expected, as the null character cannot be converted. As result,
+the test fails as expected. \chakra{}, in contrast, incorrectly
+converts the string to zero, making the test to pass. All other
+engines fail on this test. As Table~\ref{tab:bugs} shows, the
 \chakra{} team fixed the issue soon after we reported the problem.
 
-\vspace{1ex}\noindent\textbf{Issue \#16, Table~\ref{tab:cross-testing}.}
+\Mar{---------------------- estou aqui}
+
+\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.
 \Igor{
@@
 );
-------------------------------------------
 // Fuzzed file

### 2018-08-25 paper/paper.tex
minor fixes

--- 2018-08-25 paper/paper.tex
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#16, Table~\ref{tab:cross-testing}.}
+\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
 \Igor{
@@
 \vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
-\Igor{to appear...}
+Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
+de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
+the
 

### 2018-08-25 paper/paper.tex
pass on example

--- 2018-08-25 paper/paper.tex
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4,
-  Table~\Fix{XX}.}  The code snippet below show a bug
-in \chakra{}.
+\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
+snippet below shows the test input we used to reveal a bug in
+\chakra.
 
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.
-\Igor{
-  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-  function declaration. The fuzzer removes the function declaration and 
-  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-  the break statement should throw an early error (in this case a SyntaxError) 
-  if the break statement is not nested in an iterational or a switch statement. All engines works
-  as expected but \veight{} pass without failures.
-}
+\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.  The code
+snippet below shows the test input we used to reveal a bug in \veight.
+
+%% eval(
+%% "{ 
+%%     function f() { 
+%%       return 'declaration'; 
+%%     } 
+%%  }
+%%  assert.sameValue(typeof f, 'function');
+%%  \assert.sameValue(f(), 'declaration');"
+%% );
+%% // Fuzzed file
 
@@
   \begin{lstlisting}
-// Original file
-eval(
-"{ 
-    function f() { 
-      return 'declaration'; 
-    } 
- }
- assert.sameValue(typeof f, 'function');
- \assert.sameValue(f(), 'declaration');"
-);
-// Fuzzed file
 eval(function b (a) {
@@
   \normalsize
-  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
-  and reported in \veight{} engine}
+  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
+  %% and reported in \veight{} engine}
 \end{figure}
+
+This code snippet was obtained by fuzzing a Test262 test with
+\quickfuzz. In its original version, a string (omitted for space),
+passed as argument to the \CodeIn{eval} function, encoded the actual
+test. The fuzzer replaced the string argument with a function whose
+body is a \CodeIn{break} statement outside a valid block
+statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
+how eval should be handle code containing a function declaration.
+According to specification~\cite{break-statement}, the break statement
+should throw an early error--in this case a SyntaxError--if the break
+statement is not nested in an iterational or a switch statement. In
+this case, all engines behave as expected but \veight{} pass without
+failures.
+
+%% \Igor{
+%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
+%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
+%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
+%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
+%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
+%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
+%%   function declaration. The fuzzer removes the function declaration and 
+%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
+%%   the break statement should throw an early error (in this case a SyntaxError) 
+%%   if the break statement is not nested in an iterational or a switch statement. All engines works
+%%   as expected but \veight{} pass without failures.
+%% }
 

### 2018-08-25 paper/paper.tex
another pass on discussion

@@
 successful technique--test transplantation and differential testing
-(with \radamsa\ and with \quickfuzz), and (iii) to cover a case of
-rejected bug report.
+(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
+rejected bug report, and (iv) the test is short.
 
@@
 we issued to the \chakra\ development team, but they did not accept.
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. Instead of the long integer passed as
-argument to \CodeIn{"foo".repeat()}, the original test used the
-integer literal 3. The engine crashes on this input as result. The
-team answered that this was an incompatibility by design as the
-function repeat was not expected to receive such a long value.
 
@@
 
-\subsection{Threats}
+This is a testcase original from the \jsc{} suite that the
+\radamsa\ fuzzer modified. Instead of the long integer passed as
+argument to \CodeIn{"foo".repeat()}, the original test used the
+integer literal 3. The engine crashes on this input as result. The
+team answered that this was an incompatibility by design as the
+function repeat was not expected to receive such a long value.
+
+\subsection{Threats To Validity}
 

### 2018-08-25 paper/paper.tex
minor changes in examples

@@
 Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
-  chakra did that it would be fine, no?} evaluates the unary plus to
-NaN as expected, as the null character cannot be converted. As result,
-the test fails as expected. \chakra{}, in contrast, incorrectly
-converts the string to zero, making the test to pass. All other
-engines fail on this test. As Table~\ref{tab:bugs} shows, the
+  chakra did that it would be fine, no?} \Igor{
+  \chakra{} converte incorretamente o valor hexadecimal para
+  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
+  engines consideram o hexadecimal invalido (valor esperado), 
+  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
+  }evaluates the unary
+plus to NaN as expected, as the null character cannot be converted. As
+result, the test fails as expected. \chakra{}, in contrast,
+incorrectly converts the string to zero, making the test to pass. All
+other engines fail on this test. As Table~\ref{tab:bugs} shows, the
 \chakra{} team fixed the issue soon after we reported the problem.
 
-\Mar{---------------------- estou aqui}
-
-\vspace{1ex}\noindent\textbf{Issue \#16, Table~\Fix{XX}}.  The code
-snippet below shows the test input we used to reveal a bug in \veight.
-
-%% eval(
-%% "{ 
-%%     function f() { 
-%%       return 'declaration'; 
-%%     } 
-%%  }
-%%  assert.sameValue(typeof f, 'function');
-%%  \assert.sameValue(f(), 'declaration');"
-%% );
-%% // Fuzzed file
+\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
+\Igor{
+  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
+  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
+  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
+  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
+  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
+  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
+  function declaration. The fuzzer removes the function declaration and 
+  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
+  the break statement should throw an early error (in this case a SyntaxError) 
+  if the break statement is not nested in an iterational or a switch statement. All engines works
+  as expected but \veight{} pass without failures.
+}
 
@@
 This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. Instead of the long integer passed as
-argument to \CodeIn{"foo".repeat()}, the original test used the
-integer literal 3. The engine crashes on this input as result. The
-team answered that this was an incompatibility by design as the
-function repeat was not expected to receive such a long value.
+\radamsa\ fuzzer modified. The original test used the integer literal
+3 as argument to \CodeIn{repeat()}, but this test uses a long integer
+instead. As result, the engine crashes. The team answered that this
+was an incompatibility by design as the function was not expected to
+receive such a long value.
 

### 2018-08-25 paper/paper.tex
pass on results

@@
 successful technique--test transplantation and differential testing
-(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
-rejected bug report, and (iv) the test is short.
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
+(with \radamsa\ and with \quickfuzz), and (iii) to cover a case of
+rejected bug report.
 
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
-snippet below shows the test input we used to reveal a bug in
-\chakra.
-
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
-{var a =
-  {valueOf:~function(){ return "\x00"}}
-  assert(+a === 0)}
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function
-that returns a primitive value identifying the target
-object~\cite{valueof}. The original version of this code returns an
-empty string whereas the version of the code modified by the \radamsa{}
-fuzzer~\cite{radamsa} returns a string representation of a null
-character (\CodeIn{NUL} in ascii). The unary plus expression
-``\CodeIn{+a}", used in the assertion, is equivalent to the operation
+\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
+The JS code \CodeIn{\{var a =
+  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
+  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
+The object property \CodeIn{valueOf} stores a function that returns a
+primitive value identifying the target object~\cite{valueof}. The
+original version of this code returns an empty string whereas the
+version of the code modified by the Radamsa fuzzer~\cite{radamsa}
+returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
+used in the assertion, is equivalent to the operation
 \CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
@@
   \begin{lstlisting}
+// Original file
+eval(
+"{ 
+    function f() { 
+      return 'declaration'; 
+    } 
+ }
+ assert.sameValue(typeof f, 'function');
+ \assert.sameValue(f(), 'declaration');"
+);
+------------------------------------------
+// Fuzzed file
 eval(function b (a) {
@@
   \normalsize
-  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
-  %% and reported in \veight{} engine}
+  \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
+  and reported in \veight{} engine}
 \end{figure}
-
-This code snippet was obtained by fuzzing a Test262 test with
-\quickfuzz. In its original version, a string (omitted for space),
-passed as argument to the \CodeIn{eval} function, encoded the actual
-test. The fuzzer replaced the string argument with a function whose
-body is a \CodeIn{break} statement outside a valid block
-statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
-how eval should be handle code containing a function declaration.
-According to specification~\cite{break-statement}, the break statement
-should throw an early error--in this case a SyntaxError--if the break
-statement is not nested in an iterational or a switch statement. In
-this case, all engines behave as expected but \veight{} pass without
-failures.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
 
@@
 we issued to the \chakra\ development team, but they did not accept.
+This is a testcase original from the \jsc{} suite that the
+\radamsa\ fuzzer modified. Instead of the long integer passed as
+argument to \CodeIn{"foo".repeat()}, the original test used the
+integer literal 3. The engine crashes on this input as result. The
+team answered that this was an incompatibility by design as the
+function repeat was not expected to receive such a long value.
 
@@
 
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
+\subsection{Threats}
 

### 2018-08-25 paper/paper.tex

--- 2018-08-25 paper/paper.tex
@@
 This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
+\radamsa\ fuzzer modified. Instead of the long integer passed as
+argument to \CodeIn{"foo".repeat()}, the original test used the
+integer literal 3. The engine crashes on this input as result. The
+team answered that this was an incompatibility by design as the
+function repeat was not expected to receive such a long value.
 

### 2018-08-25 paper/paper.tex
pass on examples

--- 2018-08-25 paper/paper.tex
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\Fix{XX}.} The code
-snippet below shows the test input we used to reveal a bug in
+\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
+code snippet below shows the test input we used to reveal a bug in
 \chakra.
@@
 
-The object property \CodeIn{valueOf} stores a function
-that returns a primitive value identifying the target
-object~\cite{valueof}. The original version of this code returns an
-empty string whereas the version of the code modified by the \radamsa{}
-fuzzer~\cite{radamsa} returns a string representation of a null
-character (\CodeIn{NUL} in ascii). The unary plus expression
-``\CodeIn{+a}", used in the assertion, is equivalent to the operation
+The object property \CodeIn{valueOf} stores a function that returns a
+primitive value identifying the target object~\cite{valueof}. The
+original version of this code returns an empty string whereas the
+version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
+returns a string representation of a null character (\CodeIn{NUL} in
+ascii). The unary plus expression ``\CodeIn{+a}", used in the
+assertion, is equivalent to the operation
 \CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
 otherwise the operation returns NaN (Not a
-Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
-  chakra did that it would be fine, no?} \Igor{
-  \chakra{} converte incorretamente o valor hexadecimal para
-  0 e a expressao +0 resulta em 0, o que faz com que o teste passe. Os outros
-  engines consideram o hexadecimal invalido (valor esperado), 
-  quando o hexadecimal nao pode ser convertido, espera-se que retorne NaN, que +NaN resulta em NaN.
-  }evaluates the unary
-plus to NaN as expected, as the null character cannot be converted. As
-result, the test fails as expected. \chakra{}, in contrast,
-incorrectly converts the string to zero, making the test to pass. All
-other engines fail on this test. As Table~\ref{tab:bugs} shows, the
+Number)~\cite{unary-plus}. This test fails in all engines but
+\chakra{}. For all three engines the string cannot be parsed as an
+hexadecimal. As such, they produce a NaN as result and the test fails
+as expected. \chakra{}, in contrast, incorrectly converts the string
+to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
 \chakra{} team fixed the issue soon after we reported the problem.
 
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}
-\Igor{
-  Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-  Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-  que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-  de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-  that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-  B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-  function declaration. The fuzzer removes the function declaration and 
-  injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-  the break statement should throw an early error (in this case a SyntaxError) 
-  if the break statement is not nested in an iterational or a switch statement. All engines works
-  as expected but \veight{} pass without failures.
-}
+\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
+code snippet below shows the test input we used to reveal a bug in
+\veight{}.
 
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
-Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
-de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
-the
+\vspace{1ex}\noindent\textbf{Issue \#2,
+  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
+shows the test input we used to reveal a bug in \jsc{}. This test
+originates from \jerry{} test suite; the bug was found during the test
+transplantation experiment.
+
+\begin{figure}[h!]
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function, 
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+var obj = {}; var arr = [];
+try {
+  arr.sort(obj);
+  assert(false);
+} catch (e) {
+  assert(e instanceof TypeError);
+}
+  \end{lstlisting}
+  \normalsize
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
+\end{figure}
+
+According to the specification~\cite{ecmas262-array-sort}, the
+parameter to the \CodeIn{Array.sort} function should be a comparable
+object or an undefined value, otherwise it should throw a
+\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
+as argument to \CodeIn{sort} and the test fails in the subsequent
+step. The other engines raise a \CodeIn{TypeError} as expected.
 
@@
   return typeof String.prototype.repeat === "function"
-    && "foo".repeat(657604378) === "foofoofoo";
-}
+    && "foo".repeat(657604378) === "foofoofoo"; }
   \end{lstlisting}

### 2018-08-25 paper/paper.tex
pass on fixes

--- 2018-08-25 paper/paper.tex
@@
 ``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
-the test transplantaion experiment and the differential testing
+the test transplantation experiment and the differential testing
 experiment, respectively.
@@
   entendi. isto nao acabaria quebrando por um dos motivos anteriores?
-  seja mais especifico, por favor!}  \textbf{Unknown.} This category
+  seja mais especifico, por favor!}
+  \Igor{nao, o teste eh valido (nao quebra por ReferenceError/TypeError) e
+  nao entra no undefined behaviour pq nao afeta a especificacao. Isso eh um caso,
+  outros casos estao ligados a nao-compreensao do testcase }  \textbf{Unknown.} This category
 includes the cases we were unable to confidently diagnose the failure
@@
 \vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
-Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
-de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
-the
+\Igor{JSC transplantation...}
 

### 2018-08-25 paper/paper.tex
spell checking

@@
 development flexibility. In addition, they evolve frequently to
-accomodate the pressing demands from
+accommodate the pressing demands from
 developers~\cite{ecmas262-spec-repo}. An official conformance test
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). A positive aspect of the aproach is that
+not eager JIT compilation). A positive aspect of the approach is that
 it can be fully automated. As the same engine is used, the outcomes of
@@
   \item We made our testing infrastructure, results, and experimental
-    scripts available to the public. (upon request for anonimity.)
+    scripts available to the public. (upon request for anonymity.)
 
@@
 \totalTestFilesForTestTransplantation{} tests included in the circle
-from the table in the evaluation of test transplantion, \ie{}, the
+from the table in the evaluation of test transplantation, \ie{}, the
 difference between sets ``compile-in-all'' and Test262. We did not
@@
 through the violation of an assertion declared in the test. In
-contrast, warnings of type ``\lo{}'' are more likely to be asssociated
+contrast, warnings of type ``\lo{}'' are more likely to be associated
 with invalid inputs. They reflect the cases where the anomaly is
@@
 tests over this period. The variance of results was negligible; for
-that reasons, we omited standard deviations. We noticed that all four
+that reasons, we omitted standard deviations. We noticed that all four
 engines we analyzed but \chakra{} use some variant of the Test262
@@
 experimental mode with the flag \CodeIn{-ES6Experimental}.
-%% \Mar{igor,
-%%   nao consigo entender o porque deste caso nao dar aqueles erros
-%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
-%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
-%% }
-%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
-%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
-%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
-%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
-%% }
 \textbf{Non-Standard Element.} These cases manifest when a function or
@@
 its harness) capture the corresponding exception, making the test to
-fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
-  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
-  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
-  por exemplo cobre uma especificacao antiga onde o
-  teste esperava uma propriedade true, mas na documentacao 
-  cita que a propriedade tem que ser false.}\Mar{nao
-  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
-  seja mais especifico, por favor!}
-  \Igor{nao, o teste eh valido (nao quebra por ReferenceError/TypeError) e
-  nao entra no undefined behaviour pq nao afeta a especificacao. Isso eh um caso,
-  outros casos estao ligados a nao-compreensao do testcase }  \textbf{Unknown.} This category
-includes the cases we were unable to confidently diagnose the failure
-but we suspected it was a false alarm.
+fail in an assertion instead.  \textbf{Other.} This category includes
+other sources. For example, it includes the cases where the test was
+valid for some previous version of the spec but is no longer valid for
+the current spec.
 
@@
     & Non-Standard Element & 119 \\
-    & Unknown & 135 \\
+    & Other & 135 \\
     \midrule
@@
 false and true positives. Considering false positives, ``Undefined
-Behavior'' and ``Non-Standard Element'' were the most predominant
-sources. Considering true positives, we found a reasonable number of
-duplicate reports, but not enough high to justify attempting to
-automate the detection of duplicates.
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Url'' shows the URL (de-anonymized upon request) for the bug
-report entry in the corresponding bug-tracking system, column
-``Severity'' shows the severity level for confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.
+Behavior'' was the most predominant source. Considering true
+positives, we found a reasonable number of duplicate reports, but not
+enough high to justify attempting to automate the detection of
+duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
+we found with test transplantation. The first column shows the
+identifier we assigned to the bug\Comment{, column ``Date'' shows the
+  date the bug was reported in the format ``m/dd'',}, column
+``Engine'' shows the affected engine, column ``Status'' shows the
+status of the bug report at the time of the writing. The status string
+appears in bold face for status ``Confirmed'' or higher, \ie{},
+``Assigned'' and ``Fixed''.  Column ``Url'' shows the URL
+(de-anonymized upon request) for the bug report entry in the
+corresponding bug-tracking system, column ``Severity'' shows the
+severity level for confirmed bugs, and, finally, column ``Suite''
+shows the name of the engine that originated the test.
 
@@
 the basis that the offending JS file manifested an incompatibility
-across engine implementations that was cosidered to be acceptable. As
+across engine implementations that was considered to be acceptable. As
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
@@
 This section discusses a selection of bugs reports. The selection
-criteria we used was: (i) to cover each of the engines we were able to
-find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
-successful technique--test transplantation and differential testing
-(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
-rejected bug report, and (iv) the test is short.
+criteria we used was: (i) to cover each engine that we found
+bugs--\chakra, \jsc, and \veight, (ii) to cover a different
+technique--test transplantation and differential testing (with
+\radamsa\ and with \quickfuzz), (iii) to cover a case of rejected bug
+report, and (iv) to use short test inputs (for space).
 
@@
 {var a =
-  {valueOf:~function(){ return "\x00"}}
-  assert(+a === 0)}
+  {valueOf: function(){ return "\x00"}}
+  assert(+a === 0)
+}
   \end{lstlisting}
@@
 version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL} in
-ascii). The unary plus expression ``\CodeIn{+a}", used in the
+returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
+ascii}. The unary plus expression ``\CodeIn{+a}", used in the
 assertion, is equivalent to the operation
@@
 should throw an early error--in this case a SyntaxError--if the break
-statement is not nested in an iterational or a switch statement. In
+statement is not nested in an iterable or a switch statement. In
 this case, all engines behave as expected but \veight{} pass without
@@
   \begin{lstlisting}
-var obj = {}; var arr = [];
+var obj = {};
+var arr = [];
 try {
@@
   return typeof String.prototype.repeat === "function"
-    && "foo".repeat(657604378) === "foofoofoo"; }
+  && "foo".repeat(657604378) === "foofoofoo";
+}
   \end{lstlisting}
@@
 of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
-efficiency, is tighly integrated to our infrastructure.
+efficiency, is tightly integrated to our infrastructure.
 
@@
     at finding bugs in \js\ engines;
-  \item The cost of inpecting failures/warnings is high. Although the
+  \item The cost of inspecting failures/warnings is high. Although the
     inspection activity was not uninterrupted, it is safe to say that
@@
 discrepancies. Their fuzzer can be used to find bugs in JS engines and
-WebAssembly engines. The sensible parts of the infrastructure they
+Web Assembly engines. The sensible parts of the infrastructure they
 built are the checks of input validity (as to reduce waste/cost) and
@@
 %%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
-%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC
-%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii
+%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
+%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
 %%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
-%%  LocalWords:  SSL TLS ICSE
+%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber
+%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
+%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
+%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
+%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
+%%  LocalWords:  escapeinside morekeywords

### 2018-08-25 paper/paper.tex
pass

@@
 
-Considering severity levels, it is worth noting that \jsc{}~\cite{jsc-severity} 
-and \smonkey{}~\cite{mozilla-severity} uses five levels, 
-whereas \chakra{}~\cite{chakra-severity} and \veight{}~\cite{v8-severity} 
-use only three. As usual, the smallest the severity value the 
-highest the severity of the bug. We use a dash (``-'') 
-in place of the severity level for the cases where the bug 
-report is pending confirmation.\Mar{por favor,
-  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
-the \Fix{17} bugs we reported in this experiment, \Fix{9} were
-promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
-are severity-2 bugs.  Although we did not find any showstopper
-critical bugs, most of the bugs are seemingly important as per the
-categorization given by engineers. Analyzing the issue tracker of
-\chakra, we found that severity-1 bugs are indeed rare. Considering
-the bugs confirmed by developers, \chakra{} was the engine with the
-highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
-the remaining engines, \veight{} developers confirmed \Fix{two} of the
-\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
-engineers confirmed the report we issued in a few hours. We found that
-development teams of other engines, specially \jsc\, took much longer
-to analyze bug reports as can be observed in the \jsc\ stacked bar
-from Figure~\ref{fig:stacked-engine}.
+Considering severity levels, it is worth noting that
+\jsc{}~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity} uses
+five levels, whereas \chakra{}~\cite{chakra-severity} and
+\veight{}~\cite{v8-severity} use only three. As usual, the smallest
+the severity value the highest the severity of the bug. We use a dash
+(``-'') in place of the severity level for the cases where the bug
+report is pending confirmation. Of the \noBugsTransplantation{} bugs
+we reported in this experiment, \noBugsTransplantationConfirmed\ were
+promoted from the status ``New'' to ``Confirmed''. Of these, 16 are
+severity-2 bugs.  Although we did not find any critical bugs, most of
+the bugs are seemingly important as per the categorization given by
+engineers. Analyzing the issue tracker of \chakra, we found that
+severity-1 bugs are indeed rare. Considering the bug reports confirmed
+by developers, \chakra{} was the engine with the highest number--12
+(with 3 bugs fixed). Considering the remaining engines, \veight{}
+developers confirmed the three bugs we reported, fixing
+one. Curiously, Google engineers confirmed the report we issued in a
+few hours. Overall, we found that development teams of other engines,
+specially \jsc\, took much longer to analyze bug reports as can be
+observed in the \jsc\ stacked bar from
+Figure~\ref{fig:stacked-engine}. Curiously, however, the bugs that the
+\jsc{} team confirms are quickly fixed.
 

### 2018-08-25 paper/paper.tex
minor fix in related work

@@
 Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to findcross-browser HTML+JS
-discrepancies. Their fuzzer can be used to find bugs in JS engines and
-Web Assembly engines. The sensible parts of the infrastructure they
+language-agnostic fuzzer to find cross-browser HTML+JS
+discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
+Web Assembly engines.} The sensible parts of the infrastructure they
 built are the checks of input validity (as to reduce waste/cost) and

### 2018-08-25 paper/paper.tex
pass on fixes

--- 2018-08-25 paper/paper.tex
@@
 development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
+accomodate the pressing demands from
 developers~\cite{ecmas262-spec-repo}. An official conformance test
@@
 a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). A positive aspect of the approach is that
+not eager JIT compilation). A positive aspect of the aproach is that
 it can be fully automated. As the same engine is used, the outcomes of
@@
   \item We made our testing infrastructure, results, and experimental
-    scripts available to the public. (upon request for anonymity.)
+    scripts available to the public. (upon request for anonimity.)
 
@@
 \totalTestFilesForTestTransplantation{} tests included in the circle
-from the table in the evaluation of test transplantation, \ie{}, the
+from the table in the evaluation of test transplantion, \ie{}, the
 difference between sets ``compile-in-all'' and Test262. We did not
@@
 through the violation of an assertion declared in the test. In
-contrast, warnings of type ``\lo{}'' are more likely to be associated
+contrast, warnings of type ``\lo{}'' are more likely to be asssociated
 with invalid inputs. They reflect the cases where the anomaly is
@@
 tests over this period. The variance of results was negligible; for
-that reasons, we omitted standard deviations. We noticed that all four
+that reasons, we omited standard deviations. We noticed that all four
 engines we analyzed but \chakra{} use some variant of the Test262
@@
 experimental mode with the flag \CodeIn{-ES6Experimental}.
+%% \Mar{igor,
+%%   nao consigo entender o porque deste caso nao dar aqueles erros
+%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
+%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
+%% }
+%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
+%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
+%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
+%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
+%% }
 \textbf{Non-Standard Element.} These cases manifest when a function or
@@
 its harness) capture the corresponding exception, making the test to
-fail in an assertion instead.  \textbf{Other.} This category includes
-other sources. For example, it includes the cases where the test was
-valid for some previous version of the spec but is no longer valid for
-the current spec.
+fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
+  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
+  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
+  por exemplo cobre uma especificacao antiga onde o
+  teste esperava uma propriedade true, mas na documentacao 
+  cita que a propriedade tem que ser false.}\Mar{nao
+  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
+  seja mais especifico, por favor!}
+  \Igor{nao, o teste eh valido (nao quebra por ReferenceError/TypeError) e
+  nao entra no undefined behaviour pq nao afeta a especificacao. Isso eh um caso,
+  outros casos estao ligados a nao-compreensao do testcase }  \textbf{Unknown.} This category
+includes the cases we were unable to confidently diagnose the failure
+but we suspected it was a false alarm.
 
@@
     & Non-Standard Element & 119 \\
-    & Other & 135 \\
+    & Unknown & 135 \\
     \midrule
@@
 false and true positives. Considering false positives, ``Undefined
-Behavior'' was the most predominant source. Considering true
-positives, we found a reasonable number of duplicate reports, but not
-enough high to justify attempting to automate the detection of
-duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
-we found with test transplantation. The first column shows the
-identifier we assigned to the bug\Comment{, column ``Date'' shows the
-  date the bug was reported in the format ``m/dd'',}, column
-``Engine'' shows the affected engine, column ``Status'' shows the
-status of the bug report at the time of the writing. The status string
-appears in bold face for status ``Confirmed'' or higher, \ie{},
-``Assigned'' and ``Fixed''.  Column ``Url'' shows the URL
-(de-anonymized upon request) for the bug report entry in the
-corresponding bug-tracking system, column ``Severity'' shows the
-severity level for confirmed bugs, and, finally, column ``Suite''
-shows the name of the engine that originated the test.
+Behavior'' and ``Non-Standard Element'' were the most predominant
+sources. Considering true positives, we found a reasonable number of
+duplicate reports, but not enough high to justify attempting to
+automate the detection of duplicates.
+Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
+test transplantation. The first column shows the identifier we
+assigned to the bug\Comment{, column ``Date'' shows the date the bug
+  was reported in the format ``m/dd'',}, column ``Engine'' shows the
+affected engine, column ``Status'' shows the status of the bug report
+at the time of the writing. The status string appears in bold face for
+status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
+Column ``Url'' shows the URL (de-anonymized upon request) for the bug
+report entry in the corresponding bug-tracking system, column
+``Severity'' shows the severity level for confirmed bugs, and,
+finally, column ``Suite'' shows the name of the engine that originated
+the test.
 
@@
 report is pending confirmation.\Mar{por favor,
-  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
-the \Fix{17} bugs we reported in this experiment, \Fix{9} were
-promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
+  corrija estes numeros *com cuidado*! se possivel, use macros.}\Igor{Done} Of
+the \noBugsTransplantation{} bugs we reported in this experiment, \noTransConfirmed{} were
+promoted from the status ``New'' to ``Confirmed''. Of these, \noTransSeverityTwo{}
 are severity-2 bugs.  Although we did not find any showstopper
@@
 the bugs confirmed by developers, \chakra{} was the engine with the
-highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
-the remaining engines, \veight{} developers confirmed \Fix{two} of the
-\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
-engineers confirmed the report we issued in a few hours. We found that
+highest number, \noTransChakraBugs{} in total, with \noTransChakraBugsFixed{} 
+bug fixed. Considering the remaining engines, \veight{} 
+developers confirmed \noTransVeightBugsConfirmed{} of the
+\noTransVeightBugsReported{} bug we reported, fixing \noTransVeightBugsFixed{}. 
+Curiously, Google engineers confirmed the report we issued in a few hours. We found that
 development teams of other engines, specially \jsc\, took much longer
@@
 and the test suite from the original test input (``Suite''). So far,
-\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
+\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
 were fixed. Note that one bug report that we submitted was rejected on
 the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
+across engine implementations that was cosidered to be acceptable. As
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
@@
 This section discusses a selection of bugs reports. The selection
-criteria we used was: (i) to cover each engine that we found
-bugs--\chakra, \jsc, and \veight, (ii) to cover a different
-technique--test transplantation and differential testing (with
-\radamsa\ and with \quickfuzz), (iii) to cover a case of rejected bug
-report, and (iv) to use short test inputs (for space).
+criteria we used was: (i) to cover each of the engines we were able to
+find bugs--\chakra, \jsc, and \veight, (ii) to cover a different
+successful technique--test transplantation and differential testing
+(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
+rejected bug report, and (iv) the test is short.
 
@@
 {var a =
-  {valueOf: function(){ return "\x00"}}
-  assert(+a === 0)
-}
+  {valueOf:~function(){ return "\x00"}}
+  assert(+a === 0)}
   \end{lstlisting}
@@
 version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
+returns a string representation of a null character (\CodeIn{NUL} in
+ascii). The unary plus expression ``\CodeIn{+a}", used in the
 assertion, is equivalent to the operation
@@
 should throw an early error--in this case a SyntaxError--if the break
-statement is not nested in an iterable or a switch statement. In
+statement is not nested in an iterational or a switch statement. In
 this case, all engines behave as expected but \veight{} pass without
@@
   \begin{lstlisting}
-var obj = {};
-var arr = [];
+var obj = {}; var arr = [];
 try {
@@
   return typeof String.prototype.repeat === "function"
-  && "foo".repeat(657604378) === "foofoofoo";
-}
+    && "foo".repeat(657604378) === "foofoofoo"; }
   \end{lstlisting}
@@
 of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
-efficiency, is tightly integrated to our infrastructure.
+efficiency, is tighly integrated to our infrastructure.
 
@@
     at finding bugs in \js\ engines;
-  \item The cost of inspecting failures/warnings is high. Although the
+  \item The cost of inpecting failures/warnings is high. Although the
     inspection activity was not uninterrupted, it is safe to say that
@@
 discrepancies. Their fuzzer can be used to find bugs in JS engines and
-Web Assembly engines. The sensible parts of the infrastructure they
+WebAssembly engines. The sensible parts of the infrastructure they
 built are the checks of input validity (as to reduce waste/cost) and
@@
 %%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
-%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
-%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
+%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC
+%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii
 %%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
-%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber
-%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
-%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
-%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
-%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
-%%  LocalWords:  escapeinside morekeywords
+%%  LocalWords:  SSL TLS ICSE

### 2018-08-25 paper/paper.tex

--- 2018-08-25 paper/paper.tex
@@
 and the test suite from the original test input (``Suite''). So far,
-\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
+\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
 were fixed. Note that one bug report that we submitted was rejected on
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#2,
+\vspace{1ex}\noindent\textbf{Issue \#18,
   Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below

### 2018-08-25 paper/paper.tex
minor fix in list of contributions

@@
   \item We reported a total of \totalBugsReported{} bugs on these
-    engines. Of which, \totalBugsConfirmed{} confirmed and
-    \totalBugsFixed{} fixed;
+    engines. Of these, \totalBugsConfirmed{} bug reported were confirmed and
+    \totalBugsFixed{} were fixed;
 
@@
 analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \Fix{five} warnings in each group. A warning belongs to the
+analyzed \warningsIteration{} warnings in each group. A warning belongs to the
 group of a given engine if only that engine manifests distinct
@@
 sensitive to function specifications. The source ``Error Message Mismatch''
-indicates that \Mar{por favor, explique. nao consigo lembrar.}
-\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
-alterar o corpo da mensagem. Casos onde o fuzzer muda a msg em uma assercao 
-(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")').
+indicates that 
+\Igor{
+  o fuzzer realiza mutacoes em assercoes que usam comparacao de string e/ou 
+  expressoes regulares.
 }

### 2018-08-25 paper/paper.tex
minor fixes
pass on fixes
final pass

@@
 with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. The source ``Error Message Mismatch''
-indicates that 
-\Igor{
-  o fuzzer realiza mutacoes em assercoes que usam comparacao de string e/ou 
-  expressoes regulares.
-}
+sensitive to function specifications. Consequently, it can replace
+valid with invalid inputs. The source ``Error Message Mismatch''
+corresponds to the cases where the fuzzer modifies the assertion
+expression (\eg{}, some string expression or regular expression).
 
@@
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. In \veight{}, we reported two
+were duplicates and were not reported. Considering \veight{}, we reported two
 bugs, both of which were confirmed, with one fixed.
@@
 %%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
-%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU
+%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU os
 %%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
@@
 %%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
-%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber
+%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber sep
 %%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
@@
 %%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
-%%  LocalWords:  escapeinside morekeywords
+%%  LocalWords:  escapeinside morekeywords cccrr ccrrrr Duktape JSI
+%%  LocalWords:  Lembrar que

### 2018-11-12 paper/paper.tex
fix conclusion
pending commit

@@
 developers~\cite{ecmas262-spec-repo}. An official conformance test
-suites exist for \js~\cite{tc39-github}, but, naturally, many test
+suite exists for \js~\cite{tc39-github}, but, naturally, many test
 scenarios are not covered in the suite. In addition, we noticed that a
@@
 \noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
-number of bug reports found per engine (\ref{fig:stacked-engine}) and
-technique (\ref{fig:stacked-technique}). Each stacked bar breaks down
-the bugs per status (\eg{}, ``1-New''). The prefix number serves to
-indicate the ordering that status labels are assigned. Note that
-several of these reports have the label ``3-Fixed'', indicating that
-bug fixes have been incorporated into the code already.\Comment{
-  Depending on the issue date, the fix may be in the latest release of
-  the corresponding engines.} Overall, discarding bug reports with the
-``1-New'' status, we reported a total of \totalBugsConfirmed{}
-bugs. We found that the vast majority of bug reports targeted the engines
-from Microsoft and Apple. Considering the techniques, the number of
-bug reports were similar, if we consider only those confirmed or
-fixed. Most of these bugs are of moderate severity. All in all, these
-simple techniques seem promising to improve reliability of engines
-that continuously evolve with their specifications.
-
-%% We found,
-%% however, that the cost of inspecting \Fix{...elaborate...}
-%% It is
-%% also worth noting that several of these reports hold the status
-%% ``new'', which indicates that they were not reviewed yet by the
-%% development team. Note also that we did not find bugs in the Mozilla
-%% \smonkey\ engine.
+breakdown of bug reports found per engine (\ref{fig:stacked-engine})
+and technique (\ref{fig:stacked-technique}). Each stacked bar breaks
+down the bugs per status (\eg{}, ``1-New'', ``2-Confirmed'',
+etc.). The prefix number indicates the ordering that status labels are
+assigned. Note that several of these reports have the label
+``3-Fixed'', indicating that bug fixes have been incorporated into the
+code already.\Comment{ Depending on the issue date, the fix may be in
+  the latest release of the corresponding engines.} Overall, ignoring
+bug reports with the ``1-New'' status, we reported a total of
+\totalBugsConfirmed{} bugs. We found that the vast majority of bug
+reports targeted the engines from Microsoft and Apple. Considering the
+techniques, the number of bug reports were similar, if we consider
+only those confirmed or fixed. Most of these bugs are of moderate
+severity. All in all, these simple techniques seem promising to
+improve reliability of engines that continuously evolve with their
+specifications.
 
@@
 statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
-how eval should be handle code containing a function declaration.
-According to specification~\cite{break-statement}, the break statement
-should throw an early error--in this case a SyntaxError--if the break
-statement is not nested in an iterable or a switch statement. In
-this case, all engines behave as expected but \veight{} pass without
-failures.
+how eval should handle code containing function declarations.
+According to the spec~\cite{break-statement}, the virtual machine
+should throw an early error--in this case, a SyntaxError--if the break
+statement is not nested in an iterable or a switch statement. In this
+case, all engines, but \veight{}, behave as expected.
 
@@
 \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsConfirmed\ were fixed. Although more work is necessary to
+\totalBugsFixed\ were fixed. Although more work is necessary to
 reduce cost of manual analysis, we found that both techniques we used

### 2018-12-12 paper/abstract.tex
formatting paper to ISSTA + adding important comments to paper

@@
 JavaScript is a very popular programming language today with several
-engine implementations competing for market dominance. Although a
+implementations competing for market dominance. Although a
 specification document and a conformance test suite exist to guide
@@
 consequences. Implementing correct
-engines is challenging because the specification is intentionally
+engines is challenging because the spec is intentionally
 incomplete and evolves frequently.
 
-This paper reports on a study we ran to evaluate the importance of
+%reports on a study we ran to 
+This paper evaluates the importance of
 diversity to find functional bugs in JavaScript engines. For that, we
-use two simple diversity-aware techniques---test transplantation and
+explored two simple diversity-aware techniques---test transplantation and
 cross-engine differential testing. The first technique runs test
@@
 
+\sloppy
 We considered engines from four major players in our
@@
 \jsc{} and Microsoft's \chakra{}. To sum, our results show that
-exploring diversity is effective to find bugs in JavaScript engines.
+diversity-aware techniques are easy to apply and very effective in
+finding bugs in complex software, such as JavaScript engines.
 

### 2018-12-12 paper/paper.tex
formatting paper to ISSTA + adding important comments to paper

@@
-%\documentclass[conference]{IEEEtran}
-\documentclass[10pt,conference,anonymous]{IEEEtran}
-\IEEEoverridecommandlockouts
-
-%% Marcelo added this
-\makeatletter
-\renewcommand\footnoterule{%
-  \kern-3\p@
-  \hrule\@width.4\columnwidth
-  \kern2.6\p@}
-  \makeatother
-
-\input{packages}
+\documentclass[sigconf,screen,anonymous]{acmart}
+
+\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis}
+
+%\input{packages}
+
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{tikz}
+\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
+\usepackage{listings}
+\usepackage[caption=false, font=footnotesize]{subfig}
+%%%%%%%%%%%%% code listing
+\renewcommand{\ttdefault}{pcr}
+\lstset{
+  basicstyle=\scriptsize\ttfamily,
+  keywordstyle=\scriptsize\ttfamily\bfseries,
+  language=Java,             % choose the language of the code
+  frame=single,              % adds a frame around the code
+  aboveskip=0pt,
+  belowskip=0pt,
+  breaklines=true,           % sets automatic line breaking
+  breakatwhitespace=false,   % sets if automatic breaks should only happen at
+  showspaces=false,
+  %numbersep=5pt,              % Abstand der Nummern zum Text
+  %tabsize=2,                  % Groesse von Tabs
+  %extendedchars=true,         %
+  %breaklines=true,            % Zeilen werden Umgebrochen
+  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
+}
+\usepackage{balance}
+\usepackage{wrapfig}
+
 \input{macros}
 
+% Copyright
+%\setcopyright{none}
+\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+\acmDOI{10.475/123_4}
+
+% ISBN
+\acmISBN{123-4567-24-567/08/06}
+
+%Conference
+\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
+  Paso, Texas USA}
+\acmYear{1997}
+\copyrightyear{2016}
+
+\acmArticle{4}
+\acmPrice{15.00}
+
+% These commands are optional
+%\acmBooktitle{Transactions of the ACM Woodstock conference}
+\editor{Jennifer B. Sartor}
+\editor{Theo D'Hondt}
+\editor{Wolfgang De Meuter}
+
 \begin{document}
 
-%Should I Fuzz my Inputs or Improve my Tests? 
-\title{Leveraging Diversity to Find Bugs\\ in JavaScript Engines}
-
-%% \author{
-%% \IEEEauthorblockN{Igor Sim\~oes\qquad{}Marcelo d'Amorim}
-%% \IEEEauthorblockA{Federla University of Pernambuco, Brazil\\
-%% \{isol2,damorim\}@cin.ufpe.br}
-%% }
-
-\maketitle
-
-%% page numbering -M
-\thispagestyle{plain}
-\pagestyle{plain}
-
-%% JavaScript (\js{}) is a popular programming language for the
-%% web. Finding errors in JS runtime engines is an important problem.
+\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
+%% \titlenote{Produces the permission block, and
+%%   copyright information}
+%% \subtitle{Extended Abstract}
+%% \subtitlenote{The full version of the author's guide is available as
+%%   \texttt{acmart.pdf} document}
+
+%mf: the following follow acm format and prevents to have superscripts in the header of every page
+\settopmatter{authorsperrow=4}
+
+\author{Igor Lima}
+%\authornote{Dr.~Trovato insisted his name be first.}
+\orcid{1234-5678-9012}
+\affiliation{%
+  \institution{Federal University of Pernambuco}
+  \streetaddress{P.O. Box 1212}
+  \city{Recife}
+  \state{PE}
+  \country{Brazil}
+%  \postcode{43017-6221}
+}
+\email{isol2@cin.ufpe.br}
+
+\author{Marcelo d'Amorim}
+\orcid{/0000-0002-1323-8769}
+\affiliation{%
+  \institution{Federal University of Pernambuco}
+  \streetaddress{P.O. Box 1212}
+  \city{Recife}
+  \state{PE}
+  \country{Brazil}
+%  \postcode{43017-6221}
+}
+\email{damorim@cin.ufpe.br}
+
+% The default list of authors is too long for headers.
+\renewcommand{\shortauthors}{Lima and d'Amorim}
+
 \begin{abstract}
@@
 
-\begin{IEEEkeywords}
-JavaScript; Diversity; Software Testing
-\end{IEEEkeywords}
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below.
+%
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
+<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Software testing and debugging}
+
+\keywords{JavaScript, Diversity, Software Testing}
+
+\maketitle
 
@@
 
-% ,business-insider
 JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{redmonk-javascript,stackify} with
-penetration in various software development segments including, web, mobile,
+today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
 and, more recently, the Internet of
@@
 JavaScript engines.
+
+\emph{Key Findings.}~\Fix{copied from ICSE meta-review $\rightarrow$}The key
+findings could include, e.g.: - Not only multiple different
+implementations can be leveraged in differential testing, also
+differences in test suites can be important.  - Even for problems with
+fairly clear specifications, as here for a programming language and
+how it is to be executed, there is likely to be (a lot of) variation
+between different implementations.  - Differential testing is feasible
+on real, complex, widely used pieces of software.
 
@@
 \begin{table}[t]
+  \small
   \centering
@@
     that pass in all four engines we analyzed.}
-  \setlength{\tabcolsep}{2.5pt}      
+  \setlength{\tabcolsep}{2.25pt}      
   \begin{tabular}{ccrrrr}
@@
 
-% For example to run the \jerry{} tests it was necessary 
-% use the unit-test package to run it, but with our changes we added the assertion
-% does not have an assertion in the test file
-% \Fix{add code to explain}
+For example to run the \jerry{} tests it was necessary 
+use the unit-test package to run it, but with our changes we added the assertion
+does not have an assertion in the test file
+\Fix{add code to explain}
 
@@
 
+\Fix{reviewer asks for more details...}
+
 \section{Results}
@@
 %\end{wraptable}
-\
-\begin{table}[t]
+
+We used the official conformance test suite
+Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this test. However, we
+expect that results provide indication of engine's maturity. In the
+limit, it is not desirable to flood bug reports on engines at early
+stages of development. We ran the suite once a day for seven
+\begin{wraptable}[12]{r}{0.2\textwidth}  
   \centering
@@
   \normalsize
-\end{table}
-
-We used the official conformance test suite
-Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this test. However, we
-expect that results provide indication of engine's maturity. In the
-limit, it is not desirable to flood bug reports on engines at early
-stages of development. We ran the suite once a day for seven
+\end{wraptable}
 consecutive days from the period of 16 to 22 of August,
@@
 
+\sloppy
 The sources of false positives found in this experiment are as
@@
 \begin{table}[t!]
-  \setlength{\tabcolsep}{4pt}    
+  \small
+%  \setlength{\tabcolsep}{4pt}    
   \centering
@@
 
-\begin{table}[h]
+\begin{table}[t]
+  \small
   \centering
@@
 
-Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
-from Section~\ref{sec:clusterization} that we do not cluster
-\hi\ warnings\Comment{ as there was no clear clustering criteria to
-  use for that}. This table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
-and second place, respectively, in number of warnings (/failures)
-compared to other engines.
-
-\begin{table}[h]
-  \setlength{\tabcolsep}{5pt}
+\begin{table}[t]
+  \small
+  \setlength{\tabcolsep}{4.5pt}
   \centering
@@
 
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These sources are
-highlighted with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-\begin{table}[h]
+\begin{table}[t]
+  \small
   \centering
@@
 
+Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
+from Section~\ref{sec:clusterization} that we do not cluster
+\hi\ warnings\Comment{ as there was no clear clustering criteria to
+  use for that}. This table breaks down \hi\ warning by the affected
+engine, \ie, the engine manifesting distinct output among those
+analyzed. Column ``+1'' shows the cases where more than one engine
+disagree on the output. Note from the totals that the ordering of
+engines is consistent with the one observed on
+Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
+and second place, respectively, in number of warnings (/failures)
+compared to other engines.
+
+Table~\ref{tab:false-positives} shows the distribution of false
+positives per source. The sources of imprecision are as defined in
+Section~\ref{sec:transplantation} with the addition of two new
+sources, which we did not observe before. These sources are
+highlighted with a ``*'' in the table. The source ``Invalid Input''
+indicates that the test input violated some part of the
+specification. For example, the test indirectly invoked some function
+with unexpected arguments; this happens because fuzzing is not
+sensitive to function specifications. Consequently, it can replace
+valid with invalid inputs. The source ``Error Message Mismatch''
+corresponds to the cases where the fuzzer modifies the assertion
+expression (\eg{}, some string expression or regular expression).
+
+%% \Igor{devemos remover isso da 
+%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
+%% The source ``Upcoming Feature''
+%% indicates that the test fails because it uses a feature that is
+%% available in the original engine, but it is still not standard, and
+%% the target engine does not support that feature}. For example,
+%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
+
 %% The table is
@@
 %% the results obtained during the non-exploratory phase.
+
+\input{table_differential}
 
@@
 %% total of 30K test files.
-
-\input{table_differential}
 
@@
 
+\Fix{elaborate}
+
 \subsection{Lessons Learned}
@@
 
+\Fix{revisor(es) reclamaram de pouca discussao. isto poderia ser usado
+  em outros contexto? (resp: JS possui varias engine e muitos
+  tests...) ver tambem ``key findings'' na introducao (precisa ficar
+  consistente)}
+
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
+
+\subsection{Testing \js\ Programs}
+Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
+lightweight approach to detect conflicts in \js\ libraries that occur
+when names introduced by different libraries collide. This problem was
+found to be common as the design of \js\ allows for overlaps in
+namespaces. A similar problem has been investigated by Nguyen and
+colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
+colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
+programs, which are popular in the context of Content Management
+Systems as WordPress. The focus of this paper is on testing
+\js\ engines as opposed to \js\ programs. Our goal is therefore
+orthogonal to theirs.
 
@@
 
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
+\subsection{Diversity in Testing}
+
+\Fix{Discuss...}~\cite{Chen:2010:ART:1663656.1663914,7515474}
 
@@
 \balance
-\bibliographystyle{plain}
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{references,../docs/google-research-awards-latam/tmp}
@@
 \end{document}
-
-%%  LocalWords:  bytecodes JScript Ecma ome IoT Kangax DT JS fuzzer
-%%  LocalWords:  jsfunfuzz jit funfuzz \smonkey{} toPrecision JSVU os
-%%  LocalWords:  GoogleChromeLab's cccr js runtime Fuzzers Radamsa de
-%%  LocalWords:  QuickFuzz fuzzers Grammarinator LangFuzz Megadeth
-%%  LocalWords:  AFL libFuzzer toolchain sanitizers arrowed eshost
-%%  LocalWords:  cli pre EcmaScript dataset piecharts piechart \chakra{}
-%%  LocalWords:  JavascriptCore Url radamsa TinyJS \jerry{} JSC crr
-%%  LocalWords:  quickfuzz \jsc{} \chakra{}'s valueOf NUL ascii crrrr
-%%  LocalWords:  unary ToNumber NaN testcase WebKit typeof foofoofoo
-%%  LocalWords:  SSL TLS ICSE ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks subtrees ArrayBuffer RangeError eval
-%%  LocalWords:  ToIndex Clusterization DataView setInt getInt boxpos
-%%  LocalWords:  JavaScriptCore SpiderMonkey byteOffset anonymized
-%%  LocalWords:  xleftmargin framexleftmargin basicstyle numberstyle
-%%  LocalWords:  escapeinside morekeywords cccrr ccrrrr Duktape JSI
-%%  LocalWords:  Lembrar que

### 2019-01-28 paper/paper.tex
updated ACM style

@@
-\documentclass[sigconf,screen,anonymous]{acmart}
+\documentclass[sigconf,review, anonymous]{acmart}
 
@@
 \usepackage{wrapfig}
+\usepackage{enumitem}
 
@@
 %Conference
-\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
-  Paso, Texas USA}
+\acmConference[ESEC/FSE 2019]{The 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{26--30 August, 2019}{Tallinn, Estonia}
 \acmYear{1997}
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). This paper evaluates the potential
-benefits of diversity techniques, including DT. It provides data to
-support or not the decision for automation of these techniques.
+~\ref{tab:false-positives}). \Mar{rewrite. too vague.}\Fix{This paper
+  evaluates the potential benefits of diversity techniques, including
+  DT. It provides data to support or not the decision for automation
+  of these techniques.}
 
@@
 bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
-none in Mozilla's \smonkey{}. Our results indicate that both
-techniques were successful at finding bugs, but, overall, test
-transplantation demanded less effort compared to differential testing
-per bug found. Although our experience indicates that more research
-needs be done to automate parts of the inspection process, our results
-show that exploring diversity is a valuable help to find bugs in
-JavaScript engines.
-
-\emph{Key Findings.}~\Fix{copied from ICSE meta-review $\rightarrow$}The key
+none in Mozilla's \smonkey{}.
+
+\emph{Key Findings.}~Results indicate that both techniques were
+successful at finding bugs. Overall, test transplantation demanded
+less effort compared to differential testing per bug
+found.\Fix{redundant with the sentences that follow...check} Although
+our experience indicates that more research needs be done to automate
+parts of the inspection process, our results show that exploring
+diversity is a valuable help to find bugs in JavaScript
+engines. \Fix{copied from ICSE meta-review $\rightarrow$}The key
 findings could include, e.g.: - Not only multiple different
@@
 
-The specification and implementation of JavaScript are
-incomplete. Certain parts of the specification are undefined; it is
-responsibility of engine engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
+For different reasons, the specification and implementation of
+JavaScript are incomplete. Certain parts of the specification are
+undefined; it is responsibility of engineers to decide how to
+implement these functionalities. The JavaScript spec uses the label
 ``implementation-dependent'' to indicate these cases, where behavior
@@
 spec exists is to enable compiler optimizations. For example, the
-\mcodeid{for-in} loop does not clearly specify the iteration
-order of elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for optimization~\cite{for-in-undefined}.  As another
-example, the specification states that if
-the \mcodeid{Number.toPrecision()} function is called with multiple arguments then the floating-point approximation is
+\mcodeid{for-in} loop does not clearly specify the iteration order of
+elements~\cite{so-forin-undefined,javascript-in-chrome} and different
+engines capitalize on that for optimization~\cite{for-in-undefined}.
+As another example, the specification states that if the
+\mcodeid{Number.toPrecision()} function is called with multiple
+arguments then the floating-point approximation is
 implementation-dependent~\cite{es6-toPrecision}. Various other cases
@@
 as can be observed by the Kangax compatibility table~\cite{kangax}.
-It is also worth noting that, as in other languages, some
-elements in JS have non-deterministic behavior (\eg{},
-\mcodeid{Math.random} and \mcodeid{Date}). A test that make decisions
-based on these elements could, in principle, produce different
-outcomes on different runs. Carefully-written test cases should not
-manifest this kind of
-flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}, but
-fuzzed are more likely to manifest them.
-As mentioned previously, all those aspects make testing \js\ engines
-more challenging.
+It is also worth noting that, as in other languages, some elements in
+JS have non-deterministic behavior (\eg{}, \mcodeid{Math.random} and
+\mcodeid{Date}). A test that make decisions based on these elements
+could, in principle, produce different outcomes on different
+runs. Carefully-written test cases should not manifest this kind of
+flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}.  As
+mentioned previously, all those aspects make testing \js\ engines more
+challenging.
 
@@
 
-%\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
-\begin{figure}[t!]
-  \centering
-%  \includegraphics[trim=20 350 200
-%    0,clip,width=0.35\textwidth]{google-awards-workflow}
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-\end{figure}
-
-\Comment{ Several fuzzing methods
-  have been proposed in the past, varying with respect to how new
-  inputs are
-  generated~\cite{afl,honggfuzz,grammarinator,jsfunfuzz,radamsa}.}
-
 Figure~\ref{fig:workflow} illustrates the 
@@
 
-%The checker can produce multiple warnings for a given input.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+\end{figure}
 
@@
 The goal of our study is to assess reliability of \js\ engines by
-leveraging implementation diversity. We organized our study in three
-parts. First, we report on the conformance of the engines we studied
-using the official Test262 conformance
-suite~\cite{ecma262-conformance-suite}
+leveraging on diversity of test data and engine implementations. Based
+on that, we pose three questions:
+\begin{description}[leftmargin=.5in]
+\item[RQ1.] How conformant are the engines to the Test262 suite?
+\item[RQ2.] How effective is test transplantation to find bugs?
+\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
+\end{description}
+
+The first question focuses on the conformance of our selected engines
+to the official Test262 suite~\cite{ecma262-conformance-suite}
 (Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. Second, we report results
-obtained with test transplantation
-(Section~\ref{sec:transplantation}). The rationale is that developers
-consider different goals when writing test cases--suites written for a
-given engine should cover scenarios not covered by a different
-engine. Third, we analyzed the impact of using cross-engine
-differential testing to find bugs
-(Section~\ref{sec:cross-engine-diff-testing-results}). The rationale
-is that bugs may be detected using inputs which are similar to those
-already tested. Our broad goal is to evaluate ability of these simple
-diversity-aware techniques in bug finding.
-
-%Figure~\ref{fig:summary} summarizes the bugs we reported.
+relevance if the engines are too unreliable. The second question
+focuses on the effectiveness of test transplantation
+(Section~\ref{sec:transplantation}). The rationale for using inputs
+from different engines is that developers consider different goals
+when writing test cases--suites written for a given engine should
+cover scenarios not covered by a different engine. The third question
+evaluates the effectiveness of cross-engine differential testing to
+find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
+rationale is that bugs may be detected using inputs which are similar
+to those already tested. Overall, our goal is to evaluate ability of
+these simple diversity-aware techniques to find bugs.
 
@@
 
-\subsection{Conformance}
+\subsection{Answering RQ1 (Conformance)}
 \label{sec:stability}
@@
 
-\subsection{Test Transplantation}
+\begin{center}
+  \fbox{
+    \begin{minipage}{8cm}
+      \textit{Summary:}~...
+      \end{minipage}
+    }
+\end{center}
+
+\subsection{Answering RQ2 (Test Transplantation)}
 \label{sec:transplantation}
@@
 
-\subsection{Cross-Engine Differential Testing}
+\subsection{Answering RQ3 (Differential Testing)}
 \label{sec:cross-engine-diff-testing-results}
 
-This section reports the results obtained with differential
+This section reports the results obtained with cross-engine differential
 testing. More precisely, we report results obtained by fuzzing test
@@
 Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the date the bug was reported (``Date''), the fuzzing tool used
-(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
+shows the fuzzing tool used
+(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
 bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report

### 2019-01-28 paper/paper.tex
finding some room for new contributions

@@
 
-%\begin{wraptable}[10]{r}{0.25\textwidth}
-%  \vspace{-3ex}
-%\end{wraptable}
-
-We used the official conformance test suite
-Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this test. However, we
-expect that results provide indication of engine's maturity. In the
-limit, it is not desirable to flood bug reports on engines at early
-stages of development. We ran the suite once a day for seven
-\begin{wraptable}[12]{r}{0.2\textwidth}  
+\begin{wraptable}[11]{r}{0.22\textwidth}
+  \vspace{-4ex}      
   \centering
@@
   \normalsize
+  \vspace{-4ex}
 \end{wraptable}
+We used the official conformance test suite
+Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this test. However, we
+expect that results provide indication of engine's maturity. In the
+limit, it is not desirable to flood bug reports on engines at early
+stages of development. We ran the suite once a day for seven
 consecutive days from the period of 16 to 22 of August,
@@
 
-\vspace{0.5ex}
+%\vspace{0.5ex}
 \subsubsection{Methodology}
@@
 
-\vspace{0.5ex}
+%\vspace{0.5ex}
 \subsubsection{Results}
@@
     test suites.}
+  \renewcommand*{\arraystretch}{0.9}
   \begin{tabular}{crrrr}
@@
   \end{tabular}
+  \vspace{-3ex}
 \end{table}
@@
 
-%% \begin{figure}[h]
-%%   \centering
-%%   \subfloat[\label{fig:falsepositives}False Positives]{%
-%%     \includegraphics[trim=0 150 0 100,clip,width=0.4\textwidth]{R/piecharts/falsepositives}
-%%   }
-%%   \label{1a}\hfill
-%%   \subfloat[\label{fig:truepositives}True Positives]{%
-%%     \includegraphics[trim=0 150 0 150,clip,width=0.4\textwidth]{R/piecharts/truepositives}    
-%%   }
-%%   \label{1b}\\
-%%   \caption{\label{fig:piecharts-transplantation}False and True positives.}
-%% \end{figure}
-
-\begin{table}[t!]
+\begin{wraptable}[12]{r}{0.23\textwidth}  
   \small
-%  \setlength{\tabcolsep}{4pt}    
   \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution of false and true positives.}
+  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
+    of False (FP) and True Positives (TP).}
+  \setlength{\tabcolsep}{3pt}      
+  \renewcommand*{\arraystretch}{0.9}
   \begin{tabular}{ccr}
@@
     \midrule
-    \multirow{5}{*}{False Positives} & Undefined Behavior & 252 \\
+    \multirow{5}{*}{FP} & Undefined Behavior & 252 \\
     & Timeout/OME & 15 \\
@@
     \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & 10 \\
+    \multirow{2}{*}{TP} & Duplicate & 10 \\
     & Bug & 24 \\
@@
   \end{tabular}
-\end{table}
-
-%%  The piechart at the top
-%% shows false alarms. The absolute number of tests in each category is
-%% shown in parentheses to the right-side of each slice label naming the
-%% source of false positive.
-
-\input{table_transplantation}
-
-% (\eg{},``New'', ``Rejected'', ``Confirmed'', ``Fixed'')
-
+\end{wraptable}
 Table~\ref{fig:piecharts-transplantation} shows the distribution of
@@
 appears in bold face for status ``Confirmed'' or higher, \ie{},
-``Assigned'' and ``Fixed''.  Column ``Url'' shows the URL
-(de-anonymized upon request) for the bug report entry in the
-corresponding bug-tracking system, column ``Severity'' shows the
-severity level for confirmed bugs, and, finally, column ``Suite''
+``Assigned'' and ``Fixed''.  Column ``Severity'' shows the
+severity of confirmed bugs, and, finally, column ``Suite''
 shows the name of the engine that originated the test.
 
-%Note that bug reports \#4 and \#23 afected multiple engines.
+%% ``Url'' shows the URL
+%% (de-anonymized upon request) for the bug report entry in the
+%% corresponding bug-tracking system, column
+
+\input{table_transplantation}
 
@@
 
+Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings, which
+are not clustered. The table breaks down \hi\ warning by the affected
+engine, \ie, the engine manifesting distinct output among those
+analyzed. Column ``+1'' shows the cases where more than one engine
+disagree on the output. Note from the totals that the ordering of
+engines is consistent with the one observed on
+Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
+second places, respectively, in number of warnings.
+
 \begin{table}[t]
@@
 \end{table}
+
+Table~\ref{tab:false-positives} shows the distribution of false
+positives per source. The sources of imprecision are as defined in
+Section~\ref{sec:transplantation} with the addition of two new
+sources, which we did not observe before. These sources are
+highlighted with a ``*'' in the table. The source ``Invalid Input''
+indicates that the test input violated some part of the
+specification. For example, the test indirectly invoked some function
+with unexpected arguments; this happens because fuzzing is not
+sensitive to function specifications. Consequently, it can replace
+valid with invalid inputs. The source ``Error Message Mismatch''
+corresponds to the cases where the fuzzer modifies the assertion
+expression (\eg{}, some string expression or regular expression).
 
@@
 
-Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings; recall
-from Section~\ref{sec:clusterization} that we do not cluster
-\hi\ warnings\Comment{ as there was no clear clustering criteria to
-  use for that}. This table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ holding first
-and second place, respectively, in number of warnings (/failures)
-compared to other engines.
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These sources are
-highlighted with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
 %% \Igor{devemos remover isso da 
@@
 %% the results obtained during the non-exploratory phase.
-
-\input{table_differential}
 
@@
 bugs, both of which were confirmed, with one fixed.
+
+\input{table_differential}
 

### 2019-01-28 paper/table_differential.tex
adding extra space to fill 10 pages
formatting paper to ISSTA + adding important comments to paper
updated ACM style
finding some room for new contributions

--- 2018-08-24 paper/table_differential.tex
@@
-\begin{table*}[h!]
+\begin{table}[t]
+  \small
   \vspace{-3ex}
-%  \scriptsize
   \centering
@@
   \label{tab:bugs}
-  \begin{tabular}{ccccccccc}
+  \setlength{\tabcolsep}{2pt}
+  \renewcommand{\arraystretch}{0.95}
+  \begin{tabular}{rcccccc}
     \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  &
-    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
+    Issue\# \Comment{ & Date} & Fuzzer & Engine  & Status \Comment{&
+    \multicolumn{1}{c}{Url}}  & Severity & Priority & Suite \\
     \midrule
-%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
-%    \midrule    
-    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
+    1  \Comment{& 4/12} & radamsa & \chakra{}   & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
     & 2 & \textbf{\lo} & \jsc{} \\ 
-    2  & 4/12 & radamsa & \chakra{}   & Rejected  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
+    2  \Comment{& 4/12} & radamsa & \chakra{}   & WontFix  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
     & - & \hi{} & \jsc{} \\
-    3  & 4/14 & radamsa & \jsc{}  & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
+    3  \Comment{& 4/14} & radamsa & \jsc{}  & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
     } & -  & \hi{} & \jsc{}    \\
-    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
+    4  \Comment{& 4/25} & radamsa & \chakra{}  & \textbf{Fixed}     \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
     & 2 & \hi{} & \jerry{}   \\
-    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
+    5  \Comment{& 4/29} & radamsa & \jsc{}  & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
     } & 2  & \hi{}  & \jerry{}\\
 
-    \midrule
-    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
-    & 2 & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{TinyJS}\\    
-                        &                        &        &
-    \jsc{} & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
-    & - &  & \\
-    \midrule
+    6 \Comment{& 4/30}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}}
+    & 2 & \hi{} & TinyJS\\
 
-    7 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
+    7                    \Comment{& 4/30}                       &  radamsa   &
+    \jsc{} & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}}
+    & - & \hi{} & TinyJS \\
+
+    8 \Comment{& 5/02} & radamsa & \jsc{}  & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}}
     & 2 & \textbf{\lo} & \smonkey{} \\
-    8 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
+    9 \Comment{& 5/10} & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}}
     & 3 & \hi{} & \jerry{} \\
-    9 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
+    10 \Comment{& 5/17} & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}}
     & 2 & \hi{} & \veight{}\\
-    10 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
+    11 \Comment{& 5/24} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}}
     & 2 & \hi{} & \jsc{}\\
-    11 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
+    12 \Comment{& 6/26} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}}
     & 2 & \hi{} & \jerry{}\\
-    12 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
+    13 \Comment{& 7/10} & quickfuzz & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}}
     & 2 & \hi{} & \jerry{}\\
-    13 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
+    14 \Comment{& 7/10} & quickfuzz & \chakra{} & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}}
     & 2 & \hi{} & \jerry{}\\
@@
 
-    \midrule
-    \multirow{2}{*}{14} & \multirow{2}{*}{8/21}  &
-    \multirow{2}{*}{radamsa} & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & &
-    \veight{} & \textbf{Fixed} &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & 2 &  & \\
-    \midrule
+    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
+    & - & \hi{} & Test262\\
 
-    15 & 8/23 & quickfuzz & \jsc{} & New  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
+    16 \Comment{& 8/21} & radamsa &
+    \veight{} & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}}
+    & 2 & \hi{} & Test262 \\
+
+    17 \Comment{& 8/23} & quickfuzz & \jsc{} & New  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}}
     & - & \hi{} & Test262\\
-    16 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
+    18 \Comment{& 8/23} & quickfuzz & \veight{} & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}}
     & 2 & \hi{} & Test262\\
 
-    \midrule
-    \multirow{2}{*}{17} & \multirow{2}{*}{8/24}  &
-    \multirow{2}{*}{quickfuzz} & \chakra{} & New &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
-    & - & \multirow{2}{*}{\hi{}} & \multirow{2}{*}{Test262}\\    
-    & & & 
-    \jsc{} & New &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
-    & - &  & \\
+    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & New \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
+    & - & \hi{} & Test262\\
+
+    20 \Comment{& 8/24} &  quickfuzz & 
+    \jsc{} & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}}
+    & - & \hi{} & Test262 \\
+
+    21 \Comment{& 8/24} & quickfuzz & \jsc{}  & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}}
+    & - & \hi{} & Test262\\
    \bottomrule
   \end{tabular}
-\end{table*}
+\end{table}

### 2019-02-13 paper/paper.tex
pass on abstract and intro

@@
 new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, failing under
+Calendar web app, which is built in \js{}, to fail under 
 Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
@@
 scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests constantly fail on the
+significant fraction (5 to 15\%) of the tests fail regularly in the
 most popular engines, reflecting the struggle of developers in keeping
@@
 This paper reports on a study we ran to evaluate the importance of
-diversity in finding bugs on JavaScript engines. We evaluated
+diversity to find bugs in JavaScript engines. We evaluated
 effectiveness of two complementary diversity-aware testing
-techniques. \emph{Test transplantation} leverages diversity of test
-cases to find bugs. It evaluates the effects that running \js{} test
-files from a given engine have in detecting bugs in other engines. The
-intuition is that developers design test cases with different
-objectives in mind. Replaying these tests, written for a given engine,
-in a different engine may reveal unanticipated
-problems. \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
+techniques.
+
+\begin{itemize}
+
+\item \emph{Test transplantation} leverages diversity of test cases to
+  find bugs. It evaluates the effects that running test files from a
+  given engine have in detecting bugs in other engines. The intuition
+  is that developers design test cases with different objectives in
+  mind. As such, replaying these tests in different engines could
+  reveal unanticipated problems.
+
+\item \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
 bugs. More precisely, this technique fuzzes existing test
@@
 intuition is that similar inputs to those already tested may reveal
-problems. Our study measures the ability of these techniques in
-finding bugs and the impact of false positives, which
-can arise in both testing scenarios.
+problems.
+\end{itemize}
+
+Our study measures the ability of these techniques in finding bugs and
+the impact of false positives, which can arise in both testing
+scenarios, on the practicality of the approach.
 
@@
 
-\emph{Related Ideas.}  It is worth noting that Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
+\emph{Related Ideas.}\Mar{Summarize Test Transplantation.} It is worth
+noting that Differential Testing~\cite{Brumley-etal-ss07} (DT) has
+been applied in a variety of contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 not eager JIT compilation). A positive aspect of the approach is that
-it can be fully automated. As the same engine is used, the outcomes of
-the test in both configurations are expected to be identical. The
+it can be fully automated---as only one engine is used, the outcomes
+of the test in both configurations are expected to be identical. The
 Mozilla team uses this approach since 2002; they have been able to
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). \Mar{rewrite. too vague.}\Fix{This paper
-  evaluates the potential benefits of diversity techniques, including
-  DT. It provides data to support or not the decision for automation
-  of these techniques.}
+~\ref{tab:false-positives}). To sum, variations of these ideas have
+been explored before in different contexts.  The goal of the paper is
+to assess the ability of these techniques aforementioned in finding
+bugs on \javascript\ engines.
+
+%% This paper evaluates the benefits of
+%% test case diversity and engine diversity in finding bugs on
+%% \javascript\ engines.
 
@@
 bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
-none in Mozilla's \smonkey{}.
-
-\emph{Key Findings.}~Results indicate that both techniques were
-successful at finding bugs. Overall, test transplantation demanded
-less effort compared to differential testing per bug
-found.\Fix{redundant with the sentences that follow...check} Although
-our experience indicates that more research needs be done to automate
-parts of the inspection process, our results show that exploring
-diversity is a valuable help to find bugs in JavaScript
-engines. \Fix{copied from ICSE meta-review $\rightarrow$}The key
-findings could include, e.g.: - Not only multiple different
-implementations can be leveraged in differential testing, also
-differences in test suites can be important.  - Even for problems with
-fairly clear specifications, as here for a programming language and
-how it is to be executed, there is likely to be (a lot of) variation
-between different implementations.  - Differential testing is feasible
-on real, complex, widely used pieces of software.
+none in Mozilla's \smonkey{}. Overall, results indicate that both
+techniques were successful at finding bugs. Considering cost per bug
+found, test transplantation demanded less effort--from the developers
+who inspected the alarms---compared to differential testing.
+
+\emph{Key Findings.}~1) Not only multiple different implementations
+can be leveraged in differential testing, but differences in test
+suites can also be important. 2) Even for problems with fairly clear
+specifications, as in \javascript{}, there is likely to be (a lot of)
+variation between different implementations. 3) Differential testing
+is feasible on real, complex, widely used pieces of software. 4) More
+research needs be done to automate parts of the inspection process as
+to reduce false alarms and prioritize alarms for inspection.
 
 %% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following:
-\begin{itemize}
-  \item We ran a comprehensive study to analyze the effectiveness of
-    simple diversity-aware techniques to find functional bugs in
-     popular \js\ engines;
-
-  \item We reported a total of \totalBugsReported{} bugs on these
-    engines. Of these, \totalBugsConfirmed{} bug reported were confirmed and
-    \totalBugsFixed{} were fixed;
-
-  %% \item We offered insights on how to reduce cost of analyzing
-  %%   warnings reported by diversity-aware techniques and make the
-  %%   approach more practical.
-
-  \item We made our testing infrastructure, results, and experimental
-    scripts available to the public. (upon request for anonymity.)
-
-\end{itemize}
+\emph{Contributions.}~This paper contributes the following: 1)~A
+comprehensive study to analyze the effectiveness of diversity-aware
+techniques to find functional bugs in popular \javascript\ engines.
+2)~A number of bugs found and fixed. We reported a total of
+\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
+confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
+for diversity-aware testing. We made our testing infrastructure,
+results, and experimental scripts available to the public. (upon
+request for anonymity.)
+
+To sum, the paper provides initial, yet strong evidence that exploring
+diversity is a valuable help to find bugs in JavaScript engines and
+should be encouraged.
 

### 2019-02-14 paper/paper.tex
pass on intro

@@
 \subsection{Seed JS files\label{sec:seeds}}~
-We selected test files from several public projects from GitHub. We
-looked for self-contained tests from JS engine projects, initially
-using the GitHub REST API~\cite{github-rest-api}. We noticed that some
-of the tests we found depend on external libraries, which not all
-engines we use support. We decided to discard those. For example, many
-tests we found required a Node.js runtime~\cite{node} for
-execution. The main source of test cases is the official
-Test262~\cite{tc39-github} conformance test suite for the ECMA262
-specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
-  87\% of all the tests we used.} We also considered test suites of
-three of the four engines mentioned in
-Section~\ref{sec:methodology:engines} and four other engines. Overall,
-we selected a total of \totfiles{} JS
-files. Table~\ref{tab:test-suites} shows the breakdown of tests we
-considered. Column ``original'' shows the number of test cases for
-each test suite. We did not consider tests from the \chakra{}
-repository because they depend on non-portable objects. Notice that
-the number of tests in \veight\ is low. That happens because \veight{}
-uses many tests from Mozilla and \jsc{}; we discarded those to avoid
-repetition and to give credit where it is due. The columns
-``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
-the test transplantation experiment and the differential testing
-experiment, respectively.
-
-Column ``pass-in-par.'' shows the number of test cases that pass in
-their parent engine. We discarded tests that fail in their parent
-engine as we could not reliably indicate the reason for the failure,
-so we assumed the test could be broken. We removed 63 test cases that
-fail for that reason--6 tests from \jsc{} and 57 tests from
-\smonkey. Column ``compile-in-all'' shows the number of test cases
-whose executions do not throw errors because of an undefined variable
-or property. We capture these cases by looking for the presence of
-\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
-\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
-when test execution attempts to access an undefined variable
-(respectively, property of an object). We discarded those tests to
-avoid noise in the experiments as they clearly indicate some missing
-feature as opposed to bugs. For example, some tests use non-portable
-names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
-\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
-spec, not all engines currently support. We used the
-\totalTestFilesForTestTransplantation{} tests included in the circle
-from the table in the evaluation of test transplantation, \ie{}, the
-difference between sets ``compile-in-all'' and Test262. We did not
-consider tests from the conformance suite as they are more likely to
-indicate missing features as opposed to bugs. In addition, engine
-developers have access to these test and are encouraged to run
-them. Column ``no-fail-in-all'' shows the tests for which all engines
-pass. This test set is used in the evaluation of differential
-testing. Note that it is a proper subset of the ``compile-in-all''
-test set. The tests from this group are used as fuzzing seeds. The
-guarantee that they pass in all engines assures that, if discrepancies
-occur, they are related to the changes in the input as opposed to the
-original cause of failure.
-
-It is also worth mentioning that some engines use a custom shell to
-run tests, including a harness with specific assertions.  For that, we
-needed to make minor changes in the testing infrastructure to be able
-to run the tests uniformly across all engines. More precisely, we
-needed to mock non-portable harness functions, which are only
-available to certain engines.
+A good test set is critical for finding bugs with the techniques used
+in this paper. For that reason, we looked for \js\ files from various
+sources: 1) test files from the Test262~\cite{tc39-github} conformance
+suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
+from the test suite of the selected engines (see
+Section~\ref{sec:methodology:engines}); these files are accessible
+from the engine's official repositories, 3) test files mined from
+issue trackers of these engines, and 4) test files from public engines
+accessible from GitHub using the GitHub REST
+API~\cite{github-rest-api}.
+
+Table~\ref{tab:test-suites} shows the breakdown of tests we per
+source. Column ``original'' shows the number of test cases associated
+with each test suite. Column ``pass-in-par.'' shows the number of test
+cases that pass in their parent engine. We discarded tests that fail
+in their parent engine as we could not reliably indicate the reason
+for the failure, so we assumed the test could be broken. We removed 63
+test cases that fail for that reason--6 tests from \jsc{} and 57 tests
+from \smonkey. Column ``compile-in-all'' shows the number of test
+cases whose executions do not throw dynamic type errors in any of the
+engines because of an undefined variable or property. We capture these
+cases by looking for the presence of \CodeIn{ReferenceError} and
+\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
+(respectively, \CodeIn{TypeError}) is raised when test execution
+attempts to access an undefined variable (respectively, property of an
+object). We discarded those tests to avoid noise in the experiments as
+they clearly indicate some missing feature as opposed to bugs. For
+example, some tests use non-portable names (\eg{}, \jsc{}'s
+\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
+or use functions that, albeit part of the spec, not all engines
+currently support. We used the \totalTestFilesForTestTransplantation{}
+tests included in the circle from the table in the evaluation of test
+transplantation, \ie{}, all tests under the ``compile-in-all''
+column\Mar{change name to type-in-all}
+but the Test262 tests. We did not consider tests from the conformance
+suite as they are more likely to indicate missing features as opposed
+to bugs. In addition, engine developers have access to these test and
+are encouraged to run them.  Column ``no-fail-in-all'' shows the tests
+for which all engines pass. This test set is used in the evaluation of
+differential testing. Note that it is a proper subset of the
+``compile-in-all'' test set. The tests from this group are used as
+fuzzing seeds. The guarantee that they pass in all engines assures
+that, if discrepancies occur, they are related to the changes in the
+input as opposed to the original cause of failure.
+
+%% The main source of test
+%% cases is the official Test262~\cite{tc39-github} conformance test
+%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
+%%   This test suite contains 87\% of all the tests we used.} We also
+%% considered test suites of three of the four engines mentioned in
+%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
+%% we selected a total of \totfiles{} JS
+%% files.
+
+\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
+depend on external libraries, which not all selected engines
+support. We decided to discard those. For example, many tests we found
+required a Node.js runtime~\cite{node} for execution. Also, we did not
+consider tests from the \chakra{} repository because they depend on
+non-portable objects. Finally, note that the number of tests in
+\veight\ is low; that happens because \veight{} uses many tests from
+Mozilla and \jsc{}; we discarded those to avoid repetition and to give
+credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
+worth mentioning that some engines use a custom shell to run tests,
+including a harness with specific assertions.  For that, we needed to
+make minor changes in the testing infrastructure to be able to run the
+tests uniformly across all engines. More precisely, we needed to mock
+non-portable harness functions, which are only available in certain
+engines.
+
+\subsubsection{Mining Tests from Issue Trackers}
+
+\Fix{...elaborate...}
+
+\Mar{-------- estou aqui}
+
+%% \Fix{revise this}
+%% For example to run the \jerry{} tests it was necessary 
+%% use the unit-test package to run it, but with our changes we added the assertion
+%% does not have an assertion in the test file
+%% \Fix{add code to explain}
 
@@
     name), and column ``no-fail-all'' shows the number of test cases
-    that pass in all four engines we analyzed.}
+    that pass in all four engines we analyzed.\Mar{explain
+      ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}
   \setlength{\tabcolsep}{2.25pt}      
@@
 \end{table}
-
-For example to run the \jerry{} tests it was necessary 
-use the unit-test package to run it, but with our changes we added the assertion
-does not have an assertion in the test file
-\Fix{add code to explain}
 

### 2019-02-14 paper/paper.tex
pass on related work

@@
 %
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-<concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~Software testing and debugging}
+%% \begin{CCSXML}
+%% <ccs2012>
+%% <concept>
+%% <concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
+%% <concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
+%% <concept_significance>500</concept_significance>
+%% </concept>
+%% </ccs2012>
+%% \end{CCSXML}
+
+%% \ccsdesc[500]{Software and its engineering~Software testing and debugging}
 
@@
 
+\subsection{Testing \js\ Programs}
+Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
+lightweight approach to detect conflicts in \js\ libraries that occur
+when names introduced by different libraries collide. This problem was
+found to be common as the design of \js\ allows for overlaps in
+namespaces. A similar problem has been investigated by Nguyen and
+colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
+colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
+programs, which are popular in the context of Content Management
+Systems as WordPress. The focus of this paper is on testing
+\js\ engines as opposed to \js\ programs. Our goal is therefore
+orthogonal to theirs.
+
 \subsection{Testing \js{} Engines}
@@
 Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
 
@@
 \subsection{Diversity in Testing}
-
-\Fix{Discuss...}~\cite{Chen:2010:ART:1663656.1663914,7515474}
+The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
+assumption behind test set diversity is that faults often spread
+contiguously in the input domain. Consequently, it should be
+beneficial to partition the input domain and explore it more evenly as
+to find bugs faster. Later in the nineties, Chen and
+Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
+the continuity assumption. They found that faults, most open, manifest
+themselves in regular patterns across the input
+domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
+observations led researchers to investigate generalizations of the
+approach to non-numerical data types and strategies to explore the
+input (or output) space to solve different problems in Software
+Engineering (\eg{}, test input generation and test
+selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
+paper explores diversity of sources of test cases and diversity of
+engines to test and find bugs. We remain to investigate the diversity
+of test cases themselves. In principle, that could help reduce the
+number of alarms to inspect, for example.
 

### 2019-02-14 paper/paper.tex
quick pass on discussion

@@
   \lstset{escapeinside={@}{@},
-    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
     basicstyle=\ttfamily\scriptsize, boxpos=c,
@@
   \begin{lstlisting}
-{var a =
-  {valueOf: function(){ return "\x00"}}
-  assert(+a === 0)
-}
+ { var a = {valueOf: function(){ return "\x00"}}
+   assert(+a === 0) }
   \end{lstlisting}
@@
   \begin{lstlisting}
-eval(function b (a) {
-  break;
-});
+ eval(function b (a) { break;});
   \end{lstlisting}
@@
   \begin{lstlisting}
-var obj = {};
-var arr = [];
-try {
-  arr.sort(obj);
-  assert(false);
-} catch (e) {
-  assert(e instanceof TypeError);
-}
+ var obj = {}; var arr = [];
+ try { arr.sort(obj); assert(false);}
+ catch (e) { assert(e instanceof TypeError); }
   \end{lstlisting}
@@
    return typeof String.prototype.repeat === "function"
-  && "foo".repeat(657604378) === "foofoofoo";
-}
+     && "foo".repeat(657604378) === "foofoofoo"; }
   \end{lstlisting}

### 2019-02-14 paper/paper.tex
added mining bug trackers section (wip)

--- 2019-02-14 paper/paper.tex
@@
 \subsubsection{Mining Tests from Issue Trackers}
+
+N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
+Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
+Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
+se um bloco de texto eh um bloco de codigo.
+
+Motivacao:
+Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
+onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
+de similaridade entre elas.
+Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
+Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
+(melhorar definicao do modelo)
+
+Inputs:
+Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
+de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
+Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
+
+Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
 

### 2019-02-14 paper/paper.tex

@@
 
-\emph{Related Ideas.}\Mar{Summarize Test Transplantation.} It is worth
-noting that Differential Testing~\cite{Brumley-etal-ss07} (DT) has
-been applied in a variety of contexts to find
+The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
+assumption behind test set diversity is that faults often spread
+contiguously in the input domain. Consequently, it should be
+beneficial to partition the input domain and explore it more evenly as
+to find bugs faster. Later in the nineties, Chen and
+Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
+the continuity assumption. They found that faults, most open, manifest
+themselves in regular patterns across the input
+domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
+observations led researchers to investigate generalizations of the
+approach to non-numerical data types and strategies to explore the
+input (or output) space to solve different problems in Software
+Engineering (\eg{}, test input generation and test
+selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
+paper explores diversity of sources of test cases and diversity of
+engines to test and find bugs. We remain to investigate the diversity
+of test cases themselves. In principle, that could help reduce the
+number of alarms to inspect, for example.
+
+\emph{Related Ideas.}~The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In constrast
+to prior work on test set diversity, this paper explores diversity of
+sources of test cases and diversity of implementations with the goal
+of finding bugs. Section~\ref{sec:related-work} elaborates related
+work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
+has been applied in a variety of contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 \section{Related Work}
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
+\label{sec:related-work}
+
+\subsection{Diversity in Testing}
+The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
+assumption behind test set diversity is that faults often spread
+contiguously in the input domain. Consequently, it should be
+beneficial to partition the input domain and explore it more evenly as
+to find bugs faster. Later in the nineties, Chen and
+Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
+the continuity assumption. They found that faults, most open, manifest
+themselves in regular patterns across the input
+domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
+observations led researchers to investigate generalizations of the
+approach to non-numerical data types and strategies to explore the
+input (or output) space to solve different problems in Software
+Engineering (\eg{}, test input generation and test
+selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
+paper explores diversity of sources of test cases and diversity of
+engines to test and find bugs. We remain to investigate the diversity
+of test cases themselves. In principle, that could help reduce the
+number of alarms to inspect, for example.
 
@@
 
-\subsection{Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most open, manifest
-themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engines to test and find bugs. We remain to investigate the diversity
-of test cases themselves. In principle, that could help reduce the
-number of alarms to inspect, for example.
+\subsection{Testing \js\ Programs}
+Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
+lightweight approach to detect conflicts in \js\ libraries that occur
+when names introduced by different libraries collide. This problem was
+found to be common as the design of \js\ allows for overlaps in
+namespaces. A similar problem has been investigated by Nguyen and
+colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
+colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
+programs, which are popular in the context of Content Management
+Systems as WordPress. The focus of this paper is on testing
+\js\ engines as opposed to \js\ programs. Our goal is therefore
+orthogonal to theirs.
+
+\subsection{Testing \js{} Engines}
+\label{sec:testing-js-engines}
+The closest work to ours was done by Patra and
+Pradel~\cite{patra2016learning}. Their work proposes a
+language-agnostic fuzzer to find cross-browser HTML+JS
+discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
+Web Assembly engines.} The sensible parts of the infrastructure they
+built are the checks of input validity (as to reduce waste/cost) and
+output correctness (as to reduce false positives). Patra and Pradel
+work is complementary to ours--in principle, we could use their fuzzer
+in our evaluation. The main difference of our work to theirs is in
+goal--we aim at assessing reliability of \js\ engines and find bugs on
+them using simple approaches whereas they aim at proposing a new
+technique.
+
+Fuzzing is an active area of investigation with development of new
+techniques both in academia and industry. Several fuzzing tools exist
+focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
+different fuzzing strategies and tools. Existing techniques prioritize
+automation with a focus on finding crashes; see the sanitizers used in
+libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
+important for these tools that a warning reveals something potentially
+alarming as a crash given that fuzzing is a time-consuming operation,
+\ie{}, the ratio of bugs found per inputs generated is often very low.
+Our approach contrasts with that aim as we focus on finding errors
+manifested on the output, which rarely result in crashes and,
+consequently, would go undetected by current fuzzing approaches. It is
+should be noted, however, that such problems are not unimportant as
+per the severity levels reported in
+Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
 

### 2019-02-14 paper/paper.tex

@@
 Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files mined from
-issue trackers of these engines, and 4) test files from public engines
-accessible from GitHub using the GitHub REST
-API~\cite{github-rest-api}.
+from the engine's official repositories, 3) test files from the suites
+of public engines, and 4) test files mined from issue trackers of
+these engines.
+
+%% accessible from GitHub using the GitHub REST
+%% API~\cite{github-rest-api}.
 
 Table~\ref{tab:test-suites} shows the breakdown of tests we per
-source. Column ``original'' shows the number of test cases associated
-with each test suite. Column ``pass-in-par.'' shows the number of test
-cases that pass in their parent engine. We discarded tests that fail
-in their parent engine as we could not reliably indicate the reason
-for the failure, so we assumed the test could be broken. We removed 63
-test cases that fail for that reason--6 tests from \jsc{} and 57 tests
-from \smonkey. Column ``compile-in-all'' shows the number of test
-cases whose executions do not throw dynamic type errors in any of the
-engines because of an undefined variable or property. We capture these
-cases by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. We used the \totalTestFilesForTestTransplantation{}
-tests included in the circle from the table in the evaluation of test
-transplantation, \ie{}, all tests under the ``compile-in-all''
-column\Mar{change name to type-in-all}
-but the Test262 tests. We did not consider tests from the conformance
-suite as they are more likely to indicate missing features as opposed
-to bugs. In addition, engine developers have access to these test and
-are encouraged to run them.  Column ``no-fail-in-all'' shows the tests
-for which all engines pass. This test set is used in the evaluation of
-differential testing. Note that it is a proper subset of the
-``compile-in-all'' test set. The tests from this group are used as
-fuzzing seeds. The guarantee that they pass in all engines assures
-that, if discrepancies occur, they are related to the changes in the
-input as opposed to the original cause of failure.
+engine. Column ``original'' shows the number of test cases associated
+with each test suite. Column ``pass-in-par.''  shows the number of
+test cases that pass in their parent engine. We discarded tests that
+fail in their parent engine as we could not reliably indicate the
+reason for the failure, so we assumed the test could be broken. We
+removed 63 test cases that fail for that reason--6 tests from \jsc{}
+and 57 tests from \smonkey. Column ``compile-in-all'' shows the number
+of test cases whose executions do not throw dynamic type errors in any
+of the engines because of an undefined variable or property. We
+capture these cases by looking for the presence of
+\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
+\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
+when test execution attempts to access an undefined variable
+(respectively, property of an object). We discarded those tests to
+avoid noise in the experiments as they clearly indicate some missing
+feature as opposed to bugs. For example, some tests use non-portable
+names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
+\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
+spec, not all engines currently support. We used the
+\totalTestFilesForTestTransplantation{} tests included in the circle
+from the table in the evaluation of test transplantation, \ie{}, all
+tests under the ``compile-in-all'' column\Mar{change name to
+  type-in-all} but the Test262 tests. We did not consider tests from
+the conformance suite as they are more likely to indicate missing
+features as opposed to bugs. In addition, engine developers have
+access to these test and are encouraged to run them.  Column
+``no-fail-in-all'' shows the tests for which all engines pass. This
+test set is used in the evaluation of differential testing. Note that
+it is a proper subset of the ``compile-in-all'' test set. The tests
+from this group are used as fuzzing seeds. The guarantee that they
+pass in all engines assures that, if discrepancies occur, they are
+related to the changes in the input as opposed to the original cause
+of failure.
 
@@
 
-N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-se um bloco de texto eh um bloco de codigo.
-
-Motivacao:
-Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-de similaridade entre elas.
-Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-(melhorar definicao do modelo)
-
-Inputs:
-Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-\Fix{...elaborate...}
-
-\Mar{-------- estou aqui}
+\sloppy{}We observed that issue trackers are an important source of
+test data and should not be ignored. Analyzing a sample of issues, we
+observed that developers either 1) add test cases as attachments of
+issues or 2) embed test cases within the textual description of an
+issue. The test cases in attachments are longer compared to the test
+cases embedded in issue descriptions whereas the latter are more
+common. Consequently, we thought we should handle both
+cases. Accessing attachments is simpler compared to embedded
+tests. For attachments, we wrote a crawler to visit the issue trackers
+of all four engines listed in Table~\ref{tab:engines} and were able to
+retrieve a total of \Fix{XX} files
+(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}, and
+\smonkey{}=\Fix{XX}). To mine tests from the textual descriptions, we
+broke the text describing the issue in paragraphs and used a binary
+classifier to label each paragraph as ``code'' or ``not code''. Then,
+based on that information, we merged consecutive paragraphs labeled as
+``code'' and used a \js\ parser to check well-formedness of the
+corresponding code fragment. Using that method we were able to
+retrieve a total of \Fix{XX} files
+(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
+files were included in Table~\ref{tab:test-suites}.
+
+Surprisingly, we did not find a public classifier to solve the problem
+above. For space, we summarize the solution that worked the best in
+the following. We used a standard Embeddings NLP
+technique~\Fix{cite}\Mar{needs to explain what this ``Embeddings''
+  thing does at a high-level. Also, if this stuff exists why we did
+  not find a solution off-the-shelf?} that uses a neural
+net~\Fix{cite} to keep a dictionary of words and the similarity
+distance among them\Mar{but we are talking about sentences. how does
+  it go from words to sentences? Note that many words from the
+  ``code'' vocabulary are from English!}. In more detail, the
+classification model uses a Convolutional Neural Network~\Fix{cite}
+classifier with two layers\Mar{why two? is there a meaning for each
+  layer?} and has been trained and evaluated using a dataset with 25K
+samples of English paragraphs and 25K snippets of \js{}. We ran a
+standard \Fix{X}-repeated 10-fold cross validation to evaluate the
+model and obtained a predicted accuracy of \Fix{98\%}. This classifier
+is publicly available from our website as a separate component.
+
+%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
+%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
+%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
+%% se um bloco de texto eh um bloco de codigo.
+
+%% Motivacao:
+%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
+%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
+%% de similaridade entre elas.
+%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
+%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
+%% (melhorar definicao do modelo)
+
+%% Inputs:
+%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
+%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
+%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
+
+%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
+
+%% \Fix{...elaborate...}
 
@@
 \end{document}
+
+%%  LocalWords:  formedness Embeddings NLP Convolutional dataset

### 2019-02-14 paper/paper.tex
pass on mining tests

@@
 of all four engines listed in Table~\ref{tab:engines} and were able to
-retrieve a total of \Fix{XX} files
-(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}, and
-\smonkey{}=\Fix{XX}). To mine tests from the textual descriptions, we
+retrieve a total of 627 files
+(\jsc{}=147,\veight{}=370 and
+\smonkey{}=110). To mine tests from the textual descriptions, we
 broke the text describing the issue in paragraphs and used a binary

### 2019-02-14 paper/paper.tex
orgnanizing the structure and making another pass on some sections

@@
 
-\keywords{JavaScript, Diversity, Software Testing}
+%% \keywords{JavaScript, Diversity, Software Testing}
 
@@
 
-\section{Objects of Study}
+%% \section{Objects of Study}
+%% This section discusses the objects we used in our study.
+
+\section{Engines Studied}
 \label{sec:methodology}
-
-This section discusses the objects we used in our study.
-
-\subsection{Engines}
 \label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria.
-
-\begin{itemize}
-\item Released latest version after Jan 1, 2018
-\item Contains more than 1K stars on GitHub  
-\item Uses a public issue tracker
-\end{itemize}
-
-We look for highly-maintained (as per the first criterion) and popular
-(as per the second criterion) projects. As we wanted to report bugs,
-we also looked for project with public issue
-trackers. Table~\ref{tab:engines} lists the engines we analyzed in
-this work. It is worth noting that we used GoogleChromeLab's JSVU
+JS engines according to the following criteria: 1) Released latest
+version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
+and 3) Uses a public issue tracker. We looked for highly-maintained
+(as per the first criterion) and popular (as per the second criterion)
+engines. As we wanted to report bugs, we also looked for project with
+public issue trackers. Table~\ref{tab:engines} lists the engines we
+analyzed. It is worth noting that we used GoogleChromeLab's JSVU
 tool~\cite{jsvu} to automatically install and configure versions of
@@
   \centering
-  \caption{\label{tab:engines}Engines analyzed.}
+  \caption{\label{tab:engines}Engines selected.}
   \begin{tabular}{cccrr}
@@
 
-\subsection{Seed JS files\label{sec:seeds}}~
+\section{Seed JS files}
+\label{sec:seeds}
 A good test set is critical for finding bugs with the techniques used
@@
 Table~\ref{tab:test-suites} shows the breakdown of tests we per
-engine. Column ``original'' shows the number of test cases associated
-with each test suite. Column ``pass-in-par.''  shows the number of
+engine. Column ``full'' shows the number of test cases associated
+with each engine. Column ``pass-in-par.''  shows the number of
 test cases that pass in their parent engine. We discarded tests that
@@
 removed 63 test cases that fail for that reason--6 tests from \jsc{}
-and 57 tests from \smonkey. Column ``compile-in-all'' shows the number
+and 57 tests from \smonkey. Column ``type-in-all'' shows the number
 of test cases whose executions do not throw dynamic type errors in any
@@
 from the table in the evaluation of test transplantation, \ie{}, all
-tests under the ``compile-in-all'' column\Mar{change name to
+tests under the ``type-in-all'' column\Mar{change name to
   type-in-all} but the Test262 tests. We did not consider tests from
@@
 test set is used in the evaluation of differential testing. Note that
-it is a proper subset of the ``compile-in-all'' test set. The tests
+it is a proper subset of the ``type-in-all'' test set. The tests
 from this group are used as fuzzing seeds. The guarantee that they
@@
 of failure.
+
+\newcommand\marktopleft[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-a) at (0,2ex) {};%
+}
+\newcommand\markbottomright[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-b) at (0,0) {};%
+    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
+        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
+}
+
+%% \Comment{ Column ``full'' shows the number of the test cases found
+%%     for that engine, column ``compile-in-all'' shows the number of
+%%     test cases for which engines do not throw compile error (\eg{},
+%%     undefined name), and column ``no-fail-all'' shows the number of
+%%     test cases that pass in all four engines we analyzed.\Mar{explain
+%%       ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}}
+
+\begin{table}[t]
+  \small
+  \centering
+  \caption{\label{tab:test-suites}Number of test cases per suite.}
+  \setlength{\tabcolsep}{2pt}
+  \begin{tabular}{ccrrrr}
+    \toprule
+    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
+    \multicolumn{4}{c}{\# JS files} \\
+    \cline{3-6}
+                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
+    \midrule
+    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
+    \midrule
+    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
+    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
+    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
+    \midrule
+    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
+    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
+    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
+    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
+    \midrule
+     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
+   \bottomrule 
+  \end{tabular}
+\end{table}
 
@@
 
-\subsubsection{Mining Tests from Issue Trackers}
+\subsection{Mining Tests from Issue Trackers}
 
@@
 
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,1.5ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=3pt]
-        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
+\section{Cross-Engine Differential Testing}
+\label{sec:design}
+
+Figure~\ref{fig:workflow} illustrates the 
+differential testing infrastructure used in part of this study. It takes on
+input a list of JS files and generates warnings on output. Boxes in
+the figure denote encapsulation, arrowed lines denote data flow, and
+the cycle icons denote repetition--the leftmost icon indicates that
+each file in the input list will be analyzed in separate whereas the
+rightmost icon shows that a single file will be fuzzed multiple times.
+The bug-finding process works as follows. New inputs are obtained for
+a given test input using some off-the-shelf input
+fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+The oracle checks whether or not the output produced for the fuzzed
+file is consistent across all engines. In case the test passes in all
+engines or fails in all engines (\ie{}, the output is consistent), the
+infrastructure ignores the input. Otherwise, it considers the input as
+potentially fault-revealing; hence, interesting for human
+inspection. The infrastructure uses the
+open-source tool eshost-cli~\cite{eshost-cli}, also used at
+Microsoft, for checking output discrepancy.
+
+\begin{figure}[t]
   \centering
-  \caption{\label{tab:test-suites}Number of test cases per
-    suite. Column ``original'' shows the original size of the test
-    suite, column ``compile-in-all'' shows the number of test cases
-    for which engines do not throw compile error (\eg{}, undefined
-    name), and column ``no-fail-all'' shows the number of test cases
-    that pass in all four engines we analyzed.\Mar{explain
-      ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}
-  \setlength{\tabcolsep}{2.25pt}      
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
-    \midrule
-    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
-    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
-    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
-    \midrule
-    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
-    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
-    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
-    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
+  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+\end{figure}
+
+It is worth noting that a number of reasons exist, other than a bug,
+to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
+and ~\ref{tab:false-positives}) and there is no clear automatic
+approach to precisely distinguish false and true positives. As such, a
+human needs to inspect the warning to classify the issue. To
+facilitate inspection, we prioritized warnings and clustered them in
+groups. We describe these strategies in the following.
+
+\subsection{Prioritization}
+
+We classified warnings in two types, reflecting their likelihood of
+manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
+with the cases where the test code executed to completion without
+violating any internal checks, but it violated assertions declared in
+the test itself or its harness. The rationale is that the input is
+more likely to be valid as it it did not raise exceptions during the
+execution of the application code, but, it manifested discrepancy
+through the violation of an assertion declared in the test. In
+contrast, warnings of type ``\lo{}'' are more likely to be associated
+with invalid inputs. They reflect the cases where the anomaly is
+observed during the execution of functions, which are part of the
+application. We found that different engines often check
+pre-conditions of those functions differently. It can happen, for
+example, that one engine enforces a weaker pre-condition on a function
+input compared to another engine and that is acceptable.\Comment{ For
+  instance, it is acceptable to pass values greater than \Fix{x} to
+  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
+cases, the infrastructure would observe a discrepancy that is more
+likely to be associated with an invalid input produced by the fuzzer,
+\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
+bug in the engine code. However, as expected, our heuristic is not
+precise---``\lo'' warnings can reveal
+bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
+this example, the test instantiates an \CodeIn{ArrayBuffer} object and
+stores an 8-bit integer at the 0 position. According to the
+specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
+exception should be thrown if a negative value is passed to the
+function \CodeIn{ToIndex}, indirectly called by the test case. In this
+case, however, the \chakra{} engine did not throw any exception. This
+is a case of undocumented precondition, which is handled as a bug. It
+was fixed by \chakra\ developers and is no longer present in the most
+recent release of \chakra. Despite that case, most bugs we found
+emerged from ``\hi{}'' warnings.
+
+%% \Igor{
+%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
+%%   casos reportados como LO tambem podem ser considerados como um true positive.
+%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
+%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
+%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
+%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
+%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
+%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
+%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
+%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
+%%   lancar Offset is outside the bounds.
+
+%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
+%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
+%%   correto seria usar um levantar um erro
+%% }
+
+\subsection{Clusterization}
+\label{sec:clusterization}
+
+Clusterization helps to group tests that fail for similar reasons. We
+only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
+that arise from the test case, which are typically
+distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
+error messages produced by a ``\lo'' warning. Any warning, including
+this one, that has this same message signature will be included in the
+same ``bucket''. To maximize the hit ratio we remove references to
+code that may appear in the error messages.
+
+\begin{figure}[t!]
+  \centering
+  \begin{lstlisting}
+var buffer = new ArrayBuffer(64);
+var view = new DataView(buffer);
+view.setInt8(0,0x80);
+assert(view.getInt8(-1770523502845470856) === -0x80);
+
+Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
+1. RangeError: Offset is outside the bounds of the DataView
+2. RangeError: byteOffset cannot be negative
+3. RangeError: invalid or out-of-range index
+  \end{lstlisting}
+  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
+    that led to a confirmed bug report in \chakra. The bug is caused
+    by a required precondition check in the implementation of function
+    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
+\end{figure}
+
+\Fix{...reviewer asks for more details...check what we added in the
+  rebuttal for this.}
 
@@
 tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Differential Testing Infrastructure}
-\label{sec:design}
-
-Figure~\ref{fig:workflow} illustrates the 
-differential testing infrastructure used in part of this study. It takes on
-input a list of JS files and generates warnings on output. Boxes in
-the figure denote encapsulation, arrowed lines denote data flow, and
-the cycle icons denote repetition--the leftmost icon indicates that
-each file in the input list will be analyzed in separate whereas the
-rightmost icon shows that a single file will be fuzzed multiple times.
-The bug-finding process works as follows. New inputs are obtained for
-a given test input using some off-the-shelf input
-fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
-The oracle checks whether or not the output produced for the fuzzed
-file is consistent across all engines. In case the test passes in all
-engines or fails in all engines (\ie{}, the output is consistent), the
-infrastructure ignores the input. Otherwise, it considers the input as
-potentially fault-revealing; hence, interesting for human
-inspection. The infrastructure uses the
-open-source tool eshost-cli~\cite{eshost-cli}, also used at
-Microsoft, for checking output discrepancy.
-
-\begin{figure}[h!]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-\end{figure}
-
-It is worth noting that a number of reasons exist, other than a bug,
-to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
-and ~\ref{tab:false-positives}) and there is no clear automatic
-approach to precisely distinguish false and true positives. As such, a
-human needs to inspect the warning to classify the issue. To
-facilitate inspection, we prioritized warnings and clustered them in
-groups. We describe these strategies in the following.
-
-\subsection{Prioritization}
-
-We classified warnings in two types, reflecting their likelihood of
-manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
-with the cases where the test code executed to completion without
-violating any internal checks, but it violated assertions declared in
-the test itself or its harness. The rationale is that the input is
-more likely to be valid as it it did not raise exceptions during the
-execution of the application code, but, it manifested discrepancy
-through the violation of an assertion declared in the test. In
-contrast, warnings of type ``\lo{}'' are more likely to be associated
-with invalid inputs. They reflect the cases where the anomaly is
-observed during the execution of functions, which are part of the
-application. We found that different engines often check
-pre-conditions of those functions differently. It can happen, for
-example, that one engine enforces a weaker pre-condition on a function
-input compared to another engine and that is acceptable.\Comment{ For
-  instance, it is acceptable to pass values greater than \Fix{x} to
-  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
-cases, the infrastructure would observe a discrepancy that is more
-likely to be associated with an invalid input produced by the fuzzer,
-\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
-bug in the engine code. However, as expected, our heuristic is not
-precise---``\lo'' warnings can reveal
-bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
-this example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case. In this
-case, however, the \chakra{} engine did not throw any exception. This
-is a case of undocumented precondition, which is handled as a bug. It
-was fixed by \chakra\ developers and is no longer present in the most
-recent release of \chakra. Despite that case, most bugs we found
-emerged from ``\hi{}'' warnings.
-
-%% \Igor{
-%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
-%%   casos reportados como LO tambem podem ser considerados como um true positive.
-%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
-%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
-%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
-%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
-%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
-%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
-%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
-%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
-%%   lancar Offset is outside the bounds.
-
-%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
-%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
-%%   correto seria usar um levantar um erro
-%% }
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-Clusterization helps to group tests that fail for similar reasons. We
-only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
-that arise from the test case, which are typically
-distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
-error messages produced by a ``\lo'' warning. Any warning, including
-this one, that has this same message signature will be included in the
-same ``bucket''. To maximize the hit ratio we remove references to
-code that may appear in the error messages.
-
-\begin{figure}[!h]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\Fix{reviewer asks for more details...}
 
@@
 \vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows the test input we used to reveal a bug in
-\chakra.
+code snippet below shows a test that reveals a bug in \chakra.
 
@@
 \vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code snippet below shows the test input we used to reveal a bug in
-\veight{}.
-
-\begin{figure}[h!]
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assert, assertEq, var, yield, in, function, eval,
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- eval(function b (a) { break;});
-  \end{lstlisting}
-  \normalsize
-  %% \caption{\label{fig:bug-veight}Fuzzed code mutated by \quickfuzz{}
-  %% and reported in \veight{} engine}
-\end{figure}
-
-This code snippet was obtained by fuzzing a Test262 test with
-\quickfuzz. In its original version, a string (omitted for space),
-passed as argument to the \CodeIn{eval} function, encoded the actual
-test. The fuzzer replaced the string argument with a function whose
-body is a \CodeIn{break} statement outside a valid block
-statement. Section B.3.3.3 from the spec~\cite{spec-b333} documents
-how eval should handle code containing function declarations.
-According to the spec~\cite{break-statement}, the virtual machine
-should throw an early error--in this case, a SyntaxError--if the break
-statement is not nested in an iterable or a switch statement. In this
-case, all engines, but \veight{}, behave as expected.
+code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
+the test input we used to reveal a bug in \veight{}. This code snippet
+was obtained by fuzzing a Test262 test with \quickfuzz. In its
+original version, a string (omitted for space), passed as argument to
+the \CodeIn{eval} function, encoded the actual test. The fuzzer
+replaced the string argument with a function whose body is a
+\CodeIn{break} statement outside a valid block statement. Section
+B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
+handle code containing function declarations.  According to the
+spec~\cite{break-statement}, the virtual machine should throw an early
+error--in this case, a SyntaxError--if the break statement is not
+nested in an iterable or a switch statement. All engines, but
+\veight{}, behave as expected in this case.
 

### 2019-02-15 paper/paper.tex
pass on prio and clustering

@@
 %% WHAT WE DID
-This paper reports on a study we ran to evaluate the importance of
-diversity to find bugs in JavaScript engines. We evaluated
-effectiveness of two complementary diversity-aware testing
-techniques.
-
+This paper reports on a study to evaluate the importance of diversity
+to find bugs in JavaScript engines; it covers two complementary
+diversity-aware testing techniques.
+
+\vspace{-1ex}
 \begin{itemize}
-
-\item \emph{Test transplantation} leverages diversity of test cases to
-  find bugs. It evaluates the effects that running test files from a
-  given engine have in detecting bugs in other engines. The intuition
-  is that developers design test cases with different objectives in
+  \setlength\itemsep{0em}
+\item \emph{Test transplantation} leverages diversity of test
+  cases. It evaluates the effects that running test files from a given
+  engine have in detecting bugs in other engines. The intuition is
+  that developers design test cases with different objectives in
   mind. As such, replaying these tests in different engines could
@@
 
-\item \emph{Cross-engine differential testing} leverages diversity of engine implementations to find
-bugs. More precisely, this technique fuzzes existing test
+\item \emph{Cross-engine differential testing} leverages diversity of
+  engine implementations. More precisely, it fuzzes existing test
   inputs~\cite{fuzz-testing-history} and then compares the output
@@
 \end{itemize}
+\vspace{-1ex}
 
@@
 observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files\footnote{These files are created with
+example, Mozilla runs JS files against different configurations of
+a given build of their \smonkey\ engine (\eg{}, trying to enable or
+not eager JIT compilation\footnote{These files are created with
   the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.} against different configurations of
-a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation). A positive aspect of the approach is that
+  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach is that
 it can be fully automated---as only one engine is used, the outcomes
@@
 techniques were successful at finding bugs. Considering cost per bug
-found, test transplantation demanded less effort--from the developers
-who inspected the alarms---compared to differential testing.
+found, test transplantation demanded less effort from the developers
+who inspected the alarms, compared to differential testing.
 
@@
 
-For different reasons, the specification and implementation of
-JavaScript are incomplete. Certain parts of the specification are
-undefined; it is responsibility of engineers to decide how to
-implement these functionalities. The JavaScript spec uses the label
+The specification of JavaScript is incomplete for different
+reasons. Certain parts of the specification are undefined; it is
+responsibility of engineers to decide how to implement these
+functionalities. The JavaScript spec uses the label
 ``implementation-dependent'' to indicate these cases, where behavior
@@
 spec exists is to enable compiler optimizations. For example, the
-\mcodeid{for-in} loop does not clearly specify the iteration order of
+\js\ \mcodeid{for-in} loop construct does not clearly specify the
+iteration order of
 elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for optimization~\cite{for-in-undefined}.
-As another example, the specification states that if the
-\mcodeid{Number.toPrecision()} function is called with multiple
-arguments then the floating-point approximation is
+engines capitalize on that for loop
+optimizations~\cite{for-in-undefined}.  As another example, the
+specification states that if the \mcodeid{Number.toPrecision()}
+function is called with multiple arguments then the floating-point
+approximation is
 implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Such gap also exists at the
-implementation level. Given the speed the specification changes and
-the complexity of the language some features are not fully implemented
-as can be observed by the Kangax compatibility table~\cite{kangax}.
-It is also worth noting that, as in other languages, some elements in
-JS have non-deterministic behavior (\eg{}, \mcodeid{Math.random} and
-\mcodeid{Date}). A test that make decisions based on these elements
-could, in principle, produce different outcomes on different
-runs. Carefully-written test cases should not manifest this kind of
-flaky behavior~\cite{luo-etal-fse2014,palomba-zaidman-icsme2017}.  As
-mentioned previously, all those aspects make testing \js\ engines more
+like these exist in the specification. Given the speed the
+specification changes and the complexity of the language some features
+are not fully implemented as can be observed by the Kangax
+compatibility table~\cite{kangax}.  It is also worth noting that, as
+in other languages, some elements in JS have non-deterministic
+behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
+that make decisions based on these elements could, in principle,
+produce different outcomes on different runs. Carefully-written test
+cases should not manifest this kind of flaky behavior.  As mentioned
+previously, all those aspects make testing \js\ engines more
 challenging.
@@
 public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used GoogleChromeLab's JSVU
+analyzed. It is worth noting that we used Google Chrome Lab's JSVU
 tool~\cite{jsvu} to automatically install and configure versions of
@@
 
-\section{Seed JS files}
+\section{JS Files Mined}
 \label{sec:seeds}
@@
 
-Table~\ref{tab:test-suites} shows the breakdown of tests we per
-engine. Column ``full'' shows the number of test cases associated
-with each engine. Column ``pass-in-par.''  shows the number of
-test cases that pass in their parent engine. We discarded tests that
-fail in their parent engine as we could not reliably indicate the
-reason for the failure, so we assumed the test could be broken. We
-removed 63 test cases that fail for that reason--6 tests from \jsc{}
-and 57 tests from \smonkey. Column ``type-in-all'' shows the number
-of test cases whose executions do not throw dynamic type errors in any
-of the engines because of an undefined variable or property. We
-capture these cases by looking for the presence of
-\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
-\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
-when test execution attempts to access an undefined variable
-(respectively, property of an object). We discarded those tests to
-avoid noise in the experiments as they clearly indicate some missing
-feature as opposed to bugs. For example, some tests use non-portable
-names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
-\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
-spec, not all engines currently support. We used the
-\totalTestFilesForTestTransplantation{} tests included in the circle
-from the table in the evaluation of test transplantation, \ie{}, all
-tests under the ``type-in-all'' column\Mar{change name to
-  type-in-all} but the Test262 tests. We did not consider tests from
-the conformance suite as they are more likely to indicate missing
-features as opposed to bugs. In addition, engine developers have
-access to these test and are encouraged to run them.  Column
-``no-fail-in-all'' shows the tests for which all engines pass. This
-test set is used in the evaluation of differential testing. Note that
-it is a proper subset of the ``type-in-all'' test set. The tests
-from this group are used as fuzzing seeds. The guarantee that they
-pass in all engines assures that, if discrepancies occur, they are
-related to the changes in the input as opposed to the original cause
-of failure.
+Table~\ref{tab:test-suites} shows the breakdown of tests per
+engine. Column ``full'' shows the number of test cases associated with
+each engine. Column ``pass-in-par.''  shows the number of test cases
+that pass in their parent engine. We discarded tests that fail in
+their parent engine as we could not reliably indicate the reason for
+the failure, so we assumed the test could be broken. We removed 63
+test cases that fail for that reason--6 tests from \jsc{} and 57 tests
+from \smonkey. Column ``type-in-all'' shows the number of test cases
+whose executions do not throw dynamic type errors in any of the
+engines because of an undefined variable or property. These cases were
+captured by looking for the presence of \CodeIn{ReferenceError} and
+\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
+(respectively, \CodeIn{TypeError}) is raised when test execution
+attempts to access an undefined variable (respectively, property of an
+object). We discarded those tests to avoid noise in the experiments as
+they clearly indicate some missing feature as opposed to bugs. For
+example, some tests use non-portable names (\eg{}, \jsc{}'s
+\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
+or use functions that, albeit part of the spec, not all engines
+currently support. For the evaluation of test transplantation, we used
+the \totalTestFilesForTestTransplantation{} tests included in the
+dashed rectangle under column ``type-in-all'', \ie{}, all tests under
+that column but the Test262 tests. We did not consider tests from the
+conformance suite as they are more likely to indicate missing features
+as opposed to bugs. In addition, engine developers have access to
+these test and are encouraged to run them. Finally, column
+``no-fail-in-all'' shows the tests for which all engines pass. Note
+that the set of tests in this column is a subset of the
+``type-in-all'' test set. This test set is used in the evaluation of
+differential testing as fuzzing seeds. The guarantee that they pass in
+all engines assures that, if discrepancies occur, they are related to
+the changes in the input as opposed to the original cause of failure.
 
@@
     \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rounded rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
+        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
 }
-
-%% \Comment{ Column ``full'' shows the number of the test cases found
-%%     for that engine, column ``compile-in-all'' shows the number of
-%%     test cases for which engines do not throw compile error (\eg{},
-%%     undefined name), and column ``no-fail-all'' shows the number of
-%%     test cases that pass in all four engines we analyzed.\Mar{explain
-%%       ``pass-in-par.''}\Mar{why SpiderMonkey 1,977->2,116?}}}
 
@@
   \centering
-  \caption{\label{tab:test-suites}Number of test cases per suite.}
-  \setlength{\tabcolsep}{2pt}
+  \caption{\label{tab:test-suites}Number of test files. Dashed
+    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
+    shows the tests used for test transplantation (resp., cross-engine
+    differential testing).}  \setlength{\tabcolsep}{2pt}
   \begin{tabular}{ccrrrr}
@@
     \midrule
-    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
+    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & \marktopleft{c2}17,639 \\
     \midrule
@@
     JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
-    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
+    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\markbottomright{c2}\\
     \midrule
@@
 common. Consequently, we thought we should handle both
-cases. Accessing attachments is simpler compared to embedded
-tests. For attachments, we wrote a crawler to visit the issue trackers
-of all four engines listed in Table~\ref{tab:engines} and were able to
-retrieve a total of 627 files
-(\jsc{}=147,\veight{}=370 and
-\smonkey{}=110). To mine tests from the textual descriptions, we
-broke the text describing the issue in paragraphs and used a binary
-classifier to label each paragraph as ``code'' or ``not code''. Then,
-based on that information, we merged consecutive paragraphs labeled as
-``code'' and used a \js\ parser to check well-formedness of the
-corresponding code fragment. Using that method we were able to
-retrieve a total of \Fix{XX} files
-(\jsc{}=\Fix{XX},\veight{}=\Fix{XX},\chakra{}=\Fix{XX}). All those
-files were included in Table~\ref{tab:test-suites}.
-
-Surprisingly, we did not find a public classifier to solve the problem
-above. For space, we summarize the solution that worked the best in
-the following. We used a standard Embeddings NLP
-technique~\Fix{cite}\Mar{needs to explain what this ``Embeddings''
-  thing does at a high-level. Also, if this stuff exists why we did
-  not find a solution off-the-shelf?} that uses a neural
-net~\Fix{cite} to keep a dictionary of words and the similarity
-distance among them\Mar{but we are talking about sentences. how does
-  it go from words to sentences? Note that many words from the
-  ``code'' vocabulary are from English!}. In more detail, the
-classification model uses a Convolutional Neural Network~\Fix{cite}
-classifier with two layers\Mar{why two? is there a meaning for each
-  layer?} and has been trained and evaluated using a dataset with 25K
-samples of English paragraphs and 25K snippets of \js{}. We ran a
-standard \Fix{X}-repeated 10-fold cross validation to evaluate the
-model and obtained a predicted accuracy of \Fix{98\%}. This classifier
-is publicly available from our website as a separate component.
+cases.
+
+Accessing attachments was engineering-wise simpler compared to
+embedded tests. For that, we wrote a crawler to visit the issue
+trackers of all four engines listed in Table~\ref{tab:engines} and we
+were able to retrieve a total of 627 files (\jsc{}=147, \veight{}=370,
+and \smonkey{}=110).
+
+To mine tests from the textual descriptions we proceeded as
+follows. First, we broke the text describing the issue in paragraphs
+and used a binary classifier to label each paragraph as ``code'' or
+``not code''. Then, based on that information, we merged consecutive
+paragraphs labeled as ``code'' and used a \js\ parser to check
+well-formedness of the corresponding code fragment. Using that method
+we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
+\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
+included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
+find a public classifier to solve the problem above. For space, we
+summarize the solution that worked the best in the following. The
+classifier that performed best for this case uses
+a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
+  what this ``Embeddings'' thing does at a high-level. Also, if this
+  stuff exists why we did not find a solution off-the-shelf?} that
+builds on a neural net~\Fix{cite} to keep a dictionary of words and the
+similarity distance among them\Mar{but we are talking about
+  sentences. how does it go from words to sentences? Note that many
+  words from the ``code'' vocabulary are from English!}. In more
+detail, the classification model uses a Convolutional Neural
+Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
+  meaning for each layer?} and has been trained and evaluated using a
+dataset with 25K samples of English paragraphs and 25K snippets of
+\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
+evaluate the model and obtained a predicted accuracy of
+\Fix{98\%}. This classifier is publicly available from our website as
+a separate component.
 
@@
 a given test input using some off-the-shelf input
-fuzzer~\cite{fuzz-testing-history}; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+fuzzer; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
 The oracle checks whether or not the output produced for the fuzzed
@@
 open-source tool eshost-cli~\cite{eshost-cli}, also used at
-Microsoft, for checking output discrepancy.
+Microsoft, for checking output discrepancy.\Mar{any difference in
+  output is considered for reporting? are there any
+  filtering?}
 
@@
 approach to precisely distinguish false and true positives. As such, a
-human needs to inspect the warning to classify the issue. To
-facilitate inspection, we prioritized warnings and clustered them in
-groups. We describe these strategies in the following.
+human needs to inspect the warning to classify the issue. As mentioned
+earlier, this justifies why differential testing is challenging to
+automate at the functional level. To facilitate inspection, we
+prioritized warnings and clustered them in groups. We describe these
+strategies in the following.
 
@@
 
-We classified warnings in two types, reflecting their likelihood of
-manifesting a real bug. Warnings of the kind ``\hi{}'' are associated
-with the cases where the test code executed to completion without
-violating any internal checks, but it violated assertions declared in
-the test itself or its harness. The rationale is that the input is
-more likely to be valid as it it did not raise exceptions during the
-execution of the application code, but, it manifested discrepancy
-through the violation of an assertion declared in the test. In
-contrast, warnings of type ``\lo{}'' are more likely to be associated
-with invalid inputs. They reflect the cases where the anomaly is
-observed during the execution of functions, which are part of the
-application. We found that different engines often check
-pre-conditions of those functions differently. It can happen, for
-example, that one engine enforces a weaker pre-condition on a function
-input compared to another engine and that is acceptable.\Comment{ For
-  instance, it is acceptable to pass values greater than \Fix{x} to
-  function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those
-cases, the infrastructure would observe a discrepancy that is more
-likely to be associated with an invalid input produced by the fuzzer,
-\ie{}, it is likely to be a ``bug'' in the test code as opposed to a
-bug in the engine code. However, as expected, our heuristic is not
-precise---``\lo'' warnings can reveal
-bugs. Figure~\ref{fig:lo-truepositive} shows one of these cases. In
-this example, the test instantiates an \CodeIn{ArrayBuffer} object and
+We prioritized warnings based on their types, reflecting likelihood of
+manifesting a real bug. We defined two types---``\hi{}'' and
+``\lo{}''.
+
+Warnings of the kind ``\hi{}'' are associated with the cases where the
+test code executes without violating any internal checks, but it
+violates an assertion declared in the test itself or its harness. The
+rationale is that the test data is more likely to be valid in this
+case as execution does not raise exceptions in application
+code. Warnings of kind ``lo'' cover the remaining cases. These
+warnings are more likely to be associated with invalid inputs. They
+reflect the cases where the anomaly is observed during the execution
+of application functions as opposed to assertions. We observed that
+different engines often check pre-conditions of functions
+differently. It can happen, for example, that one engine enforces a
+weaker pre-condition, compared to another engine, on the inputs of a
+function and that is acceptable.\Comment{ For instance, it is
+  acceptable to pass values greater than \Fix{x} to function
+  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
+the infrastructure would report a warning that is more likely to be
+associated with an invalid input produced by the fuzzer, \ie{}, it is
+likely to be a ``bug'' in the test code as opposed to a bug in the
+engine. Recall that, for differential testing, we only use seed tests
+that pass in all engines.
+
+Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
+Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
+example, the test instantiates an \CodeIn{ArrayBuffer} object and
 stores an 8-bit integer at the 0 position. According to the
@@
 exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case. In this
-case, however, the \chakra{} engine did not throw any exception. This
-is a case of undocumented precondition, which is handled as a bug. It
-was fixed by \chakra\ developers and is no longer present in the most
-recent release of \chakra. Despite that case, most bugs we found
-emerged from ``\hi{}'' warnings.
-
-%% \Igor{
-%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
-%%   casos reportados como LO tambem podem ser considerados como um true positive.
-%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
-%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
-%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
-%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
-%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
-%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
-%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
-%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
-%%   lancar Offset is outside the bounds.
-
-%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
-%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
-%%   correto seria usar um levantar um erro
-%% }
+function \CodeIn{ToIndex}, indirectly called by the test case from the
+function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
+engine did not throw any exception, as can be confirmed from the
+report that our infrastructure produces starting with text ``Engine
+Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
+a case of undocumented precondition. It was fixed by
+\chakra\ developers and is no longer present in the most recent
+release of \chakra.
 
@@
 
-Clusterization helps to group tests that fail for similar reasons. We
-only clustered ``\lo'' warnings as ``\hi'' warnings produce messages
-that arise from the test case, which are typically
-distinct. Figure~\ref{fig:lo-truepositive} shows, at the bottom, the
-error messages produced by a ``\lo'' warning. Any warning, including
-this one, that has this same message signature will be included in the
-same ``bucket''. To maximize the hit ratio we remove references to
-code that may appear in the error messages.
+%% Prioritization helps to steer our focus to the warnings more likely to
+%% reveal bugs, but there could be several tests producing similar
+%% warnings.
+
+Clusterization is complementary to prioritization; it helps to group
+similar warnings reported by our infrastructure. We only clustered
+``\lo'' warnings as ``\hi'' warnings produce messages that arise from
+the test case, which are typically distinct.
+
+Figure~\ref{fig:lo-truepositive} shows, at the bottom, the identifier
+of an engine, the exception it raises, and the message it produces on
+a ``\lo'' warning.  This sequence of engine id, exception, and error
+message triples defines a warning signature that we use for
+clustering. It is worth mentioning that we filter references to code
+in messages as to increase ability to aggregate warnings from
+different test sources. Any warnings, including this one, that has
+this same signature will be included in the same
+``bucket''. Considering the example from
+Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
+be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
+  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
+  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
+  bounds of the DataView'')].
 
@@
 
-\Fix{...reviewer asks for more details...check what we added in the
-  rebuttal for this.}
-
 \subsection{Fuzzers}
 \label{sec:objects:fuzzers}
-
-%% In the following, we describe the list of fuzzers we analyzed. We
-%% initially considered generational grammar-based fuzzers and mutational
-%% fuzzers.
 

### 2019-02-15 paper/ICSE2019-rebuttal.txt
adding final ICSE reviews and rebuttals

We sincerely thank the reviewers for the constructive comments.

R1Q1
Because of the nature of the experiment (goal is to demonstrate bug-finding ability), the design cannot provide such guarantees. However, we do believe that the absolute size of the dataset, the duration of the experiment, and the number of confirmed/fixed bugs provide (informal) support for our conclusions.

R1Q2 (is there any characteristic of the JavaScript engine from MS/Apple that makes them susceptible to bugs?)
Although this is a very interesting question, it is not one that we planned to answer. To answer this question, we would need to obtain a good understanding of the development process of each engine. Internally, we attempted to make educated guesses. Potential factors include pace of development, how strict developers are to the specs (we saw a lot of debate on MS forums), age (MS engine is the newest of the engines), and the fact that Google/Mozilla are known to put a lot of effort on testing and quickly addressing reported issues. In summary, making such an assessment is challenging and not in the scope of this paper.

R2Q1
We believe that our conclusions and infrastructure can be reused in the context of WebAssembly (https://webassembly.org/), which is already supported by major browsers since early 2018 and has been attracting attention from the PL community (e.g., https://dl.acm.org/citation.cfm?id=3062363).

R3Q1
The identity of a cluster is formed by the error messages emitted by each engine when a discrepancy is reported (i.e., inputs with non-consensual outputs). The message of a given engine consists of the error/exception type and corresponding console message. Considering the example from Figure 2, the signature for that cluster is [(JavaScriptCore, “RangeError”, “byteOffset cannot be negative”), (SpiderMonkey, “RangeError”, “invalid or out-of-range index”), (V8, “RangeError”, Offset is outside the bounds of the DataView”)]. As explained in Section IV.A, note that clustering is only used for “lo” warnings and, as per Table X,  most bugs we found originated from “hi” warnings. (We will clarify that in IV.B)

R3Q2
At a high level, the main lesson is that implementing correct JavaScript engines is challenging (lots of gaps in the specification) and even engines known to be very reliable (e.g., Google’ s V8) contain bugs. Given the prolific use of those engines, improving bug-finding techniques/tools in this scenario (with regular updates in specs) is important and we have observed that the techniques used in this paper are promising and should further evolve. Analyzing false alarms and duplicate bugs from “hi” warnings are particularly time-consuming tasks that are target for optimization. Predicting those cases is an interesting avenue for investigation. As for novelty(ies), the paper does not propose a new technique. This is an empirical paper whose goal is to understand/document the (in)ability of known techniques to find bugs in one important domain.

----------------------- REVIEW 1 ---------------------
PAPER: 512
TITLE: Leveraging Diversity to Find Bugs in JavaScript Engines
AUTHORS: Igor Lima and Marcelo d'Amorim

Poster Paper: no

----------- Summary -----------
The primary contribution of the work is to evaluate the importance of
test-transplantation (running tests of one computing env in another)
and cross-engine testing (running mutated tests on multiple
environment and verifying consistency) in finding bugs. The test
subject is Javascript programming language and the engines considered
are from Apple, Google, MS and Mozilla. The authors conclude that
Apple and MS engines are impacted by most of the bugs and test
transplantation is more effective that cross-engine testing, in the
context.

----------- Detailed Evaluation -----------
The paper is well-written. It is important to focus on such evaluation
related problems.  However, it is not clear to the reader whether the
work warrants a publication in conference proceedings.  Two important
aspects need to be addressed or clarified further, if possible.

- What are the engineering and/or scientific challenges in conducting
  the experiments? How does the design of experiments ensure that the
  conclusions are based on representative and sufficient data points?

- The question being asked as part of the experiments is to evaluate
  whether or not differential testing is useful. The experiments seem
  to validate this claim through observation. Are there any
  conclusions that can be arrived based on the observations--for
  instance, is there any characteristic of the JavaScript engine from
  MS and Apple that makes them susceptible to bugs? Is it the design
  of these engines or the pace in which these engines are being
  developed without official conformance? Or is it the case, the test
  cases fail because their interpretation in different engines are not
  well-defined (or sound)?

----------- Strengths and Weaknesses -----------
Please refer to detailed review.

----------- Author Question 1 -----------
How does the design of experiments ensure that the conclusions are based on representative and sufficient data points?

----------- Author Question 2 -----------
What sound conclusions regarding the test-subjects can be arrived based on the observations from the experiments?

R1Q1
We believe that the absolute size of the dataset, the duration of the experiment, and the bugs we found provide support for our conclusions, but only informal support. It is worth noting that the techniques evaluated in the paper are complementary. We did not intend to indicate superiority of one over the other.

A infraestrutura da nossa ferramenta é muito simples (see Figure 1), tivemos que agrupar reports similares para conseguir ao máximo reduzir todo o esforço da inspeção manual. Para a realização da inspeção manual, é necessário um conhecimento bastante aprofundado na linguagem, pois algumas features são muito específicas ao comportamento do engine. Nossos experimentos foram conduzidos a partir dos resultados obtidos, tivemos que restringir a análise do experimento cross-engine differential testing, tivemos
que conduzir a inspeção em uma pequena porção da população obtida, estes dados podem não generalizar todo o dataset obtido.

R1Q2
In our results, we observed that the specs of engines from Microsoft and Apple are very similar, many of bugs that we found it was crashed in both. In other hand, Google and Mozilla engines are very robust to crashing them using simple inputs. Our experiments explores the conformance of EcmaScript, some bugs that we reported in ChakraCore bug tracker rendered discussions about the conformance, these specs descriptions could affect a misunderstanding in development.

----------------------- REVIEW 2 ---------------------
PAPER: 512
TITLE: Leveraging Diversity to Find Bugs in JavaScript Engines
AUTHORS: Igor Lima and Marcelo d'Amorim

Poster Paper: no

----------- Summary -----------
This article presents a study showing that test transplantation and cross-engine differential testing,  two diversity-aware techniques, work well for finding real bugs on real projects.  The test transplantation technique runs test suites of a given engine in
another engine. The  cross-engine differential testing technique fuzzes existing inputs and then compares the output produced by different engines with a differential oracle.
The study focuses on the different JavaScript interpreters present in browsers. 
Overall, authors reported 48 bugs in this study. Of which, 30 were confirmed by developers and 15 were fixed. Although more work is necessary to reduce cost of manual analysis, authors discuss that both techniques used are effective at finding bugs in JS engines.

----------- Detailed Evaluation -----------
I really enjoyed reading this article. It is well written, easy to read and well structured. Introduction and background sections are clear, related work is exhaustive. 
This article presents a very nice experiment. The work for this study is very significant and the construction of the dataset is a genuine contribution to the community. 
On the other hand, the scientific contribution as such is not easy to highlight. Browser javascript interpreters are special pieces of software for which it is indeed possible to perform differential testing. It is not clear in the discussion what could be generalized and in which context. 
The benefits of test transplantation and cross-engine differential testing have been demonstrated before. It is therefore not the core of the contribution.

As a result the core contributions which are clearly discussed in the introduction are 
- the empirical study. 
- The technical results of the study that find real bugs on real JavaScript engine.
- the testing infrastructure, results, and experimental scripts available to the public. On this last point, it would be great to use (https://anonymous.4open.science/) for sharing this infrastructure with the reviewers.

I would like to argue in for accepting this paper for the following reasons. The benefits of a rigorous analysis on a real, complex object of study is helpful for the community. Sharing this dataset to the community could lead to new results in particular to decrease the cost of manual inspections of  failures/warnings. The article does not overclaim. In particular in the related work, they often discuss that in contrast to other approaches they did not propose new techniques; their contribution is empirical.

----------- Strengths and Weaknesses -----------
Strengths: 
+ well-written, well-structured easy to read
+ excellent object of study (we could consider that these JavaScript engines represent state of the practice of Software Engineering in Industry. 
+ good testing infrastructure
+ Sharable benchmark for the community

Limitation
- Novelty is not clear: mainly a new empirical study that assess the benefits of existing testing techniques

----------- Author Question 1 -----------

----------------------- REVIEW 3 ---------------------
PAPER: 512
TITLE: Leveraging Diversity to Find Bugs in JavaScript Engines
AUTHORS: Igor Lima and Marcelo d'Amorim

Poster Paper: yes

----------- Summary -----------
Reports on a detailed case study of using test cases from diverse sources to test Javascript engines. The main sources are test cases from the Javascript specification as well as a number of Javascript engines and github Javascript projects. This initial set of seed test cases are also mutated using black-box fuzzers to find additional problems. After extensive, manual classification of warnings/problems identified a number of actual bugs was found, confirmed and sometimes even fixed by developers of the engines.

----------- Detailed Evaluation -----------
# Overview of evaluation and Justification for recommendation
This is an extensive empirical study on using test cases from diverse sources (either from other systems trying to conform to the same specification, or by mutation of an initial set of such test cases) to test of systems with similar goals and specification. The effort involved and that real bugs have been found, confirmed, and (partly) even fixed is impressive.

However, it is less clear what more general knowledge or lessons learnt we can take from the study. For a case study of this type the lessons learnt have to be discussed in depth. Here they are not.

On balance, I think this is an ok empirical study but the limitations in generalizability indicates for me a weak accept and I could be convinced to also reject. There is no major problems with the work but there is also nothing that really stands out as critically important from a scientific perspective.

## PROS of paper
+ 1. Included JS seed files also from other projects and engines not investigated
  - This makes sense from a diversity perspective.

- 2. Finding real bugs that have been confirmed/fixed by developers
  - This shows real-world benefit. Of course, it should be properly discussed in relation to the effort/time needed. You don't discuss this enough.

## CONS of paper
- 1. Novelty unclear
  - The paper does not fully spell out what is the added knowledge from this empirical study. Since the paper does not innovate in the particular technologies used it should make very clear what are the added "lessons learned" from the application of existing and well-known technologies for this particular case(s). Currently the reader is left wondering what more we have learnt than that these technologies can be effective (which we already know from the related literature).

- 2. Lack of details on how warnings are clustered. 
  - Is it based on the values, exception messages or something else? Details missing.

- 3. Claim that test transplantation found more tests is dubious
  - Since the basis for the differential testing was test cases that didn't already fail in any of the engines it is hard to claim the two methods can be compared as being used "from scratch"; you used them in slightly different settings. IMHO it would be wrong if readers take away from your study that "test transplantation" is to be preferred. You used them "in sequence", not "in parallel".

- 4. Too little discussion of lessons learnt

# ICSE criteria

## Soundness
The papers contributions are somewhat unclear since it is more of an experience report from applying existing techniques. Given that caveat I find the research methods appropriate and their application rigorous.

## Significance
It is not clear what is the significance of the work. It is novel in the sense that these particular testing techniques have not been previously used in this way on these specific software systems but it is not clear what we actually learn from the authors' experience.

## Verifiability
Yes, there is enough information here to independently verify and even replicate.

## Presentation
The paper is well-written and presented.

# Smaller problems with the paper that would need to be clarified/fixed

- 1. Your paper doesn't cite key results on the value of diversity in software testing such as for example:
  - Chen, Tsong Yueh, et al. "Adaptive random testing: The art of test case diversity." Journal of Systems and Software 83.1 (2010): 60-66.
  - Feldt, Robert, Simon Poulding et al "Test set diameter: Quantifying the diversity of sets of test cases." Software Testing, Verification and Validation (ICST), 2016 IEEE International Conference on. IEEE, 2016.

----------- Strengths and Weaknesses -----------
## PROS of paper
+ 1. Included JS seed files also from other projects and engines not investigated
+ 2. Finding real bugs that have been confirmed/fixed by developers

## CONS of paper
- 1. Novelty unclear
- 2. Lack of details on how warnings are clustered. 
- 3. Claim that test transplantation found more tests is dubious
- 4. Too little discussion of lessons learnt

----------- Author Question 1 -----------
How do you cluster warnings so that they are in a cluster with test cases that fail for "a similar reason" and what does the "message signature" used for this include?

----------- Author Question 2 -----------
What are the main lessons learnt and novelty(ies) of the work compared to what we already know about test transplantation and differential testing?

------------------------------------------------------

### 2019-02-15 paper/paper.tex
reorganizing intro

@@
 
-\vspace{-1ex}
-\begin{itemize}
-  \setlength\itemsep{0em}
+%\vspace{-1ex}
+%noitemsep,
+\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
 \item \emph{Test transplantation} leverages diversity of test
@@
 \end{itemize}
-\vspace{-1ex}
 
@@
 
-\emph{Results.}~We considered engines from four major players--Apple,
-Google, Microsoft, and Mozilla. Our results indicate that both
+\emph{Results.}~We considered the following engines--Apple, Google,
+Microsoft, and Mozilla. Figure~\ref{fig:summary} shows the breakdown
+of bug reports per engine (\ref{fig:stacked-engine}) and per technique
+(\ref{fig:stacked-technique}). Additionally, each stacked bar breaks
+down the bugs per status (\eg{}, ``1-New''). The prefix number
+indicates the ordering that status labels are assigned. Note that
+several of these reports have the label ``3-Fixed'', indicating that
+bug fixes have been incorporated into the code already. Note that most
+of these bugs affected two engines--Microsoft's \chakra{} and Apple's
+\jsc{}.  We reported \noBugsBugsReportedGoogle{} bugs in Google
+\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
+Mozilla's \smonkey{}.  Furthermore, our results show that both
 techniques revealed several bugs, most of which confirmed by
@@
 \noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed). Furthermore, results
-indicate that most of these bugs affected two engines--Apple's \jsc{}
-and Microsoft's \chakra{}.  We reported \noBugsBugsReportedGoogle{}
-bugs in Google \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and
-none in Mozilla's \smonkey{}. Overall, results indicate that both
-techniques were successful at finding bugs. Considering cost per bug
-found, test transplantation demanded less effort from the developers
-who inspected the alarms, compared to differential testing.
+\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
+indicate that both techniques were successful at finding bugs. The
+number of bug reports were similar, if we consider only those
+confirmed or fixed. Considering cost per bug found, we found that test
+transplantation, compared to differential testing, demanded less
+effort from the developers who inspected the alarms. Most of the bugs
+we found are of moderate severity.
+
+%% All in all, these simple techniques
+%% seem promising to improve reliability of engines that continuously
+%% evolve with their specifications.
 
@@
 variation between different implementations. 3) Differential testing
-is feasible on real, complex, widely used pieces of software. 4) More
-research needs be done to automate parts of the inspection process as
-to reduce false alarms and prioritize alarms for inspection.
+is feasible on real, complex, widely used pieces of software.
 
@@
 
-To sum, the paper provides initial, yet strong evidence that exploring
-diversity is a valuable help to find bugs in JavaScript engines and
-should be encouraged.
+\vspace{1ex} To sum, although more research needs be done to automate
+parts of the inspection process (\eg{}, reduction of false alarms),
+the paper provides initial, yet strong evidence that exploring
+diversity should be encouraged to find functional bugs in JavaScript
+engines.
+
+\begin{figure}[t]
+%  \vspace{-2ex}  
+  \centering
+  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
+    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \vspace{-5ex}
+  }\\
+  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
+    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
+    \vspace{-5ex}        
+  }
+  \caption{\label{fig:summary}Summary of bug reports.}
+  \vspace{-3ex}
+\end{figure}
 
@@
 these simple diversity-aware techniques to find bugs.
-
-\vspace{1ex}
-\noindent\textbf{Summary of Bugs.}~Figure~\ref{fig:summary} shows the
-breakdown of bug reports found per engine (\ref{fig:stacked-engine})
-and technique (\ref{fig:stacked-technique}). Each stacked bar breaks
-down the bugs per status (\eg{}, ``1-New'', ``2-Confirmed'',
-etc.). The prefix number indicates the ordering that status labels are
-assigned. Note that several of these reports have the label
-``3-Fixed'', indicating that bug fixes have been incorporated into the
-code already.\Comment{ Depending on the issue date, the fix may be in
-  the latest release of the corresponding engines.} Overall, ignoring
-bug reports with the ``1-New'' status, we reported a total of
-\totalBugsConfirmed{} bugs. We found that the vast majority of bug
-reports targeted the engines from Microsoft and Apple. Considering the
-techniques, the number of bug reports were similar, if we consider
-only those confirmed or fixed. Most of these bugs are of moderate
-severity. All in all, these simple techniques seem promising to
-improve reliability of engines that continuously evolve with their
-specifications.
-
-\begin{figure}[h!]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-%  \vspace{-3ex}
-\end{figure}
 

### 2019-02-15 paper/paper.tex
6.1

@@
 
-The goal of our study is to assess reliability of \js\ engines by
-leveraging on diversity of test data and engine implementations. Based
-on that, we pose three questions:
+The goal of this paper is to assess ability of techniques that
+leverage data and implementation diversity on to find functional bugs
+in \javascript\ engines. Based on that, we pose three questions:
 \begin{description}[leftmargin=.5in]
@@
 from different engines is that developers consider different goals
-when writing test cases--suites written for a given engine should
-cover scenarios not covered by a different engine. The third question
+when writing tests---suites written for a given engine may cover
+scenarios not covered by a different engine. The third question
 evaluates the effectiveness of cross-engine differential testing to
 find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale is that bugs may be detected using inputs which are similar
-to those already tested. Overall, our goal is to evaluate ability of
-these simple diversity-aware techniques to find bugs.
+rationale for this question is that fuzzing inputs may explore
+scenarios not well tested by at least one of the engines.
 
@@
 
-\begin{wraptable}[11]{r}{0.22\textwidth}
-  \vspace{-4ex}      
+The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to check conformance of
+engines to the \js\ current standard. As it is acceptable to release
+engines fulfilling the specification only partially~\cite{kangax}, it
+is expected that engines do not fully pass this check. However, we
+expect that results provide indication of engine's maturity. In the
+limit, it is not desirable to flood bug reports on engines at early
+stages of development. We ran the suite once a day for seven
+consecutive days from the period of a week and averaged the passing ratios.
+
+\begin{wraptable}[10]{r}{0.22\textwidth}
+%  \vspace{-2ex}      
   \centering
@@
     the Test262 conformance suite.}
+  \vspace{-2ex}        
   \small
@@
 \end{wraptable}
-We used the official conformance test suite
-Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this test. However, we
-expect that results provide indication of engine's maturity. In the
-limit, it is not desirable to flood bug reports on engines at early
-stages of development. We ran the suite once a day for seven
-consecutive days from the period of 16 to 22 of August,
-2018. Table~\ref{tab:test262} shows the average number of passing
-tests over this period. The variance of results was negligible; for
-that reasons, we omitted standard deviations. We noticed that all four
-engines we analyzed but \chakra{} use some variant of the Test262
-suite as part of their regression process, but we used the same
-version in this experiment; the one available from the Test262 web
-site~\cite{ecma262-conformance-suite}. Results show that there are
-still many unsupported cases as can be observed from the percentages
-in the table, but the number of passing tests is high, with
-\veight\ and \smonkey\ performing better compared to others and
+Table~\ref{tab:test262} shows the average number of passing tests over
+this period. The variance of results was negligible; for that reasons,
+we omitted standard deviations. We noticed that all four engines but
+\chakra{} used some variant of the Test262 suite as part of their
+regression process, but we used the same version in this
+experiment~\cite{ecma262-conformance-suite}. Results show that there
+are still many unsupported cases as can be observed from the
+percentages in the table, but the number of passing tests is high,
+with \veight\ and \smonkey\ performing better compared to others and
 \chakra\ performing well worse than others. It is important to
@@
 test suite and the one we were able to find more bugs. Although it is
-possible to find correlation between the percentage of passing tests
-in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
-measured by the number of bugs found (as per
-Figure~\ref{fig:summary}), we do not not imply causality.
+plausible to find correlation between the passing ratios and
+reliability as measured by the number of bugs found (as per
+Figure~\ref{fig:summary}), we not not imply causality.
 
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~...
+      \textit{Summary:}~All engines seems to adhere well to the
+      \js\ standard. Except for \chakra, the passing ratio of all
+      engines is above 90\%.
       \end{minipage}

### 2019-02-18 paper/paper.tex
pass on mining tests

@@
 included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
-find a public classifier to solve the problem above. For space, we
+find a public classifier to solve the problem above. 
+\Igor{
+For space, we summarize the solution that worked the best in the following. 
+We used a standard Embeddings NLP word2vec \cite{kusner2015word}
+to get the relationship between sentences and as feature extractor to 
+feed the neural network (NN). 
+Embedding is a technique that uses a neural network to encoding data 
+in a vector of fixed length, mainly, categorical data. 
+In this context, embedding was used following the method skip-gram whose 
+the purpose is given a word, predict the neighbors words.
+The model has been trained and evaluated using a
+dataset with 25K samples of English paragraphs and 25K snippets of
+\js{}. Devido a quantidade de amostras ser relativamente grande, 
+utilizamos a validação durante cada epoch no treinamento and 
+obtained a predicted accuracy of \Fix{98\%}.
+This classifier is publicly available from our website as
+a separate component.
+}
+\Comment{
+For space, we
 summarize the solution that worked the best in the following. The
@@
 a separate component.
+}
 

### 2019-02-18 paper/paper.tex
pass on classification

--- 2019-02-15 paper/paper.tex
@@
 
-Accessing attachments was engineering-wise simpler compared to
-embedded tests. For that, we wrote a crawler to visit the issue
-trackers of all four engines listed in Table~\ref{tab:engines} and we
-were able to retrieve a total of 627 files (\jsc{}=147, \veight{}=370,
-and \smonkey{}=110).
-
-To mine tests from the textual descriptions we proceeded as
-follows. First, we broke the text describing the issue in paragraphs
-and used a binary classifier to label each paragraph as ``code'' or
-``not code''. Then, based on that information, we merged consecutive
-paragraphs labeled as ``code'' and used a \js\ parser to check
-well-formedness of the corresponding code fragment. Using that method
-we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
-\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
-included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
-find a public classifier to solve the problem above. For space, we
-summarize the solution that worked the best in the following. The
-classifier that performed best for this case uses
-a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
-  what this ``Embeddings'' thing does at a high-level. Also, if this
-  stuff exists why we did not find a solution off-the-shelf?} that
-builds on a neural net~\Fix{cite} to keep a dictionary of words and the
-similarity distance among them\Mar{but we are talking about
-  sentences. how does it go from words to sentences? Note that many
-  words from the ``code'' vocabulary are from English!}. In more
-detail, the classification model uses a Convolutional Neural
-Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-  meaning for each layer?} and has been trained and evaluated using a
-dataset with 25K samples of English paragraphs and 25K snippets of
-\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-evaluate the model and obtained a predicted accuracy of
-\Fix{98\%}. This classifier is publicly available from our website as
-a separate component.
+% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
+% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
+To obtain test files included as attachments, we wrote a crawler to
+visit the issue trackers of all engines listed in
+Table~\ref{tab:engines} and we were able to retrieve a total of
+\Fix{627} files.  To mine tests from the textual descriptions we
+proceeded as follows. First, we broke the text describing the issue in
+paragraphs and used a binary classifier to label each paragraph as
+``code'' or ``not code'' (\ie{}, natural language). Then, based on
+that information, we merged consecutive paragraphs labeled as ``code''
+and used a \js\ parser to check well-formedness of the retrieved code
+fragment. Using that method we were able to retrieve a total of
+\Fix{XX} files. All those files were included in
+Table~\ref{tab:test-suites}. For the classification of ``code''
+vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
+NLP technique to produce word embeddings. A word embedding is a
+mapping of words---in our case, sentences---to vectors of real
+numbers. With that mapping it is possible to measure distance between
+two sentences as the distance between the vectors characterizing
+them. Consequently, one can measure, for example, the minimum distance
+between a sentence in English and a sentence in a \js\ embedding,
+built with word2vec using a corpus of \js\ sentences. \Mar{Please
+  confirm if this is the idea! If yes, shouldn't just one corpus
+  (e.g., the JS corpus) be enough to solve the problem? Are there two
+  separate embeddings (one for English and one for JS)? If not, how
+  they are combined? What about the classification scheme?  It needs
+  to answer yes/no (not a distance).}  We used a corpus with 25K
+samples of English paragraphs and 25K snippets of \js{} code and
+obtained a classifier with accuracy of 98\%. This classifier is
+publicly available from our website as a separate component.
+
+%% For space, we summarize the solution that worked the best in
+%% the following. The classifier that performed best for this case uses a
+%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
+%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
+%%   exists why we did not find a solution off-the-shelf?}  that builds
+%% on a neural net~\Fix{cite} to keep a dictionary of words and the
+%% similarity distance among them\Mar{but we are talking about
+%%   sentences. how does it go from words to sentences? Note that many
+%%   words from the ``code'' vocabulary are from English!}. In more
+%% detail, the classification model uses a Convolutional Neural
+%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
+%%   meaning for each layer?} and has been trained and evaluated using a
+%% dataset with 25K samples of English paragraphs and 25K snippets of
+%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
+%% evaluate the model and obtained a predicted accuracy of
+%% \Fix{98\%}. This classifier is publicly available from our website as
+%% a separate component.
 

### 2019-02-19 paper/paper.tex
pass on RQ1

@@
 
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to check conformance of
-engines to the \js\ current standard. As it is acceptable to release
-engines fulfilling the specification only partially~\cite{kangax}, it
-is expected that engines do not fully pass this check. However, we
-expect that results provide indication of engine's maturity. In the
-limit, it is not desirable to flood bug reports on engines at early
-stages of development. We ran the suite once a day for seven
-consecutive days from the period of a week and averaged the passing ratios.
+The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
+check conformance of engines to the \js\ standard. It is
+acceptable to release engines fulfilling the specification only
+partially~\cite{kangax}. We expect that the pass rate on this suite
+provide some indication of the engine's maturity. In the limit, it is
+not desirable to flood bug reports on engines at early stages of
+development.
 
@@
 \end{wraptable}
-Table~\ref{tab:test262} shows the average number of passing tests over
-this period. The variance of results was negligible; for that reasons,
-we omitted standard deviations. We noticed that all four engines but
-\chakra{} used some variant of the Test262 suite as part of their
-regression process, but we used the same version in this
+For this experiment, we ran the suite once a day for seven consecutive
+days and averaged the passing ratios. Table~\ref{tab:test262} shows
+the average number of passing tests over this period. The variance of
+results was negligible; for that reason, we omitted standard
+deviations. We noticed that all four engines but \chakra{} used some
+variant of the Test262 suite as part of their regression process, but
+we used the same version in this
 experiment~\cite{ecma262-conformance-suite}. Results show that there
-are still many unsupported cases as can be observed from the
-percentages in the table, but the number of passing tests is high,
-with \veight\ and \smonkey\ performing better compared to others and
-\chakra\ performing well worse than others. It is important to
-highlight that failures in this conformance test suite indicates
-missing features as opposed to bugs. However, note that \chakra\ is
-both the engine that has the lowest passing ratio in the conformance
-test suite and the one we were able to find more bugs. Although it is
-plausible to find correlation between the passing ratios and
-reliability as measured by the number of bugs found (as per
-Figure~\ref{fig:summary}), we not not imply causality.
+are still many unsupported scenarios as can be observed from the
+percentages in the table. The number of passing tests is high and
+similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
+worse compared to the other engines. Note also that \chakra\ is both
+the engine that has the lowest passing ratio in this test suite and
+the one we were able to find more bugs (as per
+Figure~\ref{fig:summary}). Although it is plausible to find
+correlation between the passing ratios and reliability as measured by
+the number of bugs found, we do not imply causality. It is important
+to note that failures in this conformance test suite indicates missing
+features as opposed to bugs.
 
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seems to adhere well to the
+      \textit{Summary:}~All engines seem to adhere well to the
       \js\ standard. Except for \chakra, the passing ratio of all

### 2019-02-19 paper/paper.tex
pass on RQ2

@@
 want to assess how effective is the idea of cross-fertilization of
-knowledge among \js\ developers.
+testing knowledge among \js\ developers.
 
@@
 In this experiment, a developer with experience in \js\ analyzed each
-test file that reveals failure in a given engine and classified that
-file as potentially fault-revealing or not. The co-authors supervised
-the classification process to validate correctness. For the cases the
-developer classified the failures as potentially fault-revealing, one
-of the co-authors carefully inspected the case and reported the bug,
-if confirmed, or re-classified the failure as a false alarm.
+test failure, affecting a particular engine, and classified that
+failure as potentially fault-revealing or not. The authors supervised
+the classification process to validate correctness. For the
+potentially fault-revealing cases, one of the authors carefully
+inspected the scenario and, if agreed on the classification, reported
+the bug on the issue tracker of the affected engine.
+
+%If not, re-classified the failure as a false alarm.
 
@@
 \label{sec:results}
+
+\Fix{Igor, please check these numbers! The status of most reports should
+  have changed.}
 
@@
 tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
+Section~\ref{sec:seeds}, we used the
 \totalTestFilesForTestTransplantation{} tests included in the circle
-from Table~\ref{tab:test-suites}. Running those tests we observed a
-total of 812 failures manifested across 543 distinct files (8.9\% of
-total). Table~\ref{tab:cross-testing} shows that, considering the
-engines analyzed, \smonkey\ was the engine that failed the least
-whereas \chakra\ was the engine that failed the most. The
-\smonkey\ test suite also revealed more failures than any other,
-perhaps as expected, considering that it is the suite with more tests
-(see Table~\ref{tab:test-suites}).
+from Table~\ref{tab:test-suites} in this experiment. Running those
+tests we observed a total of 812 failures manifested across 543
+distinct files (8.9\% of total). Table~\ref{tab:cross-testing} shows
+that \smonkey\ was the engine that failed the least whereas
+\chakra\ was the engine that failed the most. The \smonkey\ test suite
+also revealed more failures than any other, perhaps as expected,
+considering that it is the suite with more tests (see
+Table~\ref{tab:test-suites}).
 
@@
 
-\sloppy
-The sources of false positives found in this experiment are as
+\sloppy The sources of false positives found in this experiment are as
 follows: \textbf{Undefined Behavior.} False positives of this kind are
@@
 is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} does not
+engine yet. For example, at the time of writing, \chakra{} did not
 implement by default various properties from the \mcodeid{Symbol}
@@
 an object property is undefined in the execution engine but we were
-unable to capture looking for error types like \CodeIn{ReferenceError}
-and \CodeIn{TypeError}. For example, we found cases where the test (or
-its harness) capture the corresponding exception, making the test to
-fail in an assertion instead.  \textbf{Other.} This category includes
-other sources. For example, it includes the cases where the test was
-valid for some previous version of the spec but is no longer valid for
-the current spec.
+unable to capture that by looking for error types like
+\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example, we found
+cases where the test (or its harness) fails in an assertion because of
+an undefined property.}
+\textbf{Other.} This category includes other sources. For example, it
+includes the cases where the test was valid for some previous version
+of the spec but is no longer valid for the current spec.
 
 \begin{wraptable}[12]{r}{0.23\textwidth}
+  \vspace{-3ex}
   \small
@@
 Table~\ref{fig:piecharts-transplantation} shows the distribution of
-false and true positives. Considering false positives, ``Undefined
-Behavior'' was the most predominant source. Considering true
-positives, we found a reasonable number of duplicate reports, but not
-enough high to justify attempting to automate the detection of
-duplicates.  Table~\ref{tab:test-transplantation-bugs} lists all bugs
-we found with test transplantation. The first column shows the
-identifier we assigned to the bug\Comment{, column ``Date'' shows the
-  date the bug was reported in the format ``m/dd'',}, column
-``Engine'' shows the affected engine, column ``Status'' shows the
-status of the bug report at the time of the writing. The status string
-appears in bold face for status ``Confirmed'' or higher, \ie{},
-``Assigned'' and ``Fixed''.  Column ``Severity'' shows the
-severity of confirmed bugs, and, finally, column ``Suite''
-shows the name of the engine that originated the test.
+False Positives (FPs) and True Positives (TPs). Considering false
+positives, ``Undefined Behavior'' was the most predominant
+source. Considering true positives, we found a reasonable number of
+duplicate reports, but not high enough to justify attempting to
+automate the detection of duplicates.
 
@@
 
-Considering severity levels, it is worth noting that
-\jsc{}~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity} uses
-five levels, whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} use only three. As usual, the smallest
-the severity value the highest the severity of the bug. We use a dash
-(``-'') in place of the severity level for the cases where the bug
-report is pending confirmation. Of the \noBugsTransplantation{} bugs
-we reported in this experiment, \noBugsTransplantationConfirmed\ were
-promoted from the status ``New'' to ``Confirmed''. Of these, 16 are
-severity-2 bugs.  Although we did not find any critical bugs, most of
-the bugs are seemingly important as per the categorization given by
-engineers. Analyzing the issue tracker of \chakra, we found that
-severity-1 bugs are indeed rare. Considering the bug reports confirmed
-by developers, \chakra{} was the engine with the highest number--12
-(with 3 bugs fixed). Considering the remaining engines, \veight{}
-developers confirmed the three bugs we reported, fixing
-one. Curiously, Google engineers confirmed the report we issued in a
-few hours. Overall, we found that development teams of other engines,
-specially \jsc\, took much longer to analyze bug reports as can be
-observed in the \jsc\ stacked bar from
-Figure~\ref{fig:stacked-engine}. Curiously, however, the bugs that the
-\jsc{} team confirms are quickly fixed.
+Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
+test transplantation. The first column shows the identifier we
+assigned to the bug\Comment{, column ``Date'' shows the date the bug
+  was reported in the format ``m/dd'',}, column ``Engine'' shows the
+affected engine, column ``Status'' shows the status of the bug report
+at the time of the writing. The status string appears in bold face for
+status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
+Column ``Severity'' shows the severity of confirmed bugs, and,
+finally, column ``Suite'' shows the name of the engine that originated
+the test.  (We omitted the URLs of the issues to protect anonymity.)
+Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
+and \smonkey{}~\cite{mozilla-severity} developers use five levels,
+whereas \chakra{}~\cite{chakra-severity} and
+\veight{}~\cite{v8-severity} developers use only three. As usual, the
+smallest the severity value the highest the severity of the bug. We
+use a dash (``-'') in place of the severity level for the cases where
+the bug report is pending confirmation. Of the
+\noBugsTransplantation{} bugs we reported in this experiment,
+\noBugsTransplantationConfirmed\ were promoted from the status ``New''
+to ``Confirmed''. Of these, 16 are severity-2 bugs.  Although we did
+not find any critical bugs, most of the bugs are seemingly important
+as per the categorization given by engineers. Analyzing the issue
+tracker of \chakra, we found that severity-1 bugs are indeed
+rare. Considering the number of bug reports confirmed by developers,
+\chakra{} was the engine with the highest number--12 (with 3 bugs
+fixed). Considering the remaining engines, \veight{} developers
+confirmed the three bugs we reported, fixing one. Curiously, Google
+engineers confirmed the issued bug reports in a few hours. Overall, we
+found that development teams of other engines, specially \jsc\, took
+much longer to analyze bug reports as can be observed in the
+\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
+However, the bugs the \jsc{} team confirmed were quickly fixed.
 

### 2019-02-19 paper/paper.tex
pass on RQ2

@@
 \subsubsection{Methodology}
-The experimental methodology we used is as follows. To avoid
-experimental noise, we only fuzz test files that pass in all
-engines--a total of \totalTestFilesPassInAll\ tests satisfy this
-restriction.  Those tests appear under the column ``no-fail-in-all''
-from Table~\ref{tab:test-suites}.  The intuition is that we wanted to
-avoid the scenario where fuzzing produces a fault-revealing input
-based on a test that was already revealing failures on some
-engine. This decision facilitates our inspection task; it helps us
-establish cause-effect relationship between fuzzing and the
-observation of discrepancy.  We configured our infrastructure (see
-Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files per
-input file, \ie{}, the number of fuzzing iterations can exceed the
-number above as we discard syntactically invalid files.
+The experimental methodology we used is as follows. As explained in
+Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
+QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
+we only fuzz test files that pass in all engines--a total of
+\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
+appear under the column ``no-fail-in-all'' on
+Table~\ref{tab:test-suites}.  We want to avoid the scenario where
+fuzzing produces a fault-revealing input based on a test that was
+already revealing failures on some engine. This decision facilitates
+our inspection task; it helps us establish cause-effect relationship
+between fuzzing and the observation of discrepancy.  We configured our
+infrastructure (see Figure~\ref{fig:workflow}) to produce 20
+well-formed fuzzed files per input file, \ie{}, the number of fuzzing
+iterations can exceed the number above as we discard generated files
+that are syntactically invalid.
 
@@
 \vspace{0.5ex}
-\noindent\textbf{Exploratory Phase.} For the first three months of the
+\lbrack{}Exploratory Phase.\rbrack{} For the first three months of the
 study, our inspection process was exploratory.  In this phase, we
 wanted to learn whether or not black-box fuzzers could reveal real
-bugs and how effective \lo\ warnings were relative to
-\hi\ warnings. The rationale for studying the \hi\ and \lo\ warning
-classification was that if we realized that the ratio of bugs from
-\lo\ warnings was rather low, we could focus our inspection efforts
-only on \hi\ warnings as we expected the number of warnings to
-increase dramatically compared to the previous experiment. To run this
-experiment, we trained eight students in analyzing the warnings that
-our infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases; the tests from the
-Mozilla suite are often longer than others. Only after the co-authors
-reviewed the diagnosis, a bug report was filed. Each student found at
-least one bug using this methodology.
+bugs and how effective was the \hi{}-\lo\ warning classification.  We
+expected the number of warnings to increase dramatically compared to
+the previous experiment and, if we realized that the ratio of bugs
+from \lo\ warnings was rather low, we could focus our inspection
+efforts on \hi\ warnings. To run this experiment, we trained eight
+students in analyzing the warnings that our infrastructure
+produces. The students were enrolled in a graduate-level testing
+class. We listed warnings in a spreadsheet and requested the students
+to update an ``owner'' column indicating who was working on it, but we
+did not enforce a strict order on the warnings the students should
+inspect. Recall from Section~\ref{sec:clusterization} that we
+clustered \lo\ warnings in buckets. For that reason, we only listed
+one \lo\ warning per representative class/bucket in the
+spreadsheet. First, we explained, through examples, the possible
+sources of false alarms they could find and then we asked the students
+to use the following procedure when finding a suspicious
+warning. Analyze the parts of the spec related to the problem and, if
+still suspicious, look for potential duplicates on the bug tracker of
+the affected engine using related keywords. If none was reported,
+indicate in the spreadsheet that that warning is potentially
+fault-revealing. We encouraged students to use lithium~\cite{lithium}
+to minimize long test cases\Comment{; the tests from the Mozilla suite are
+often longer than others}. Only after the co-authors reviewed the
+diagnosis, a bug report was filed. Each student found at least one bug
+using this methodology.
 
 \vspace{0.5ex}
-\noindent\textbf{Non-Exploratory Phase.} Results obtained in the
+\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
 exploratory phase confirmed our expectations that most of the bugs
@@
 analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning belongs to the
-group of a given engine if only that engine manifests distinct
-behavior, \ie{}, it produces a distinct output compared to others. We
-separated in a distinct group the warnings for which two engines
-diverge. The rationale for this methodology was to give attention to
-each engine more uniformly, enabling more fair comparison across
-engines.
+analyzed \warningsIteration{} warnings in each group. A warning
+belongs to the group of a given engine if only that engine manifests
+distinct behavior, \ie{}, it produces a distinct output compared to
+others. We separated in a distinct group the warnings for which two
+engines diverge. The rationale for this methodology was to give
+attention to each engine more uniformly, enabling more fair comparison
+across engines.
 
@@
 number of files involved in these warnings, and column ``avg. \# files
-per bucket'' show the average number of files per bucket. Note that,
+per bucket'' shows the average number of files per bucket. Note that,
 although the number of buckets and files differ substantially across
-fuzzers, the difference of files per bucket was negligible.
+fuzzers, the difference of files per bucket was not very high.\Mar{not
+sure how relevant is this par.}
 
@@
 Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These sources are
-highlighted with a ``*'' in the table. The source ``Invalid Input''
+sources, which we did not observe before. These new sources are
+marked with a ``*'' in the table. The source ``Invalid Input''
 indicates that the test input violated some part of the
@@
   \centering
-  \caption{\label{tab:false-positives}Distribution of false
-    and true positives.}
+  \caption{\label{tab:false-positives}Distribution of False (FP)
+    and True Positives (TP).\Mar{why numbers in this table does match with
+      that on table ``Number of hi warnings...''?}}
   \begin{tabular}{ccrr}
@@
     \midrule
-    \multirow{4}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
+    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\
     & Timeout/OME & 28 & 13 \\
@@
     \midrule
-    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
+    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\
     & Bug & 12 & 6\\
@@
 (``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
-(``Url''), the severity of the bug report (``Severity''), the priority
+bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
+(``Url'')}, the severity of the bug report (``Severity''), the priority
 that we assigned to the warning that revealed the bug (``Priority''),
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was also
-      effective at finding bugs in \js\ engines. However, compared to
-      test transplantation, it required substantial more human effort
-      per bug found.
+      \textit{Summary:}~Cross-engine differential testing was very
+      effective at finding bugs in \js\ engines. 
       \end{minipage}

### 2019-02-19 paper/paper.tex
pass on macros

@@
 their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed 63
-test cases that fail for that reason--6 tests from \jsc{} and 57 tests
-from \smonkey. Column ``type-in-all'' shows the number of test cases
-whose executions do not throw dynamic type errors in any of the
-engines because of an undefined variable or property. These cases were
-captured by looking for the presence of \CodeIn{ReferenceError} and
+the failure, so we assumed the test could be broken. We removed \testsThatFail{}
+test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
+\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
+shows the number of test cases whose executions do not throw 
+dynamic type errors in any of the engines because of an undefined variable or property. 
+These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
 \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
@@
 consider tests from the \chakra{} repository because they depend on
-non-portable objects. Finally, note that the number of tests in
+non-portable objects. \Fix{fix... the number will increase}
+Finally, note that the number of tests in
 \veight\ is low; that happens because \veight{} uses many tests from
@@
 Table~\ref{tab:engines} and we were able to retrieve a total of
-\Fix{627} files.  To mine tests from the textual descriptions we
+\filesAttached{} files.  To mine tests from the textual descriptions we
 proceeded as follows. First, we broke the text describing the issue in
@@
 fragment. Using that method we were able to retrieve a total of
-\Fix{XX} files. All those files were included in
+\filesMining{} files. All those files were included in
 Table~\ref{tab:test-suites}. For the classification of ``code''
@@
   they are combined? What about the classification scheme?  It needs
-  to answer yes/no (not a distance).}  We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code and
-obtained a classifier with accuracy of 98\%. This classifier is
+  to answer yes/no (not a distance).}  We used a corpus with \samplesEnglish{}
+samples of English paragraphs and \samplesJSSnippets{} snippets of \js{} code and
+obtained a classifier with accuracy of \accuracyMining{}. This classifier is
 publicly available from our website as a separate component.
@@
   output is considered for reporting? are there any
-  filtering?}
+  filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
+  nao estamos mais utilizando isso devido a essa ferramenta nao 
+  capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
+  A respeito de filtros nos reports, nao. Nos so capturamos o output,
+  o que modificamos eh apenas a formatacao do output para coletar apenas a
+  mensagem e nao o stack trace.
+  Mas eu lembro que se houver um crash ou algo do tipo, nos reportamos de qualquer maneira,
+  mas nao tenho certeza (vou olhar no nosso codigo)
+  }
 
@@
     \midrule
-    \jsc{} & 92\%\\
-    \veight{} & 95\% \\
-    \chakra{} & 75\% \\    
-    \smonkey{} & 93\% \\
+    \jsc{} & \percentSuiteTestJSC{}\\
+    \veight{} & \percentSuiteTestVeight{} \\
+    \chakra{} & \percentSuiteTestChakra{} \\    
+    \smonkey{} & \percentSuiteTestSM{} \\
     \bottomrule
@@
 Section~\ref{sec:seeds}, we used the
-\totalTestFilesForTestTransplantation{} tests included in the circle
+\totalTestFilesForTestTransplantation{} tests included in the \Igor{rectangle area}
 from Table~\ref{tab:test-suites} in this experiment. Running those
-tests we observed a total of 812 failures manifested across 543
-distinct files (8.9\% of total). Table~\ref{tab:cross-testing} shows
+tests we observed a total of \failuresTestTrans{} failures manifested across 
+\failuresTestTransDistictFiles{} distinct files (\failuresTestTransPercent{} of total). 
+Table~\ref{tab:cross-testing} shows
 that \smonkey\ was the engine that failed the least whereas
@@
 \noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, 16 are severity-2 bugs.  Although we did
+to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
 not find any critical bugs, most of the bugs are seemingly important
@@
 rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--12 (with 3 bugs
+\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
 fixed). Considering the remaining engines, \veight{} developers
-confirmed the three bugs we reported, fixing one. Curiously, Google
+confirmed the \bugsVeight{} bugs we reported, fixing \bugsVeightFixed{}. Curiously, Google
 engineers confirmed the issued bug reports in a few hours. Overall, we
@@
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. Considering \veight{}, we reported two
-bugs, both of which were confirmed, with one fixed.
+were duplicates and were not reported. Considering \veight{}, we reported \bugsVeight{}
+bugs, all of them were confirmed, with \bugsVeightFixed{} fixed.
 

### 2019-02-19 paper/paper.tex
pass on mining

@@
 Table~\ref{tab:test-suites}. For the classification of ``code''
-vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
-NLP technique to produce word embeddings. A word embedding is a
-mapping of words---in our case, sentences---to vectors of real
-numbers. With that mapping it is possible to measure distance between
-two sentences as the distance between the vectors characterizing
-them. Consequently, one can measure, for example, the minimum distance
-between a sentence in English and a sentence in a \js\ embedding,
-built with word2vec using a corpus of \js\ sentences. \Mar{Please
-  confirm if this is the idea! If yes, shouldn't just one corpus
-  (e.g., the JS corpus) be enough to solve the problem? Are there two
-  separate embeddings (one for English and one for JS)? If not, how
-  they are combined? What about the classification scheme?  It needs
-  to answer yes/no (not a distance).}  We used a corpus with \samplesEnglish{}
-samples of English paragraphs and \samplesJSSnippets{} snippets of \js{} code and
-obtained a classifier with accuracy of \accuracyMining{}. This classifier is
+vs. ``not code'',
+
+% we used word2vec~\cite{kusner2015word}, a popular
+% NLP technique to produce word embeddings. A word embedding is a
+% mapping of words---in our case, sentences---to vectors of real
+% numbers. With that mapping it is possible to measure distance between
+% two sentences as the distance between the vectors characterizing
+% them. Consequently, one can measure, for example, the minimum distance
+% between a sentence in English and a sentence in a \js\ embedding,
+%   built with word2vec using a corpus of \js\ sentences.
+% \Mar{Please
+%   confirm if this is the idea! If yes, shouldn't just one corpus
+%   (e.g., the JS corpus) be enough to solve the problem? Are there two
+%   separate embeddings (one for English and one for JS)? If not, how
+%   they are combined? What about the classification scheme?  It needs
+%   to answer yes/no (not a distance).}
+% We used a corpus with \samplesEnglish{}
+% samples of English paragraphs and \samplesJSSnippets{} snippets of \js{} code and
+% obtained a classifier with accuracy of \accuracyMining{}. This classifier is
+% publicly available from our website as a separate component.
+
+\Igor{
+  we used a corpus with \samplesEnglish{} samples of English 
+  paragraphs and \samplesJSSnippets{} snippets of \js{} code.
+  To process the corpus we used word2vec~\cite{kusner2015word}, a popular
+  NLP technique to produce word embeddings as an input for a Multi-Layer Perceptron (MLP).
+  A word embedding is a mapping of tokens that represents 
+  words---in our case, sentences---to vectors of real
+  numbers. The output of word2vec gives the context and extra informations about the tokens,
+  for example the distance between them. Consequently, one can measure, for example, the minimum distance
+  between a token in English and a token in a \js\ embedding, using a corpus of \js\ sentences.
+  We used a simple supervised MLP to train and predicted the inputs, 
+  the classifier obtained accuracy of \accuracyMining{}. This classifier is
   publicly available from our website as a separate component.
+}
 
@@
 fixed). Considering the remaining engines, \veight{} developers
-confirmed the \bugsVeight{} bugs we reported, fixing \bugsVeightFixed{}. Curiously, Google
+confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
+\noTransVeightBugsFixed{}. Curiously, Google
 engineers confirmed the issued bug reports in a few hours. Overall, we

### 2019-02-19 paper/paper.tex
revising classifier par.

--- 2019-02-19 paper/paper.tex
@@
 \Fix{XX} files. All those files were included in
-Table~\ref{tab:test-suites}. For the classification of ``code''
-vs. ``not code'', we used word2vec~\cite{kusner2015word}, a popular
-NLP technique to produce word embeddings. A word embedding is a
-mapping of words---in our case, sentences---to vectors of real
-numbers. With that mapping it is possible to measure distance between
-two sentences as the distance between the vectors characterizing
-them. Consequently, one can measure, for example, the minimum distance
-between a sentence in English and a sentence in a \js\ embedding,
-built with word2vec using a corpus of \js\ sentences. \Mar{Please
-  confirm if this is the idea! If yes, shouldn't just one corpus
-  (e.g., the JS corpus) be enough to solve the problem? Are there two
-  separate embeddings (one for English and one for JS)? If not, how
-  they are combined? What about the classification scheme?  It needs
-  to answer yes/no (not a distance).}  We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code and
-obtained a classifier with accuracy of 98\%. This classifier is
-publicly available from our website as a separate component.
+Table~\ref{tab:test-suites}.
+
+For the classification of ``code'' vs. ``not code'', we used a
+pipeline of two Neural Networks (NN), a popular design for solving NLP
+classification problems~\Fix{cite}. The first net in the pipeline
+takes as input an arbitrary sentence and produces on output a
+characterization vector for that sentence. The second net in the
+pipeline takes that vector on input and the class for that attribute
+(\ie{}, ``(not) code'') and produces a yes/no answer, determining
+whether or not the input sentence was code. More in detail, for the
+first net, we used word2vec~\cite{kusner2015word}, a popular NLP
+technique to produce word embeddings. A word embedding is a mapping of
+words to vectors of real numbers. For the second net, we used a
+multi-layer perceptron~\Fix{cite} to infer the probability of the
+input belonging or not to the class. We classify as code an input for
+which the pipeline produces a probability of 0.7 or higher. We used a
+corpus with 25K samples of English paragraphs and 25K snippets of
+\js{} code and obtained a classifier with accuracy of 98\%. This
+classifier is publicly available from our website as a separate
+component.
+
+%% With that mapping it is
+%% possible to measure distance between two sentences as the distance
+%% between the vectors characterizing them. Consequently, one can
+%% measure, for example, the minimum distance between a sentence in
+%% English and a sentence in a \js\ embedding, built with word2vec using
+%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
+%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
+%%   solve the problem? Are there two separate embeddings (one for
+%%   English and one for JS)? If not, how they are combined? What about
+%%   the classification scheme?  It needs to answer yes/no (not a
+%%   distance).}
 

### 2019-02-19 paper/paper.tex

@@
 rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--12 (with 3 bugs
+\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
 fixed). Considering the remaining engines, \veight{} developers
-confirmed the three bugs we reported, fixing one. Curiously, Google
+confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
+\noTransVeightBugsFixed{}. Curiously, Google
 engineers confirmed the issued bug reports in a few hours. Overall, we
@@
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. Considering \veight{}, we reported two
-bugs, both of which were confirmed, with one fixed.
+were duplicates and were not reported. Considering \veight{}, 
+we reported \noDiffVeight{} bugs, 
+all of them were confirmed, with \noDiffVeightFixed{} fixed.
 

### 2019-02-20 paper/paper.tex
pass on evaluation

--- 2019-02-19 paper/paper.tex
@@
 
+\begin{figure}[t]
+%  \vspace{-2ex}  
+  \centering
+  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
+    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \vspace{-5ex}
+  }\\
+  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
+    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
+    \vspace{-5ex}        
+  }
+  \caption{\label{fig:summary}Summary of bug reports.}
+  \vspace{-3ex}
+\end{figure}
+
 \emph{Results.}~We considered the following engines--Apple, Google,
@@
 variation between different implementations. 3) Differential testing
-is feasible on real, complex, widely used pieces of software.
+is feasible on real, complex, widely used pieces of
+software. Section~\ref{sec:lessons} expands and elaborates key
+findings and lessons learned.
 
@@
 
-\vspace{1ex} To sum, although more research needs be done to automate
-parts of the inspection process (\eg{}, reduction of false alarms),
-the paper provides initial, yet strong evidence that exploring
-diversity should be encouraged to find functional bugs in JavaScript
-engines.
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
+\vspace{1ex} To sum, the paper provides initial, yet strong evidence
+that exploring diversity should be encouraged to find functional bugs
+in JavaScript engines.
 
@@
 
-\section{JS Files Mined}
+\section{Mined JS Files}
 \label{sec:seeds}
@@
 
-Figure~\ref{fig:workflow} illustrates the 
-differential testing infrastructure used in part of this study. It takes on
-input a list of JS files and generates warnings on output. Boxes in
-the figure denote encapsulation, arrowed lines denote data flow, and
-the cycle icons denote repetition--the leftmost icon indicates that
-each file in the input list will be analyzed in separate whereas the
-rightmost icon shows that a single file will be fuzzed multiple times.
-The bug-finding process works as follows. New inputs are obtained for
-a given test input using some off-the-shelf input
-fuzzer; Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
+This section describes the infrastructure we used for cross-engine
+differential testing. Figure~\ref{fig:workflow} illustrate the
+workflow of the approach. It takes on input a list of JS files and
+generates warnings on output. Boxes in the figure denote
+encapsulation, arrowed lines denote data flow, and the cycle icons
+denote repetition--the leftmost icon indicates that each file in the
+input list will be analyzed in separate whereas the rightmost icon
+shows that a single file will be fuzzed multiple times.  The
+bug-finding process works as follows. New inputs are obtained for a
+given test input using some off-the-shelf input fuzzer;
+Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
 The oracle checks whether or not the output produced for the fuzzed
@@
 potentially fault-revealing; hence, interesting for human
-inspection. The infrastructure uses the
-open-source tool eshost-cli~\cite{eshost-cli}, also used at
-Microsoft, for checking output discrepancy.\Mar{any difference in
-  output is considered for reporting? are there any
-  filtering?}
+inspection. The infrastructure uses the open-source tool
+eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
+output discrepancy.\Mar{any difference in output is considered for
+  reporting? are there any filtering?}
 
@@
 
+For this experiment, we ran the suite once a day for seven consecutive
+days and averaged the passing ratios. Table~\ref{tab:test262} shows
 \begin{wraptable}[10]{r}{0.22\textwidth}
-%  \vspace{-2ex}      
+  \vspace{-2ex}      
   \centering
@@
 \end{wraptable}
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
 the average number of passing tests over this period. The variance of
@@
 
-\Fix{Igor, please check these numbers! The status of most reports should
-  have changed.}
-
 Table~\ref{tab:cross-testing} shows the number of failures observed
@@
   \centering
-  \caption{\label{tab:cross-testing}Number of failures observed exchanging
-    test suites.}
+  \caption{\label{tab:cross-testing}Number of failures with
+    Test Transplantation.}
   \renewcommand*{\arraystretch}{0.9}
@@
 \begin{wraptable}[12]{r}{0.23\textwidth}
-  \vspace{-3ex}
+  \vspace{-1ex}
   \small
@@
 
+%% Table~\ref{tab:summary-lo}
+%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
+%% different tools. Column ``\# buckets'' shows the number of buckets
+%% associated with ``\lo'' warnings, column ``\# files'' shows the total
+%% number of files involved in these warnings, and column ``avg. \# files
+%% per bucket'' shows the average number of files per bucket. Note that,
+%% although the number of buckets and files differ substantially across
+%% fuzzers, the difference of files per bucket was not very high.\Mar{not
+%% sure how relevant is this par.}
+
+%% \begin{table}[t]
+%%   \small
+%%   \centering
+%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
+%%   \begin{tabular}{crrr}
+%%     \toprule
+%%     & \# buckets & \# files & avg. \# files per bucket \\
+%%     \midrule
+%%     \radamsa{} & 82 & 319 & 3.8 \\
+%%     \quickfuzz{} & 78 & 218 & 2.7 \\
+%%     \bottomrule
+%%   \end{tabular}
+%% \end{table}
+
 \vspace{0.5ex}
-\subsubsection{Results} Table~\ref{tab:summary-lo}
-shows statistics of \lo\ warnings obtained when fuzzing inputs with
-different tools. Column ``\# buckets'' shows the number of buckets
-associated with ``\lo'' warnings, column ``\# files'' shows the total
-number of files involved in these warnings, and column ``avg. \# files
-per bucket'' shows the average number of files per bucket. Note that,
-although the number of buckets and files differ substantially across
-fuzzers, the difference of files per bucket was not very high.\Mar{not
-sure how relevant is this par.}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-  \begin{tabular}{crrr}
-    \toprule
-    & \# buckets & \# files & avg. \# files per bucket \\
-    \midrule
-    \radamsa{} & 82 & 319 & 3.8 \\
-    \quickfuzz{} & 78 & 218 & 2.7 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings, which
-are not clustered. The table breaks down \hi\ warning by the affected
+\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
 engine, \ie, the engine manifesting distinct output among those
@@
   \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).\Mar{why numbers in this table does match with
-      that on table ``Number of hi warnings...''?}}
+    and True Positives (TP).}
   \begin{tabular}{ccrr}
@@
 
-\subsection{Lessons Learned}
+\subsection{Key Findings and Lessons}
 \label{sec:lessons}
 
-We learned several lessons in this study:
+The main findings of this study are as follows.
 
 \begin{itemize}
-  \item The diversity-aware techniques we used are great
-    at finding bugs in \js\ engines;
-  \item The cost of inspecting failures/warnings is high. Although the
-    inspection activity was not uninterrupted, it is safe to say that
-    each warning required a substantial amount of time to analyze for
-    potential false alarms;
-  \item We have found more bugs with test transplantation than we have
-    with cross-engine differential testing. In addition, test
-    transplantation demanded less effort per bug;
+  \item Both techniques investigated were successful in revealing
+    bugs (several of them);
+  %% \item We have found more bugs with test transplantation than we have
+  %%   with cross-engine differential testing. In addition, test
+  %%   transplantation demanded less effort per bug;
   \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs;
+    interesting inputs. We conjecture that there is room to find more
+    bugs using other fuzzers;
   \item Mozilla's \smonkey\ appears to be the most reliable
@@
 
-\Fix{revisor(es) reclamaram de pouca discussao. isto poderia ser usado
-  em outros contexto? (resp: JS possui varias engine e muitos
-  tests...) ver tambem ``key findings'' na introducao (precisa ficar
-  consistente)}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-%%% comentario de igor
-%%%%%%%%%%%%%%%%%%%%%%%
-%% sim, me refiro a testes que possuem algum comentário do que se trata aquele teste. Por exemplo os testes262, possuem comentários descrevendo o que o teste tem que fazer
-%% os testes da suite do mozilla são mais dificeis de debuggar... não dificeis de grosso modo, mas custava um pouco para identificar o real problema
+The main lessons we learned in this study are the following: 1)~Even
+for problems with fairly clear specifications, as in \javascript{},
+there is likely to be (a lot of) variation between different
+implementations. 2)~Not only multiple different implementations can be
+leveraged in differential testing, but differences in test suites can
+also be important. 3)~Differential testing is feasible on real,
+complex, widely used pieces of software. 4)~The cost of inspecting
+failures/warnings is high. Although the inspection activity was not
+uninterrupted, it is safe to say that each warning required a
+substantial amount of time to analyze for potential false alarms. We
+prefer to see this as an opportunity for future research in applying
+learning techniques to prioritize warnings more likely to be faulty.
+%based on static and dynamic features.
 
@@
 
+\Fix{
+although more research needs be done to automate
+parts of the inspection process (\eg{}, reduction of false alarms),}
+
 JavaScript is a very popular language. For that reason, bugs in engine

### 2019-02-20 paper/paper.tex

@@
 potentially fault-revealing; hence, interesting for human
-inspection. The infrastructure uses the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy.\Mar{any difference in output is considered for
-  reporting? are there any filtering?}
+inspection. The infrastructure uses the
+open-source tool eshost-cli~\cite{eshost-cli}, also used at
+Microsoft, for checking output discrepancy.\Mar{any difference in
+  output is considered for reporting? are there any
+  filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
+  nao estamos mais utilizando isso devido a essa ferramenta nao 
+  capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
+  A respeito de filtros nos reports, nao. Nos so capturamos o output,
+  o que modificamos eh apenas a formatacao do output para coletar apenas a
+  mensagem e nao o stack trace.
+  }
 

### 2019-02-20 paper/paper.tex
pass on macros

@@
     \midrule
-    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & \marktopleft{c2}17,639 \\
+    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
     \midrule
-    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
-    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
-    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
+    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
+    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
+    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
     \midrule
-    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
-    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
-    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
-    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\markbottomright{c2}\\
+    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
+    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
+    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
+    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
     \midrule
@@
 consider tests from the \chakra{} repository because they depend on
-non-portable objects. \Fix{fix... the number will increase}
+non-portable objects. 
 Finally, note that the number of tests in

### 2019-02-20 paper/paper.tex
minor edits

@@
 %% system's implementations to detect anomalous behavior.
-
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most open, manifest
-themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engines to test and find bugs. We remain to investigate the diversity
-of test cases themselves. In principle, that could help reduce the
-number of alarms to inspect, for example.
-
 \emph{Related Ideas.}~The idea of test set diversity dates back to the
@@
 been explored before in different contexts.  The goal of the paper is
-to assess the ability of these techniques aforementioned in finding
+to assess the ability of the techniques aforementioned in finding
 bugs on \javascript\ engines.
@@
 tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used the
-\totalTestFilesForTestTransplantation{} tests included in the \Igor{rectangle area}
-from Table~\ref{tab:test-suites} in this experiment. Running those
+Section~\ref{sec:seeds}, we used in this experiment the
+\totalTestFilesForTestTransplantation{} tests included in the
+rectangle area under column ``type-in-all'' from Table~\ref{tab:test-suites}. Running those
 tests we observed a total of \failuresTestTrans{} failures manifested across 
@@
 Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most open, manifest
+the continuity assumption. They found that faults, most often, manifest
 themselves in regular patterns across the input

### 2019-02-20 paper/table_differential.tex
pass on evaluation
pass on numbers

@@
   \centering
-  \caption{List of bug reports issued as result of cross-engine
-    differential testing.}
+  \caption{List of bugs reports from Differential Testing.}
   \label{tab:bugs}
-  \setlength{\tabcolsep}{2pt}
-  \renewcommand{\arraystretch}{0.95}
+  \setlength{\tabcolsep}{1.5pt}
+%  \renewcommand{\arraystretch}{0.95}
   \begin{tabular}{rcccccc}
@@
 
-    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
-    & - & \hi{} & Test262\\
+    & 3 & \hi{} & Test262\\
 
@@
 
-    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & New \Comment{&
+    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & \textbf{Confirmed} \Comment{&
     \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
-    & - & \hi{} & Test262\\
+    & 2 & \hi{} & Test262\\
 

### 2019-02-20 paper/paper.tex
pass on numbers
pass on data (wip)

--- 2019-02-20 paper/paper.tex
@@
 \jsc{}.  We reported \noBugsBugsReportedGoogle{} bugs in Google
-\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
+\veight{} (\noBugsBugsConfirmedGoogle{} confirmed \Igor{and one classified as Won't Fix}) and none in
 Mozilla's \smonkey{}.  Furthermore, our results show that both
@@
 fragment. Using that method we were able to retrieve a total of
-\Fix{XX} files. All those files were included in
+\filesMining{} files. All those files were included in
 Table~\ref{tab:test-suites}.
@@
     }
-    \jsc{} & - & 9 & 10 & 58   \\
-    \veight{} & 29 & - & 0 & 0  \\
+    \jsc{} & - & 9 & 10 & 58   \\ % - & 9 & 10 & 58
+    \veight{} & 41 & - & 0 & 0  \\ % 29 & - & 0 & 0
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 279 \\
+    \smonkey{} & 218 & 107 & - & 279 \\ % 218 & 107 & - & 279
     Duktape & 0 & 4 & 4 & 1   \\
@@
     \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & 252 \\
-    & Timeout/OME & 15 \\
-    & Not Implemented & 22 \\
-    & Non-Standard Element & 119 \\
-    & Other & 135 \\
+    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
+    & Timeout/OME & \noTransTimeout{} \\
+    & Not Implemented & \noTransNotImplemented{} \\
+    & Non-Standard Element & \noTransNonStandard{} \\
+    & Other & \noTransOther{} \\
     \midrule
-    \multirow{2}{*}{TP} & Duplicate & 10 \\
-    & Bug & 24 \\
+    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
+    & Bug & \noTransTPBugs{} \\
     \bottomrule

### 2019-02-20 paper/paper.tex
pass on differential testing

--- 2019-02-20 paper/paper.tex
@@
 of these bugs affected two engines--Microsoft's \chakra{} and Apple's
-\jsc{}.  We reported \noBugsBugsReportedGoogle{} bugs in Google
+JavaScriptCore (\jsc{}).  We reported \noBugsBugsReportedGoogle{} bugs in Google
 \veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
@@
 transplantation, compared to differential testing, demanded less
-effort from the developers who inspected the alarms. Most of the bugs
+effort from the developers who inspected the alarms. Most bugs
 we found are of moderate severity.
@@
 
-\vspace{1ex} To sum, the paper provides initial, yet strong evidence
+\vspace{1ex} To sum, this paper provides initial, yet strong evidence
 that exploring diversity should be encouraged to find functional bugs
@@
 
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrate the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Boxes in the figure denote
-encapsulation, arrowed lines denote data flow, and the cycle icons
-denote repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.  The
-bug-finding process works as follows. New inputs are obtained for a
-given test input using some off-the-shelf input fuzzer;
-Section~\ref{sec:objects:fuzzers} describes the fuzzers we selected.
-The oracle checks whether or not the output produced for the fuzzed
-file is consistent across all engines. In case the test passes in all
-engines or fails in all engines (\ie{}, the output is consistent), the
-infrastructure ignores the input. Otherwise, it considers the input as
-potentially fault-revealing; hence, interesting for human
-inspection. The infrastructure uses the
-open-source tool eshost-cli~\cite{eshost-cli}, also used at
-Microsoft, for checking output discrepancy.\Mar{any difference in
-  output is considered for reporting? are there any
-  filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-  nao estamos mais utilizando isso devido a essa ferramenta nao 
-  capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-  A respeito de filtros nos reports, nao. Nos so capturamos o output,
-  o que modificamos eh apenas a formatacao do output para coletar apenas a
-  mensagem e nao o stack trace.
-  }
-
 \begin{figure}[t]
@@
   \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \vspace{-5ex}  
   \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+  \vspace{-2ex}
 \end{figure}
 
-It is worth noting that a number of reasons exist, other than a bug,
-to explain discrepancy (see Tables~\ref{fig:piecharts-transplantation}
-and ~\ref{tab:false-positives}) and there is no clear automatic
-approach to precisely distinguish false and true positives. As such, a
-human needs to inspect the warning to classify the issue. As mentioned
+\section{Cross-Engine Differential Testing}
+\label{sec:design}
+
+This section describes the infrastructure we used for cross-engine
+differential testing. Figure~\ref{fig:workflow} illustrates the
+workflow of the approach. It takes on input a list of JS files and
+generates warnings on output. Numbered boxes in the figure denote the
+data processors and arrowed lines denote data flows. The cycle icons
+indicate repetition--the leftmost icon indicates that each file in the
+input list will be analyzed in separate whereas the rightmost icon
+shows that a single file will be fuzzed multiple times.
+
+The bug-finding process works as follows. For a given test input, the
+toolchain produces new inputs using some off-the-shelf input fuzzer
+(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
+selected.)  Then, the oracle checks whether or not the output produced
+for the fuzzed file is consistent across all engines (step 2). In case
+the test passes in all engines or fails in all engines (\ie{}, the
+output is consistent), the infrastructure ignores the
+input. Otherwise, it considers the input as potentially
+fault-revealing; hence, interesting for human inspection. Finally, to
+facilitate the human inspection process, the infrastructure
+prioritizes warnings and clusters them in groups (step 3). We describe
+these features in Sections~\ref{sec:prioritization} and
+\ref{sec:clusterization}. Note that a number of reasons exist, other
+than a bug, to explain discrepancy (see
+Tables~\ref{fig:piecharts-transplantation} and
+~\ref{tab:false-positives}) and there is no clear automatic approach
+to precisely distinguish false and true positives. As such, a human
+needs to inspect the warning to classify the issue. As mentioned
 earlier, this justifies why differential testing is challenging to
-automate at the functional level. To facilitate inspection, we
-prioritized warnings and clustered them in groups. We describe these
-strategies in the following.
+automate at the functional level.
+
+For step 2, we considered using the open-source tool
+eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
+output discrepancy. However, we noticed that eshost-cli does not
+handle discrepancies involving crashes. As such, we forked the
+eshost-cli GitHub project and implemented that functionality on it. It
+is also important to note that our checker does not support the case
+where the test fails in all engines but the kind of failure (\eg{},
+exception thrown) is different. Currently, our infrastructure does not
+report discrepancy for that case. For that, it would be necessary to
+properly parse the error message to retrieve the error types. We left
+that as future work as we already found several discrepancies even
+without that.
+
+%% \Mar{any difference in
+%%   output is considered for reporting? are there any
+%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
+%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
+%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
+%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
+%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
+%%   mensagem e nao o stack trace.
+%%   }
 
 \subsection{Prioritization}
+\label{sec:prioritization}
 

### 2019-02-20 paper/paper.tex

@@
 days and averaged the passing ratios. Table~\ref{tab:test262} shows
+the average number of passing tests over this period. The variance of
+results was negligible; for that reason, we omitted standard
+deviations. We noticed that all four engines but \chakra{} used some
+variant of the Test262 suite as part of their regression process, but
+we used the same version in this
+experiment~\cite{ecma262-conformance-suite}. Results show that there
 \begin{wraptable}[10]{r}{0.22\textwidth}
-  \vspace{-2ex}      
+%  \vspace{-2ex}      
   \centering
@@
 \end{wraptable}
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}. Results show that there
 are still many unsupported scenarios as can be observed from the
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was very
-      effective at finding bugs in \js\ engines. 
+      \textit{Summary:}~Cross-engine differential testing was
+      effective at finding \js\ engines bugs, several of which have
+      been fixed already.
       \end{minipage}
@@
 \begin{itemize}
-  \item Both techniques investigated were successful in revealing
+  \item Both techniques we investigated were successful in revealing
     bugs (several of them);
@@
   \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we used, with Google's \veight\ after it;
-  \item Reporting real bugs is a great way to train (and encourage)
-    students in software testing.
+    \js\ engine we used, with Google's \veight\ after it.
 \end{itemize}
 
-The main lessons we learned in this study are the following: 1)~Even
-for problems with fairly clear specifications, as in \javascript{},
-there is likely to be (a lot of) variation between different
-implementations. 2)~Not only multiple different implementations can be
-leveraged in differential testing, but differences in test suites can
-also be important. 3)~Differential testing is feasible on real,
-complex, widely used pieces of software. 4)~The cost of inspecting
-failures/warnings is high. Although the inspection activity was not
+The main lessons we learned from this study are as follows: 1)~Even
+for software projects with fairly clear specifications, as the case of
+\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
+variation between different implementations and, therefore,
+opportunities for bugs. 2)~Not only multiple different implementations
+can be leveraged in differential testing, but differences in test
+suites can also be important. 3)~Finding functional/non-crash bugs
+with differential testing is feasible on real, complex, widely used
+pieces of software. 4)~Further reducing cost of inspection is an
+important problem. Although the inspection activity was not
 uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. We
-prefer to see this as an opportunity for future research in applying
-learning techniques to prioritize warnings more likely to be faulty.
-%based on static and dynamic features.
+substantial amount of time to analyze for potential false alarms. In
+fact, many \hi\ warnings reported with differential testing were not
+analyzed. In determining cost, we observed, from experience, that the
+complexity of the \js\ specifications that the original test covers
+increases cost of diagnosing (as developers need to read and
+understand those) and the availability of alternative implementations
+(for the cases warnings are revealed through differential testing)
+reduces the cost of diagnosis. We prefer to see such problem as an
+opportunity for future research. For example, applying learning
+techniques to prioritize the warnings more likely to be faulty may be
+a promising avenue to explore. Recall that most of those warnings are
+false positives.  5)~We learned that reporting real bugs is a great
+way to train (and encourage) students in software testing. Students
+praised the experience of diagnosing failures, understanding part of
+the specs (as needed), writing bug reports, participating in
+discussions on issue trackers, and observing the change of
+status. That was a relatively self-contained hands-on activity that
+enabled students to engage in a real-life serious industrial project.
 

### 2019-02-20 paper/paper.tex
pass on macros
pass on threats to validity and key findings

@@
 
-As it is the case for most empirical evaluations, there are both
-external and construct threats to validity associated to the results
-we presented. In terms of external validity, our results might not
-generalize to other test inputs and engines. To mitigate this threat,
-we carefully selected inputs from various sources and cleaned them
-according to a well-defined criteria. Considering the \js\ engines, we
-used engines associated with the most popular browsers in the
-market. In terms of construct validity, there might be errors in the
-implementation of our infrastructure. To mitigate this threat, we
-extensively inspected the results of our evaluation manually and, when
-we found the need for implementing a different component we kept the
-old one for cross-checking. For example, we used
-eshost-cli~\cite{eshost-cli} to validate our fork-join implementation
-of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
-efficiency, is tightly integrated to our infrastructure.
-
-\Fix{elaborate}
+As it is the case for most empirical evaluations, our findings are
+subject to internal, external, and construct validity
+threats. Considering internal validity, conceptually, it is possible
+that the authors of this paper made mistakes in the implementation of
+the scripts supporting the experiments. To mitigate this threat, we
+carefully inspected the implementation and results, looking for
+inconsistencies whenever possible. As for external validity, our
+results might not generalize to other test inputs and engines. To
+mitigate this threat, we carefully selected inputs from various
+sources according to a well-defined criteria. Likewise, we selected
+the engines by using using a well-defined criteria and found that the
+engines selected were associated, certainly not by coincidence, with
+the browsers informally considered the most popular in the market. In
+terms of construct validity, we used standard metrics to determine the
+effectiveness of the testing techniques we studied (\eg{}, number of
+bugs confirmed and fixed and severity). Engine developers were
+responsible for determining the labels of the bug reports and their
+severity. Consequently, these metrics originate from a trusted source.
+
+%% there might be errors in the implementation of our
+%% infrastructure. To mitigate this threat, we extensively inspected the
+%% results of our evaluation manually and, when we found the need for
+%% implementing a different component we kept the old one for
+%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
+%% validate our fork-join implementation of the ``Checker'' component
+%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
+%% integrated to our infrastructure.
+%% \Fix{elaborate}
 
@@
   \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we used, with Google's \veight\ after it.
+    \js\ engine we analyzed, with Google's \veight\ after it.
 \end{itemize}
@@
 contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
+contribution was empirical. \Fix{differential testing of debuggers...}
 

### 2019-02-20 paper/paper.tex
pass on macros

@@
     }
-    \jsc{} & - & 9 & 10 & 58   \\ % - & 9 & 10 & 58
-    \veight{} & 41 & - & 0 & 0  \\ % 29 & - & 0 & 0
+    \jsc{} & - & 10 & 10 & 59   \\
+    \veight{} & 41 & - & 3 & 5  \\
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 279 \\ % 218 & 107 & - & 279
+    \smonkey{} & 218 & 107 & - & 281 \\
     Duktape & 0 & 4 & 4 & 1   \\
@@
     \midrule
-   \textbf{total} & 270 & 145 & 36 & 361 \\
+   \textbf{total} & 282 & 146 & 39 & 369 \\
     \bottomrule 
@@
 \end{wraptable}
+
+\Igor{
+  Os numeros da Tabela 5 correspondem ao numero de arquivos que falharam 
+  em test transplantation (nesse caso \failuresTestTransDistictFiles{}).
+  houveram \failuresTestTrans{} falhas que correspondem aos dados da Tabela 4.
+}
+
 Table~\ref{fig:piecharts-transplantation} shows the distribution of

### 2019-02-20 paper/paper.tex
tweak in 4.1

@@
 pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\Fix{cite}. The first net in the pipeline
-takes as input an arbitrary sentence and produces on output a
+classification problems~\cite{kusner2015word}. The first net in the
+pipeline takes as input an arbitrary sentence and produces on output a
 characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and the class for that attribute
-(\ie{}, ``(not) code'') and produces a yes/no answer, determining
-whether or not the input sentence was code. More in detail, for the
-first net, we used word2vec~\cite{kusner2015word}, a popular NLP
+pipeline takes that vector on input and produces a yes/no answer,
+determining whether or not the input sentence was code.  During the
+training phase, the second neural net in the pipeline takes
+additionaly on input the value for the class attribute for the sample;
+in this case, ``code'' or ``not code''. More in detail, for the first
+net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
 technique to produce word embeddings. A word embedding is a mapping of
 words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\Fix{cite} to infer the probability of the
-input belonging or not to the class. We classify as code an input for
-which the pipeline produces a probability of 0.7 or higher. We used a
-corpus with 25K samples of English paragraphs and 25K snippets of
-\js{} code and obtained a classifier with accuracy of 98\%. This
+multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
+infer the probability of the input belonging or not to the class. The
+classifier labels the input input as code if the predicted probability
+of the input being code is 0.7 or higher. We used a corpus with 25K
+samples of English paragraphs and 25K snippets of \js{} code to train
+and test the classifier and obtained an accuracy of 98\%. This
 classifier is publicly available from our website as a separate

### 2019-02-21 paper/paper.tex
related work + conclusions + spell checking

@@
 \emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In constrast
+eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
 to prior work on test set diversity, this paper explores diversity of
@@
 training phase, the second neural net in the pipeline takes
-additionaly on input the value for the class attribute for the sample;
+additionally on input the value for the class attribute for the sample;
 in this case, ``code'' or ``not code''. More in detail, for the first
@@
 \begin{wraptable}[12]{r}{0.23\textwidth}
-  \vspace{-1ex}
+  \vspace{-3ex}
   \small
@@
 
-\Igor{
-  Os numeros da Tabela 5 correspondem ao numero de arquivos que falharam 
-  em test transplantation (nesse caso \failuresTestTransDistictFiles{}).
-  houveram \failuresTestTrans{} falhas que correspondem aos dados da Tabela 4.
-}
+%% \Igor{
+%%   Os numeros da Tabela 5 correspondem ao numero de arquivos que falharam 
+%%   em test transplantation (nesse caso \failuresTestTransDistictFiles{}).
+%%   houveram \failuresTestTrans{} falhas que correspondem aos dados da Tabela 4.
+%% }
 
 Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). Considering false
+False Positives (FPs) and True Positives (TPs). The sum of the numbers
+in this table correspond to the number of files that manifested
+failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
 positives, ``Undefined Behavior'' was the most predominant
@@
 assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
+\CodeIn{To Number(a.valueOf())} that converts a string to a number,
 otherwise the operation returns NaN (Not a
@@
 opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty may be
-a promising avenue to explore. Recall that most of those warnings are
-false positives.  5)~We learned that reporting real bugs is a great
-way to train (and encourage) students in software testing. Students
-praised the experience of diagnosing failures, understanding part of
-the specs (as needed), writing bug reports, participating in
-discussions on issue trackers, and observing the change of
-status. That was a relatively self-contained hands-on activity that
-enabled students to engage in a real-life serious industrial project.
+techniques to prioritize the warnings more likely to be faulty (in the
+spirit of the work of Chen and
+colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
+avenue to explore. Recall that the rate of true positives of the
+techniques we studied is rather small.  5)~We learned that reporting
+real bugs is a great way to train (and encourage) students in software
+testing. Students praised the experience of diagnosing failures,
+understanding part of the specs (as needed), writing bug reports,
+participating in discussions on issue trackers, and observing the
+change of status. That was a relatively self-contained hands-on
+activity that enabled students to engage in a real-life serious
+industrial project.
 
@@
 Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can comprimise security
+different SSL/TLS implementations. Those bugs can compromise security
 of servers which rely on these certificates to properly authenticate
@@
 symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-and to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609}. All
-in all, it has shown to be flexible and effective for a wide range of
+to test disassemblers and binary
+lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
+and very recently to test JavaScript
+debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
+shown to be flexible and effective for a wide range of
 applications. Surprisingly, not much work has been done on
 differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepanices across different configurations of
+testing to look for discrepancies across different configurations of
 the same version of its \smonkey\ engine (using the ``compare\_jit''
@@
 contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical. \Fix{differential testing of debuggers...}
+contribution was empirical.
 
@@
 
-\Fix{
-although more research needs be done to automate
-parts of the inspection process (\eg{}, reduction of false alarms),}
+%% \Fix{
+%% although more research needs be done to automate
+%% parts of the inspection process (\eg{}, reduction of false alarms),}
 
@@
 Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs is
-challenging for similar reasons. We conducted a study to evaluate two
-simple diversity-aware techniques--test transplantation and
-cross-engine differential testing. The first technique runs test
-suites of a given engine in another engine. The second technique
-fuzzes existing inputs and then compares the output produced by
-different engines with a differential oracle.
-
-Overall, we reported \totalBugsReported\ bugs in this study. Of which,
-\totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to
-reduce cost of manual analysis, we found that both techniques we used
-are effective at finding bugs in
-\js\ engines. Section~\ref{sec:lessons} elaborates on the lessons
-learned from this study. The result data, infrastructure, and
-experimental scripts we prepared to run this study are available upon
-request. Future work includes mining test inputs from alternative
-sources (\eg{}, bug trackers) and predicting likelihood of false
-positives as to guide human effort on the most promising warnings
-first.
-
-\balance
-\bibliographystyle{ACM-Reference-Format}
+is intentionally incomplete and evolves frequently. Finding bugs in
+\js\ engines is challenging for similar reasons.
+
+This paper reports on a study to evaluate two diversity-aware
+techniques--test transplantation and cross-engine differential
+testing. The first technique explores diversity of test sources; it
+runs the test suite of one given engine in another engine. The second
+technique explores diversity of implementations; it fuzzes existing
+inputs and then compares the output produced by different engines with
+a differential oracle.
+
+We found that both techniques were very effective at finding bugs in
+\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
+study. Of which, \totalBugsConfirmed\ were confirmed by developers and
+\totalBugsFixed\ were fixed. Although more work is necessary to reduce
+cost of manual analysis, we found that our results provide strong
+evidence that exploring diversity should be encouraged to find
+functional bugs in JavaScript engines.
+
+In the near future, we plan to explore techniques to prioritize the
+warnings reported by these techniques and to continue involving
+students in the task of diagnosing these warnings. Using learning
+techniques for prioritization, similar to what Chen and
+colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
+warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
+seems a promising starting point for this improvement. The result
+data, infrastructure, and experimental scripts we prepared to run this
+study will be available upon request.
+
+\balance \bibliographystyle{ACM-Reference-Format}
 \bibliography{references,../docs/google-research-awards-latam/tmp}
@@
 
-%%  LocalWords:  formedness Embeddings NLP Convolutional dataset
+%%  LocalWords:  formedness Embeddings NLP Convolutional dataset DT
+%%  LocalWords:  JS JIT fuzzer jsfunfuzz jit funfuzz JavaScriptCore
+%%  LocalWords:  bytecodes JScript Ecma toPrecision Kangax JSVU cccrr
+%%  LocalWords:  WebKit ReferenceError TypeError drainMicrotasks sep
+%%  LocalWords:  lineNumber ccrrrr Duktape JSI js runtime NN arrowed
+%%  LocalWords:  embeddings perceptron toolchain fuzzers eshost cli
+%%  LocalWords:  pre ArrayBuffer RangeError ToIndex getInt byteOffset
+%%  LocalWords:  Clusterization SpiderMonkey DataView setInt Radamsa
+%%  LocalWords:  QuickFuzz Grammarinator LangFuzz Megadeth AFL RQ crr
+%%  LocalWords:  libFuzzer sanitizers subtrees conformant crrrr OME
+%%  LocalWords:  ome FP TP ccr FPs TPs crrrrr ccrr escapeinside NUL
+%%  LocalWords:  basicstyle boxpos numberstyle morekeywords assertEq
+%%  LocalWords:  typeof valueOf ascii unary NaN eval SyntaxError Yu
+%%  LocalWords:  iterable instanceof foofoofoo testcase SSL TLS SIMD
+%%  LocalWords:  Lidbury OpenCL GPUs Purdom parsers Lammel Shulte PHP
+%%  LocalWords:  Geno XPath combinatorial CSmith LLVM disassemblers
+%%  LocalWords:  Patra Pradel namespaces Eshkevari WordPress

### 2019-02-21 paper/paper.tex
pass on fuzzing

--- 2019-02-20 paper/paper.tex
@@
     \midrule
-    \radamsa{} & 137 & 47 & 323 & 21 & 483 \\
-    \quickfuzz{} & 81 & 62 & 349 & 13 & 369 \\
+    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
+    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
     \midrule
-    \textbf{total} & 218 & 109 & 672 & 34 & 852 \\
+    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
     \bottomrule
@@
     \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\
-    & Timeout/OME & 28 & 13 \\
-    & * Invalid Input & 39 & 48 \\    
-    & * Error Message Mismatch & 41 & 12 \\
+    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\ % 26 & 9 
+    & Timeout/OME & 28 & 13 \\ % 28 & 13
+    & * Invalid Input & 39 & 48 \\ % 39 & 48
+    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
     \midrule
-    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\
+    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
     & Bug & 12 & 6\\

### 2019-02-21 paper/paper.tex

--- 2019-02-21 paper/paper.tex
@@
     \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 9 \\
-    & Timeout/OME & 28 & 13 \\
-    & * Invalid Input & 39 & 48 \\    
-    & * Error Message Mismatch & 41 & 12 \\
+    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 13 \\ % 26 & 9 
+    & Timeout/OME & 28 & 13 \\ % 28 & 13
+    & * Invalid Input & 39 & 48 \\ % 39 & 48
+    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
     \midrule
-    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\
+    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
     & Bug & 12 & 6\\

### 2019-02-21 paper/paper.tex
pass on fuzzing

@@
     \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 26 & 13 \\ % 26 & 9 
-    & Timeout/OME & 28 & 13 \\ % 28 & 13
-    & * Invalid Input & 39 & 48 \\ % 39 & 48
+    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
+    & Timeout/OME & 30 & 15 \\ % 28 & 13
+    & * Invalid Input & 46 & 55 \\ % 39 & 48
     & * Error Message Mismatch & 41 & 12 \\ % 41 & 12

### 2019-02-21 paper/paper.tex
adding datarepo

@@
 confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. We made our testing infrastructure,
-results, and experimental scripts available to the public. (upon
-request for anonymity.)
+for diversity-aware testing. The scripts to run the experiments will
+be available upon request. The data is publicly available \dataRepo{}.
 
@@
 
+\noindent
+\textbf{Data Availability.}~The data, including the tests, warning
+reports, and diagnostic outcomes, is publicly available from a
+preserved repository \dataRepo.
+
 \section{Discussion}
@@
 
-This section discusses a selection of bugs reports. The selection
-criteria we used was: (i) to cover each engine that we found
-bugs--\chakra, \jsc, and \veight, (ii) to cover a different
-technique--test transplantation and differential testing (with
-\radamsa\ and with \quickfuzz), (iii) to cover a case of rejected bug
-report, and (iv) to use short test inputs (for space).
+This section discusses a sample of bugs reports. The selection
+criteria we used was: (i) to cover all engines we found bugs--\chakra,
+\jsc, and \veight, (ii) to cover each technique--test transplantation
+and differential testing (with \radamsa\ and with \quickfuzz), (iii)
+to cover a case of rejected bug report, and (iv) to use short tests
+(for space).
 
@@
 assertion, is equivalent to the operation
-\CodeIn{To Number(a.valueOf())} that converts a string to a number,
+\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
 otherwise the operation returns NaN (Not a
@@
 hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, in contrast, incorrectly converts the string
+as expected. \chakra{}, instead, incorrectly converts the string
 to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
@@
 warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement. The result
-data, infrastructure, and experimental scripts we prepared to run this
-study will be available upon request.
+seems a promising starting point for this improvement.
+
+The scripts to run the experiments for this study will be available
+upon request. The data is publicly available \dataRepo{}.
 

### 2019-02-21 paper/paper.tex
pass on diff
pass on intro

@@
 eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on test set diversity, this paper explores diversity of
-sources of test cases and diversity of implementations with the goal
-of finding bugs. Section~\ref{sec:related-work} elaborates related
-work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
-has been applied in a variety of contexts to find
+to prior work on this topic, this paper explores diversity of
+implementations and diversity of sources of test cases as opposed to
+diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
+elaborates related work on this topic. Differential
+Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
+contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of
-a given build of their \smonkey\ engine (\eg{}, trying to enable or
-not eager JIT compilation\footnote{These files are created with
-  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach is that
-it can be fully automated---as only one engine is used, the outcomes
-of the test in both configurations are expected to be identical. The
-Mozilla team uses this approach since 2002; they have been able to
-find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
-security bugs. Cross-engine differential testing, in contrast, has not
-been widely popularized. One possible reason is that it is still not
+example, Mozilla runs JS files against different configurations of a
+given build of their \smonkey\ engine (\eg{}, trying to enable or not
+eager JIT compilation\footnote{These files are created with the
+  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
+  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
+is that it can be fully automated---as only one engine is used, the
+outcomes of the test in both configurations are expected to be
+identical. The Mozilla team uses this approach since 2002; they have
+been able to find over 270 bugs since
+then~\cite{jsfunfuzz-at-mozilla}, including security
+bugs. Cross-engine differential testing, in contrast, has not been
+widely popularized. One possible reason is that it is still not
 practical to fully automate the technique. In contrast to other
@@
 been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding
-bugs on \javascript\ engines.
+to assess the ability of the techniques aforementioned in finding bugs
+on \javascript\ engines.
 
@@
 
-\emph{Results.}~We considered the following engines--Apple, Google,
-Microsoft, and Mozilla. Figure~\ref{fig:summary} shows the breakdown
-of bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Additionally, each stacked bar breaks
-down the bugs per status (\eg{}, ``1-New''). The prefix number
-indicates the ordering that status labels are assigned. Note that
-several of these reports have the label ``3-Fixed'', indicating that
-bug fixes have been incorporated into the code already. Note that most
-of these bugs affected two engines--Microsoft's \chakra{} and Apple's
-JavaScriptCore (\jsc{}).  We reported \noBugsBugsReportedGoogle{} bugs in Google
-\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
-Mozilla's \smonkey{}.  Furthermore, our results show that both
-techniques revealed several bugs, most of which confirmed by
-developers. Test transplantation revealed \noBugsTransplantation{}
-bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
+\sloppy \emph{Results.}~We considered the following engines--\chakra{}
+(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
+\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
+bug reports per engine (\ref{fig:stacked-engine}) and per technique
+(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
+per status (\eg{}, ``1-New''). The prefix number indicates the
+ordering that status labels are assigned. Note that several of these
+reports have the label ``3-Fixed'', indicating that bug fixes have
+been incorporated into the code already. Note that most of these bugs
+affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
+reported \noBugsBugsReportedGoogle{} bugs in \veight{}
+(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
+Furthermore, our results show that both techniques revealed several
+bugs, most of which confirmed by developers. Test transplantation
+revealed \noBugsTransplantation{} bugs (of which,
+\noBugsTransplantationConfirmed{} were confirmed and
 \noBugsTransplantationFixed{} were fixed) whereas differential testing
@@
 number of bug reports were similar, if we consider only those
-confirmed or fixed. Considering cost per bug found, we found that test
-transplantation, compared to differential testing, demanded less
-effort from the developers who inspected the alarms. Most bugs
-we found are of moderate severity.
+confirmed or fixed. Most bugs we found are of moderate severity.
+
+%% Considering cost per bug found, we found that test
+%% transplantation, compared to differential testing, demanded less
+%% effort from the developers who inspected the alarms.
 
@@
     \midrule
-    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
-    & Bug & 12 & 6\\
+    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
+    & Bug & 15 & 7\\
     \bottomrule     
@@
 
-\subsection{Diversity in Testing}
+\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
 The idea of test set diversity dates back to the

### 2019-02-21 paper/paper.tex
final pass

@@
 
-\emph{Key Findings.}~1) Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 2) Even for problems with fairly clear
-specifications, as in \javascript{}, there is likely to be (a lot of)
-variation between different implementations. 3) Differential testing
-is feasible on real, complex, widely used pieces of
+\emph{Key Findings.}~The list of findings of this work includes--1)
+Not only multiple different implementations can be leveraged in
+differential testing, but differences in test suites can also be
+important. 2) Even for problems with fairly clear specifications, as
+in \javascript{}, there is likely to be (a lot of) variation between
+different implementations. 3) Differential testing is feasible on
+real, complex, widely used pieces of
 software. Section~\ref{sec:lessons} expands and elaborates key
@@
 
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, the identifier
-of an engine, the exception it raises, and the message it produces on
-a ``\lo'' warning.  This sequence of engine id, exception, and error
-message triples defines a warning signature that we use for
-clustering. It is worth mentioning that we filter references to code
-in messages as to increase ability to aggregate warnings from
-different test sources. Any warnings, including this one, that has
-this same signature will be included in the same
+Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
+three elements that we use to characterize a warning--1) the
+identifier of an engine, 2) the exception it raises, and 3) the
+message it produces on a ``\lo'' warning.  This sequence of triples
+defines a warning signature that we use for clustering. It is worth
+mentioning that we filter references to code in messages as to
+increase ability to aggregate warnings. Any warnings, including this
+one, that has this same signature will be included in the same
 ``bucket''. Considering the example from
@@
       non-negligible, the approach revealed several non-trivial bugs
-      in widely popular engines.
+      in three of the four engines we analyzed.
       \end{minipage}
@@
 \begin{figure}[h!]
+  \vspace{-1ex}
   \centering
@@
   %% \label{fig:hi-priority}
+  \vspace{-1ex}  
 \end{figure}
@@
 \begin{figure}[h!]
+  \vspace{-0.5ex}  
   \centering
@@
 Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often, manifest
-themselves in regular patterns across the input
+the continuity assumption. They found that faults, most often,
+manifest themselves in regular patterns across the input
 domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
@@
 paper explores diversity of sources of test cases and diversity of
-engines to test and find bugs. We remain to investigate the diversity
-of test cases themselves. In principle, that could help reduce the
-number of alarms to inspect, for example.
+engine implementations. We remain to investigate the diversity of test
+cases themselves. In principle, that could help reduce the number of
+alarms to inspect, for example.
 
@@
 
-JavaScript is a very popular language. For that reason, bugs in engine
+JavaScript (\js{}) is very popular today. Bugs in engine
 implementations often affect lots of people and organizations.
@@
 This paper reports on a study to evaluate two diversity-aware
-techniques--test transplantation and cross-engine differential
-testing. The first technique explores diversity of test sources; it
-runs the test suite of one given engine in another engine. The second
-technique explores diversity of implementations; it fuzzes existing
-inputs and then compares the output produced by different engines with
-a differential oracle.
+techniques for finding bugs in \js{}--test transplantation and
+cross-engine differential testing. The first technique explores
+diversity of test sources; it runs the test suite of one given engine
+in another engine. The second technique explores diversity of
+implementations; it fuzzes existing inputs and then compares the
+output produced by different engines with a differential oracle.
 

### 2019-06-20 paper/paper.tex
JSS format

@@
-\documentclass[sigconf,review, anonymous]{acmart}
-
-\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis}
-
+\documentclass[final,5p,times,twocolumn]{elsarticle}
+\biboptions{numbers,sort&compress}
+%\documentclass[sigconf,review, anonymous]{acmart}
+%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
 %\input{packages}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Comment the \draftmodetrue line before submission
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newif\ifdraftmode
+\draftmodetrue
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Uncomment \showsplattexttrue to show text from our splat paper
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newif\ifshowsplattext
+%\showsplattexttrue
+
+\pagenumbering{arabic}
 
@@
 \usepackage{enumitem}
+\usepackage{url}
 
@@
 
-% Copyright
-%\setcopyright{none}
-\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-\acmDOI{10.475/123_4}
-
-% ISBN
-\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ESEC/FSE 2019]{The 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{26--30 August, 2019}{Tallinn, Estonia}
-\acmYear{1997}
-\copyrightyear{2016}
-
-\acmArticle{4}
-\acmPrice{15.00}
-
-% These commands are optional
-%\acmBooktitle{Transactions of the ACM Woodstock conference}
-\editor{Jennifer B. Sartor}
-\editor{Theo D'Hondt}
-\editor{Wolfgang De Meuter}
-
 \begin{document}
@@
 \title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-%% \titlenote{Produces the permission block, and
-%%   copyright information}
-%% \subtitle{Extended Abstract}
-%% \subtitlenote{The full version of the author's guide is available as
-%%   \texttt{acmart.pdf} document}
-
-%mf: the following follow acm format and prevents to have superscripts in the header of every page
-\settopmatter{authorsperrow=4}
-
-\author{Igor Lima}
-%\authornote{Dr.~Trovato insisted his name be first.}
-\orcid{1234-5678-9012}
-\affiliation{%
-  \institution{Federal University of Pernambuco}
-  \streetaddress{P.O. Box 1212}
-  \city{Recife}
-  \state{PE}
-  \country{Brazil}
-%  \postcode{43017-6221}
-}
-\email{isol2@cin.ufpe.br}
-
-\author{Marcelo d'Amorim}
-\orcid{/0000-0002-1323-8769}
-\affiliation{%
-  \institution{Federal University of Pernambuco}
-  \streetaddress{P.O. Box 1212}
-  \city{Recife}
-  \state{PE}
-  \country{Brazil}
-%  \postcode{43017-6221}
-}
-\email{damorim@cin.ufpe.br}
-
-% The default list of authors is too long for headers.
-\renewcommand{\shortauthors}{Lima and d'Amorim}
+
+\author[ufpe]{Igor Lima}
+\ead{isol2@cin.ufpe.br}
+\author[ufpe]{Breno Miranda}
+\ead{bafm@cin.ufpe.br}
+\author[ufpe]{Marcelo d'Amorim}
+\ead{damorim@cin.ufpe.br}
+\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
+
+%\renewcommand{\shortauthors}{Lima et al.}
 
@@
 \end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below.
-%
-%% \begin{CCSXML}
-%% <ccs2012>
-%% <concept>
-%% <concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
-%% <concept_desc>Software and its engineering~Software testing and debugging</concept_desc>
-%% <concept_significance>500</concept_significance>
-%% </concept>
-%% </ccs2012>
-%% \end{CCSXML}
-
-%% \ccsdesc[500]{Software and its engineering~Software testing and debugging}
-
-%% \keywords{JavaScript, Diversity, Software Testing}
 
@@
 The goal of this paper is to assess ability of techniques that
-leverage data and implementation diversity on to find functional bugs
+leverage diversity to find functional bugs
 in \javascript\ engines. Based on that, we pose three questions:
@@
 we used the same version in this
-experiment~\cite{ecma262-conformance-suite}. Results show that there
-\begin{wraptable}[10]{r}{0.22\textwidth}
-%  \vspace{-2ex}      
+experiment~\cite{ecma262-conformance-suite}.
+
+\begin{wraptable}[8]{r}{0.22\textwidth}
+  \vspace{-4ex}
   \centering
@@
     the Test262 conformance suite.}
-  \vspace{-2ex}        
   \small
@@
   \normalsize
-  \vspace{-4ex}
 \end{wraptable}
-are still many unsupported scenarios as can be observed from the
+
+Results show that there are still many unsupported scenarios as can be observed from the
 percentages in the table. The number of passing tests is high and
@@
 the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors carefully
-inspected the scenario and, if agreed on the classification, reported
-the bug on the issue tracker of the affected engine.
-
-%If not, re-classified the failure as a false alarm.
-
-%\vspace{0.5ex}
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from Table~\ref{tab:test-suites}. Running those
-tests we observed a total of \failuresTestTrans{} failures manifested across 
-\failuresTestTransDistictFiles{} distinct files (\failuresTestTransPercent{} of total). 
-Table~\ref{tab:cross-testing} shows
-that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, perhaps as expected,
-considering that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%% This suggests that the investiment in
-%% testing paid off in this case.
+potentially fault-revealing cases, one of the authors inspected the
+scenario and, if agreed on the classification, reported the bug to the
+issue tracker of the affected engine.
+
 \begin{table}[t]
@@
 
+\subsubsection{Results}
+\label{sec:results}
+
+Table~\ref{tab:cross-testing} shows the number of failures observed
+for each pair of test suite and engine. The first column shows the
+test suites and the first row shows the engines that run those
+tests. We use a dash (``-'') to indicate that we did not consider the
+combinations that associate a test suite with its parent engine;
+failures in those cases would either indicate regressions or flaky
+tests as opposed to unknown bugs for that engine. As explained in
+Section~\ref{sec:seeds}, we used in this experiment the
+\totalTestFilesForTestTransplantation{} tests included in the
+rectangle area under column ``type-in-all'' from
+Table~\ref{tab:test-suites}. Running those tests we observed a total
+of \failuresTestTrans{} failures manifested across
+\failuresTestTransDistictFiles{} distinct files
+(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
+shows that \smonkey\ was the engine that failed the least whereas
+\chakra\ was the engine that failed the most. The \smonkey\ test suite
+also revealed more failures than any other, as expected, given
+that it is the suite with more tests (see
+Table~\ref{tab:test-suites}).
+
 %%  As another example, some tests from \Fix{Y} use the
@@
 unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example, we found
-cases where the test (or its harness) fails in an assertion because of
-an undefined property.}
-\textbf{Other.} This category includes other sources. For example, it
-includes the cases where the test was valid for some previous version
-of the spec but is no longer valid for the current spec.
-
-\begin{wraptable}[12]{r}{0.23\textwidth}
-  \vspace{-3ex}
+\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
+  we found cases where the test (or its harness) fails in an assertion
+  because of an undefined property.}  \textbf{Other.} This category
+includes other sources of false positives. For example, it includes
+the cases where the test was valid for some previous version of the
+spec but is no longer valid for the current spec.
+
+\begin{wraptable}[11]{r}{0.23\textwidth}
+  \vspace{-4ex}
   \small
@@
 
-%% \Igor{
-%%   Os numeros da Tabela 5 correspondem ao numero de arquivos que falharam 
-%%   em test transplantation (nesse caso \failuresTestTransDistictFiles{}).
-%%   houveram \failuresTestTrans{} falhas que correspondem aos dados da Tabela 4.
-%% }
-
 Table~\ref{fig:piecharts-transplantation} shows the distribution of
@@
 automate the detection of duplicates.
-
-%% ``Url'' shows the URL
-%% (de-anonymized upon request) for the bug report entry in the
-%% corresponding bug-tracking system, column
 
@@
 
-\vspace{0.5ex}
-\lbrack{}Exploratory Phase.\rbrack{} For the first three months of the
-study, our inspection process was exploratory.  In this phase, we
-wanted to learn whether or not black-box fuzzers could reveal real
-bugs and how effective was the \hi{}-\lo\ warning classification.  We
-expected the number of warnings to increase dramatically compared to
-the previous experiment and, if we realized that the ratio of bugs
-from \lo\ warnings was rather low, we could focus our inspection
-efforts on \hi\ warnings. To run this experiment, we trained eight
-students in analyzing the warnings that our infrastructure
-produces. The students were enrolled in a graduate-level testing
-class. We listed warnings in a spreadsheet and requested the students
-to update an ``owner'' column indicating who was working on it, but we
-did not enforce a strict order on the warnings the students should
-inspect. Recall from Section~\ref{sec:clusterization} that we
-clustered \lo\ warnings in buckets. For that reason, we only listed
-one \lo\ warning per representative class/bucket in the
-spreadsheet. First, we explained, through examples, the possible
-sources of false alarms they could find and then we asked the students
-to use the following procedure when finding a suspicious
-warning. Analyze the parts of the spec related to the problem and, if
-still suspicious, look for potential duplicates on the bug tracker of
-the affected engine using related keywords. If none was reported,
-indicate in the spreadsheet that that warning is potentially
-fault-revealing. We encouraged students to use lithium~\cite{lithium}
-to minimize long test cases\Comment{; the tests from the Mozilla suite are
-often longer than others}. Only after the co-authors reviewed the
-diagnosis, a bug report was filed. Each student found at least one bug
-using this methodology.
+\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
+three months of the study, our inspection process was exploratory.  In
+this phase, we wanted to learn whether or not black-box fuzzers could
+reveal real bugs and how effective was the \hi{}-\lo\ warning
+classification.  We expected the number of warnings to increase
+dramatically compared to the previous experiment and, if we realized
+that the ratio of bugs from \lo\ warnings was rather low, we could
+focus our inspection efforts on \hi\ warnings. To run this experiment,
+we trained eight students in analyzing the warnings that our
+infrastructure produces. The students were enrolled in a
+graduate-level testing class. We listed warnings in a spreadsheet and
+requested the students to update an ``owner'' column indicating who
+was working on it, but we did not enforce a strict order on the
+warnings the students should inspect. Recall from
+Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
+buckets. For that reason, we only listed one \lo\ warning per
+representative class/bucket in the spreadsheet. First, we explained,
+through examples, the possible sources of false alarms they could find
+and then we asked the students to use the following procedure when
+finding a suspicious warning. Analyze the parts of the spec related to
+the problem and, if still suspicious, look for potential duplicates on
+the bug tracker of the affected engine using related keywords. If none
+was reported, indicate in the spreadsheet that that warning is
+potentially fault-revealing. We encouraged students to use
+lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
+  from the Mozilla suite are often longer than others}. A bug report
+was filed only after one of the authors reviewed the diagnosis. Each
+student found at least one bug using this methodology.
 
@@
 bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Severity''), the priority
+(``Url'')}, the severity of the bug report (``Sev.''), the priority
 that we assigned to the warning that revealed the bug (``Priority''),
@@
 of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. Considering \veight{}, 
+were duplicates and were not reported. For \veight{}, 
 we reported \noDiffVeight{} bugs, 
-all of them were confirmed, with \noDiffVeightFixed{} fixed.
+all of them confirmed, with \noDiffVeightFixed{} fixed.
 
@@
 
-\balance \bibliographystyle{ACM-Reference-Format}
+\vspace{1ex}
+\noindent\textbf{Acknowledgments.~}Igor was supported by the FACEPE
+fellowship \Fix{...}  This research was partially funded by INES 2.0,
+FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17, and CNPq
+grant 465614/2014-0.
+
+\balance
+\bibliographystyle{elsarticle-num}
 \bibliography{references,../docs/google-research-awards-latam/tmp}
@@
 \end{document}
-
-%%  LocalWords:  formedness Embeddings NLP Convolutional dataset DT
-%%  LocalWords:  JS JIT fuzzer jsfunfuzz jit funfuzz JavaScriptCore
-%%  LocalWords:  bytecodes JScript Ecma toPrecision Kangax JSVU cccrr
-%%  LocalWords:  WebKit ReferenceError TypeError drainMicrotasks sep
-%%  LocalWords:  lineNumber ccrrrr Duktape JSI js runtime NN arrowed
-%%  LocalWords:  embeddings perceptron toolchain fuzzers eshost cli
-%%  LocalWords:  pre ArrayBuffer RangeError ToIndex getInt byteOffset
-%%  LocalWords:  Clusterization SpiderMonkey DataView setInt Radamsa
-%%  LocalWords:  QuickFuzz Grammarinator LangFuzz Megadeth AFL RQ crr
-%%  LocalWords:  libFuzzer sanitizers subtrees conformant crrrr OME
-%%  LocalWords:  ome FP TP ccr FPs TPs crrrrr ccrr escapeinside NUL
-%%  LocalWords:  basicstyle boxpos numberstyle morekeywords assertEq
-%%  LocalWords:  typeof valueOf ascii unary NaN eval SyntaxError Yu
-%%  LocalWords:  iterable instanceof foofoofoo testcase SSL TLS SIMD
-%%  LocalWords:  Lidbury OpenCL GPUs Purdom parsers Lammel Shulte PHP
-%%  LocalWords:  Geno XPath combinatorial CSmith LLVM disassemblers
-%%  LocalWords:  Patra Pradel namespaces Eshkevari WordPress

### 2019-06-20 paper/abstract.tex
pass on abstract and intro
pass on paper

@@
 
-%reports on a study we ran to 
+\sloppy
 This paper evaluates the importance of
 diversity to find functional bugs in JavaScript engines. For that, we
-explored two simple diversity-aware techniques---test transplantation and
+explored two existing diversity-aware techniques---test transplantation and
 cross-engine differential testing. The first technique runs test
@@
 different engines with a differential oracle.
-
-\sloppy
 We considered engines from four major players in our
@@
 finding bugs in complex software, such as JavaScript engines.
-
-%% Although more research needs to be done to optimizie 
-%% warning triaging,
-
-%% ; we found
-%% only \Fix{one} bug in Google \veight{} and none in Mozilla's
-%% \smonkey{}

### 2019-06-20 paper/paper.tex
pass on paper

@@
 
+%% avoid footnotes across pages
+\interfootnotelinepenalty=10000
+%\raggedbottom
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%% paragraphs within margins
+\usepackage[english]{babel}
+\setlength{\emergencystretch}{2pt}
 \usepackage{booktabs}
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum, variations of these ideas have
+~\ref{tab:false-positives}). To sum up, variations of these ideas have
 been explored before in different contexts.  The goal of the paper is
@@
 
-\vspace{1ex} To sum, this paper provides initial, yet strong evidence
+\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
 that exploring diversity should be encouraged to find functional bugs
@@
 to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum, a high percentage of inputs
+reflected very simple scenarios. To sum up, a high percentage of inputs
 that Grammarinator and Megadeth generated were semantically-invalid
@@
 mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace subtrees of the syntax
+of the \js\ syntax; it is able to replace sub-trees of the syntax
 tree~\cite{grieco2016quickfuzz} with trees created anew.
@@
 \vspace{1ex}
-\noindent\textbf{Acknowledgments.~}Igor was supported by the FACEPE
-fellowship \Fix{...}  This research was partially funded by INES 2.0,
-FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17, and CNPq
-grant 465614/2014-0.
+\sloppy
+\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
+fellowship IBPG-0123-1.03/17. This research was partially funded by
+INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
+and CNPq grant 465614/2014-0.
 
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{references,../docs/google-research-awards-latam/tmp}
+\bibliography{references,tmp}
 
 \end{document}
+
+%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
+%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
+%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
+%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
+%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
+%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
+%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
+%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
+%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2019-06-21 paper/paper.tex
minor changes in intro

@@
 \item \emph{Test transplantation} leverages diversity of test
-  cases. It evaluates the effects that running test files from a given
-  engine have in detecting bugs in other engines. The intuition is
-  that developers design test cases with different objectives in
-  mind. As such, replaying these tests in different engines could
-  reveal unanticipated problems.
+  cases. This technique evaluates the effect of running test files
+  written for a given engine in other engines. The intuition is that
+  developers design test cases with different objectives in mind. As
+  such, replaying these tests in different engines could reveal
+  unanticipated problems.
 
 \item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. More precisely, it fuzzes existing test
+  engine implementations. This technique fuzzes existing test
   inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines using a differential oracle. The
-  intuition is that similar inputs to those already tested may reveal
-  problems.
+  produced by different engines.\Comment{ using a differential
+    oracle.} The intuition is that interesting inputs can be created
+  from existing inputs and multiple engines can be used to address the
+  lack of oracles.
 \end{itemize}
@@
 the impact of false positives, which can arise in both testing
-scenarios, on the practicality of the approach.
+scenarios, on their practicality.
 

### 2019-06-21 paper/abstract.tex
minor

@@
 most of these bugs affected two engines--Apple's
-\jsc{} and Microsoft's \chakra{}. To sum, our results show that
+\jsc{} and Microsoft's \chakra{}. To summarize, our results show that
 diversity-aware techniques are easy to apply and very effective in

### 2019-06-21 paper/abstract.tex
structured abstract

@@
-JavaScript is a very popular programming language today with several
+\textbf{Context.} JavaScript is a very popular programming language today with several
 implementations competing for market dominance. Although a
@@
 incomplete and evolves frequently.
-
-\sloppy
-This paper evaluates the importance of
-diversity to find functional bugs in JavaScript engines. For that, we
+\textbf{Objective.} This paper evaluates the importance of
+diversity to find functional bugs in JavaScript engines. \textbf{Method.} For that, we
 explored two existing diversity-aware techniques---test transplantation and
@@
 different engines with a differential oracle.
-We considered engines from four major players in our
+\textbf{Results.} We considered engines from four major players in our
 experiments--Apple, Google, Microsoft, and Mozilla. Our results

### 2019-06-25 paper/paper.tex
preparing JSS submission

@@
 
-Our study measures the ability of these techniques in finding bugs and
-the impact of false positives, which can arise in both testing
-scenarios, on their practicality.
+The study measures the ability of these techniques in finding bugs and
+the impact of false positives on their practicality.
 
@@
 produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As mentioned
-previously, all those aspects make testing \js\ engines more
-challenging.
+cases should not manifest this kind of flaky behavior.  As previously
+mentioned, all those aspects make testing \js\ engines challenging.
 

### 2019-09-27 paper/paper.tex
SQJ version

@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
+%\documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[smallextended]{svjour3}
+%\biboptions{numbers,sort&compress}
 %\documentclass[sigconf,review, anonymous]{acmart}
@@
 
+\journalname{Software Quality Journal}
+
 \begin{document}
@@
 \title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
+%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head
+
+\author{Igor Lima \and Breno Miranda \and Marcelo d'Amorim}
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{Igor Lima \and \email{isol2@cin.ufpe.br} \\
+Breno Miranda \and \email{bafm@cin.ufpe.br} \\
+Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
+\at Universidade Federal de Pernambuco, Recife, PE, Brazil}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
 
 %\renewcommand{\shortauthors}{Lima et al.}
+
+\maketitle
 
@@
   \input{abstract}
+  \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
 \end{abstract}
-
-\maketitle
 
@@
 %% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
+This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
 to find bugs in JavaScript engines; it covers two complementary
@@
 \emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
+eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
 to prior work on this topic, this paper explores diversity of
@@
   \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
     \vspace{-5ex}
@@
   \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
+    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
     \vspace{-5ex}        
@@
 per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
+ordering that status labels are assigned. Several of these
 reports have the label ``3-Fixed'', indicating that bug fixes have
@@
 %% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
+\emph{Contributions.}~The most important contribution of this work is empirical: 
+we provide a comprehensive study analyzing the effectiveness of diversity-aware
 techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
+Additional contributions are:
+1)~A number of bugs found and fixed. 
+We reported a total of \totalBugsReported{} bugs. 
+Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
+2)~An infrastructure for diversity-aware testing.
+The scripts to run the experiments will be available upon request. 
+The data is publicly available \dataRepo{}.
 
@@
   \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \includegraphics[trim=0 350 0 0,clip,width=1.0\textwidth]{diff-testing-runtimes}
   \vspace{-5ex}  
@@
 
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
+\begin{table}
+  %\vspace{-4ex}
   \centering
@@
     the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
+  %\small
+  \begin{tabular}{rr}
     \toprule
@@
   \end{tabular}
-  \normalsize
-\end{wraptable}
+  %\normalsize
+\end{table}
 
@@
 
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
+\begin{table}
   \centering
@@
     of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
+  %\setlength{\tabcolsep}{3pt}      
   \renewcommand*{\arraystretch}{0.9}
@@
   \end{tabular}
-\end{wraptable}
+\end{table}
 
@@
 The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
+eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
 assumption behind test set diversity is that faults often spread
@@
 \balance
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
+\bibliographystyle{spmpsci}
 \bibliography{references,tmp}

### 2019-12-03 paper/paper.tex

@@
 
-\author{Igor Lima \and Breno Miranda \and Marcelo d'Amorim}
+\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
 %\authorrunning{Short form of author list} % if too long for running head
 
-\institute{Igor Lima \and \email{isol2@cin.ufpe.br} \\
+\institute{
+* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
+Igor Lima \and \email{isol2@cin.ufpe.br} \\
 Breno Miranda \and \email{bafm@cin.ufpe.br} \\
@@
 % The correct dates will be entered by the editor
+
+%\institute{Corresponding author.}
 

### 2020-01-06 msc-thesis/appendix/JAVA/dde.tex
added msc-thesis

% % ----------------------------------------------------------
\chapter{Código Java do DDE2}
\label{sec:dde2java}
% % ----------------------------------------------------------

\begin{lstlisting}[caption={Código em linguagem de programação Java do DDE2},label=dde2java]

/*
 *    DDE.java
 *    Copyright (C) 2015 Maciel, Santos, Barros 
 *    @authors Bruno I. F. Maciel (bifm@cin.ufpe.br)
 *    			Silas Garrido T. de Carvalho Santos (sgtcs@cin.ufpe.br)
 *             	Roberto S. M. Barros (roberto@cin.ufpe.br) 
 *             
 *    @version $Version: 1 $
 *
 *    This program is free software; you can redistribute it and/or modify
 *    it under the terms of the GNU General Public License as published by
 *    the Free Software Foundation; either version 3 of the License, or
 *    (at your option) any later version.
 *
 *    This program is distributed in the hope that it will be useful,
 *    but WITHOUT ANY WARRANTY; without even the implied warranty of
 *    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
 *    GNU General Public License for more details.
 *
 *    You should have received a copy of the GNU General Public License
 *    along with this program. If not, see <http://www.gnu.org/licenses/>.
 */

/**
 * Drift Detection Ensemble (DDE),
 * published as:
 * <p> Bruno I. F. Maciel, Silas Garrido T. C. Santos and Roberto S. M. Barros: 
 *     A Lightweight Concept Drift Detection Ensemble. 
 *     27th IEEE International Conference on Tools with Artificial Intelligence 
 *     (ICTAI) Vietri sul Mare, Italy, November 9-11, 2015</p>
 */

package moa.classifiers.drift;

import moa.classifiers.meta.WEKAClassifier;
import java.util.LinkedList;
import java.util.List;
import moa.classifiers.AbstractClassifier;
import moa.classifiers.Classifier;
import moa.classifiers.core.driftdetection.ChangeDetector;
import moa.core.Measurement;
import moa.options.ClassOption;
import moa.options.IntOption;
import weka.core.Instance;
import weka.core.Utils;

public class DDE2 extends AbstractClassifier  {
    private static final long serialVersionUID = 1L;

    public double[] getVotesForInstance(Instance inst) {
        return this.classifier.getVotesForInstance(inst);
    }

    @Override
    public boolean isRandomizable() {
        return true;
    }

    @Override
    public void getModelDescription(StringBuilder out, int indent) {
        ((AbstractClassifier) this.classifier).getModelDescription(out, indent);
    }

    @Override
    protected Measurement[] getModelMeasurementsImpl() {
        List<Measurement> measurementList = new LinkedList<Measurement>();
        measurementList.add(new Measurement("Change detected", this.changeDetected));
        measurementList.add(new Measurement("Warning detected", this.warningDetected));
        Measurement[] modelMeasurements = ((AbstractClassifier) this.classifier).getModelMeasurements();
        if (modelMeasurements != null) {
            for (Measurement measurement : modelMeasurements) {
                measurementList.add(measurement);
            }
        }
        this.changeDetected = 0;
        this.warningDetected = 0;
        return measurementList.toArray(new Measurement[measurementList.size()]);
    }}

\end{lstlisting}

### 2020-01-06 msc-thesis/chapter/background.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
+\chapter{Background}
 
@@
 
-JavaScript engines are virtual machines that parse source code,
+\js{} engines are virtual machines that parse source code,
 compile it in bytecodes, and run these bytecodes. These engines
@@
 A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
+in this work. For that reason, we looked for \js\ files from various
 sources: 1) test files from the Test262~\cite{tc39-github} conformance
@@
   \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
+  \caption{\label{tab:test-suites}Number of test files.}
+    % Dashed rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
+    % shows the tests used for test transplantation (resp., cross-engine differential testing).
+    \setlength{\tabcolsep}{2pt}
   \begin{tabular}{ccrrrr}
@@
     \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
+    Test262 & \href{\repoEcma{}}{GitHub} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
     \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
+    \jsc{} & \href{\repoJSC{}}{GitHub} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
+    \smonkey\ & \href{\repoSM{}}{GitHub} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
+    \veight{} & \href{\repoVeight{}}{GitHub} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
     \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
+    Duktape & \href{\repoDuktape{}}{GitHub} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
+    \jerry{} & \href{\repoJerry{}}{GitHub} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
+    JSI & \href{\repoJSI{}}{GitHub} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
+    Tiny-js & \href{\repoTinyJS{}}{GitHub} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
     \midrule
@@
 support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
+required a Node.js runtime~\footnote{The official NodeJS website. Available at \url{https://nodejs.org}}
+for execution. Also, we did not
 consider tests from the \chakra{} repository because they depend on
@@
 To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
+visit the issue trackers of \veight{} and \smonkey{} listed in
 Table~\ref{tab:engines} and we were able to retrieve a total of
@@
 
+\Igor{R1 comentou sobre este passo, se eh necessario ou nao. Dado que 
+a nossa infraestrutura ignora arquivos invalidos. Aqui ainda nao foi citado
+como a infraestrutura foi implementada.
+}
 For the classification of ``code'' vs. ``not code'', we used a
@@
 additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
+in this case, ``code'' or ``not code''. 
+\Igor{
+  * Aqui ainda nao foi citado como a infraestrutura foi implementada.
+  This step is required to reduce the corpus of invalid entries for our infrastructure,
+  as we are fuzzing those entries and testing on each engine,
+  consequently spending unnecessary time. We decided to use this approach to increase
+  the efficiency of the proposed tool with valid inputs.
+}
+
+More in detail, for the first
 net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
 technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
+words to vectors of real numbers. 
+\Igor{We chose the Word2Vec technique to extract context information of
+each JS token or english word. Since the dictionary of a programming language
+is shorten than english natural language, we could identify similarity
+between JS keywords thought the distance vector in the embedding matrix.}
+For the second net, we used a
 multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
@@
   \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
+  \includegraphics[trim=0 350 150 0,clip,width=1.0\textwidth]{diff-testing-runtimes}
   \vspace{-5ex}
@@
 \end{figure}
-
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrates the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Numbered boxes in the figure denote the
-data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
-input. Otherwise, it considers the input as potentially
-fault-revealing; hence, interesting for human inspection. Finally, to
-facilitate the human inspection process, the infrastructure
-prioritizes warnings and clusters them in groups (step 3). We describe
-these features in Sections~\ref{sec:prioritization} and
-\ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
-Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
-earlier, this justifies why differential testing is challenging to
-automate at the functional level.
-
-For step 2, we considered using the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
-
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
-\subsection{Prioritization}
-\label{sec:prioritization}
-
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-likely to be a ``bug'' in the test code as opposed to a bug in the
-engine. Recall that, for differential testing, we only use seed tests
-that pass in all engines.
-
-Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
-Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
-example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case from the
-function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
-engine did not throw any exception, as can be confirmed from the
-report that our infrastructure produces starting with text ``Engine
-Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
-
-Clusterization is complementary to prioritization; it helps to group
-similar warnings reported by our infrastructure. We only clustered
-``\lo'' warnings as ``\hi'' warnings produce messages that arise from
-the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
-three elements that we use to characterize a warning--1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\subsection{Fuzzers}
-\label{sec:objects:fuzzers}
-
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
-grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz},
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
-Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. Another fundamental issue associated with
-generational fuzzers in our context is that the tests they produce do
-not contain assertions; to enable the integration of this kind of
-fuzzers in our infrastructure---we would need to look for
-discrepancies across compiler error messages as opposed to assertion
-violations.  All in all, although grammar-based fuzzers have been
-shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
-fuzzers in this study for the reasons above.
-
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
-properties\footnote{There are options in the clang toolchain to build
-  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
-  provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
-
-We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
-existing inputs randomly. The strength of the approach is
-limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose these specific fuzzers
-because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Results}
-\label{sec:results}
-
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
-\begin{description}[leftmargin=.5in]
-\item[RQ1.] How conformant are the engines to the Test262 suite?
-\item[RQ2.] How effective is test transplantation to find bugs?
-\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
-\end{description}
-
-The first question focuses on the conformance of our selected engines
-to the official Test262 suite~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. The second question
-focuses on the effectiveness of test transplantation
-(Section~\ref{sec:transplantation}). The rationale for using inputs
-from different engines is that developers consider different goals
-when writing tests---suites written for a given engine may cover
-scenarios not covered by a different engine. The third question
-evaluates the effectiveness of cross-engine differential testing to
-find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
-
-\subsection{Answering RQ1 (Conformance)}
-\label{sec:stability}
-
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
-check conformance of engines to the \js\ standard. It is
-acceptable to release engines fulfilling the specification only
-partially~\cite{kangax}. We expect that the pass rate on this suite
-provide some indication of the engine's maturity. In the limit, it is
-not desirable to flood bug reports on engines at early stages of
-development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}.
-
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
-  \centering
-  \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
-    \toprule
-    engine & \% passing \\
-    \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
-    \chakra{} & \percentSuiteTestChakra{} \\    
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \bottomrule
-  \end{tabular}
-  \normalsize
-\end{wraptable}
-
-Results show that there are still many unsupported scenarios as can be observed from the
-percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
-Figure~\ref{fig:summary}). Although it is plausible to find
-correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
-to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
-      engines is above 90\%.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ2 (Test Transplantation)}
-\label{sec:transplantation}
-
-This section reports results of test transplantation. More
-specifically, we analyzed the failures observed when running a test
-suite original from a given engine in another engine. Intuitively, we
-want to assess how effective is the idea of cross-fertilization of
-testing knowledge among \js\ developers.
-
-%\vspace{0.5ex}
-\subsubsection{Methodology}
-\label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
-test failure, affecting a particular engine, and classified that
-failure as potentially fault-revealing or not. The authors supervised
-the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors inspected the
-scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:cross-testing}Number of failures with
-    Test Transplantation.}
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
-    \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
-    \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
-    \jsc{} & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\ 
-   Tiny-js & 0 & 0 & 0 & 0  \\
-    \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
-    \bottomrule 
-  \end{tabular}
-  \vspace{-3ex}
-\end{table}
-
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
-
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
-manifested when tests cover implementation-dependent behavior, as
-defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-example, one of the tests from \jerry\ uses the function
-\CodeIn{Number.toPrecision([precision])}, which translates a number to
-a string, considering a given number of significant digits. The
-floating-point approximation of the real value is
-implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
-engine that runs the test does not optimize the code as the original
-engine of the test. As result, the test fails to finish at the
-specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
-this kind manifest when a test fails because it covers a function that
-is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} did not
-implement by default various properties from the \mcodeid{Symbol}
-object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
-an object property is undefined in the execution engine but we were
-unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
-the cases where the test was valid for some previous version of the
-spec but is no longer valid for the current spec.
-
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
-  \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{ccr}
-    \toprule
-    & source &  \#\\
-    \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
-    & Timeout/OME & \noTransTimeout{} \\
-    & Not Implemented & \noTransNotImplemented{} \\
-    & Non-Standard Element & \noTransNonStandard{} \\
-    & Other & \noTransOther{} \\
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
-    & Bug & \noTransTPBugs{} \\
-    \bottomrule
-  \end{tabular}
-\end{wraptable}
-
-Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
-failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
-positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
-duplicate reports, but not high enough to justify attempting to
-automate the detection of duplicates.
-
-\input{table_transplantation}
-
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Severity'' shows the severity of confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
-\noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
-However, the bugs the \jsc{} team confirmed were quickly fixed.
-
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation was effective at finding
-      functional bugs. Although the cost of classifying failures was
-      non-negligible, the approach revealed several non-trivial bugs
-      in three of the four engines we analyzed.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ3 (Differential Testing)}
-\label{sec:cross-engine-diff-testing-results}
-
-This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
-\subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
-Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
-we only fuzz test files that pass in all engines--a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
-appear under the column ``no-fail-in-all'' on
-Table~\ref{tab:test-suites}.  We want to avoid the scenario where
-fuzzing produces a fault-revealing input based on a test that was
-already revealing failures on some engine. This decision facilitates
-our inspection task; it helps us establish cause-effect relationship
-between fuzzing and the observation of discrepancy.  We configured our
-infrastructure (see Figure~\ref{fig:workflow}) to produce 20
-well-formed fuzzed files per input file, \ie{}, the number of fuzzing
-iterations can exceed the number above as we discard generated files
-that are syntactically invalid.
-
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
-three months of the study, our inspection process was exploratory.  In
-this phase, we wanted to learn whether or not black-box fuzzers could
-reveal real bugs and how effective was the \hi{}-\lo\ warning
-classification.  We expected the number of warnings to increase
-dramatically compared to the previous experiment and, if we realized
-that the ratio of bugs from \lo\ warnings was rather low, we could
-focus our inspection efforts on \hi\ warnings. To run this experiment,
-we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
-
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
-similar discipline as before. However, the set of warnings inspected
-and the order of inspection changed. We restricted our analysis to
-\hi\ warnings and, aware that we would be unable to analyze each and
-every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning
-belongs to the group of a given engine if only that engine manifests
-distinct behavior, \ie{}, it produces a distinct output compared to
-others. We separated in a distinct group the warnings for which two
-engines diverge. The rationale for this methodology was to give
-attention to each engine more uniformly, enabling more fair comparison
-across engines.
-
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
-\vspace{0.5ex}
-\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
-second places, respectively, in number of warnings.
-
-\begin{table}[t]
-  \small
-  \setlength{\tabcolsep}{4.5pt}
-  \centering
-  \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
-  \begin{tabular}{crrrrr}
-    \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
-    \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
-    \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These new sources are
-marked with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
-  \begin{tabular}{ccrr}
-    \toprule
-    & & \radamsa\ & \quickfuzz\ \\
-    \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
-
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the fuzzing tool used
-(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
-that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite''). So far,
-\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
-were fixed. Note that one bug report that we submitted was rejected on
-the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. For \veight{}, 
-we reported \noDiffVeight{} bugs, 
-all of them confirmed, with \noDiffVeightFixed{} fixed.
-
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was
-      effective at finding \js\ engines bugs, several of which have
-      been fixed already.
-      \end{minipage}
-    }
-\end{center}
-
-\noindent
-\textbf{Data Availability.}~The data, including the tests, warning
-reports, and diagnostic outcomes, is publicly available from a
-preserved repository \dataRepo.
-
-\section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
-
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
-\sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- var obj = {}; var arr = [];
- try { arr.sort(obj); assert(false);}
- catch (e) { assert(e instanceof TypeError); }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- function test() {
-   return typeof String.prototype.repeat === "function"
-     && "foo".repeat(657604378) === "foofoofoo"; }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
-
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
-that the authors of this paper made mistakes in the implementation of
-the scripts supporting the experiments. To mitigate this threat, we
-carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
-engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
-\label{sec:lessons}
-
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
-real bugs is a great way to train (and encourage) students in software
-testing. Students praised the experience of diagnosing failures,
-understanding part of the specs (as needed), writing bug reports,
-participating in discussions on issue trackers, and observing the
-change of status. That was a relatively self-contained hands-on
-activity that enabled students to engage in a real-life serious
-industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
-
-\subsection{Differential Testing}
-Several different applications of differential testing have been
-proposed in recent years. Chen and
-colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
-technique to generate X.509 certificates based on Request For
-Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can compromise security
-of servers which rely on these certificates to properly authenticate
-the parties involved in a communication session. Lidbury and
-colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
-colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
-focusing on finding bugs in programs for graphic cards (\eg{},
-OpenCL). These programs use the Single-Instruction Multiple-Data
-(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
-application of differential testing that received most attention to
-date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
-the use of a generator of sentences from grammars to test correctness
-of automatically generated parsers. After that, significant progress
-has been made. Lammel and Shulte proposed Geno to cross-check XPath
-implementations using grammar-based testing with controllable
-combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
-randomly create C programs from a grammar, for a subset of C, and then
-check the output of these programs in different compilers (\eg{}, GCC
-and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed ``equivalence modulo inputs'', which creates variants of
-program which should have equivalent behavior compared to the
-original, but for which the compiler manifests
-discrepancy. Differential testing has also been applied to test
-refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
-symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
-and very recently to test JavaScript
-debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
-shown to be flexible and effective for a wide range of
-applications. Surprisingly, not much work has been done on
-differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepancies across different configurations of
-the same version of its \smonkey\ engine (using the ``compare\_jit''
-flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
-fuzzing strategy using differential testing. Their focuses on finding
-differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/chapter/evaluation.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
-
-\section{JavaScript}
-\label{sec:es6-design}
-\label{sec:imp-dep-behavior}
-
-JavaScript engines are virtual machines that parse source code,
-compile it in bytecodes, and run these bytecodes. These engines
-implement some version of the ECMAScript (\es{}), which emerged with
-the goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript\footnote{The name JavaScript still
-  prevails today, certainly for historical reasons.}. The \es{}
-specification is regulated by Ecma International~\cite{es6-website}
-under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
-
-The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
-``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
-\js\ \mcodeid{for-in} loop construct does not clearly specify the
-iteration order of
-elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for loop
-optimizations~\cite{for-in-undefined}.  As another example, the
-specification states that if the \mcodeid{Number.toPrecision()}
-function is called with multiple arguments then the floating-point
-approximation is
-implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
-compatibility table~\cite{kangax}.  It is also worth noting that, as
-in other languages, some elements in JS have non-deterministic
-behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
-produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
-
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
-\section{Engines Studied}
-\label{sec:methodology}
-\label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria: 1) Released latest
-version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
-and 3) Uses a public issue tracker. We looked for highly-maintained
-(as per the first criterion) and popular (as per the second criterion)
-engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
-    \toprule
-    Team & Name & URL & \# Stars  & DOB \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
-   \bottomrule     
-  \end{tabular}
-\end{table}
-
-\section{Mined JS Files}
-\label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
-shows the number of test cases whose executions do not throw 
-dynamic type errors in any of the engines because of an undefined variable or property. 
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
-
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
-    \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
-
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
-non-portable objects. 
-Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines.
-
-\subsection{Mining Tests from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
-cases.
-
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
-To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
-Table~\ref{tab:engines} and we were able to retrieve a total of
-\filesAttached{} files.  To mine tests from the textual descriptions we
-proceeded as follows. First, we broke the text describing the issue in
-paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
-that information, we merged consecutive paragraphs labeled as ``code''
-and used a \js\ parser to check well-formedness of the retrieved code
-fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
-Table~\ref{tab:test-suites}.
-
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary 
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}  
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
-
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrates the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Numbered boxes in the figure denote the
-data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
-input. Otherwise, it considers the input as potentially
-fault-revealing; hence, interesting for human inspection. Finally, to
-facilitate the human inspection process, the infrastructure
-prioritizes warnings and clusters them in groups (step 3). We describe
-these features in Sections~\ref{sec:prioritization} and
-\ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
-Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
-earlier, this justifies why differential testing is challenging to
-automate at the functional level.
-
-For step 2, we considered using the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
-
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
-\subsection{Prioritization}
-\label{sec:prioritization}
-
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-likely to be a ``bug'' in the test code as opposed to a bug in the
-engine. Recall that, for differential testing, we only use seed tests
-that pass in all engines.
-
-Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
-Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
-example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case from the
-function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
-engine did not throw any exception, as can be confirmed from the
-report that our infrastructure produces starting with text ``Engine
-Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
-
-Clusterization is complementary to prioritization; it helps to group
-similar warnings reported by our infrastructure. We only clustered
-``\lo'' warnings as ``\hi'' warnings produce messages that arise from
-the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
-three elements that we use to characterize a warning--1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\subsection{Fuzzers}
-\label{sec:objects:fuzzers}
-
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
-grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz},
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
-Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. Another fundamental issue associated with
-generational fuzzers in our context is that the tests they produce do
-not contain assertions; to enable the integration of this kind of
-fuzzers in our infrastructure---we would need to look for
-discrepancies across compiler error messages as opposed to assertion
-violations.  All in all, although grammar-based fuzzers have been
-shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
-fuzzers in this study for the reasons above.
-
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
-properties\footnote{There are options in the clang toolchain to build
-  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
-  provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
-
-We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
-existing inputs randomly. The strength of the approach is
-limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose these specific fuzzers
-because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
+\chapter{Evaluation}
 
@@
 
-The goal of this paper is to assess ability of techniques that
+The goal of this work is to assess ability of techniques that
 leverage diversity to find functional bugs
@@
 rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
+scenarios not well-tested by at least one of the engines.
 
@@
 development. 
-
+\Igor{R1 criticou o pq este experimento. Não faz muito sentido deixar
+isso, já que nao houve quase nenhum progresso durante a semana.
+Ou podemos deixar executando varias vezes por dia, durante uns 15 dias ou 1 mes
+para monitorar o progresso.
+}
 For this experiment, we ran the suite once a day for seven consecutive
@@
 \label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
+\Igor{manter isso?}
+\Fix{In this experiment, a developer with experience in \js\ analyzed each
 test failure, affecting a particular engine, and classified that
@@
 scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
+issue tracker of the affected engine.}
+% In this experiment, we analyzed each test failure,
+% affecting a particular engine, and classified that
+% failure as potentially fault-revealing or not. This methodology
+% was supervised the classification process to validate correctness. For the
+% potentially fault-revealing cases, if agreed on the classification, we 
+% reported the bug to the issue tracker of the affected engine.
 
@@
     % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
+    % \Comment{
+    %   Lembrar dos testes que os testes da propria engine falham:
+    %   V8 0 
+    %   JSC 2 
+    %   Spidermonkey 58
+    % }
     \jsc{} & - & 10 & 10 & 59   \\
@@
 
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
+\sloppy The sources of FP found in this experiment are as
+follows: \textbf{Undefined Behavior.} FP of this kind are
 manifested when tests cover implementation-dependent behavior, as
@@
 \chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
+    error.}.} FP of this kind typically manifest when the
 engine that runs the test does not optimize the code as the original
@@
 recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
+tail-call optimization. \textbf{Not implemented.} FP of
 this kind manifest when a test fails because it covers a function that
@@
 unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
+\CodeIn{ReferenceError} and \CodeIn{TypeError}.
+% \Comment{ For example,
+%   we found cases where the test (or its harness) fails in an assertion
+%   because of an undefined property.}
+\textbf{Other.} This category
+includes other sources of FP. For example, it includes
 the cases where the test was valid for some previous version of the
@@
 
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
+\begin{table}
   \centering
   \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
+    of FP and TP.}
+  %\setlength{\tabcolsep}{3pt}      
   \renewcommand*{\arraystretch}{0.9}
@@
   \end{tabular}
-\end{wraptable}
+\end{table}
 
 Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
+\gls{fp} and \gls{tp}. The sum of the numbers
 in this table correspond to the number of files that manifested
@@
 positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
+source. Considering TP, we found a reasonable number of
 duplicate reports, but not high enough to justify attempting to
@@
 test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
+assigned to the bug,%\Comment{, column ``Date'' shows the date the bug was reported in the format ``m/dd'',}
+column ``Engine'' shows the
 affected engine, column ``Status'' shows the status of the bug report
@@
 Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
+QuickFuzz~\cite{grieco2016quickfuzz} for fuzzing. To avoid experimental noise,
 we only fuzz test files that pass in all engines--a total of
@@
 potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
+lithium~\cite{lithium} to minimize long test cases.
+% \Comment{; the tests from the Mozilla suite are often longer than others}
+A bug report was filed only after one of the authors reviewed the diagnosis.
+Each student found at least one bug using this methodology.
 
@@
   \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
+  \caption{\label{tab:false-positives}Distribution of FP and TP.}
   \begin{tabular}{ccrr}
@@
 (``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
+bug report (``Status''),
+% \Comment{ as of Aug. 24, 2018, the Url of the bug report (``Url'')}
+the severity of the bug report (``Sev.''), the priority
 that we assigned to the warning that revealed the bug (``Priority''),
@@
 version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
+returns a string representation of a null character (\CodeIn{NUL}).%\Comment{ in ascii}
+The unary plus expression ``\CodeIn{+a}", used in the
 assertion, is equivalent to the operation
 \CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
+otherwise the operation returns \gls{nan}~\cite{unary-plus}.
+This test fails in all engines but
 \chakra{}. For all three engines the string cannot be parsed as an
@@
 receive such a long value.
-
-\subsection{Threats To Validity}
-
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
-that the authors of this paper made mistakes in the implementation of
-the scripts supporting the experiments. To mitigate this threat, we
-carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
-engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
-\label{sec:lessons}
-
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
-real bugs is a great way to train (and encourage) students in software
-testing. Students praised the experience of diagnosing failures,
-understanding part of the specs (as needed), writing bug reports,
-participating in discussions on issue trackers, and observing the
-change of status. That was a relatively self-contained hands-on
-activity that enabled students to engage in a real-life serious
-industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
-
-\subsection{Differential Testing}
-Several different applications of differential testing have been
-proposed in recent years. Chen and
-colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
-technique to generate X.509 certificates based on Request For
-Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can compromise security
-of servers which rely on these certificates to properly authenticate
-the parties involved in a communication session. Lidbury and
-colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
-colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
-focusing on finding bugs in programs for graphic cards (\eg{},
-OpenCL). These programs use the Single-Instruction Multiple-Data
-(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
-application of differential testing that received most attention to
-date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
-the use of a generator of sentences from grammars to test correctness
-of automatically generated parsers. After that, significant progress
-has been made. Lammel and Shulte proposed Geno to cross-check XPath
-implementations using grammar-based testing with controllable
-combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
-randomly create C programs from a grammar, for a subset of C, and then
-check the output of these programs in different compilers (\eg{}, GCC
-and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed ``equivalence modulo inputs'', which creates variants of
-program which should have equivalent behavior compared to the
-original, but for which the compiler manifests
-discrepancy. Differential testing has also been applied to test
-refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
-symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
-and very recently to test JavaScript
-debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
-shown to be flexible and effective for a wide range of
-applications. Surprisingly, not much work has been done on
-differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepancies across different configurations of
-the same version of its \smonkey\ engine (using the ``compare\_jit''
-flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
-fuzzing strategy using differential testing. Their focuses on finding
-differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/chapter/lessons.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
-
-\section{JavaScript}
-\label{sec:es6-design}
-\label{sec:imp-dep-behavior}
-
-JavaScript engines are virtual machines that parse source code,
-compile it in bytecodes, and run these bytecodes. These engines
-implement some version of the ECMAScript (\es{}), which emerged with
-the goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript\footnote{The name JavaScript still
-  prevails today, certainly for historical reasons.}. The \es{}
-specification is regulated by Ecma International~\cite{es6-website}
-under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
-
-The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
-``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
-\js\ \mcodeid{for-in} loop construct does not clearly specify the
-iteration order of
-elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for loop
-optimizations~\cite{for-in-undefined}.  As another example, the
-specification states that if the \mcodeid{Number.toPrecision()}
-function is called with multiple arguments then the floating-point
-approximation is
-implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
-compatibility table~\cite{kangax}.  It is also worth noting that, as
-in other languages, some elements in JS have non-deterministic
-behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
-produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
-
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
-\section{Engines Studied}
-\label{sec:methodology}
-\label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria: 1) Released latest
-version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
-and 3) Uses a public issue tracker. We looked for highly-maintained
-(as per the first criterion) and popular (as per the second criterion)
-engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
-    \toprule
-    Team & Name & URL & \# Stars  & DOB \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
-   \bottomrule     
-  \end{tabular}
-\end{table}
-
-\section{Mined JS Files}
-\label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
-shows the number of test cases whose executions do not throw 
-dynamic type errors in any of the engines because of an undefined variable or property. 
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
-
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
-    \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
-
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
-non-portable objects. 
-Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines.
-
-\subsection{Mining Tests from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
-cases.
-
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
-To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
-Table~\ref{tab:engines} and we were able to retrieve a total of
-\filesAttached{} files.  To mine tests from the textual descriptions we
-proceeded as follows. First, we broke the text describing the issue in
-paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
-that information, we merged consecutive paragraphs labeled as ``code''
-and used a \js\ parser to check well-formedness of the retrieved code
-fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
-Table~\ref{tab:test-suites}.
-
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary 
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}  
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
-
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrates the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Numbered boxes in the figure denote the
-data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
-input. Otherwise, it considers the input as potentially
-fault-revealing; hence, interesting for human inspection. Finally, to
-facilitate the human inspection process, the infrastructure
-prioritizes warnings and clusters them in groups (step 3). We describe
-these features in Sections~\ref{sec:prioritization} and
-\ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
-Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
-earlier, this justifies why differential testing is challenging to
-automate at the functional level.
-
-For step 2, we considered using the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
-
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
-\subsection{Prioritization}
-\label{sec:prioritization}
-
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-likely to be a ``bug'' in the test code as opposed to a bug in the
-engine. Recall that, for differential testing, we only use seed tests
-that pass in all engines.
-
-Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
-Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
-example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case from the
-function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
-engine did not throw any exception, as can be confirmed from the
-report that our infrastructure produces starting with text ``Engine
-Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
-
-Clusterization is complementary to prioritization; it helps to group
-similar warnings reported by our infrastructure. We only clustered
-``\lo'' warnings as ``\hi'' warnings produce messages that arise from
-the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
-three elements that we use to characterize a warning--1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\subsection{Fuzzers}
-\label{sec:objects:fuzzers}
-
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
-grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz},
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
-Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. Another fundamental issue associated with
-generational fuzzers in our context is that the tests they produce do
-not contain assertions; to enable the integration of this kind of
-fuzzers in our infrastructure---we would need to look for
-discrepancies across compiler error messages as opposed to assertion
-violations.  All in all, although grammar-based fuzzers have been
-shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
-fuzzers in this study for the reasons above.
-
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
-properties\footnote{There are options in the clang toolchain to build
-  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
-  provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
-
-We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
-existing inputs randomly. The strength of the approach is
-limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose these specific fuzzers
-because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Results}
-\label{sec:results}
-
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
-\begin{description}[leftmargin=.5in]
-\item[RQ1.] How conformant are the engines to the Test262 suite?
-\item[RQ2.] How effective is test transplantation to find bugs?
-\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
-\end{description}
-
-The first question focuses on the conformance of our selected engines
-to the official Test262 suite~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. The second question
-focuses on the effectiveness of test transplantation
-(Section~\ref{sec:transplantation}). The rationale for using inputs
-from different engines is that developers consider different goals
-when writing tests---suites written for a given engine may cover
-scenarios not covered by a different engine. The third question
-evaluates the effectiveness of cross-engine differential testing to
-find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
-
-\subsection{Answering RQ1 (Conformance)}
-\label{sec:stability}
-
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
-check conformance of engines to the \js\ standard. It is
-acceptable to release engines fulfilling the specification only
-partially~\cite{kangax}. We expect that the pass rate on this suite
-provide some indication of the engine's maturity. In the limit, it is
-not desirable to flood bug reports on engines at early stages of
-development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}.
-
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
-  \centering
-  \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
-    \toprule
-    engine & \% passing \\
-    \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
-    \chakra{} & \percentSuiteTestChakra{} \\    
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \bottomrule
-  \end{tabular}
-  \normalsize
-\end{wraptable}
-
-Results show that there are still many unsupported scenarios as can be observed from the
-percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
-Figure~\ref{fig:summary}). Although it is plausible to find
-correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
-to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
-      engines is above 90\%.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ2 (Test Transplantation)}
-\label{sec:transplantation}
-
-This section reports results of test transplantation. More
-specifically, we analyzed the failures observed when running a test
-suite original from a given engine in another engine. Intuitively, we
-want to assess how effective is the idea of cross-fertilization of
-testing knowledge among \js\ developers.
-
-%\vspace{0.5ex}
-\subsubsection{Methodology}
-\label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
-test failure, affecting a particular engine, and classified that
-failure as potentially fault-revealing or not. The authors supervised
-the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors inspected the
-scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:cross-testing}Number of failures with
-    Test Transplantation.}
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
-    \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
-    \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
-    \jsc{} & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\ 
-   Tiny-js & 0 & 0 & 0 & 0  \\
-    \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
-    \bottomrule 
-  \end{tabular}
-  \vspace{-3ex}
-\end{table}
-
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
-
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
-manifested when tests cover implementation-dependent behavior, as
-defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-example, one of the tests from \jerry\ uses the function
-\CodeIn{Number.toPrecision([precision])}, which translates a number to
-a string, considering a given number of significant digits. The
-floating-point approximation of the real value is
-implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
-engine that runs the test does not optimize the code as the original
-engine of the test. As result, the test fails to finish at the
-specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
-this kind manifest when a test fails because it covers a function that
-is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} did not
-implement by default various properties from the \mcodeid{Symbol}
-object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
-an object property is undefined in the execution engine but we were
-unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
-the cases where the test was valid for some previous version of the
-spec but is no longer valid for the current spec.
-
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
-  \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{ccr}
-    \toprule
-    & source &  \#\\
-    \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
-    & Timeout/OME & \noTransTimeout{} \\
-    & Not Implemented & \noTransNotImplemented{} \\
-    & Non-Standard Element & \noTransNonStandard{} \\
-    & Other & \noTransOther{} \\
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
-    & Bug & \noTransTPBugs{} \\
-    \bottomrule
-  \end{tabular}
-\end{wraptable}
-
-Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
-failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
-positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
-duplicate reports, but not high enough to justify attempting to
-automate the detection of duplicates.
-
-\input{table_transplantation}
-
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Severity'' shows the severity of confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
-\noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
-However, the bugs the \jsc{} team confirmed were quickly fixed.
-
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation was effective at finding
-      functional bugs. Although the cost of classifying failures was
-      non-negligible, the approach revealed several non-trivial bugs
-      in three of the four engines we analyzed.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ3 (Differential Testing)}
-\label{sec:cross-engine-diff-testing-results}
-
-This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
-\subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
-Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
-we only fuzz test files that pass in all engines--a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
-appear under the column ``no-fail-in-all'' on
-Table~\ref{tab:test-suites}.  We want to avoid the scenario where
-fuzzing produces a fault-revealing input based on a test that was
-already revealing failures on some engine. This decision facilitates
-our inspection task; it helps us establish cause-effect relationship
-between fuzzing and the observation of discrepancy.  We configured our
-infrastructure (see Figure~\ref{fig:workflow}) to produce 20
-well-formed fuzzed files per input file, \ie{}, the number of fuzzing
-iterations can exceed the number above as we discard generated files
-that are syntactically invalid.
-
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
-three months of the study, our inspection process was exploratory.  In
-this phase, we wanted to learn whether or not black-box fuzzers could
-reveal real bugs and how effective was the \hi{}-\lo\ warning
-classification.  We expected the number of warnings to increase
-dramatically compared to the previous experiment and, if we realized
-that the ratio of bugs from \lo\ warnings was rather low, we could
-focus our inspection efforts on \hi\ warnings. To run this experiment,
-we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
-
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
-similar discipline as before. However, the set of warnings inspected
-and the order of inspection changed. We restricted our analysis to
-\hi\ warnings and, aware that we would be unable to analyze each and
-every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning
-belongs to the group of a given engine if only that engine manifests
-distinct behavior, \ie{}, it produces a distinct output compared to
-others. We separated in a distinct group the warnings for which two
-engines diverge. The rationale for this methodology was to give
-attention to each engine more uniformly, enabling more fair comparison
-across engines.
-
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
-\vspace{0.5ex}
-\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
-second places, respectively, in number of warnings.
-
-\begin{table}[t]
-  \small
-  \setlength{\tabcolsep}{4.5pt}
-  \centering
-  \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
-  \begin{tabular}{crrrrr}
-    \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
-    \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
-    \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These new sources are
-marked with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
-  \begin{tabular}{ccrr}
-    \toprule
-    & & \radamsa\ & \quickfuzz\ \\
-    \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
-
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the fuzzing tool used
-(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
-that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite''). So far,
-\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
-were fixed. Note that one bug report that we submitted was rejected on
-the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. For \veight{}, 
-we reported \noDiffVeight{} bugs, 
-all of them confirmed, with \noDiffVeightFixed{} fixed.
-
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was
-      effective at finding \js\ engines bugs, several of which have
-      been fixed already.
-      \end{minipage}
-    }
-\end{center}
-
-\noindent
-\textbf{Data Availability.}~The data, including the tests, warning
-reports, and diagnostic outcomes, is publicly available from a
-preserved repository \dataRepo.
-
-\section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
-
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
-\sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- var obj = {}; var arr = [];
- try { arr.sort(obj); assert(false);}
- catch (e) { assert(e instanceof TypeError); }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- function test() {
-   return typeof String.prototype.repeat === "function"
-     && "foo".repeat(657604378) === "foofoofoo"; }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
-
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
-that the authors of this paper made mistakes in the implementation of
-the scripts supporting the experiments. To mitigate this threat, we
-carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
-engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
+\chapter{Key Findings and Lessons}
 \label{sec:lessons}
@@
 colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
+avenue to explore. Recall that the rate of TP of the
 techniques we studied is rather small.  5)~We learned that reporting
@@
 industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
-
-\subsection{Differential Testing}
-Several different applications of differential testing have been
-proposed in recent years. Chen and
-colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
-technique to generate X.509 certificates based on Request For
-Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can compromise security
-of servers which rely on these certificates to properly authenticate
-the parties involved in a communication session. Lidbury and
-colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
-colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
-focusing on finding bugs in programs for graphic cards (\eg{},
-OpenCL). These programs use the Single-Instruction Multiple-Data
-(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
-application of differential testing that received most attention to
-date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
-the use of a generator of sentences from grammars to test correctness
-of automatically generated parsers. After that, significant progress
-has been made. Lammel and Shulte proposed Geno to cross-check XPath
-implementations using grammar-based testing with controllable
-combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
-randomly create C programs from a grammar, for a subset of C, and then
-check the output of these programs in different compilers (\eg{}, GCC
-and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed ``equivalence modulo inputs'', which creates variants of
-program which should have equivalent behavior compared to the
-original, but for which the compiler manifests
-discrepancy. Differential testing has also been applied to test
-refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
-symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
-and very recently to test JavaScript
-debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
-shown to be flexible and effective for a wide range of
-applications. Surprisingly, not much work has been done on
-differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepancies across different configurations of
-the same version of its \smonkey\ engine (using the ``compare\_jit''
-flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
-fuzzing strategy using differential testing. Their focuses on finding
-differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/chapter/related_work.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
-
-\section{JavaScript}
-\label{sec:es6-design}
-\label{sec:imp-dep-behavior}
-
-JavaScript engines are virtual machines that parse source code,
-compile it in bytecodes, and run these bytecodes. These engines
-implement some version of the ECMAScript (\es{}), which emerged with
-the goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript\footnote{The name JavaScript still
-  prevails today, certainly for historical reasons.}. The \es{}
-specification is regulated by Ecma International~\cite{es6-website}
-under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
-
-The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
-``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
-\js\ \mcodeid{for-in} loop construct does not clearly specify the
-iteration order of
-elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for loop
-optimizations~\cite{for-in-undefined}.  As another example, the
-specification states that if the \mcodeid{Number.toPrecision()}
-function is called with multiple arguments then the floating-point
-approximation is
-implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
-compatibility table~\cite{kangax}.  It is also worth noting that, as
-in other languages, some elements in JS have non-deterministic
-behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
-produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
-
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
-\section{Engines Studied}
-\label{sec:methodology}
-\label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria: 1) Released latest
-version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
-and 3) Uses a public issue tracker. We looked for highly-maintained
-(as per the first criterion) and popular (as per the second criterion)
-engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
-    \toprule
-    Team & Name & URL & \# Stars  & DOB \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
-   \bottomrule     
-  \end{tabular}
-\end{table}
-
-\section{Mined JS Files}
-\label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
-shows the number of test cases whose executions do not throw 
-dynamic type errors in any of the engines because of an undefined variable or property. 
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
-
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
-    \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
-
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
-non-portable objects. 
-Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines.
-
-\subsection{Mining Tests from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
-cases.
-
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
-To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
-Table~\ref{tab:engines} and we were able to retrieve a total of
-\filesAttached{} files.  To mine tests from the textual descriptions we
-proceeded as follows. First, we broke the text describing the issue in
-paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
-that information, we merged consecutive paragraphs labeled as ``code''
-and used a \js\ parser to check well-formedness of the retrieved code
-fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
-Table~\ref{tab:test-suites}.
-
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary 
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}  
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
-
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrates the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Numbered boxes in the figure denote the
-data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
-input. Otherwise, it considers the input as potentially
-fault-revealing; hence, interesting for human inspection. Finally, to
-facilitate the human inspection process, the infrastructure
-prioritizes warnings and clusters them in groups (step 3). We describe
-these features in Sections~\ref{sec:prioritization} and
-\ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
-Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
-earlier, this justifies why differential testing is challenging to
-automate at the functional level.
-
-For step 2, we considered using the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
-
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
-\subsection{Prioritization}
-\label{sec:prioritization}
-
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-likely to be a ``bug'' in the test code as opposed to a bug in the
-engine. Recall that, for differential testing, we only use seed tests
-that pass in all engines.
-
-Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
-Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
-example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case from the
-function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
-engine did not throw any exception, as can be confirmed from the
-report that our infrastructure produces starting with text ``Engine
-Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
-
-Clusterization is complementary to prioritization; it helps to group
-similar warnings reported by our infrastructure. We only clustered
-``\lo'' warnings as ``\hi'' warnings produce messages that arise from
-the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
-three elements that we use to characterize a warning--1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\subsection{Fuzzers}
-\label{sec:objects:fuzzers}
-
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
-grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz},
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
-Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. Another fundamental issue associated with
-generational fuzzers in our context is that the tests they produce do
-not contain assertions; to enable the integration of this kind of
-fuzzers in our infrastructure---we would need to look for
-discrepancies across compiler error messages as opposed to assertion
-violations.  All in all, although grammar-based fuzzers have been
-shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
-fuzzers in this study for the reasons above.
-
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
-properties\footnote{There are options in the clang toolchain to build
-  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
-  provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
-
-We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
-existing inputs randomly. The strength of the approach is
-limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose these specific fuzzers
-because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Results}
-\label{sec:results}
-
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
-\begin{description}[leftmargin=.5in]
-\item[RQ1.] How conformant are the engines to the Test262 suite?
-\item[RQ2.] How effective is test transplantation to find bugs?
-\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
-\end{description}
-
-The first question focuses on the conformance of our selected engines
-to the official Test262 suite~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. The second question
-focuses on the effectiveness of test transplantation
-(Section~\ref{sec:transplantation}). The rationale for using inputs
-from different engines is that developers consider different goals
-when writing tests---suites written for a given engine may cover
-scenarios not covered by a different engine. The third question
-evaluates the effectiveness of cross-engine differential testing to
-find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
-
-\subsection{Answering RQ1 (Conformance)}
-\label{sec:stability}
-
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
-check conformance of engines to the \js\ standard. It is
-acceptable to release engines fulfilling the specification only
-partially~\cite{kangax}. We expect that the pass rate on this suite
-provide some indication of the engine's maturity. In the limit, it is
-not desirable to flood bug reports on engines at early stages of
-development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}.
-
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
-  \centering
-  \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
-    \toprule
-    engine & \% passing \\
-    \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
-    \chakra{} & \percentSuiteTestChakra{} \\    
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \bottomrule
-  \end{tabular}
-  \normalsize
-\end{wraptable}
-
-Results show that there are still many unsupported scenarios as can be observed from the
-percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
-Figure~\ref{fig:summary}). Although it is plausible to find
-correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
-to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
-      engines is above 90\%.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ2 (Test Transplantation)}
-\label{sec:transplantation}
-
-This section reports results of test transplantation. More
-specifically, we analyzed the failures observed when running a test
-suite original from a given engine in another engine. Intuitively, we
-want to assess how effective is the idea of cross-fertilization of
-testing knowledge among \js\ developers.
-
-%\vspace{0.5ex}
-\subsubsection{Methodology}
-\label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
-test failure, affecting a particular engine, and classified that
-failure as potentially fault-revealing or not. The authors supervised
-the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors inspected the
-scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:cross-testing}Number of failures with
-    Test Transplantation.}
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
-    \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
-    \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
-    \jsc{} & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\ 
-   Tiny-js & 0 & 0 & 0 & 0  \\
-    \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
-    \bottomrule 
-  \end{tabular}
-  \vspace{-3ex}
-\end{table}
-
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
-
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
-manifested when tests cover implementation-dependent behavior, as
-defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-example, one of the tests from \jerry\ uses the function
-\CodeIn{Number.toPrecision([precision])}, which translates a number to
-a string, considering a given number of significant digits. The
-floating-point approximation of the real value is
-implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
-engine that runs the test does not optimize the code as the original
-engine of the test. As result, the test fails to finish at the
-specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
-this kind manifest when a test fails because it covers a function that
-is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} did not
-implement by default various properties from the \mcodeid{Symbol}
-object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
-an object property is undefined in the execution engine but we were
-unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
-the cases where the test was valid for some previous version of the
-spec but is no longer valid for the current spec.
-
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
-  \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{ccr}
-    \toprule
-    & source &  \#\\
-    \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
-    & Timeout/OME & \noTransTimeout{} \\
-    & Not Implemented & \noTransNotImplemented{} \\
-    & Non-Standard Element & \noTransNonStandard{} \\
-    & Other & \noTransOther{} \\
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
-    & Bug & \noTransTPBugs{} \\
-    \bottomrule
-  \end{tabular}
-\end{wraptable}
-
-Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
-failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
-positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
-duplicate reports, but not high enough to justify attempting to
-automate the detection of duplicates.
-
-\input{table_transplantation}
-
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Severity'' shows the severity of confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
-\noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
-However, the bugs the \jsc{} team confirmed were quickly fixed.
-
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation was effective at finding
-      functional bugs. Although the cost of classifying failures was
-      non-negligible, the approach revealed several non-trivial bugs
-      in three of the four engines we analyzed.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ3 (Differential Testing)}
-\label{sec:cross-engine-diff-testing-results}
-
-This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
-\subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
-Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
-we only fuzz test files that pass in all engines--a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
-appear under the column ``no-fail-in-all'' on
-Table~\ref{tab:test-suites}.  We want to avoid the scenario where
-fuzzing produces a fault-revealing input based on a test that was
-already revealing failures on some engine. This decision facilitates
-our inspection task; it helps us establish cause-effect relationship
-between fuzzing and the observation of discrepancy.  We configured our
-infrastructure (see Figure~\ref{fig:workflow}) to produce 20
-well-formed fuzzed files per input file, \ie{}, the number of fuzzing
-iterations can exceed the number above as we discard generated files
-that are syntactically invalid.
-
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
-three months of the study, our inspection process was exploratory.  In
-this phase, we wanted to learn whether or not black-box fuzzers could
-reveal real bugs and how effective was the \hi{}-\lo\ warning
-classification.  We expected the number of warnings to increase
-dramatically compared to the previous experiment and, if we realized
-that the ratio of bugs from \lo\ warnings was rather low, we could
-focus our inspection efforts on \hi\ warnings. To run this experiment,
-we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
-
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
-similar discipline as before. However, the set of warnings inspected
-and the order of inspection changed. We restricted our analysis to
-\hi\ warnings and, aware that we would be unable to analyze each and
-every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning
-belongs to the group of a given engine if only that engine manifests
-distinct behavior, \ie{}, it produces a distinct output compared to
-others. We separated in a distinct group the warnings for which two
-engines diverge. The rationale for this methodology was to give
-attention to each engine more uniformly, enabling more fair comparison
-across engines.
-
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
-\vspace{0.5ex}
-\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
-second places, respectively, in number of warnings.
-
-\begin{table}[t]
-  \small
-  \setlength{\tabcolsep}{4.5pt}
-  \centering
-  \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
-  \begin{tabular}{crrrrr}
-    \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
-    \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
-    \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These new sources are
-marked with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
-  \begin{tabular}{ccrr}
-    \toprule
-    & & \radamsa\ & \quickfuzz\ \\
-    \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
-
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the fuzzing tool used
-(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
-that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite''). So far,
-\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
-were fixed. Note that one bug report that we submitted was rejected on
-the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. For \veight{}, 
-we reported \noDiffVeight{} bugs, 
-all of them confirmed, with \noDiffVeightFixed{} fixed.
-
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was
-      effective at finding \js\ engines bugs, several of which have
-      been fixed already.
-      \end{minipage}
-    }
-\end{center}
-
-\noindent
-\textbf{Data Availability.}~The data, including the tests, warning
-reports, and diagnostic outcomes, is publicly available from a
-preserved repository \dataRepo.
-
-\section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
-
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
-\sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- var obj = {}; var arr = [];
- try { arr.sort(obj); assert(false);}
- catch (e) { assert(e instanceof TypeError); }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- function test() {
-   return typeof String.prototype.repeat === "function"
-     && "foo".repeat(657604378) === "foofoofoo"; }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
-
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
-that the authors of this paper made mistakes in the implementation of
-the scripts supporting the experiments. To mitigate this threat, we
-carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
-engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
-\label{sec:lessons}
-
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
-real bugs is a great way to train (and encourage) students in software
-testing. Students praised the experience of diagnosing failures,
-understanding part of the specs (as needed), writing bug reports,
-participating in discussions on issue trackers, and observing the
-change of status. That was a relatively self-contained hands-on
-activity that enabled students to engage in a real-life serious
-industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
+\chapter{Related Work}
+\label{sec:related}
+\section{Diversity in Testing}
+\label{sec:related:diversity-testing}
 The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
+eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
 assumption behind test set diversity is that faults often spread
@@
 selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
+study explores diversity of sources of test cases and diversity of
 engine implementations. We remain to investigate the diversity of test
@@
 
-\subsection{Differential Testing}
+\section{Differential Testing}
 Several different applications of differential testing have been
@@
 flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
+across engines. \citeonline{patra2016learning} evaluated their language-agnostic
 fuzzing strategy using differential testing. Their focuses on finding
 differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
+browsers. As such they specialized their
+fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}).
+\Igor{In \citeonline{Chen-etal-pldi16} is presented the \textit{classfuzz}, a tool
+that uses coverage-directed fuzzing technique to improving the generation
+of valid mutants on different JVM implementations. In this case, their focuses
+is the Java environment and evaluate their technique with another coverage-directed
+fuzzing. In contrast to \citeonline{patra2016learning} and \citeonline{Chen-etal-pldi16}, we did not propose new techniques; our
 contribution was empirical.
+}
 
-\subsection{Testing \js\ Programs}
+\section{Testing \js\ Programs}
 Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
@@
 programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
+Systems as WordPress. The focus of this work is on testing
 \js\ engines as opposed to \js\ programs. Our goal is therefore
@@
 
-\subsection{Testing \js{} Engines}
+\section{Testing \js{} Engines}
 \label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
+The closest work to ours was done by \citeonline{patra2016learning}. Their work proposes a
 language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
+discrepancies.%\Comment{ They applied the proposed fuzzer to find bugs in JS engines and Web Assembly engines.}
+The sensible parts of the infrastructure they
 built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
+output correctness (as to reduce FP). Patra and Pradel
 work is complementary to ours--in principle, we could use their fuzzer
@@
 Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/chapter/subjects.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
-
-\section{JavaScript}
-\label{sec:es6-design}
-\label{sec:imp-dep-behavior}
-
-JavaScript engines are virtual machines that parse source code,
-compile it in bytecodes, and run these bytecodes. These engines
-implement some version of the ECMAScript (\es{}), which emerged with
-the goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript\footnote{The name JavaScript still
-  prevails today, certainly for historical reasons.}. The \es{}
-specification is regulated by Ecma International~\cite{es6-website}
-under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
-
-The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
-``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
-\js\ \mcodeid{for-in} loop construct does not clearly specify the
-iteration order of
-elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for loop
-optimizations~\cite{for-in-undefined}.  As another example, the
-specification states that if the \mcodeid{Number.toPrecision()}
-function is called with multiple arguments then the floating-point
-approximation is
-implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
-compatibility table~\cite{kangax}.  It is also worth noting that, as
-in other languages, some elements in JS have non-deterministic
-behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
-produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
-
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
-\section{Engines Studied}
-\label{sec:methodology}
-\label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria: 1) Released latest
-version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
-and 3) Uses a public issue tracker. We looked for highly-maintained
-(as per the first criterion) and popular (as per the second criterion)
-engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
-    \toprule
-    Team & Name & URL & \# Stars  & DOB \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
-   \bottomrule     
-  \end{tabular}
-\end{table}
-
-\section{Mined JS Files}
-\label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
-shows the number of test cases whose executions do not throw 
-dynamic type errors in any of the engines because of an undefined variable or property. 
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
-
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
-    \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
-
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
-non-portable objects. 
-Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines.
-
-\subsection{Mining Tests from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
-cases.
-
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
-To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
-Table~\ref{tab:engines} and we were able to retrieve a total of
-\filesAttached{} files.  To mine tests from the textual descriptions we
-proceeded as follows. First, we broke the text describing the issue in
-paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
-that information, we merged consecutive paragraphs labeled as ``code''
-and used a \js\ parser to check well-formedness of the retrieved code
-fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
-Table~\ref{tab:test-suites}.
-
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary 
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}  
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
+\chapter{Objects of Analysis}
 
@@
 ~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
+to precisely distinguish false and \gls{tp}. As such, a human
 needs to inspect the warning to classify the issue. As mentioned
@@
 eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
+output discrepancy. \Igor{However, we noticed that eshost-cli does not
+handle discrepancies involving crashes, but our oracle checks if
+there are a crash report on the running.}
+% \Igor{nos nao fizemos esse fork e implementamos essa funcionalidade no eshost}
+%As such, we forked the
+%eshost-cli GitHub project and implemented that functionality on it.
+It is also important to note that our checker does not support the case
 where the test fails in all engines but the kind of failure (\eg{},
@@
 weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
+function and that is acceptable.
+% \Comment{ For instance, it is acceptable to pass values
+% greater than \Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.}
+In those cases, the infrastructure would report a warning that is more likely to be
 associated with an invalid input produced by the fuzzer, \ie{}, it is
@@
   \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
+  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning.}
+    % that led to a confirmed bug report in \chakra.}
+    % The bug is caused by a required precondition check in the implementation of function
+    % \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test.
 \end{figure}
@@
 (mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
+fuzzers %\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
 in this study. In the following, we provide rationale for this
@@
 with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
+were able to produce more%\Comment{ \Fix{Y, Y$>$Y?}}
+valid inputs as it contains some heuristics to circumvent 
+violations of certain typing rules. %\Comment{ such as \Fix{variable used must be defined?}.}
 Nonetheless, running those inputs in our infrastructure we were unable
@@
 Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
+mutational fuzzers are typically coverage-based. American Fuzz Lop
+(AFL)~\footnote{American Fuzz Loop. Available at \url{http://lcamtuf.coredump.cx/afl/}} 
+and LibFuzzer~\footnote{LibFuzzer. Available at \url{https://llvm.org/docs/LibFuzzer.html}}
+are examples of this kind of fuzzers.
+These fuzzers run tests inputs against instrumented
 versions of the program under testing with the typical goal of finding
@@
 We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
+study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{grieco2016quickfuzz}. These
 fuzzers require no instrumentation and domain-knowledge. They mutate
@@
 tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Results}
-\label{sec:results}
-
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
-\begin{description}[leftmargin=.5in]
-\item[RQ1.] How conformant are the engines to the Test262 suite?
-\item[RQ2.] How effective is test transplantation to find bugs?
-\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
-\end{description}
-
-The first question focuses on the conformance of our selected engines
-to the official Test262 suite~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. The second question
-focuses on the effectiveness of test transplantation
-(Section~\ref{sec:transplantation}). The rationale for using inputs
-from different engines is that developers consider different goals
-when writing tests---suites written for a given engine may cover
-scenarios not covered by a different engine. The third question
-evaluates the effectiveness of cross-engine differential testing to
-find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
-
-\subsection{Answering RQ1 (Conformance)}
-\label{sec:stability}
-
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
-check conformance of engines to the \js\ standard. It is
-acceptable to release engines fulfilling the specification only
-partially~\cite{kangax}. We expect that the pass rate on this suite
-provide some indication of the engine's maturity. In the limit, it is
-not desirable to flood bug reports on engines at early stages of
-development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}.
-
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
-  \centering
-  \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
-    \toprule
-    engine & \% passing \\
-    \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
-    \chakra{} & \percentSuiteTestChakra{} \\    
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \bottomrule
-  \end{tabular}
-  \normalsize
-\end{wraptable}
-
-Results show that there are still many unsupported scenarios as can be observed from the
-percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
-Figure~\ref{fig:summary}). Although it is plausible to find
-correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
-to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
-      engines is above 90\%.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ2 (Test Transplantation)}
-\label{sec:transplantation}
-
-This section reports results of test transplantation. More
-specifically, we analyzed the failures observed when running a test
-suite original from a given engine in another engine. Intuitively, we
-want to assess how effective is the idea of cross-fertilization of
-testing knowledge among \js\ developers.
-
-%\vspace{0.5ex}
-\subsubsection{Methodology}
-\label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
-test failure, affecting a particular engine, and classified that
-failure as potentially fault-revealing or not. The authors supervised
-the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors inspected the
-scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:cross-testing}Number of failures with
-    Test Transplantation.}
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
-    \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
-    \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
-    \jsc{} & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\ 
-   Tiny-js & 0 & 0 & 0 & 0  \\
-    \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
-    \bottomrule 
-  \end{tabular}
-  \vspace{-3ex}
-\end{table}
-
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
-
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
-manifested when tests cover implementation-dependent behavior, as
-defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-example, one of the tests from \jerry\ uses the function
-\CodeIn{Number.toPrecision([precision])}, which translates a number to
-a string, considering a given number of significant digits. The
-floating-point approximation of the real value is
-implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
-engine that runs the test does not optimize the code as the original
-engine of the test. As result, the test fails to finish at the
-specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
-this kind manifest when a test fails because it covers a function that
-is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} did not
-implement by default various properties from the \mcodeid{Symbol}
-object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
-an object property is undefined in the execution engine but we were
-unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
-the cases where the test was valid for some previous version of the
-spec but is no longer valid for the current spec.
-
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
-  \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{ccr}
-    \toprule
-    & source &  \#\\
-    \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
-    & Timeout/OME & \noTransTimeout{} \\
-    & Not Implemented & \noTransNotImplemented{} \\
-    & Non-Standard Element & \noTransNonStandard{} \\
-    & Other & \noTransOther{} \\
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
-    & Bug & \noTransTPBugs{} \\
-    \bottomrule
-  \end{tabular}
-\end{wraptable}
-
-Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
-failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
-positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
-duplicate reports, but not high enough to justify attempting to
-automate the detection of duplicates.
-
-\input{table_transplantation}
-
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Severity'' shows the severity of confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
-\noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
-However, the bugs the \jsc{} team confirmed were quickly fixed.
-
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation was effective at finding
-      functional bugs. Although the cost of classifying failures was
-      non-negligible, the approach revealed several non-trivial bugs
-      in three of the four engines we analyzed.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ3 (Differential Testing)}
-\label{sec:cross-engine-diff-testing-results}
-
-This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
-\subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
-Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
-we only fuzz test files that pass in all engines--a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
-appear under the column ``no-fail-in-all'' on
-Table~\ref{tab:test-suites}.  We want to avoid the scenario where
-fuzzing produces a fault-revealing input based on a test that was
-already revealing failures on some engine. This decision facilitates
-our inspection task; it helps us establish cause-effect relationship
-between fuzzing and the observation of discrepancy.  We configured our
-infrastructure (see Figure~\ref{fig:workflow}) to produce 20
-well-formed fuzzed files per input file, \ie{}, the number of fuzzing
-iterations can exceed the number above as we discard generated files
-that are syntactically invalid.
-
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
-three months of the study, our inspection process was exploratory.  In
-this phase, we wanted to learn whether or not black-box fuzzers could
-reveal real bugs and how effective was the \hi{}-\lo\ warning
-classification.  We expected the number of warnings to increase
-dramatically compared to the previous experiment and, if we realized
-that the ratio of bugs from \lo\ warnings was rather low, we could
-focus our inspection efforts on \hi\ warnings. To run this experiment,
-we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
-
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
-similar discipline as before. However, the set of warnings inspected
-and the order of inspection changed. We restricted our analysis to
-\hi\ warnings and, aware that we would be unable to analyze each and
-every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning
-belongs to the group of a given engine if only that engine manifests
-distinct behavior, \ie{}, it produces a distinct output compared to
-others. We separated in a distinct group the warnings for which two
-engines diverge. The rationale for this methodology was to give
-attention to each engine more uniformly, enabling more fair comparison
-across engines.
-
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
-\vspace{0.5ex}
-\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
-second places, respectively, in number of warnings.
-
-\begin{table}[t]
-  \small
-  \setlength{\tabcolsep}{4.5pt}
-  \centering
-  \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
-  \begin{tabular}{crrrrr}
-    \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
-    \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
-    \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These new sources are
-marked with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
-  \begin{tabular}{ccrr}
-    \toprule
-    & & \radamsa\ & \quickfuzz\ \\
-    \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
-
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the fuzzing tool used
-(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
-that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite''). So far,
-\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
-were fixed. Note that one bug report that we submitted was rejected on
-the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. For \veight{}, 
-we reported \noDiffVeight{} bugs, 
-all of them confirmed, with \noDiffVeightFixed{} fixed.
-
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was
-      effective at finding \js\ engines bugs, several of which have
-      been fixed already.
-      \end{minipage}
-    }
-\end{center}
-
-\noindent
-\textbf{Data Availability.}~The data, including the tests, warning
-reports, and diagnostic outcomes, is publicly available from a
-preserved repository \dataRepo.
-
-\section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
-
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
-\sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- var obj = {}; var arr = [];
- try { arr.sort(obj); assert(false);}
- catch (e) { assert(e instanceof TypeError); }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- function test() {
-   return typeof String.prototype.repeat === "function"
-     && "foo".repeat(657604378) === "foofoofoo"; }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
-
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
-that the authors of this paper made mistakes in the implementation of
-the scripts supporting the experiments. To mitigate this threat, we
-carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
-engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
-\label{sec:lessons}
-
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
-real bugs is a great way to train (and encourage) students in software
-testing. Students praised the experience of diagnosing failures,
-understanding part of the specs (as needed), writing bug reports,
-participating in discussions on issue trackers, and observing the
-change of status. That was a relatively self-contained hands-on
-activity that enabled students to engage in a real-life serious
-industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
-
-\subsection{Differential Testing}
-Several different applications of differential testing have been
-proposed in recent years. Chen and
-colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
-technique to generate X.509 certificates based on Request For
-Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can compromise security
-of servers which rely on these certificates to properly authenticate
-the parties involved in a communication session. Lidbury and
-colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
-colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
-focusing on finding bugs in programs for graphic cards (\eg{},
-OpenCL). These programs use the Single-Instruction Multiple-Data
-(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
-application of differential testing that received most attention to
-date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
-the use of a generator of sentences from grammars to test correctness
-of automatically generated parsers. After that, significant progress
-has been made. Lammel and Shulte proposed Geno to cross-check XPath
-implementations using grammar-based testing with controllable
-combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
-randomly create C programs from a grammar, for a subset of C, and then
-check the output of these programs in different compilers (\eg{}, GCC
-and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed ``equivalence modulo inputs'', which creates variants of
-program which should have equivalent behavior compared to the
-original, but for which the compiler manifests
-discrepancy. Differential testing has also been applied to test
-refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
-symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
-and very recently to test JavaScript
-debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
-shown to be flexible and effective for a wide range of
-applications. Surprisingly, not much work has been done on
-differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepancies across different configurations of
-the same version of its \smonkey\ engine (using the ``compare\_jit''
-flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
-fuzzing strategy using differential testing. Their focuses on finding
-differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/chapter/threats_validity.tex
added msc-thesis

--- 2019-06-25 paper/paper.tex
@@
-\documentclass[final,5p,times,twocolumn]{elsarticle}
-\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis} 
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifdraftmode
-\draftmodetrue
-
-%% avoid footnotes across pages
-\interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newif\ifshowsplattext
-%\showsplattexttrue
-
-\pagenumbering{arabic}
-
-%% paragraphs within margins
-\usepackage[english]{babel}
-\setlength{\emergencystretch}{2pt}
-\usepackage{booktabs}
-\usepackage{multirow}
-\usepackage{tikz}
-\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
-\usepackage{listings}
-\usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
-\renewcommand{\ttdefault}{pcr}
-\lstset{
-  basicstyle=\scriptsize\ttfamily,
-  keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
-  aboveskip=0pt,
-  belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
-  showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
-  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
-}
-\usepackage{balance}
-\usepackage{wrapfig}
-\usepackage{enumitem}
-\usepackage{url}
-
-\input{macros}
-
-\begin{document}
-
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-
-\author[ufpe]{Igor Lima}
-\ead{isol2@cin.ufpe.br}
-\author[ufpe]{Breno Miranda}
-\ead{bafm@cin.ufpe.br}
-\author[ufpe]{Marcelo d'Amorim}
-\ead{damorim@cin.ufpe.br}
-\address[ufpe]{Universidade Federal de Pernambuco, Recife, PE, Brazil}
-
-%\renewcommand{\shortauthors}{Lima et al.}
-
-\begin{abstract}
-  \input{abstract}
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under 
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
-
-Finding bugs in \js\ engines is an important problem given the range
-of applications that could be affected with those bugs. It is also
-challenging.  Specifications are intentionally incomplete as to enable
-development flexibility. In addition, they evolve frequently to
-accommodate the pressing demands from
-developers~\cite{ecmas262-spec-repo}. An official conformance test
-suite exists for \js~\cite{tc39-github}, but, naturally, many test
-scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
-up with the pace of spec evolution (see Table~\ref{tab:test262}).
-
-%% WHAT WE DID
-This paper reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
-
-%\vspace{-1ex}
-%noitemsep,
-\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
-  written for a given engine in other engines. The intuition is that
-  developers design test cases with different objectives in mind. As
-  such, replaying these tests in different engines could reveal
-  unanticipated problems.
-
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
-\end{itemize}
-
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
-
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
-bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
-It has shown to be specially practical in scenarios where the
-observation of difference gives a strong signal of a real problem. For
-example, Mozilla runs JS files against different configurations of a
-given build of their \smonkey\ engine (\eg{}, trying to enable or not
-eager JIT compilation\footnote{These files are created with the
-  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
-  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
-is that it can be fully automated---as only one engine is used, the
-outcomes of the test in both configurations are expected to be
-identical. The Mozilla team uses this approach since 2002; they have
-been able to find over 270 bugs since
-then~\cite{jsfunfuzz-at-mozilla}, including security
-bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
-exist, other than a bug, for a test execution to manifest discrepancy
-(see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
-
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
-\begin{figure}[t]
-%  \vspace{-2ex}  
-  \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
-    \vspace{-5ex}
-  }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.45\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
-    \vspace{-5ex}        
-  }
-  \caption{\label{fig:summary}Summary of bug reports.}
-  \vspace{-3ex}
-\end{figure}
-
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Note that several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
-indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
-
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
-
-%% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~This paper contributes the following: 1)~A
-comprehensive study to analyze the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
-2)~A number of bugs found and fixed. We reported a total of
-\totalBugsReported{} bugs. Of these, \totalBugsConfirmed{} bugs were
-confirmed and \totalBugsFixed{} bugs were fixed. 3)~An infrastructure
-for diversity-aware testing. The scripts to run the experiments will
-be available upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
-in JavaScript engines.
-
-\section{JavaScript}
-\label{sec:es6-design}
-\label{sec:imp-dep-behavior}
-
-JavaScript engines are virtual machines that parse source code,
-compile it in bytecodes, and run these bytecodes. These engines
-implement some version of the ECMAScript (\es{}), which emerged with
-the goal to standardize variants of the language, such as Netscape's
-JavaScript and Microsoft's JScript\footnote{The name JavaScript still
-  prevails today, certainly for historical reasons.}. The \es{}
-specification is regulated by Ecma International~\cite{es6-website}
-under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
-
-The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
-``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
-\js\ \mcodeid{for-in} loop construct does not clearly specify the
-iteration order of
-elements~\cite{so-forin-undefined,javascript-in-chrome} and different
-engines capitalize on that for loop
-optimizations~\cite{for-in-undefined}.  As another example, the
-specification states that if the \mcodeid{Number.toPrecision()}
-function is called with multiple arguments then the floating-point
-approximation is
-implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
-compatibility table~\cite{kangax}.  It is also worth noting that, as
-in other languages, some elements in JS have non-deterministic
-behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
-produce different outcomes on different runs. Carefully-written test
-cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
-
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
-\section{Engines Studied}
-\label{sec:methodology}
-\label{sec:methodology:engines}~We selected 
-JS engines according to the following criteria: 1) Released latest
-version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
-and 3) Uses a public issue tracker. We looked for highly-maintained
-(as per the first criterion) and popular (as per the second criterion)
-engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
-    \toprule
-    Team & Name & URL & \# Stars  & DOB \\
-    \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
-   \bottomrule     
-  \end{tabular}
-\end{table}
-
-\section{Mined JS Files}
-\label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and 
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all'' 
-shows the number of test cases whose executions do not throw 
-dynamic type errors in any of the engines because of an undefined variable or property. 
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
-
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
-  \begin{tabular}{ccrrrr}
-    \toprule
-    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
-    \multicolumn{4}{c}{\# JS files} \\
-    \cline{3-6}
-                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
-    \midrule
-    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
-    \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
-    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \midrule
-    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\ 
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
-    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
-   \bottomrule 
-  \end{tabular}
-\end{table}
-
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
-non-portable objects. 
-Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines.
-
-\subsection{Mining Tests from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
-cases.
-
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
-To obtain test files included as attachments, we wrote a crawler to
-visit the issue trackers of all engines listed in
-Table~\ref{tab:engines} and we were able to retrieve a total of
-\filesAttached{} files.  To mine tests from the textual descriptions we
-proceeded as follows. First, we broke the text describing the issue in
-paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
-that information, we merged consecutive paragraphs labeled as ``code''
-and used a \js\ parser to check well-formedness of the retrieved code
-fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
-Table~\ref{tab:test-suites}.
-
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos. 
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia 
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary 
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=0.65\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}  
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
-
-\section{Cross-Engine Differential Testing}
-\label{sec:design}
-
-This section describes the infrastructure we used for cross-engine
-differential testing. Figure~\ref{fig:workflow} illustrates the
-workflow of the approach. It takes on input a list of JS files and
-generates warnings on output. Numbered boxes in the figure denote the
-data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
-
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
-input. Otherwise, it considers the input as potentially
-fault-revealing; hence, interesting for human inspection. Finally, to
-facilitate the human inspection process, the infrastructure
-prioritizes warnings and clusters them in groups (step 3). We describe
-these features in Sections~\ref{sec:prioritization} and
-\ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
-Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}) and there is no clear automatic approach
-to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
-earlier, this justifies why differential testing is challenging to
-automate at the functional level.
-
-For step 2, we considered using the open-source tool
-eshost-cli~\cite{eshost-cli}, also used at Microsoft, for checking
-output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
-
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli", 
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao 
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
-\subsection{Prioritization}
-\label{sec:prioritization}
-
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
-  \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
-the infrastructure would report a warning that is more likely to be
-associated with an invalid input produced by the fuzzer, \ie{}, it is
-likely to be a ``bug'' in the test code as opposed to a bug in the
-engine. Recall that, for differential testing, we only use seed tests
-that pass in all engines.
-
-Despite the problem mentioned above, ``\lo'' warnings can reveal bugs.
-Figure~\ref{fig:lo-truepositive} shows one of these cases. In this
-example, the test instantiates an \CodeIn{ArrayBuffer} object and
-stores an 8-bit integer at the 0 position. According to the
-specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
-exception should be thrown if a negative value is passed to the
-function \CodeIn{ToIndex}, indirectly called by the test case from the
-function call \CodeIn{getInt8()}. In this case, however, the \chakra{}
-engine did not throw any exception, as can be confirmed from the
-report that our infrastructure produces starting with text ``Engine
-Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
-
-\subsection{Clusterization}
-\label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
-
-Clusterization is complementary to prioritization; it helps to group
-similar warnings reported by our infrastructure. We only clustered
-``\lo'' warnings as ``\hi'' warnings produce messages that arise from
-the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
-three elements that we use to characterize a warning--1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
-
-\subsection{Fuzzers}
-\label{sec:objects:fuzzers}
-
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
-grammar-based fuzzers--Grammarinator~\cite{grammarinator},
-jsfunfuzz~\cite{jsfunfuzz},
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
-Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
-LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
-publicly available. Another fundamental issue associated with
-generational fuzzers in our context is that the tests they produce do
-not contain assertions; to enable the integration of this kind of
-fuzzers in our infrastructure---we would need to look for
-discrepancies across compiler error messages as opposed to assertion
-violations.  All in all, although grammar-based fuzzers have been
-shown effective to find real
-bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
-fuzzers in this study for the reasons above.
-
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
-properties\footnote{There are options in the clang toolchain to build
-  programs with fuzzing instrumentation~\cite{libfuzzer}. clang
-  provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
-
-We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
-existing inputs randomly. The strength of the approach is
-limited by the quality of the test suite and the supported mutation
-operators, which are typically simple. We chose these specific fuzzers
-because, conceptually, one complements the other. \quickfuzz\ creates
-mutations like \radamsa. However, in contrast to \radamsa, \quickfuzz\ is aware
-of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
-
-\section{Results}
-\label{sec:results}
-
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
-\begin{description}[leftmargin=.5in]
-\item[RQ1.] How conformant are the engines to the Test262 suite?
-\item[RQ2.] How effective is test transplantation to find bugs?
-\item[RQ3.] How effective is cross-engine differential testing to find bugs?  
-\end{description}
-
-The first question focuses on the conformance of our selected engines
-to the official Test262 suite~\cite{ecma262-conformance-suite}
-(Section~\ref{sec:stability}). In the limit, bugs would have low
-relevance if the engines are too unreliable. The second question
-focuses on the effectiveness of test transplantation
-(Section~\ref{sec:transplantation}). The rationale for using inputs
-from different engines is that developers consider different goals
-when writing tests---suites written for a given engine may cover
-scenarios not covered by a different engine. The third question
-evaluates the effectiveness of cross-engine differential testing to
-find bugs (Section~\ref{sec:cross-engine-diff-testing-results}). The
-rationale for this question is that fuzzing inputs may explore
-scenarios not well tested by at least one of the engines.
-
-\subsection{Answering RQ1 (Conformance)}
-\label{sec:stability}
-
-The ECMA Test262~\cite{ecma262-conformance-suite} test suite serves to
-check conformance of engines to the \js\ standard. It is
-acceptable to release engines fulfilling the specification only
-partially~\cite{kangax}. We expect that the pass rate on this suite
-provide some indication of the engine's maturity. In the limit, it is
-not desirable to flood bug reports on engines at early stages of
-development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
-the average number of passing tests over this period. The variance of
-results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
-experiment~\cite{ecma262-conformance-suite}.
-
-\begin{wraptable}[8]{r}{0.22\textwidth}
-  \vspace{-4ex}
-  \centering
-  \caption{\label{tab:test262}Percentage of passing tests on
-    the Test262 conformance suite.}
-  \small
-  \begin{tabular}{crr}
-    \toprule
-    engine & \% passing \\
-    \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
-    \chakra{} & \percentSuiteTestChakra{} \\    
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \bottomrule
-  \end{tabular}
-  \normalsize
-\end{wraptable}
-
-Results show that there are still many unsupported scenarios as can be observed from the
-percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
-Figure~\ref{fig:summary}). Although it is plausible to find
-correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
-to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
-      engines is above 90\%.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ2 (Test Transplantation)}
-\label{sec:transplantation}
-
-This section reports results of test transplantation. More
-specifically, we analyzed the failures observed when running a test
-suite original from a given engine in another engine. Intuitively, we
-want to assess how effective is the idea of cross-fertilization of
-testing knowledge among \js\ developers.
-
-%\vspace{0.5ex}
-\subsubsection{Methodology}
-\label{sec:methodology}
-In this experiment, a developer with experience in \js\ analyzed each
-test failure, affecting a particular engine, and classified that
-failure as potentially fault-revealing or not. The authors supervised
-the classification process to validate correctness. For the
-potentially fault-revealing cases, one of the authors inspected the
-scenario and, if agreed on the classification, reported the bug to the
-issue tracker of the affected engine.
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:cross-testing}Number of failures with
-    Test Transplantation.}
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
-    \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
-    \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
-    \Comment{
-      Lembrar dos testes que os testes da propria engine falham:
-      V8 0 
-      JSC 2 
-      Spidermonkey 58
-    }
-    \jsc{} & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\ 
-   Tiny-js & 0 & 0 & 0 & 0  \\
-    \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
-    \bottomrule 
-  \end{tabular}
-  \vspace{-3ex}
-\end{table}
-
-\subsubsection{Results}
-\label{sec:results}
-
-Table~\ref{tab:cross-testing} shows the number of failures observed
-for each pair of test suite and engine. The first column shows the
-test suites and the first row shows the engines that run those
-tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
-failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
-
-\sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
-manifested when tests cover implementation-dependent behavior, as
-defined in the ECMA262 specification~\cite{ecmas262-spec}. For
-example, one of the tests from \jerry\ uses the function
-\CodeIn{Number.toPrecision([precision])}, which translates a number to
-a string, considering a given number of significant digits. The
-floating-point approximation of the real value is
-implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
-engine that runs the test does not optimize the code as the original
-engine of the test. As result, the test fails to finish at the
-specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
-this kind manifest when a test fails because it covers a function that
-is part of the official spec, but is not implemented in the target
-engine yet. For example, at the time of writing, \chakra{} did not
-implement by default various properties from the \mcodeid{Symbol}
-object. These properties are only available activating the ES6
-experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
-an object property is undefined in the execution engine but we were
-unable to capture that by looking for error types like
-\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
-  we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
-includes other sources of false positives. For example, it includes
-the cases where the test was valid for some previous version of the
-spec but is no longer valid for the current spec.
-
-\begin{wraptable}[11]{r}{0.23\textwidth}
-  \vspace{-4ex}
-  \small
-  \centering
-  \caption{\label{fig:falsepositives}\label{fig:truepositives}\label{fig:piecharts-transplantation}Distribution
-    of False (FP) and True Positives (TP).}
-  \setlength{\tabcolsep}{3pt}      
-  \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{ccr}
-    \toprule
-    & source &  \#\\
-    \midrule
-    \multirow{5}{*}{FP} & Undefined Behavior & \noTransUndefined{} \\
-    & Timeout/OME & \noTransTimeout{} \\
-    & Not Implemented & \noTransNotImplemented{} \\
-    & Non-Standard Element & \noTransNonStandard{} \\
-    & Other & \noTransOther{} \\
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & \noTransTPDuplicated{} \\
-    & Bug & \noTransTPBugs{} \\
-    \bottomrule
-  \end{tabular}
-\end{wraptable}
-
-Table~\ref{fig:piecharts-transplantation} shows the distribution of
-False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
-failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
-positives, ``Undefined Behavior'' was the most predominant
-source. Considering true positives, we found a reasonable number of
-duplicate reports, but not high enough to justify attempting to
-automate the detection of duplicates.
-
-\input{table_transplantation}
-
-Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
-test transplantation. The first column shows the identifier we
-assigned to the bug\Comment{, column ``Date'' shows the date the bug
-  was reported in the format ``m/dd'',}, column ``Engine'' shows the
-affected engine, column ``Status'' shows the status of the bug report
-at the time of the writing. The status string appears in bold face for
-status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
-Column ``Severity'' shows the severity of confirmed bugs, and,
-finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
-\noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing 
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}. 
-However, the bugs the \jsc{} team confirmed were quickly fixed.
-
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Test transplantation was effective at finding
-      functional bugs. Although the cost of classifying failures was
-      non-negligible, the approach revealed several non-trivial bugs
-      in three of the four engines we analyzed.
-      \end{minipage}
-    }
-\end{center}
-
-\subsection{Answering RQ3 (Differential Testing)}
-\label{sec:cross-engine-diff-testing-results}
-
-This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
-\subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
-Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
-QuickFuzz~\cite{quickfuzz} for fuzzing. To avoid experimental noise,
-we only fuzz test files that pass in all engines--a total of
-\totalTestFilesPassInAll\ tests satisfy this restriction. Those tests
-appear under the column ``no-fail-in-all'' on
-Table~\ref{tab:test-suites}.  We want to avoid the scenario where
-fuzzing produces a fault-revealing input based on a test that was
-already revealing failures on some engine. This decision facilitates
-our inspection task; it helps us establish cause-effect relationship
-between fuzzing and the observation of discrepancy.  We configured our
-infrastructure (see Figure~\ref{fig:workflow}) to produce 20
-well-formed fuzzed files per input file, \ie{}, the number of fuzzing
-iterations can exceed the number above as we discard generated files
-that are syntactically invalid.
-
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
-three months of the study, our inspection process was exploratory.  In
-this phase, we wanted to learn whether or not black-box fuzzers could
-reveal real bugs and how effective was the \hi{}-\lo\ warning
-classification.  We expected the number of warnings to increase
-dramatically compared to the previous experiment and, if we realized
-that the ratio of bugs from \lo\ warnings was rather low, we could
-focus our inspection efforts on \hi\ warnings. To run this experiment,
-we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
-graduate-level testing class. We listed warnings in a spreadsheet and
-requested the students to update an ``owner'' column indicating who
-was working on it, but we did not enforce a strict order on the
-warnings the students should inspect. Recall from
-Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
-buckets. For that reason, we only listed one \lo\ warning per
-representative class/bucket in the spreadsheet. First, we explained,
-through examples, the possible sources of false alarms they could find
-and then we asked the students to use the following procedure when
-finding a suspicious warning. Analyze the parts of the spec related to
-the problem and, if still suspicious, look for potential duplicates on
-the bug tracker of the affected engine using related keywords. If none
-was reported, indicate in the spreadsheet that that warning is
-potentially fault-revealing. We encouraged students to use
-lithium~\cite{lithium} to minimize long test cases\Comment{; the tests
-  from the Mozilla suite are often longer than others}. A bug report
-was filed only after one of the authors reviewed the diagnosis. Each
-student found at least one bug using this methodology.
-
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
-similar discipline as before. However, the set of warnings inspected
-and the order of inspection changed. We restricted our analysis to
-\hi\ warnings and, aware that we would be unable to analyze each and
-every warning reported, we grouped those warnings per engine,
-analyzing each group in a round-robin fashion.  At each iteration, we
-analyzed \warningsIteration{} warnings in each group. A warning
-belongs to the group of a given engine if only that engine manifests
-distinct behavior, \ie{}, it produces a distinct output compared to
-others. We separated in a distinct group the warnings for which two
-engines diverge. The rationale for this methodology was to give
-attention to each engine more uniformly, enabling more fair comparison
-across engines.
-
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
-\vspace{0.5ex}
-\subsubsection{Results}~Table~\ref{tab:summary-hi} shows statistics of \hi\ warnings. The table breaks down \hi\ warning by the affected
-engine, \ie, the engine manifesting distinct output among those
-analyzed. Column ``+1'' shows the cases where more than one engine
-disagree on the output. Note from the totals that the ordering of
-engines is consistent with the one observed on
-Table~\ref{tab:cross-testing}, with \chakra\ and \jsc\ in first and
-second places, respectively, in number of warnings.
-
-\begin{table}[t]
-  \small
-  \setlength{\tabcolsep}{4.5pt}
-  \centering
-  \caption{\label{tab:summary-hi}Number of \hi\ warning
-    reports per engine.}
-  \begin{tabular}{crrrrr}
-    \toprule
-    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
-    \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
-    \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Table~\ref{tab:false-positives} shows the distribution of false
-positives per source. The sources of imprecision are as defined in
-Section~\ref{sec:transplantation} with the addition of two new
-sources, which we did not observe before. These new sources are
-marked with a ``*'' in the table. The source ``Invalid Input''
-indicates that the test input violated some part of the
-specification. For example, the test indirectly invoked some function
-with unexpected arguments; this happens because fuzzing is not
-sensitive to function specifications. Consequently, it can replace
-valid with invalid inputs. The source ``Error Message Mismatch''
-corresponds to the cases where the fuzzer modifies the assertion
-expression (\eg{}, some string expression or regular expression).
-
-\begin{table}[t]
-  \small
-  \centering
-  \caption{\label{tab:false-positives}Distribution of False (FP)
-    and True Positives (TP).}
-  \begin{tabular}{ccrr}
-    \toprule
-    & & \radamsa\ & \quickfuzz\ \\
-    \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
-    \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
-    \bottomrule     
-  \end{tabular}
-\end{table}
-
-%% \Igor{devemos remover isso da 
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
-
-Table~\ref{tab:bugs} shows the list of bugs we reported. The table
-shows the fuzzing tool used
-(``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
-that we assigned to the warning that revealed the bug (``Priority''),
-and the test suite from the original test input (``Suite''). So far,
-\noDiffConfirmed{} of the bugs we reported were confirmed, \noDiffFixed{} of which
-were fixed. Note that one bug report that we submitted was rejected on
-the basis that the offending JS file manifested an incompatibility
-across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
-were duplicates and were not reported. For \veight{}, 
-we reported \noDiffVeight{} bugs, 
-all of them confirmed, with \noDiffVeightFixed{} fixed.
-
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
-
-\begin{center}
-  \fbox{
-    \begin{minipage}{8cm}
-      \textit{Summary:}~Cross-engine differential testing was
-      effective at finding \js\ engines bugs, several of which have
-      been fixed already.
-      \end{minipage}
-    }
-\end{center}
-
-\noindent
-\textbf{Data Availability.}~The data, including the tests, warning
-reports, and diagnostic outcomes, is publicly available from a
-preserved repository \dataRepo.
-
-\section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
-
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
-
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
-\sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.}  The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a 
-%%   function declaration. The fuzzer removes the function declaration and 
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError) 
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- var obj = {}; var arr = [];
- try { arr.sort(obj); assert(false);}
- catch (e) { assert(e instanceof TypeError); }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}  
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function, 
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- function test() {
-   return typeof String.prototype.repeat === "function"
-     && "foo".repeat(657604378) === "foofoofoo"; }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}  
-\end{figure}
-
-This is a testcase original from the \jsc{} suite that the
-\radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
-
-\subsection{Threats To Validity}
+\chapter{Threats to Validity}
 
@@
 subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
+threats.
+\section{Internal Validity}
+Considering internal validity, conceptually, it is possible
 that the authors of this paper made mistakes in the implementation of
@@
 carefully inspected the implementation and results, looking for
-inconsistencies whenever possible. As for external validity, our
+inconsistencies whenever possible.
+
+\section{External Validity}
+As for external validity, our
 results might not generalize to other test inputs and engines. To
@@
 engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
-terms of construct validity, we used standard metrics to determine the
+the browsers informally considered the most popular in the market.
+
+\section{Construct Validity}
+In terms of construct validity, we used standard metrics to determine the
 effectiveness of the testing techniques we studied (\eg{}, number of
@@
 severity. Consequently, these metrics originate from a trusted source.
-
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
-\subsection{Key Findings and Lessons}
-\label{sec:lessons}
-
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
-avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
-real bugs is a great way to train (and encourage) students in software
-testing. Students praised the experience of diagnosing failures,
-understanding part of the specs (as needed), writing bug reports,
-participating in discussions on issue trackers, and observing the
-change of status. That was a relatively self-contained hands-on
-activity that enabled students to engage in a real-life serious
-industrial project.
-
-\section{Related Work}
-\label{sec:related-work}
-
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
-
-\subsection{Differential Testing}
-Several different applications of differential testing have been
-proposed in recent years. Chen and
-colleagues~\cite{Chen:2018:RDT:3180155.3180226} recently proposed a
-technique to generate X.509 certificates based on Request For
-Proposals (RFC) as specification with the goal of detecting bugs in
-different SSL/TLS implementations. Those bugs can compromise security
-of servers which rely on these certificates to properly authenticate
-the parties involved in a communication session. Lidbury and
-colleagues~\cite{Lidbury:2015:MCF:2737924.2737986} and Donaldson and
-colleagues~\cite{Donaldson:2017:ATG:3152284.3133917} have been
-focusing on finding bugs in programs for graphic cards (\eg{},
-OpenCL). These programs use the Single-Instruction Multiple-Data
-(SIMD) programming abstraction and typically run on GPUs.  Perhaps the
-application of differential testing that received most attention to
-date was compiler testing. In 1972, Purdom~\cite{Purdom1972} proposed
-the use of a generator of sentences from grammars to test correctness
-of automatically generated parsers. After that, significant progress
-has been made. Lammel and Shulte proposed Geno to cross-check XPath
-implementations using grammar-based testing with controllable
-combinatorial coverage~\cite{10.1007/11754008_2}. Yang and
-colleagues~\cite{Yang:2011:FUB:1993498.1993532} proposed CSmith to
-randomly create C programs from a grammar, for a subset of C, and then
-check the output of these programs in different compilers (\eg{}, GCC
-and LLVM). Le and colleagues~\cite{Le:2014:CVV:2594291.2594334}
-proposed ``equivalence modulo inputs'', which creates variants of
-program which should have equivalent behavior compared to the
-original, but for which the compiler manifests
-discrepancy. Differential testing has also been applied to test
-refactoring engines~\cite{Daniel:2007:ATR:1287624.1287651}, to test
-symbolic engine implementations~\cite{Kapus:2017:ATS:3155562.3155636},
-to test disassemblers and binary
-lifters~\cite{Paleari:2010:NDD:1831708.1831741,Kim:2017:TIR:3155562.3155609},
-and very recently to test JavaScript
-debuggers~\cite{DBLP:conf/sigsoft/LehmannP18}. All in all, it has
-shown to be flexible and effective for a wide range of
-applications. Surprisingly, not much work has been done on
-differential testing of \js\ engines. Mozilla uses differential
-testing to look for discrepancies across different configurations of
-the same version of its \smonkey\ engine (using the ``compare\_jit''
-flag of jsfunfuzz~\cite{jsfunfuzz}) whereas we focus on discrepancy
-across engines. Patra and Pradel evaluated their language-agnostic
-fuzzing strategy using differential testing. Their focuses on finding
-differential bugs across multiple
-browsers~\cite{patra2016learning}. As such they specialized their
-fuzzer to HTML and JS (see Section~\ref{sec:testing-js-engines}). In
-contrast to Patra and Pradel, we did not propose new techniques; our
-contribution was empirical.
-
-\subsection{Testing \js\ Programs}
-Patra and colleagues~\cite{Patra:2018:CFU:3180155.3180184} proposed a
-lightweight approach to detect conflicts in \js\ libraries that occur
-when names introduced by different libraries collide. This problem was
-found to be common as the design of \js\ allows for overlaps in
-namespaces. A similar problem has been investigated by Nguyen and
-colleagues~\cite{nguyen-etal-icse2014} and Eshkevari and
-colleagues~\cite{eshkevari-etal-icpc2014} in the context of PHP
-programs, which are popular in the context of Content Management
-Systems as WordPress. The focus of this paper is on testing
-\js\ engines as opposed to \js\ programs. Our goal is therefore
-orthogonal to theirs.
-
-\subsection{Testing \js{} Engines}
-\label{sec:testing-js-engines}
-The closest work to ours was done by Patra and
-Pradel~\cite{patra2016learning}. Their work proposes a
-language-agnostic fuzzer to find cross-browser HTML+JS
-discrepancies.\Comment{ They applied the proposed fuzzer to find bugs in JS engines and
-Web Assembly engines.} The sensible parts of the infrastructure they
-built are the checks of input validity (as to reduce waste/cost) and
-output correctness (as to reduce false positives). Patra and Pradel
-work is complementary to ours--in principle, we could use their fuzzer
-in our evaluation. The main difference of our work to theirs is in
-goal--we aim at assessing reliability of \js\ engines and find bugs on
-them using simple approaches whereas they aim at proposing a new
-technique.
-
-Fuzzing is an active area of investigation with development of new
-techniques both in academia and industry. Several fuzzing tools exist
-focused on \js. Section~\ref{sec:objects:fuzzers} briefly explain
-different fuzzing strategies and tools. Existing techniques prioritize
-automation with a focus on finding crashes; see the sanitizers used in
-libFuzzer~\cite{libfuzzer-tutorial}, for instance. In general, it is
-important for these tools that a warning reveals something potentially
-alarming as a crash given that fuzzing is a time-consuming operation,
-\ie{}, the ratio of bugs found per inputs generated is often very low.
-Our approach contrasts with that aim as we focus on finding errors
-manifested on the output, which rarely result in crashes and,
-consequently, would go undetected by current fuzzing approaches. It is
-should be noted, however, that such problems are not unimportant as
-per the severity levels reported in
-Tables~\ref{tab:test-transplantation-bugs} and~\ref{tab:bugs}.
-
-\section{Conclusions}
-
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
-JavaScript (\js{}) is very popular today. Bugs in engine
-implementations often affect lots of people and organizations.
-Implementing correct engines is challenging because the specification
-is intentionally incomplete and evolves frequently. Finding bugs in
-\js\ engines is challenging for similar reasons.
-
-This paper reports on a study to evaluate two diversity-aware
-techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
-output produced by different engines with a differential oracle.
-
-We found that both techniques were very effective at finding bugs in
-\js\ engines.  Overall, we reported \totalBugsReported\ bugs in this
-study. Of which, \totalBugsConfirmed\ were confirmed by developers and
-\totalBugsFixed\ were fixed. Although more work is necessary to reduce
-cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
-
-In the near future, we plan to explore techniques to prioritize the
-warnings reported by these techniques and to continue involving
-students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
-seems a promising starting point for this improvement.
-
-The scripts to run the experiments for this study will be available
-upon request. The data is publicly available \dataRepo{}.
-
-\vspace{1ex}
-\sloppy
-\noindent\textbf{Acknowledgments.~}Igor is supported by the FACEPE
-fellowship IBPG-0123-1.03/17. This research was partially funded by
-INES 2.0, FACEPE grants PRONEX APQ 0388-1.03/14 and APQ-0399-1.03/17,
-and CNPq grant 465614/2014-0.
-
-\balance
-\bibliographystyle{elsarticle-num}
-\bibliography{references,tmp}
-
-\end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-01-06 msc-thesis/custom.tex
added msc-thesis

% ----------------------------------------------------------
% DADOS DO TRABALHO - CAPA e FOLHA DE ROSTO
% ----------------------------------------------------------
\titulo{\textbf{Leveraging Diversity to Find Bugs in JavaScript Engines}}
\autor{Igor Simões de Oliveira Lima}
\local{Recife}
\data{2020}
\areaconcentracao{\textbf{Concentration Area}: Software Engineering, Software Testing}
\orientador{\textbf{Advisor}: Marcelo Bezerra d'Amorim}
%\coorientador{Coorientador: Roberto Souto Maior de Barros2}
\instituicao{Federal University of Pernambuco}
\departamento{Centro de Informática}
\programa{Pós-graduação em Ciência da Computação}
\emailprograma{posgraduacao@cin.ufpe.br}
\siteprograma{http://cin.ufpe.br/\textasciitilde posgraduacao}

\tipotrabalho{Tese de Doutorado}
% O preambulo deve conter o tipo do trabalho, o objetivo, 
% o nome da instituição e a área de concentração 
% \preambulo{Tese de Doutorado apresentada ao Programa de Pós-graduação em Ciência da Computação do Centro de Informática da Universidade Federal de Pernambuco, como requisito parcial para obtenção do título de Doutor em Ciência da Computação.}
\preambulo{
A M.Sc. Dissertation presented to the Center of Informatics
of Federal University of Pernambuco in partial fulfillment
of the requirements for the degree of Master of Science in
Computer Science.
}

% \preambuloatadefesa{Tese de Doutorado apresentada ao Programa de Pós-Graduação em Ciência da Computação da Universidade Federal de Pernambuco, como requisito parcial para a obtenção do título de Doutor em Ciência da Computação.}
\preambuloatadefesa{
A M.Sc. Dissertation presented to the Center of Informatics
of Federal University of Pernambuco in partial fulfillment
of the requirements for the degree of Master of Science in
Computer Science.
}

% \renewcommand*{\acronymname}{Abreviaturas e Siglas}

\input{userlists}

% \renewcommand\partname{Part} % menu personalidado

### 2020-01-06 msc-thesis/table_differential.tex
added msc-thesis

\begin{table}[t]
  %\small
  \vspace{-3ex}
  \centering
  \caption{List of bugs reports from Differential Testing.}
  \label{tab:bugs}
  \setlength{\tabcolsep}{1.5pt}
  \renewcommand{\arraystretch}{0.95}
  \begin{tabular}{rcccccccc}
    \toprule
    Issue\#  & Date & Fuzzer & Engine  & Status & Url  & Sev. & Priority & Suite \\
    \midrule
    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
    \href{\repoCH/issues/4978}{\#4978}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  & 4/12 & radamsa & \chakra{}   & WontFix  &
    \href{\repoCH/issues/4979}{\#4979}
    & - & \hi{} & \jsc{} \\
    3  & 4/14 & radamsa & \jsc{}  & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
     & -  & \hi{} & \jsc{}    \\
    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
    \href{\repoCH/issues/5038}{\#5038}
    & 2 & \hi{} & \jerry{}   \\
    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
     & 2  & \hi{}  & \jerry{}\\

    6 & 4/30  & radamsa & \chakra{} & \textbf{Confirmed} &
    \href{\repoCH/issues/5076}{\#5076}
    & 2 & \hi{} & TinyJS\\

    7                    & 4/30                       &  radamsa   &
    \jsc{} & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    & - & \hi{} & TinyJS \\

    8 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}
    & 2 & \textbf{\lo} & \smonkey{} \\
    9 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
    \href{\repoCH/issues/5128}{\#5128}
    & 3 & \hi{} & \jerry{} \\
    10 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
    \href{\repoCH/issues/5182}{\#5182}
    & 2 & \hi{} & \veight{}\\
    11 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}
    & 2 & \hi{} & \jsc{}\\
    12 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
    \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}
    & 2 & \hi{} & \jerry{}\\
    13 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
    \href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}
    & 2 & \hi{} & \jerry{}\\
    14 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
    \href{\repoCH/issues/5443}{\#5443}
    & 2 & \hi{} & \jerry{}\\
    %    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\

    15 & 8/21  & radamsa & \chakra{} & \textbf{Fixed} &
    \href{\repoCH/issues/5617}{\#5617}
    & 3 & \hi{} & Test262\\

    16 & 8/21 & radamsa &
    \veight{} & \textbf{Fixed} &
    \href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}
    & 2 & \hi{} & Test262 \\

    17 & 8/23 & quickfuzz & \jsc{} & New  &
    \href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}
    & - & \hi{} & Test262\\
    18 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
    \href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}
    & 2 & \hi{} & Test262\\

    19 & 8/24  & quickfuzz & \chakra{} & \textbf{Confirmed} &
    \href{\repoCH/issues/5630}{\#5630}
    & 2 & \hi{} & Test262\\

    20 & 8/24 &  quickfuzz & 
    \jsc{} & New &
    \href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}
    & - & \hi{} & Test262 \\

    21 & 8/24 & quickfuzz & \jsc{}  & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}
    & - & \hi{} & Test262\\

    22 & 8/21  & radamsa & \chakra{} & \textbf{Confirmed} &
    \href{\repoCH/issues/5968}{\#5968}
    & 3 & \hi{} & \smonkey{}\\
   \bottomrule
  \end{tabular}
\end{table}

### 2020-01-06 msc-thesis/table_transplantation.tex
added msc-thesis

\begin{table}[t!]
  %\small
%  \setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{0.95}
  %  \vspace{-3ex}
    %  \scriptsize
      \centering
      \caption{List of bugs reports from Test Transplantation.}
      \label{tab:test-transplantation-bugs}

      \begin{tabular}{rcccccc}
        \toprule Issue\# & Date & Engine  & Status & Url & Severity & Suite \\
        \midrule
       1  & 4/18  & \jsc{}  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & - & \jerry{} \\
       2  & 4/23 & \chakra{}  & \textbf{Confirmed}  & \href{\repoCH/issues/5033}{\#5033} & 2 & \smonkey{} \\   
       3  & 4/29 & \chakra{}  & \textbf{Fixed}   & \href{\repoCH/issues/5065}{\#5065} & 2 & \smonkey{} \\
%      \midrule
       4  & \multirow{2}{*}{4/29} & \chakra{} & \textbf{Confirmed} & \href{\repoCH/issues/5067}{\#5067} & 2 & \smonkey{} \\
       5  &  & \jsc{} & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} &  -  & \smonkey{}\\
%      \midrule
       6 & 5/02  & \jsc{} & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & - & \smonkey{} \\
       7 & 5/02  & \jsc{} & \textbf{Confirmed}  & \href{https://bugs.webkit.org/show_bug.cgi?id=185211}{\#185211} & 2 & \smonkey{}\\ % webkit
       %  8 & 5/02  & \chakra{} & \textbf{Confirmed} & \href{\repoCH/issues/5187}{\#5087}}} & 3 & \smonkey{}\\
       8 & 5/17  & \chakra{} & \textbf{Confirmed} & \href{\repoCH/issues/5187}{\#5187} & 2 & \jsc{}\\
       9 & 5/21  & \chakra{} & \textbf{Fixed} & \href{\repoCH/issues/5203}{\#5203} & 2 & \smonkey{}\\
       10 & 6/28  & \chakra{} & \textbf{Confirmed}  & \href{\repoCH/issues/5388}{\#5388} & 2 & \jsc{}\\
       11 & 7/10  & \chakra{} & \textbf{Confirmed} & \href{\repoCH/issues/5442}{\#5442} & 2 & \jerry{}\\ % duktape
       12 & 7/18  & \chakra{} & \textbf{Fixed} & \href{\repoCH/issues/5478}{\#5478} & 2 & \smonkey{}\\
       13 & 7/18  & \jsc{} & New & \href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777} & - & \jerry{}\\
       14 & 7/18  & \chakra{} & \textbf{Fixed} & \href{\repoCH/issues/5549}{\#5549} & 2 & \jerry{}\\ % test262
       15 & 8/07  & \chakra{} & \textbf{Fixed} & \href{\repoCH/issues/5576}{\#5576} & 3 & \jerry{}\\
       16 & 8/07  & \jsc{} & \textbf{Fixed} & \href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378} & 2 & \jerry{}\\
       17 & 8/07  & \chakra{} & \textbf{Confirmed} & \href{\repoCH/issues/5579}{\#5579} & 3 & \jerry{}\\
       18 & 8/07  & \jsc{} & \textbf{Fixed} & \href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382} & 2 & \jerry{}\\
       19 & 8/08  & \veight{} & \textbf{Fixed} & \href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033} & 3 & \jerry{}\\
       20 & 8/08  & \jsc{} & New & \href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407} & - & \jerry{}\\
       21 & 8/16  & \veight{} & WontFix & \href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064} & 2 & Duktape\\
       22 & 8/22  & \chakra{} & \textbf{Fixed} & \href{\repoCH/issues/5621}{\#5621} & 2 & \smonkey{}\\
       23 & 8/22  & \jsc{} & \textbf{Fixed} & \href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874} & 2 & \smonkey{}\\
       24 & \multirow{3}{*}{8/22} & \jsc{} & New & \href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875} & - & \smonkey{}\\
       25 &  & \veight{} & \textbf{Fixed} & \href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082} &  2  & \smonkey{}\\
       26 &  & \chakra{} & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624} &  2  & \smonkey{}\\
       27 & 8/23  & \jsc{} & New & \href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877} & - & \smonkey{}\\
       \bottomrule
      \end{tabular}
      \vspace{-2ex}
\end{table}

### 2020-04-15 paper/SQJ-answers_to_reviewers.txt
Added file to track answers to reviewers

====================
Associate Editor
====================

AE1: Other than answering the many punctual questions of the reviewers, I urge the authors to reconsider the way the current manuscript frames their contribution and novelty claims, since both reviewers express strong complains.

ANSWER: ?????

AE2: The concepts of diversity and diversity-awareness seem badly characterised. A reviewer complains that test transplantation and differential testing are techniques for test reuse and test oracles but defining them as diversity-aware techniques appears arbitrary, and distracts from understanding the actual contribution of the paper.

ANSWER: ?????

AE3: Another reviewer complains about the novelty of the findings, since it is known that test transplantation and differential testing can help to reveal bugs. Possibly the authors should partially downgrade or at least re-argue their novelty claims.

ANSWER: ?????

====================
Reviewer #1
====================

R1-1: This paper is well written and presents interesting experiments that exposed confirmed JS engine bugs.
The experiments are well designed and clearly explained.

ANSWER: Thank you.

*R1-2: My main criticism of this paper is the concept of "diversity" that the authors used to frame this work.
As stated in the paper this work has the objective to evaluate the importance of diversity to find functional bugs.
Claiming that test transplantation and cross-engine differential testing are "diversity-aware techniques" Why is that?
Test transplantation simply re-uses tests for one engine to test another engine, it does not make sure that the tests are different.
It just passively re-use tests without promoting diversity.
Differential testing compares the results of executing the same tests on different engines, it is not a diversity aware technique.
As such, the explanation in the introduction of why test transplantation and differential testing are diversity-aware is a bit artificial.
Moreover, the authors at page 2 stated that "this paper explores diversity of implementations and diversity of sources of test cases as opposed to diversity of the test cases themselves."
I think this creates an overload and confusion of the term diversity.
Framing the work on this concept of diversity is artificial and distracts the reader from the main objective of this paper: showing that test transplantation and differential testing can be useful in exposing bugs in JS engines.

ANSWER: ?????

R1-3: The technical contribution of this paper is not well stated, what are the challenges of applying test transplantation, fuzzy and differential testing for JS engines?

ANSWER: ?????

R1-4: Since the input of a JS engine is a JS program, why we need test transplantation or fuzzy generators? Why we cannot rely on a corpus of JS programs as tests?

ANSWER: ?????

R1-5: Page 3 line 24, please explain this sentence: "One possible reason is that it is still not practical to fully automate the technique."
why is not practical, what are the challenges of differential testing in this context?

ANSWER: ?????

R1-6: Page 4, some claiming in the key findings are not justified. Did you check if the tests implemented for different JS engines are really different? How to measure test diversity across different implementations? Again the concept of diversity is not clear in this paper.

ANSWER: ?????

R1-7: Page 6 line 40, why discard tests that require external libraries?

ANSWER: ?????

R1-8: Page 7 Section 4.1. Indeed, issue trackers contain many tests, but usually, these tests are added to the test suite for regression. Did you check if the tests extracted from the issue tracker were duplicates with the one in the test suite?

ANSWER: ?????

R1-9: Page 7 Lines 24 to 41. The NN to recognise ``code'' and ``non code'' is not well-motivated. Why don't just assume that all file is "code"? Since for differential testing, you will exclude those tests that fail on all engines, in this case, invalid inputs will be automatically ignored. Is this approach motivated? Is it really needed? Or all "non code" files will make all engine fails? Please provide empirical evidence that this extra step is needed.

ANSWER: ?????

R1-10: Page 7 It is also unclear why you use word2vec. Word2vec is used to measure the semantic similarity between two words. Word2vec analyzes a set of documents and trains a model that embeds words into a vector space, where words with similar semantics are close in the space. Why you need semantic similarity?

ANSWER: ?????

R1-11: Page 8 You mentioned that differential testing is challenging because a human need to inspect the differences? How you addressed the challenge? Do you address the challenge?

ANSWER: ?????

*R1-12: Page 9 I don't understand why you didn't mine JS programs from github, these would have yielded to a larger set of tests.

ANSWER: ?????

R1-13: Page 11 It is unclear why you ran the suite once a day for seven consecutive days and averaged the passing ratios. Why once a day? and why you do this? For detecting and avoid flakiness tests? Why you didn't run the tests 7 times the same day?

ANSWER: ?????

R1-14: Page 14 how did you decided FP and TP? One author or multiple authors of this paper participated in the labelling?

ANSWER: ?????

R1-15: Page 21 Given lesson 3) why you motivated the paper saying that differential testing is challenging? What are the technical challenges entailed by differential test JS engines that this paper address?

ANSWER: ?????

====================
Reviewer #2: 
====================

R2-1: Overall, the authors did non-trivial engineering work, conducted an interesting experiment, and made a good contribution to the open-source community by reporting those bugs.

ANSWER: Thank you.

*R2-2: However, as a scientific study, the key findings listed in Section 1 are not very novel:
1. It is not surprising to find some bugs if running a different set of test suites (with thousands of test cases) from a different engine.
2. Although the ECMAScript is very well-defined (most parts of the specification are pseudocode), it is also well-known that the specification does not define everything and that JavaScript engines vary in those undefined behaviors. Therefore, the results obtained in RQ1 are not novel.
3. "Differential testing is feasible on real, complex, widely used pieces of software." This is also not a novel finding. People have been using differential testing on C/C++ compilers and JVMs. The following paper is one example: Coverage-Directed Differential Testing of JVM Implementations [PLDI'16]

ANSWER: ?????

*R2-3: I think a more impactful contribution would be to categorize all those extracted test files and to release an open-source project that automates the testing techniques proposed in this paper on any JavaScript engine binary (e.g., Hermes, JerryScript, or Duktape, etc.).

ANSWER: ?????

R2-4: In Section 3, the paper claimed to have tested the Microsoft Chakra engine. However, I believe the authors meant the ChakraCore engine, which is the open-sourced variation of the Chakra engine. Moreover, Microsoft announced a year ago that the Edge browser will be based on Chromium. I believe ChakraCore is not being actively developed anymore. I understand that the experiment might be done a while ago. The paper should clarify the version number of JavaScript engines under test and document when the bug reports got confirmed.

ANSWER: ?????

R2-5: Facebook released Hermes, which is a JavaScript engine designed for ReactNative and mobile devices. It would be interesting to see how many bugs can be found on Hermes.

ANSWER: ?????

R2-6: Section 4 - The structure of this section could be improved. The authors should probably put the description of test cases from all engines in one subsection, and description of test files mined from issue tracker in a parallel subsection.

ANSWER: ?????

R2-7: "We did not consider tests from the Chakra repository because they dependent on non-portable objects". Please explain in detail and give an example of the non-portable objects.

ANSWER: ?????

R2-8: "This classifier is publicly available from our website as a separate component". Not sure which website the author is referring to. It would be great to provide a permanent link.

ANSWER: ?????

R2-9: Section 4.1 - The paper also mentioned that 1,240 JavaScript files are crawled from the issue tracker. Those files are used as test drivers in the experiment. How many bugs come from the issue tracker? If a bug is revealed by a file uploaded to the issue tracker, why the JavaScript engine maintainers didn't fix them in the first place?

ANSWER: ?????

R2-10: Section 5.1 - Is the test case in Figure 3 crawled from ChakraCore's codebase? Or is it revealed after a fuzzer mutates the argument of getView?

ANSWER: ?????

R2-11: Section 5.2 - How effective is the clusterization?

ANSWER: ?????

R2-12: Section 5.3 - The selection of fuzzer does not sound convincing to me. The authors mentioned that some fuzzers (e.g., AFL) are not used in the experiments because they produce test input that is not syntactically valid. However, they chose radamsa, which is a general-purpose fuzzer that may also produce syntactically invalid inputs.

ANSWER: ?????

R2-13: Section 6.1 - The ECMAScript conformance statistics of JavaScript engines are already publicly available on the Internet from multiple sources. Therefore, the findings in Section 6.1 are not novel. Moreover, JavaScript engines are evolving quickly, the manuscript should report date and engine versions associated with those conformance numbers.

ANSWER: ?????

R2-14: Section 6.2 - Since the authors mined test files from Duktape, JerryScript, JSI, and Tiny-js. It seems natural to run test transplantation on these engines, which may reveal more bugs. It would be good to explain why the authors did not do so.

ANSWER: ?????

R2-15: Since the manuscript is suggesting that test transplantation is effective for testing complex software. It would be great to quantify the manual work required to transplant tests (written in JavaScript) from one engine to another. For example, how many non-portable harness functions are mocked for each transplantation?

ANSWER: ?????

R2-16: Section 6.3 - Please provide a more detailed description of the configuration of the two black-box mutation fuzzers. How many valid and invalid inputs are generated by the fuzzers?
The description should also report the time spent in fuzzing and the number of machines (including hardware configuration) used for differential testing.

ANSWER: ?????

R2-17: In the first row of Table 7, the total number of "hi" warnings of JSC, V8, ChakraCore, and SpiderMonkey is only 626, while the "+1" column is 628, which is more than the total number of the previous columns combined. Please double-check the data.

ANSWER: ?????

R2-18: Section 7 looks more like a "Case Study" section instead of a "Discussion" section.
It would be interesting to analyze why test transplantation could reveal some bugs. Does each engine focus on testing different aspects? What kind of tests are more likely to expose bugs?

ANSWER: ?????

R2-19 (minor issues): Please clean up or use a consistent format for the following text:
"[Cleansing]" on line 40 of page 6.
"[Test Harness]" on line 46-47 of page 6.
"[Exploratory Phase.]" on line 23, page 16
"[Non-Exploratory Phase.]" on line 46-47, page 16
Ecmascript 6 -> "ECMAScript 6"
"well tested" -> "well-tested"

ANSWER: ?????

R2-20: The references use too many external links to websites, which may not be available in the next few years or decades.

ANSWER: ?????

### 2020-05-23 paper/abstract.tex
Revised the whole text and removed instances of diversity ou diversity-aware

@@
-\textbf{Context.} JavaScript is a very popular programming language today with several
+\textbf{Context.} 
+JavaScript is a very popular programming language today with several
 implementations competing for market dominance. Although a
@@
 incomplete and evolves frequently.
-\textbf{Objective.} This paper evaluates the importance of
-diversity to find functional bugs in JavaScript engines. \textbf{Method.} For that, we
-explored two existing diversity-aware techniques---test transplantation and
-cross-engine differential testing. The first technique runs test
-suites of a given engine in another engine. The second technique
-fuzzes existing inputs and then compares the output produced by
-different engines with a differential oracle.
-\textbf{Results.} We considered engines from four major players in our
-experiments--Apple, Google, Microsoft, and Mozilla. Our results
-indicate that both techniques revealed several bugs, many of which
+\textbf{Objective.} 
+This paper investigates the use of test transplantation and differential testing
+for revealing functional bugs in JavaScript engines.
+The former technique runs test suites of a given engine on another engine. 
+The latter technique fuzzes existing inputs 
+and then compares the output produced by different engines with a differential oracle.
+\textbf{Method.} 
+We conducted experiments with engines from four major players
+--Apple, Google, Microsoft, and Mozilla--to assess the effectiveness of 
+test transplantation and differential testing.
+\textbf{Results.} 
+Our results indicate that both techniques revealed several bugs, many of which
 confirmed by developers. We reported \noBugsTransplantation{} bugs
@@
 most of these bugs affected two engines--Apple's
-\jsc{} and Microsoft's \chakra{}. To summarize, our results show that
-diversity-aware techniques are easy to apply and very effective in
+\jsc{} and Microsoft's \chakra{}. 
+To summarize, our results show that
+test transplantation and differential testing
+are easy to apply and very effective in
 finding bugs in complex software, such as JavaScript engines.

### 2020-05-23 paper/paper.tex
Revised the whole text and removed instances of diversity ou diversity-aware

@@
 
-\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
+%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
+\title{New title}
 %\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head
@@
   \input{abstract}
-  \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
+  %\keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
+  \keywords{Test Transplantation \and Differential Testing \and JavaScript}
 \end{abstract}
@@
 %% WHAT WE DID
-This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
-to find bugs in JavaScript engines; it covers two complementary
-diversity-aware testing techniques.
+This work, which is empirical in nature, reports on a study to evaluate
+the ability of two testing techniques to expose bugs in JavaScript engines.
 
@@
 \begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation} leverages diversity of test
-  cases. This technique evaluates the effect of running test files
+\item \emph{Test transplantation}. 
+  This technique evaluates the effect of running test files
   written for a given engine in other engines. The intuition is that
@@
 
-\item \emph{Cross-engine differential testing} leverages diversity of
-  engine implementations. This technique fuzzes existing test
+\item \emph{Cross-engine differential testing}. 
+  This technique fuzzes existing test
   inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines.\Comment{ using a differential
-    oracle.} The intuition is that interesting inputs can be created
+  produced by different engines using a differential
+  oracle. The intuition is that interesting inputs can be created
   from existing inputs and multiple engines can be used to address the
@@
 %% system's implementations to detect anomalous behavior.
-\emph{Related Ideas.}~The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
-to prior work on this topic, this paper explores diversity of
-implementations and diversity of sources of test cases as opposed to
-diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-elaborates related work on this topic. Differential
-Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
-contexts to find
+%\emph{Related Ideas.}~The idea of test set diversity dates back to the
+%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
+%to prior work on this topic, this paper explores diversity of
+%implementations and diversity of sources of test cases as opposed to
+%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
+%elaborates related work on this topic.
+%
+\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT) 
+has been applied in a variety of contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). To sum up, variations of these ideas have
+~\ref{tab:false-positives}). Variations of these ideas have
 been explored before in different contexts.  The goal of the paper is
@@
 \emph{Contributions.}~The most important contribution of this work is empirical: 
-we provide a comprehensive study analyzing the effectiveness of diversity-aware
-techniques to find functional bugs in popular \javascript\ engines.
+we provide a comprehensive study analyzing the effectiveness of 
+test transplantation and differential testing
+in revealing functional bugs in popular \javascript\ engines.
 Additional contributions are:
@@
 Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
-2)~An infrastructure for diversity-aware testing.
+2)~An infrastructure for performing test transplantation and differential testing.
 The scripts to run the experiments will be available upon request. 
@@
 \vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring diversity should be encouraged to find functional bugs
+that exploring test transplantation and differential testing
+should be encouraged to find functional bugs
 in JavaScript engines.
@@
 
-The goal of this paper is to assess ability of techniques that
-leverage diversity to find functional bugs
+The goal of this paper is to assess ability of 
+test transplantation and differential testing
+to find functional bugs
 in \javascript\ engines. Based on that, we pose three questions:
@@
 
-\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
+\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
 three months of the study, our inspection process was exploratory.  In
@@
 \vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
+\lbrack{}Non-Exploratory Phase\rbrack{} Results obtained in the
 exploratory phase confirmed our expectations that most of the bugs
@@
 
-\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-The idea of test set diversity dates back to the
-eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
-assumption behind test set diversity is that faults often spread
-contiguously in the input domain. Consequently, it should be
-beneficial to partition the input domain and explore it more evenly as
-to find bugs faster. Later in the nineties, Chen and
-Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-the continuity assumption. They found that faults, most often,
-manifest themselves in regular patterns across the input
-domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-observations led researchers to investigate generalizations of the
-approach to non-numerical data types and strategies to explore the
-input (or output) space to solve different problems in Software
-Engineering (\eg{}, test input generation and test
-selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-paper explores diversity of sources of test cases and diversity of
-engine implementations. We remain to investigate the diversity of test
-cases themselves. In principle, that could help reduce the number of
-alarms to inspect, for example.
+%\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
+%The idea of test set diversity dates back to the
+%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
+%assumption behind test set diversity is that faults often spread
+%contiguously in the input domain. Consequently, it should be
+%beneficial to partition the input domain and explore it more evenly as
+%to find bugs faster. Later in the nineties, Chen and
+%Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
+%the continuity assumption. They found that faults, most often,
+%manifest themselves in regular patterns across the input
+%domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
+%observations led researchers to investigate generalizations of the
+%approach to non-numerical data types and strategies to explore the
+%input (or output) space to solve different problems in Software
+%Engineering (\eg{}, test input generation and test
+%selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
+%paper explores diversity of sources of test cases and diversity of
+%engine implementations. We remain to investigate the diversity of test
+%cases themselves. In principle, that could help reduce the number of
+%alarms to inspect, for example.
 
@@
 
-This paper reports on a study to evaluate two diversity-aware
+This paper reports on a study to evaluate two
 techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique explores
-diversity of test sources; it runs the test suite of one given engine
-in another engine. The second technique explores diversity of
-implementations; it fuzzes existing inputs and then compares the
+cross-engine differential testing. The first technique 
+runs the test suite of one given engine in another engine. 
+The second technique fuzzes existing inputs and then compares the
 output produced by different engines with a differential oracle.
@@
 cost of manual analysis, we found that our results provide strong
-evidence that exploring diversity should be encouraged to find
-functional bugs in JavaScript engines.
+evidence that exploring test transplantation and differential testing 
+should be encouraged to find functional bugs in JavaScript engines.
 

### 2020-06-01 paper/paper.tex
Updated title
edits

--- 2019-12-03 paper/paper.tex
@@
 \usepackage{tikz}
+\usepackage{xspace}
 \usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
@@
   \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
+  \subfloat[\label{fig:stacked-engine}Bug reports per engine.\Gustavo{Não esquecer de atualizar as figuras.
+  }]{
     \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
@@
 \sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
-\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
-bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
+(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
+\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
+(\ref{fig:stacked-technique}).
+\Fix{Jefferson, atualize a figura!}
+Each stacked bar breaks down the bugs
 per status (\eg{}, ``1-New''). The prefix number indicates the

### 2020-06-01 paper/paper.tex

--- 2020-05-23 paper/paper.tex
@@
 %\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-\title{New title}
+\title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
 %\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

### 2020-06-03 paper/abstract.tex
edits no abstract

@@
 \textbf{Method.}
-We conducted experiments with engines from four major players
---Apple, Google, Microsoft, and Mozilla--to assess the effectiveness of 
+We conducted experiments with engines from five major players
+--Apple, Google, Microsoft, Facebook, and Mozilla--to assess the effectiveness of 
 test transplantation and differential testing.

### 2020-06-03 paper/paper.tex
Atualização de tabelas e figuras

@@
     \multicolumn{1}{c}{1100+} & Mar 1996\\
+    Facebook & \hermes{} & \cite{hermes2020repo} &
+    \multicolumn{1}{c}{5400+} & Jun 2019\\
    \bottomrule
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
+    Hermes & \cite{jsi} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{}\\
     \midrule

### 2020-06-03 paper/paper.tex
Moved comment outside subfloat

--- 2020-06-01 paper/paper.tex
@@
   \centering
-  \subfloat[\label{fig:stacked-engine}Bug reports per engine.\Gustavo{Não esquecer de atualizar as figuras.
-  }]{
+  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
     \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
@@
   }
-  \caption{\label{fig:summary}Summary of bug reports.}
+  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
+  }}
   \vspace{-3ex}

### 2020-06-05 paper/abstract.tex
pass on intro

--- 2020-05-23 paper/abstract.tex
@@
 \textbf{Context.}
-JavaScript is a very popular programming language today with several
+JavaScript is a popular programming language today with several
 implementations competing for market dominance. Although a
@@
 \textbf{Objective.}
-This paper investigates the use of test transplantation and differential testing
-for revealing functional bugs in JavaScript engines.
-The former technique runs test suites of a given engine on another engine. 
-The latter technique fuzzes existing inputs 
-and then compares the output produced by different engines with a differential oracle.
+This paper investigates the use of test transplantation and
+differential testing for revealing functional bugs in JavaScript
+engines.  The former technique runs the regression test suite of a
+given engine on another engine.  The latter technique fuzzes existing
+inputs and then compares the output produced by different engines with
+a differential oracle.
 \textbf{Method.}
-We conducted experiments with engines from four major players
---Apple, Google, Microsoft, and Mozilla--to assess the effectiveness of 
-test transplantation and differential testing.
+We conducted experiments with engines from five major players--Apple,
+Google, Microsoft, Facebook, and Mozilla--to assess the effectiveness
+of test transplantation and differential testing.
 \textbf{Results.}

### 2020-06-05 paper/paper.tex
pass on intro

@@
 
-\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
+\author{Jefferson Silva \and Igor Lima \and Breno Miranda\footnotemark
+  \and Gustavo Pinto \and Marcelo d'Amorim}
 %\authorrunning{Short form of author list} % if too long for running head
@@
 * Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
+Jefferson Silva \and \email{jefferson.alves.silva@icen.ufpa.br}\\
 Igor Lima \and \email{isol2@cin.ufpe.br} \\
+Gustavo Pinto \and \email{gpinto@ufpa.br} \\
 Breno Miranda \and \email{bafm@cin.ufpe.br} \\
@@
 JavaScript (\js{}) is one of the most popular programming languages
-today~\cite{stackify,redmonk-javascript}, with penetration in various software development segments including, web, mobile,
-and, more recently, the Internet of
-Things~(IoT)~\cite{simply-technologies}. The interest of the community
-for the language encourages constant improvements in its specification~\cite{ecmas262-spec}. It is natural to expect that such improvements
-lead to sensible changes in engine implementations~\cite{kangax}. Even small
-changes can have high practical impact. For example, in October 2014 a
-new attribute added to Array objects resulted in the MS Outlook
-Calendar web app, which is built in \js{}, to fail under
-Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
+today~\cite{stackify,redmonk-javascript}, with penetration in various
+software development segments including, web, mobile, and, more
+recently, the Internet of Things~(IoT)~\cite{simply-technologies}. The
+interest of the community for the language encourages constant
+improvements in its specification~\cite{ecmas262-spec}. It is natural
+to expect that such improvements lead to sensible changes in engine
+implementations~\cite{kangax}. Even small changes can have high
+practical impact. For example, in October 2014 a new attribute added
+to Array objects resulted in the MS Outlook Calendar web app to fail
+under Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}.
 
@@
 scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests fail regularly in the
-most popular engines, reflecting the struggle of developers in keeping
+significant fraction (5 to 15\%) of the tests in that stuite fail
+regularly in the most popular engines, reflecting the struggle of developers in keeping
 up with the pace of spec evolution (see Table~\ref{tab:test262}).
@@
 
-\item \emph{Cross-engine differential testing}.
-  This technique fuzzes existing test
-  inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines using a differential
-  oracle. The intuition is that interesting inputs can be created
-  from existing inputs and multiple engines can be used to address the
-  lack of oracles.
+\item \emph{Cross-engine differential testing}.  This technique fuzzes
+  existing test inputs~\cite{fuzz-testing-history} and then compares
+  the output produced by different engines using a differential
+  oracle. The intuition is that interesting inputs can be created from
+  existing inputs and multiple engines can be used to address the lack
+  of oracles for the newly created inputs.
 \end{itemize}
@@
 The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality.
+the impact of false positives on their practicality. \Mar{seria bom
+  adicionar uma frase com rationale para escolha destas tecnicas.}
 
@@
 %
-\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT)
-has been applied in a variety of contexts to find
+\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07}
+(DT) has been applied in a variety of contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 bugs. Cross-engine differential testing, in contrast, has not been
-widely popularized. One possible reason is that it is still not
-practical to fully automate the technique. In contrast to other
-applications of differential testing, a number of legitimate reasons
+widely popularized because the reported differences are more unlikely
+to be false alarms. In this context, a number of legitimate reasons
 exist, other than a bug, for a test execution to manifest discrepancy
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). Variations of these ideas have
-been explored before in different contexts.  The goal of the paper is
-to assess the ability of the techniques aforementioned in finding bugs
-on \javascript\ engines.
+~\ref{tab:false-positives}). As consequence, humans need to inspect
+the reports.
+
+%Variations of these ideas have been explored before in different contexts.
+
+%It is important to note that the goal of the paper is to assess the
+%ability of the techniques aforementioned in finding bugs on \javascript\ engines.
 
@@
 
-\sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
-\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}).
-\Fix{Jefferson, atualize a figura!}
-Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
+\sloppy \emph{Results.}~Our study considered the following
+engines--\chakra{}~(Microsoft), \hermes~(Facebook),
+JavaScriptCore~(Apple), \smonkey{}~(Mozilla), and
+\veight{}~(Google). Figure~\ref{fig:summary} shows the breakdown of
+bug reports per engine (\ref{fig:stacked-engine}) and per technique
+(\ref{fig:stacked-technique}).  \Fix{Jefferson, atualize a figura!
+  Estranho nao ter pilha para as 5 engines.}  Each stacked bar breaks
+down the bugs per status (\eg{}, ``1-New''). The number indicates the
+ordering that status labels are assigned by developers: ``New'', then
+``Confirmed'', then ``Fixed''. Several of these reports have the label
+``3-Fixed'', indicating that bug fixes have been incorporated into the
+code already. Note that most of these bugs affected two
+engines--\chakra{} and JavaScriptCore (\jsc{}).  We reported
+\noBugsBugsReportedGoogle{} bugs in \veight{}
 (\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
@@
 
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
+\emph{Key Findings.}~We found that--1)~Differential testing and Test
+Transplation are practical and effective to find bugs on real,
+complex, and widely used pieces of software, 2)~Even for problems with
+fairly clear specifications, as in \javascript{}, there is likely (a
+lot of) variation between different
+implementations. Section~\ref{sec:lessons} expands and elaborates key
 findings and lessons learned.
@@
 %% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~The most important contribution of this work is empirical:
-we provide a comprehensive study analyzing the effectiveness of
-test transplantation and differential testing
-in revealing functional bugs in popular \javascript\ engines.
-Additional contributions are:
-1)~A number of bugs found and fixed.
-We reported a total of \totalBugsReported{} bugs.
-Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed.
-2)~An infrastructure for performing test transplantation and differential testing.
-The scripts to run the experiments will be available upon request.
-The data is publicly available \dataRepo{}.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring test transplantation and differential testing
-should be encouraged to find functional bugs
-in JavaScript engines.
+\emph{Contributions.}~The most important contribution of this work is
+empirical: we provide a comprehensive study analyzing the
+effectiveness of two practical techniques in revealing functional bugs
+in popular \javascript\ engines. The results of the study include:
+1)~A number of bugs found and fixed and 2)~An infrastructure for
+performing test transplantation and differential testing. Our data and
+tools are publicly available under the following link:
+
+\dataRepo{}.
+
+\vspace{1ex} To summarize, this paper provides initial, yet strong
+evidence, that exploring test transplantation and differential testing
+is practical to find functional bugs in JavaScript engines and should
+be encouraged.
 

### 2020-06-05 paper/paper.tex
fixing tabble with versioning info

--- 2020-06-03 paper/paper.tex
@@
   }
-  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
-  }}
+  \caption{\label{fig:summary}Summary of bug reports.}
   \vspace{-3ex}
@@
 (\ref{fig:stacked-technique}).
-\Fix{Jefferson, atualize a figura!}
 Each stacked bar breaks down the bugs
@@
 2)~An infrastructure for performing test transplantation and differential testing.
-The scripts to run the experiments will be available upon request.
-The data is publicly available \dataRepo{}.
+Both the scripts to run the experiments and the data processed are publicly available at \dataRepo{}.
 
@@
 reasons. Certain parts of the specification are undefined; it is
-responsibility of engineers to decide how to implement these
+the responsibility of engineers to decide how to implement these
 functionalities. The JavaScript spec uses the label
@@
 may differ from engine to engine. One reason this flexibility in the
-spec exists is to enable compiler optimizations. For example, the
+spec exists to enable compiler optimizations. For example, the
 \js\ \mcodeid{for-in} loop construct does not clearly specify the
@@
 behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
-that make decisions based on these elements could, in principle,
+that makes decisions based on these elements could, in principle,
 produce different outcomes on different runs. Carefully-written test
@@
   \caption{\label{tab:engines}Engines selected.}
-  \begin{tabular}{cccrr}
+  \begin{tabular}{cccrrr}
     \toprule
-    Team & Name & URL & \# Stars  & DOB \\
+    Team & Name & URL & \# Stars  & DOB & Version \\
     \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
-    \multicolumn{1}{c}{3300+} & Jun 2001\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
-    \multicolumn{1}{c}{1100+} & Mar 1996\\
+    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 & xxxx\\
+    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 & 8.4.138\\
+    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 & xxxx\\
+    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 & 76.0b6\\
+    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 & 0.5.0\\
    \bottomrule
@@
 \end{table}
+
+% hermes very first commit: https://github.com/facebook/hermes/commit/f22a18f67da3f03db59c1ec715d6ec3776b03fbf
 

### 2020-06-05 paper/SQJ/old_version.tex

--- 2020-06-03 paper/paper.tex
@@
-%\documentclass[final,5p,times,twocolumn]{elsarticle}
 \documentclass[smallextended]{svjour3}
-%\biboptions{numbers,sort&compress}
-%\documentclass[sigconf,review, anonymous]{acmart}
-%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis}
-%\input{packages}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Comment the \draftmodetrue line before submission
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newif\ifdraftmode
@@
 
-%% avoid footnotes across pages
 \interfootnotelinepenalty=10000
-%\raggedbottom
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Uncomment \showsplattexttrue to show text from our splat paper
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \newif\ifshowsplattext
-%\showsplattexttrue
 
@@
 
-%% paragraphs within margins
 \usepackage[english]{babel}
@@
 \usepackage{tikz}
-\usepackage{xspace}
 \usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
@@
 \usepackage[caption=false, font=footnotesize]{subfig}
-%%%%%%%%%%%%% code listing
 \renewcommand{\ttdefault}{pcr}
@@
   keywordstyle=\scriptsize\ttfamily\bfseries,
-  language=Java,             % choose the language of the code
-  frame=single,              % adds a frame around the code
+  language=Java,             
+  frame=single,              
   aboveskip=0pt,
   belowskip=0pt,
-  breaklines=true,           % sets automatic line breaking
-  breakatwhitespace=false,   % sets if automatic breaks should only happen at
+  breaklines=true,           
+  breakatwhitespace=false,   
   showspaces=false,
-  %numbersep=5pt,              % Abstand der Nummern zum Text
-  %tabsize=2,                  % Groesse von Tabs
-  %extendedchars=true,         %
-  %breaklines=true,            % Zeilen werden Umgebrochen
   keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
@@
 
-\input{macros}
+\newcommand{\js}{JS}
+\newcommand{\javascript}{JavaScript}
+\newcommand{\es}{ES}
+\newcommand{\ecmascript}{\es{}}
+\newcommand{\tname}{TNAME}
+\newcommand{\Comment}[1]{}
+\newcommand{\numsubjects}{5}
+\newcommand{\etal}{and colleagues'}
+\newcommand{\ie}{i.e.}
+\newcommand{\eg}{e.g.}
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{{\color{red}\ding{55}}}
+\newcommand{\pGoodGood}{$\mathit{P}${\small\cmark\!\cmark}}
+\newcommand{\pGoodBad}{$\mathit{P}${\small\cmark\!\xmark}}
+\newcommand{\pBadDontCare}{$\mathit{P_?}$}
+\newcommand{\sfl}{SFL\xspace}
+\newcommand{\ddg}{DDG\xspace}
+\newcommand{\totfiles}{$\sim$38K}
+
+\newif\ifdraftmode
+\draftmodetrue
+\ifdraftmode
+ \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
+ \newcommand{\Mar}[1]{\textbf{[[Marcelo: }{\color{magenta} #1}\textbf{]]}}
+ \newcommand{\Igor}[1]{\textbf{[[Igor: }{\color{blue} #1}\textbf{]]}}
+ \newcommand{\notes}[1]{\todo[inline,color=red!30,caption={}]{#1}}
+\else
+ \newcommand{\Fix}[1]{\relax}
+ \newcommand{\Mar}[1]{\relax}
+ \newcommand{\Igor}[1]{\relax}
+ \newcommand{\notes}[1]{\relax}
+\fi
+
+\pagenumbering{arabic}
+
+\newcommand{\codesize}{\small}
+\newcommand{\CodeIn}[1]{\mcodeid{#1}}
+\newcommand{\CodeInM}[1]{\mcodeid{#1}}
+\def\|#1|{\mathid{#1}}
+\newcommand{\mathid}[1]{\ensuremath{\mathit{#1}}}
+\def\<#1>{\codeid{#1}}
+\newcommand{\codeid}[1]{\ifmmode{\mbox{\codesize\ttfamily{#1}}}\else{\codesize\ttfamily #1}\fi}
+\def\<#1>{\mcodeid{#1}}
+\newcommand{\mcodeid}[1]{\mbox{\codesize\ttfamily{#1}}}
+\newcommand{\CodeInSmaller}[1]{\mbox{\scriptsize\ttfamily{#1}}}
+
+\newcommand*{\RightThumbsUpAux}[1]{
+  \begingroup
+    \sbox0{Ag}
+    \raisebox{-\dp0}{
+      \includegraphics[{
+        height=\dimexpr\dp0+\ht0\relax,
+        #1
+      }]{thumbsup.pdf}
+    }
+  \endgroup
+}
+\newcommand*{\RightThumbsUp}{
+  \RightThumbsUpAux{}
+}
+\newcommand*{\RightThumbsDown}{
+  \RightThumbsUpAux{origin=c,angle=180}
+}
+\newcommand*{\LeftThumbsUp}{
+  \scalebox{-1}[1]{\RightThumbsUp}
+}
+\newcommand*{\LeftThumbsDown}{
+  \scalebox{-1}[1]{\RightThumbsDown}
+}
+
+\newcommand{\checkm}{Y}
+\newcommand{\crossmark}{N}
+
+\newcommand{\totalTestFiles}{40,041} 
+\newcommand{\totalTestFilesPassInPar}{7,061} 
+\newcommand{\totalTestFilesCompileInAll}{36,448} 
+\newcommand{\totalTestFilesPassInAll}{23,808} 
+\newcommand{\totalTestFilesForTestTransplantation}{6,602}
+
+\newcommand{\nofuzzAll}{209}
+\newcommand{\nofuzzBugs}{\Fix{XX}}
+\newcommand{\nofuzzDuplicates}{63}
+\newcommand{\nofuzzFalsePositives}{24}
+\newcommand{\nofuzzHITotal}{177}
+\newcommand{\nofuzzLOTotal}{32}
+\newcommand{\nofuzzTotalFiles}{977} 
+\newcommand{\nofuzzFilesHI}{940} 
+\newcommand{\nofuzzFilesLO}{37} 
+\newcommand{\nofuzzBucketsBugsHI}{\Fix{124}} 
+\newcommand{\nofuzzBucketsBugsLO}{\Fix{11}} 
+\newcommand{\nofuzzDupsHI}{\Fix{X}}
+\newcommand{\nofuzzDupsLO}{\Fix{Y}}
+\newcommand{\tableBugsNum}{\Fix{26}}
+
+\newcommand{\noBugsTransplantation}{28}
+\newcommand{\noBugsTransplantationConfirmed}{20}
+\newcommand{\noBugsTransplantationFixed}{12}
+
+\newcommand{\noBugsDifferentialTesting}{22}
+\newcommand{\noBugsDifferentialTestingConfirmed}{16}
+\newcommand{\noBugsDifferentialTestingFixed}{10}
+
+\newcommand{\totalBugsReported}{49}
+\newcommand{\totalBugsConfirmed}{33}
+\newcommand{\totalBugsFixed}{22}
+
+\newcommand{\noBugsBugsReportedGoogle}{five}
+\newcommand{\noBugsBugsConfirmedGoogle}{four}
+
+\newcommand{\percChakra}{\Fix{52\%}} 
+\newcommand{\percJSC}{\Fix{45\%}}
+
+\newcommand{\noTransConfirmed}{18}
+\newcommand{\noTransSeverityTwo}{16}
+\newcommand{\noTransChakraBugs}{13}
+\newcommand{\noTransChakraBugsFixed}{7}
+\newcommand{\noTransVeightBugsConfirmed}{two}
+\newcommand{\noTransVeightBugsReported}{three}
+\newcommand{\noTransVeightBugsFixed}{two}
+
+\newcommand{\noTransUndefined}{204} 
+\newcommand{\noTransTimeout}{23} 
+\newcommand{\noTransNotImplemented}{54} 
+\newcommand{\noTransNonStandard}{122} 
+\newcommand{\noTransOther}{174} 
+\newcommand{\noTransTPDuplicated}{11} 
+\newcommand{\noTransTPBugs}{24}
+
+\newcommand{\noDiffConfirmed}{fifteen}
+\newcommand{\noDiffFixed}{ten}
+\newcommand{\noDiffVeight}{2}
+\newcommand{\noDiffVeightConfirmed}{2}
+\newcommand{\noDiffVeightFixed}{1}
+
+\newcommand{\warningsIteration}{five}
+
+\ifdraftmode
+\newcommand{\anonym}[1]{{\tiny\colorbox{black}{xxx}}}
+\else
+\newcommand{\anonym}[1]{{\tiny\colorbox{black}{#1}}}
+\fi
+
+\newcommand{\radamsa}{radamsa}
+\newcommand{\quickfuzz}{quickfuzz}
+
+\newcommand{\jsc}{JSC}
+\newcommand{\veight}{V8}
+\newcommand{\chakra}{Chakra}
+\newcommand{\smonkey}{SpiderMonkey}
+\newcommand{\jerry}{JerryScript}
+
+\newcommand{\lo}{lo}
+\newcommand{\hi}{hi}
+
+\newcommand{\testsThatFail}{63}
+\newcommand{\testsThatFailJSC}{6}
+\newcommand{\testsThatFailSM}{57}
+\newcommand{\filesAttached}{490}
+\newcommand{\filesAttachedSM}{110}
+\newcommand{\filesAttachedJSC}{10}
+\newcommand{\filesAttachedVeight}{370}
+\newcommand{\filesMining}{1,240}
+\newcommand{\filesMiningSM}{377}
+\newcommand{\filesMiningJSC}{224}
+\newcommand{\filesMiningVeight}{639}
+\newcommand{\samplesEnglish}{25K}
+\newcommand{\samplesJSSnippets}{25K}
+\newcommand{\accuracyMining}{98\%}
+
+\newcommand{\percentSuiteTestJSC}{92\%}
+\newcommand{\percentSuiteTestVeight}{95\%}
+\newcommand{\percentSuiteTestChakra}{75\%}
+\newcommand{\percentSuiteTestSM}{93\%}
+
+\newcommand{\failuresTestTrans}{836}
+\newcommand{\failuresTestTransDistictFiles}{612} 
+\newcommand{\failuresTestTransPercent}{9.2\%}
+\newcommand{\noBugsTransplantationSeverityTwo}{16}
+\newcommand{\bugsChakra}{12}
+\newcommand{\bugsChakraFixed}{3}
+
+\newcommand{\testOriginal}{31,276} 
+\newcommand{\testPassInPar}{-}
+\newcommand{\testCompileAll}{29,846} 
+\newcommand{\testNoFailAll}{17,639}
+
+\newcommand{\veightOriginal}{1,084} 
+\newcommand{\veightPassInPar}{482} 
+\newcommand{\veightCompileAll}{478} 
+\newcommand{\veightNoFailAll}{426}
+
+\newcommand{\smOriginal}{3,122} 
+\newcommand{\smPassInPar}{2,155} 
+\newcommand{\smCompileAll}{2,103} 
+\newcommand{\smNoFailAll}{1,837}
+
+\newcommand{\jscOriginal}{1,265} 
+\newcommand{\jscPassInPar}{1,130} 
+\newcommand{\jscCompileAll}{1,122} 
+\newcommand{\jscNoFailAll}{1,054}
+
+\newcommand{\duktapeOriginal}{1,195}
+\newcommand{\duktapePassInPar}{1,195}
+\newcommand{\duktapeCompileAll}{921}
+\newcommand{\duktapeNoFailAll}{915}
+
+\newcommand{\jerryOriginal}{1,951}
+\newcommand{\jerryPassInPar}{1,951}
+\newcommand{\jerryCompileAll}{1,878}
+\newcommand{\jerryNoFailAll}{1,837}
+
+\newcommand{\jsiOriginal}{99}
+\newcommand{\jsiPassInPar}{99}
+\newcommand{\jsiCompileAll}{63}
+\newcommand{\jsiNoFailAll}{63}
+
+\newcommand{\tinyOriginal}{49}
+\newcommand{\tinyPassInPar}{49}
+\newcommand{\tinyCompileAll}{37}
+\newcommand{\tinyNoFailAll}{37}
+
+\newcommand{\dataRepo}{\url{https://figshare.com/s/ee2e3821c2f022c7f5cc}}
 
@@
 
-%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
-\title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
-%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head
+\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
 
 \author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
-%\authorrunning{Short form of author list} % if too long for running head
 
@@
 \date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-%\institute{Corresponding author.}
-
-%\renewcommand{\shortauthors}{Lima et al.}
 
@@
 \begin{abstract}
-  \input{abstract}
-  %\keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
-  \keywords{Test Transplantation \and Differential Testing \and JavaScript}
+  \textbf{Context.} JavaScript is a very popular programming language today with several
+implementations competing for market dominance. Although a
+specification document and a conformance test suite exist to guide
+engine development, bugs occur and have important practical
+consequences. Implementing correct
+engines is challenging because the spec is intentionally
+incomplete and evolves frequently.
+\textbf{Objective.} This paper evaluates the importance of
+diversity to find functional bugs in JavaScript engines. \textbf{Method.} For that, we
+studied two existing diversity-aware techniques---test transplantation and
+cross-engine differential testing. The first technique runs test
+suites of a given engine in another engine. The second technique
+fuzzes existing inputs and then compares the output produced by
+different engines with a differential oracle.
+\textbf{Results.} We considered engines from four major players in our
+experiments--Apple, Google, Microsoft, and Mozilla. Our results
+indicate that both techniques revealed several bugs, many of which
+confirmed by developers. We reported \noBugsTransplantation{} bugs
+with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
+confirmed and \noBugsTransplantationFixed{} fixed) and reported
+\noBugsDifferentialTesting{} bugs with differential testing
+(\noBugsDifferentialTestingConfirmed{} of these confirmed
+and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
+most of these bugs affected two engines--Apple's
+\jsc{} and Microsoft's \chakra{}. To summarize, our results show that
+diversity-aware techniques are easy to apply and very effective in
+finding bugs in complex software, such as JavaScript engines.
+   \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
 \end{abstract}
@@
 
-%% WHAT WE DID
-This work, which is empirical in nature, reports on a study to evaluate
-the ability of two testing techniques to expose bugs in JavaScript engines.
-
-%\vspace{-1ex}
-%noitemsep,
+This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
+to find bugs in JavaScript engines; it covers two complementary
+diversity-aware testing techniques.
+
 \begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
-\item \emph{Test transplantation}.
-  This technique evaluates the effect of running test files
+\item \emph{Test transplantation} leverages diversity of test
+  cases. This technique evaluates the effect of running test files
   written for a given engine in other engines. The intuition is that
@@
 
-\item \emph{Cross-engine differential testing}.
-  This technique fuzzes existing test
+\item \emph{Cross-engine differential testing} leverages diversity of
+  engine implementations. This technique fuzzes existing test
   inputs~\cite{fuzz-testing-history} and then compares the output
-  produced by different engines using a differential
-  oracle. The intuition is that interesting inputs can be created
+  produced by different engines.\Comment{ using a differential
+    oracle.} The intuition is that interesting inputs can be created
   from existing inputs and multiple engines can be used to address the
@@
 
-%One of
-%various causes of output discrepancy is a bug.
-
-%% It automates test generation in scenarios where multiple
-%% implementations of a system exist. DT leverages diversity across
-%% system's implementations to detect anomalous behavior.
-%\emph{Related Ideas.}~The idea of test set diversity dates back to the
-%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
-%to prior work on this topic, this paper explores diversity of
-%implementations and diversity of sources of test cases as opposed to
-%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
-%elaborates related work on this topic.
-%
-\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT)
-has been applied in a variety of contexts to find
+\emph{Related Ideas.}~The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
+to prior work on this topic, this paper explores diversity of
+implementations and diversity of sources of test cases as opposed to
+diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
+elaborates related work on this topic. Differential
+Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
+contexts to find
 bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
@@
 (see Tables~\ref{fig:piecharts-transplantation} and
-~\ref{tab:false-positives}). Variations of these ideas have
+~\ref{tab:false-positives}). To sum up, variations of these ideas have
 been explored before in different contexts.  The goal of the paper is
@@
 
-%% This paper evaluates the benefits of
-%% test case diversity and engine diversity in finding bugs on
-%% \javascript\ engines.
-
-%% Recently, Patra and
-%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
-%% find cross-browser HTML+JS discrepancies. The main difference of our
-%% work to theirs is in goal; our goal is to evaluate ability and cost of
-%% simple diversity-aware approaches to find bugs in \js\ engines.
-
-%% Their main contribution was
-%% analytical whereas our main contribution is empirical--
-
 \begin{figure}[t]
-%  \vspace{-2ex}
   \centering
@@
 \sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
-\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}).
-\Fix{Jefferson, atualize a figura!}
-Each stacked bar breaks down the bugs
+(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
+\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
+bug reports per engine (\ref{fig:stacked-engine}) and per technique
+(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
 per status (\eg{}, ``1-New''). The prefix number indicates the
@@
 
-%% Considering cost per bug found, we found that test
-%% transplantation, compared to differential testing, demanded less
-%% effort from the developers who inspected the alarms.
-
-%% All in all, these simple techniques
-%% seem promising to improve reliability of engines that continuously
-%% evolve with their specifications.
-
 \emph{Key Findings.}~The list of findings of this work includes--1)
@@
 
-%% LIST OF CONTRIBUTIONS
 \emph{Contributions.}~The most important contribution of this work is empirical: 
-we provide a comprehensive study analyzing the effectiveness of
-test transplantation and differential testing
-in revealing functional bugs in popular \javascript\ engines.
+we provide a comprehensive study analyzing the effectiveness of diversity-aware
+techniques to find functional bugs in popular \javascript\ engines.
 Additional contributions are:
@@
 Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
-2)~An infrastructure for performing test transplantation and differential testing.
+2)~An infrastructure for diversity-aware testing.
 The scripts to run the experiments will be available upon request. 
@@
 \vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring test transplantation and differential testing
-should be encouraged to find functional bugs
+that exploring diversity should be encouraged to find functional bugs
 in JavaScript engines.
@@
 ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
-
-%% In the following, we briefly describe different sources of
-%% discrepancies that can emerge across different engine implementations
-%% as results of the active changes in the \es{} specification.
-%% .........
-%% A compatibility table relating features and supporting engines is
-%% publicly available~\cite{kangax}.
 
@@
 
-%\subsection{Randomness}
-
-%\subsection{\Fix{Other}}
-
-%% 1) The stack depth in JS is often close to the real (native) C stack
-%% depth, nevertheless observable by JS through recursion. This causes
-%% differential behavior even on the same engine when JITs are enabled or
-%% disabled, as the stack frame sizes vary. LangFuzz in particular
-%% produces a lot of recursions and hits these problems even more often
-%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
-%%   could be different.}
-
-%% \section{Objects of Study}
-%% This section discusses the objects we used in our study.
-
 \section{Engines Studied}
@@
 reporting old and already-fixed bugs to developers.
-
-%% Table~\ref{tab:engines} shows the engines we selected in this
-%% study. We made an exception to the second criterion with
-%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
-%% thought there was insufficient time to obtain 1K stars for XS. We
-%% still considered this project as it seems to be attracting interest
-%% from the community\Fix{is this true?}
 
@@
 these engines.
-
-%% accessible from GitHub using the GitHub REST
-%% API~\cite{github-rest-api}.
 
@@
 
-\newcommand\marktopleft[1]{%
+\newcommand\marktopleft[1]{
     \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,2ex) {};%
+        \node (marker-#1-a) at (0,2ex) {};
 }
-\newcommand\markbottomright[1]{%
+\newcommand\markbottomright[1]{
     \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
+        \node (marker-#1-b) at (0,0) {};
     \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
-        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
+        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};
 }
@@
 
-%% The main source of test
-%% cases is the official Test262~\cite{tc39-github} conformance test
-%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
-%%   This test suite contains 87\% of all the tests we used.} We also
-%% considered test suites of three of the four engines mentioned in
-%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
-%% we selected a total of \totfiles{} JS
-%% files.
-
 \lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
@@
 
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
 To obtain test files included as attachments, we wrote a crawler to
@@
 
-%% With that mapping it is
-%% possible to measure distance between two sentences as the distance
-%% between the vectors characterizing them. Consequently, one can
-%% measure, for example, the minimum distance between a sentence in
-%% English and a sentence in a \js\ embedding, built with word2vec using
-%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
-%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
-%%   solve the problem? Are there two separate embeddings (one for
-%%   English and one for JS)? If not, how they are combined? What about
-%%   the classification scheme?  It needs to answer yes/no (not a
-%%   distance).}
-
-%% For space, we summarize the solution that worked the best in
-%% the following. The classifier that performed best for this case uses a
-%% standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain what
-%%   this ``Embeddings'' thing does at a high-level. Also, if this stuff
-%%   exists why we did not find a solution off-the-shelf?}  that builds
-%% on a neural net~\Fix{cite} to keep a dictionary of words and the
-%% similarity distance among them\Mar{but we are talking about
-%%   sentences. how does it go from words to sentences? Note that many
-%%   words from the ``code'' vocabulary are from English!}. In more
-%% detail, the classification model uses a Convolutional Neural
-%% Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
-%%   meaning for each layer?} and has been trained and evaluated using a
-%% dataset with 25K samples of English paragraphs and 25K snippets of
-%% \js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
-%% evaluate the model and obtained a predicted accuracy of
-%% \Fix{98\%}. This classifier is publicly available from our website as
-%% a separate component.
-
-%% N\'os mineramos as issues em bug trackers dos engines javascript mais conhecidos.
-%% Foi necessario capturar tanto os arquivos javascript anexados quanto os codigos escritos nos reports.
-%% Para obter o codigo extraido dos reports, foi criado um modelo de aprendizagem para reconhecer
-%% se um bloco de texto eh um bloco de codigo.
-
-%% Motivacao:
-%% Utilizamos a tecnica de Embeddings que eh reconhecida pela comunidade pelo seu uso em PLN (Processing Language Natural),
-%% onde atraves de uma rede neural, consegue-se montar um dicionario de palavras com a distancia
-%% de similaridade entre elas.
-%% Para treinamenteo, foi utilizado uma rede neural simples CNN (Convolutional Neural network) com apenas 2 camadas, uma de entrada e outra de saida.
-%% Utilizando as variaveis \Fix{XYZ} e as funcoes \Fix{XYZ}. Obtivemos 98\% de acuracia em nosso treinamento.
-%% (melhorar definicao do modelo)
-
-%% Inputs:
-%% Para nosso modelo de dados, foi necessario gerar um arquivo CSV com cerca de 50K de dados extraidos
-%% de arquivos javascript (nossas seeds) e de linguagem natural, utilizamos 25K para cada classe.
-%% Os rotulos das classes sao definidas em 0 (is not code) ou 1 (is code).
-
-%% Com isso, extraimos cerca de \Fix{X} codigo e apos realizar o parser para validar o arquivo, obtivemos um total de \Fix{X} novas seeds.
-
-%% \Fix{...elaborate...}
-
-%% \Fix{revise this}
-%% For example to run the \jerry{} tests it was necessary
-%% use the unit-test package to run it, but with our changes we added the assertion
-%% does not have an assertion in the test file
-%% \Fix{add code to explain}
-
 \begin{figure}[t]
@@
 
-%% \Mar{any difference in
-%%   output is considered for reporting? are there any
-%%   filtering?}\Igor{acho que nos equivocamos ao deixar o "eshost-cli",
-%%   nao estamos mais utilizando isso devido a essa ferramenta nao
-%%   capturar certos tipo de issues (e.g. crash), retirar tambem da Figura 2.
-%%   A respeito de filtros nos reports, nao. Nos so capturamos o output,
-%%   o que modificamos eh apenas a formatacao do output para coletar apenas a
-%%   mensagem e nao o stack trace.
-%%   }
-
 \subsection{Prioritization}
@@
 \label{sec:clusterization}
-
-%% Prioritization helps to steer our focus to the warnings more likely to
-%% reveal bugs, but there could be several tests producing similar
-%% warnings.
 
@@
 
-%% Our
-%% infrastructure supports any grammar fuzzer with a few
-%% adjusts. However, we try to integrate several grammar-based fuzzers,
-%% for example
-%% and \Fix{others fuzzers} to
-%% generate new JavaScript files based on grammar, but after several runs
-%% it was observed that this approach was ineffective due the amount of
-%% invalid files and/or files without discrepancies.
-%% For example, if we
-%% ran Grammarinator to generate 1K JS files ten times with a random seed
-%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
-%% environment almost \Fix{XX\%} are js files that shows undefined
-%% variables and due the differential testing in our environment all
-%% engines will raise a SyntaxError and this approach was not relevant to
-%% our experiment.
-
-%% We initially considered used representatives of popular fuzzing approaches. For
-%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
-%% coverage-based fuzzing we used
-%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
-%% generative-based fuzzing we used
-%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
-%% be found elsewhere~\cite{fuzz-bart}.
-
 Mutational fuzzers can be either white-box or black-box. White-box
@@
 
-The goal of this paper is to assess ability of
-test transplantation and differential testing
-to find functional bugs
+The goal of this paper is to assess ability of techniques that
+leverage diversity to find functional bugs
 in \javascript\ engines. Based on that, we pose three questions:
@@
 rationale for this question is that fuzzing inputs may explore
-scenarios not well-tested by at least one of the engines.
+scenarios not well tested by at least one of the engines.
 
@@
 \begin{table}
-  %\vspace{-4ex}
   \centering
@@
     the Test262 conformance suite.}
-  %\small
   \begin{tabular}{rr}
@@
   \end{tabular}
-  %\normalsize
 \end{table}
@@
 
-%\vspace{0.5ex}
 \subsubsection{Methodology}
@@
     \midrule
-    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
     \Comment{
@@
     \veight{} & 41 & - & 3 & 5  \\
-%    \chakra{} & - & - & - & -  \\
     \smonkey{} & 218 & 107 & - & 281 \\
@@
 Table~\ref{tab:test-suites}).
-
-%%  As another example, some tests from \Fix{Y} use the
-%% implementation-dependent description message\Mar{what is the name of
-%%   the property?} encapsulated in an \CodeIn{Error} object in
-%% assertions. As such, those tests fail in all engines but
-%% \Fix{Y}.
 
@@
     of False (FP) and True Positives (TP).}
-  %\setlength{\tabcolsep}{3pt}
   \renewcommand*{\arraystretch}{0.9}
@@
 
-\input{table_transplantation}
+\begin{table}[t!]
+  \renewcommand{\arraystretch}{0.95}
+      \centering
+      \caption{List of bugs reports from Test Transplantation.}
+      \label{tab:test-transplantation-bugs}
+
+      \begin{tabular}{rccccc}
+        \toprule Issue\#\Comment{    & Date} & Engine  & Status  \Comment{& \multicolumn{1}{c}{Url}}  & Severity & Suite \\
+        \midrule    
+        1  \Comment{& 4/18  }& \jsc{}  & New  \Comment{& \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}}} & - & \jerry{}      \\
+       2  \Comment{& 4/23 }& \chakra{}  & \textbf{Confirmed}  \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5033}{\#5033}}} & 2 & \smonkey{}      \\
+
+       3  \Comment{& 4/29 }& \chakra{}  & \textbf{Fixed}   \Comment{&
+        \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5065}{\#5065}}}
+        & 2 & \smonkey{} \\
+       4\Comment{& \multirow{2}{*}{4/29}} & \chakra{} &
+       \textbf{Confirmed} \Comment{&
+       \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5067}{\#5067}}} & 2 & \smonkey{}\\
+       5                    &\Comment{  &}
+        \jsc{} & New \Comment{&    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}}} &  -  & \smonkey{}\\
+       6 \Comment{& 5/02  }& \jsc{} & New  \Comment{& \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}}} & - & \smonkey{} \\
+       7 \Comment{& 5/02  }& \jsc{} & \textbf{Confirmed} \Comment{ & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=185211}{\#185211}}} & 2 & \smonkey{}\\ 
+       8 \Comment{& 5/17  }& \chakra{} & \textbf{Confirmed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5187}{\#5187}}} & 2 & \jsc{}\\
+       9 \Comment{& 5/21  }& \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5203}{\#5203}}} & 2 & \smonkey{}\\
+       10 \Comment{& 6/28  }& \chakra{} & \textbf{Confirmed}  \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5388}{\#5388}}} & 2 & \jsc{}\\
+       11 \Comment{& 7/10  }& \chakra{} & \textbf{Confirmed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5442}{\#5442}}} & 2 & \jerry{}\\ 
+       12 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5478}{\#5478}}} & 2 & \smonkey{}\\
+       13 \Comment{& 7/18  }& \jsc{} & New \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}}} & - & \jerry{}\\
+       14 \Comment{& 7/18  }& \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5549}{\#5549}}} & 2 & \jerry{}\\ 
+       15 \Comment{& 8/07  }& \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5576}{\#5576}}} & 3 & \jerry{}\\
+       16 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}}} & 2 & \jerry{}\\
+       17 \Comment{& 8/07  }& \chakra{} & \textbf{Confirmed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5579}{\#5579}}} & 3 & \jerry{}\\
+       18 \Comment{& 8/07  }& \jsc{} & \textbf{Fixed} \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}}} & 2 & \jerry{}\\
+       19 \Comment{& 8/08  }& \veight{} & \textbf{Fixed} \Comment{& \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}}} & 3 & \jerry{}\\
+       20 \Comment{& 8/08  }& \jsc{} & New \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}}} & - & \jerry{}\\
+       21 \Comment{& 8/16  }& \veight{} & WontFix \Comment{& \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8064}{\#8064}}} & 2 & Duktape\\
+       22 \Comment{& 8/22  }& \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5621}{\#5621}}} & 2 & \smonkey{}\\
+       23 \Comment{& 8/22  }& \jsc{} & \textbf{Fixed} \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188874}{\#188874}}} & 2 & \smonkey{}\\
+
+       24\Comment{& 
+        \multirow{3}{*}{8/22}} & \jsc{} & New \Comment{&
+       \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188875}{\#188875}}}
+       & - & \smonkey{}\\
+       25 &  \Comment{&}
+        \veight{} & \textbf{Fixed} \Comment{& \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8082}{\#8082}}} &  2  & \smonkey{}\\
+       26 &  \Comment{&}
+        \chakra{} & \textbf{Fixed} \Comment{& \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5624}{\#5624}}} &  2  & \smonkey{}\\
+
+       27 \Comment{& 8/23  }& \jsc{} & New \Comment{& \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188877}{\#188877}}} & - & \smonkey{}\\
+       \bottomrule
+      \end{tabular}
+      \vspace{-2ex}
+\end{table}
 
@@
 
-%% Overall, we found these results promising given that precision (\ie{},
-%% the ratio of true positives over all reports) needs to take into
-%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
-%% it took a week for the developer to inspect the entire set of
-%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
-%% seems a low rate, but it took approximately \Fix{x} days to find
-%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
-%% of false and true positives.
-
 \begin{center}
@@
 
-%%  That
-%% finding would be important to reduce inspection cost and guide future
-%% developments of this approach.
-
-\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
+\vspace{0.5ex} \lbrack{}Exploratory Phase.\rbrack{} For the first
 three months of the study, our inspection process was exploratory.  In
@@
 \vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase\rbrack{} Results obtained in the
+\lbrack{}Non-Exploratory Phase.\rbrack{} Results obtained in the
 exploratory phase confirmed our expectations that most of the bugs
@@
 
-%% Table~\ref{tab:summary-lo}
-%% shows statistics of \lo\ warnings obtained when fuzzing inputs with
-%% different tools. Column ``\# buckets'' shows the number of buckets
-%% associated with ``\lo'' warnings, column ``\# files'' shows the total
-%% number of files involved in these warnings, and column ``avg. \# files
-%% per bucket'' shows the average number of files per bucket. Note that,
-%% although the number of buckets and files differ substantially across
-%% fuzzers, the difference of files per bucket was not very high.\Mar{not
-%% sure how relevant is this par.}
-
-%% \begin{table}[t]
-%%   \small
-%%   \centering
-%%   \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
-%%   \begin{tabular}{crrr}
-%%     \toprule
-%%     & \# buckets & \# files & avg. \# files per bucket \\
-%%     \midrule
-%%     \radamsa{} & 82 & 319 & 3.8 \\
-%%     \quickfuzz{} & 78 & 218 & 2.7 \\
-%%     \bottomrule
-%%   \end{tabular}
-%% \end{table}
-
 \vspace{0.5ex}
@@
     \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
-    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
+    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ 
+    \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ 
     \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
+    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ 
     \bottomrule
@@
     \midrule
-    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9
-    & Timeout/OME & 30 & 15 \\ % 28 & 13
-    & * Invalid Input & 46 & 55 \\ % 39 & 48
-    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
+    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ 
+    & Timeout/OME & 30 & 15 \\ 
+    & * Invalid Input & 46 & 55 \\ 
+    & * Error Message Mismatch & 41 & 12 \\ 
     \midrule
-    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
+    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ 
     & Bug & 15 & 7\\
@@
 \end{table}
-
-%% \Igor{devemos remover isso da
-%% etapa de fuzzing upcoming feature falha mesmo sem fuzzing...$\rightarrow$
-%% The source ``Upcoming Feature''
-%% indicates that the test fails because it uses a feature that is
-%% available in the original engine, but it is still not standard, and
-%% the target engine does not support that feature}. For example,
-%% \Fix{provide concrete example}. \Fix{explain error message mismatch}
-
-%% The table is
-%% organized in two sections. The top section shows results obtained
-%% during the exploratory phase of the study and the bottom section shows
-%% the results obtained during the non-exploratory phase.
 
@@
 
-\input{table_differential}
-
-%% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
-%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
-%%     bug tracker was defined as confirmed, however the bugs are
-%%     included on a milestone for the next release following an internal
-%%     priority.  }}
-
-%% Finally, it is worth noting that \Fix{11 of the 19}
-%% JS files that manifested discrepancies were \emph{not} produced with
-%% fuzzing (column ``Fuzz''). These are test files from suites of
-%% different engines. This observation emphasizes the importance of
-%% continuously collecting test suites from multiple sources; today, we
-%% use test suites from seven different open source engines, including a
-%% total of 30K test files.
+\begin{table}[t]
+  \vspace{-3ex}
+  \centering
+  \caption{List of bugs reports from Differential Testing.}
+  \label{tab:bugs}
+  \setlength{\tabcolsep}{1.5pt}
+  \renewcommand{\arraystretch}{0.95}
+  \begin{tabular}{rcccccc}
+    \toprule
+    Issue\# \Comment{ & Date} & Fuzzer & Engine  & Status \Comment{&
+    \multicolumn{1}{c}{Url}}  & Sev. & Priority & Suite \\
+    \midrule
+    1  \Comment{& 4/12} & radamsa & \chakra{}   & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
+    & 2 & \textbf{\lo} & \jsc{} \\ 
+    2  \Comment{& 4/12} & radamsa & \chakra{}   & WontFix  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
+    & - & \hi{} & \jsc{} \\
+    3  \Comment{& 4/14} & radamsa & \jsc{}  & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
+    } & -  & \hi{} & \jsc{}    \\
+    4  \Comment{& 4/25} & radamsa & \chakra{}  & \textbf{Fixed}     \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
+    & 2 & \hi{} & \jerry{}   \\
+    5  \Comment{& 4/29} & radamsa & \jsc{}  & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
+    } & 2  & \hi{}  & \jerry{}\\
+
+    6 \Comment{& 4/30}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}}
+    & 2 & \hi{} & TinyJS\\
+
+    7                    \Comment{& 4/30}                       &  radamsa   &
+    \jsc{} & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}}
+    & - & \hi{} & TinyJS \\
+
+    8 \Comment{& 5/02} & radamsa & \jsc{}  & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}}
+    & 2 & \textbf{\lo} & \smonkey{} \\
+    9 \Comment{& 5/10} & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}}
+    & 3 & \hi{} & \jerry{} \\
+    10 \Comment{& 5/17} & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}}
+    & 2 & \hi{} & \veight{}\\
+    11 \Comment{& 5/24} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}}
+    & 2 & \hi{} & \jsc{}\\
+    12 \Comment{& 6/26} & radamsa & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}}
+    & 2 & \hi{} & \jerry{}\\
+    13 \Comment{& 7/10} & quickfuzz & \jsc{} & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}}
+    & 2 & \hi{} & \jerry{}\\
+    14 \Comment{& 7/10} & quickfuzz & \chakra{} & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}}
+    & 2 & \hi{} & \jerry{}\\
+
+    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
+    & 3 & \hi{} & Test262\\
+
+    16 \Comment{& 8/21} & radamsa &
+    \veight{} & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}}
+    & 2 & \hi{} & Test262 \\
+
+    17 \Comment{& 8/23} & quickfuzz & \jsc{} & New  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}}
+    & - & \hi{} & Test262\\
+    18 \Comment{& 8/23} & quickfuzz & \veight{} & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}}
+    & 2 & \hi{} & Test262\\
+
+    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
+    & 2 & \hi{} & Test262\\
+
+    20 \Comment{& 8/24} &  quickfuzz & 
+    \jsc{} & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}}
+    & - & \hi{} & Test262 \\
+
+    21 \Comment{& 8/24} & quickfuzz & \jsc{}  & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}}
+    & - & \hi{} & Test262\\
+
+    22 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5968}{\#5968}}}
+    & - & \hi{} & \smonkey{}\\
+   \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 
-%% \CodeIn{\{var a =
-%%   \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
-%%   assert(+a === 0)\}}
-
 \sloppy
@@
   \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
     basicstyle=\ttfamily\scriptsize, boxpos=c,
@@
   \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
   \vspace{-1ex}  
@@
 
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a
-%%   function declaration. The fuzzer removes the function declaration and
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError)
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
 \vspace{1ex}\noindent\textbf{Issue \#18,
@@
 
-%% there might be errors in the implementation of our
-%% infrastructure. To mitigate this threat, we extensively inspected the
-%% results of our evaluation manually and, when we found the need for
-%% implementing a different component we kept the old one for
-%% cross-checking. For example, we used eshost-cli~\cite{eshost-cli} to
-%% validate our fork-join implementation of the ``Checker'' component
-%% from Figure~\ref{fig:workflow} that, for efficiency, is tightly
-%% integrated to our infrastructure.
-%% \Fix{elaborate}
-
 \subsection{Key Findings and Lessons}
@@
     bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
   \item Even simple black-box fuzzers can create surprisingly
@@
 
-%\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
-%The idea of test set diversity dates back to the
-%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
-%assumption behind test set diversity is that faults often spread
-%contiguously in the input domain. Consequently, it should be
-%beneficial to partition the input domain and explore it more evenly as
-%to find bugs faster. Later in the nineties, Chen and
-%Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
-%the continuity assumption. They found that faults, most often,
-%manifest themselves in regular patterns across the input
-%domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
-%observations led researchers to investigate generalizations of the
-%approach to non-numerical data types and strategies to explore the
-%input (or output) space to solve different problems in Software
-%Engineering (\eg{}, test input generation and test
-%selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
-%paper explores diversity of sources of test cases and diversity of
-%engine implementations. We remain to investigate the diversity of test
-%cases themselves. In principle, that could help reduce the number of
-%alarms to inspect, for example.
+\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
+The idea of test set diversity dates back to the
+eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. The
+assumption behind test set diversity is that faults often spread
+contiguously in the input domain. Consequently, it should be
+beneficial to partition the input domain and explore it more evenly as
+to find bugs faster. Later in the nineties, Chen and
+Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
+the continuity assumption. They found that faults, most often,
+manifest themselves in regular patterns across the input
+domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
+observations led researchers to investigate generalizations of the
+approach to non-numerical data types and strategies to explore the
+input (or output) space to solve different problems in Software
+Engineering (\eg{}, test input generation and test
+selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
+paper explores diversity of sources of test cases and diversity of
+engine implementations. We remain to investigate the diversity of test
+cases themselves. In principle, that could help reduce the number of
+alarms to inspect, for example.
 
@@
 
-%% \Fix{
-%% although more research needs be done to automate
-%% parts of the inspection process (\eg{}, reduction of false alarms),}
-
 JavaScript (\js{}) is very popular today. Bugs in engine
@@
 
-This paper reports on a study to evaluate two
+This paper reports on a study to evaluate two diversity-aware
 techniques for finding bugs in \js{}--test transplantation and
-cross-engine differential testing. The first technique
-runs the test suite of one given engine in another engine.
-The second technique fuzzes existing inputs and then compares the
+cross-engine differential testing. The first technique explores
+diversity of test sources; it runs the test suite of one given engine
+in another engine. The second technique explores diversity of
+implementations; it fuzzes existing inputs and then compares the
 output produced by different engines with a differential oracle.
@@
 cost of manual analysis, we found that our results provide strong
-evidence that exploring test transplantation and differential testing
-should be encouraged to find functional bugs in JavaScript engines.
+evidence that exploring diversity should be encouraged to find
+functional bugs in JavaScript engines.
 
@@
 \balance
-%\bibliographystyle{elsarticle-num}
 \bibliographystyle{spmpsci}
@@
 \end{document}
-
-%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
-%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
-%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
-%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
-%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
-%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
-%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers

### 2020-06-05 paper/paper.tex
small edits

@@
 
-\emph{Key Findings.}~The list of findings of this work includes--1)
-Not only multiple different implementations can be leveraged in
-differential testing, but differences in test suites can also be
-important. 2) Even for problems with fairly clear specifications, as
-in \javascript{}, there is likely to be (a lot of) variation between
-different implementations. 3) Differential testing is feasible on
-real, complex, widely used pieces of
-software. Section~\ref{sec:lessons} expands and elaborates key
+\emph{Key Findings.}~We found that--1)~Differential testing and Test
+Transplation are practical and effective techniques to find bugs on real,
+complex, and widely used software systems, 2)~Even for problems with
+fairly clear specifications, as in \javascript{}, there is likely (a
+lot of) variation between different implementations, which brings instrinsic
+challenges to developers that work on them.
+Section~\ref{sec:lessons} expands and elaborates key
 findings and lessons learned.

### 2020-06-07 paper/paper.tex

@@
     \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 & xxxx\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 & 8.4.138\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 & xxxx\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 & 76.0b6\\
-    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 & 0.5.0\\
+    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
+    \multicolumn{1}{c}{3300+} & Jun 2001\\
+    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
+    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
+    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
+    \multicolumn{1}{c}{1100+} & Mar 1996\\
+    Facebook & \hermes{} & \cite{hermes2020repo} &
+    \multicolumn{1}{c}{5400+} & Jun 2019\\
    \bottomrule

### 2020-06-08 paper/paper.tex
edits

--- 2020-06-05 paper/paper.tex
@@
     \toprule
-    Team & Name & URL & \# Stars  & DOB & Version \\
+    Team & Name & URL & \# Stars  & DOB \\
     \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 & xxxx\\
-    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 & 8.4.138\\
-    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 & xxxx\\
-    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 & 76.0b6\\
-    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 & 0.5.0\\
+    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 \\
+    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 \\
+    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 \\
+    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 \\
+    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 \\
    \bottomrule
@@
     shows the tests used for test transplantation (resp., cross-engine
-    differential testing).}  \setlength{\tabcolsep}{2pt}
+    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
   \begin{tabular}{ccrrrr}
@@
     \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
+    \chakra & \cite{chakracore}\\
+    \hermes & \cite{hermes2020repo}\\
     \midrule
@@
     \smonkey{} & \percentSuiteTestSM{} \\
+    \hermes & xxx \\
     \bottomrule

### 2020-06-08 paper/table_differential.tex
pass on diff
final pass
JSS format
SQJ version
update tables/reports

--- 2018-08-25 paper/table_differential.tex
@@
-\begin{table*}[h!]
+\begin{table}[t]
+  %\small
   \vspace{-3ex}
-%  \scriptsize
   \centering
-  \caption{List of bug reports issued as result of cross-engine
-    differential testing.}
+  \caption{List of bugs reports from Differential Testing.}
   \label{tab:bugs}
-  \begin{tabular}{rcccccccc}
+  \setlength{\tabcolsep}{1.5pt}
+  \renewcommand{\arraystretch}{0.95}
+  \begin{tabular}{rccccccc}
     \toprule
-    Issue\#    & Date & Fuzz & Engine  & Status  &
-    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
+    Issue\# \Comment{ & Date} & Fuzzer & Engine & Version & Status \Comment{&
+    \multicolumn{1}{c}{Url}}  & Sev. & Priority & Suite \\
     \midrule
-%    \multicolumn{9}{c}{\emph{Exploratory Phase}} \\
-%    \midrule    
-    1  & 4/12 & radamsa & \chakra{}   & \textbf{Fixed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}
+    1  \Comment{& 4/12} & radamsa & \chakra{} & 1.9 & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
     & 2 & \textbf{\lo} & \jsc{} \\
-    2  & 4/12 & radamsa & \chakra{}   & WontFix  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}
+    2  \Comment{& 4/12} & radamsa & \chakra{} & 1.9 & WontFix  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
     & - & \hi{} & \jsc{} \\
-    3  & 4/14 & radamsa & \jsc{}  & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
+    3  \Comment{& 4/14} & radamsa & \jsc{} & 606.1.9.4 & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
     } & -  & \hi{} & \jsc{}    \\
-    4  & 4/25 & radamsa & \chakra{}  & \textbf{Fixed}     &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}
+    4  \Comment{& 4/25} & radamsa & \chakra{} & 1.9 & \textbf{Fixed}     \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
     & 2 & \hi{} & \jerry{}   \\
-    5  & 4/29 & radamsa & \jsc{}  & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
+    5  \Comment{& 4/29} & radamsa & \jsc{} & 606.1.9.4 & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
     } & 2  & \hi{}  & \jerry{}\\
-
-    6 & 4/30  & radamsa & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}
+    6 \Comment{& 4/30}  & radamsa & \chakra{} & 1.10-beta & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5076}{\#5076}}}
     & 2 & \hi{} & TinyJS\\
-
-    7                    & 4/30                       &  radamsa   &
-    \jsc{} & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
+    7                    \Comment{& 4/30}                       &  radamsa   &
+    \jsc{} & 606.1.9.4 & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}}
     & - & \hi{} & TinyJS \\
-
-    8 & 5/02 & radamsa & \jsc{}  & \textbf{Fixed} &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
+    8 \Comment{& 5/02} & radamsa & \jsc{} & 606.1.9.4 & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}}
     & 2 & \textbf{\lo} & \smonkey{} \\
-    9 & 5/10 & radamsa & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}
+    9 \Comment{& 5/10} & radamsa & \chakra{} & 1.10-beta & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5128}{\#5128}}}
     & 3 & \hi{} & \jerry{} \\
-    10 & 5/17 & radamsa & \chakra{} & \textbf{Fixed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}
+    10 \Comment{& 5/17} & radamsa & \chakra{} & 1.10-beta & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5182}{\#5182}}}
     & 2 & \hi{} & \veight{}\\
-    11 & 5/24 & radamsa & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
+    11 \Comment{& 5/24} & radamsa & \jsc{} & 606.1.9.4 & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}}
     & 2 & \hi{} & \jsc{}\\
-    12 & 6/26 & radamsa & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
+    12 \Comment{& 6/26} & radamsa & \jsc{} & 606.1.9.4 & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}}
     & 2 & \hi{} & \jerry{}\\
-    13 & 7/10 & quickfuzz & \jsc{} & \textbf{Fixed}  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
+    13 \Comment{& 7/10} & quickfuzz & \jsc{} & 606.1.9.4 & \textbf{Fixed}  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}}
     & 2 & \hi{} & \jerry{}\\
-    14 & 7/10 & quickfuzz & \chakra{} & \textbf{Confirmed}  &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}
+    14 \Comment{& 7/10} & quickfuzz & \chakra{} & 1.11-beta & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5443}{\#5443}}}
     & 2 & \hi{} & \jerry{}\\
-    %    \multicolumn{9}{c}{\emph{Non-Exploratory Phase}} \\
-
-    15 & 8/21  & radamsa & \chakra{} & \textbf{Confirmed} &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}
+    15 \Comment{& 8/21}  & radamsa & \chakra{} & 1.10.2 & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
+    & 3 & \hi{} & Test262\\
+    16 \Comment{& 8/21} & radamsa &
+    \veight{} & 7.0.244 & \textbf{Fixed} \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}}
+    & 2 & \hi{} & Test262 \\
+    17 \Comment{& 8/23} & quickfuzz & \jsc{} & 235121 &  New  \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}}
     & - & \hi{} & Test262\\
-
-    16 & 8/21 & radamsa &
-    \veight{} & \textbf{Fixed} &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8078}{\#8078}}
-    & 2 & \hi{} & Test262 \\
-
-    17 & 8/23 & quickfuzz & \jsc{} & New  &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188899}{\#188899}}
+    18 \Comment{& 8/23} & quickfuzz & \veight{}  & 7.0.244 & \textbf{Confirmed}  \Comment{&
+    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}}
+    & 2 & \hi{} & Test262\\
+    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & 1.10.2 & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
+    & 2 & \hi{} & Test262\\
+    20 \Comment{& 8/24} &  quickfuzz &
+    \jsc{} & 235318 &  New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}}
+    & - & \hi{} & Test262 \\
+    21 \Comment{& 8/24} & quickfuzz & \jsc{} & 235318 & New \Comment{&
+    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}}
     & - & \hi{} & Test262\\
-    18 & 8/23 & quickfuzz & \veight{} & \textbf{Confirmed}  &
-    \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8088}{\#8088}}
-    & 2 & \hi{} & Test262\\
-
-    19 & 8/24  & quickfuzz & \chakra{} & New &
-    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}
-    & - & \hi{} & Test262\\
-
-    20 & 8/24 &  quickfuzz & 
-    \jsc{} & New &
-    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188920}{\#188920}}
-    & - & \hi{} & Test262 \\
-
-    21 & 8/24 & quickfuzz & \jsc{}  & New &
-    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=188930}{\#188930}}
-    & - & \hi{} & Test262\\
+    22 \Comment{& 8/21}  & radamsa & \chakra{} & 1.11.6.0 & \textbf{Confirmed} \Comment{&
+    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5968}{\#5968}}}
+    & - & \hi{} & \smonkey{}\\
    \bottomrule
   \end{tabular}
-\end{table*}
+\end{table}

### 2020-06-08 paper/paper.tex

@@
   \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \includegraphics[trim=0 190 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
     \vspace{-5ex}
@@
 been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
+affected two engines--\chakra{} and JavaScriptCore (\jsc).  We
 reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
+(\noBugsBugsConfirmedGoogle{} confirmed),
+\noBugsBugsReportedHermes in \hermes,
+and \noBugsBugsReportedSMonkey in \smonkey{}.
 Furthermore, our results show that both techniques revealed several
 bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation{} bugs (of which,
-\noBugsTransplantationConfirmed{} were confirmed and
-\noBugsTransplantationFixed{} were fixed) whereas differential testing
-revealed \noBugsDifferentialTesting{} bugs (of which,
-\noBugsDifferentialTestingConfirmed{} were confirmed and
-\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
+revealed \noBugsTransplantation bugs (of which,
+\noBugsTransplantationConfirmed were confirmed and
+\noBugsTransplantationFixed were fixed) whereas differential testing
+revealed \noBugsDifferentialTesting bugs (of which,
+\noBugsDifferentialTestingConfirmed were confirmed and
+\noBugsDifferentialTestingFixed were fixed).  Overall, results
 indicate that both techniques were successful at finding bugs. The
@@
 1)~A number of bugs found and fixed.
-We reported a total of \totalBugsReported{} bugs.
-Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed.
+We reported a total of \totalBugsReported bugs.
+Of these, \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were fixed.
 2)~An infrastructure for performing test transplantation and differential testing.
-Both the scripts to run the experiments and the data processed are publicly available at \dataRepo{}.
+Both the scripts to run the experiments and the data processed are publicly available at \dataRepo.
 
@@
     \midrule
-    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 \\
+    Apple & \jsc (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 \\
     Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 \\
@@
 the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and
+test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
 \testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
@@
 they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc{}'s
+example, some tests use non-portable names (\eg{}, \jsc's
 \CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
@@
     \midrule
-    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
+    \jsc & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
     \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
@@
 \veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc{}; we discarded those to avoid repetition and to give
+Mozilla and \jsc; we discarded those to avoid repetition and to give
 credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
@@
 
-% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
-% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
+% (\jsc=147, \veight{}=370, and \smonkey{}=110).
+% (\jsc=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
 To obtain test files included as attachments, we wrote a crawler to
@@
     \midrule
-    \jsc{} & \percentSuiteTestJSC{}\\
+    \jsc & \percentSuiteTestJSC{}\\
     \veight{} & \percentSuiteTestVeight{} \\
@@
 percentages in the table. The number of passing tests is high and
-similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
+similar for \jsc, \veight{}, and \smonkey\ whereas \chakra\ performs
 worse compared to the other engines. Note also that \chakra\ is both
@@
     \toprule
-    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
+    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{}\\
     \midrule
@@
     }
-    \jsc{} & - & 10 & 10 & 59   \\
+    \jsc & - & 10 & 10 & 59   \\
     \veight{} & 41 & - & 3 & 5  \\
@@
 specified time budget or it exceeds the memory budget. For example, a
-test case from \jsc{} defines a function with a tail-call
-recursion. The test fails in all engines but \jsc{}, which implements
+test case from \jsc defines a function with a tail-call
+recursion. The test fails in all engines but \jsc, which implements
 tail-call optimization. \textbf{Not implemented.} False positives of
@@
 the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
+Considering severity levels, we found that \jsc~\cite{jsc-severity}
 and \smonkey{}~\cite{mozilla-severity} developers use five levels,
@@
 \jsc\ stacked bar from Figure~\ref{fig:stacked-engine}.
-However, the bugs the \jsc{} team confirmed were quickly fixed.
+However, the bugs the \jsc team confirmed were quickly fixed.
 
@@
 %% Note from the table that all bug reports still waiting for
-%% confirmation are associated with the \jsc{} engine. A closer look at
-%% the \jsc{} issue tracker showed that their triage process is slow
+%% confirmation are associated with the \jsc engine. A closer look at
+%% the \jsc issue tracker showed that their triage process is slow
 %% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
@@
   Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc{}. This test
+shows the test input we used to reveal a bug in \jsc. This test
 originates from \jerry{} test suite; the bug was found during the test
@@
 object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
+\CodeIn{TypeError}. In this case, \jsc accepts a non-callable object
 as argument to \CodeIn{sort} and the test fails in the subsequent
@@
 
-This is a testcase original from the \jsc{} suite that the
+This is a testcase original from the \jsc suite that the
 \radamsa\ fuzzer modified. The original test used the integer literal

### 2020-06-08 paper/paper.tex

@@
     \midrule
-    \jsc & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
+    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
     \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
-    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \chakra & \cite{chakracore}\\
+    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
+    \chakra & \cite{chakra2018repo}\\
     \hermes & \cite{hermes2020repo}\\
@@
     Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
-    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
+    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
     JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\

### 2020-06-09 paper/paper.tex
add hermes and github projects in table 2

@@
     \chakra & \cite{chakra2018repo}\\
-    \hermes & \cite{hermes2020repo}\\
+    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
     \midrule
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    Hermes & \cite{jsi} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{}\\
+    \midrule
+    GitHub Projects & - & 494,394 & - & - & - \\
     \midrule

### 2020-06-09 paper/paper.tex
few edits

@@
   \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
-    \includegraphics[trim=0 190 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
+    \includegraphics[trim=0 150 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
     \vspace{-5ex}
@@
   \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
-    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
+    \includegraphics[trim=0 150 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
     \vspace{-5ex}
   }
-  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
-  }}
+  \caption{\label{fig:summary}Summary of bug reports.}
   \vspace{-3ex}
@@
 
-Figure~\ref{fig:lo-truepositive} shows, at the bottom, a sequence of
+\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
+available in the \jsc codebase.  The \radamsa fuzzing technique
+mutated the test. In particular, it introduced the negative
+long \texttt{-1770523502845470856} as a parameter of the
+\texttt{view.getInt8()} method. Before the mutation, the
+\texttt{view.getInt8()} method received a zero integer.}
+At the botom of this figure, there is a sequence of
 three elements that we use to characterize a warning--1) the
@@
 engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market. In
+the browsers informally considered the most popular in the market.
+\Fix{One reader might argue that since we mined files from other JS engines,
+such as Duktape, JerryScript, JSI, and Tiny-js, we could also run test
+transplantation on them. We did not run test transplantation on these
+JS engines due to several reasons, including: JSI was deprecated,
+TinyJS is not actively maintained. Finally, at the time we started this work,
+Duktape and JerryScript did not provide support to ES6. We checked this
+information again in Jun 2020, and they are still only partially supporting ES6.
+}
+In
 terms of construct validity, we used standard metrics to determine the

### 2020-06-09 paper/paper.tex
few more edits

@@
 from the engine's official repositories, 3) test files from the suites
-of public engines, and 4) test files mined from issue trackers of
-these engines.
+of public engines (ie., Duktape, JerryScript, JSI, and Tiny-js),
+4) test files mined from issue trackers of
+these engines, and 5) test files from other GitHub projects.
 
@@
 or use functions that, albeit part of the spec, not all engines
-currently support. For the evaluation of test transplantation, we used
+currently support. \Fix{Similarly, the \chakra project does not use the default
+well-known assertions available in JS, which the other JS engines use.
+Instead, it uses its own testing framework, WScript. In this case, we could
+not easily reproduce the \chakra unit tests in the other engines since it would
+raise a ReferenceError. Also, updating the other engines to use WScript would
+require a non-trivial manual process.}
+
+For the evaluation of test transplantation, we used
 the \totalTestFilesForTestTransplantation{} tests included in the
@@
 
-\subsection{Mining Tests from Issue Trackers}
+\subsection{Mining Tests}
+
+\subsubsection{from GitHub projects}
+
+\Fix{We mined JS programs from the GitHub repository. In this case, we searched
+for projects written in JavaScript, that were tagged with ``javascript-engine",
+and that have both ``Javascript" and ``engine" the name or the description of
+the project. After this process, we ended up with 2200 JS programs, which we
+downloaded locally. However, after careful investigation, we noted that 160 of
+these projects do not  have any JS file, which were excluded from our study.
+We used the 2040 remaining ones as input to our testing approaches.}
+
+\subsubsection{from Issue Trackers}
 

### 2020-06-10 paper/paper.tex
edits
spell checking and minor change in abstract

@@
 
-\author{Jefferson Silva \and Igor Lima \and Breno Miranda\footnotemark
+\author{Igor Lima \and Jefferson Silva \and Breno Miranda\footnotemark
   \and Gustavo Pinto \and Marcelo d'Amorim}
@@
 \institute{
-* Corresponding author: Breno Miranda \and \email{bafm@cin.ufpe.br}\\ \\
+* Corresponding author: Breno Miranda \and
+\email{bafm@cin.ufpe.br}\\ \\
+Igor Lima \and \email{isol2@cin.ufpe.br} \\
 Jefferson Silva \and \email{jefferson.alves.silva@icen.ufpa.br}\\
-Igor Lima \and \email{isol2@cin.ufpe.br} \\
+Breno Miranda \and \email{bafm@cin.ufpe.br} \\
 Gustavo Pinto \and \email{gpinto@ufpa.br} \\
-Breno Miranda \and \email{bafm@cin.ufpe.br} \\
 Marcelo d'Amorim \and \email{damorim@cin.ufpe.br} \\
@@
 scenarios are not covered in the suite. In addition, we noticed that a
-significant fraction (5 to 15\%) of the tests in that stuite fail
+significant fraction (5 to 15\%) of the tests in that suite fail
 regularly in the most popular engines, reflecting the struggle of developers in keeping
@@
 \emph{Key Findings.}~We found that--1)~Differential testing and Test
-Transplation are practical and effective techniques to find bugs on real,
+Transplantation are practical and effective techniques to find bugs on real,
 complex, and widely used software systems, 2)~Even for problems with
 fairly clear specifications, as in \javascript{}, there is likely (a
-lot of) variation between different implementations, which brings instrinsic
+lot of) variation between different implementations, which brings intrinsic
 challenges to developers that work on them.
@@
 from the engine's official repositories, 3) test files from the suites
-of public engines (ie., Duktape, JerryScript, JSI, and Tiny-js),
+of public engines (\ie{}, Duktape, JerryScript, JSI, and Tiny-js),
 4) test files mined from issue trackers of
@@
 raise a ReferenceError. Also, updating the other engines to use WScript would
-require a non-trivial manual process.}
+require a non-trivial manual process. This is why \chakra is not showed
+in Table~\ref{tab:test-suites}.}
 
@@
     \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
-    \chakra & \cite{chakra2018repo}\\
+    %\chakra & \cite{chakra2018repo}\\
     \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
@@
 %%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
-%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers
+%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
+%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno
+% LocalWords:  d'Amorim Universidade Pernambuco

### 2020-06-10 paper/paper.tex
pass on intro

@@
 \title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
-%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head
+\titlerunning{Exposing Bugs in JavaScript Engines}        % if too long for running head
 
@@
 
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality. \Mar{seria bom
-  adicionar uma frase com rationale para escolha destas tecnicas.}
+These techniques demand different effort from developers. Cross-engine
+differential testing is semi-automated as developers need to decide if
+alarms are manifestations of real bugs. Test transplantation is fully
+automated, but it can only reveal bugs that the original tests could
+reveal. This study measures the ability of these techniques in finding
+bugs and the human cost associated with each technique.
 
@@
 not easily reproduce the \chakra unit tests in the other engines since it would
-raise a ReferenceError. Also, updating the other engines to use WScript would
+raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
 require a non-trivial manual process. This is why \chakra is not showed
@@
 \Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
-available in the \jsc codebase.  The \radamsa fuzzing technique
+available in the \jsc code base.  The \radamsa fuzzing technique
 mutated the test. In particular, it introduced the negative
@@
 \texttt{view.getInt8()} method received a zero integer.}
-At the botom of this figure, there is a sequence of
+At the bottom of this figure, there is a sequence of
 three elements that we use to characterize a warning--1) the
@@
 development.
-
-For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios. Table~\ref{tab:test262} shows
+\Fix{For this experiment, we ran the suite once a day for seven consecutive
+days and averaged the passing ratios.
+We performed seven consecutive executions because,
+since the studied JS engines release new versions on a daily basis,
+we wanted to make sure if the failing tests raised by the Test262 suite
+were rapidly fixed by the maintenance team. If these errors were quickly
+fixed, that would suggest that this given engine would be aligned with
+the ECMAScript specification.}
+Table~\ref{tab:test262} shows
 the average number of passing tests over this period. The variance of
@@
     \smonkey{} & \percentSuiteTestSM{} \\
-    \hermes & xxx \\
+    \hermes & \percentSuiteTestHermes{} \\
     \bottomrule
@@
 
+%Nao envolver o hermes nos experimentos antigos pq o hermes vai
+%lancar erros pq a funcionalidade não foi implementada
+
 Results show that there are still many unsupported scenarios as can be observed from the
 percentages in the table. The number of passing tests is high and
-similar for \jsc, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
+similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
+worse when compared to the other engines.
+\Fix{This happens because \hermes
+still has many unsupported features, such as Proxy, Promisse, and Async.}
+Moreover, one can also note that \chakra\ also a low passing ratio
+in this test suite and the one we were able to find more bugs (as per
 Figure~\ref{fig:summary}). Although it is plausible to find
 correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
+the number of bugs found, we do not imply causality. As aforementioned,
+it is important
 to note that failures in this conformance test suite indicates missing
@@
     \begin{minipage}{8cm}
-      \textit{Summary:}~All engines seem to adhere well to the
-      \js\ standard. Except for \chakra, the passing ratio of all
+      \textit{Summary:}~Most of the engines seem to adhere well to the
+      \js\ standard. Except for \hermes and \chakra, the passing ratio of all
       engines is above 90\%.
@@
   \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrr}
+  \begin{tabular}{crrrrr}
     \toprule
-    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{}\\
+    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} & \hermes{} \\
     \midrule
@@
     }
-    \jsc & - & 10 & 10 & 59   \\
-    \veight{} & 41 & - & 3 & 5  \\
+    \jsc & - & 10 & 10 & 59 & 340  \\
+    \veight{} & 41 & - & 3 & 5 & 315 \\
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 \\
-    Duktape & 0 & 4 & 4 & 1   \\
-    \jerry{} & 23 & 25 & 22 & 23   \\
-    JSI & 0 & 0 & 0 & 0   \\
-   Tiny-js & 0 & 0 & 0 & 0  \\
+    \smonkey{} & 218 & 107 & - & 281 & - \\
+    Hermes & 8 & 14 & 8 & 26 & -  \\
+    Duktape & 0 & 4 & 4 & 1 & 140  \\
+    \jerry{} & 23 & 25 & 22 & 23 & 311  \\
+    JSI & 0 & 0 & 0 & 0 & 40\\
+   Tiny-js & 0 & 0 & 0 & 0 & 10  \\
     \midrule
-   \textbf{total} & 282 & 146 & 39 & 369 \\
+   \textbf{total} & 290 & 160 & 47 & 395 & 1156 \\
     \bottomrule
@@
 tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine;
+combinations that associate a test suite with its parent engine.
+\Fix{
+In particular, we were not able to reuse the \smonkey tests on the
+\hermes engine. This happened because \smonkey has its own assertion
+framework, but \hermes did not interpret these assertions, resulting
+in failures in all test executions from this engine. These failures
+did not happen when the \smonkey tests were transplanted to the other engines,
+though.
+}
 failures in those cases would either indicate regressions or flaky
@@
     \midrule
-    \radamsa{} & 151 & 50 & 331 & 94 & 628 \\ % 137 & 47 & 323 & 21 & 483
+    \radamsa{} & 151 & 50 & 331 & 94 & 528 \\ % 137 & 47 & 323 & 21 & 483
     \quickfuzz{} & 83 & 63 & 351 & 21 & 403 \\ % 81 & 62 & 349 & 13 & 369
     \midrule
-    \textbf{total} & 234 & 113 & 682 & 115 & 1031 \\ % 218 & 109 & 672 & 34 & 852
+    \textbf{total} & 234 & 113 & 682 & 115 & 931 \\ % 218 & 109 & 672 & 34 & 852
     \bottomrule
@@
 (``Fuzzer''), the \js\ engine affected (``Engine''), the status of the
-bug report (``Status'')\Comment{ as of Aug. 24, 2018, the Url of the bug report
-(``Url'')}, the severity of the bug report (``Sev.''), the priority
+bug report (``Status'')\Comment{ as of Aug. 24, 2018, the URL of the bug report
+(``URL'')}, the severity of the bug report (``Sev.''), the priority
 that we assigned to the warning that revealed the bug (``Priority''),
@@
 
-This is a testcase original from the \jsc suite that the
+This is a test case original from the \jsc suite that the
 \radamsa\ fuzzer modified. The original test used the integer literal
@@
 students in the task of diagnosing these warnings. Using learning
-techniques for prioritization, similar to what Chen and
-colleagues~\cite{Chen:2017:LPT:3097368.3097451} did to prioritize the
-warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
+techniques for prioritization~\cite{icst2020violations}, 
+similar to what Chen and colleagues~\cite{Chen:2017:LPT:3097368.3097451} 
+did to prioritize the warnings reported by CSmith~\cite{Yang:2011:FUB:1993498.1993532},
 seems a promising starting point for this improvement.
@@
 %%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
-%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno
-% LocalWords:  d'Amorim Universidade Pernambuco
+%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
+% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
+% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
+% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
+% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
+% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
+% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
+% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
+% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
+% LocalWords:  PRONEX

### 2020-06-10 paper/paper.tex
edits

--- 2020-06-09 paper/paper.tex
@@
 not easily reproduce the \chakra unit tests in the other engines since it would
-raise a ReferenceError. Also, updating the other engines to use WScript would
-require a non-trivial manual process.}
+raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
+require a non-trivial manual process. This is why \chakra is not showed
+in Table~\ref{tab:test-suites}.}
 

### 2020-06-10 paper/abstract.tex

@@
 We conducted experiments with engines from five major players--Apple,
-Google, Microsoft, Facebook, and Mozilla--to assess the effectiveness
+Facebook, Google, Microsoft, and Mozilla--to assess the effectiveness
 of test transplantation and differential testing.
@@
 most of these bugs affected two engines--Apple's
-\jsc{} and Microsoft's \chakra{}.
+\jsc and Microsoft's \chakra{} (24 and 26 bugs, respectively).
 To summarize, our results show that

### 2020-06-10 paper/paper.tex
pecentual hermes table 4

@@
 not easily reproduce the \chakra unit tests in the other engines since it would
-raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
+raise a ReferenceError. Also, updating the other engines to use WScript would
 require a non-trivial manual process. This is why \chakra is not showed
@@
 development.
-\Fix{For this experiment, we ran the suite once a day for seven consecutive
-days and averaged the passing ratios.
-We performed seven consecutive executions because,
-since the studied JS engines release new versions on a daily basis,
-we wanted to make sure if the failing tests raised by the Test262 suite
-were rapidly fixed by the maintenance team. If these errors were quickly
-fixed, that would suggest that this given engine would be aligned with
-the ECMAScript specification.}
-Table~\ref{tab:test262} shows
+
+For this experiment, we ran the suite once a day for seven consecutive
+days and averaged the passing ratios. Table~\ref{tab:test262} shows
 the average number of passing tests over this period. The variance of

### 2020-06-11 paper/paper.tex
Fixed running title
wip
pass on TT table and fixing wrong number in table
fixing TT table
edits

--- 2020-06-10 paper/paper.tex
@@
 
+%Nao envolver o hermes nos experimentos antigos pq o hermes vai
+%lancar erros pq a funcionalidade não foi implementada
+
 Results show that there are still many unsupported scenarios as can be observed from the
 percentages in the table. The number of passing tests is high and
-similar for \jsc, \veight{}, and \smonkey\ whereas \chakra\ performs
-worse compared to the other engines. Note also that \chakra\ is both
-the engine that has the lowest passing ratio in this test suite and
-the one we were able to find more bugs (as per
+similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
+worse when compared to the other engines.
+\Fix{This happens because \hermes
+still has many unsupported features, such as Proxy, Promisse, and XXX.}
+Moreover, one can also note that \chakra\ also a low passing ratio
+in this test suite and the one we were able to find more bugs (as per
 Figure~\ref{fig:summary}). Although it is plausible to find
 correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. It is important
+the number of bugs found, we do not imply causality. As aforementioned,
+it is important
 to note that failures in this conformance test suite indicates missing

### 2020-06-11 paper/paper.tex
edits

@@
 \Fix{This happens because \hermes
-still has many unsupported features, such as Proxy, Promisse, and XXX.}
+still has many unsupported features, such as Proxy, Promisse, and Async.}
 Moreover, one can also note that \chakra\ also a low passing ratio

### 2020-06-11 paper/paper.tex
pass on section 2

@@
 
-The study measures the ability of these techniques in finding bugs and
-the impact of false positives on their practicality. \Mar{seria bom
-  adicionar uma frase com rationale para escolha destas tecnicas.}
+\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
+  (more coherent/compelling) as to justify the selection of these two
+  techniques?}These techniques demand different effort from
+developers. Cross-engine differential testing is semi-automated as
+developers need to decide if alarms are manifestations of real
+bugs. Test transplantation is fully automated, but it can only reveal
+bugs that the original tests could reveal. This study measures the
+ability of these techniques in finding bugs and the human cost
+associated with each technique.
 
@@
 \sloppy \emph{Results.}~We considered the following engines--\chakra{}
-(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
-\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
-(\ref{fig:stacked-technique}).
-Each stacked bar breaks down the bugs
-per status (\eg{}, ``1-New''). The prefix number indicates the
-ordering that status labels are assigned. Several of these
-reports have the label ``3-Fixed'', indicating that bug fixes have
-been incorporated into the code already. Note that most of these bugs
-affected two engines--\chakra{} and JavaScriptCore (\jsc).  We
-reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed),
-\noBugsBugsReportedHermes in \hermes,
-and \noBugsBugsReportedSMonkey in \smonkey{}.
+(Microsoft), JavaScriptCore (Apple), \veight{} (Google), \smonkey{}
+(Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the
+breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per
+technique (\ref{fig:stacked-technique}).  Each stacked bar breaks down
+the bugs per status (\eg{}, ``1-New''). The prefix number indicates
+the ordering that status labels are assigned. Several of these reports
+have the label ``3-Fixed'', indicating that bug fixes have been
+incorporated into the code already. Note that most of these bugs
+affected two engines--\chakra{}\footnote{Microsoft announced in
+  December 2018 that the Edge browser will be based on Chromium and
+  ChakraCore development would be
+  discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
+We reported \noBugsBugsReportedGoogle{} bugs in \veight{}
+(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
+\hermes (\Fix{? confirmed}\Mar{by the color, there is some, no?}), and
+\noBugsBugsReportedSMonkey in \smonkey{} (\Fix{? confirmed}).
 Furthermore, our results show that both techniques revealed several
@@
 indicate that both techniques were successful at finding bugs. The
-number of bug reports were similar, if we consider only those
-confirmed or fixed. Most bugs we found are of moderate severity.
+number of fixed bugs were similar, if we consider only those confirmed
+or fixed. Most bugs we found are of moderate severity.
 
@@
 Transplantation are practical and effective techniques to find bugs on real,
-complex, and widely used software systems, 2)~Even for problems with
+complex, and widely used software systems and 2)~Even for problems with
 fairly clear specifications, as in \javascript{}, there is likely (a
@@
 %% LIST OF CONTRIBUTIONS
-\emph{Contributions.}~The most important contribution of this work is empirical:
-we provide a comprehensive study analyzing the effectiveness of
-test transplantation and differential testing
-in revealing functional bugs in popular \javascript\ engines.
-Additional contributions are:
-1)~A number of bugs found and fixed.
-We reported a total of \totalBugsReported bugs.
-Of these, \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were fixed.
-2)~An infrastructure for performing test transplantation and differential testing.
-Both the scripts to run the experiments and the data processed are publicly available at \dataRepo.
-
-\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
-that exploring test transplantation and differential testing
-should be encouraged to find functional bugs
-in JavaScript engines.
+\emph{Contributions.}~The most important contribution of this work is
+empirical: we provide a comprehensive study analyzing the
+effectiveness of test transplantation and differential testing in
+revealing functional bugs in popular \javascript\ engines.  Additional
+contributions include: 1)~A number of bugs found and fixed.  We
+reported a total of \totalBugsReported bugs.  Of these,
+\totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
+fixed.  2)~An infrastructure for performing test transplantation and
+differential testing.  The tools we used and the data sets of tests
+and bugs are publicly available online at the following link:
+
+\dataRepo.
+
+\vspace{1ex} To summarize, this paper provides initial, yet strong
+evidence that test transplantation and differential testing are simple
+and effective techniques to find functional bugs in JavaScript engines
+and should be encouraged.
 
@@
 under the TC39~\cite{tc39-github} technical committee.  Every year, a
-new version of the \es{} specification is produced with new features
-and minor fixes. The canonical spec today is
-ES6~\cite{ecmas262-spec-repo,ecmas262-spec}.
+new version of the \es{} specification is released with new features
+and minor fixes~\cite{ecmas262-spec-repo,ecmas262-spec}.
 
@@
 The specification of JavaScript is incomplete for different
-reasons. Certain parts of the specification are undefined; it is
-the responsibility of engineers to decide how to implement these
+reasons. Certain parts of the specification are undefined; it is the
+responsibility of engineers to decide how to implement these
 functionalities. The JavaScript spec uses the label
 ``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason this flexibility in the
-spec exists to enable compiler optimizations. For example, the
+may differ from engine to engine. One reason for suchs flexibility in
+the spec is to enable compiler optimizations. For example, the
 \js\ \mcodeid{for-in} loop construct does not clearly specify the
@@
 implementation-dependent~\cite{es6-toPrecision}. Various other cases
-like these exist in the specification. Given the speed the
-specification changes and the complexity of the language some features
-are not fully implemented as can be observed by the Kangax
+like these exist in the specification. Added to that, given the speed
+the specification changes and the complexity of the language some
+features are not fully implemented as can be observed by the Kangax
 compatibility table~\cite{kangax}.  It is also worth noting that, as
@@
 cases should not manifest this kind of flaky behavior.  As previously
-mentioned, all those aspects make testing \js\ engines challenging.
+mentioned, all those aspects make testing \js\ engines challenging,
+albeit very important given the its tremendous popularity.
 

### 2020-06-11 paper/paper.tex
pass on section 4

@@
 \label{sec:seeds}
-A good test set is critical for finding bugs with the techniques used
-in this paper. For that reason, we looked for \js\ files from various
-sources: 1) test files from the Test262~\cite{tc39-github} conformance
-suite of the ECMA262 specification~\cite{ecmas262-spec}, 2) test files
-from the test suite of the selected engines (see
-Section~\ref{sec:methodology:engines}); these files are accessible
-from the engine's official repositories, 3) test files from the suites
-of public engines (\ie{}, Duktape, JerryScript, JSI, and Tiny-js),
-4) test files mined from issue trackers of
-these engines, and 5) test files from other GitHub projects.
+
+Obtaining good sets of JS test cases is imperative to evaluate the
+techniques in this paper. For that, we looked for \js\ files from
+various sources: 1) test files from the Test262~\cite{tc39-github}
+conformance suite of the ECMA262 specification~\cite{ecmas262-spec},
+2) test files from the test suite of our selected engines; these files
+are accessible from the engine's official repositories, 3) test files
+from the suites of other public engines (\ie{}, Duktape, JerryScript,
+JSI, and Tiny-js), 4) test files mined from issue trackers of these
+engines, and 5) test files from other GitHub projects.
 
@@
 %% API~\cite{github-rest-api}.
-
-Table~\ref{tab:test-suites} shows the breakdown of tests per
-engine. Column ``full'' shows the number of test cases associated with
-each engine. Column ``pass-in-par.''  shows the number of test cases
-that pass in their parent engine. We discarded tests that fail in
-their parent engine as we could not reliably indicate the reason for
-the failure, so we assumed the test could be broken. We removed \testsThatFail{}
-test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
-\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
-shows the number of test cases whose executions do not throw
-dynamic type errors in any of the engines because of an undefined variable or property.
-These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
-\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc's
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. \Fix{Similarly, the \chakra project does not use the default
-well-known assertions available in JS, which the other JS engines use.
-Instead, it uses its own testing framework, WScript. In this case, we could
-not easily reproduce the \chakra unit tests in the other engines since it would
-raise a \texttt{ReferenceError}. Also, updating the other engines to use WScript would
-require a non-trivial manual process. This is why \chakra is not showed
-in Table~\ref{tab:test-suites}.}
-
-For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
-conformance suite as they are more likely to indicate missing features
-as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
 
@@
   \caption{\label{tab:test-suites}Number of test files. Dashed
-    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
-    shows the tests used for test transplantation (resp., cross-engine
-    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
+    rectangle under column ``type-in-all'' shows the tests used for
+    test transplantation whereas the rectangle under column
+    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
+    the tests used in cross-engine differential
+    testing.\Gustavo{Terminar essa tabela}}
+  \setlength{\tabcolsep}{2pt}
   \begin{tabular}{ccrrrr}
@@
 
+Table~\ref{tab:test-suites} shows the breakdown of tests. Column
+``Name'' and ``Source'' show the origin of the test suite. Column
+``total'' shows the number of test cases associated with a givem
+source. Column ``pass-in-par.''  shows the number of test cases that
+pass in their parent engine. We discarded tests that fail in their
+parent engine as we could not reliably indicate the reason for the
+failure, so we assumed the test could be broken. We removed
+\testsThatFail{} test cases that fail for that
+reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
+tests from \smonkey. Column ``type-in-all'' shows the number of test
+cases whose executions do not throw dynamic type errors in any of the
+engines because of an undefined variable or property.  These cases
+were captured by looking for the presence of \CodeIn{ReferenceError}
+and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
+(respectively, \CodeIn{TypeError}) is raised when test execution
+attempts to access an undefined variable (respectively, property of an
+object). We discarded those tests to avoid noise in the experiments as
+they clearly indicate some missing feature as opposed to bugs. For
+example, some tests use non-portable names (\eg{}, \jsc's
+\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
+or use functions that, albeit part of the spec, not all engines
+currently support. \Fix{Similarly, the \chakra project does not use
+  the default well-known assertions available in JS, which the other
+  JS engines use.  Instead, it uses its own testing framework,
+  WScript. In this case, we could not easily reproduce the \chakra
+  unit tests in the other engines since it would raise a
+  \texttt{ReferenceError}. Also, updating the other engines to use
+  WScript would require a non-trivial manual process. This is why
+  \chakra is not showed in Table~\ref{tab:test-suites}.}\Mar{did not
+  review part in red}
+
+\Mar{Numbers seem inconsistent. I will stop here...}
+For the evaluation of test transplantation, we used
+the \totalTestFilesForTestTransplantation{} tests included in the
+dashed rectangle under column ``type-in-all'', \ie{}, all tests under
+that column but the Test262 tests. We did not consider tests from the
+conformance suite as they are more likely to indicate missing features
+as opposed to bugs. In addition, engine developers have access to
+these test and are encouraged to run them. Finally, column
+``no-fail-in-all'' shows the tests for which all engines pass. Note
+that the set of tests in this column is a subset of the
+``type-in-all'' test set. This test set is used in the evaluation of
+differential testing as fuzzing seeds. The guarantee that they pass in
+all engines assures that, if discrepancies occur, they are related to
+the changes in the input as opposed to the original cause of failure.
+
 %% The main source of test
@@
 
-\subsubsection{from GitHub projects}
+\subsubsection{From GitHub projects}
 
@@
 
-\subsubsection{from Issue Trackers}
-
-\sloppy{}We observed that issue trackers are an important source of
-test data and should not be ignored. Analyzing a sample of issues, we
-observed that developers either 1) add test cases as attachments of
-issues or 2) embed test cases within the textual description of an
-issue. The test cases in attachments are longer compared to the test
-cases embedded in issue descriptions whereas the latter are more
-common. Consequently, we thought we should handle both
+\subsubsection{From Issue Trackers}
+
+Teste cases embedded in issue trackers are an important source of data
+as they may have already shown usefulness to reveal problems in some
+engine. For example, a developer may have found a corner case that a
+given engine did not handle properly. Therefore, it is possible that
+other engine do not handle those cases. We thought that we should not
+ignore issue trackers for that reason. By manually analyzing a sample
+of issues, we observed that developers either 1) add test cases as
+attachments of an issue or 2) embed the test cases within the textual
+description of an issue. The test cases in attachments are longer
+compared to the test cases embedded in issue descriptions whereas the
+latter are more common. Consequently, we thought we should handle both
 cases.
@@
 paragraphs and used a binary classifier to label each paragraph as
-``code'' or ``not code'' (\ie{}, natural language). Then, based on
+``code'' or ``not code'' (\ie{}, text written in natural language). Then, based on
 that information, we merged consecutive paragraphs labeled as ``code''
@@
 fragment. Using that method we were able to retrieve a total of
-\filesMining{} files. All those files were included in
+\filesMining{} additional files. All those files were included in
 Table~\ref{tab:test-suites}.

### 2020-06-11 paper/paper.tex
pass on step2

@@
 output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
+handle discrepancies involving crashes, \Igor{If the criteria is to
+find crashes or fatal errors, it is possible to run the
+infrastructure with any runner(?) tool, including the
+javascript binaries itself.}. As such, we forked the
 eshost-cli GitHub project and implemented that functionality on it. It

### 2020-06-11 paper/paper.tex
pass on word2vec

@@
 
-For the classification of ``code'' vs. ``not code'', we used a
-pipeline of two Neural Networks (NN), a popular design for solving NLP
-classification problems~\cite{kusner2015word}. The first net in the
-pipeline takes as input an arbitrary sentence and produces on output a
-characterization vector for that sentence. The second net in the
-pipeline takes that vector on input and produces a yes/no answer,
-determining whether or not the input sentence was code.  During the
-training phase, the second neural net in the pipeline takes
-additionally on input the value for the class attribute for the sample;
-in this case, ``code'' or ``not code''. More in detail, for the first
-net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
-technique to produce word embeddings. A word embedding is a mapping of
-words to vectors of real numbers. For the second net, we used a
-multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
-infer the probability of the input belonging or not to the class. The
-classifier labels the input input as code if the predicted probability
-of the input being code is 0.7 or higher. We used a corpus with 25K
-samples of English paragraphs and 25K snippets of \js{} code to train
+% For the classification of ``code'' vs. ``not code'', we used a
+% pipeline of two Neural Networks (NN), a popular design for solving NLP
+% classification problems~\cite{kusner2015word}. The first net in the
+% pipeline takes as input an arbitrary sentence and produces on output a
+% characterization vector for that sentence. The second net in the
+% pipeline takes that vector on input and produces a yes/no answer,
+% determining whether or not the input sentence was code.  During the
+% training phase, the second neural net in the pipeline takes
+% additionally on input the value for the class attribute for the sample;
+% in this case, ``code'' or ``not code''. More in detail, for the first
+% net, we used word2vec~\cite{mikolov2013distributed}, a popular NLP
+% technique to produce word embeddings. A word embedding is a mapping of
+% words to vectors of real numbers. For the second net, we used a
+% multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to
+% infer the probability of the input belonging or not to the class. The
+% classifier labels the input input as code if the predicted probability
+% of the input being code is 0.7 or higher. We used a corpus with 25K
+% samples of English paragraphs and 25K snippets of \js{} code to train
+% and test the classifier and obtained an accuracy of 98\%. This
+% classifier is publicly available from our website as a separate
+% component.
+\Igor{
+For the classification of ``code'' vs. ``not code'', we used popular 
+techniques for solving NLP classification problems~\cite{kusner2015word}.
+More in detail, we used word2vec~\cite{mikolov2013distributed},
+a popular NLP technique to produce word embeddings. A word embedding is 
+a mapping of words to vectors of real numbers. We chose word2vec for
+two mainly reasons: i) similarity between sentences and ii)
+to obtaining a low-dimensional vector that can be used in
+a traditional classifier. The next step we used a
+ multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293}
+to infer the probability of the input belonging or not to the class based 
+on the distance of similarity of sentences, the classifier takes that vector
+on input and produces a ``code'' or ``not code'' answer. The classifier labels
+the input as code if the predicted probability of the input being code is 0.7 or higher. 
+We used a corpus with 25K samples of English paragraphs and 25K snippets of \js{} code to train
 and test the classifier and obtained an accuracy of 98\%. This
@@
 component.
+}
 

### 2020-06-11 paper/paper.tex
minor layout changes

@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[trim=0 350 0 0,clip,width=1.0\textwidth]{diff-testing-runtimes}
-  \vspace{-5ex}
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
-  \vspace{-2ex}
-\end{figure}
-
 \section{Cross-Engine Differential Testing}
@@
 shows that a single file will be fuzzed multiple times.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+\end{figure}
 
@@
 \ref{sec:clusterization}. Note that a number of reasons exist, other
-than a bug, to explain discrepancy (see
+than a bug, for discrepancy to arise (see
 Tables~\ref{fig:piecharts-transplantation} and
@@
 earlier, this justifies why differential testing is challenging to
-automate at the functional level.
+automate at the functional level. Existing techniques that use
+differential testing control rate of false alarms differently. For
+example, Mozilla uses varies the configurations of thei
+\smonkey\ engine, but the implementation is the
+same~\cite{mozilla-severity}. The sources of non-determinism are
+therefore similar. CSmith~\cite{Yang:2011:FUB:1993498.1993532}
+addresses the problem by trying to avoid generating C files that
+produce undefined behavior. However, mapping all sources of
+undefinedness in JS is impractical.
 

### 2020-06-11 paper/paper.tex
pass on NLP par

@@
 % component.
-\Igor{
-For the classification of ``code'' vs. ``not code'', we used popular 
-techniques for solving NLP classification problems~\cite{kusner2015word}.
-More in detail, we used word2vec~\cite{mikolov2013distributed},
-a popular NLP technique to produce word embeddings. A word embedding is 
-a mapping of words to vectors of real numbers. We chose word2vec for
-two mainly reasons: i) similarity between sentences and ii)
-to obtaining a low-dimensional vector that can be used in
-a traditional classifier. The next step we used a
- multi-layer perceptron~\cite{Rumelhart:1986:LIR:104279.104293}
-to infer the probability of the input belonging or not to the class based 
-on the distance of similarity of sentences, the classifier takes that vector
-on input and produces a ``code'' or ``not code'' answer. The classifier labels
-the input as code if the predicted probability of the input being code is 0.7 or higher. 
-We used a corpus with 25K samples of English paragraphs and 25K snippets of \js{} code to train
-and test the classifier and obtained an accuracy of 98\%. This
-classifier is publicly available from our website as a separate
-component.
-}
+
+For the classification of ``code'' vs. ``nocode'', we used popular
+techniques for solving NLP classification
+problems~\cite{kusner2015word}.  First, we used
+word2vec~\cite{mikolov2013distributed}, a popular NLP technique to
+produce word embeddings. A word embedding is a mapping of words to
+vectors of real numbers. Then, we used a multi-layer
+perceptron~\cite{Rumelhart:1986:LIR:104279.104293} to infer the
+probability of the input belonging or not to the class based on the
+distance between sentences (\ie{}, the distance from an input sentence
+to a code example or to a nocode example) as induced by the distance
+of comprising words computed with word2vec. The classifier labels the
+input as code if the predicted probability of the input being code is
+0.7 or higher.  We used a corpus with 25K samples of English
+paragraphs and 25K snippets of \js{} code to train and test the
+classifier and obtained an accuracy of 98\%. This classifier is
+publicly available from our website as a separate component.
+
+% We chose word2vec for two main reasons: i) similarity between
+% sentences and ii) to obtaining a low-dimensional vector that can be used in a traditional classifier.
 

### 2020-06-11 paper/paper.tex
Addressing a comment in the Introduction

@@
   (more coherent/compelling) as to justify the selection of these two
-  techniques?}These techniques demand different effort from
-developers. Cross-engine differential testing is semi-automated as
+  techniques?}
+\Breno{Changed the paragraph a bit to include the reuse argument.}
+We selected these two techniques because they can take advantage 
+of existing test suites and reuse them --- in a semi-automated way 
+as we propose here --- to enhance the coverage of the engine under testing.
+%These techniques demand different effort from developers. 
+Cross-engine differential testing is semi-automated as
 developers need to decide if alarms are manifestations of real

### 2020-06-11 paper/paper.tex
new section for hermes in the case study

@@
 (\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
-\hermes (\Fix{? confirmed}\Mar{by the color, there is some, no?}), and
-\noBugsBugsReportedSMonkey in \smonkey{} (\Fix{? confirmed}).
+\hermes (\noBugsBugsConfirmedHermes confirmed), and
+\noBugsBugsReportedSMonkey in \smonkey{} (\noBugsBugsConfirmedSMonkey confirmed).
 Furthermore, our results show that both techniques revealed several
@@
 \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
-fixed.  2)~An infrastructure for performing test transplantation and
-differential testing.  The tools we used and the data sets of tests
+fixed.  2)~An infrastructure called \entente for performing test transplantation and
+differential testing.  Both \entente code and the data sets of tests
 and bugs are publicly available online at the following link:
@@
   \texttt{ReferenceError}. Also, updating the other engines to use
-  WScript would require a non-trivial manual process. This is why
-  \chakra is not showed in Table~\ref{tab:test-suites}.}\Mar{did not
+  WScript would require a non-trivial manual effort. This is why
+  \chakra does not appear in Table~\ref{tab:test-suites}.}\Mar{did not
   review part in red}
@@
 
-\section{Discussion}
+\section{Case Study}
 \label{sec:bugs}
+
+In this section we describe additional experiments to better understand the effectiveness of \entente in a recently introduced JavaScript engine.
+We also cover additional description of a sample of bug reports.
+
+\subsection{Finding bugs in Hermes}
+
+\hermes is a JavaScript engine introduced by Facebook in 2019.
+According to its website, \hermes ``is a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
+Before testing \hermes with our both test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0.
+We observed that only 26\% of the Test262 tests were passing at the \hermes project.
+When taking a closer look, we noticed that this high percentage of failing test was due to the a also high number of features not yet suported by \hermes.
+For instance, in its most recent release, \hermes still do not offer support for features such as Proxy, Promisse, and Async.
+For this reason (the low coverage of Test262 tests), we also opted not to include \hermes along with the other JavaScript engines.
+Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the numbers of test used in the experiments.
+
+We then ran both test transplantation and differential testing on \hermes.
+To do this work, we follow the same methodology described for the others JavaScript engines.
+When experimenting with test transplantation, we noted many errors when replaying the \smonkey testing stuite on \hermes.
+This happened because \smonkey has its own assertion framework, but \hermes did not interpret these assertions, resulting in failures in all test executions from this engine.
+These failures did not happen when the \smonkey tests were transplanted to the other engines, though.
+Overall, we found and repoted three bugs on \hermes using the test transplantation technique.
+One of them was confirmed by the \hermes maintainers.
+For one of the other bugs reported, the maintainer mentioned that the bug in question was regarding a feature not yet supported (a \texttt{return} statement outside the block scope).
+For the third one, the maintainers diverged regarding the proper implementation of one particular item of the specification (i.e., whether a numeric escape (non-octal-eight, \texttt{\textbackslash{8}}) should be allowed or not in strict mode.
+The issue was closed, but the maintainers opened a new one to discuss this matter.
+Among the discussions, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).
+As for the differential testing, we found and reported one bug on \hermes using \radamsa.
+As of this writing, this particular bug report was not yet addressed by any \hermes maintainer.
+
+Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced, with many non-supported official features, engine).
 

### 2020-06-11 paper/paper.tex
edits fuzzers discussion
Made a pass on 7.1 Finding bugs in Hermes

@@
 \hermes is a JavaScript engine introduced by Facebook in 2019.
-According to its website, \hermes ``is a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
-Before testing \hermes with our both test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0.
+According to its website, \hermes is ``a JavaScript engine optimized for fast start-up of React Native apps on Android''~\cite{hermes2020repo}.
+Before applying \entente on \hermes for performing test transplantation and differential testing, we ran the Test262 conformance suite on the most recent version of \hermes, 0.5.0.
 We observed that only 26\% of the Test262 tests were passing at the \hermes project.
-When taking a closer look, we noticed that this high percentage of failing test was due to the a also high number of features not yet suported by \hermes.
-For instance, in its most recent release, \hermes still do not offer support for features such as Proxy, Promisse, and Async.
-For this reason (the low coverage of Test262 tests), we also opted not to include \hermes along with the other JavaScript engines.
-Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the numbers of test used in the experiments.
+When taking a closer look, we noticed that this high percentage of failing tests was due to the high number of features not yet suported by \hermes.
+For instance, in its most recent release, \hermes still does not offer support for features such as Proxy, Promisse, and Async.
+For this reason (the low coverage of Test262 tests), we opted not to include \hermes along with the other JavaScript engines.
+Since we only fuzz test files that pass in all engines, this would require us to significantly reduce the number of tests used in the experiments.
 
@@
 Overall, we found and repoted three bugs on \hermes using the test transplantation technique.
-One of them was confirmed by the \hermes maintainers.
-For one of the other bugs reported, the maintainer mentioned that the bug in question was regarding a feature not yet supported (a \texttt{return} statement outside the block scope).
+One of them was already confirmed by the \hermes maintainers.
+For one of the other bugs reported, the maintainer mentioned that the bug in question is related to a feature not yet supported (a \texttt{return} statement outside the block scope).
 For the third one, the maintainers diverged regarding the proper implementation of one particular item of the specification (i.e., whether a numeric escape (non-octal-eight, \texttt{\textbackslash{8}}) should be allowed or not in strict mode.
 The issue was closed, but the maintainers opened a new one to discuss this matter.
-Among the discussions, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).
+By following the discussion, it was interesting to observe that maintainers are aware that this feature is implemented by other engines such as \veight, \chakra, and \smonkey (yet they were unsure how they should treat it at \hermes).
 As for the differential testing, we found and reported one bug on \hermes using \radamsa.
@@
 
-Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced, with many non-supported official features, engine).
+Overall, we noted that the use of test transplantation and differential testing could be effective techniques in discovering bugs in non-trivial JavaScript software systems, regardless of their maintenance scenario (that is, we found bugs in both extremely roubust and largely adopted engines and also on a recently introduced one with many non-supported official features).
 

### 2020-06-12 paper/paper.tex
pass on section 7 (Hermes)

--- 2020-06-11 paper/paper.tex
@@
 
+\input{table_differential}
+
 Table~\ref{tab:bugs} shows the list of bugs we reported. The table
@@
 
-\input{table_differential}
-
 %% Note from the table that all bug reports still waiting for
@@
 
+\section{Case Study: \hermes}
+\label{sec:bugs}
+
+This section describes the experiment we conducted to evaluate the
+effectiveness of the techniques we studied to find new bugs in
+\hermes, a JavaScript engine that has started development very
+recently. \hermes is a JavaScript engine introduced by Facebook in
+2019. According to its website, \hermes is ``a JavaScript engine
+optimized for fast start-up of React Native apps on
+Android''~\cite{hermes2020repo}.\Mar{short sentence saying where it is
+  used.}
+
+%  for performing 
+As a preparatory step to apply test transplantation and differential
+testing to \hermes, we ran the Test262 conformance suite on the most
+recent version of \hermes, 0.5.0. We observed that only 26\% of the
+Test262 tests passed. When taking a closer look, we noticed that this
+high percentage of failing tests was due to the high number of
+features not yet suported by \hermes\footnote{See
+  \url{https://github.com/facebook/hermes/blob/master/doc/Features.md}}. For
+instance, in its most recent release, \hermes still does not support
+for features such as Proxy, Promise, and Async calls. For this
+reason---low coverage on Test262---, we opted not to include \hermes
+with other JavaScript engines. Since we only fuzz test files that pass
+in all engines, this would require us to significantly reduce the
+number of tests used in the experiments, affecting overall results.
+
+We followed the same methodology described in previous sections to
+evaluate \hermes. When experimenting with test transplantation, we
+noted many errors when replaying the test suite of \smonkey on
+\hermes. This happened because \smonkey has its own assertion
+framework, but \hermes was unable to interpret those assertions,
+resulting in failures in all test executions from this engine. These
+failures did not happen when the \smonkey tests were transplanted to
+the other engines, though\Mar{Why? Was the framework using some of the
+  features aforementioned? Say it, please.}. Overall, we repoted three
+issues to the \hermes bug tracker as result of using test
+transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},
+  with id 265, 266, 267.}. One of them was confirmed by the \hermes
+maintainers by the time of this submission. For another, the
+maintainer explained the issue was related to a feature not yet
+supported---a \texttt{return} statement outside the scope of a
+block. For the third issue, developers disagreed on the proper
+implementation of one particular part of the specification involved in
+the issue (i.e., whether a numeric escape character (non-octal-eight,
+\texttt{\textbackslash{8}}) should be allowed or not in strict
+mode. The issue was closed, but the maintainers opened a new one to
+discuss this matter. By following the discussion, it was interesting
+to observe that maintainers are aware that this feature is implemented
+by other engines such as \veight, \chakra, and \smonkey. Yet, they
+were unsure how they should treat it in \hermes.  Considering
+differential testing, we found and reported one bug on \hermes using
+\radamsa. As of this writing, this particular bug report was not yet
+addressed by any \hermes maintainer.
+
+Overall, we noted that test transplantation and differential testing
+were effective techniques in revealing potential bugs in non-trivial
+JavaScript engines of varying degrees of maturity. We found bugs both
+in extremely robust and largely adopted engines and also in recently
+developed engines. \Mar{check $\rightarrow$}The issue diagnosis of
+developers seem to differ though. Issues reported to stable engines
+are more likely to be real bugs---as lots of problems have been
+already scrutinized---whereas issues reported to new engines are more
+likely to be inconsistencies related to influx development as opposed
+to real bugs.
+
 \section{Discussion}
-\label{sec:bugs}
-
-\subsection{Example Bug Reports}
+
+This section discusses bug reports, threats to validity, and key
+findings and lessons learned.
+
+\subsection{Bug Reports}
 

### 2020-06-12 paper/paper.tex
pass

@@
 
-This section discusses a sample of bugs reports. The selection
-criteria we used was: (i) to cover all engines we found bugs--\chakra,
-\jsc, and \veight, (ii) to cover each technique--test transplantation
-and differential testing (with \radamsa\ and with \quickfuzz), (iii)
-to cover a case of rejected bug report, and (iv) to use short tests
-(for space).
+We issued several bug reports as result of this work. For space, we
+are unable to discuss all of them. We sampled some bug reports to
+discuss in the following. The selection criteria we used was: (i) to
+cover all engines we found bugs--\chakra, \jsc, and \veight, (ii) to
+cover each technique--test transplantation and differential testing
+(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
+rejected bug report, and (iv) to use short tests (for space).
 
@@
 version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character (\CodeIn{NUL})\Comment{ in
-ascii}. The unary plus expression ``\CodeIn{+a}", used in the
-assertion, is equivalent to the operation
+returns a string representation of a null character
+(\CodeIn{NUL})\Comment{ in ascii}. The unary plus expression
+``\CodeIn{+a}", used in the assertion, is equivalent to the operation
 \CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
@@
 \chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN as result and the test fails
-as expected. \chakra{}, instead, incorrectly converts the string
-to zero, making the test to pass. As Table~\ref{tab:bugs} shows, the
-\chakra{} team fixed the issue soon after we reported the problem.
+hexadecimal. As such, they produce a NaN and the test fails as
+expected. \chakra{}, instead, incorrectly converts the string to zero,
+and the test passes. As Table~\ref{tab:bugs} shows, the \chakra{} team
+fixed the issue soon after our report.
+
+\Mar{--------------- estou aqui}
 

### 2020-06-12 paper/paper.tex
pass on 8.1

@@
   }\\
-  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
+  \subfloat[\label{fig:stacked-technique}Bug reports per technique.]{
     \includegraphics[trim=0 150 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
@@
 are unable to discuss all of them. We sampled some bug reports to
-discuss in the following. The selection criteria we used was: (i) to
-cover all engines we found bugs--\chakra, \jsc, and \veight, (ii) to
-cover each technique--test transplantation and differential testing
-(with \radamsa\ and with \quickfuzz), (iii) to cover a case of
-rejected bug report, and (iv) to use short tests (for space).
+discuss in the following. The selection criteria we used was:
+\begin{enumerate}
+\item to cover all engines we found bugs--\chakra, \hermes, \jsc,
+  \smonkey, \veight (see Figure~\ref{fig:summary});
+\item to cover each technique--test transplantation and differential
+  testing;
+\item to cover a case of rejected bug report;
+\item to use short tests (for space).  
+\end{enumerate}
 
@@
 
-\Mar{--------------- estou aqui}
-
 \vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
-code {\footnotesize\ttfamily{eval(function b(a)\{break;\});}} shows
-the test input we used to reveal a bug in \veight{}. This code snippet
-was obtained by fuzzing a Test262 test with \quickfuzz. In its
-original version, a string (omitted for space), passed as argument to
-the \CodeIn{eval} function, encoded the actual test. The fuzzer
-replaced the string argument with a function whose body is a
-\CodeIn{break} statement outside a valid block statement. Section
-B.3.3.3 from the spec~\cite{spec-b333} documents how eval should
-handle code containing function declarations.  According to the
+snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
+revealed a bug in \veight{} version 7.0.244. This code snippet was
+obtained by fuzzing a Test262 test with \quickfuzz. In its original
+version, a string (omitted for space), passed as argument to the
+\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
+the string argument with a function whose body is a \CodeIn{break}
+statement outside a valid block statement. Section B.3.3.3 from the
+\es\ spec~\cite{spec-b333} documents how eval should handle code
+containing function declarations.  According to the
 spec~\cite{break-statement}, the virtual machine should throw an early
 error--in this case, a SyntaxError--if the break statement is not
-nested in an iterable or a switch statement. All engines, but
-\veight{}, behave as expected in this case.
+nested in a loop or switch statement. All engines, but \veight{},
+behave as expected in this case.
 
@@
 
+\Mar{--------------- estou aqui}
+
 \vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
-shows the test input we used to reveal a bug in \jsc. This test
-originates from \jerry{} test suite; the bug was found during the test
-transplantation experiment.
+  Table~\ref{tab:test-transplantation-bugs}.}\Mar{$\leftarrow$ isto
+  esta errado! A tabela diz que eh Chakra}  The code snippet below
+shows the test input we used to reveal a bug in \jsc.
 
@@
 
-According to the specification~\cite{ecmas262-array-sort}, the
-parameter to the \CodeIn{Array.sort} function should be a comparable
-object or an undefined value, otherwise it should throw a
-\CodeIn{TypeError}. In this case, \jsc accepts a non-callable object
-as argument to \CodeIn{sort} and the test fails in the subsequent
-step. The other engines raise a \CodeIn{TypeError} as expected.
-
-\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.}  The
-code snippet below shows an example input related to a bug report that
-we issued to the \chakra\ development team, but they did not accept.
+This is a test case of the \jerry{} suite. The bug was found during
+the test transplantation experiment. According to the
+\es\ spec~\cite{ecmas262-array-sort}, the parameter to the
+\CodeIn{Array.sort} function should be a comparable object or an
+undefined value, otherwise it should throw a \CodeIn{TypeError}. In
+this case, \jsc incorrectly accepts a non-callable object as argument
+to \CodeIn{sort} and the test fails in the subsequent step. The other
+engines raise a \CodeIn{TypeError} as expected.
+
+\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
+reported the code snippet below to the \chakra\ development team as a
+bug, but they did \emph{not} accept.
 
@@
 \radamsa\ fuzzer modified. The original test used the integer literal
-3 as argument to \CodeIn{repeat()}, but this test uses a long integer
-instead. As result, the engine crashes. The team answered that this
-was an incompatibility by design as the function was not expected to
-receive such a long value.
+3 as argument to \CodeIn{repeat()}, \ie{}, the expression produced a
+string with three repetitiong of the string ``foo''. The new test uses
+a long integer instead as parameter to \CodeIn{repeat()}. As result,
+the engine crashes. The team answered that this was an incompatibility
+by design\footnote{We interpreted as a violation of an undocumented
+  precondition} as the function was not expected to receive such a
+long value.
 

### 2020-06-12 paper/paper.tex
pass

@@
 
-As it is the case for most empirical evaluations, our findings are
-subject to internal, external, and construct validity
-threats. Considering internal validity, conceptually, it is possible
+As it is the case of most empirical evaluations, our findings are
+subject to internal, external, and construct threats to
+validity. Considering internal validity, conceptually, it is possible
 that the authors of this paper made mistakes in the implementation of
@@
 sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a well-defined criteria and found that the
+the engines by using using a documented criteria and found that the
 engines selected were associated, certainly not by coincidence, with
-the browsers informally considered the most popular in the market.
-\Fix{One reader might argue that since we mined files from other JS engines,
-such as Duktape, JerryScript, JSI, and Tiny-js, we could also run test
-transplantation on them. We did not run test transplantation on these
-JS engines due to several reasons, including: JSI was deprecated,
-TinyJS is not actively maintained. Finally, at the time we started this work,
-Duktape and JerryScript did not provide support to ES6. We checked this
-information again in Jun 2020, and they are still only partially supporting ES6.
-}
-In
-terms of construct validity, we used standard metrics to determine the
-effectiveness of the testing techniques we studied (\eg{}, number of
-bugs confirmed and fixed and severity). Engine developers were
-responsible for determining the labels of the bug reports and their
-severity. Consequently, these metrics originate from a trusted source.
+the browsers informally considered the most popular in the market.  A
+reader might argue that since we mined files from other JS engines,
+such as Duktape, JerryScript, JSI, and Tiny-js, we could also have ran
+test transplantation on them. We decided not to do so for different
+reasons: JSI was deprecated, TinyJS is not actively
+maintained. Finally, at the time we started this work, Duktape and
+JerryScript did not provide support to ES6. We checked this
+information again in Jun 2020, and they are still only partially
+supporting ES6. In terms of construct validity, we used standard
+metrics to determine the effectiveness of the testing techniques we
+studied (\eg{}, number of bugs confirmed and fixed and
+severity). Engine developers were responsible for determining the
+labels of the bug reports and their severity. Consequently, these
+metrics originate from a trusted source.
 

### 2020-06-12 paper/paper.tex
fix bug number in discussion

@@
 
-\vspace{1ex}\noindent\textbf{Issue \#18,
-  Table~\ref{tab:test-transplantation-bugs}.}\Mar{$\leftarrow$ isto
-  esta errado! A tabela diz que eh Chakra}  The code snippet below
+\vspace{1ex}\noindent\textbf{Issue \#19,
+  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
 shows the test input we used to reveal a bug in \jsc.

### 2020-06-12 paper/paper.tex
adding sm bug in discussion

@@
 long value.
+
+\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
+reported the code snippet below to the \smonkey\ development team as a
+bug, the bug was confirmed in a few hours.
+
+\begin{figure}[h!]
+  \vspace{-0.5ex}
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+    "use strict"
+    010
+  \end{lstlisting}
+  \normalsize
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
+  \vspace{-1ex}
+\end{figure}
+
+This is a test case original from the \hermes suite using test transplantation.
+According the specification, in strict mode, the engine must use 
+the prefix '0o' or '0O' to represents octal numeric literals. It was an
+issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
+The others engine throws a SyntaxError due the missing of the octal token, but 
+\smonkey returns a integer 8 that represents 010 in octal literal.
 

### 2020-06-12 paper/paper.tex
intro

--- 2020-06-12 paper/paper.tex
@@
 
-\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
-  (more coherent/compelling) as to justify the selection of these two
-  techniques?}
-\Breno{Changed the paragraph a bit to include the reuse argument.}
+%\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
+%  (more coherent/compelling) as to justify the selection of these two
+%  techniques?}
+%\Breno{Changed the paragraph a bit to include the reuse argument.}
 We selected these two techniques because they can take advantage
@@
 \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
-fixed.  2)~An infrastructure called \entente for performing test transplantation and
-differential testing.  Both \entente code and the data sets of tests
+fixed.  2)~An infrastructure for performing test transplantation and
+differential testing. The soruce code produced and the generated data sets of tests
 and bugs are publicly available online at the following link:
@@
     the tests used in cross-engine differential
-    testing.\Gustavo{Terminar essa tabela}}
+    testing.}
   \setlength{\tabcolsep}{2pt}
@@
     %\chakra & \cite{chakra2018repo}\\
-    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
+    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
     \midrule
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    \midrule
-    GitHub Projects & - & 494,394 & - & - & - \\
+    %\midrule
+    %GitHub Projects & - & 494,394 & - & - & - \\
     \midrule
@@
 of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew.
+tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
+since \radamsa performs simpler syntactic source code modifications,
+it also produces a higher number of valid inputs (when compared with,
+for instance, AFL).
 

### 2020-06-12 paper/paper.tex
edits section 2 and 3
pass on findings and lessons

@@
 engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. Table~\ref{tab:engines} lists the engines we
+public issue trackers. We initially selected four JS engines:
+\jsc, \veight, \chakra, and \smonkey. Additionally, we also included
+\hermes in the list of studied engines. The main reason for this was
+to investigate how our approach would work on a recently introduced JS
+engined. More about \hermes on Section~\ref{sec:hermes}.
+Table~\ref{tab:engines} lists the engines we
 analyzed. It is worth noting that we used Google Chrome Lab's JSVU
@@
 \section{Case Study: \hermes}
-\label{sec:bugs}
+\label{sec:hermes}
 
@@
 
-\subsection{Key Findings and Lessons}
+\subsection{Key Findings}
+\label{sec:findings}
+
+The main findings of this study are as follows.
+
+\begin{enumerate}
+  \item Both techniques we studied have shown to be practical and
+    effective to find bugs on real, complex, and widely used software
+    systems;
+  \item Even for language APIs with fairly clear specs, as it is the
+    case of JavaScript, there is likely (a lot of) variation between
+    different implementations, which brings intrinsic challenges to
+    developers that work on them;
+  \item Even simple black-box fuzzers can create surprisingly
+    interesting inputs;
+
+\end{enumerate}
+
+%% 3)~Not only multiple different
+%% implementations can be leveraged in differential testing, but
+%% differences in test suites can also be important.
+
+The main findings of this study are as follows: 1) The techniques we
+selected found, with relatively low effort, several bugs even in very
+robust engines, such as Mozilla's \smonkey, 2)~Even for software
+projects with fairly clear specifications, as the case of
+\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
+implementation-specific behaviors whose implementation can
+inadvertedly lead to interference in the well-specified parts of the
+spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
+differential testing is feasible on real, complex, widely used pieces
+of software. Even black-box mutational fuzzers revealed bugs. We do
+expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
+black-box grammar-based generational fuzzers) could reveal even more
+bugs
+
+\subsection{Key Lessons}
 \label{sec:lessons}
 
-The main findings of this study are as follows.
-
-\begin{itemize}
-  \item Both techniques we investigated were successful in revealing
-    bugs (several of them);
-  %% \item We have found more bugs with test transplantation than we have
-  %%   with cross-engine differential testing. In addition, test
-  %%   transplantation demanded less effort per bug;
-  \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs. We conjecture that there is room to find more
-    bugs using other fuzzers;
-  \item Mozilla's \smonkey\ appears to be the most reliable
-    \js\ engine we analyzed, with Google's \veight\ after it.
-\end{itemize}
-
-The main lessons we learned from this study are as follows: 1)~Even
-for software projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
-variation between different implementations and, therefore,
-opportunities for bugs. 2)~Not only multiple different implementations
-can be leveraged in differential testing, but differences in test
-suites can also be important. 3)~Finding functional/non-crash bugs
-with differential testing is feasible on real, complex, widely used
-pieces of software. 4)~Further reducing cost of inspection is an
-important problem. Although the inspection activity was not
-uninterrupted, it is safe to say that each warning required a
-substantial amount of time to analyze for potential false alarms. In
-fact, many \hi\ warnings reported with differential testing were not
-analyzed. In determining cost, we observed, from experience, that the
-complexity of the \js\ specifications that the original test covers
-increases cost of diagnosing (as developers need to read and
-understand those) and the availability of alternative implementations
-(for the cases warnings are revealed through differential testing)
-reduces the cost of diagnosis. We prefer to see such problem as an
-opportunity for future research. For example, applying learning
-techniques to prioritize the warnings more likely to be faulty (in the
-spirit of the work of Chen and
+The key lessons of this study are as follows:
+
+\begin{enumerate}
+\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
+  should be encouraged;
+\item The cost of inspection of the warnings in differential testing
+  should be reduced;
+\item Finding bugs in large software is a very effective way to engage
+  student in contributing to open-source software and learning
+  Software Testing practices.
+\end{enumerate}
+
+1)~When taking into consideration our bug finding campaign, Mozilla's
+\smonkey\ and Google's \veight\ stood out as the most reliable
+engines. Therefore, we recommend the use of these engine for running
+\js\ applications. 2)~Further reducing cost of inspection in
+differential testing is an important problem. Although the inspection
+activity was not uninterrupted, it is safe to say that each warning
+required a substantial amount of time to analyze for potential false
+alarms. In fact, many \hi\ warnings reported with differential testing
+were not analyzed. We observed empirically that the cost of analysis
+was proportional to (i) the \js\ specification covered by the original
+test (as developers need to read and understand those parts) and (ii)
+the availability of alternative implementations. We prefer to see such
+problem as an opportunity for future research. For example, applying
+learning techniques to prioritize the warnings more likely to be
+faulty (in the spirit of the work of Chen and
 colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
 avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small.  5)~We learned that reporting
+techniques we studied is rather small. 3)~We learned that reporting
 real bugs is a great way to train (and encourage) students in software
@@
 % LocalWords:  PRONEX
+<

### 2020-06-12 paper/paper.tex
pass on example tests

@@
 \vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \chakra.
+code snippet below shows a test that reveals a bug in \textbf{\chakra}.
 
@@
 snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
-revealed a bug in \veight{} version 7.0.244. This code snippet was
+revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
 obtained by fuzzing a Test262 test with \quickfuzz. In its original
@@
 
-\Mar{--------------- estou aqui}
-
 \vspace{1ex}\noindent\textbf{Issue \#19,
   Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
-shows the test input we used to reveal a bug in \jsc.
+shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.
 
@@
 \vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
-reported the code snippet below to the \chakra\ development team as a
+reported the code snippet below to the \textbf{\chakra} development team as a
 bug, but they did \emph{not} accept.
@@
 \vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
-reported the code snippet below to the \smonkey\ development team as a
-bug, the bug was confirmed in a few hours.
-
-\begin{figure}[h!]
-  \vspace{-0.5ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function,
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
-    "use strict"
-    010
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}
-\end{figure}
-
-This is a test case original from the \hermes suite using test transplantation.
-According the specification, in strict mode, the engine must use
-the prefix '0o' or '0O' to represents octal numeric literals. It was an
-issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
-The others engine throws a SyntaxError due the missing of the octal token, but
-\smonkey returns a integer 8 that represents 010 in octal literal.
+reported the snippet \CodeIn{"use strict" 010} to the
+\textbf{\smonkey} development team as a bug and the bug was confirmed
+in a few hours.  This is a test case original from the \hermes suite
+using test transplantation.  According the specification, in strict
+mode, the engine must use the prefix '0o' or '0O' to represents octal
+numeric literals. It was an issue which explores a deprecated octal
+token after ASI (Automatic Semicolon Insertion).  The others engine
+throws a SyntaxError due the missing of the octal token, but \smonkey
+returns a integer 8 that represents 010 in octal.
+
+%% \begin{figure}[h!]
+%%   \vspace{-0.5ex}
+%%   \centering
+%%   \scriptsize
+%%   \lstset{escapeinside={@}{@},
+%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%%     numberstyle=\tiny,
+%%     morekeywords={assertEq, var, yield, in, function,
+%%     typeof, return, throw, new, Error, if},
+%%   }
+%%   \begin{lstlisting}
+%%     "use strict"
+%%     010
+%%   \end{lstlisting}
+%%   \normalsize
+%%   %% \caption{Warning captured as \hi{} priority.}
+%%   %% \label{fig:hi-priority}
+%%   \vspace{-1ex}
+%% \end{figure}
 

### 2020-06-12 paper/paper.tex
adding hermes bug in discussion

--- 2020-06-12 paper/paper.tex
@@
 
-%\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
-%  (more coherent/compelling) as to justify the selection of these two
-%  techniques?}
-%\Breno{Changed the paragraph a bit to include the reuse argument.}
+\Mar{@Gustavo,@Breno, can you please make this par a bit stronger
+  (more coherent/compelling) as to justify the selection of these two
+  techniques?}
+\Breno{Changed the paragraph a bit to include the reuse argument.}
 We selected these two techniques because they can take advantage
@@
 \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were
-fixed.  2)~An infrastructure for performing test transplantation and
-differential testing. The soruce code produced and the generated data sets of tests
+fixed.  2)~An infrastructure called \entente for performing test transplantation and
+differential testing.  Both \entente code and the data sets of tests
 and bugs are publicly available online at the following link:
@@
     the tests used in cross-engine differential
-    testing.}
+    testing.\Gustavo{Terminar essa tabela}}
   \setlength{\tabcolsep}{2pt}
@@
     %\chakra & \cite{chakra2018repo}\\
-    %\hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
+    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
     \midrule
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    %\midrule
-    %GitHub Projects & - & 494,394 & - & - & - \\
+    \midrule
+    GitHub Projects & - & 494,394 & - & - & - \\
     \midrule
@@
 of the \js\ syntax; it is able to replace sub-trees of the syntax
-tree~\cite{grieco2016quickfuzz} with trees created anew. Notwithstanding,
-since \radamsa performs simpler syntactic source code modifications,
-it also produces a higher number of valid inputs (when compared with,
-for instance, AFL).
+tree~\cite{grieco2016quickfuzz} with trees created anew.
 
@@
 
-\Mar{--------------- estou aqui}
-
 \vspace{1ex}\noindent\textbf{Issue \#19,
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
+\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
 reported the code snippet below to the \smonkey\ development team as a
@@
   \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
   \vspace{-1ex}
@@
 \smonkey returns a integer 8 that represents 010 in octal literal.
+
+\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
+above represents a bug confirmed in \hermes\ engine with 
+differential testing using radamsa on a repository mined from GitHub.
+
+\begin{figure}[h!]
+  \vspace{-0.5ex}
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+    b+/v/a
+  \end{lstlisting}
+  \normalsize
+  \vspace{-1ex}
+\end{figure}
+
+The original test case contains a string concatenation. 
+This is a case of validation of RegExp flags because the fuzzer mutated
+the file with a regular expression "/v/" between the variables.
+The plus operator in this case is set as a flag of the RegExp "+/v/",
+but in this case the plus operator is not valid as a flag. The behavior expected
+is throws an early SyntaxError due to a invalid regular expression flag,
+but \hermes seems not threat the early validation of the regexp flags as 
+commented by a team developer.
 

### 2020-06-12 paper/paper.tex

--- 2020-06-12 paper/paper.tex
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
+\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
 reported the snippet \CodeIn{"use strict" 010} to the
@@
 %% \end{figure}
+
+\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
+above represents a bug confirmed in \hermes\ engine with 
+differential testing using radamsa on a repository mined from GitHub.
+
+\begin{figure}[h!]
+  \vspace{-0.5ex}
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+    b+/v/a
+  \end{lstlisting}
+  \normalsize
+  \vspace{-1ex}
+\end{figure}
+
+The original test case contains a string concatenation. 
+This is a case of validation of RegExp flags because the fuzzer mutated
+the file with a regular expression "/v/" between the variables.
+The plus operator in this case is set as a flag of the RegExp "+/v/",
+but in this case the plus operator is not valid as a flag. The behavior expected
+is throws an early SyntaxError due to a invalid regular expression flag,
+but \hermes seems not threat the early validation of the regexp flags as 
+commented by a team developer.
 

### 2020-06-12 paper/paper.tex
adding hermes bug in discussion

--- 2020-06-12 paper/paper.tex
@@
 %% \end{figure}
+
+\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
+\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
+differential testing using radamsa on a repository mined from GitHub.
+The original test case contains a string concatenation. 
+This is a case of validation of RegExp flags. The fuzzer mutate
+the file with a regular expression "/v/" between the plus operator and
+the variable. The plus operator in this case is used as a flag of the RegExp "+/v/",
+but in this case the plus operator is not valid. The behavior expected
+is throws an early SyntaxError due to a invalid regular expression flag,
+but \hermes Hermes seems not treats the early validation of the regexp flags
+as commented by a maintainer.
 

### 2020-06-12 paper/paper.tex
improving explanation of bug#24

@@
 The original test case contains a string concatenation. 
-This is a case of validation of RegExp flags. The fuzzer mutate
-the file with a regular expression "/v/" between the plus operator and
-the variable. The plus operator in this case is used as a flag of the RegExp "+/v/",
-but in this case the plus operator is not valid. The behavior expected
-is throws an early SyntaxError due to a invalid regular expression flag,
-but \hermes Hermes seems not treats the early validation of the regexp flags
+This is a case of validation of RegExp flags. The fuzzer mutates
+the file with a regular expression \CodeIn{/v/} after the plus operator.
+In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
+but this flag is not valid. The behavior expected is throws an early
+SyntaxError due to a invalid regular expression flag,
+but \hermes\ seems not treats the early validation of the regexp flags
 as commented by a maintainer.

### 2020-06-12 paper/paper.tex
overall edits

@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
+    \midrule
+    %GitHub Projects & - & 494,394 & - & - & - \\
     %\midrule
-    %GitHub Projects & - & 494,394 & - & - & - \\
-    \midrule
      &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
@@
 or use functions that, albeit part of the spec, not all engines
-currently support. \Fix{Similarly, the \chakra project does not use
+currently support. Similarly, the \chakra project does not use
   the default well-known assertions available in JS, which the other
@@
   WScript would require a non-trivial manual effort. This is why
-  \chakra does not appear in Table~\ref{tab:test-suites}.}\Mar{did not
-  review part in red}
+  \chakra does not appear in Table~\ref{tab:test-suites}.
 
@@
 support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, we did not
-consider tests from the \chakra{} repository because they depend on
+required a Node.js runtime~\cite{node} for execution. Also, as aforementioned,
+we did not consider tests from the \chakra{} repository because they depend on
 non-portable objects.
@@
 make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines. More precisely, we needed to mock
+tests uniformly across all engines.
+
+More precisely, we needed to mock
 non-portable harness functions, which are only available in certain
-engines.
+engines. Since we had to transplant more than 40k test files,
+we tried to mock the minimum amount of code possible to
+make the test file work in the other engine.
+For instance, if a test had a statement such as \texttt{print(1==1);}
+we manually refactored that statement to \texttt{assertEquals(1,1)}.
+If the change would require more substantial manual work, we opted to
+discard the test instead. Overall we may have manually refactored more
+than a thousand test files.
 
@@
 
+To enrich our dataset of test files, we mined additional tests available on
+JavaScript GitHub projects as well as in the issue trackers of the studied
+JS engines. We explain this process next.
+
 \subsubsection{From GitHub projects}
 
-\Fix{We mined JS programs from the GitHub repository. In this case, we searched
+We mined JS programs from the GitHub repository. In this case, we searched
 for projects written in JavaScript, that were tagged with ``javascript-engine",
 and that have both ``Javascript" and ``engine" the name or the description of
-the project. After this process, we ended up with 2200 JS programs, which we
+the project. After this process, we ended up with 2,200 JS programs, which we
 downloaded locally. However, after careful investigation, we noted that 160 of
 these projects do not have any JS file, which were excluded from our study.
-We used the 2040 remaining ones as input to our testing approaches.}
+From these 2,040 projects, we could select 494,394 test files,
+which we as input to our testing approaches.
 
@@
 
-\Fix{Figure~\ref{fig:lo-truepositive} shows a test was originally
+Figure~\ref{fig:lo-truepositive} shows a test was originally
 available in the \jsc code base.  The \radamsa fuzzing technique
@@
 \texttt{view.getInt8()} method. Before the mutation, the
-\texttt{view.getInt8()} method received a zero integer.}
+\texttt{view.getInt8()} method received a zero integer.
 At the bottom of this figure, there is a sequence of
-three elements that we use to characterize a warning--1) the
+three elements that we use to characterize a warning: 1) the
 identifier of an engine, 2) the exception it raises, and 3) the
@@
 We used two black-box mutational fuzzers in this
-study--\radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
+study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
 fuzzers require no instrumentation and domain-knowledge. They mutate
@@
 development.
-\Fix{For this experiment, we ran the suite once a day for seven consecutive
+For this experiment, we ran the suite once a day for seven consecutive
 days and averaged the passing ratios.
@@
 were rapidly fixed by the maintenance team. If these errors were quickly
-fixed, that would suggest that this given engine would be aligned with
-the ECMAScript specification.}
+fixed, this would suggest that this given engine would be closely aligned with
+the ECMAScript specification.
 Table~\ref{tab:test262} shows
@@
 results was negligible; for that reason, we omitted standard
-deviations. We noticed that all four engines but \chakra{} used some
-variant of the Test262 suite as part of their regression process, but
-we used the same version in this
+deviations. We noticed that all engines but \chakra used some
+variant of the Test262 suite as part of their regression process.
+We used the same version in this
 experiment~\cite{ecma262-conformance-suite}.
@@
 percentages in the table. The number of passing tests is high and
-similar for \jsc, \veight{}, and \smonkey\ whereas \hermes performs
-worse when compared to the other engines.
-\Fix{This happens because \hermes
-still has many unsupported features, such as Proxy, Promisse, and Async.}
-Moreover, one can also note that \chakra\ also a low passing ratio
-in this test suite and the one we were able to find more bugs (as per
+similar for \jsc, \veight, and \smonkey
+%, whereas \chakra performs
+%worse when compared to the other engines.
+%\Fix{This happens because \hermes
+%still has many unsupported features, such as Proxy, Promisse, and Async.}
+Moreover, one can also note that \chakra has a low passing ratio
+in this test suite. Intestingly, it is also the one we were able to find more bugs (as per
 Figure~\ref{fig:summary}). Although it is plausible to find
@@
 \vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \textbf{\chakra}.
+code snippet below shows a test that reveals a bug in \chakra.
 
@@
 snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
-revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
+revealed a bug in \veight{} version 7.0.244. This code snippet was
 obtained by fuzzing a Test262 test with \quickfuzz. In its original
@@
 
+\Mar{--------------- estou aqui}
+
 \vspace{1ex}\noindent\textbf{Issue \#19,
   Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
-shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.
+shows the test input we used to reveal a bug in \jsc.
 
@@
 \vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
-reported the code snippet below to the \textbf{\chakra} development team as a
+reported the code snippet below to the \chakra\ development team as a
 bug, but they did \emph{not} accept.
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
-reported the snippet \CodeIn{"use strict" 010} to the
-\textbf{\smonkey} development team as a bug and the bug was confirmed
-in a few hours.  This is a test case original from the \hermes suite
-using test transplantation.  According the specification, in strict
-mode, the engine must use the prefix '0o' or '0O' to represents octal
-numeric literals. It was an issue which explores a deprecated octal
-token after ASI (Automatic Semicolon Insertion).  The others engine
-throws a SyntaxError due the missing of the octal token, but \smonkey
-returns a integer 8 that represents 010 in octal.
-
-%% \begin{figure}[h!]
-%%   \vspace{-0.5ex}
-%%   \centering
-%%   \scriptsize
-%%   \lstset{escapeinside={@}{@},
-%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%%     numberstyle=\tiny,
-%%     morekeywords={assertEq, var, yield, in, function,
-%%     typeof, return, throw, new, Error, if},
-%%   }
-%%   \begin{lstlisting}
-%%     "use strict"
-%%     010
-%%   \end{lstlisting}
-%%   \normalsize
-%%   %% \caption{Warning captured as \hi{} priority.}
-%%   %% \label{fig:hi-priority}
-%%   \vspace{-1ex}
-%% \end{figure}
-
-\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet 
-\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with 
-differential testing using radamsa on a repository mined from GitHub.
-The original test case contains a string concatenation. 
-This is a case of validation of RegExp flags. The fuzzer mutates
-the file with a regular expression \CodeIn{/v/} after the plus operator.
-In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
-but this flag is not valid. The behavior expected is throws an early
-SyntaxError due to a invalid regular expression flag,
-but \hermes\ seems not treats the early validation of the regexp flags
-as commented by a maintainer.
+\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
+reported the code snippet below to the \smonkey\ development team as a
+bug, the bug was confirmed in a few hours.
+
+\begin{figure}[h!]
+  \vspace{-0.5ex}
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+    "use strict"
+    010
+  \end{lstlisting}
+  \normalsize
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
+  \vspace{-1ex}
+\end{figure}
+
+This is a test case original from the \hermes suite using test transplantation.
+According the specification, in strict mode, the engine must use
+the prefix '0o' or '0O' to represents octal numeric literals. It was an
+issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
+The others engine throws a SyntaxError due the missing of the octal token, but
+\smonkey returns a integer 8 that represents 010 in octal literal.
 
@@
 
-\subsection{Key Findings}
-\label{sec:findings}
+\subsection{Key Findings and Lessons}
+\label{sec:lessons}
 
@@
 
-\begin{enumerate}
-  \item Both techniques we studied have shown to be practical and
-    effective to find bugs on real, complex, and widely used software
-    systems;
-  \item Even for language APIs with fairly clear specs, as it is the
-    case of JavaScript, there is likely (a lot of) variation between
-    different implementations, which brings intrinsic challenges to
-    developers that work on them;
+\begin{itemize}
+  \item Both techniques we investigated were successful in revealing
+    bugs (several of them);
+  %% \item We have found more bugs with test transplantation than we have
+  %%   with cross-engine differential testing. In addition, test
+  %%   transplantation demanded less effort per bug;
   \item Even simple black-box fuzzers can create surprisingly
-    interesting inputs;
-
-\end{enumerate}
-
-%% 3)~Not only multiple different
-%% implementations can be leveraged in differential testing, but
-%% differences in test suites can also be important.
-
-The main findings of this study are as follows: 1) The techniques we
-selected found, with relatively low effort, several bugs even in very
-robust engines, such as Mozilla's \smonkey, 2)~Even for software
-projects with fairly clear specifications, as the case of
-\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
-implementation-specific behaviors whose implementation can
-inadvertedly lead to interference in the well-specified parts of the
-spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
-differential testing is feasible on real, complex, widely used pieces
-of software. Even black-box mutational fuzzers revealed bugs. We do
-expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
-black-box grammar-based generational fuzzers) could reveal even more
-bugs
-
-\subsection{Key Lessons}
-\label{sec:lessons}
-
-The key lessons of this study are as follows:
-
-\begin{enumerate}
-\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
-  should be encouraged;
-\item The cost of inspection of the warnings in differential testing
-  should be reduced;
-\item Finding bugs in large software is a very effective way to engage
-  student in contributing to open-source software and learning
-  Software Testing practices.
-\end{enumerate}
-
-1)~When taking into consideration our bug finding campaign, Mozilla's
-\smonkey\ and Google's \veight\ stood out as the most reliable
-engines. Therefore, we recommend the use of these engine for running
-\js\ applications. 2)~Further reducing cost of inspection in
-differential testing is an important problem. Although the inspection
-activity was not uninterrupted, it is safe to say that each warning
-required a substantial amount of time to analyze for potential false
-alarms. In fact, many \hi\ warnings reported with differential testing
-were not analyzed. We observed empirically that the cost of analysis
-was proportional to (i) the \js\ specification covered by the original
-test (as developers need to read and understand those parts) and (ii)
-the availability of alternative implementations. We prefer to see such
-problem as an opportunity for future research. For example, applying
-learning techniques to prioritize the warnings more likely to be
-faulty (in the spirit of the work of Chen and
+    interesting inputs. We conjecture that there is room to find more
+    bugs using other fuzzers;
+  \item Mozilla's \smonkey\ appears to be the most reliable
+    \js\ engine we analyzed, with Google's \veight\ after it.
+\end{itemize}
+
+The main lessons we learned from this study are as follows: 1)~Even
+for software projects with fairly clear specifications, as the case of
+\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
+variation between different implementations and, therefore,
+opportunities for bugs. 2)~Not only multiple different implementations
+can be leveraged in differential testing, but differences in test
+suites can also be important. 3)~Finding functional/non-crash bugs
+with differential testing is feasible on real, complex, widely used
+pieces of software. 4)~Further reducing cost of inspection is an
+important problem. Although the inspection activity was not
+uninterrupted, it is safe to say that each warning required a
+substantial amount of time to analyze for potential false alarms. In
+fact, many \hi\ warnings reported with differential testing were not
+analyzed. In determining cost, we observed, from experience, that the
+complexity of the \js\ specifications that the original test covers
+increases cost of diagnosing (as developers need to read and
+understand those) and the availability of alternative implementations
+(for the cases warnings are revealed through differential testing)
+reduces the cost of diagnosis. We prefer to see such problem as an
+opportunity for future research. For example, applying learning
+techniques to prioritize the warnings more likely to be faulty (in the
+spirit of the work of Chen and
 colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
 avenue to explore. Recall that the rate of true positives of the
-techniques we studied is rather small. 3)~We learned that reporting
+techniques we studied is rather small.  5)~We learned that reporting
 real bugs is a great way to train (and encourage) students in software
@@
 % LocalWords:  PRONEX
-<

### 2020-06-12 paper/paper.tex
another pass

@@
 from the suites of other public engines (\ie{}, Duktape, JerryScript,
-JSI, and Tiny-js), 4) test files mined from issue trackers of these
-engines, and 5) test files from other GitHub projects.
+JSI, Tiny-js, Babel, and BlogEngine.NET),
+and 4) test files mined from issue trackers of these
+engines.
 
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
+    Babel &&&&& \\
+    BlogEngine.NET &&&&& \\
     \midrule
@@
 attempts to access an undefined variable (respectively, property of an
-object). We discarded those tests to avoid noise in the experiments as
+object).
+
+We discarded those tests to avoid noise in the experiments as
 they clearly indicate some missing feature as opposed to bugs. For
@@
   \chakra does not appear in Table~\ref{tab:test-suites}.
+  Moreover, we also did not include \hermes in the table because,
+  as the reader shall see in Table~\ref{tab:test262}, \hermes presents
+  a very low adherence to the Test262 conformance stuite. If we decided
+  to keep \hermes, considering only the number of passing tests
+  (the ``no-fail-in-all'' column), it would significantly reduce our
+  amount of test files.
 
@@
 
-\subsection{Mining Tests}
-
-To enrich our dataset of test files, we mined additional tests available on
-JavaScript GitHub projects as well as in the issue trackers of the studied
-JS engines. We explain this process next.
-
-\subsubsection{From GitHub projects}
-
-We mined JS programs from the GitHub repository. In this case, we searched
-for projects written in JavaScript, that were tagged with ``javascript-engine",
-and that have both ``Javascript" and ``engine" the name or the description of
-the project. After this process, we ended up with 2,200 JS programs, which we
-downloaded locally. However, after careful investigation, we noted that 160 of
-these projects do not have any JS file, which were excluded from our study.
-From these 2,040 projects, we could select 494,394 test files,
-which we as input to our testing approaches.
-
-\subsubsection{From Issue Trackers}
+\subsection{Mining Tests From Issue Trackers}
+
+%o enrich our dataset of test files, we mined additional tests available on
+%JavaScript GitHub projects as well as in the issue trackers of the studied
+%JS engines. We explain this process next.
+
+%\subsubsection{From GitHub projects}
+
+%We mined JS programs from the GitHub repository. In this case, we searched
+%for projects written in JavaScript, that were tagged with ``javascript-engine",
+%and that have both ``Javascript" and ``engine" the name or the description of
+%the project. After this process, we ended up with 2,200 JS programs, which we
+%downloaded locally. However, after careful investigation, we noted that 160 of
+%these projects do not have any JS file, which were excluded from our study.
+%From these 2,040 projects, we could select 494,394 test files,
+%which we as input to our testing approaches.
+
+%\subsubsection{From Issue Trackers}
 
@@
 
-\begin{table}[t]
+\begin{table}[b]
   \small
@@
   \renewcommand*{\arraystretch}{0.9}
-  \begin{tabular}{crrrrr}
+  \begin{tabular}{crrrr}
     \toprule
-    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} & \hermes{} \\
+    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{} \\
     \midrule
@@
     }
-    \jsc & - & 10 & 10 & 59 & 340  \\
-    \veight{} & 41 & - & 3 & 5 & 315 \\
+    \jsc & - & 10 & 10 & 59 \\
+    \veight{} & 41 & - & 3 & 5 \\
 %    \chakra{} & - & - & - & -  \\
-    \smonkey{} & 218 & 107 & - & 281 & - \\
-    Hermes & 8 & 14 & 8 & 26 & -  \\
-    Duktape & 0 & 4 & 4 & 1 & 140  \\
-    \jerry{} & 23 & 25 & 22 & 23 & 311  \\
-    JSI & 0 & 0 & 0 & 0 & 40\\
-   Tiny-js & 0 & 0 & 0 & 0 & 10  \\
+    \smonkey{} & 218 & 107 & - & 281 \\
+    %Hermes & 8 & 14 & 8 & 26 & -  \\
+    Duktape & 0 & 4 & 4 & 1 \\
+    \jerry{} & 23 & 25 & 22 & 23 \\
+    JSI & 0 & 0 & 0 & 0 \\
+   Tiny-js & 0 & 0 & 0 & 0 \\
     \midrule
-   \textbf{total} & 290 & 160 & 47 & 395 & 1156 \\
+   \textbf{total} & 282 & 146 & 39 & 369  \\
     \bottomrule
@@
 }
-failures in those cases would either indicate regressions or flaky
+\Gustavo{Falar pq Hermes nao esta na tabela}
+Failures in those cases would either indicate regressions or flaky
 tests as opposed to unknown bugs for that engine. As explained in
@@
 \sloppy The sources of false positives found in this experiment are as
-follows: \textbf{Undefined Behavior.} False positives of this kind are
+follows:
+
+\begin{description}
+  \item[\textbf{Undefined Behavior.}] False positives of this kind are
   manifested when tests cover implementation-dependent behavior, as
@@
   implementation-dependent, making that test to pass only in
-\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
-    error.}.} False positives of this kind typically manifest when the
+  \chakra.
+  \item[\textbf{Timeout/OME\footnote{ome is for out of memory
+      error.}.}] False positives of this kind typically manifest when the
      engine that runs the test does not optimize the code as the original
@@
      recursion. The test fails in all engines but \jsc, which implements
-tail-call optimization. \textbf{Not implemented.} False positives of
+     tail-call optimization.
+
+  \item[\textbf{Not implemented.}] False positives of
 this kind manifest when a test fails because it covers a function that
@@
 experimental mode with the flag \CodeIn{-ES6Experimental}.
-\textbf{Non-Standard Element.} These cases manifest when a function or
+
+\item[\textbf{Non-Standard Element.}] These cases manifest when a function or
 an object property is undefined in the execution engine but we were
@@
   we found cases where the test (or its harness) fails in an assertion
-  because of an undefined property.}  \textbf{Other.} This category
+  because of an undefined property.}
+
+\item[\textbf{Other.}] This category
 includes other sources of false positives. For example, it includes
@@
 spec but is no longer valid for the current spec.
+
+\end{description}
 

### 2020-06-12 paper/paper.tex
First pass on Sections 7 and 8

@@
 \textbf{\smonkey} development team as a bug and the bug was confirmed
-in a few hours.  This is a test case original from the \hermes suite
+in a few hours.  This is a test case originally from the \hermes suite
 using test transplantation.  According the specification, in strict
-mode, the engine must use the prefix '0o' or '0O' to represents octal
-numeric literals. It was an issue which explores a deprecated octal
-token after ASI (Automatic Semicolon Insertion).  The others engine
-throws a SyntaxError due the missing of the octal token, but \smonkey
-returns a integer 8 that represents 010 in octal.
+mode, the engine must use the prefix '0o' or '0O' to represent octal
+numeric literals. This is an issue that explores a deprecated octal
+token after ASI (Automatic Semicolon Insertion). The other engines
+throw a SyntaxError due to the missing of the octal token, but \smonkey
+returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.
 
@@
 \vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
-\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with
+\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
 differential testing using radamsa on a repository mined from GitHub.
@@
 In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
-but this flag is not valid. The behavior expected is throws an early
-SyntaxError due to a invalid regular expression flag,
-but \hermes\ seems not treats the early validation of the regexp flags
+but this flag is not valid. The expected behavior is to throw an early
+SyntaxError due to the invalid regular expression flag,
+but \hermes\ seems not to treat the early validation of the regexp flags
 as commented by a maintainer.

### 2020-06-12 paper/paper.tex
Pass on Section 8

@@
 \item Finding bugs in large software is a very effective way to engage
-  student in contributing to open-source software and learning
+  students in contributing to open-source software and learning
   Software Testing practices.

### 2020-06-12 paper/paper.tex
Pass on Section 7
pass on discussion of bug in Hermes

@@
 in extremely robust and largely adopted engines and also in recently
-developed engines. \Mar{check $\rightarrow$}The issue diagnosis of
+developed engines. The issue diagnosis of
 developers seem to differ though. Issues reported to stable engines
@@
 \CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
-differential testing using radamsa on a repository mined from GitHub.
+differential testing using radamsa.
 The original test case contains a string concatenation.
-This is a case of validation of RegExp flags. The fuzzer mutates
+This is a case of validation of RegEx flags. The fuzzer mutates
 the file with a regular expression \CodeIn{/v/} after the plus operator.
-In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
+In this case, the plus operator turns into a flag of the RegEx \CodeIn{+/v/},
 but this flag is not valid. The expected behavior is to throw an early
@@
 but \hermes\ seems not to treat the early validation of the regexp flags
-as commented by a maintainer.
+as explained by one of their developers.
 

### 2020-06-13 paper/paper.tex
pass

@@
   discontinued~\cite{chakra-discontinued}.} and JavaScriptCore (\jsc).
-We reported \noBugsBugsReportedGoogle{} bugs in \veight{}
-(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes in
-\hermes (\noBugsBugsConfirmedHermes confirmed), and
-\noBugsBugsReportedSMonkey in \smonkey{} (\noBugsBugsConfirmedSMonkey confirmed).
-Furthermore, our results show that both techniques revealed several
-bugs, most of which confirmed by developers. Test transplantation
-revealed \noBugsTransplantation bugs (of which,
-\noBugsTransplantationConfirmed were confirmed and
+We also reported \noBugsBugsReportedGoogle{} bugs in \veight{}
+(\noBugsBugsConfirmedGoogle{} confirmed), \noBugsBugsReportedHermes
+bugs in \hermes (\noBugsBugsConfirmedHermes confirmed), and
+\noBugsBugsReportedSMonkey bugs in \smonkey{}
+(\noBugsBugsConfirmedSMonkey confirmed).  Our results show that both
+techniques revealed several bugs, most of which confirmed by
+developers. Test transplantation revealed \noBugsTransplantation bugs
+(of which, \noBugsTransplantationConfirmed were confirmed and
 \noBugsTransplantationFixed were fixed) whereas differential testing
@@
 indicate that both techniques were successful at finding bugs. The
-number of fixed bugs were similar, if we consider only those confirmed
-or fixed. Most bugs we found are of moderate severity.
+number of confirmed or fixed bugs are similar. Most bugs we found are
+of moderate severity.
 
@@
 
-\emph{Key Findings.}~We found that--1)~Differential testing and Test
-Transplantation are practical and effective techniques to find bugs on real,
-complex, and widely used software systems and 2)~Even for problems with
-fairly clear specifications, as in \javascript{}, there is likely (a
-lot of) variation between different implementations, which brings intrinsic
-challenges to developers that work on them.
-Section~\ref{sec:lessons} expands and elaborates key
-findings and lessons learned.
+\emph{Key Findings.}~To sum up, we found that 1)~Differential testing
+and Test Transplantation are practical and effective techniques to
+find bugs on real, complex, and widely used software systems and
+2)~Even for problems with fairly clear specifications, as in
+\javascript{}, there is likely (a lot of) variation between different
+implementations, which brings intrinsic challenges to developers that
+work on them.  Section~\ref{sec:lessons} expands and elaborates our
+key findings and lessons learned.
 
@@
 fixed.  2)~An infrastructure for performing test transplantation and
-differential testing. The soruce code produced and the generated data sets of tests
+differential testing. The source code produced and the generated data sets of tests
 and bugs are publicly available online at the following link:

### 2020-06-13 paper/paper.tex
pass on section 2 and 3

@@
 reasons. Certain parts of the specification are undefined; it is the
-responsibility of engineers to decide how to implement these
-functionalities. The JavaScript spec uses the label
+responsibility of the community to regulate the evolution of the
+language. The JavaScript spec uses the label
 ``implementation-dependent'' to indicate these cases, where behavior
-may differ from engine to engine. One reason for suchs flexibility in
+may differ from engine to engine. One reason for such flexibility in
 the spec is to enable compiler optimizations. For example, the
@@
 engines. As we wanted to report bugs, we also looked for project with
-public issue trackers. We initially selected four JS engines:
-\jsc, \veight, \chakra, and \smonkey. Additionally, we also included
-\hermes in the list of studied engines. The main reason for this was
-to investigate how our approach would work on a recently introduced JS
-engined. More about \hermes on Section~\ref{sec:hermes}.
-Table~\ref{tab:engines} lists the engines we
-analyzed. It is worth noting that we used Google Chrome Lab's JSVU
-tool~\cite{jsvu} to automatically install and configure versions of
-different JS engines in our host environment. This is important as we
-aim to use the most recent stable versions of each engine as to avoid
-reporting old and already-fixed bugs to developers.
+public issue trackers. We initially selected four JS engines: \jsc,
+\veight, \chakra, and \smonkey. Later, we included \hermes in the list
+of studied engines. The main reason was to investigate how our
+approach would work on a recently introduced JS engined. More about
+\hermes on Section~\ref{sec:hermes}.  Table~\ref{tab:engines} lists
+the engines we analyzed. It is worth noting that we used Google Chrome
+Lab's JSVU tool~\cite{jsvu} to automatically install and configure
+versions of different JS engines in our host environment. This is
+important as we aim to use the most recent stable versions of each
+engine as to avoid reporting old and already-fixed bugs to developers.
 

### 2020-06-13 paper/paper.tex
pass on 4.0 (needs work)

@@
 ``Name'' and ``Source'' show the origin of the test suite. Column
-``total'' shows the number of test cases associated with a givem
-source. Column ``pass-in-par.''  shows the number of test cases that
-pass in their parent engine. We discarded tests that fail in their
-parent engine as we could not reliably indicate the reason for the
-failure, so we assumed the test could be broken. We removed
+``total'' shows the number of test cases associated with a given
+source of \js\ files. Column ``pass-in-par.''  shows the number of
+test cases that pass in the corresponding engine. We discarded tests
+that fail in their engine as we could not reliably indicate the reason
+for the failure, so we assumed the test could be broken. We removed
 \testsThatFail{} test cases that fail for that
 reason--\testsThatFailJSC{} tests from \jsc and \testsThatFailSM{}
-tests from \smonkey. Column ``type-in-all'' shows the number of test
-cases whose executions do not throw dynamic type errors in any of the
-engines because of an undefined variable or property.  These cases
-were captured by looking for the presence of \CodeIn{ReferenceError}
-and \CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
-(respectively, \CodeIn{TypeError}) is raised when test execution
-attempts to access an undefined variable (respectively, property of an
-object).
-
-We discarded those tests to avoid noise in the experiments as
-they clearly indicate some missing feature as opposed to bugs. For
-example, some tests use non-portable names (\eg{}, \jsc's
-\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
-or use functions that, albeit part of the spec, not all engines
-currently support. Similarly, the \chakra project does not use
-  the default well-known assertions available in JS, which the other
-  JS engines use.  Instead, it uses its own testing framework,
-  WScript. In this case, we could not easily reproduce the \chakra
-  unit tests in the other engines since it would raise a
-  \texttt{ReferenceError}. Also, updating the other engines to use
-  WScript would require a non-trivial manual effort. This is why
-  \chakra does not appear in Table~\ref{tab:test-suites}.
-  Moreover, we also did not include \hermes in the table because,
-  as the reader shall see in Table~\ref{tab:test262}, \hermes presents
-  a very low adherence to the Test262 conformance stuite. If we decided
-  to keep \hermes, considering only the number of passing tests
-  (the ``no-fail-in-all'' column), it would significantly reduce our
-  amount of test files.
-
-\Mar{Numbers seem inconsistent. I will stop here...}
-For the evaluation of test transplantation, we used
-the \totalTestFilesForTestTransplantation{} tests included in the
-dashed rectangle under column ``type-in-all'', \ie{}, all tests under
-that column but the Test262 tests. We did not consider tests from the
+tests from \smonkey.
+
+Column ``type-in-all'' shows the number of test cases whose executions
+do not throw dynamic type errors in any of the engines because of an
+undefined variable or property.  These cases were captured by looking
+for the presence of \CodeIn{ReferenceError} and \CodeIn{TypeError} on
+the output. A \CodeIn{ReferenceError} (respectively,
+\CodeIn{TypeError}) is raised when test execution attempts to access
+an undefined variable (respectively, property of an object). We
+discarded those tests to avoid noise in the experiments as they
+indicate some missing feature in the implementation of the engine as
+opposed to bugs. For example, some tests use non-portable names
+(\eg{}, \jsc's \CodeIn{drainMicrotasks()} and \smonkey{}'s
+\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
+spec, not all engines currently support. Similarly, the \chakra
+project does not use common assertions available used in JS program,
+which other JS engines support. Instead, it uses its own testing
+framework, WScript. In such cases, we are unable to reproduce the
+\chakra unit tests in other engines---it raises a
+\CodeIn{ReferenceError}. Also, updating the other engines to use
+WScript would require a non-trivial manual effort. This is why \chakra
+does not appear in Table~\ref{tab:test-suites}. For the evaluation of
+test transplantation, we used the
+\totalTestFilesForTestTransplantation{} tests included in the dashed
+rectangle under column ``type-in-all'', \ie{}, all tests under that
+column but the Test262 tests. We did not consider tests from the
 conformance suite as they are more likely to indicate missing features
 as opposed to bugs. In addition, engine developers have access to
-these test and are encouraged to run them. Finally, column
-``no-fail-in-all'' shows the tests for which all engines pass. Note
-that the set of tests in this column is a subset of the
-``type-in-all'' test set. This test set is used in the evaluation of
-differential testing as fuzzing seeds. The guarantee that they pass in
-all engines assures that, if discrepancies occur, they are related to
-the changes in the input as opposed to the original cause of failure.
+these tests and are encouraged to run them.
+
+Column ``no-fail-in-all'' shows the tests for which all engines
+pass. The set of tests in this column is a subset of the
+``type-in-all'' test set. The tests in this set are as fuzzing seeds
+in the evaluation of differential testing. The guarantee that they
+pass in all engines assures that, if discrepancies occur, they are
+related to the changes in the input as opposed to the original cause
+of failure. It is worth noting that we also did not include the tests
+from \hermes\ in the table because, as the reader shall see in
+Table~\ref{tab:test262}, \hermes presents a very low adherence to the
+Test262 conformance suite. If we decided to keep \hermes, considering
+only the number of passing tests in all engines (the
+``no-fail-in-all'' column), it would significantly \Mar{Not sure if I
+  understood the conclusion. Do you mean the total amount of test
+  (also from other suites)? Why?}reduce our amount of test files.
 
@@
 
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
-depend on external libraries, which not all selected engines
-support. We decided to discard those. For example, many tests we found
-required a Node.js runtime~\cite{node} for execution. Also, as aforementioned,
-we did not consider tests from the \chakra{} repository because they depend on
-non-portable objects.
-Finally, note that the number of tests in
+\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
+tests we found depend on external libraries, which not all selected
+engines support. We decided to discard those. For example, many tests
+we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
+  the reason?  Please, confirm$\rightarrow$} require libraries to be
+installed before running the test and different tests require
+different sets of libraries. Also, as already mentioned, we did not
+consider tests from the \chakra{} repository because they depend on
+non-portable objects.  Finally, note that the number of tests in
 \veight\ is low; that happens because \veight{} uses many tests from
 Mozilla and \jsc; we discarded those to avoid repetition and to give
-credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
-worth mentioning that some engines use a custom shell to run tests,
-including a harness with specific assertions.  For that, we needed to
-make minor changes in the testing infrastructure to be able to run the
-tests uniformly across all engines.
-
-More precisely, we needed to mock
-non-portable harness functions, which are only available in certain
-engines. Since we had to transplant more than 40k test files,
-we tried to mock the minimum amount of code possible to
-make the test file work in the other engine.
-For instance, if a test had a statement such as \texttt{print(1==1);}
-we manually refactored that statement to \texttt{assertEquals(1,1)}.
-If the change would require more substantial manual work, we opted to
-discard the test instead. Overall we may have manually refactored more
-than a thousand test files.
+credit where it is due\Mar{@Gustavo/@Breno, we can mention in the
+  author response that we did sanity/diligence check.}.
+
+\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
+engines use a custom shell to run tests, including a harness with
+specific assertions\Mar{@Igor, can you name which?}. For that, we
+needed to make minor changes in the testing infrastructure to be able
+to run the tests uniformly across all engines. More precisely, we
+needed to mock non-portable functions, which are only available in
+certain engines. Since we had to transplant more than 40k test files,
+we tried to mock the minimum amount of code possible to make the test
+file work in the other engine.\Mar{This seems a different problem
+  (tests without assertions). I did not understand how this is related
+  to portability?}  For instance, if a test had a statement such as
+\texttt{print(1==1);} we manually refactored that statement to
+\texttt{assertEquals(1,1)}.  If the change would require more
+substantial manual work, we opted to discard the test instead. Overall
+we may have manually refactored more than a thousand test files.
 

### 2020-06-13 paper/paper.tex
pass on section 4

@@
 
+\lbrack{}Dedup\rbrack{}~\Fix{Explain what we did to avoid
+  dups. Consider moving to the the sentence ``Finally, note that the number of tests in V8''}
+
 \subsection{Mining Tests From Issue Trackers}
@@
 
-Teste cases embedded in issue trackers are an important source of data
-as they may have already shown usefulness to reveal problems in some
+Test cases embedded in issue trackers are an important source of data
+as they may have already shown useful to reveal problems in some
 engine. For example, a developer may have found a corner case that a
 given engine did not handle properly. Therefore, it is possible that
-other engine do not handle those cases. We thought that we should not
-ignore issue trackers for that reason. By manually analyzing a sample
-of issues, we observed that developers either 1) add test cases as
-attachments of an issue or 2) embed the test cases within the textual
-description of an issue. The test cases in attachments are longer
-compared to the test cases embedded in issue descriptions whereas the
-latter are more common. Consequently, we thought we should handle both
-cases.
+some other engine does not handle that case as well. For that reasons,
+we thought that we should not ignore issue trackers. By manually
+analyzing a sample of issues, we observed that developers either 1)
+add test cases as attachments of an issue or 2) embed the test cases
+within the textual description of an issue. The test cases in
+attachments are longer compared to the test cases embedded in issue
+descriptions whereas the latter are more common. Consequently, we
+thought we should handle both cases.
 
@@
 %% \Fix{add code to explain}
+
+\subsection{Characterization of Test Suites}
+
+\Fix{...add and discuss histograms}
 

### 2020-06-13 paper/paper.tex
pass on 5.0

@@
 data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the leftmost icon indicates that each file in the
-input list will be analyzed in separate whereas the rightmost icon
-shows that a single file will be fuzzed multiple times.
+indicate repetition--the cycle icon close to the cylinder icon
+indicates that each file in the input list will be analyzed in
+separate whereas the other cycle icon shows that a single file will be
+fuzzed multiple times.
 
@@
   \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
+  \caption{\label{fig:workflow}Differential Testing infrastructure
+    overview.\Fix{tem certeza que Hermes estah usando mesma fonte/tamanho?}}
 \end{figure}
 
-The bug-finding process works as follows. For a given test input, the
-toolchain produces new inputs using some off-the-shelf input fuzzer
-(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
-selected.)  Then, the oracle checks whether or not the output produced
-for the fuzzed file is consistent across all engines (step 2). In case
-the test passes in all engines or fails in all engines (\ie{}, the
-output is consistent), the infrastructure ignores the
+The bug-finding process works as follows. First, for a given test
+input, the toolchain produces new inputs using some off-the-shelf
+input fuzzer (step 1). Section~\ref{sec:objects:fuzzers} describes the
+fuzzers we selected. Then, the oracle checks whether or not the output
+produced for the fuzzed file is consistent across all engines (step
+2). In case the test passes in all engines or fails in all engines
+(\ie{}, the output is consistent), the infrastructure ignores the
 input. Otherwise, it considers the input as potentially
@@
 to precisely distinguish false and true positives. As such, a human
-needs to inspect the warning to classify the issue. As mentioned
+needs to inspect a warning to classify the issue. As mentioned
 earlier, this justifies why differential testing is challenging to
 automate at the functional level. Existing techniques that use
-differential testing control rate of false alarms differently. For
-example, Mozilla uses varies the configurations of thei
-\smonkey\ engine, but the implementation is the
-same~\cite{mozilla-severity}. The sources of non-determinism are
-therefore similar. CSmith~\cite{Yang:2011:FUB:1993498.1993532}
-addresses the problem by trying to avoid generating C files that
-produce undefined behavior. However, mapping all sources of
-undefinedness in JS is impractical.
+differential testing deal with false alarms differently. For example,
+Mozilla varies the configurations of their \smonkey\ engine, but the
+implementation is the same~\cite{mozilla-severity}. Non-determinism is
+therefore more likely to be associated with the variations across
+version as these version use the same core
+implementation. CSmith~\cite{Yang:2011:FUB:1993498.1993532} addresses
+the problem by trying to avoid generating C files that produce
+undefined behavior. Mapping all sources of undefinedness in JS is
+impractical.
+
+%\Igor{If the criteria is to find crashes or fatal errors, it is
+%possible to run the infrastructure with any runner(?) tool, including
+%the javascript binaries itself.}
 
@@
 output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes, \Igor{If the criteria is to
-find crashes or fatal errors, it is possible to run the
-infrastructure with any runner(?) tool, including the
-javascript binaries itself.}. As such, we forked the
+handle discrepancies involving crashes. As such, we forked the
 eshost-cli GitHub project and implemented that functionality on it. It
-is also important to note that our checker does not support the case
-where the test fails in all engines but the kind of failure (\eg{},
-exception thrown) is different. Currently, our infrastructure does not
-report discrepancy for that case. For that, it would be necessary to
-properly parse the error message to retrieve the error types. We left
-that as future work as we already found several discrepancies even
-without that.
+is important to note that our checker does not support the case where
+the test fails in all engines with a different kind of failure as it
+is unclear how to properly relate those failures. Currently, our
+infrastructure does not report discrepancy on that case. We left that
+as future work as we already found several discrepancies even without
+that.
+
+%% For that, it would be
+%% necessary to properly parse the error message to retrieve the error
+%% types.
 

### 2020-06-13 paper/paper.tex
Addressed a comment from Marcelo

@@
 Mozilla and \jsc; we discarded those to avoid repetition and to give
-credit where it is due\Mar{@Gustavo/@Breno, we can mention in the
-  author response that we did sanity/diligence check.}.
+credit where it is due.
 

### 2020-06-13 paper/paper.tex
section 5.1

@@
 
-We prioritized warnings based on their types, reflecting likelihood of
-manifesting a real bug. We defined two types---``\hi{}'' and
-``\lo{}''.
-
-Warnings of the kind ``\hi{}'' are associated with the cases where the
-test code executes without violating any internal checks, but it
-violates an assertion declared in the test itself or its harness. The
-rationale is that the test data is more likely to be valid in this
-case as execution does not raise exceptions in application
-code. Warnings of kind ``lo'' cover the remaining cases. These
-warnings are more likely to be associated with invalid inputs. They
-reflect the cases where the anomaly is observed during the execution
-of application functions as opposed to assertions. We observed that
-different engines often check pre-conditions of functions
-differently. It can happen, for example, that one engine enforces a
-weaker pre-condition, compared to another engine, on the inputs of a
-function and that is acceptable.\Comment{ For instance, it is
-  acceptable to pass values greater than \Fix{x} to function
+We prioritized warnings based on their likelihood of manifesting a
+real bug. We defined two types of warnings based on empirical evidence
+weobtained while analyzing bugs. The types ``\hi{}'' and
+``\lo{}''. Warnings of the kind ``\hi{}'' are associated with the
+cases where the test code executes without violating any internal
+checks, but it violates an assertion declared in the test itself or
+its harness. The rationale is that the test data is more likely to be
+valid in this case as execution does not raise exceptions in
+application code. Warnings of kind ``lo'' cover the remaining
+cases. These warnings are more likely to be associated with invalid
+inputs. They reflect the cases where the anomaly is observed during
+the execution of application functions as opposed to assertions. We
+observed that different engines often check pre-conditions of
+functions differently. It can happen, for example, that one engine
+enforces a weaker pre-condition, compared to another engine, on the
+inputs of a function and that is acceptable.\Comment{ For instance, it
+  is acceptable to pass values greater than \Fix{x} to function
   \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}.} In those cases,
@@
 that pass in all engines.
+
+\begin{figure}[h!]
+  \centering
+  \begin{lstlisting}
+var buffer = new ArrayBuffer(64);
+var view = new DataView(buffer);
+view.setInt8(0,0x80);
+assert(view.getInt8(-1770523502845470856) === -0x80);
+
+Message from Engines (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
+1. RangeError: Offset is outside the bounds of the DataView
+2. RangeError: byteOffset cannot be negative
+3. RangeError: invalid or out-of-range index
+  \end{lstlisting}
+  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
+    that led to a confirmed bug report in \chakra. The bug is caused
+    by a required precondition check in the implementation of function
+    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
+\end{figure}
 
@@
 Messages'' at the bottom of Figure~\ref{fig:lo-truepositive}. This is
-a case of undocumented precondition. It was fixed by
-\chakra\ developers and is no longer present in the most recent
-release of \chakra.
+a case of undocumented precondition. It was fixed by developers and is
+no longer present in the most recent release of the engine.
 
@@
   bounds of the DataView'')].
-
-\begin{figure}[t!]
-  \centering
-  \begin{lstlisting}
-var buffer = new ArrayBuffer(64);
-var view = new DataView(buffer);
-view.setInt8(0,0x80);
-assert(view.getInt8(-1770523502845470856) === -0x80);
-
-Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
-1. RangeError: Offset is outside the bounds of the DataView
-2. RangeError: byteOffset cannot be negative
-3. RangeError: invalid or out-of-range index
-  \end{lstlisting}
-  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
-    that led to a confirmed bug report in \chakra. The bug is caused
-    by a required precondition check in the implementation of function
-    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
-\end{figure}
 

### 2020-06-13 paper/paper.tex
pass on comments

--- 2020-06-13 paper/paper.tex
@@
     Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
-    Babel &&&&& \\
-    BlogEngine.NET &&&&& \\
+    Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
+    BlogEngine.NET & \cite{babel2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
     \midrule
@@
 we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
-  the reason?  Please, confirm$\rightarrow$} require libraries to be
+  the reason?  Please, confirm$\rightarrow$}\Igor{yes, it is. Some Node internal features are 
+not included in the JS engine, including some keywords (ie. require, module).
+In addiction, a project with nodejs require a package.json with a lot of external dependencies.} require libraries to be
 installed before running the test and different tests require
@@
 \lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
-engines use a custom shell to run tests, including a harness with
-specific assertions\Mar{@Igor, can you name which?}. For that, we
+engines uses a custom shell to run tests, including a harness with
+specific assertions, \Igor{for example, tests provided by Mozilla contains a lot 
+of custom functions (\ie\ assertThrowsInstanceOf, assertEqArray, getPromiseResult).
+The shell contains those functions to made the test run correctly.}
+\Mar{@Igor, can you name which?}. For that, we
 needed to make minor changes in the testing infrastructure to be able
@@
   (tests without assertions). I did not understand how this is related
-  to portability?}  For instance, if a test had a statement such as
+  to portability?}\Igor{A test is a simple JS file input.
+  Some tests are not well-defined.}  For instance, if a test had a statement such as
 \texttt{print(1==1);} we manually refactored that statement to
-\texttt{assertEquals(1,1)}.  If the change would require more
-substantial manual work, we opted to discard the test instead. Overall
+\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
+If the change would require more substantial manual work, we opted to discard the test instead. Overall,
 we may have manually refactored more than a thousand test files.
-
-\lbrack{}Dedup\rbrack{}~\Fix{Explain what we did to avoid
-  dups. Consider moving to the the sentence ``Finally, note that the number of tests in V8''}
 
@@
 
-Test cases embedded in issue trackers are an important source of data
-as they may have already shown useful to reveal problems in some
+Teste cases embedded in issue trackers are an important source of data
+as they may have already shown usefulness to reveal problems in some
 engine. For example, a developer may have found a corner case that a
 given engine did not handle properly. Therefore, it is possible that
-some other engine does not handle that case as well. For that reasons,
-we thought that we should not ignore issue trackers. By manually
-analyzing a sample of issues, we observed that developers either 1)
-add test cases as attachments of an issue or 2) embed the test cases
-within the textual description of an issue. The test cases in
-attachments are longer compared to the test cases embedded in issue
-descriptions whereas the latter are more common. Consequently, we
-thought we should handle both cases.
+other engine do not handle those cases. We thought that we should not
+ignore issue trackers for that reason. By manually analyzing a sample
+of issues, we observed that developers either 1) add test cases as
+attachments of an issue or 2) embed the test cases within the textual
+description of an issue. The test cases in attachments are longer
+compared to the test cases embedded in issue descriptions whereas the
+latter are more common. Consequently, we thought we should handle both
+cases.
 
@@
 
-\subsection{Characterization of Test Suites}
-
-\Fix{...add and discuss histograms}
-
 \section{Cross-Engine Differential Testing}
@@
 data processors and arrowed lines denote data flows. The cycle icons
-indicate repetition--the cycle icon close to the cylinder icon
-indicates that each file in the input list will be analyzed in
-separate whereas the other cycle icon shows that a single file will be
-fuzzed multiple times.
+indicate repetition--the leftmost icon indicates that each file in the
+input list will be analyzed in separate whereas the rightmost icon
+shows that a single file will be fuzzed multiple times.
 
@@
   \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure
-    overview.\Fix{tem certeza que Hermes estah usando mesma fonte/tamanho?}}
+  \caption{\label{fig:workflow}Differential Testing infrastructure overview.}
 \end{figure}
 
-The bug-finding process works as follows. First, for a given test
-input, the toolchain produces new inputs using some off-the-shelf
-input fuzzer (step 1). Section~\ref{sec:objects:fuzzers} describes the
-fuzzers we selected. Then, the oracle checks whether or not the output
-produced for the fuzzed file is consistent across all engines (step
-2). In case the test passes in all engines or fails in all engines
-(\ie{}, the output is consistent), the infrastructure ignores the
+The bug-finding process works as follows. For a given test input, the
+toolchain produces new inputs using some off-the-shelf input fuzzer
+(step 1).  (Section~\ref{sec:objects:fuzzers} describes the fuzzers we
+selected.)  Then, the oracle checks whether or not the output produced
+for the fuzzed file is consistent across all engines (step 2). In case
+the test passes in all engines or fails in all engines (\ie{}, the
+output is consistent), the infrastructure ignores the
 input. Otherwise, it considers the input as potentially
@@
 to precisely distinguish false and true positives. As such, a human
-needs to inspect a warning to classify the issue. As mentioned
+needs to inspect the warning to classify the issue. As mentioned
 earlier, this justifies why differential testing is challenging to
 automate at the functional level. Existing techniques that use
-differential testing deal with false alarms differently. For example,
-Mozilla varies the configurations of their \smonkey\ engine, but the
-implementation is the same~\cite{mozilla-severity}. Non-determinism is
-therefore more likely to be associated with the variations across
-version as these version use the same core
-implementation. CSmith~\cite{Yang:2011:FUB:1993498.1993532} addresses
-the problem by trying to avoid generating C files that produce
-undefined behavior. Mapping all sources of undefinedness in JS is
-impractical.
-
-%\Igor{If the criteria is to find crashes or fatal errors, it is
-%possible to run the infrastructure with any runner(?) tool, including
-%the javascript binaries itself.}
+differential testing control rate of false alarms differently. For
+example, Mozilla uses varies the configurations of thei
+\smonkey\ engine, but the implementation is the
+same~\cite{mozilla-severity}. The sources of non-determinism are
+therefore similar. CSmith~\cite{Yang:2011:FUB:1993498.1993532}
+addresses the problem by trying to avoid generating C files that
+produce undefined behavior. However, mapping all sources of
+undefinedness in JS is impractical.
 
@@
 output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is important to note that our checker does not support the case where
-the test fails in all engines with a different kind of failure as it
-is unclear how to properly relate those failures. Currently, our
-infrastructure does not report discrepancy on that case. We left that
-as future work as we already found several discrepancies even without
-that.
-
-%% For that, it would be
-%% necessary to properly parse the error message to retrieve the error
-%% types.
+handle discrepancies involving crashes, \Igor{If the criteria is to
+find crashes or fatal errors, it is possible to run the
+infrastructure with any runner tool, including the
+javascript binaries itself, in this case the tool captures all output provided by the binaries}.
+It is also important to note that our checker does not support the case
+where the test fails in all engines but the kind of failure (\eg{},
+exception thrown) is different. Currently, our infrastructure does not
+report discrepancy for that case. For that, it would be necessary to
+properly parse the error message to retrieve the error types. We left
+that as future work as we already found several discrepancies even
+without that.
 
@@
 Android''~\cite{hermes2020repo}.\Mar{short sentence saying where it is
-  used.}
+  used.}\Igor{Currently, hermes is being used in the react-native framework,
+  also maintained by Facebook, as a beta component to increase the performance of Android applications,
+  such as startup time, reduce memory consumption and application size\cite{reactnative2020hermes}.
+}
 
@@
 \hermes. This happened because \smonkey has its own assertion
-framework, but \hermes was unable to interpret those assertions,
+framework, but \hermes was unable to interpret those assertions \Igor{due to 
+the missing features mentioned before (\ie\ Class definitions, Proxy properties)}
 resulting in failures in all test executions from this engine. These
 failures did not happen when the \smonkey tests were transplanted to
-the other engines, though\Mar{Why? Was the framework using some of the
-  features aforementioned? Say it, please.}. Overall, we repoted three
-issues to the \hermes bug tracker as result of using test
+the other engines, though.\Mar{Why? Was the framework using some of the
+  features aforementioned? Say it, please}\Igor{fixed above}.
+Overall, we reported three issues to the \hermes bug tracker as result of using test
 transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},

### 2020-06-13 paper/paper.tex

--- 2020-06-13 paper/paper.tex
@@
   (tests without assertions). I did not understand how this is related
-  to portability?}  For instance, if a test had a statement such as
+  to portability?}\Igor{A test is a simple JS file input.
+  Some tests are not well-defined.}  For instance, if a test had a statement such as
 \texttt{print(1==1);} we manually refactored that statement to
-\texttt{assertEquals(1,1)}.  If the change would require more
-substantial manual work, we opted to discard the test instead. Overall
+\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
+If the change would require more substantial manual work, we opted to discard the test instead. Overall,
 we may have manually refactored more than a thousand test files.
@@
 output discrepancy. However, we noticed that eshost-cli does not
-handle discrepancies involving crashes. As such, we forked the
-eshost-cli GitHub project and implemented that functionality on it. It
-is important to note that our checker does not support the case where
+handle discrepancies involving crashes. Our tool supports the execution of the
+binaries themselves to obtain these fatal errors.
+It is important to note that our checker does not support the case where
 the test fails in all engines with a different kind of failure as it

### 2020-06-13 paper/paper.tex

@@
 
-Clusterization is complementary to prioritization; it helps to group
+Clusterization is complementary to prioritization. It helps to group
 similar warnings reported by our infrastructure. We only clustered
@@
 the test case, which are typically distinct.
-
-Figure~\ref{fig:lo-truepositive} shows a test was originally
-available in the \jsc code base.  The \radamsa fuzzing technique
-mutated the test. In particular, it introduced the negative
-long \texttt{-1770523502845470856} as a parameter of the
-\texttt{view.getInt8()} method. Before the mutation, the
-\texttt{view.getInt8()} method received a zero integer.
-At the bottom of this figure, there is a sequence of
-three elements that we use to characterize a warning: 1) the
-identifier of an engine, 2) the exception it raises, and 3) the
-message it produces on a ``\lo'' warning.  This sequence of triples
-defines a warning signature that we use for clustering. It is worth
-mentioning that we filter references to code in messages as to
-increase ability to aggregate warnings. Any warnings, including this
-one, that has this same signature will be included in the same
-``bucket''. Considering the example from
-Figure~\ref{fig:lo-truepositive}, the signature for that cluster will
-be [(JavaScriptCore, ``RangeError'', ``byteOffset cannot be
-  negative''), (SpiderMonkey, ``RangeError'', ``invalid or
-  out-of-range index''), (V8, ``RangeError'', ``Offset is outside the
-  bounds of the DataView'')].
+Figure~\ref{fig:lo-truepositive} shows a test that was originally
+available in the \jsc suite. The \radamsa fuzzer mutated the test. It
+introduced the negative long \CodeIn{-1770523502845470856} as a
+parameter of the \CodeIn{view.getInt8()} method. Before the mutation,
+the \CodeIn{view.getInt8()} method received zero as parameter.  At the
+bottom of this figure, there is a sequence of three elements that we
+use to characterize a warning: 1) the identifier of an engine, 2) the
+exception it raises, and 3) the message it produces on a ``\lo''
+warning.  This sequence of triples defines a warning signature that we
+use for clustering. It is worth mentioning that we filter references
+to code in messages as to increase ability to aggregate warnings. Any
+warnings, including this one, that has this same signature will be
+included in the same ``bucket''. Considering this particular example,
+the signature for that cluster will be [(JavaScriptCore,
+  ``RangeError'', ``byteOffset cannot be negative''), (SpiderMonkey,
+  ``RangeError'', ``invalid or out-of-range index''), (V8,
+  ``RangeError'', ``Offset is outside the bounds of the DataView'')].
 

### 2020-06-13 paper/paper.tex
pass on technique

@@
     Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
-    BlogEngine.NET & \cite{babel2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
+    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
     \midrule
@@
 related to the changes in the input as opposed to the original cause
-of failure. It is worth noting that we also did not include the tests
+of failure. 
+\Fix{It is worth noting that we also did not include the tests
 from \hermes\ in the table because, as the reader shall see in
@@
 only the number of passing tests in all engines (the
-``no-fail-in-all'' column), it would significantly \Mar{Not sure if I
-  understood the conclusion. Do you mean the total amount of test
-  (also from other suites)? Why?}reduce our amount of test files.
+``no-fail-in-all'' column), it would significantly reduce our amount of test files.}
+$\leftarrow$\Breno{Haven't we decided that Hermes should be removed from Table 3? 
+If yes, maybe this explanation will only create confusing.}
+\Mar{Not sure if I understood the conclusion. Do you mean the total amount of test
+  (also from other suites)? Why?}
 
@@
 engines support. We decided to discard those. For example, many tests
-we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
-  the reason?  Please, confirm$\rightarrow$}\Igor{yes, it is. Some Node internal features are 
-not included in the JS engine, including some keywords (ie. require, module).
-In addiction, a project with nodejs require a package.json with a lot of external dependencies.} require libraries to be
+we found were based on Node.js~\cite{node} which
+%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
+%\Igor{yes, it is. Some Node internal features are 
+%not included in the JS engine, including some keywords (ie. require, module).
+%In addiction, a project with nodejs require a package.json with a lot of external dependencies.} 
+require libraries to be
 installed before running the test and different tests require
@@
 engines uses a custom shell to run tests, including a harness with
-specific assertions, \Igor{for example, tests provided by Mozilla contains a lot 
-of custom functions (\ie\ assertThrowsInstanceOf, assertEqArray, getPromiseResult).
-The shell contains those functions to made the test run correctly.}
-\Mar{@Igor, can you name which?}. For that, we
-needed to make minor changes in the testing infrastructure to be able
+specific assertions. For example, tests provided by Mozilla contain a lot 
+of custom functions (\eg\ assertThrowsInstanceOf, assertEqArray, getPromiseResult)
+and those are included in the shell to make the test run correctly.
+For that, we needed to make minor changes in the testing infrastructure to be able
 to run the tests uniformly across all engines. More precisely, we
@@
 
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
+%% Fuzzers are typically categorized in two main groups--those that build
+%% inputs anew (generational) and those that modify existing inputs
+%% (mutational).
+
+Fuzzers are tools for generating inputs for a given input
+format~\cite{8863940}. Different fuzzing strategies exist. We analyzed
+\emph{generational} and \emph{mutational} fuzzers.
+
+Generational fuzzers create inputs anew, typically following a
+language description, typically context-free grammars. Intuitively,
+those fuzzers implement a traversal of the production rules of the
+grammar to create syntax trees, which are then pretty-printed and used
+as a fresh input. Such strategy to create inputs produces inputs that
+are syntactically valid by construction. We analyzed four
 grammar-based fuzzers--Grammarinator~\cite{grammarinator},
@@
 Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
-were effective out of the box. For example, we produced 100K inputs
-with Grammarinator and only few inputs were valid. With Megadeth, we
-were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
-contains some heuristics to circumvent violations of certain typing
-rules.\Comment{ such as \Fix{variable used must be defined?}.}
-Nonetheless, running those inputs in our infrastructure we were unable
-to find discrepancies. Inspecting those inputs, we realized that they
-reflected very simple scenarios. To sum up, a high percentage of inputs
-that Grammarinator and Megadeth generated were semantically-invalid
-that we needed to discard whereas the valid inputs manifested no
-discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
-that, in addition to the issues mentioned above, it produces inputs
-that use functions that are only available in the \smonkey{}
-engine. We would need either to mock those functions in other engines
-or to discard those tests. Considering
+were effective out-of-the-box. For example, we produced 100K inputs
+with Grammarinator and only few inputs were semantically valid. With
+Megadeth, we were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid
+inputs as it contains some heuristics to circumvent violations of
+certain typing rules.\Comment{ such as \Fix{variable used must be
+    defined?}.}  Nonetheless, running those inputs in our
+infrastructure we were unable to find discrepancies. Inspecting those
+inputs, we realized that they reflected very simple scenarios. To sum
+up, a high percentage of inputs that Grammarinator and Megadeth
+generated were semantically-invalid that we needed to discard whereas
+the valid inputs manifested no discrepancies. Considering
+jsfunfuzz~\cite{jsfunfuzz}, which has been developed by the Mozilla
+team, we noticed that, in addition to the issues mentioned above, it
+produces inputs that use functions that are only available in the
+\smonkey{} engine. We would need either to mock those functions in
+other engines or to discard those tests. Considering
 LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not

### 2020-06-13 paper/paper.tex
done with my pass on section 5

@@
 
-Fuzzers are typically categorized in two main groups--those that build
-inputs anew (generational) and those that modify existing inputs
-(mutational). We used two black-box mutational
-fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
-in this study. In the following, we provide rationale for this
-selection.
-
-Generational fuzzers are typically grammar-based. These fuzzers
-generate a new file using the grammar of the language whose inputs
-should be fuzzed. Intuitively, those fuzzers implement a traversal of
-the production rules of the input grammar to create syntax trees,
-which are then pretty-printed. Consequently, this approach produces
-inputs that are syntactically valid by construction. We analyzed four
+%% Fuzzers are typically categorized in two main groups--those that build
+%% inputs anew (generational) and those that modify existing inputs
+%% (mutational).
+
+Fuzzers are tools for generating inputs for a given input
+format~\cite{8863940}. Different fuzzing strategies exist. We analyzed
+\emph{generational} and \emph{mutational} fuzzers.
+
+Generational fuzzers create inputs anew, typically following a
+language description, typically context-free grammars. Intuitively,
+those fuzzers implement a traversal of the production rules of a
+grammar to create syntax trees, which are then pretty-printed and used
+as a fresh input. Such strategy to create inputs produces inputs that
+are syntactically valid by construction. We analyzed four
 grammar-based fuzzers--Grammarinator~\cite{grammarinator},
@@
 
-Mutational fuzzers can be either white-box or black-box. White-box
-mutational fuzzers are typically coverage-based. American Fuzz Loop
-(AFL)~\cite{afl} and libFuzzer~\cite{libfuzzer} are examples of this
-kind of fuzzers. These fuzzers run tests inputs against instrumented
-versions of the program under testing with the typical goal of finding
-universal errors like crashes and buffer overflows. The instrumentation
-adds code to collect branch coverage and to monitor specific
+Mutational fuzzers modify inputs files provided as seeds. Gray-box
+mutational fuzzers use coverage information to guide the mutation
+process. American Fuzz Loop (AFL)~\cite{afl} and
+libFuzzer~\cite{libfuzzer} are the most popular coverage-guided
+fuzzers of today. These fuzzers run tests inputs against instrumented
+versions of the programwith the typical goal of finding universal
+errors, like crashes and buffer overflows. The instrumentation adds
+code to collect branch coverage and to monitor specific
 properties\footnote{There are options in the clang toolchain to build
@@
   provides several sanitizers for property
-  checking~\cite{clang-documentation}.}. AFL uses coverage to determine
-inputs that uncover a new branch and hence should be fuzzed more
-whereas libFuzzer uses evolutionary generation--it tries to minimize
-the distances to still-uncovered branches of the program. AFL takes
-the instrumented program binary (say, a JS engine) and one seed input
-to that program (say, a JS program) and produces on output
-fault-revealing inputs, if found. Considering our context of
-application, we needed to instrument one runtime engine for fuzzing.
-We chose \veight\ for that. Unfortunately, we found that most of the inputs produced
-by AFL violate the JS grammar. Furthermore, the fuzzing task can take
-days for a single seed input and there is no simple way to guide the
-exploration\footnote{Exchanged emails with the tool author.}. That
-happens because the fuzzer aims to explore the entire decision tree
-induced from the engine's main function, including the branches
-associated with the higher layers of the compiler (\eg{}, lexer and
-parser). It is worth mentioning that Google mitigates that problem
-with libFuzzer by asking developers to create fuzz targets for
-specific program
-functions~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}. Although
-that approach has shown to be effective, it requires domain knowledge
-to create the calling context to invoke the fuzz target. For that, we
-decide not to consider coverage-based in this study.
+  checking~\cite{clang-documentation}.}. AFL and libFuzzer work very
+similarly. They use coverage to find inputs that uncover a new branch
+and hence should be fuzzed more. These tools take as input a program
+binary (say, a JS engine), which is instrumented to collect coverage
+information and to capture runtime violations (\eg{}, illegal memory
+accesses), and one seed input to that program (say, a JS program) and
+produces on output fault-revealing inputs. We chose to use AFL and
+instrument \veight. Unfortunately, we found that most of the inputs
+produced by AFL violate the JS grammar. We would need to translate
+production rules of Python to the AFL format to circumvent that
+issue. We found that the fuzzing task can take days for a single seed
+input and there is no clear way to guide the exploration. That happens
+because the fuzzer aims to explore the entire decision tree induced
+from the engine's main function, including the branches associated
+with the higher layers of the compiler (\eg{}, lexer and parser). One
+way to mitigate that problem is by writing fuzzing targets
+(a.k.a. targets) for specific program functions. Although that
+approach has shown to be effective at
+Google~\cite{libFuzzer-tutorial-google,libFuzzer-chromium-google}, it
+requires domain knowledge to create the calling context to invoke the
+fuzz target. For that, we decide not to consider coverage-based in
+this study.
 
@@
 since \radamsa performs simpler syntactic source code modifications,
-it also produces a higher number of valid inputs (when compared with,
-for instance, AFL).
+it also produces a higher number of valid inputs.
 

### 2020-06-13 paper/paper.tex
pass on 6.1 and 6.2

@@
 to find functional bugs
-in \javascript\ engines. Based on that, we pose three questions:
+in \javascript\ engines. Based on that, we pose the following three questions:
 \begin{description}[leftmargin=.5in]
@@
 
-\subsection{Answering RQ1 (Conformance)}
+\subsection{Answering RQ1 (Test262 Conformance)}
 \label{sec:stability}
@@
 we wanted to make sure if the failing tests raised by the Test262 suite
-were rapidly fixed by the maintenance team. If these errors were quickly
-fixed, this would suggest that this given engine would be closely aligned with
+were rapidly fixed by the maintenance team. If errors were quickly
+fixed, this would suggest that a given engine would be closely aligned with
 the ECMAScript specification.
@@
 Moreover, one can also note that \chakra has a low passing ratio
-in this test suite. Intestingly, it is also the one we were able to find more bugs (as per
+in this test suite. Interestingly, it is also the one we were able to find more bugs (as per
 Figure~\ref{fig:summary}). Although it is plausible to find
 correlation between the passing ratios and reliability as measured by
-the number of bugs found, we do not imply causality. As aforementioned,
+the number of bugs found, we do not imply causality. As discussed above,
 it is important
@@
   \fbox{
-    \begin{minipage}{8cm}
+    \begin{minipage}{11cm}
       \textit{Summary:}~Most of the engines seem to adhere well to the
@@
 tests. We use a dash (``-'') to indicate that we did not consider the
-combinations that associate a test suite with its parent engine.
+combinations that run the test suite of an engine in itself.  Failures
+in those cases would either indicate regressions or flaky tests as
+opposed to unknown bugs for that engine. As explained in
+Section~\ref{sec:seeds}, we used a total of
+\totalTestFilesForTestTransplantation{} tests in this
+experiment. These tests are included in the dashed rectangle under
+column ``type-in-all'' on Table~\ref{tab:test-suites}. Running those
+tests we observed a total of \failuresTestTrans{} failures manifested
+across \failuresTestTransDistictFiles{} distinct files
+(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
+shows that \smonkey\ was the engine that failed the least whereas
+\chakra\ was the engine that failed the most. The \smonkey\ test suite
+also revealed more failures than any other, perhaps as expected, given
+that it is the suite with more tests (see
+Table~\ref{tab:test-suites}).
+
 \Fix{
@@
 \Gustavo{Falar pq Hermes nao esta na tabela}
-Failures in those cases would either indicate regressions or flaky
-tests as opposed to unknown bugs for that engine. As explained in
-Section~\ref{sec:seeds}, we used in this experiment the
-\totalTestFilesForTestTransplantation{} tests included in the
-rectangle area under column ``type-in-all'' from
-Table~\ref{tab:test-suites}. Running those tests we observed a total
-of \failuresTestTrans{} failures manifested across
-\failuresTestTransDistictFiles{} distinct files
-(\failuresTestTransPercent{} of total).  Table~\ref{tab:cross-testing}
-shows that \smonkey\ was the engine that failed the least whereas
-\chakra\ was the engine that failed the most. The \smonkey\ test suite
-also revealed more failures than any other, as expected, given
-that it is the suite with more tests (see
-Table~\ref{tab:test-suites}).
 
@@
 
-\begin{table}
+\begin{table}[h!]
   \centering
@@
 False Positives (FPs) and True Positives (TPs). The sum of the numbers
-in this table correspond to the number of files that manifested
+in this table corresponds to the number of files that manifested
 failures, \ie{}, \failuresTestTransDistictFiles{}. Considering false
@@
 finally, column ``Suite'' shows the name of the engine that originated
-the test.  (We omitted the URLs of the issues to protect anonymity.)
-Considering severity levels, we found that \jsc~\cite{jsc-severity}
-and \smonkey{}~\cite{mozilla-severity} developers use five levels,
-whereas \chakra{}~\cite{chakra-severity} and
-\veight{}~\cite{v8-severity} developers use only three. As usual, the
-smallest the severity value the highest the severity of the bug. We
-use a dash (``-'') in place of the severity level for the cases where
-the bug report is pending confirmation. Of the
-\noBugsTransplantation{} bugs we reported in this experiment,
+the test. Considering severity levels, we found that
+\jsc~\cite{jsc-severity} and \smonkey{}~\cite{mozilla-severity}
+developers use five levels, whereas \chakra{}~\cite{chakra-severity}
+and \veight{}~\cite{v8-severity} developers use only three. As usual,
+the smallest the number the highest the severity of the bug. We use a
+dash (``-'') in place of the severity level for the cases where the
+bug report is pending confirmation. Of the \noBugsTransplantation{}
+bugs we reported in this experiment,
 \noBugsTransplantationConfirmed\ were promoted from the status ``New''
-to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
-not find any critical bugs, most of the bugs are seemingly important
-as per the categorization given by engineers. Analyzing the issue
-tracker of \chakra, we found that severity-1 bugs are indeed
-rare. Considering the number of bug reports confirmed by developers,
-\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
-fixed). Considering the remaining engines, \veight{} developers
-confirmed the \noTransVeightBugsReported{} bugs we reported, fixing
-\noTransVeightBugsFixed{}. Curiously, Google
-engineers confirmed the issued bug reports in a few hours. Overall, we
-found that development teams of other engines, specially \jsc\, took
-much longer to analyze bug reports as can be observed in the
-\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}.
-However, the bugs the \jsc team confirmed were quickly fixed.
+to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are
+severity-2 bugs.  Although we did not find any critical bugs, most of
+the bugs are seemingly important as per the categorization given by
+engineers. Analyzing the issue tracker of \chakra, we found that
+severity-1 bugs are indeed rare. Considering the number of bug reports
+confirmed by developers, \chakra{} was the engine with the highest
+number: \bugsChakra{}, with \bugsChakraFixed{} bugs fixed. Considering
+the remaining engines, \veight{} developers confirmed the
+\noTransVeightBugsReported{} bugs we reported, fixing
+\noTransVeightBugsFixed{}. Curiously, Google engineers confirmed the
+issued bug reports in a few hours. Likewise, we reported only one bug
+on Mozilla's \smonkey, which was quickly fixed.  Overall, we found
+that development teams of other engines, specially \jsc, took much
+longer to analyze bug reports as can be observed in the \jsc\ stacked
+bar from Figure~\ref{fig:stacked-engine}. However, once the team
+confirmed those bugs they were then quickly fixed.
 
@@
   \fbox{
-    \begin{minipage}{8cm}
+    \begin{minipage}{11cm}
       \textit{Summary:}~Test transplantation was effective at finding
@@
   \fbox{
-    \begin{minipage}{8cm}
+    \begin{minipage}{11cm}
       \textit{Summary:}~Cross-engine differential testing was

### 2020-06-13 paper/paper.tex
pass on eval

@@
 This section reports the results obtained with cross-engine differential
-testing. More precisely, we report results obtained by fuzzing test
-inputs, running those inputs on different engines, and checking the
-outcomes with a differential oracle.
-
-\vspace{0.5ex}
+testing.
+
+%More precisely, we report results obtained by fuzzing test
+%inputs, running those inputs on different engines, and checking the
+%outcomes with a differential oracle.
+
+%\vspace{0.5ex}
 \subsubsection{Methodology}
-The experimental methodology we used is as follows. As explained in
+The experimental methodology we used is as follows. As explained on
 Section~\ref{sec:objects:fuzzers}, we used Radamsa~\cite{radamsa} and
@@
 we trained eight students in analyzing the warnings that our
-infrastructure produces. The students were enrolled in a
+infrastructure produced. The students were enrolled in a
 graduate-level testing class. We listed warnings in a spreadsheet and
@@
 
-\vspace{0.5ex}
-\lbrack{}Non-Exploratory Phase\rbrack{} Results obtained in the
-exploratory phase confirmed our expectations that most of the bugs
-found during the initial period of investigation were related to
-\hi\ warnings. For that reason, we changed our inspection
-strategy. This time, only the co-authors inspected the bugs using a
+\vspace{0.5ex} \lbrack{}Non-Exploratory Phase\rbrack{} Results
+obtained in the exploratory phase confirmed our expectations that most
+of the bugs found during the initial period of investigation were
+related to \hi\ warnings. For that reason, we changed our inspection
+strategy. This time, some of the co-authors inspected the bugs using a
 similar discipline as before. However, the set of warnings inspected
@@
 optimized for fast start-up of React Native apps on
-Android''~\cite{hermes2020repo}.\Mar{short sentence saying where it is
-  used.}\Igor{Currently, hermes is being used in the react-native framework,
-  also maintained by Facebook, as a beta component to increase the performance of Android applications,
-  such as startup time, reduce memory consumption and application size\cite{reactnative2020hermes}.
-}
+Android''~\cite{hermes2020repo}. Currently, \hermes\ is used as a beta
+component of the react-native framework, which is also maintained by
+Facebook. The goal of \hermes\ at Facebook is to increase the
+performance of Android applications, such as startup time, to reduce
+memory consumption and application size~\cite{reactnative2020hermes}.
 
@@
 \hermes. This happened because \smonkey has its own assertion
-framework, but \hermes was unable to interpret those assertions \Igor{due to 
-the missing features mentioned before (\ie\ Class definitions, Proxy properties)}
-resulting in failures in all test executions from this engine. These
-failures did not happen when the \smonkey tests were transplanted to
-the other engines, though.\Mar{Why? Was the framework using some of the
-  features aforementioned? Say it, please}\Igor{fixed above}.
-Overall, we reported three issues to the \hermes bug tracker as result of using test
+framework, but \hermes was unable to interpret those assertions
+(because of missing features), resulting in failures in all test
+executions from. These failures did not happen when the \smonkey tests
+were transplanted to the other engines, though.  Overall, we reported
+three issues to the \hermes bug tracker as result of using test
 transplantation\footnote{\url{https://github.com/facebook/hermes/issues/<id>},

### 2020-06-13 paper/paper.tex
corrigindo largura das figuras

@@
   \centering
-  \includegraphics[trim=0 0 0 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
+  \includegraphics[trim=0 330 170 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
   \caption{\label{fig:workflow}Differential Testing infrastructure
-    overview.\Fix{tem certeza que Hermes estah usando mesma fonte/tamanho?}}
+    overview.}
 \end{figure}

### 2020-06-13 paper/paper.tex
Reordered Bug Reports in Section 8.1
com histograms

@@
 
-\Fix{...add and discuss histograms}
+To provide a brief overview of the test suites and understand if the engines
+have specific testing purposes, we investigated the most common
+objects and functions that each one of the JS engines employ.
+To achieve this goal, we started by filtering out many non-relevant source
+code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
+special characters (such as parentheses, mathematical symbols, and semicolons).
+For the remaining source code constructs, we search for the ``.'' character, which
+indicates a function call. We then stored the function and the object that host
+that function.  By manually analyzing this data, we noted many general purpose
+functions, that do not provide any hint on the kind of behavior the engine is
+more likely to test (such as \texttt{console.log}). We also removed these
+general purpose functions. The remaining object/functions are shown at
+Figure~\ref{fig:histograms}.
+
+\begin{figure}[thp]
+\begin{center}
+$
+\begin{array}{cc}
+Charka & Duktape \\
+\includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
+Hermes & JerryJS \\
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
+JSI & Test262 \\
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
+TinyJS & V8 \\
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
+\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
+\end{array}
+$
+\end{center}
+\caption{histograms.}
+\label{fig:histograms}
+\end{figure}
 

### 2020-06-14 paper/paper.tex
removing histograms
Pass on Introduction

@@
 as we propose here --- to enhance the coverage of the engine under testing.
-%These techniques demand different effort from developers.
+%These techniques are semi-automated and they can demand different effort from developers.
 Cross-engine differential testing is semi-automated as
 developers need to decide if alarms are manifestations of real
-bugs. Test transplantation is fully automated, but it can only reveal
-bugs that the original tests could reveal. This study measures the
-ability of these techniques in finding bugs and the human cost
-associated with each technique.
+bugs. 
+Test transplantation is also semi-automated
+and developer intervention may be required to ensure that a test case from one engine can be performed on another engine without adaptations; 
+or to verify that alarms are manifestations of real bugs and not the result of an unsupported feature or an obsolete specification.
+%Test transplantation is fully automated, but it can only reveal
+%bugs that the original tests could reveal. 
+This study measures the ability of these techniques 
+in finding bugs and the human cost associated with each technique.
 
@@
 To achieve this goal, we started by filtering out many non-relevant source
-code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
+code statements available on the test suites. We started by removing JS language constructs (such as \texttt{if}, \texttt{for}, and \texttt{var}). We then removed
 special characters (such as parentheses, mathematical symbols, and semicolons).
@@
 \sloppy
-\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
-code snippet below shows a test that reveals a bug in \textbf{\chakra}.
-
-\begin{figure}[h!]
-  \vspace{-1ex}
-  \centering
-  \scriptsize
-  \lstset{escapeinside={@}{@},
-%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-    basicstyle=\ttfamily\scriptsize, boxpos=c,
-    numberstyle=\tiny,
-    morekeywords={assertEq, var, yield, in, function,
-    typeof, return, throw, new, Error, if},
-  }
-  \begin{lstlisting}
- { var a = {valueOf: function(){ return "\x00"}}
-   assert(+a === 0) }
-  \end{lstlisting}
-  \normalsize
-  %% \caption{Warning captured as \hi{} priority.}
-  %% \label{fig:hi-priority}
-  \vspace{-1ex}
-\end{figure}
-
-The object property \CodeIn{valueOf} stores a function that returns a
-primitive value identifying the target object~\cite{valueof}. The
-original version of this code returns an empty string whereas the
-version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
-returns a string representation of a null character
-(\CodeIn{NUL})\Comment{ in ascii}. The unary plus expression
-``\CodeIn{+a}", used in the assertion, is equivalent to the operation
-\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
-otherwise the operation returns NaN (Not a
-Number)~\cite{unary-plus}. This test fails in all engines but
-\chakra{}. For all three engines the string cannot be parsed as an
-hexadecimal. As such, they produce a NaN and the test fails as
-expected. \chakra{}, instead, incorrectly converts the string to zero,
-and the test passes. As Table~\ref{tab:bugs} shows, the \chakra{} team
-fixed the issue soon after our report.
-
-\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
-snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
-revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
-obtained by fuzzing a Test262 test with \quickfuzz. In its original
-version, a string (omitted for space), passed as argument to the
-\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
-the string argument with a function whose body is a \CodeIn{break}
-statement outside a valid block statement. Section B.3.3.3 from the
-\es\ spec~\cite{spec-b333} documents how eval should handle code
-containing function declarations.  According to the
-spec~\cite{break-statement}, the virtual machine should throw an early
-error--in this case, a SyntaxError--if the break statement is not
-nested in a loop or switch statement. All engines, but \veight{},
-behave as expected in this case.
-
-%% \Igor{
-%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
-%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
-%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
-%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
-%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
-%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a
-%%   function declaration. The fuzzer removes the function declaration and
-%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
-%%   the break statement should throw an early error (in this case a SyntaxError)
-%%   if the break statement is not nested in an iterational or a switch statement. All engines works
-%%   as expected but \veight{} pass without failures.
-%% }
-
+
+%-----Issue \#19, Table~\ref{tab:test-transplantation-bugs}
 \vspace{1ex}\noindent\textbf{Issue \#19,
@@
 
+%-----Issue \#35, Table~\ref{tab:test-transplantation-bugs}
+\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
+reported the snippet \CodeIn{"use strict" 010} to the
+\textbf{\smonkey} development team as a bug and the bug was confirmed
+in a few hours.  This is a test case originally from the \hermes suite
+using test transplantation.  According the specification, in strict
+mode, the engine must use the prefix '0o' or '0O' to represent octal
+numeric literals. This is an issue that explores a deprecated octal
+token after ASI (Automatic Semicolon Insertion). The other engines
+throw a SyntaxError due to the missing of the octal token, but \smonkey
+returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.
+
+%% \begin{figure}[h!]
+%%   \vspace{-0.5ex}
+%%   \centering
+%%   \scriptsize
+%%   \lstset{escapeinside={@}{@},
+%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
+%%     numberstyle=\tiny,
+%%     morekeywords={assertEq, var, yield, in, function,
+%%     typeof, return, throw, new, Error, if},
+%%   }
+%%   \begin{lstlisting}
+%%     "use strict"
+%%     010
+%%   \end{lstlisting}
+%%   \normalsize
+%%   %% \caption{Warning captured as \hi{} priority.}
+%%   %% \label{fig:hi-priority}
+%%   \vspace{-1ex}
+%% \end{figure}
+
+%-----Issue \#2, Table~\ref{tab:bugs}
 \vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
@@
 
-\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
-reported the snippet \CodeIn{"use strict" 010} to the
-\textbf{\smonkey} development team as a bug and the bug was confirmed
-in a few hours.  This is a test case originally from the \hermes suite
-using test transplantation.  According the specification, in strict
-mode, the engine must use the prefix '0o' or '0O' to represent octal
-numeric literals. This is an issue that explores a deprecated octal
-token after ASI (Automatic Semicolon Insertion). The other engines
-throw a SyntaxError due to the missing of the octal token, but \smonkey
-returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.
-
-%% \begin{figure}[h!]
-%%   \vspace{-0.5ex}
-%%   \centering
-%%   \scriptsize
-%%   \lstset{escapeinside={@}{@},
-%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
-%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
-%%     numberstyle=\tiny,
-%%     morekeywords={assertEq, var, yield, in, function,
-%%     typeof, return, throw, new, Error, if},
+%-----Issue \#4, Table~\ref{tab:bugs}
+\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
+code snippet below shows a test that reveals a bug in \textbf{\chakra}.
+
+\begin{figure}[h!]
+  \vspace{-1ex}
+  \centering
+  \scriptsize
+  \lstset{escapeinside={@}{@},
+%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
+    basicstyle=\ttfamily\scriptsize, boxpos=c,
+    numberstyle=\tiny,
+    morekeywords={assertEq, var, yield, in, function,
+    typeof, return, throw, new, Error, if},
+  }
+  \begin{lstlisting}
+ { var a = {valueOf: function(){ return "\x00"}}
+   assert(+a === 0) }
+  \end{lstlisting}
+  \normalsize
+  %% \caption{Warning captured as \hi{} priority.}
+  %% \label{fig:hi-priority}
+  \vspace{-1ex}
+\end{figure}
+
+The object property \CodeIn{valueOf} stores a function that returns a
+primitive value identifying the target object~\cite{valueof}. The
+original version of this code returns an empty string whereas the
+version of the code modified by the \radamsa{} fuzzer~\cite{radamsa}
+returns a string representation of a null character
+(\CodeIn{NUL})\Comment{ in ascii}. The unary plus expression
+``\CodeIn{+a}", used in the assertion, is equivalent to the operation
+\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
+otherwise the operation returns NaN (Not a
+Number)~\cite{unary-plus}. This test fails in all engines but
+\chakra{}. For all three engines the string cannot be parsed as an
+hexadecimal. As such, they produce a NaN and the test fails as
+expected. \chakra{}, instead, incorrectly converts the string to zero,
+and the test passes. As Table~\ref{tab:bugs} shows, the \chakra{} team
+fixed the issue soon after our report.
+
+%-----Issue \#18, Table~\ref{tab:bugs}
+\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
+snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
+revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
+obtained by fuzzing a Test262 test with \quickfuzz. In its original
+version, a string (omitted for space), passed as argument to the
+\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
+the string argument with a function whose body is a \CodeIn{break}
+statement outside a valid block statement. Section B.3.3.3 from the
+\es\ spec~\cite{spec-b333} documents how eval should handle code
+containing function declarations.  According to the
+spec~\cite{break-statement}, the virtual machine should throw an early
+error--in this case, a SyntaxError--if the break statement is not
+nested in a loop or switch statement. All engines, but \veight{},
+behave as expected in this case.
+
+%% \Igor{
+%%   Este foi caso de bug confirmado que foi manifestado no engenho \veight{}.
+%%   Este test case oriundo da suite Test262 foi fuzzado pelo \quickfuzz{}
+%%   que por ser um fuzzer mutacional, usa uma gramatica \js{} que auxilia na geracao
+%%   de entradas validas. In Figure~\ref{fig:bug-veight}, we observed a \CodeIn{eval} statement
+%%   that try to evaluate a \CodeIn{function f()}, this test case specify the ecma spec
+%%   B.3.3.3~\cite{spec-b333} that describe an evaluation of a block statement in eval code containing a
+%%   function declaration. The fuzzer removes the function declaration and
+%%   injects a function with a break statement outside a loop. According to specification~\cite{break-statement},
+%%   the break statement should throw an early error (in this case a SyntaxError)
+%%   if the break statement is not nested in an iterational or a switch statement. All engines works
+%%   as expected but \veight{} pass without failures.
 %% }
-%%   \begin{lstlisting}
-%%     "use strict"
-%%     010
-%%   \end{lstlisting}
-%%   \normalsize
-%%   %% \caption{Warning captured as \hi{} priority.}
-%%   %% \label{fig:hi-priority}
-%%   \vspace{-1ex}
-%% \end{figure}
-
+
+%-----Issue \#24, Table~\ref{tab:bugs}
 \vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet

### 2020-06-14 paper/paper.tex
pass on section 4

--- 2020-06-13 paper/paper.tex
@@
     JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
-    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
+    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{} & \tinyNoFailAll{}\\
     Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
-    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
+    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{}\markbottomright{c1} & \blogEngineNetNoFailAll{}\markbottomright{c2} \\
     \midrule
@@
 these tests and are encouraged to run them.
-
 Column ``no-fail-in-all'' shows the tests for which all engines
-pass. The set of tests in this column is a subset of the
-``type-in-all'' test set. The tests in this set are as fuzzing seeds
-in the evaluation of differential testing. The guarantee that they
-pass in all engines assures that, if discrepancies occur, they are
-related to the changes in the input as opposed to the original cause
-of failure.
-\Fix{It is worth noting that we also did not include the tests
-from \hermes\ in the table because, as the reader shall see in
-Table~\ref{tab:test262}, \hermes presents a very low adherence to the
-Test262 conformance suite. If we decided to keep \hermes, considering
-only the number of passing tests in all engines (the
-``no-fail-in-all'' column), it would significantly reduce our amount of test files.}
-$\leftarrow$\Breno{Haven't we decided that Hermes should be removed from Table 3?
-If yes, maybe this explanation will only create confusing.}
-\Mar{Not sure if I understood the conclusion. Do you mean the total amount of test
-  (also from other suites)? Why?}
+pass. The tests in this set are used as fuzzing seeds in the
+evaluation of differential testing. The guarantee that tests pass in
+all engines assures that discrepancies are related to the changes in
+the input produced by fuzzers.
 
@@
 
-\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
-tests we found depend on external libraries, which not all selected
-engines support. We decided to discard those. For example, many tests
-we found were based on Node.js~\cite{node} which
+\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
+depend on external libraries, which not all selected engines
+support. We decided to discard those. For example, we found many tests
+based on Node.js~\cite{node} that
 %\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
-%\Igor{yes, it is. Some Node internal features are
-%not included in the JS engine, including some keywords (ie. require, module).
-%In addiction, a project with nodejs require a package.json with a lot of external dependencies.}
-require libraries to be
-installed before running the test and different tests require
-different sets of libraries. Also, as already mentioned, we did not
+%\Igor{yes, it is. Some Node internal features are not included in the
+%JS engine, including some keywords (ie. require, module).  In
+%addiction, a project with nodejs require a package.json with a lot of
+%external dependencies.}
+require libraries to be installed before running the test and
+different tests require different sets of libraries. Supporting those
+tests would require an extra setup step and would slow down the
+execution of our experiments. Also, as already mentioned, we did not
 consider tests from the \chakra{} repository because they depend on
-non-portable objects.  Finally, note that the number of tests in
-\veight\ is low; that happens because \veight{} uses many tests from
-Mozilla and \jsc; we discarded those to avoid repetition and to give
-credit where it is due.
-
-\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
-engines uses a custom shell to run tests, including a harness with
-specific assertions. For example, tests provided by Mozilla contain a lot
-of custom functions (\eg\ assertThrowsInstanceOf, assertEqArray, getPromiseResult)
-and those are included in the shell to make the test run correctly.
-For that, we needed to make minor changes in the testing infrastructure to be able
+non-portable objects.
+
+\lbrack{}Test Harness\rbrack{}~We noticed that some engines use a
+custom shell to run tests, including a harness with specific
+assertions. For example, tests provided by Mozilla contain a lot of
+custom functions (\eg{}, \CodeIn{assertThrowsInstanceOf},
+\CodeIn{assertEqArray}, and \CodeIn{getPromiseResult}) and those are
+included in the shell to make the test run correctly.  For that, we
+needed to make minor changes in the testing infrastructure to be able
 to run the tests uniformly across all engines. More precisely, we
@@
 we tried to mock the minimum amount of code possible to make the test
-file work in the other engine.\Mar{This seems a different problem
-  (tests without assertions). I did not understand how this is related
-  to portability?}\Igor{A test is a simple JS file input.
-  Some tests are not well-defined.}  For instance, if a test had a statement such as
-\texttt{print(1==1);} we manually refactored that statement to
-\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
-If the change would require more substantial manual work, we opted to discard the test instead. Overall,
-we may have manually refactored more than a thousand test files.
-
-\lbrack{}Dedup\rbrack{}~\Fix{Explain what we did to avoid
-  dups. Consider moving to the the sentence ``Finally, note that the number of tests in V8''}
+file work in the other engine. For instance, if a test had a statement
+such as \texttt{print(1==1);} we manually refactored that statement to
+\texttt{assert(1==1)} which should throw an assertion violation if the
+condition returns false.  If we found the change would require
+substantial manual work, we opted to discard the test instead.
+
+%Overall, we may have manually refactored more than a thousand test files.
+
+%% \Mar{This seems a different problem
+%%   (tests without assertions). I did not understand how this is related
+%%   to portability?}\Igor{A test is a simple JS file input.  Some tests
+%%   are not well-defined.}
+
+\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
+we dicarded duplicate tests with Mozilla and \jsc. The rationale is to
+avoid inflating results and giving credit where it is due. We also
+wrote a script that compares each pair of tests from different suites
+for similarity. We did not find identical tests, although it is
+possible there are equivalent tests modulo renaming.
+
+%\Fix{Explain what we did to avoid dups. Consider
+%  moving to the the sentence ``Finally, note that the number of tests
+%  in V8''}
 
@@
 
-\subsection{Characterization of Test Suites}
-
-\Fix{...add and discuss histograms}
+%% \subsection{Characterization of Test Suites}
+
+%% To provide a brief overview of the test suites and understand if the engines
+%% have specific testing purposes, we investigated the most common
+%% objects and functions that each one of the JS engines employ.
+%% To achieve this goal, we started by filtering out many non-relevant source
+%% code statements available on the test suites. We started by removing JS language constructs (such as \texttt{if}, \texttt{for}, and \texttt{var}). We then removed
+%% special characters (such as parentheses, mathematical symbols, and semicolons).
+%% For the remaining source code constructs, we search for the ``.'' character, which
+%% indicates a function call. We then stored the function and the object that host
+%% that function.  By manually analyzing this data, we noted many general purpose
+%% functions, that do not provide any hint on the kind of behavior the engine is
+%% more likely to test (such as \texttt{console.log}). We also removed these
+%% general purpose functions. The remaining object/functions are shown at
+%% Figure~\ref{fig:histograms}.
+
+%% \begin{figure}[thp]
+%% \begin{center}
+%% $
+%% \begin{array}{cc}
+%% Charka & Duktape \\
+%% \includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
+%% Hermes & JerryJS \\
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
+%% JSI & Test262 \\
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
+%% TinyJS & V8 \\
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
+%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
+%% \end{array}
+%% $
+%% \end{center}
+%% \caption{histograms.}
+%% \label{fig:histograms}
+%% \end{figure}
 
@@
 
+\Mar{moved from Section 4. check if useful. $\rightarrow$}
+\Fix{It is worth noting that we also
+  did not include the tests from \hermes\ in the table because, as the
+  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
+  low adherence to the Test262 conformance suite. If we decided to
+  keep \hermes, considering only the number of passing tests in all
+  engines (the ``no-fail-in-all'' column), it would significantly
+  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
+  decided that Hermes should be removed from Table 3?  If yes, maybe
+  this explanation will only create confusing.}  \Mar{Not sure if I
+  understood the conclusion. Do you mean the total amount of test
+  (also from other suites)? Why?}
+
 This section discusses bug reports, threats to validity, and key

### 2020-06-14 paper/paper.tex
finalizando passada...

--- 2020-06-13 paper/paper.tex
@@
 
-\subsection{Characterization of Test Suites}
-
-To provide a brief overview of the test suites and understand if the engines
-have specific testing purposes, we investigated the most common
-objects and functions that each one of the JS engines employ.
-To achieve this goal, we started by filtering out many non-relevant source
-code statements available on the test suites. We started by removing JS language constructs (such as \textt{if}, \textt{for}, and \textt{var}). We then removed
-special characters (such as parentheses, mathematical symbols, and semicolons).
-For the remaining source code constructs, we search for the ``.'' character, which
-indicates a function call. We then stored the function and the object that host
-that function.  By manually analyzing this data, we noted many general purpose
-functions, that do not provide any hint on the kind of behavior the engine is
-more likely to test (such as \texttt{console.log}). We also removed these
-general purpose functions. The remaining object/functions are shown at
-Figure~\ref{fig:histograms}.
-
-\begin{figure}[thp]
-\begin{center}
-$
-\begin{array}{cc}
-Charka & Duktape \\
-\includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
-Hermes & JerryJS \\
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
-JSI & Test262 \\
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
-TinyJS & V8 \\
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
-\includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
-\end{array}
-$
-\end{center}
-\caption{histograms.}
-\label{fig:histograms}
-\end{figure}
-
 \section{Cross-Engine Differential Testing}
@@
     \midrule
+    \veight{} & \percentSuiteTestVeight{} \\
+    \smonkey{} & \percentSuiteTestSM{} \\
     \jsc & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
     \chakra{} & \percentSuiteTestChakra{} \\
-    \smonkey{} & \percentSuiteTestSM{} \\
-    \hermes & \percentSuiteTestHermes{} \\
+    %\hermes & \percentSuiteTestHermes{} \\
     \bottomrule
@@
       \textit{Summary:}~Most of the engines seem to adhere well to the
-      \js\ standard. Except for \hermes and \chakra, the passing ratio of all
+      \js\ standard. Except for \chakra, the passing ratio of all
       engines is above 90\%.
@@
 
-\Fix{
 In particular, we were not able to reuse the \smonkey tests on the
@@
 though.
-}
-\Gustavo{Falar pq Hermes nao esta na tabela}
 

### 2020-06-14 paper/paper.tex

--- 2020-06-14 paper/paper.tex
@@
     \midrule
+    \veight{} & \percentSuiteTestVeight{} \\
+    \smonkey{} & \percentSuiteTestSM{} \\
     \jsc & \percentSuiteTestJSC{}\\
-    \veight{} & \percentSuiteTestVeight{} \\
     \chakra{} & \percentSuiteTestChakra{} \\
-    \smonkey{} & \percentSuiteTestSM{} \\
     \hermes & \percentSuiteTestHermes{} \\
@@
 %still has many unsupported features, such as Proxy, Promisse, and Async.}
-Moreover, one can also note that \chakra has a low passing ratio
-in this test suite. Interestingly, it is also the one we were able to find more bugs (as per
+Moreover, one can also note that \hermes and \chakra have a low passing ratio
+in this test suite. Interestingly, \chakra is also the one we were able to find more bugs (as per
 Figure~\ref{fig:summary}). Although it is plausible to find
@@
 to note that failures in this conformance test suite indicates missing
-features as opposed to bugs.
+features as opposed to bugs. Finally, since \hermes has a
+very low adherence to the Test262 conformance suite, we opted to conduct
+a case study with them. Therefore, we will only discuss \hermes data at
+Section~\ref{sec:hermes}.
 
@@
 
-\Mar{moved from Section 4. check if useful. $\rightarrow$}
-\Fix{It is worth noting that we also
-  did not include the tests from \hermes\ in the table because, as the
-  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
-  low adherence to the Test262 conformance suite. If we decided to
-  keep \hermes, considering only the number of passing tests in all
-  engines (the ``no-fail-in-all'' column), it would significantly
-  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
-  decided that Hermes should be removed from Table 3?  If yes, maybe
-  this explanation will only create confusing.}  \Mar{Not sure if I
-  understood the conclusion. Do you mean the total amount of test
-  (also from other suites)? Why?}
+%\Mar{moved from Section 4. check if useful. $\rightarrow$}
+%\Fix{It is worth noting that we also
+%  did not include the tests from \hermes\ in the table because, as the
+%  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
+%  low adherence to the Test262 conformance suite. If we decided to
+%  keep \hermes, considering only the number of passing tests in all
+%  engines (the ``no-fail-in-all'' column), it would significantly
+%  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
+%  decided that Hermes should be removed from Table 3?  If yes, maybe
+%  this explanation will only create confusing.}  \Mar{Not sure if I
+%  understood the conclusion. Do you mean the total amount of test
+%  (also from other suites)? Why?}
 
@@
 %-----Issue \#35, Table~\ref{tab:test-transplantation-bugs}
-\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
+\vspace{1ex}\noindent\textbf{Issue \#32, Table~\ref{tab:test-transplantation-bugs}.} We
 reported the snippet \CodeIn{"use strict" 010} to the
@@
 %-----Issue \#24, Table~\ref{tab:bugs}
-\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
+\vspace{1ex}\noindent\textbf{Bug reported on \hermes.} The snippet
 \CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with

### 2020-06-14 paper/paper.tex
Small fix in Table 9
final final pass

@@
 
-In particular, we were not able to reuse the \smonkey tests on the
-\hermes engine. This happened because \smonkey has its own assertion
-framework, but \hermes did not interpret these assertions, resulting
-in failures in all test executions from this engine. These failures
-did not happen when the \smonkey tests were transplanted to the other engines,
-though.
+%In particular, we were not able to reuse the \smonkey tests on the
+%\hermes engine. This happened because \smonkey has its own assertion
+%framework, but \hermes did not interpret these assertions, resulting
+%in failures in all test executions from this engine. These failures
+%did not happen when the \smonkey tests were transplanted to the other engines,
+%though.
 
@@
 dash (``-'') in place of the severity level for the cases where the
-bug report is pending confirmation. Of the \noBugsTransplantation{}
+bug report is pending confirmation. Of the 32
 bugs we reported in this experiment,
@@
 across engine implementations that was considered to be acceptable. As
-of now, we did not find any new bugs on \smonkey{}; the bugs we found
+of now, we did not find any new bugs on \smonkey{} using differential
+testing; the bugs we found
 were duplicates and were not reported. For \veight{},

### 2020-06-14 paper/paper.tex
Fixed typos

--- 2020-06-14 paper/paper.tex
@@
 of studied engines. The main reason was to investigate how our
-approach would work on a recently introduced JS engined. More about
+approach would work on a recently introduced JS engine. More about
 \hermes on Section~\ref{sec:hermes}.  Table~\ref{tab:engines} lists
@@
 \lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
-we dicarded duplicate tests with Mozilla and \jsc. The rationale is to
+we discarded duplicate tests with Mozilla and \jsc. The rationale is to
 avoid inflating results and giving credit where it is due. We also
@@
 real bug. We defined two types of warnings based on empirical evidence
-weobtained while analyzing bugs. The types ``\hi{}'' and
+we obtained while analyzing bugs. The types ``\hi{}'' and
 ``\lo{}''. Warnings of the kind ``\hi{}'' are associated with the
@@
 study: \radamsa~\cite{radamsa} and \quickfuzz~\cite{quickfuzz}. These
-fuzzers require no instrumentation and domain-knowledge. They mutate
+fuzzers require no instrumentation and domain knowledge. They mutate
 existing inputs randomly. The strength of the approach is
@@
 percentages in the table. The number of passing tests is high and
-similar for \jsc, \veight, and \smonkey
+similar for \jsc, \veight, and \smonkey.
 %, whereas \chakra performs
@@
 high percentage of failing tests was due to the high number of
-features not yet suported by \hermes\footnote{See
+features not yet supported by \hermes\footnote{See
   \url{https://github.com/facebook/hermes/blob/master/doc/Features.md}}. For
@@
 3 as argument to \CodeIn{repeat()}, \ie{}, the expression produced a
-string with three repetitiong of the string ``foo''. The new test uses
+string with three repetitions of the string ``foo''. The new test uses
 a long integer instead as parameter to \CodeIn{repeat()}. As result,
@@
 implementation-specific behaviors whose implementation can
-inadvertedly lead to interference in the well-specified parts of the
+inadvertently lead to interference in the well-specified parts of the
 spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with

### 2020-10-07 paper/paper.tex
pass on macros
new edits

@@
 
-\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
+\vspace{0.2cm}
+\noindent
+\textbf{Cleansing}~We noticed that some of the tests we found
 depend on external libraries, which not all selected engines
@@
 
-\lbrack{}Test Harness\rbrack{}~We noticed that some engines use a
+\vspace{0.2cm}
+\noindent
+\textbf{Test Harness}~We noticed that some engines use a
 custom shell to run tests, including a harness with specific
@@
 
-\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
+\vspace{0.2cm}
+\noindent
+\textbf{Dedup}~The number of tests in \veight\ is low because
 we discarded duplicate tests with Mozilla and \jsc. The rationale is to
@@
   \centering
-  \includegraphics[trim=0 330 170 0,clip,width=0.85\textwidth]{diff-testing-runtimes}
-  \caption{\label{fig:workflow}Differential Testing infrastructure
-    overview.}
+  \includegraphics[width=0.85\textwidth]{figs/diff-testing-runtimes-2.pdf}
+  \caption{\label{fig:workflow}The workflow of the referred differential
+testing approach.}
 \end{figure}
@@
 
-\vspace{0.5ex} \lbrack{}Exploratory Phase\rbrack{} For the first
+\vspace{0.2cm}
+\noindent
+\textbf{Exploratory Phase} For the first
 three months of the study, our inspection process was exploratory.  In
@@
 
-\vspace{0.5ex} \lbrack{}Non-Exploratory Phase\rbrack{} Results
+\vspace{0.2cm}
+\noindent
+\textbf{Non-Exploratory Phase} Results
 obtained in the exploratory phase confirmed our expectations that most
@@
     \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
-    & Bug & 15 & 7\\
+    & Bug & 16 & 7\\
     \bottomrule
@@
 inconsistencies whenever possible. As for external validity, our
-results might not generalize to other test inputs and engines. To
-mitigate this threat, we carefully selected inputs from various
-sources according to a well-defined criteria. Likewise, we selected
-the engines by using using a documented criteria and found that the
+results might not generalize to other test inputs and engines.
+We though carefully selected inputs from various
+sources according to a well-defined criteria (Section~\ref{sec:seeds}).
+Likewise, we selected
+the engines by using using a documented criteria (Section~\ref{sec:methodology:engines})
+and found that the
 engines selected were associated, certainly not by coincidence, with

### 2020-10-09 paper/paper.tex
few edits

@@
   \caption{\label{fig:workflow}The workflow of the referred differential
-testing approach.}
+testing approach.
+In this Activity Diagram, the first black clircle is the start of the process, while the last one if the termination of the process.
+The green boxes mean activites to be done during the differential testing approach.
+The small black box mean that there are parallel activities (which in the end are combined).}
 \end{figure}

### 2020-10-21 paper/paper.tex
edits
alteração com dados do zenodo
new zenodo repo

@@
 differential testing. The source code produced and the generated data sets of tests
-and bugs are publicly available online at the following link:
-
-\dataRepo.
+and bugs are available on Zenodo~\footnote{https://zenodo.org/record/4116092} and online at the following link: \dataRepo.
 
